### 2025-01-09 AT_2025.qmd
Initial commit

---
title: "Alix Thomas, PA & PE lipid interactomics"
format: html
---

<!-- Data overview
Two lipid probes, PA and PE for a single cell line
 -->

## Publication information

DOI: <https://doi.org/10.1039/D4CC03599B>

## Publication overview

## Data visualization

```{r setup, echo=FALSE, include=FALSE}

## intitialize libraries
library(dplyr)
library(tidyr)
library(plotly)
library(ggplot2)
library(grid)
library(readr)
library(rmarkdown)
library(emojifont)
library(gt)
library(crosstalk)
library(DT)

## Read the data to a df
AT_2025_data <- readr::read_csv("DataTables/AT_ChemicalCommunications_2025.csv")

## Pivot the data to be longer
AT_2025_Long <- AT_2025_data |>
	pivot_longer(cols = -gene_name,
				names_to = c(".value", "Sample"),
				names_pattern = "^(logFC|pvalue|hit_annotation)_(.+)$")

print(unique(AT_2025_Long$hit_annotation))

# Organize the hit annotations as factors
AT_2025_Long$hit_annotation <- factor(pull(AT_2025_Long, hit_annotation), levels = c("enriched hit", "enriched candidate", "no hit", "NA"), ordered=TRUE)

```

```{r, echo=FALSE, include=FALSE}

ID <- c()
for(i in 0:(nrow(AT_2025_Long)/2)){
	ID[i] = i
}

### The ggplot customizations that make the ranked order plots
AT_2025_ranked_PE <- AT_2025_Long |>
    arrange(logFC) |>
	filter(Sample == "PE") |>
	mutate(ID = ID)

AT_2025_ranked_PA <- AT_2025_Long |>
    arrange(logFC) |>
	filter(Sample == "PA") |>
	mutate(ID = ID)

AT_2025_ranked <- rbind(AT_2025_ranked_PE, AT_2025_ranked_PA)

?merge.data.frame()

RankedOrderPlots <- AT_2025_ranked |>
    ggplot(aes(
        x = ID,
        y = logFC,
        color = factor(hit_annotation),
        fill = factor(hit_annotation),
        shape = factor(hit_annotation),
        alpha = factor(hit_annotation),
        size = factor(hit_annotation)
    )) +
    geom_point(aes(text = paste0("Gene name: ", gene_name, "\n",
                                 "LogFC: ", logFC, "\n",
                                 "p-value: ", pvalue, "\n"))) +
    geom_hline(yintercept = 0, linetype = 2) +
    geom_vline(xintercept = 0, linetype = 2) +
    scale_shape_manual(values = c("enriched hit" = 21,
                                  "enriched candidate" = 24,
                                  "no hit" = 22), 
                       name = "Trend") +
    scale_color_manual(values = c("enriched hit" = "black",
                                  "enriched candidate" = "black",
                                  "no hit" = "black"), 
                       name = "Trend") +
    scale_fill_manual(values = c("enriched hit" = "orange",
                                 "enriched candidate" = "purple",
                                 "no hit" = "black"), 
                      name = "Trend") +
    scale_alpha_manual(values = c("enriched hit" = 0.8,
                                  "enriched candidate" = 0.5,
                                  "no hit" = 0.25), 
                       name = "Trend") +
    scale_size_manual(values = c("enriched hit" = 4,
                                 "enriched candidate" = 2,
                                 "no hit" = 0.75), 
                      name = "Trend") +
    facet_wrap(~Sample) +
	ylab("Log2 fold-change") +
	xlab("Ranked-order gene") +
    theme_minimal() +
    theme(panel.border = element_rect(color = "#cfcfcf", fill = NA)) +
    theme(legend.title = element_text(size = 12, face = "bold")) +
    theme(axis.title = element_text(size = 12, face = "bold")) +
    theme(legend.text = element_text(size = 12))

m <- list(l=50, r = 50, b= 100, pad = 4)

RankedOrderPlotly <- ggplotly(RankedOrderPlots,
						  tooltip = c("text", dynamicTicks = TRUE),
						  hovermode = "closest",
						  autosize = T,
						  margin = m) |>
				layout(showlegend = FALSE)

```

#### Ranked-order Log2 Fold-change

:::{.border}
```{r, echo=FALSE}
#| fig-cap: "Ranked-order plots depict the relative enrichment of each protein versus control (y-axis) from lowest to highest. The left panel depicts the results of a pulldown using trifunctionalized phosphatidic acid; the right panel depicts the results of the pulldown using trifunctionalized phosphatidylethanolamine. Black proteins are unenriched or depleted in the presence of probe, Purple proteins are enriched to the probe but fall below a FDR or p-value threshold of significance, and Orange proteins surpass the threshold of significance (need details of threshold). "

RankedOrderPlotly
```
:::

```{r, echo=FALSE, include=FALSE}

### The ggplot customizations that make the volcano plots
VolcanoPlots <- AT_2025_Long |>
	ggplot(aes(x = logFC,
			   y = -log10(pvalue),
			   color = factor(hit_annotation), 
			   fill = factor(hit_annotation), 
			   shape = factor(hit_annotation),
			   alpha = factor(hit_annotation),
			   size = factor(hit_annotation))) +
	geom_point(aes(text = paste0("Gene name: ", gene_name, "\n",
								 "LogFC: ", logFC, "\n",
								 "p-value: ", pvalue, "\n"))) +
	geom_hline(yintercept = 0, linetype = 2) +
	geom_vline(xintercept = 0, linetype = 2) +
	scale_x_continuous(limits=c(-1.1 * max(abs(AT_2025_Long$logFC)), 1.1* max(abs(AT_2025_Long$logFC)))) +
    scale_y_continuous(limits=c(0, max(-log10(AT_2025_Long$pvalue)))) +
	scale_shape_manual(values = c("enriched hit" = 21,
								  "enriched candidate" = 24,
								  "no hit" = 22), 
					   name = "Trend") +
	scale_color_manual(values = c("enriched hit" = "black",
								 "enriched candidate" = "black",
								 "no hit" = "black"), 
								 name = "Trend") +
	scale_fill_manual(values = c("enriched hit" = "orange",
								  "enriched candidate" = "purple",
								  "no hit" = "black"), 
					   name = "Trend") +
	scale_alpha_manual(values = c("enriched hit" = 0.8,
								  "enriched candidate" = 0.5,
								  "no hit" = 0.25), 
					   name = "Trend") +
	scale_size_manual(values = c("enriched hit" = 4,
								  "enriched candidate" = 2,
								  "no hit" = 0.75), 
					   name = "Trend") +
	facet_wrap(~Sample) +
	xlab("Log2 fold-change") +
	ylab("-log10(p-value)") +
	theme_minimal() +
	theme(panel.border = element_rect(color = "#cfcfcf", fill = NA))+
	theme(strip.text = element_text(size = 12, face = "bold")) +
	theme(legend.title = element_text(size = 12, face = "bold")) +
	theme(axis.title = element_text(size = 12, face = "bold")) +
	theme(legend.text = element_text(size = 12))

m <- list(l=50, r = 50, b= 100, pad = 10)

VolcanoPlotly <- ggplotly(VolcanoPlots,
						  tooltip = c("text", dynamicTicks = TRUE),
						  hovermode = "closest",
						  autosize = T,
						  margin = m) |>
				layout(showlegend = FALSE)

VolcanoPlotly

```

#### Volcano plots

:::{.border}
```{r, echo=FALSE}
#| fig-cap: "Volcano plots depict the relative enrichment of each protein versus control (x-axis) and the statistical significance of each protein following a Student's t-test (y-axis, -log10 transformed). The left panel depicts the results of a pulldown using trifunctionalized phosphatidic acid; the right panel depicts the results of the pulldown using trifunctionalized phosphatidylethanolamine. Black proteins are unenriched or depleted in the presence of probe, Purple proteins are enriched to the probe but fall below a FDR or p-value threshold of significance, and Orange proteins surpass the threshold of significance (need details of threshold)"

VolcanoPlotly
```
:::

## Enriched proteins

#### Proteins enriched via pulldown with trifunctional phosphatidic acid

:::{.border}
```{r, echo=FALSE}
### Here is the code to make the filterable lists shown in the crosstalk table below

# Creates a reactive dataframe
AT_2025_Long_reactive <- crosstalk::SharedData$new(AT_2025_Long)

filter_select(id = "Sample",
				label = "Functional probe used in pulldown:", 
				sharedData = AT_2025_Long_reactive,
				group = ~Sample)

filter_select(id = "hit_annotation",
				label = "Enrichment criteria:", 
				sharedData = AT_2025_Long_reactive,
				group = ~hit_annotation)

datatable(AT_2025_Long_reactive)

```
:::

## Data download

{{< downloadthis DataTables/AT_ChemicalCommunications_2025.csv dname="AT_ChemicalCommunications_2025">}}

### 2025-01-09 index.qmd
Initial commit

---
title: "LipidInteractomics_Website"
---

This is a Quarto website.

To learn more about Quarto websites visit <https://quarto.org/docs/websites>.

### 2025-01-09 ggplot_styles.R

@@ -1,0 +1,17 @@
+# A centralized spot to save a custom theme across the whole site
+
+library(ggplot2)
+library(ggrepel)
+library(emojifont)
+library(dplyr)
+library(tidyr)
+
+# A universal Volcano plot theme
+
+VolcanoPlot <- function(data, enrichmentColumn, pvalueColumn, fillFactor, shapeFactor) {
+	
+	ggplot(data, aes(x = {{ enrichmentColumn }}, y = {{ pvalueColumn }}, color = "black", fill = {{fillFactor }}, shape = {{ shapeFactor }})) +
+		geom_point() +
+		labs( x = "Log2 fold-change",
+			  y = "p-value")
+}

### 2025-01-09 AT_2025.qmd
Updating site
Minor update to test push

@@
 title: "Alix Thomas, PA & PE lipid interactomics"
-format: html
+format: 
+  html:
+    embed-resources: true
+standalone: true
 ---
@@
 
-DOI: <https://doi.org/10.1039/D4CC03599B>
+**Authors:**
 
-## Publication overview
+**Date published:**
+
+**Journal, issue, CRBN:** Chemical Communications
+
+**DOI:** <https://doi.org/10.1039/D4CC03599B>
+
+## Abstract
+
+Phosphatidylethanolamine (PE) is a ubiquitous lipid species in higher eukaryotes which resides preferentially in mitochondria.
+Here, we synthesized a multifunctionalized PE derivative (1) de-signed to identify PE-binding proteins in intact cells through photo-crosslinking and subsequent isolation and proteomic analysis of the PE-protein conjugates.
+Due to its aromatic caging group, 1 is initial-ly concentrating in perinuclear membranes.
+After uncaging, rapid translocation to mitochondria was observed.
+Hence, the tool is useful for tracking PE location and for determining the PE interac-tome.
+A trifunctional phosphatidic acid (PA) derivative in compari-son was rapidly metabolized and is hence more limited in its use.
 

### 2025-01-09 AT_2025.qmd
Continuing minor updates

@@
 ---
-title: "Alix Thomas, PA & PE lipid interactomics"
+title: "Thomas et al. 2025"
 format: 
@@
 
-**Authors:**
+**Title:** Trifunctional lipid derivatives: PE’s mitochondrial interactome
+
+**Authors:** Alix Thomas, Rainer Mueller, Ana Kojic, Scotland E. Farley, Frank Stein, Per Haberkant, Carsten Schultz*
+
+(* corresponding: <schulcar@ohsu.edu>{target="_blank"})
 
@@
 
-**Journal, issue, CRBN:** Chemical Communications
+**Journal, ISSN:** Chemical Communications, 1359-7345, 1364-548X
 
-**DOI:** <https://doi.org/10.1039/D4CC03599B>
+**DOI:** <https://doi.org/10.1039/D4CC03599B>{target="_blank"}
 
@@
 Here, we synthesized a multifunctionalized PE derivative (1) de-signed to identify PE-binding proteins in intact cells through photo-crosslinking and subsequent isolation and proteomic analysis of the PE-protein conjugates.
-Due to its aromatic caging group, 1 is initial-ly concentrating in perinuclear membranes.
+Due to its aromatic caging group, 1 is initially concentrating in perinuclear membranes.
 After uncaging, rapid translocation to mitochondria was observed.
-Hence, the tool is useful for tracking PE location and for determining the PE interac-tome.
+Hence, the tool is useful for tracking PE location and for determining the PE interactome.
 A trifunctional phosphatidic acid (PA) derivative in compari-son was rapidly metabolized and is hence more limited in its use.

### 2025-01-10 AT_2025.qmd
New formatting .R file

@@
 
-## Read the data to a df
+## Set up the source for the standardized ggplot styles
+source("ggplot_styles.R")
+```
+
+```{r, echo=FALSE, include=FALSE}
+
+# Data wrangling to prepare Alix's data to the standardized inputs for my plotting functions.
+# Read the data to a df
 AT_2025_data <- readr::read_csv("DataTables/AT_ChemicalCommunications_2025.csv")
 
-## Pivot the data to be longer
+# Pivot the data to be longer
 AT_2025_Long <- AT_2025_data |>
@@
 
-```
-
-```{r, echo=FALSE, include=FALSE}
-
+# Building an ID column to maintain the order on the x-axis
 ID <- c()
@@
 
-### The ggplot customizations that make the ranked order plots
+# Applies the ID column to the PE results
 AT_2025_ranked_PE <- AT_2025_Long |>
@@
 
+# Applies the ID column to the PA results
 AT_2025_ranked_PA <- AT_2025_Long |>
@@
 
+# Assembles the dataset to plot
 AT_2025_ranked <- rbind(AT_2025_ranked_PE, AT_2025_ranked_PA)
-
-?merge.data.frame()
-
-RankedOrderPlots <- AT_2025_ranked |>
-    ggplot(aes(
-        x = ID,
-        y = logFC,
-        color = factor(hit_annotation),
-        fill = factor(hit_annotation),
-        shape = factor(hit_annotation),
-        alpha = factor(hit_annotation),
-        size = factor(hit_annotation)
-    )) +
-    geom_point(aes(text = paste0("Gene name: ", gene_name, "\n",
-                                 "LogFC: ", logFC, "\n",
-                                 "p-value: ", pvalue, "\n"))) +
-    geom_hline(yintercept = 0, linetype = 2) +
-    geom_vline(xintercept = 0, linetype = 2) +
-    scale_shape_manual(values = c("enriched hit" = 21,
-                                  "enriched candidate" = 24,
-                                  "no hit" = 22), 
-                       name = "Trend") +
-    scale_color_manual(values = c("enriched hit" = "black",
-                                  "enriched candidate" = "black",
-                                  "no hit" = "black"), 
-                       name = "Trend") +
-    scale_fill_manual(values = c("enriched hit" = "orange",
-                                 "enriched candidate" = "purple",
-                                 "no hit" = "black"), 
-                      name = "Trend") +
-    scale_alpha_manual(values = c("enriched hit" = 0.8,
-                                  "enriched candidate" = 0.5,
-                                  "no hit" = 0.25), 
-                       name = "Trend") +
-    scale_size_manual(values = c("enriched hit" = 4,
-                                 "enriched candidate" = 2,
-                                 "no hit" = 0.75), 
-                      name = "Trend") +
-    facet_wrap(~Sample) +
-	ylab("Log2 fold-change") +
-	xlab("Ranked-order gene") +
-    theme_minimal() +
-    theme(panel.border = element_rect(color = "#cfcfcf", fill = NA)) +
-    theme(legend.title = element_text(size = 12, face = "bold")) +
-    theme(axis.title = element_text(size = 12, face = "bold")) +
-    theme(legend.text = element_text(size = 12))
-
-m <- list(l=50, r = 50, b= 100, pad = 4)
-
-RankedOrderPlotly <- ggplotly(RankedOrderPlots,
-						  tooltip = c("text", dynamicTicks = TRUE),
-						  hovermode = "closest",
-						  autosize = T,
-						  margin = m) |>
-				layout(showlegend = FALSE)
 
@@
 :::{.border}
-```{r, echo=FALSE}
+```{r, echo=FALSE, warning=FALSE}
 #| fig-cap: "Ranked-order plots depict the relative enrichment of each protein versus control (y-axis) from lowest to highest.
@@
 
-RankedOrderPlotly
+RankedOrderPlotStandard(AT_2025_ranked)
 ```
 :::
-
-```{r, echo=FALSE, include=FALSE}
-
-### The ggplot customizations that make the volcano plots
-VolcanoPlots <- AT_2025_Long |>
-	ggplot(aes(x = logFC,
-			   y = -log10(pvalue),
-			   color = factor(hit_annotation), 
-			   fill = factor(hit_annotation), 
-			   shape = factor(hit_annotation),
-			   alpha = factor(hit_annotation),
-			   size = factor(hit_annotation))) +
-	geom_point(aes(text = paste0("Gene name: ", gene_name, "\n",
-								 "LogFC: ", logFC, "\n",
-								 "p-value: ", pvalue, "\n"))) +
-	geom_hline(yintercept = 0, linetype = 2) +
-	geom_vline(xintercept = 0, linetype = 2) +
-	scale_x_continuous(limits=c(-1.1 * max(abs(AT_2025_Long$logFC)), 1.1* max(abs(AT_2025_Long$logFC)))) +
-    scale_y_continuous(limits=c(0, max(-log10(AT_2025_Long$pvalue)))) +
-	scale_shape_manual(values = c("enriched hit" = 21,
-								  "enriched candidate" = 24,
-								  "no hit" = 22), 
-					   name = "Trend") +
-	scale_color_manual(values = c("enriched hit" = "black",
-								 "enriched candidate" = "black",
-								 "no hit" = "black"), 
-								 name = "Trend") +
-	scale_fill_manual(values = c("enriched hit" = "orange",
-								  "enriched candidate" = "purple",
-								  "no hit" = "black"), 
-					   name = "Trend") +
-	scale_alpha_manual(values = c("enriched hit" = 0.8,
-								  "enriched candidate" = 0.5,
-								  "no hit" = 0.25), 
-					   name = "Trend") +
-	scale_size_manual(values = c("enriched hit" = 4,
-								  "enriched candidate" = 2,
-								  "no hit" = 0.75), 
-					   name = "Trend") +
-	facet_wrap(~Sample) +
-	xlab("Log2 fold-change") +
-	ylab("-log10(p-value)") +
-	theme_minimal() +
-	theme(panel.border = element_rect(color = "#cfcfcf", fill = NA))+
-	theme(strip.text = element_text(size = 12, face = "bold")) +
-	theme(legend.title = element_text(size = 12, face = "bold")) +
-	theme(axis.title = element_text(size = 12, face = "bold")) +
-	theme(legend.text = element_text(size = 12))
-
-m <- list(l=50, r = 50, b= 100, pad = 10)
-
-VolcanoPlotly <- ggplotly(VolcanoPlots,
-						  tooltip = c("text", dynamicTicks = TRUE),
-						  hovermode = "closest",
-						  autosize = T,
-						  margin = m) |>
-				layout(showlegend = FALSE)
-
-VolcanoPlotly
-
-```
 
@@
 
-VolcanoPlotly
+VolcanoPlotStandardized(AT_2025_Long)
 ```

### 2025-01-10 ggplot_styles.R

@@ -6,12 +6,120 @@ library(emojifont)
 library(dplyr)
 library(tidyr)
 
-# A universal Volcano plot theme
+# A standardized Ranked Order plot theme
 
-VolcanoPlot <- function(data, enrichmentColumn, pvalueColumn, fillFactor, shapeFactor) {
+RankedOrderPlotStandard <- function(data) {
+    RankedOrderPlots <- data |>
+        ggplot(aes(x = ID,
+                   y = logFC,
+                   color = factor(hit_annotation),
+                   fill = factor(hit_annotation),
+                   shape = factor(hit_annotation),
+                   alpha = factor(hit_annotation),
+                   size = factor(hit_annotation))) +
+        geom_point(aes(text = paste0("Gene name: ", gene_name, "\n",
+                                    "LogFC: ", logFC, "\n",
+                                    "p-value: ", pvalue, "\n"))) +
+        geom_hline(yintercept = 0, linetype = 2) +
+        geom_vline(xintercept = 0, linetype = 2) +
+        scale_shape_manual(values = c("enriched hit" = 21,
+                                    "enriched candidate" = 24,
+                                    "no hit" = 22), 
+                        name = "Trend") +
+        scale_color_manual(values = c("enriched hit" = "black",
+                                    "enriched candidate" = "black",
+                                    "no hit" = "black"), 
+                        name = "Trend") +
+        scale_fill_manual(values = c("enriched hit" = "orange",
+                                    "enriched candidate" = "purple",
+                                    "no hit" = "black"), 
+                        name = "Trend") +
+        scale_alpha_manual(values = c("enriched hit" = 0.8,
+                                    "enriched candidate" = 0.5,
+                                    "no hit" = 0.25), 
+                        name = "Trend") +
+        scale_size_manual(values = c("enriched hit" = 4,
+                                    "enriched candidate" = 2,
+                                    "no hit" = 0.75), 
+                        name = "Trend") +
+        facet_wrap(~Sample) +
+        ylab("Log2 fold-change") +
+        xlab("Ranked-order gene") +
+        theme_minimal() +
+        theme(panel.border = element_rect(color = "#cfcfcf", fill = NA)) +
+        theme(legend.title = element_text(size = 12, face = "bold")) +
+        theme(axis.title = element_text(size = 12, face = "bold")) +
+        theme(legend.text = element_text(size = 12))
+
[…]

### 2025-01-10 AT_2025.qmd
Adding a page for Scotty's ACS CB paper

@@
 :::{.border}
-```{r, echo=FALSE}
+```{r, echo=FALSE, warning=FALSE}
 #| fig-cap: "Volcano plots depict the relative enrichment of each protein versus control (x-axis) and the statistical significance of each protein following a Student's t-test (y-axis, -log10 transformed).
@@
 ## Enriched proteins
-
-#### Proteins enriched via pulldown with trifunctional phosphatidic acid
 

### 2025-01-10 SF_2024.qmd
Adding a page for Scotty's ACS CB paper

---
title: "Farley et al. 2024"
format: 
  html:
    embed-resources: true
standalone: true
---

```{r setup, echo=FALSE, include=FALSE}

## Publication information

**Title:** Trifunctional Sphinganine: A New Tool to Dissect Sphingolipid Function

**Authors:** Scotland E. Farley, Frank Stein, Per Haberkant, Fikadu G. Tafesse, Carsten Schultz*

(* corresponding: <schulcar@ohsu.edu>{target="_blank"})

**Date published:**

**Journal, ISSN:** [ACS Chemical Biology](https://pubs.acs.org/doi/10.1021/acschembio.3c00554){target="_blank"}, 1554-8929, 1554-8937

**DOI:** <https://doi.org/10.1021/acschembio.3c00554>{target="_blank"}

## Abstract

Functions of the sphingolipids sphingosine and sphinganine in cells are not well established. While some signaling roles for sphingosine have been elucidated, the closely related sphinganine has been described only insofar as it does not elicit many of the same signaling responses. The underlying mechanisms behind the cell biological differences between these lipids are not well understood. Here, we prepared multifunctionalized derivatives of the two lipid species that only differ in a single double bond of the carbon backbone. Using these novel probes, we were able to define their spatiotemporal distribution within cells. Furthermore, we used these tools to systematically map the protein interactomes of both lipids. The lipid-protein conjugates, prepared through photo-crosslinking in live cells and extraction via click chemistry to azide beads, revealed significant differences in the captured proteins, highlighting their distinct roles in various cellular processes. This work elucidates mechanistic differences between these critical lipids and sets the foundation for further studies on the functions of sphingosine and sphinganine.

## Data visualization

#### Ranked-order Log2 Fold-change plots

#### Volcano plots

## Enriched Proteins

### 2025-01-10 AT_2025.qmd
Update before pausing

@@
 	pivot_longer(cols = -gene_name,
-				names_to = c(".value", "Sample"),
+				names_to = c(".value", "LipidProbe"),
 				names_pattern = "^(logFC|pvalue|hit_annotation)_(.+)$")
@@
     arrange(logFC) |>
-	filter(Sample == "PE") |>
+	filter(LipidProbe == "PE") |>
 	mutate(ID = ID)
@@
     arrange(logFC) |>
-	filter(Sample == "PA") |>
+	filter(LipidProbe == "PA") |>
 	mutate(ID = ID)
@@
 
-filter_select(id = "Sample",
+filter_select(id = "LipidProbe",
 				label = "Functional probe used in pulldown:", 
 				sharedData = AT_2025_Long_reactive,
-				group = ~Sample)
+				group = ~LipidProbe)
 

### 2025-01-10 SF_2024.qmd
Update before pausing

@@
 ```{r setup, echo=FALSE, include=FALSE}
+source("ggplot_styles.R")
+
+SF_2024_data <- readr::read_csv("DataTables/SF_ACS-ChemBio_2024_Limma_results_V3.csv")
+
+SF_2024_data_2 <- SF_2024_data |>
+	select(gene_name, keep_Huh7, comparison, logFC, pvalue, hit_annotation) |>
+	filter(keep_Huh7 == TRUE) |>
+	select(-keep_Huh7) |>
+	glimpse()
+
+print(head(SF_2024_data_2))
+```
 

### 2025-01-10 ggplot_styles.R

@@ -42,7 +42,7 @@ RankedOrderPlotStandard <- function(data) {
                                     "enriched candidate" = 2,
                                     "no hit" = 0.75), 
                         name = "Trend") +
-        facet_wrap(~Sample) +
+        facet_wrap(~LipidProbe) +
         ylab("Log2 fold-change") +
         xlab("Ranked-order gene") +
         theme_minimal() +
@@ -101,7 +101,7 @@ VolcanoPlotStandardized <- function(data) {
                                     "enriched candidate" = 2,
                                     "no hit" = 0.75), 
                         name = "Trend") +
-        facet_wrap(~Sample) +
+        facet_wrap(~LipidProbe) +
         xlab("Log2 fold-change") +
         ylab("-log10(p-value)") +
         theme_minimal() +

### 2025-01-10 SF_2024.qmd
Scotty's data is live

--- 2025-01-10 SF_2024.qmd
@@
 ```{r setup, echo=FALSE, include=FALSE}
+## intitialize libraries
+library(dplyr)
+library(tidyr)
+library(plotly)
+library(ggplot2)
+library(grid)
+library(readr)
+library(rmarkdown)
+library(emojifont)
+library(gt)
+library(crosstalk)
+library(DT)
+
+## Opening the source file for the ggplot custom theme
+source("ggplot_styles.R")
+
+## Some data wrangling to clean up Scotty's data
+SF_2024_data_raw <- readr::read_csv("DataTables/SF_ACS-ChemBio_2024_Limma_results_V3.csv")
+
+SF_2024_data <- SF_2024_data_raw |>
+	select(gene_name, keep_Huh7, comparison, logFC, pvalue, hit_annotation) |>
+	filter(keep_Huh7 == TRUE) |>
+	select(-keep_Huh7) |>
+	mutate(LipidProbe = case_when(comparison == "FA_8_3_UV - FA_8_3_noUV" ~ "8-3 FA",
+															 comparison == "FA_1_10_UV - FA_1_10_noUV" ~ "1-10 FA",
+															 comparison == "Spa_UV - Spa_noUV" ~ "Spa",
+															 comparison == "Sph_UV - Sph_noUV" ~ "Sph")) |>
+	filter(LipidProbe == "8-3 FA" | LipidProbe == "1-10 FA" | LipidProbe == "Spa" | LipidProbe == "Sph") |>
+	select(-comparison) |>
+	glimpse()
+
+# Organize the hit annotations as factors
+SF_2024_data$hit_annotation <- factor(pull(SF_2024_data, hit_annotation), levels = c("enriched hit", "hit", "enriched candidate", "candidate", "no hit", "NA"), ordered = TRUE)
+
+# Organize the probes as factors
+SF_2024_data$LipidProbe <- factor(pull(SF_2024_data, LipidProbe), levels = c("Spa", "Sph", "8-3 FA", "1-10 FA"), ordered = TRUE)
+
+# Building an ID column to maintain the order on the x-axis
+ID <- c()
+for(i in 0:(nrow(SF_2024_data)/4)){
+	ID[i] = i
+}
+
+# Applies the ID column to the 1-10 FA results
+SF_2024_ranked_1_10_FA <- SF_2024_data |>
+    arrange(logFC) |>
+	filter(LipidProbe == "1-10 FA") |>
+	mutate(ID = ID)
+
+# Applies the ID column to the 8-3 FA results
+SF_2024_ranked_8_3_FA <- SF_2024_data |>
+    arrange(logFC) |>
+	filter(LipidProbe == "8-3 FA") |>
+	mutate(ID = ID)
+
+# Applies the ID column to the Spa results
+SF_2024_ranked_Spa <- SF_2024_data |>
+    arrange(logFC) |>
+	filter(LipidProbe == "Spa") |>
+	mutate(ID = ID)
+
+# Applies the ID column to the Sph results
+SF_2024_ranked_Sph <- SF_2024_data |>
+    arrange(logFC) |>
+	filter(LipidProbe == "Sph") |>
+	mutate(ID = ID)
+
+# Assembles the dataset to plot
+SF_2024_ranked <- rbind(SF_2024_ranked_Sph, SF_2024_ranked_Spa, SF_2024_ranked_8_3_FA, SF_2024_ranked_1_10_FA)
+
+unique(SF_2024_data$hit_annotation)
+
+print(head(SF_2024_data))
+```
 
@@
 
+:::{.border}
+```{r, echo=FALSE}
+#| fig-cap: ""
+
+RankedOrderPlotStandard(SF_2024_ranked)
+```
+:::
+
 #### Volcano plots
 
+:::{.border}
+```{r, echo=FALSE}
+#| fig-cap: ""
+
+VolcanoPlotStandardized(SF_2024_data)
+
+```
+:::
+
 ## Enriched Proteins
+
+:::{.border}
+```{r, echo=FALSE, warning=FALSE}
+### Here is the code to make the filterable lists shown in the crosstalk table below
+
+# Creates a reactive dataframe
+SF_2024_data_reactive <- crosstalk::SharedData$new(SF_2024_data)
+
+filter_select(id = "LipidProbe",
+				label = "Functional probe used in pulldown:", 
+				sharedData = SF_2024_data_reactive,
+				group = ~LipidProbe)
+
+filter_select(id = "hit_annotation",
+				label = "Enrichment criteria:", 
+				sharedData = SF_2024_data_reactive,
+				group = ~hit_annotation)
+
+datatable(SF_2024_data_reactive)
+```
+:::

### 2025-01-10 ggplot_styles.R

@@ -23,23 +23,33 @@ RankedOrderPlotStandard <- function(data) {
         geom_hline(yintercept = 0, linetype = 2) +
         geom_vline(xintercept = 0, linetype = 2) +
         scale_shape_manual(values = c("enriched hit" = 21,
+                                    "hit" = 21,
                                     "enriched candidate" = 24,
+                                    "candidate" = 24,
                                     "no hit" = 22), 
                         name = "Trend") +
         scale_color_manual(values = c("enriched hit" = "black",
+                                    "hit" = "black",
                                     "enriched candidate" = "black",
+                                    "candidate" = "black",
                                     "no hit" = "black"), 
                         name = "Trend") +
         scale_fill_manual(values = c("enriched hit" = "orange",
+                                    "hit" = "orange",
                                     "enriched candidate" = "purple",
+                                    "candidate" = "purple",
                                     "no hit" = "black"), 
                         name = "Trend") +
         scale_alpha_manual(values = c("enriched hit" = 0.8,
+                                    "hit" = 0.8,
                                     "enriched candidate" = 0.5,
+                                    "candidate" = 0.5,
                                     "no hit" = 0.25), 
                         name = "Trend") +
         scale_size_manual(values = c("enriched hit" = 4,
+                                    "hit" = 4,
                                     "enriched candidate" = 2,
+                                    "candidate" = 2, 
                                     "no hit" = 0.75), 
                         name = "Trend") +
         facet_wrap(~LipidProbe) +
@@ -79,26 +89,36 @@ VolcanoPlotStandardized <- function(data) {
                                      "p-value: ", pvalue, "\n"))) +
         geom_hline(yintercept = 0, linetype = 2) +
         geom_vline(xintercept = 0, linetype = 2) +
-        scale_x_continuous(limits=c(-1.1 * max(abs(AT_2025_Long$logFC)), 1.1* max(abs(AT_2025_Long$logFC)))) +
-        scale_y_continuous(limits=c(0, max(-log10(AT_2025_Long$pvalue)))) +
+        scale_x_continuous(limits=c(-1.1 * max(abs(data$logFC)), 1.1* max(abs(data$logFC)))) +
+        scale_y_continuous(limits=c(0, max(-log10(data$pvalue)))) +
         scale_shape_manual(values = c("enriched hit" = 21,
-                                      "enriched candidate" = 24,
-                                      "no hit" = 22), 
-                           name = "Trend") +
+                                    "hit" = 21,
[…]

### 2025-01-10 AT_2025.qmd
Formatting updates

@@
 title: "Thomas et al. 2025"
+subtitle: "Trifunctional lipid derivatives: PE’s mitochondrial interactome"
 format: 
@@
 
-## Publication information
+Alix Thomas, Rainer Mueller, Ana Kojic, Scotland E. Farley, Frank Stein, Per Haberkant, Carsten Schultz
 
-**Title:** Trifunctional lipid derivatives: PE’s mitochondrial interactome
+Correspondence: <schulcar@ohsu.edu>{target="_blank"}
 
-**Authors:** Alix Thomas, Rainer Mueller, Ana Kojic, Scotland E. Farley, Frank Stein, Per Haberkant, Carsten Schultz*
+Chemical Communications
 
-(* corresponding: <schulcar@ohsu.edu>{target="_blank"})
-
-**Date published:**
-
-**Journal, ISSN:** Chemical Communications, 1359-7345, 1364-548X
-
-**DOI:** <https://doi.org/10.1039/D4CC03599B>{target="_blank"}
+<https://doi.org/10.1039/D4CC03599B>{target="_blank"}
 
@@
 
-{{< downloadthis DataTables/AT_ChemicalCommunications_2025.csv dname="AT_ChemicalCommunications_2025">}}
+{{< downloadthis DataTables/AT_ChemicalCommunications_2025_download.csv dname="AT_ChemicalCommunications_2025">}}

### 2025-01-10 ggplot_styles.R

@@ -56,7 +56,8 @@ RankedOrderPlotStandard <- function(data) {
         ylab("Log2 fold-change") +
         xlab("Ranked-order gene") +
         theme_minimal() +
-        theme(panel.border = element_rect(color = "#cfcfcf", fill = NA)) +
+        theme(text = element_text(family = "serif")) +
+        theme(panel.border = element_rect(color = NA, fill = NA)) +
         theme(legend.title = element_text(size = 12, face = "bold")) +
         theme(axis.title = element_text(size = 12, face = "bold")) +
         theme(legend.text = element_text(size = 12))
@@ -125,7 +126,8 @@ VolcanoPlotStandardized <- function(data) {
         xlab("Log2 fold-change") +
         ylab("-log10(p-value)") +
         theme_minimal() +
-        theme(panel.border = element_rect(color = "#cfcfcf", fill = NA))+
+        theme(text = element_text(family = "serif")) +
+        theme(panel.border = element_rect(color = NA, fill = NA))+
         theme(strip.text = element_text(size = 12, face = "bold")) +
         theme(legend.title = element_text(size = 12, face = "bold")) +
         theme(axis.title = element_text(size = 12, face = "bold")) +

### 2025-01-10 IndividualStudies/SF_2024.qmd
Smoothing site architecture

--- 2025-01-10 SF_2024.qmd
@@
 title: "Farley et al. 2024"
+subtitle: "Trifunctional Sphinganine: A New Tool to Dissect Sphingolipid Function"
 format: 
@@
 
+write.csv(x = SF_2024_data, file = "DataTables/SF_ACS-Chem-Bio_2024_download.csv")
+
 # Building an ID column to maintain the order on the x-axis
@@
 
-## Publication information
+Scotland E. Farley, Frank Stein, Per Haberkant, Fikadu G. Tafesse, Carsten Schultz*
 
-**Title:** Trifunctional Sphinganine: A New Tool to Dissect Sphingolipid Function
+Correspondence: <schulcar@ohsu.edu>{target="_blank"}
 
-**Authors:** Scotland E. Farley, Frank Stein, Per Haberkant, Fikadu G. Tafesse, Carsten Schultz*
+2024-02-16
 
-(* corresponding: <schulcar@ohsu.edu>{target="_blank"})
+[ACS Chemical Biology](https://pubs.acs.org/doi/10.1021/acschembio.3c00554){target="_blank"}
 
-**Date published:**
-
-**Journal, ISSN:** [ACS Chemical Biology](https://pubs.acs.org/doi/10.1021/acschembio.3c00554){target="_blank"}, 1554-8929, 1554-8937
-
-**DOI:** <https://doi.org/10.1021/acschembio.3c00554>{target="_blank"}
+<https://doi.org/10.1021/acschembio.3c00554>{target="_blank"}
 
@@
 :::{.border}
-```{r, echo=FALSE}
+```{r, echo=FALSE, warning=FALSE}
 #| fig-cap: ""
@@
 :::
+
+## Data download
+
+{{< downloadthis DataTables/SF_ACS-Chem-Bio_2024_download.csv dname="SF_ACS-Chem-Bio_2024">}}

### 2025-01-10 IndividualStudies/AT_2025.qmd
added checkboxes to table

--- 2025-01-10 AT_2025.qmd
@@
 
-filter_select(id = "LipidProbe",
-				label = "Functional probe used in pulldown:", 
+htmltools::tags$div(
+  class = "filter-container",
+  filter_checkbox(id = "LipidProbe",
+                  label = "Lipid probe in pulldown:", 
                   sharedData = AT_2025_Long_reactive,
-				group = ~LipidProbe)
-
-filter_select(id = "hit_annotation",
+                  group = ~LipidProbe),
+  filter_checkbox(id = "hit_annotation",
                   label = "Enrichment criteria:", 
@@
                   group = ~hit_annotation)
+)
 

### 2025-01-10 IndividualStudies/SF_2024.qmd
added checkboxes to table

@@
 library(DT)
+library(htmltools)
 
@@
 
-filter_select(id = "LipidProbe",
-				label = "Functional probe used in pulldown:", 
+htmltools::tags$div(
+  class = "filter-container",
+  filter_checkbox(id = "LipidProbe",
+                  label = "Lipid probe in pulldown:", 
                   sharedData = SF_2024_data_reactive,
-				group = ~LipidProbe)
-
-filter_select(id = "hit_annotation",
+                  group = ~LipidProbe),
+  filter_checkbox(id = "hit_annotation",
                   label = "Enrichment criteria:", 

### 2025-01-10 IndividualStudies/AT_2025.qmd
prepping demo for Carsten

@@
   html:
-    embed-resources: true
-standalone: true
+    embed-resources: false
+standalone: false
 ---
@@
 
+Check the boxes below to filter the dataset by which lipid probe was used in the pulldown and by significance thresholds.
+
 :::{.border}
 ```{r, echo=FALSE}
-### Here is the code to make the filterable lists shown in the crosstalk table below
 
-# Creates a reactive dataframe
+# Here is the code to make the filterable lists shown in the crosstalk table below
+
+## Creates a reactive dataframe
 AT_2025_Long_reactive <- crosstalk::SharedData$new(AT_2025_Long)
@@
 
-datatable(AT_2025_Long_reactive)
+?crosstalk::filter_checkbox()
+
+## Displays the reactive dataframe
+datatable(AT_2025_Long_reactive, options = list(pageLength = 20))
 

### 2025-01-10 IndividualStudies/SF_2024.qmd
prepping demo for Carsten

@@
 
+Check the boxes below to filter the dataset by which lipid probe was used in the pulldown and by significance thresholds.
+
 :::{.border}
 ```{r, echo=FALSE, warning=FALSE}
-### Here is the code to make the filterable lists shown in the crosstalk table below
 
-# Creates a reactive dataframe
+# Here is the code to make the filterable lists shown in the crosstalk table below
+
+## Creates a reactive dataframe
 SF_2024_data_reactive <- crosstalk::SharedData$new(SF_2024_data)
@@
 
-datatable(SF_2024_data_reactive)
+## Displays the reactive dataframe
+datatable(SF_2024_data_reactive, options = list(pageLength = 25))
+
 ```

### 2025-01-10 TrifunctionalLipidProbesOverview.qmd
prepping demo for Carsten

---
title: "Trifunctional Lipid Probes Primer"
author: "Gaelen Guzman"
format: 
  html:
    embed-resources: false
standalone: true
---

### 2025-01-11 IndividualStudies/AT_2025.qmd
Committing EOD

@@
 
-print(unique(AT_2025_Long$hit_annotation))
-
 # Organize the hit annotations as factors
@@
 The left panel depicts the results of a pulldown using trifunctionalized phosphatidic acid; the right panel depicts the results of the pulldown using trifunctionalized phosphatidylethanolamine.
-Black proteins are unenriched or depleted in the presence of probe, Purple proteins are enriched to the probe but fall below a FDR or p-value threshold of significance, and Orange proteins surpass the threshold of significance (need details of threshold).
-"
+Black proteins are unenriched or depleted in the presence of probe, Purple proteins are enriched to the probe but fall below a FDR or p-value threshold of significance, and Orange proteins surpass the threshold of significance (need details of threshold)."
 
@@
 The left panel depicts the results of a pulldown using trifunctionalized phosphatidic acid; the right panel depicts the results of the pulldown using trifunctionalized phosphatidylethanolamine.
-Black proteins are unenriched or depleted in the presence of probe, Purple proteins are enriched to the probe but fall below a FDR or p-value threshold of significance, and Orange proteins surpass the threshold of significance (need details of threshold)"
+Black proteins are unenriched or depleted in the presence of probe, Purple proteins are enriched to the probe but fall below a FDR or p-value threshold of significance, and Orange proteins surpass the threshold of significance (need details of threshold)."
 

### 2025-01-11 IndividualStudies/SF_2024.qmd
Committing EOD

@@
 
+## This is a little messy, but converts the raw data Scotty received from Frank and Per to a clean and minimal dataframe.
 SF_2024_data <- SF_2024_data_raw |>
@@
 SF_2024_data$LipidProbe <- factor(pull(SF_2024_data, LipidProbe), levels = c("Spa", "Sph", "8-3 FA", "1-10 FA"), ordered = TRUE)
-
-write.csv(x = SF_2024_data, file = "DataTables/SF_ACS-Chem-Bio_2024_download.csv")
 
@@
 SF_2024_ranked <- rbind(SF_2024_ranked_Sph, SF_2024_ranked_Spa, SF_2024_ranked_8_3_FA, SF_2024_ranked_1_10_FA)
-
-unique(SF_2024_data$hit_annotation)
-
-print(head(SF_2024_data))
 ```
@@
 ```{r, echo=FALSE, warning=FALSE}
-#| fig-cap: ""
+#| fig-cap: "Ranked-order plots depict the relative enrichment of each protein versus control (y-axis) from lowest to highest.
+The left panel depicts the results of a pulldown using trifunctionalized phosphatidic acid; the right panel depicts the results of the pulldown using trifunctionalized phosphatidylethanolamine.
+Black proteins are unenriched or depleted in the presence of probe, Purple proteins are enriched to the probe but fall below a FDR or p-value threshold of significance, and Orange proteins surpass the threshold of significance (need details of threshold)."
 
@@
 ```{r, echo=FALSE, warning=FALSE}
-#| fig-cap: ""
+#| fig-cap: "Volcano plots depict the relative enrichment of each protein versus control (x-axis) and the statistical significance of each protein following a Student's t-test (y-axis, -log10 transformed).
+The left panel depicts the results of a pulldown using trifunctionalized phosphatidic acid; the right panel depicts the results of the pulldown using trifunctionalized phosphatidylethanolamine.
+Black proteins are unenriched or depleted in the presence of probe, Purple proteins are enriched to the probe but fall below a FDR or p-value threshold of significance, and Orange proteins surpass the threshold of significance (need details of threshold)."
 

### 2025-01-11 MaintenanceInstructions.qmd
Committing EOD

---
title: "Maintenance Instructions"
author: "Gaelen Guzman"
date: 2025/01/09
format: 
  html:
    embed-resources: true
standalone: true
---

## Site Organization

I've done my best to make the site organization logical, but really only the next person to try to update this site can be the judge on whether I succeeded in that...

Under the "IndividualStudies" folder are the .qmd files that define the preparation of each corresponding .html page. The data going into these .qmd files is stored under the "DataTables" subfolder.

The _quarto.yml page is described further below, but here it should be mentioned that it will need to be modified to add pages to the site, as it defines the linking structure throughout the whole site.

## Maintenance

### Basic overview

This site was built using Quarto. This is a form of R Markdown that is highly documented, and one can learn how to modify this site here: <https://quarto.org/docs/websites>{target="_blank"}.

The overarching formatting of the site is controlled within the _quarto.yml file. Here one can update the site theme from the array of [Bootswatch](https://bootswatch.com/){target="_blank"} themes, or if you're feeling ambitious you can design your own theme.

When making updates to the site, one first edits/makes a file, then you use the Bash command "quarto render". This will update the site directory within the _site folder. There are a lot of ways to do the editing, but it's nicest to use the IDE Visual Studio Code because there's a terminal in-window and you can see nice previews of what the site will look like without leaving the program.

Any changes can then be pushed to the github repository; Netlify will pull the changes and automatically deploy the updated site! See site owners for Netlify login information and .git access. It will be TBD how GitHub ownership is transferred after I leave.

### Quarto formatting

I have found that Quarto is highly documented and it's pretty easy to figure out how to format or change the way things look (if all else fails, ask ChatGPT and you usually get a pretty good answer).

As a reference to help get you started, I very much appreciated [this blog post](https://blog.posertinlab.com/posts/2023-06-09-writing-a-dissertation-in-quarto/){target="_blank"} by Richard Posert about using Quarto.

I honestly get the most confused when it comes to formatting the _quarto.yml file because there aren't many fully-fleshed examples out there for all the options. This is where I've (embarrassingly) leaned on ChatGPT for help -- it's not always right, but it's usually close enough that you can make it work properly anyways.

If you want to add a page, you need to make a new .qmd file in the proper subfolder and render it as an .html file (conveniently, the Preview button in VS Code does that for you, but you can use whatever IDE you want). Then you need to add two lines to the .yml file so that the page is properly linked on the sidebar or navbar (if you don't it'll be unlinked and you'll need to know the whole path to find it, like this maintenance page).

If your data looks at all like [Alix's](IndividualStudies/DataTables/AT_ChemicalCommunications_2025.csv){target="_blank"} or [Scotty's](IndividualStudies/DataTables/SF_ACS-Chem-Bio_2024_download.csv){target="_blank"}, the ggplot functions I built in the ggplot_styles.R file will apply. Call the RankedOrderPlotStandard() and VolcanoPlotStandardized() functions to produce these plots with the same standardized formatting. On that note, you can alter the ggplot_styles.R file to change the standardized formatting.

There are a ton of things you can do within html divs, but I haven't dipped my toes in those yet - use these to finely adjust how elements of each page look.

### 2025-01-11 IndividualStudies/AT_2025.qmd
EOD commit third try

@@
 ---
-
+s
 <!-- Data overview

### 2025-01-11 MaintenanceInstructions.qmd
Wrapping up for the week

@@
 
-If your data looks at all like [Alix's](IndividualStudies/DataTables/AT_ChemicalCommunications_2025.csv){target="_blank"} or [Scotty's](IndividualStudies/DataTables/SF_ACS-Chem-Bio_2024_download.csv){target="_blank"}, the ggplot functions I built in the ggplot_styles.R file will apply.
+If your data looks at all like [Alix's](https://lipidinteractomicsrepository.netlify.app/individualstudies/at_2025){target="_blank"} or [Scotty's](https://lipidinteractomicsrepository.netlify.app/individualstudies/sf_2024){target="_blank"}, the ggplot functions I built in the ggplot_styles.R file will apply.
 Call the RankedOrderPlotStandard() and VolcanoPlotStandardized() functions to produce these plots with the same standardized formatting.

### 2025-01-12 IndividualStudies/SF_2024_B.qmd
Holy cow my git seems confused

--- 2025-01-11 IndividualStudies/SF_2024.qmd
@@
 ---
-title: "Farley et al. 2024"
-subtitle: "Trifunctional Sphinganine: A New Tool to Dissect Sphingolipid Function"
+title: "Farley et al. 2024 B"
+subtitle: "Trifunctional fatty acid derivatives: the impact of diazirine placement"
 format: 
@@
 	mutate(LipidProbe = case_when(comparison == "FA_8_3_UV - FA_8_3_noUV" ~ "8-3 FA",
-															 comparison == "FA_1_10_UV - FA_1_10_noUV" ~ "1-10 FA",
-															 comparison == "Spa_UV - Spa_noUV" ~ "Spa",
-															 comparison == "Sph_UV - Sph_noUV" ~ "Sph")) |>
+															 comparison == "FA_1_10_UV - FA_1_10_noUV" ~ "1-10 FA")) |>
 	filter(LipidProbe == "8-3 FA" | LipidProbe == "1-10 FA" | LipidProbe == "Spa" | LipidProbe == "Sph") |>
@@
 
+#write.csv(SF_2024_data, "IndividualStudies/DataTables/SF_Chem_Comm_2024_download.csv")
+
 # Building an ID column to maintain the order on the x-axis
 ID <- c()
-for(i in 0:(nrow(SF_2024_data)/4)){
+for(i in 0:(nrow(SF_2024_data)/2)){
 	ID[i] = i
@@
 
-# Applies the ID column to the Spa results
-SF_2024_ranked_Spa <- SF_2024_data |>
-    arrange(logFC) |>
-	filter(LipidProbe == "Spa") |>
-	mutate(ID = ID)
-
-# Applies the ID column to the Sph results
-SF_2024_ranked_Sph <- SF_2024_data |>
-    arrange(logFC) |>
-	filter(LipidProbe == "Sph") |>
-	mutate(ID = ID)
-
 # Assembles the dataset to plot
-SF_2024_ranked <- rbind(SF_2024_ranked_Sph, SF_2024_ranked_Spa, SF_2024_ranked_8_3_FA, SF_2024_ranked_1_10_FA)
+SF_2024_ranked <- rbind(SF_2024_ranked_8_3_FA, SF_2024_ranked_1_10_FA)
 ```
 
-Scotland E. Farley, Frank Stein, Per Haberkant, Fikadu G. Tafesse, Carsten Schultz*
+Scotland E. Farley, Ryu Hashimoto, Judah Evangelista, Frank Stein, Per Haberkant, Kazuya Kikuchi, Fikadu G. Tafesse, Carsten Schultz*
 
@@
 
-2024-02-16
+2024-05-25
 
-[ACS Chemical Biology](https://pubs.acs.org/doi/10.1021/acschembio.3c00554){target="_blank"}
+[Chemical Communications](https://xlink.rsc.org/?DOI=D4CC00974F){target="_blank"}
 
@@
 
-Functions of the sphingolipids sphingosine and sphinganine in cells are not well established.
-While some signaling roles for sphingosine have been elucidated, the closely related sphinganine has been described only insofar as it does not elicit many of the same signaling responses.
-The underlying mechanisms behind the cell biological differences between these lipids are not well understood.
-Here, we prepared multifunctionalized derivatives of the two lipid species that only differ in a single double bond of the carbon backbone.
-Using these novel probes, we were able to define their spatiotemporal distribution within cells.
-Furthermore, we used these tools to systematically map the protein interactomes of both lipids.
-The lipid-protein conjugates, prepared through photo-crosslinking in live cells and extraction via click chemistry to azide beads, revealed significant differences in the captured proteins, highlighting their distinct roles in various cellular processes.
-This work elucidates mechanistic differences between these critical lipids and sets the foundation for further studies on the functions of sphingosine and sphinganine.
+Functionalized lipid probes are a critical new tool to interrogate the function of individual lipid species, but the structural parameters that constrain their utility have not been thoroughly described.
+Functionalized lipid probes are a critical new tool to interrogate the function of individual lipid species, but the structural parameters that constrain their utility have not been thoroughly described.
+Here, we synthesize three palmitic acid derivatives with a diazirine at different positions on the acyl chain and examine their metabolism, subcellular localization, and protein interactions.
+We demonstrate that while they produce very similar metabolites and subcellular distributions, probes with the diazirine at either end pulldown distinct subsets of proteins after photo-crosslinking.
+This highlights the importance of thoughtful diazirine placement when developing probes based on biological molecules.
 
@@
 
-{{< downloadthis DataTables/SF_ACS-Chem-Bio_2024_download.csv dname="SF_ACS-Chem-Bio_2024">}}
+{{< downloadthis DataTables/SF_Chem_Comm_2024_download.csv dname="SF_Chem_Comm_2024">}}

### 2025-01-12 IndividualStudies/AT_2025.qmd
updating with two pages for SFs data

--- 2025-01-11 IndividualStudies/AT_2025.qmd
@@
 ---
-
 <!-- Data overview

### 2025-01-12 IndividualStudies/SF_2024.qmd
updating with two pages for SFs data

@@
 	select(-keep_Huh7) |>
-	mutate(LipidProbe = case_when(comparison == "FA_8_3_UV - FA_8_3_noUV" ~ "8-3 FA",
-															 comparison == "FA_1_10_UV - FA_1_10_noUV" ~ "1-10 FA",
-															 comparison == "Spa_UV - Spa_noUV" ~ "Spa",
+	mutate(LipidProbe = case_when(comparison == "Spa_UV - Spa_noUV" ~ "Spa",
 															 comparison == "Sph_UV - Sph_noUV" ~ "Sph")) |>
@@
 ID <- c()
-for(i in 0:(nrow(SF_2024_data)/4)){
+for(i in 0:(nrow(SF_2024_data)/2)){
 	ID[i] = i
 }
-
-# Applies the ID column to the 1-10 FA results
-SF_2024_ranked_1_10_FA <- SF_2024_data |>
-    arrange(logFC) |>
-	filter(LipidProbe == "1-10 FA") |>
-	mutate(ID = ID)
-
-# Applies the ID column to the 8-3 FA results
-SF_2024_ranked_8_3_FA <- SF_2024_data |>
-    arrange(logFC) |>
-	filter(LipidProbe == "8-3 FA") |>
-	mutate(ID = ID)
 
@@
 # Assembles the dataset to plot
-SF_2024_ranked <- rbind(SF_2024_ranked_Sph, SF_2024_ranked_Spa, SF_2024_ranked_8_3_FA, SF_2024_ranked_1_10_FA)
+SF_2024_ranked <- rbind(SF_2024_ranked_Sph, SF_2024_ranked_Spa)
 ```

### 2025-01-12 IndividualStudies/TestingCrosstalkAndPlotly.R

@@ -1,0 +1,15 @@
+library(crosstalk)
+library(plotly)
+
+shared_mtcars <- SharedData$new(mtcars)
+bscols(widths = c(3, NA),
+       list(
+         filter_checkbox("cyl", "Cylinders", shared_mtcars, ~cyl, inline = TRUE),
+         filter_checkbox("vs", "VS", shared_mtcars, ~vs, inline = TRUE)
+       ),
+       plotly::ggplotly(shared_mtcars %>% 
+                          ggplot(aes(x = mpg,group=paste0(cyl,vs))) + 
+                          geom_histogram(fill = "pale green",
+                                         color = "black") + 
+                          theme(legend.position = "none"))
+)

### 2025-01-13 IndividualStudies/SF_2024_B.qmd
Minor updates, new help symbol

@@
 
+## Study details
+
+### Lipid probes utilized
+
+### Cell line analyzed
+
+### Additional sample preparation <span class="help-symbol" title="e.g. sub-cellular fractionation, depletion, etc.">?</span>
+
 ## Data visualization
@@
 ## Displays the reactive dataframe
-datatable(SF_2024_data_reactive, options = list(pageLength = 25))
+datatable(SF_2024_data_reactive, options = list(pageLength = 20))
 

### 2025-01-13 IndividualStudies/AT_2025.qmd
Minor updates, new help symbol
New options for hiding details, showing refs

@@
 
+::: {.callout-note collapse="true"}
+
+## Study details
+
+#### Authors:
 Alix Thomas, Rainer Mueller, Ana Kojic, Scotland E. Farley, Frank Stein, Per Haberkant, Carsten Schultz
@@
 
+#### Journal:
 Chemical Communications
@@
 
-## Abstract
-
+#### Abstract
 Phosphatidylethanolamine (PE) is a ubiquitous lipid species in higher eukaryotes which resides preferentially in mitochondria.
@@
 A trifunctional phosphatidic acid (PA) derivative in compari-son was rapidly metabolized and is hence more limited in its use.
+
+#### Lipid probes utilized
+
+#### Cell line analyzed
+
+#### Additional sample preparation <span class="help-symbol" title="e.g. sub-cellular fractionation, depletion, etc.">?</span>
+:::
 
@@
 # Read the data to a df
-AT_2025_data <- readr::read_csv("DataTables/AT_ChemicalCommunications_2025.csv")
 
-# Pivot the data to be longer
-AT_2025_Long <- AT_2025_data |>
-	pivot_longer(cols = -gene_name,
-				names_to = c(".value", "LipidProbe"),
-				names_pattern = "^(logFC|pvalue|hit_annotation)_(.+)$")
+AT_2025_Long <- readr::read_csv("DataTables/AT_ChemicalCommunications_2025_download.csv")
 

### 2025-01-13 IndividualStudies/SF_2024.qmd
Minor updates, new help symbol
New options for hiding details, showing refs

@@
 
-## Some data wrangling to clean up Scotty's data
-SF_2024_data_raw <- readr::read_csv("DataTables/SF_ACS-ChemBio_2024_Limma_results_V3.csv")
-
-## This is a little messy, but converts the raw data Scotty received from Frank and Per to a clean and minimal dataframe.
-SF_2024_data <- SF_2024_data_raw |>
-	select(gene_name, keep_Huh7, comparison, logFC, pvalue, hit_annotation) |>
-	filter(keep_Huh7 == TRUE) |>
-	select(-keep_Huh7) |>
-	mutate(LipidProbe = case_when(comparison == "Spa_UV - Spa_noUV" ~ "Spa",
-															 comparison == "Sph_UV - Sph_noUV" ~ "Sph")) |>
-	filter(LipidProbe == "8-3 FA" | LipidProbe == "1-10 FA" | LipidProbe == "Spa" | LipidProbe == "Sph") |>
-	select(-comparison) |>
-	glimpse()
+# Opening the datatable for this page
+SF_2024_data <- readr::read_csv("DataTables/SF_ACS-Chem-Bio_2024_download.csv")
 
@@
 This work elucidates mechanistic differences between these critical lipids and sets the foundation for further studies on the functions of sphingosine and sphinganine.
+
+::: {.callout-note collapse="true"}
+
+## Study details
+
+#### Lipid probes utilized
+
+#### Cell line analyzed
+
+#### Additional sample preparation <span class="help-symbol" title="e.g. sub-cellular fractionation, depletion, etc.">?</span>
+:::
 

### 2025-01-13 IndividualStudies/SF_2024_B.qmd
New options for hiding details, showing refs

@@
 
-## Some data wrangling to clean up Scotty's data
-SF_2024_data_raw <- readr::read_csv("DataTables/SF_ACS-ChemBio_2024_Limma_results_V3.csv")
+# Opening the datatable for this page
+SF_2024_data <- readr::read_csv("DataTables/SF_Chem_Comm_2024_download.csv")
 
-## This is a little messy, but converts the raw data Scotty received from Frank and Per to a clean and minimal dataframe.
-SF_2024_data <- SF_2024_data_raw |>
-	select(gene_name, keep_Huh7, comparison, logFC, pvalue, hit_annotation) |>
-	filter(keep_Huh7 == TRUE) |>
-	select(-keep_Huh7) |>
-	mutate(LipidProbe = case_when(comparison == "FA_8_3_UV - FA_8_3_noUV" ~ "8-3 FA",
-															 comparison == "FA_1_10_UV - FA_1_10_noUV" ~ "1-10 FA")) |>
-	filter(LipidProbe == "8-3 FA" | LipidProbe == "1-10 FA" | LipidProbe == "Spa" | LipidProbe == "Sph") |>
-	select(-comparison) |>
-	glimpse()
-
-# Organize the hit annotations as factors
+# Organizing the hit annotations as factors
 SF_2024_data$hit_annotation <- factor(pull(SF_2024_data, hit_annotation), levels = c("enriched hit", "hit", "enriched candidate", "candidate", "no hit", "NA"), ordered = TRUE)
@@
 
+::: {.callout-note collapse="true"}
+
 ## Study details
 
-### Lipid probes utilized
+#### Lipid probes utilized
 
-### Cell line analyzed
+#### Cell line analyzed
 
-### Additional sample preparation <span class="help-symbol" title="e.g. sub-cellular fractionation, depletion, etc.">?</span>
+#### Additional sample preparation <span class="help-symbol" title="e.g. sub-cellular fractionation, depletion, etc.">?</span>
+:::
 

### 2025-01-13 TrifunctionalLipidProbesOverview.qmd
Committing EOD
New options for hiding details, showing refs

@@
 ---
+
+I could use help writing a succinct article here to describe the use of these probes.
+We can additionally reference prior publications here -- but I think it would be nice to have a novel description with figures for this site.
+
+I have a few example figures, but I am open to using whichever figures seem best -- if that is a new figure, I'll need guidance on what it should look like.
+
+:::{.border}
+![](SiteFigures/BaselineProteomics_ExperimentalDesign.png){group="Overview_gallery"}
+:::
+
+\br
+
+(Here's an example of what references would look like on the site: [@thomasTrifunctionalLipidDerivatives2025; @schultzFlashClickMultifunctionalized2022a; @schultzChemicalToolsLipid2023])

### 2025-01-13 index.qmd
added checkboxes to table
Committing EOD
Wrapping up for the week
New options for hiding details, showing refs

@@
 ---
-title: "LipidInteractomics_Website"
+title: "Lipid Interactomics Website"
 ---
 
-This is a Quarto website.
+A blurb about the objective of this site, maybe a gallery of images from select publications to put here.
 
-To learn more about Quarto websites visit <https://quarto.org/docs/websites>.
+Possible site names:
+
+* CLiP Database -- **C**lickable **Li**pid **P**roteomics Database
+
+* TriP Database -- **Tri**functional lipid **P**roteome Database
+
+* TriLiP Database -- **Tri**functional **L**ipid **P**roteome: A Resource for Trifunctional Lipid-Based Proteomics Data

### 2025-01-14 LipidProbe/Phosphatidylethanolamine.qmd
Beginning to overhaul site structure

---
title: "Trifunctional Phosphatidylethanolamine"
---

### 2025-01-14 MaintenanceInstructions.qmd
Minor updates, new help symbol
EOD update

@@
 standalone: true
+meta:
+  robots: "noindex"
 ---
@@
 If you want to add a page, you need to make a new .qmd file in the proper subfolder and render it as an .html file (conveniently, the Preview button in VS Code does that for you, but you can use whatever IDE you want).
-Then you need to add two lines to the .yml file so that the page is properly linked on the sidebar or navbar (if you don't it'll be unlinked and you'll need to know the whole path to find it, like this maintenance page).
+Then you need to add two lines to the .yml file so that the page is properly linked on the sidebar or navbar (first the href to denote the file path to the .html file, then the text to display on the page) -- if you don't add these, the page will remain unlinked and you'll need to know the whole URL to find it (like this maintenance page).
 

### 2025-01-14 about.qmd
EOD update

---
title: "About"
---

About this site

Contact the site administrators for additional information about protocols, experimental design, and website feedback:

(I am working on making a comment submission form which will send an email to a site admin -- something like ContactUs\@LipidInteractome.org)

### 2025-01-14 index.qmd
Beginning to overhaul site structure
EOD update

@@
 
-Possible site names:
-
-* CLiP Database -- **C**lickable **Li**pid **P**roteomics Database
-
-* TriP Database -- **Tri**functional lipid **P**roteome Database
-
-* TriLiP Database -- **Tri**functional **L**ipid **P**roteome: A Resource for Trifunctional Lipid-Based Proteomics Data
+A site map with big buttons leading to each of the lipid classes.

### 2025-01-14 index.qmd
successfully added some buttons to the home page

@@
 ---
-title: "Lipid Interactomics Website"
+title: "The Lipid Interactome Repository"
+format: 
+  html:
+    embed-resources: false
+standalone: false
 ---
@@
 
-A site map with big buttons leading to each of the lipid classes.
+```{=html}
+<div style="text-align: center; margin: 20px;">
+    <a href="LipidProbe/PhosphatidicAcid.qmd" style="text-decoration: none;">
+        <button style="background-color: #3498db; color: white; font-size: 20px; padding: 15px 30px; border: none; border-radius: 8px; margin: 10px; cursor: pointer;">
+            Phosphatidic Acid
+        </button>
+    </a>
+    <a href="LipidProbe/Phosphatidylethanolamine.qmd" style="text-decoration: none;">
+        <button style="background-color: #e74c3c; color: white; font-size: 20px; padding: 15px 30px; border: none; border-radius: 8px; margin: 10px; cursor: pointer;">
+            Phosphatidylethanolamine
+        </button>
+    </a>
+		<br>
+		<a href="LipidProbe/Diacylglycerol.qmd" style="text-decoration: none;">
+        <button style="background-color: #3277a8; color: white; font-size: 20px; padding: 15px 30px; border: none; border-radius: 8px; margin: 10px; cursor: pointer;">
+            Diacylglycerol
+        </button>
+    </a>
+		<br>
+    <a href="LipidProbe/Sphinganine.qmd" style="text-decoration: none;">
+        <button style="background-color: #2ecc71; color: white; font-size: 20px; padding: 15px 30px; border: none; border-radius: 8px; margin: 10px; cursor: pointer;">
+            Sphinganine
+        </button>
+    </a>
+		<a href="LipidProbe/Sphingosine.qmd" style="text-decoration: none;">
+        <button style="background-color: #eba434; color: white; font-size: 20px; padding: 15px 30px; border: none; border-radius: 8px; margin: 10px; cursor: pointer;">
+            Sphingosine
+        </button>
+    </a>
+		<a href="LipidProbe/FattyAcids.qmd" style="text-decoration: none;">
+        <button style="background-color: #ba34eb; color: white; font-size: 20px; padding: 15px 30px; border: none; border-radius: 8px; margin: 10px; cursor: pointer;">
+            Fatty Acid
+        </button>
+    </a>
+</div>
+```

### 2025-01-14 IndividualStudies/DH_2017.qmd
Added a page for Hoglinger  2017

---
title: "Höglinger et al. 2017"
subtitle: "Trifunctional lipid probes for comprehensive studies of single lipid species in living cells"
format:
  html:
    embed-resources: false
standalone: false
---

::: {.callout-note collapse="true"}

## Study details

#### Authors

Doris Höglinger, André Nadler,  Per Haberkant, Joanna Kirkpatrick, Martina Schifferer, Frank Stein, Sebastian Hauke, Forbes D. Porter, Carsten Schultz

Correspondence: <schulcar@ohsu.edu>{target="_blank"}

#### Journal

PNAS

<https://doi.org/10.1073/pnas.1611096114>{target="_blank"}

#### Abstract

Lipid-mediated signaling events regulate many cellular processes. Investigations of the complex underlying mechanisms are difficult because several different methods need to be used under varying conditions. Here we introduce multifunctional lipid derivatives to study lipid metabolism, lipid−protein interactions, and intracellular lipid localization with a single tool per target lipid. The probes are equipped with two photoreactive groups to allow photoliberation (uncaging) and photo–cross-linking in a sequential manner, as well as a click-handle for subsequent functionalization. We demonstrate the versatility of the design for the signaling lipids sphingosine and diacylglycerol; uncaging of the probe for these two species triggered calcium signaling and intracellular protein translocation events, respectively. We performed proteomic screens to map the lipid-interacting proteome for both lipids. Finally, we visualized a sphingosine transport deficiency in patient-derived Niemann−Pick disease type C fibroblasts by fluorescence as well as correlative light and electron microscopy, pointing toward the diagnostic potential of such tools. We envision that this type of probe will become important for analyzing and ultimately understanding lipid signaling events in a comprehensive manner.

#### Lipid probes utilized

Sphinganine

Diacylglycerol

8-3 Fatty acid

#### Cell line analyzed

[HeLa](https://www.atcc.org/products/ccl-2){target="_blank"}

#### Mass spectrometry quantification method

Peptide spectral counting

:::

## Data visualization

#### Heat map

#### Venn Diagram

## Data download

{{< downloadthis DataTables/DH_PNAS_2017_download.csv dname="DH_PNAS_2017">}}

### 2025-01-14 LipidProbe/Diacylglycerol.qmd
minor tweaks

---
title: "Trifunctional Diacylglycerol"
---

## Structure

## Subcellular localization

## Protein interactome

### 2025-01-14 LipidProbe/Sphingosine.qmd
minor tweaks
Testing embedded chem structures

--- 2025-01-14 LipidProbe/Diacylglycerol.qmd
@@
 ---
-title: "Trifunctional Diacylglycerol"
+title: "Trifunctional Sphingosine"
 ---
@@
 
+:::{.callout collapse="true"}
+
+#### Option 1: Static png
+
+![](/LipidProbe/Structures/SphingosineStructure.png)
+
+:::
+
+:::{.callout collapse="true"}
+#### Option 2: pubchem viewer embed
+
+```{=html}
+<iframe 
+    src="https://pubchem.ncbi.nlm.nih.gov/compound/Sphingosine#section=3D-Conformer&fullscreen=true" 
+    width="100%" 
+    height="1000" 
+    style="border:none;">
+</iframe>
+
+```
+:::
+
+(This might not be possible if the structure is not published to pubchem, there may be other options for embedding, but I don't know them right now)
+
 ## Subcellular localization

### 2025-01-14 index.qmd
Testing embedded chem structures

--- 2025-01-14 index.qmd
@@
 
-A site map with big buttons leading to each of the lipid classes.
+```{=html}
+<div style="text-align: center; margin: 20px;">
+    <a href="LipidProbe/PhosphatidicAcid.qmd" style="text-decoration: none;">
+        <button style="background-color: #3498db; color: white; font-size: 20px; padding: 15px 30px; border: none; border-radius: 8px; margin: 10px; cursor: pointer;">
+            Phosphatidic Acid
+        </button>
+    </a>
+    <a href="LipidProbe/Phosphatidylethanolamine.qmd" style="text-decoration: none;">
+        <button style="background-color: #e74c3c; color: white; font-size: 20px; padding: 15px 30px; border: none; border-radius: 8px; margin: 10px; cursor: pointer;">
+            Phosphatidylethanolamine
+        </button>
+    </a>
+		<br>
+		<a href="LipidProbe/Diacylglycerol.qmd" style="text-decoration: none;">
+        <button style="background-color: #3277a8; color: white; font-size: 20px; padding: 15px 30px; border: none; border-radius: 8px; margin: 10px; cursor: pointer;">
+            Diacylglycerol
+        </button>
+    </a>
+		<br>
+    <a href="LipidProbe/Sphinganine.qmd" style="text-decoration: none;">
+        <button style="background-color: #2ecc71; color: white; font-size: 20px; padding: 15px 30px; border: none; border-radius: 8px; margin: 10px; cursor: pointer;">
+            Sphinganine
+        </button>
+    </a>
+		<a href="LipidProbe/Sphingosine.qmd" style="text-decoration: none;">
+        <button style="background-color: #eba434; color: white; font-size: 20px; padding: 15px 30px; border: none; border-radius: 8px; margin: 10px; cursor: pointer;">
+            Sphingosine
+        </button>
+    </a>
+
+	<a href="LipidProbe/8-3_FattyAcid.qmd" style="text-decoration: none;">
+        <button style="background-color: #ba34eb; color: white; font-size: 20px; padding: 15px 30px; border: none; border-radius: 8px; margin: 10px; cursor: pointer;">
+            8-3 Fatty Acid
+        </button>
+    </a>
+
+    <a href="LipidProbe/1-10_FattyAcid.qmd" style="text-decoration: none;">
+        <button style="background-color: #a83260; color: white; font-size: 20px; padding: 15px 30px; border: none; border-radius: 8px; margin: 10px; cursor: pointer;">
+            1-10 Fatty Acid
+        </button>
+    </a>
+</div>
+```

### 2025-01-15 LipidProbe/PhosphatidylinositolTrisphosphate.qmd
added some PIP buttons, still need content

---
title: "Trifunctional Phosphatidylinositol 3,4,5-*bis*phosphate"
subtitle: "PI(3,4,5)P~3~"
---

## Structure

## Protein interactome

### 2025-01-15 index.qmd
added some PIP buttons, still need content

--- 2025-01-14 index.qmd
@@
 
-A site map with big buttons leading to each of the lipid classes.
+```{=html}
+<div style="text-align: center; margin: 20px;">
+    <a href="LipidProbe/PhosphatidicAcid.qmd" style="text-decoration: none;">
+        <button style="background-color: #3498db; color: white; font-size: 20px; padding: 15px 30px; border: none; border-radius: 8px; margin: 10px; cursor: pointer;">
+            Phosphatidic Acid
+        </button>
+    </a>
+    <a href="LipidProbe/Phosphatidylethanolamine.qmd" style="text-decoration: none;">
+        <button style="background-color: #e74c3c; color: white; font-size: 20px; padding: 15px 30px; border: none; border-radius: 8px; margin: 10px; cursor: pointer;">
+            Phosphatidylethanolamine
+        </button>
+    </a>
+
+    <a href="LipidProbe/PhosphatidylinositolBisphosphate.qmd" style="text-decoration: none;">
+        <button style="background-color: #a86532; color: white; font-size: 20px; padding: 15px 30px; border: none; border-radius: 8px; margin: 10px; cursor: pointer;">
+            PI(4,5)P~2~
+        </button>
+    </a>
+
+    <a href="LipidProbe/PhosphatidylinositolTrisphosphate.qmd" style="text-decoration: none;">
+        <button style="background-color: #8732a8; color: white; font-size: 20px; padding: 15px 30px; border: none; border-radius: 8px; margin: 10px; cursor: pointer;">
+            PI(3,4,5)P~3~
+        </button>
+    </a>
+
+		<br>
+		<a href="LipidProbe/Diacylglycerol.qmd" style="text-decoration: none;">
+        <button style="background-color: #3277a8; color: white; font-size: 20px; padding: 15px 30px; border: none; border-radius: 8px; margin: 10px; cursor: pointer;">
+            Diacylglycerol
+        </button>
+    </a>
+		<br>
+    <a href="LipidProbe/Sphinganine.qmd" style="text-decoration: none;">
+        <button style="background-color: #2ecc71; color: white; font-size: 20px; padding: 15px 30px; border: none; border-radius: 8px; margin: 10px; cursor: pointer;">
+            Sphinganine
+        </button>
+    </a>
+		<a href="LipidProbe/Sphingosine.qmd" style="text-decoration: none;">
+        <button style="background-color: #eba434; color: white; font-size: 20px; padding: 15px 30px; border: none; border-radius: 8px; margin: 10px; cursor: pointer;">
+            Sphingosine
+        </button>
+    </a>
+
+	<a href="LipidProbe/8-3_FattyAcid.qmd" style="text-decoration: none;">
+        <button style="background-color: #ba34eb; color: white; font-size: 20px; padding: 15px 30px; border: none; border-radius: 8px; margin: 10px; cursor: pointer;">
+            8-3 Fatty Acid
+        </button>
+    </a>
+
+    <a href="LipidProbe/1-10_FattyAcid.qmd" style="text-decoration: none;">
+        <button style="background-color: #a83260; color: white; font-size: 20px; padding: 15px 30px; border: none; border-radius: 8px; margin: 10px; cursor: pointer;">
+            1-10 Fatty Acid
+        </button>
+    </a>
+</div>
+```

### 2025-01-15 index.qmd
fixed html subscripts in index.qmd

@@
 
+    <br>
+
     <a href="LipidProbe/PhosphatidylinositolBisphosphate.qmd" style="text-decoration: none;">
         <button style="background-color: #a86532; color: white; font-size: 20px; padding: 15px 30px; border: none; border-radius: 8px; margin: 10px; cursor: pointer;">
-            PI(4,5)P~2~
+            PI(4,5)P<sub>2</sub>
         </button>
@@
         <button style="background-color: #8732a8; color: white; font-size: 20px; padding: 15px 30px; border: none; border-radius: 8px; margin: 10px; cursor: pointer;">
-            PI(3,4,5)P~3~
+            PI(3,4,5)P<sub>3</sub>
         </button>

### 2025-01-16 IndividualStudies/DH_2017.qmd
EOD push

@@
 ---
+<!-- R setup, reading data tables, wrangling data -->
+```{r setup, echo=FALSE, include=FALSE}
+
+## intitialize libraries
+library(dplyr)
+library(tidyr)
+library(plotly)
+library(ggplot2)
+library(grid)
+library(readr)
+library(rmarkdown)
+library(emojifont)
+library(gt)
+library(crosstalk)
+library(DT)
+library(stringr)
+library(pheatmap)
+
+DH_2017_data <- read.csv("DataTables/DH_PNAS_2017_download.csv") |>
+  mutate(gene_name = str_extract(Description, "GN=([^\\s]+)") |> str_remove("GN=")) |>
+  mutate(Species = str_extract(Description, "OS=([^=]+?)\\sGN=") |> str_remove("OS=") |> str_remove("GN=")) |>
+  filter(Species == "Homo sapiens ") |>
+  mutate(PSM_Sph = (PSM_Sph1 + PSM_Sph2) / 2,
+         PSM_FA = (PSM_FA1 + PSM_FA2) / 2,
+         PSM_DAG = (PSM_DAG1 + PSM_DAG2) /2) |>
+  select(gene_name, PSM_Sph, PSM_FA, PSM_DAG) |>
+
+  glimpse()
+
+```
 
@@
 Doris Höglinger, André Nadler,  Per Haberkant, Joanna Kirkpatrick, Martina Schifferer, Frank Stein, Sebastian Hauke, Forbes D. Porter, Carsten Schultz
-
-Correspondence: <schulcar@ohsu.edu>{target="_blank"}
 
@@
 
+```{r, echo=FALSE, warning=FALSE, fig.height=15}
+
+DH_2017_data_long <- read.csv("DataTables/DH_PNAS_2017_long.csv")
+
+DH_2017_data_long$name <- factor(pull(DH_2017_data_long, name), ordered = TRUE, levels = c("Sph", "FA", "DAG"))
+
+m <- list(l=50, r = 50, b= 100, pad = 4)
+
+heatmap <- DH_2017_data_long |>
+  ggplot(aes(y = id, x = name)) +
+  theme(panel.border = element_rect(color = NA, fill = "grey25")) +
+  geom_tile(aes(fill = value, text = paste0("Gene name: ", gene_name, '\n', "Lipid Probe:", name, "\n", "PSM: ", value))) +
+  scale_fill_gradientn(colors = c("grey95", "purple", "orange"),
+  values = scales::rescale(c(0, 10, 25))) +
+  ylab("Gene") +
+  xlab("Lipid Probe") +
+  theme_minimal() +
+  theme(text = element_text(family = "serif")) +
+
+  theme(legend.title = element_text(size = 12, face = "bold")) +
+  theme(axis.title = element_text(size = 12, face = "bold")) +
+  theme(legend.text = element_text(size = 12))
+
+ggplotly(heatmap,
+        tooltip = c("text", dynamicTicks = TRUE),
+        hovermode = "closest",
+        autosize = T,
+        margin = m) |>
+  layout(showlegend = FALSE)
+
+```
+
 #### Venn Diagram

### 2025-01-16 IndividualStudies/RM_2021.qmd
EOD push

--- 2025-01-13 IndividualStudies/SF_2024_B.qmd
@@
 ---
-title: "Farley et al. 2024 B"
-subtitle: "Trifunctional fatty acid derivatives: the impact of diazirine placement"
+title: "Muller et al. 2021"
+subtitle: "Synthesis and Cellular Labeling of Multifunctional Phosphatidylinositol *Bis*- and *Tris*phosphate Derivatives"
 format: 
@@
 
-Scotland E. Farley, Ryu Hashimoto, Judah Evangelista, Frank Stein, Per Haberkant, Kazuya Kikuchi, Fikadu G. Tafesse, Carsten Schultz*
-
-Correspondence: <schulcar@ohsu.edu>{target="_blank"}
-
-2024-05-25
-
-[Chemical Communications](https://xlink.rsc.org/?DOI=D4CC00974F){target="_blank"}
-
-<https://doi.org/10.1021/acschembio.3c00554>{target="_blank"}
-
-## Abstract
-
-Functionalized lipid probes are a critical new tool to interrogate the function of individual lipid species, but the structural parameters that constrain their utility have not been thoroughly described.
-Functionalized lipid probes are a critical new tool to interrogate the function of individual lipid species, but the structural parameters that constrain their utility have not been thoroughly described.
-Here, we synthesize three palmitic acid derivatives with a diazirine at different positions on the acyl chain and examine their metabolism, subcellular localization, and protein interactions.
-We demonstrate that while they produce very similar metabolites and subcellular distributions, probes with the diazirine at either end pulldown distinct subsets of proteins after photo-crosslinking.
-This highlights the importance of thoughtful diazirine placement when developing probes based on biological molecules.
-
 ::: {.callout-note collapse="true"}
@@
 
+#### Authors
+Rainer Muller, Ana Kojic, Mevlut Citir, Carsten Schultz
+
+#### Journal
+Angewandte Chemie
+
+<https://doi.org/10.1002/anie.202103599>{target="_blank"}
+
+#### Abstract
+
+We synthesized the first multifunctionalized phosphoinositide polyphosphate derivatives featuring a photo-removable protecting group (“cage”), a photo-crosslinkable diazirine group, and a terminal alkyne group useful for click chemistry.
+We demonstrate that the lipid derivatives readily enter cells.
+After photo-crosslinking, cell fixation and fluorescent tagging via click chemistry, we determined the intracellular location of the lipid derivatives before and after uncaging of the lipids.
+We find that there is rapid trafficking of PI(3,4)P2 and PI(3,4,5)P3 derivatives to the plasma membrane, opening the intriguing possibility that there is active transport of these lipids involved.
+We employed the photo-crosslinking and click chemistry functions to analyze the proteome of PI(3,4,5)P3-binding proteins.
+From the latter, we validated by RNAi that the putative lipid binding proteins ATP11A and MPP6 are involved in the transport of PI(3,4,5)P3 to the plasma membrane.
+
 #### Lipid probes utilized
 
+[PI(3,4,5)P~3~](/LipidProbe/PhosphatidylinositolTrisphosphate.qmd)
+
 #### Cell line analyzed
+
+[HeLa](https://www.atcc.org/products/ccl-2){target="_blank"}
+
+#### Mass spectrometry quantification method
+
+Peptide spectral counting
 
@@
 
-#### Ranked-order Log2 Fold-change plots
+#### Heat map
 
-:::{.border}
-```{r, echo=FALSE, warning=FALSE}
-#| fig-cap: "Ranked-order plots depict the relative enrichment of each protein versus control (y-axis) from lowest to highest.
-The left panel depicts the results of a pulldown using trifunctionalized phosphatidic acid; the right panel depicts the results of the pulldown using trifunctionalized phosphatidylethanolamine.
-Black proteins are unenriched or depleted in the presence of probe, Purple proteins are enriched to the probe but fall below a FDR or p-value threshold of significance, and Orange proteins surpass the threshold of significance (need details of threshold)."
-
-RankedOrderPlotStandard(SF_2024_ranked)
-```
-:::
-
-#### Volcano plots
-
-:::{.border}
-```{r, echo=FALSE, warning=FALSE}
-#| fig-cap: "Volcano plots depict the relative enrichment of each protein versus control (x-axis) and the statistical significance of each protein following a Student's t-test (y-axis, -log10 transformed).
-The left panel depicts the results of a pulldown using trifunctionalized phosphatidic acid; the right panel depicts the results of the pulldown using trifunctionalized phosphatidylethanolamine.
-Black proteins are unenriched or depleted in the presence of probe, Purple proteins are enriched to the probe but fall below a FDR or p-value threshold of significance, and Orange proteins surpass the threshold of significance (need details of threshold)."
-
-VolcanoPlotStandardized(SF_2024_data)
-
-```
-:::
-
-## Enriched Proteins
-
-Check the boxes below to filter the dataset by which lipid probe was used in the pulldown and by significance thresholds.
-
-:::{.border}
-```{r, echo=FALSE, warning=FALSE}
-
-# Here is the code to make the filterable lists shown in the crosstalk table below
-
-## Creates a reactive dataframe
-SF_2024_data_reactive <- crosstalk::SharedData$new(SF_2024_data)
-
-htmltools::tags$div(
-  class = "filter-container",
-  filter_checkbox(id = "LipidProbe",
-                  label = "Lipid probe in pulldown:", 
-                  sharedData = SF_2024_data_reactive,
-                  group = ~LipidProbe),
-  filter_checkbox(id = "hit_annotation",
-                  label = "Enrichment criteria:", 
-                  sharedData = SF_2024_data_reactive,
-                  group = ~hit_annotation)
-)
-
-## Displays the reactive dataframe
-datatable(SF_2024_data_reactive, options = list(pageLength = 20))
-
-```
-:::
+#### Venn Diagram
 
@@
 
-{{< downloadthis DataTables/SF_Chem_Comm_2024_download.csv dname="SF_Chem_Comm_2024">}}
+{{< downloadthis DataTables/RM_Angewandte_2021_download.csv dname="RM_Angewandte_2021">}}

### 2025-01-16 LipidProbe/1-10_FattyAcid.qmd
Testing embedded chem structures
EOD push

--- 2025-01-14 LipidProbe/Diacylglycerol.qmd
@@
 ---
-title: "Trifunctional Diacylglycerol"
+title: "Trifunctional 1-10 Fatty Acid"
 ---
+
+<!-- R setup, reading dataframes and minor data wrangling -->
+```{r setup, echo=FALSE, include=FALSE}
+## intitialize libraries
+library(dplyr)
+library(tidyr)
+library(plotly)
+library(ggplot2)
+library(grid)
+library(readr)
+library(rmarkdown)
+library(emojifont)
+library(gt)
+library(crosstalk)
+library(DT)
+library(htmltools)
+
+## Opening the source file for the ggplot custom theme
+source("ggplot_styles.R")
+
+# Opening the datatable for this page
+SF_2024_data <- readr::read_csv("DataSets/1-10_FA_Huh7_SF_2024.csv") |>
+	filter(LipidProbe == "1-10 FA")
+
+# Organizing the hit annotations as factors
+SF_2024_data$hit_annotation <- factor(pull(SF_2024_data, hit_annotation), levels = c("enriched hit", "hit", "enriched candidate", "candidate", "no hit", "NA"), ordered = TRUE)
+
+```
 
@@
 
-## Subcellular localization
+## Protein interactome
 
-## Protein interactome
+::: {.panel-tabset}
+
+## Huh7 cells
+
+```{r, echo=FALSE, warning=FALSE}
+#| fig-cap: "Data as reported in [Farley et al., 2024(B)](/IndividualStudies/SF_2024_B.qmd)"
+VolcanoPlotStandardized(SF_2024_data)
+```
+
+:::
+
+## Enriched hits
+
+```{r, echo=FALSE}
+
+```

### 2025-01-16 LipidProbe/8-3_FattyAcid.qmd
Testing embedded chem structures
EOD push

--- 2025-01-14 LipidProbe/Diacylglycerol.qmd
@@
 ---
-title: "Trifunctional Diacylglycerol"
+title: "Trifunctional 8-3 Fatty Acid"
 ---
+
+<!-- R setup, reading dataframes and minor data wrangling -->
+```{r setup, echo=FALSE, include=FALSE}
+## intitialize libraries
+library(dplyr)
+library(tidyr)
+library(plotly)
+library(ggplot2)
+library(grid)
+library(readr)
+library(rmarkdown)
+library(emojifont)
+library(gt)
+library(crosstalk)
+library(DT)
+library(htmltools)
+
+## Opening the source file for the ggplot custom theme
+source("ggplot_styles.R")
+
+# Opening the datatable for this page
+SF_2024_data <- readr::read_csv("DataSets/8-3FA_Huh7_SF_2024.csv") |>
+	filter(LipidProbe == "8-3 FA")
+
+# Organizing the hit annotations as factors
+SF_2024_data$hit_annotation <- factor(pull(SF_2024_data, hit_annotation), levels = c("enriched hit", "hit", "enriched candidate", "candidate", "no hit", "NA"), ordered = TRUE)
+
+```
 

### 2025-01-16 index.qmd
EOD push

@@
 
+## Site Overview
+
 A blurb about the objective of this site, maybe a gallery of images from select publications to put here.
+
+## Lipid Interactomes
 
@@
     </a>
+
     <br>
@@
 
+    <br>
 	<a href="LipidProbe/8-3_FattyAcid.qmd" style="text-decoration: none;">

### 2025-01-16 LipidProbe/ggplot_styles.R

@@ -1,0 +1,147 @@
+# A centralized spot to save a custom theme across the whole site
+
+library(ggplot2)
+library(ggrepel)
+library(emojifont)
+library(dplyr)
+library(tidyr)
+
+# A standardized Ranked Order plot theme
+
+RankedOrderPlotStandard <- function(data) {
+    RankedOrderPlots <- data |>
+        ggplot(aes(x = ID,
+                   y = logFC,
+                   color = factor(hit_annotation),
+                   fill = factor(hit_annotation),
+                   shape = factor(hit_annotation),
+                   alpha = factor(hit_annotation),
+                   size = factor(hit_annotation))) +
+        geom_point(aes(text = paste0("Gene name: ", gene_name, "\n",
+                                    "LogFC: ", logFC, "\n",
+                                    "p-value: ", pvalue, "\n"))) +
+        geom_hline(yintercept = 0, linetype = 2) +
+        geom_vline(xintercept = 0, linetype = 2) +
+        scale_shape_manual(values = c("enriched hit" = 21,
+                                    "hit" = 21,
+                                    "enriched candidate" = 24,
+                                    "candidate" = 24,
+                                    "no hit" = 22), 
+                        name = "Trend") +
+        scale_color_manual(values = c("enriched hit" = "black",
+                                    "hit" = "black",
+                                    "enriched candidate" = "black",
+                                    "candidate" = "black",
+                                    "no hit" = "black"), 
+                        name = "Trend") +
+        scale_fill_manual(values = c("enriched hit" = "orange",
+                                    "hit" = "orange",
+                                    "enriched candidate" = "purple",
+                                    "candidate" = "purple",
+                                    "no hit" = "black"), 
+                        name = "Trend") +
+        scale_alpha_manual(values = c("enriched hit" = 0.8,
+                                    "hit" = 0.8,
+                                    "enriched candidate" = 0.5,
+                                    "candidate" = 0.5,
+                                    "no hit" = 0.25), 
+                        name = "Trend") +
+        scale_size_manual(values = c("enriched hit" = 4,
+                                    "hit" = 4,
+                                    "enriched candidate" = 2,
+                                    "candidate" = 2, 
+                                    "no hit" = 0.75), 
+                        name = "Trend") +
+        facet_wrap(~LipidProbe) +
+        ylab("Log2 fold-change") +
[…]

### 2025-01-16 IndividualStudies/DH_2017.qmd
Actual EOD

@@
 
-DH_2017_data_long <- read.csv("DataTables/DH_PNAS_2017_long.csv")
+DH_2017_data_long <- read.csv("DataTables/DH_PNAS_2017_long.csv") |>
+  mutate(PSM = value, sample = name) |>
+  group_by(gene_name, sample) |>
+  summarise(PSM = mean(PSM, na.rm = TRUE), .groups = "drop") |>
+  distinct()
 
-DH_2017_data_long$name <- factor(pull(DH_2017_data_long, name), ordered = TRUE, levels = c("Sph", "FA", "DAG"))
-
-m <- list(l=50, r = 50, b= 100, pad = 4)
+DH_2017_data_long$sample <- factor(pull(DH_2017_data_long, sample), ordered = TRUE, levels = c("Sph", "FA", "DAG"))
 
 heatmap <- DH_2017_data_long |>
-  ggplot(aes(y = id, x = name)) +
+  ggplot(aes(y = gene_name, x = sample)) +
   theme(panel.border = element_rect(color = NA, fill = "grey25")) +
-  geom_tile(aes(fill = value, text = paste0("Gene name: ", gene_name, '\n', "Lipid Probe:", name, "\n", "PSM: ", value))) +
+  geom_tile(aes(fill = PSM, text = paste0("Gene name: ", gene_name, '\n', "Lipid Probe:", sample, "\n", "PSM: ", PSM))) +
   scale_fill_gradientn(colors = c("grey95", "purple", "orange"),
@@
   theme(text = element_text(family = "serif")) +
-
   theme(legend.title = element_text(size = 12, face = "bold")) +
@@
   theme(legend.text = element_text(size = 12))
+
+m <- list(l=50, r = 50, b= 100, pad = 4)
 

### 2025-01-16 IndividualStudies/AT_2025.qmd
successfully added some buttons to the home page
Added a page for Hoglinger  2017
EOD push
Updating individual study pages

@@
 
-#### Authors:
+#### Authors
 Alix Thomas, Rainer Mueller, Ana Kojic, Scotland E. Farley, Frank Stein, Per Haberkant, Carsten Schultz
 
-Correspondence: <schulcar@ohsu.edu>{target="_blank"}
-
-#### Journal:
+#### Journal
 Chemical Communications
@@
 #### Cell line analyzed
+
+[HeLa](https://www.atcc.org/products/ccl-2){target="_blank"}
+
+#### Mass spectrometry quantification method
+
+16-channel Tandem Mass Tagging (TMT16)
 
@@
 
-#### Ranked-order Log2 Fold-change
+::: {.panel-tabset}
+
+#### Volcano plots
 
@@
 ```{r, echo=FALSE, warning=FALSE}
-#| fig-cap: "Ranked-order plots depict the relative enrichment of each protein versus control (y-axis) from lowest to highest.
+#| fig-cap: "Volcano plots depict the relative enrichment of each protein versus non-crosslinked control (x-axis) and the statistical significance of each protein following a Student's t-test (y-axis, -log10 transformed).
 The left panel depicts the results of a pulldown using trifunctionalized phosphatidic acid; the right panel depicts the results of the pulldown using trifunctionalized phosphatidylethanolamine.
-Black proteins are unenriched or depleted in the presence of probe, Purple proteins are enriched to the probe but fall below a FDR or p-value threshold of significance, and Orange proteins surpass the threshold of significance (need details of threshold)."
+Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV)."
+
+VolcanoPlotStandardized(AT_2025_Long)
+
+```
+:::
+
+#### Ranked-order plots
+
+:::{.border}
+```{r, echo=FALSE, warning=FALSE}
+#| fig-cap: "Ranked-order plots depict the relative enrichment of each protein versus non-crosslinked control (y-axis) from lowest to highest.
+The left panel depicts the results of a pulldown using trifunctionalized phosphatidic acid; the right panel depicts the results of the pulldown using trifunctionalized phosphatidylethanolamine.
+Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV)."
 
@@
 
-#### Volcano plots
+#### MA Plots
 
@@
 ```{r, echo=FALSE, warning=FALSE}
-#| fig-cap: "Volcano plots depict the relative enrichment of each protein versus control (x-axis) and the statistical significance of each protein following a Student's t-test (y-axis, -log10 transformed).
-The left panel depicts the results of a pulldown using trifunctionalized phosphatidic acid; the right panel depicts the results of the pulldown using trifunctionalized phosphatidylethanolamine.
-Black proteins are unenriched or depleted in the presence of probe, Purple proteins are enriched to the probe but fall below a FDR or p-value threshold of significance, and Orange proteins surpass the threshold of significance (need details of threshold)."
+#| fig-cap: "MA plots depict the average abundance of each protein in the crosslinked and uncrosslinked conditions (x-axis) versus the log2-transformed fold-change between the crosslinked and uncrosslinked conditions (y-axis).
+Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV)."
 
-VolcanoPlotStandardized(AT_2025_Long)
+print("Data not yet provided.")
+
 ```
+
+:::
 :::

### 2025-01-16 IndividualStudies/RM_2021.qmd
Updating individual study pages

@@
 
-# Opening the datatable for this page
-SF_2024_data <- readr::read_csv("DataTables/SF_Chem_Comm_2024_download.csv")
+# Opening the datatable for this page WHILE TESTING
+# RM_2021_data <- readr::read_csv("IndividualStudies/DataTables/RM_Angewandte_2021_download.csv")
 
-# Organizing the hit annotations as factors
-SF_2024_data$hit_annotation <- factor(pull(SF_2024_data, hit_annotation), levels = c("enriched hit", "hit", "enriched candidate", "candidate", "no hit", "NA"), ordered = TRUE)
+# Opening the datatable for this page WHILE RENDERING
+RM_2021_data <- readr::read_csv("DataTables/RM_Angewandte_2021_download.csv")
 
-# Organize the probes as factors
-SF_2024_data$LipidProbe <- factor(pull(SF_2024_data, LipidProbe), levels = c("Spa", "Sph", "8-3 FA", "1-10 FA"), ordered = TRUE)
-
-#write.csv(SF_2024_data, "IndividualStudies/DataTables/SF_Chem_Comm_2024_download.csv")
-
-# Building an ID column to maintain the order on the x-axis
-ID <- c()
-for(i in 0:(nrow(SF_2024_data)/2)){
-	ID[i] = i
-}
-
-# Applies the ID column to the 1-10 FA results
-SF_2024_ranked_1_10_FA <- SF_2024_data |>
-    arrange(logFC) |>
-	filter(LipidProbe == "1-10 FA") |>
-	mutate(ID = ID)
-
-# Applies the ID column to the 8-3 FA results
-SF_2024_ranked_8_3_FA <- SF_2024_data |>
-    arrange(logFC) |>
-	filter(LipidProbe == "8-3 FA") |>
-	mutate(ID = ID)
-
-# Assembles the dataset to plot
-SF_2024_ranked <- rbind(SF_2024_ranked_8_3_FA, SF_2024_ranked_1_10_FA)
 ```

### 2025-01-16 IndividualStudies/SF_2024.qmd
Beginning to overhaul site structure
successfully added some buttons to the home page
EOD push
Updating individual study pages

@@
 library(htmltools)
+library(scales)
 
@@
 
-# Opening the datatable for this page
+# Opening the datatable for this page IN FINAL RENDER
 SF_2024_data <- readr::read_csv("DataTables/SF_ACS-Chem-Bio_2024_download.csv")
+
+# # # Opening the datatable for this page WHILE EDITING
+# SF_2024_data <- readr::read_csv("IndividualStudies/DataTables/SF_ACS-Chem-Bio_2024_download.csv")
 
@@
 # Organize the probes as factors
-SF_2024_data$LipidProbe <- factor(pull(SF_2024_data, LipidProbe), levels = c("Spa", "Sph", "8-3 FA", "1-10 FA"), ordered = TRUE)
+SF_2024_data$LipidProbe <- factor(pull(SF_2024_data, LipidProbe), levels = c("Sph", "Spa", "8-3 FA", "1-10 FA"), ordered = TRUE)
 
@@
 
-Scotland E. Farley, Frank Stein, Per Haberkant, Fikadu G. Tafesse, Carsten Schultz*
+::: {.callout-note collapse="true"}
 
-Correspondence: <schulcar@ohsu.edu>{target="_blank"}
+## Study details
 
-2024-02-16
+#### Authors
+Scotland E. Farley, Frank Stein, Per Haberkant, Fikadu G. Tafesse, Carsten Schultz
 
-[ACS Chemical Biology](https://pubs.acs.org/doi/10.1021/acschembio.3c00554){target="_blank"}
+#### Journal
+ACS Chemical Biology
 
@@
 
-## Abstract
+#### Abstract
 
@@
 
-::: {.callout-note collapse="true"}
-
-## Study details
-
 #### Lipid probes utilized
@@
 #### Cell line analyzed
+
+[Huh7](https://huh7.com){target="_blank"}
+
+#### Mass spectrometry quantification method
+
+16-channel Tandem Mass Tagging (TMT16)
 
@@
 
-#### Ranked-order Log2 Fold-change plots
-
-:::{.border}
-```{r, echo=FALSE, warning=FALSE}
-#| fig-cap: "Ranked-order plots depict the relative enrichment of each protein versus control (y-axis) from lowest to highest.
-The left panel depicts the results of a pulldown using trifunctionalized phosphatidic acid; the right panel depicts the results of the pulldown using trifunctionalized phosphatidylethanolamine.
-Black proteins are unenriched or depleted in the presence of probe, Purple proteins are enriched to the probe but fall below a FDR or p-value threshold of significance, and Orange proteins surpass the threshold of significance (need details of threshold)."
-
-RankedOrderPlotStandard(SF_2024_ranked)
-```
-:::
+::: {.panel-tabset}
 
@@
 
+#### Ranked-order plots
+
+:::{.border}
+```{r, echo=FALSE, warning=FALSE}
+#| fig-cap: "Ranked-order plots depict the relative enrichment of each protein versus control (y-axis) from lowest to highest.
+The left panel depicts the results of a pulldown using trifunctionalized phosphatidic acid; the right panel depicts the results of the pulldown using trifunctionalized phosphatidylethanolamine.
+Black proteins are unenriched or depleted in the presence of probe, Purple proteins are enriched to the probe but fall below a FDR or p-value threshold of significance, and Orange proteins surpass the threshold of significance (need details of threshold)."
+
+RankedOrderPlotStandard(SF_2024_ranked)
+```
+:::
+
+#### MA Plots
+
+:::{.border}
+```{r, echo=FALSE, warning=FALSE}
+#| fig-cap: "MA plots"
+
+MAStandard(SF_2024_data)
+
+```
+
+:::
+
+:::
+
 ## Enriched Proteins
@@
 # Here is the code to make the filterable lists shown in the crosstalk table below
+
+SF_2024_data <- SF_2024_data |>
+  select(gene_name, LipidProbe, hit_annotation, logFC, pvalue, fdr) |>
+  mutate(logFC = signif(logFC, digits=3),
+          pvalue = signif(pvalue, digits=3),
+          fdr = signif(fdr, digits = 3)) |>
+  arrange(hit_annotation) |>
+  arrange(LipidProbe)
 
@@
 ## Displays the reactive dataframe
-datatable(SF_2024_data_reactive, options = list(pageLength = 20))
+datatable(SF_2024_data_reactive, 
+          options = list(pageLength = 15),
+                         colnames = c("Gene Name", "Lipid Probe", "Hit Annotation", "LogFC", "p value", "FDR"))
 

### 2025-01-16 IndividualStudies/SF_2024_B.qmd
Beginning to overhaul site structure
successfully added some buttons to the home page
EOD push
Updating individual study pages

@@
 
-# Opening the datatable for this page
+# Opening the datatable for this page IN FINAL RENDER
 SF_2024_data <- readr::read_csv("DataTables/SF_Chem_Comm_2024_download.csv")
+
+# # # Opening the datatable for this page WHILE EDITING
+# SF_2024_data <- readr::read_csv("IndividualStudies/DataTables/SF_Chem_Comm_2024_download.csv")
 
@@
 
-Scotland E. Farley, Ryu Hashimoto, Judah Evangelista, Frank Stein, Per Haberkant, Kazuya Kikuchi, Fikadu G. Tafesse, Carsten Schultz*
+::: {.callout-note collapse="true"}
 
-Correspondence: <schulcar@ohsu.edu>{target="_blank"}
+## Study details
 
-2024-05-25
+#### Authors
+Scotland E. Farley, Ryu Hashimoto, Judah Evangelista, Frank Stein, Per Haberkant, Kazuya Kikuchi, Fikadu G. Tafesse, Carsten Schultz
 
-[Chemical Communications](https://xlink.rsc.org/?DOI=D4CC00974F){target="_blank"}
+#### Journal
+Chemical Communications
 
@@
 
-::: {.callout-note collapse="true"}
-
-## Study details
-
 #### Lipid probes utilized
 
+[8-3 Fatty Acid](/LipidProbe/8-3_FattyAcid.qmd)
+
 #### Cell line analyzed
+
+[Huh7](https://huh7.com){target="_blank"}
+
+#### Mass spectrometry quantification method
+
+16-channel Tandem Mass Tagging (TMT16)
 
@@
 
-#### Ranked-order Log2 Fold-change plots
+::: {.panel-tabset}
+
+#### Volcano plots
 
@@
 ```{r, echo=FALSE, warning=FALSE}
-#| fig-cap: "Ranked-order plots depict the relative enrichment of each protein versus control (y-axis) from lowest to highest.
+#| fig-cap: "Volcano plots depict the relative enrichment of each protein versus non-crosslinked control (x-axis) and the statistical significance of each protein following a Student's t-test (y-axis, -log10 transformed).
 The left panel depicts the results of a pulldown using trifunctionalized phosphatidic acid; the right panel depicts the results of the pulldown using trifunctionalized phosphatidylethanolamine.
-Black proteins are unenriched or depleted in the presence of probe, Purple proteins are enriched to the probe but fall below a FDR or p-value threshold of significance, and Orange proteins surpass the threshold of significance (need details of threshold)."
+Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV)."
+
+VolcanoPlotStandardized(SF_2024_data)
+
+```
+:::
+
+#### Ranked-order plots
+
+:::{.border}
+```{r, echo=FALSE, warning=FALSE}
+#| fig-cap: "Ranked-order plots depict the relative enrichment of each protein versus non-crosslinked control (y-axis) from lowest to highest.
+The left panel depicts the results of a pulldown using trifunctionalized phosphatidic acid; the right panel depicts the results of the pulldown using trifunctionalized phosphatidylethanolamine.
+Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV)."
 
@@
 ```{r, echo=FALSE, warning=FALSE}
-#| fig-cap: "Volcano plots depict the relative enrichment of each protein versus control (x-axis) and the statistical significance of each protein following a Student's t-test (y-axis, -log10 transformed).
-The left panel depicts the results of a pulldown using trifunctionalized phosphatidic acid; the right panel depicts the results of the pulldown using trifunctionalized phosphatidylethanolamine.
-Black proteins are unenriched or depleted in the presence of probe, Purple proteins are enriched to the probe but fall below a FDR or p-value threshold of significance, and Orange proteins surpass the threshold of significance (need details of threshold)."
+#| fig-cap: "MA plots depict the average abundance of each protein in the crosslinked and uncrosslinked conditions (x-axis) versus the log2-transformed fold-change between the crosslinked and uncrosslinked conditions (y-axis).
+Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV)."
 
-VolcanoPlotStandardized(SF_2024_data)
+MAStandard(SF_2024_data)
 
 ```
+
+:::
 :::
@@
 ## Displays the reactive dataframe
-datatable(SF_2024_data_reactive, options = list(pageLength = 20))
+datatable(SF_2024_data_reactive, options = list(pageLength = 15))
 

### 2025-01-16 IndividualStudies/ggplot_styles.R

@@ -6,6 +6,80 @@ library(emojifont)
 library(dplyr)
 library(tidyr)
 
+# A standardized MA plot function
+
+MAStandard <- function(data) {
+
+    MAPlots <- data |>
+        ggplot(aes(x = AveExpr,
+                   y = logFC,
+                   color = factor(hit_annotation),
+                   fill = factor(hit_annotation),
+                   shape = factor(hit_annotation),
+                   alpha = factor(hit_annotation),
+                   size = factor(hit_annotation))) +
+        geom_point(aes(text = paste0("Gene name: ", gene_name, "\n",
+                                    "LogFC: ", logFC, "\n",
+                                    "p-value: ", pvalue, "\n"))) +
+        geom_hline(yintercept = 0, linetype = 2) +
+        geom_vline(xintercept = 0, linetype = 2) +
+        scale_x_continuous(limits=c(0.9 * min(abs(data$AveExpr)), 1.1* max(abs(data$AveExpr))))+
+        scale_y_continuous(limits=c(-1.1 * max(abs(data$logFC)), 1.1* max(abs(data$logFC))))+
+        scale_shape_manual(values = c("enriched hit" = 21,
+                                    "hit" = 21,
+                                    "enriched candidate" = 24,
+                                    "candidate" = 24,
+                                    "no hit" = 22), 
+                        name = "Trend") +
+        scale_color_manual(values = c("enriched hit" = "black",
+                                    "hit" = "black",
+                                    "enriched candidate" = "black",
+                                    "candidate" = "black",
+                                    "no hit" = "black"), 
+                        name = "Trend") +
+        scale_fill_manual(values = c("enriched hit" = "orange",
+                                    "hit" = "orange",
+                                    "enriched candidate" = "purple",
+                                    "candidate" = "purple",
+                                    "no hit" = "black"), 
+                        name = "Trend") +
+        scale_alpha_manual(values = c("enriched hit" = 0.8,
+                                    "hit" = 0.8,
+                                    "enriched candidate" = 0.5,
+                                    "candidate" = 0.5,
+                                    "no hit" = 0.25), 
+                        name = "Trend") +
+        scale_size_manual(values = c("enriched hit" = 4,
+                                    "hit" = 4,
+                                    "enriched candidate" = 2,
[…]

### 2025-01-16 LipidProbe/1-10_FattyAcid.qmd
checking render of PE page

@@
 
+# SF_2024_data <- readr::read_csv("LipidProbe/DataSets/SF_Chem_Comm_2024_download.csv") |>
+# 	filter(LipidProbe == "1-10 FA")
+
+# write.csv(SF_2024_data, "LipidProbe/DataSets/1-10_FA_Huh7_SF_2024.csv")
+
 # Opening the datatable for this page
@@
 
+# Building an ID column to maintain the order on the x-axis
+ID <- c()
+for(i in 0:(nrow(SF_2024_data))){
+	ID[i] = i
+}
+
+# Applies the ID column to the Spa results
+SF_2024_ranked <- SF_2024_data |>
+    arrange(logFC) |>
+	filter(LipidProbe == "1-10 FA") |>
+	mutate(ID = ID)
+
 ```
@@
 
+### Cell background: HeLa
+
+::: {.callout-note collapse="true"}
+
+### Study details
+
+#### Authors
+Scotland E. Farley, Frank Stein, Per Haberkant, Fikadu G. Tafesse, Carsten Schultz
+
+#### Journal
+ACS Chemical Biology
+
+<https://doi.org/10.1021/acschembio.3c00554>{target="_blank"}
+
+#### Abstract
+
+Functions of the sphingolipids sphingosine and sphinganine in cells are not well established.
+While some signaling roles for sphingosine have been elucidated, the closely related sphinganine has been described only insofar as it does not elicit many of the same signaling responses.
+The underlying mechanisms behind the cell biological differences between these lipids are not well understood.
+Here, we prepared multifunctionalized derivatives of the two lipid species that only differ in a single double bond of the carbon backbone.
+Using these novel probes, we were able to define their spatiotemporal distribution within cells.
+Furthermore, we used these tools to systematically map the protein interactomes of both lipids.
+The lipid-protein conjugates, prepared through photo-crosslinking in live cells and extraction via click chemistry to azide beads, revealed significant differences in the captured proteins, highlighting their distinct roles in various cellular processes.
+This work elucidates mechanistic differences between these critical lipids and sets the foundation for further studies on the functions of sphingosine and sphinganine.
+
+#### Lipid probes utilized
+
+1-10 Fatty acid
+
+8-3 Fatty acid
+
+#### Cell line analyzed
+
+[Huh7](https://huh7.com){target="_blank"}
+
+#### Mass spectrometry quantification method
+
+16-channel Tandem Mass Tagging (TMT16)
+
+#### Additional sample preparation <span class="help-symbol" title="e.g. sub-cellular fractionation, depletion, etc.">?</span>
+:::
+
 ::: {.panel-tabset}
 
-## Huh7 cells
+## Volcano plot
 
+:::{.border}
 ```{r, echo=FALSE, warning=FALSE}
-#| fig-cap: "Data as reported in [Farley et al., 2024(B)](/IndividualStudies/SF_2024_B.qmd)"
+#| fig-cap: "Data as reported in [Farley et al., 2024(B)](/IndividualStudies/SF_2024_B.qmd).
+Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV)."
+
 VolcanoPlotStandardized(SF_2024_data)
 ```
+:::
 
+## Ranked order plot
+
+:::{.border}
+```{r, echo=FALSE, warning=FALSE}
+#| fig-cap: "Data as reported in [Farley et al., 2024(B)](/IndividualStudies/SF_2024_B.qmd).
+Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV)."
+
+RankedOrderPlotStandard(SF_2024_ranked)
+```
+:::
+
+## MA Plots
+
+:::{.border}
+```{r, echo=FALSE, warning=FALSE}
+#| fig-cap: "Data as reported in [Farley et al., 2024(B)](/IndividualStudies/SF_2024_B.qmd).
+Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV)."
+
+MAStandard(SF_2024_data)
+
+```
+:::
 :::
@@
 
-```{r, echo=FALSE}
+:::{.border}
+```{r, echo=FALSE, warning=FALSE}
+
+# Here is the code to make the filterable lists shown in the crosstalk table below
+
+SF_2024_data <- SF_2024_data |>
+  select(gene_name, LipidProbe, hit_annotation, logFC, pvalue, fdr) |>
+  mutate(logFC = signif(logFC, digits=3),
+          pvalue = signif(pvalue, digits=3),
+          fdr = signif(fdr, digits = 3)) |>
+  arrange(hit_annotation) |>
+  arrange(LipidProbe)
+
+## Creates a reactive dataframe
+SF_2024_data_reactive <- crosstalk::SharedData$new(SF_2024_data)
+
+htmltools::tags$div(
+  class = "filter-container",
+  filter_checkbox(id = "hit_annotation",
+                  label = "Enrichment criteria:", 
+                  sharedData = SF_2024_data_reactive,
+                  group = ~hit_annotation,
+									inline=TRUE)
+)
+
+## Displays the reactive dataframe
+datatable(SF_2024_data_reactive, 
+          options = list(pageLength = 10),
+                         colnames = c("Gene Name", "Lipid Probe", "Hit Annotation", "LogFC", "p value", "FDR"))
 
 ```
+:::
+
+## Data download
+
+{{< downloadthis DataSets/1-10_FA_Huh7_SF_2024.csv dname="1-10_FA_Huh7_SF_ACS-Chem-Bio_2024">}}

### 2025-01-16 LipidProbe/8-3_FattyAcid.qmd
checking render of PE page

@@
 
+# SF_2024_data <- readr::read_csv("LipidProbe/DataSets/SF_Chem_Comm_2024_download.csv") |>
+# 	filter(LipidProbe == "8-3 FA")
+
+# write.csv(SF_2024_data, "LipidProbe/DataSets/8-3_FA_Huh7_SF_2024.csv")
+
 # Opening the datatable for this page
-SF_2024_data <- readr::read_csv("DataSets/8-3FA_Huh7_SF_2024.csv") |>
+SF_2024_data <- readr::read_csv("DataSets/8-3_FA_Huh7_SF_2024.csv") |>
 	filter(LipidProbe == "8-3 FA")
@@
 SF_2024_data$hit_annotation <- factor(pull(SF_2024_data, hit_annotation), levels = c("enriched hit", "hit", "enriched candidate", "candidate", "no hit", "NA"), ordered = TRUE)
+
+# Building an ID column to maintain the order on the x-axis
+ID <- c()
+for(i in 0:(nrow(SF_2024_data))){
+	ID[i] = i
+}
+
+# Applies the ID column to the Spa results
+SF_2024_ranked <- SF_2024_data |>
+    arrange(logFC) |>
+	filter(LipidProbe == "8-3 FA") |>
+	mutate(ID = ID)
 
@@
 
+### Cell background: Huh7
+
+::: {.callout-note collapse="true"}
+
+#### Study details
+
+##### Authors
+Scotland E. Farley, Frank Stein, Per Haberkant, Fikadu G. Tafesse, Carsten Schultz
+
+##### Journal
+ACS Chemical Biology
+
+<https://doi.org/10.1021/acschembio.3c00554>{target="_blank"}
+
+##### Abstract
+
+Functions of the sphingolipids sphingosine and sphinganine in cells are not well established.
+While some signaling roles for sphingosine have been elucidated, the closely related sphinganine has been described only insofar as it does not elicit many of the same signaling responses.
+The underlying mechanisms behind the cell biological differences between these lipids are not well understood.
+Here, we prepared multifunctionalized derivatives of the two lipid species that only differ in a single double bond of the carbon backbone.
+Using these novel probes, we were able to define their spatiotemporal distribution within cells.
+Furthermore, we used these tools to systematically map the protein interactomes of both lipids.
+The lipid-protein conjugates, prepared through photo-crosslinking in live cells and extraction via click chemistry to azide beads, revealed significant differences in the captured proteins, highlighting their distinct roles in various cellular processes.
+This work elucidates mechanistic differences between these critical lipids and sets the foundation for further studies on the functions of sphingosine and sphinganine.
+
+##### Lipid probes utilized
+
+1-10 Fatty acid
+
+8-3 Fatty acid
+
+##### Cell line analyzed
+
+[Huh7](https://huh7.com){target="_blank"}
+
+##### Mass spectrometry quantification method
+
+16-channel Tandem Mass Tagging (TMT16)
+
+##### Additional sample preparation <span class="help-symbol" title="e.g. sub-cellular fractionation, depletion, etc.">?</span>
+:::
+
 ::: {.panel-tabset}
 
-## Huh7 cells
+##### Volcano plot
 
+:::{.border}
 ```{r, echo=FALSE, warning=FALSE}
-#| fig-cap: "Data as reported in [Farley et al., 2024(B)](/IndividualStudies/SF_2024_B.qmd)"
+#| fig-cap: "Data as reported in [Farley et al., 2024(B)](/IndividualStudies/SF_2024_B.qmd).
+Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV)."
+
 VolcanoPlotStandardized(SF_2024_data)
 ```
+:::
+
+##### Ranked order plot
+
+:::{.border}
+```{r, echo=FALSE, warning=FALSE}
+#| fig-cap: "Data as reported in [Farley et al., 2024(B)](/IndividualStudies/SF_2024_B.qmd).
+Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV)."
+
+RankedOrderPlotStandard(SF_2024_ranked)
+```
+:::
+
+##### MA Plots
+
+:::{.border}
+```{r, echo=FALSE, warning=FALSE}
+#| fig-cap: "Data as reported in [Farley et al., 2024(B)](/IndividualStudies/SF_2024_B.qmd).
+Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV)."
+
+MAStandard(SF_2024_data)
+
+```
+:::
+:::
+
+#### Huh7 Data download
+
+{{< downloadthis DataSets/8-3_FA_Huh7_SF_2024.csv dname="8-3_FA_Huh7_SF_ACS-Chem-Bio_2024">}}
+
+### Cell background: HeLa
+
+::: {.callout-note collapse="true"}
+
+## Study details
+
+#### Authors
+
+Doris Höglinger, André Nadler,  Per Haberkant, Joanna Kirkpatrick, Martina Schifferer, Frank Stein, Sebastian Hauke, Forbes D. Porter, Carsten Schultz
+
+#### Journal
+
+PNAS
+
+<https://doi.org/10.1073/pnas.1611096114>{target="_blank"}
+
+#### Abstract
+
+Lipid-mediated signaling events regulate many cellular processes.
+Investigations of the complex underlying mechanisms are difficult because several different methods need to be used under varying conditions.
+Here we introduce multifunctional lipid derivatives to study lipid metabolism, lipid−protein interactions, and intracellular lipid localization with a single tool per target lipid.
+The probes are equipped with two photoreactive groups to allow photoliberation (uncaging) and photo–cross-linking in a sequential manner, as well as a click-handle for subsequent functionalization.
+We demonstrate the versatility of the design for the signaling lipids sphingosine and diacylglycerol; uncaging of the probe for these two species triggered calcium signaling and intracellular protein translocation events, respectively.
+We performed proteomic screens to map the lipid-interacting proteome for both lipids.
+Finally, we visualized a sphingosine transport deficiency in patient-derived Niemann−Pick disease type C fibroblasts by fluorescence as well as correlative light and electron microscopy, pointing toward the diagnostic potential of such tools.
+We envision that this type of probe will become important for analyzing and ultimately understanding lipid signaling events in a comprehensive manner.
+
+#### Lipid probes utilized
+
+Sphinganine
+
+Diacylglycerol
+
+8-3 Fatty acid
+
+#### Cell line analyzed
+
+[HeLa](https://www.atcc.org/products/ccl-2){target="_blank"}
+
+#### Mass spectrometry quantification method
+
+Peptide spectral counting
 
 :::
-
-## Enriched hits
-
-```{r, echo=FALSE}
-
-```

### 2025-01-16 LipidProbe/Phosphatidylethanolamine.qmd
minor tweaks
checking render of PE page

@@
 ---
+
+## Structure
+
+![](Structures/PhosphatidylethanolamineStructure.png)
+
+## Protein interactome
+
+### Cell background: HeLa
+
+::: {.callout-note collapse="true"}
+
+#### Study details
+
+##### Authors
+Alix Thomas, Rainer Mueller, Ana Kojic, Scotland E. Farley, Frank Stein, Per Haberkant, Carsten Schultz
+
+##### Journal
+Chemical Communications
+
+<https://doi.org/10.1039/D4CC03599B>{target="_blank"}
+
+##### Abstract
+Phosphatidylethanolamine (PE) is a ubiquitous lipid species in higher eukaryotes which resides preferentially in mitochondria.
+Here, we synthesized a multifunctionalized PE derivative (1) de-signed to identify PE-binding proteins in intact cells through photo-crosslinking and subsequent isolation and proteomic analysis of the PE-protein conjugates.
+Due to its aromatic caging group, 1 is initially concentrating in perinuclear membranes.
+After uncaging, rapid translocation to mitochondria was observed.
+Hence, the tool is useful for tracking PE location and for determining the PE interactome.
+A trifunctional phosphatidic acid (PA) derivative in compari-son was rapidly metabolized and is hence more limited in its use.
+
+##### Lipid probes utilized
+
+##### Cell line analyzed
+
+[HeLa](https://www.atcc.org/products/ccl-2){target="_blank"}
+
+##### Mass spectrometry quantification method
+
+16-channel Tandem Mass Tagging (TMT16)
+
+##### Additional sample preparation <span class="help-symbol" title="e.g. sub-cellular fractionation, depletion, etc.">?</span>
+:::
+
+#### Data visualization
+
+```{r setup, echo=FALSE, include=FALSE}
+
+## intitialize libraries
+library(dplyr)
+library(tidyr)
+library(plotly)
+library(ggplot2)
+library(grid)
+library(readr)
+library(rmarkdown)
+library(emojifont)
+library(gt)
+library(crosstalk)
+library(DT)
+
+## Set up the source for the standardized ggplot styles
+source("ggplot_styles.R")
+```
+
+```{r, echo=FALSE, include=FALSE}
+
+# Data wrangling to prepare Alix's data to the standardized inputs for my plotting functions.
+# Read the data to a df
+
+# AT_2025_Long <- readr::read_csv("LipidProbe/DataSets/AT_ChemicalCommunications_2025_download.csv") |>
+# 	filter(LipidProbe == "PE")
+
+# write.csv(AT_2025_Long, "LipidProbe/DataSets/PE_HeLa_AT_2025.csv")
+
+AT_2025_Long <- readr::read_csv("DataSets/PE_HeLa_AT_2025.csv")
+
+# Organize the hit annotations as factors
+AT_2025_Long$hit_annotation <- factor(pull(AT_2025_Long, hit_annotation), levels = c("enriched hit", "enriched candidate", "no hit", "NA"), ordered=TRUE)
+
+# Building an ID column to maintain the order on the x-axis
+ID <- c()
+for(i in 0:(nrow(AT_2025_Long))){
+	ID[i] = i
+}
+
+# Applies the ID column to the PE results
+AT_2025_ranked <- AT_2025_Long |>
+    arrange(logFC) |>
+	filter(LipidProbe == "PE") |>
+	mutate(ID = ID)
+
+```
+
+::: {.panel-tabset}
+
+##### Volcano plots
+
+:::{.border}
+```{r, echo=FALSE, warning=FALSE}
+#| fig-cap: "Volcano plots depict the relative enrichment of each protein versus non-crosslinked control (x-axis) and the statistical significance of each protein following a Student's t-test (y-axis, -log10 transformed).
+The left panel depicts the results of a pulldown using trifunctionalized phosphatidic acid; the right panel depicts the results of the pulldown using trifunctionalized phosphatidylethanolamine.
+Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV)."
+
+VolcanoPlotStandardized(AT_2025_Long)
+
+```
+:::
+
+##### Ranked-order plots
+
+:::{.border}
+```{r, echo=FALSE, warning=FALSE}
+#| fig-cap: "Ranked-order plots depict the relative enrichment of each protein versus non-crosslinked control (y-axis) from lowest to highest.
+The left panel depicts the results of a pulldown using trifunctionalized phosphatidic acid; the right panel depicts the results of the pulldown using trifunctionalized phosphatidylethanolamine.
+Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV)."
+
+RankedOrderPlotStandard(AT_2025_ranked)
+```
+:::
+
+##### MA Plots
+
+:::{.border}
+```{r, echo=FALSE, warning=FALSE}
+#| fig-cap: "MA plots depict the average abundance of each protein in the crosslinked and uncrosslinked conditions (x-axis) versus the log2-transformed fold-change between the crosslinked and uncrosslinked conditions (y-axis).
+Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV)."
+
+print("Data not yet provided.")
+
+```
+
+:::
+:::
+
+#### Enriched proteins
+
+Check the boxes below to filter the dataset by which lipid probe was used in the pulldown and by significance thresholds.
+
+:::{.border}
+```{r, echo=FALSE}
+
+# Here is the code to make the filterable lists shown in the crosstalk table below
+
+## Creates a reactive dataframe
+AT_2025_Long_reactive <- crosstalk::SharedData$new(AT_2025_Long)
+
+htmltools::tags$div(
+  class = "filter-container",
+  filter_checkbox(id = "LipidProbe",
+                  label = "Lipid probe in pulldown:", 
+                  sharedData = AT_2025_Long_reactive,
+                  group = ~LipidProbe),
+  filter_checkbox(id = "hit_annotation",
+                  label = "Enrichment criteria:", 
+                  sharedData = AT_2025_Long_reactive,
+                  group = ~hit_annotation)
+)
+
+?crosstalk::filter_checkbox()
+
+## Displays the reactive dataframe
+datatable(AT_2025_Long_reactive, options = list(pageLength = 10))
+
+```
+:::
+
+#### Data download
+
+{{< downloadthis DataSets/PE_HeLa_AT_2025.csv dname="PE_HeLa_AT_ChemComm_download.csv">}}

### 2025-01-16 LipidProbe/Phosphatidylethanolamine.qmd
Updates for Carsten

@@
 ```{r, echo=FALSE, warning=FALSE}
-#| fig-cap: "Volcano plots depict the relative enrichment of each protein versus non-crosslinked control (x-axis) and the statistical significance of each protein following a Student's t-test (y-axis, -log10 transformed).
+#| fig-cap: "Data as reported in [Thomas et al., 2025](/IndividualStudies/AT_2025.qmd).
+Volcano plots depict the relative enrichment of each protein versus non-crosslinked control (x-axis) and the statistical significance of each protein following a Student's t-test (y-axis, -log10 transformed).
 The left panel depicts the results of a pulldown using trifunctionalized phosphatidic acid; the right panel depicts the results of the pulldown using trifunctionalized phosphatidylethanolamine.
@@
 ```{r, echo=FALSE, warning=FALSE}
-#| fig-cap: "Ranked-order plots depict the relative enrichment of each protein versus non-crosslinked control (y-axis) from lowest to highest.
+#| fig-cap: "Data as reported in [Thomas et al., 2025](/IndividualStudies/AT_2025.qmd).
+Ranked-order plots depict the relative enrichment of each protein versus non-crosslinked control (y-axis) from lowest to highest.
 The left panel depicts the results of a pulldown using trifunctionalized phosphatidic acid; the right panel depicts the results of the pulldown using trifunctionalized phosphatidylethanolamine.
@@
 ```{r, echo=FALSE, warning=FALSE}
-#| fig-cap: "MA plots depict the average abundance of each protein in the crosslinked and uncrosslinked conditions (x-axis) versus the log2-transformed fold-change between the crosslinked and uncrosslinked conditions (y-axis).
+#| fig-cap: "Data as reported in [Thomas et al., 2025](/IndividualStudies/AT_2025.qmd).
+MA plots depict the average abundance of each protein in the crosslinked and uncrosslinked conditions (x-axis) versus the log2-transformed fold-change between the crosslinked and uncrosslinked conditions (y-axis).
 Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV)."

### 2025-01-16 LipidProbe/Sphinganine.qmd
minor tweaks
added some PIP buttons, still need content
Updates for Carsten

--- 2025-01-14 LipidProbe/Diacylglycerol.qmd
@@
 ---
-title: "Trifunctional Diacylglycerol"
+title: "Trifunctional sphinganine"
 ---
@@
 
-## Subcellular localization
+## Protein interactome
 
-## Protein interactome
+### Cell background: Huh7
+
+::: {.callout-note collapse="true"}
+
+#### Study details
+
+##### Authors
+Scotland E. Farley, Frank Stein, Per Haberkant, Fikadu G. Tafesse, Carsten Schultz
+
+##### Journal
+ACS Chemical Biology
+
+<https://doi.org/10.1021/acschembio.3c00554>{target="_blank"}
+
+##### Abstract
+
+Functions of the sphingolipids sphingosine and sphinganine in cells are not well established.
+While some signaling roles for sphingosine have been elucidated, the closely related sphinganine has been described only insofar as it does not elicit many of the same signaling responses.
+The underlying mechanisms behind the cell biological differences between these lipids are not well understood.
+Here, we prepared multifunctionalized derivatives of the two lipid species that only differ in a single double bond of the carbon backbone.
+Using these novel probes, we were able to define their spatiotemporal distribution within cells.
+Furthermore, we used these tools to systematically map the protein interactomes of both lipids.
+The lipid-protein conjugates, prepared through photo-crosslinking in live cells and extraction via click chemistry to azide beads, revealed significant differences in the captured proteins, highlighting their distinct roles in various cellular processes.
+This work elucidates mechanistic differences between these critical lipids and sets the foundation for further studies on the functions of sphingosine and sphinganine.
+
+##### Lipid probes utilized
+
+##### Cell line analyzed
+
+[Huh7](https://huh7.com){target="_blank"}
+
+##### Mass spectrometry quantification method
+
+16-channel Tandem Mass Tagging (TMT16)
+
+##### Additional sample preparation <span class="help-symbol" title="e.g. sub-cellular fractionation, depletion, etc.">?</span>
+:::
+
+::: {.panel-tabset}
+
+```{r setup, echo=FALSE, warning=FALSE, include = FALSE}
+## intitialize libraries
+library(dplyr)
+library(tidyr)
+library(plotly)
+library(ggplot2)
+library(grid)
+library(readr)
+library(rmarkdown)
+library(emojifont)
+library(gt)
+library(crosstalk)
+library(DT)
+
+## Set up the source for the standardized ggplot styles
+source("ggplot_styles.R")
+
+#  SF_2024_data <- readr::read_csv("LipidProbe/DataSets/SF_ACS-Chem-Bio_2024_download.csv") |>
+#  	filter(LipidProbe == "Spa")
+
+# 	write.csv(SF_2024_data, "LipidProbe/DataSets/Spa_Huh7_SF_2024.csv")
+
+# Opening the datatable for this page
+SF_2024_data <- readr::read_csv("DataSets/Spa_Huh7_SF_2024.csv") |>
+	filter(LipidProbe == "Spa")
+
+# Organizing the hit annotations as factors
+SF_2024_data$hit_annotation <- factor(pull(SF_2024_data, hit_annotation), levels = c("enriched hit", "hit", "enriched candidate", "candidate", "no hit", "NA"), ordered = TRUE)
+
+# Building an ID column to maintain the order on the x-axis
+ID <- c()
+for(i in 0:(nrow(SF_2024_data))){
+	ID[i] = i
+}
+
+# Applies the ID column to the Spa results
+SF_2024_ranked <- SF_2024_data |>
+    arrange(logFC) |>
+	filter(LipidProbe == "Spa") |>
+	mutate(ID = ID)
+
+```
+
+##### Volcano plot
+
+:::{.border}
+```{r, echo=FALSE, warning=FALSE}
+#| fig-cap: "Data as reported in [Farley et al., 2024](/IndividualStudies/SF_2024.qmd).
+Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV)."
+
+VolcanoPlotStandardized(SF_2024_data)
+```
+:::
+
+##### Ranked order plot
+
+:::{.border}
+```{r, echo=FALSE, warning=FALSE}
+#| fig-cap: "Data as reported in [Farley et al., 2024](/IndividualStudies/SF_2024.qmd).
+Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV)."
+
+RankedOrderPlotStandard(SF_2024_ranked)
+```
+:::
+
+##### MA Plots
+
+:::{.border}
+```{r, echo=FALSE, warning=FALSE}
+#| fig-cap: "Data as reported in [Farley et al., 2024](/IndividualStudies/SF_2024.qmd).
+Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV)."
+
+MAStandard(SF_2024_data)
+
+```
+:::
+:::
+
+Check the boxes below to filter by significance thresholds.
+
+:::{.border}
+```{r, echo=FALSE, warning=FALSE}
+
+# Here is the code to make the filterable lists shown in the crosstalk table below
+
+SF_2024_data <- SF_2024_data |>
+  select(gene_name, LipidProbe, hit_annotation, logFC, pvalue, fdr) |>
+  mutate(logFC = signif(logFC, digits=3),
+          pvalue = signif(pvalue, digits=3),
+          fdr = signif(fdr, digits = 3)) |>
+  arrange(hit_annotation) |>
+  arrange(LipidProbe)
+
+## Creates a reactive dataframe
+SF_2024_data_reactive <- crosstalk::SharedData$new(SF_2024_data)
+
+htmltools::tags$div(
+  class = "filter-container",
+  filter_checkbox(id = "hit_annotation",
+                  label = "Enrichment criteria:", 
+                  sharedData = SF_2024_data_reactive,
+                  group = ~hit_annotation)
+)
+
+## Displays the reactive dataframe
+datatable(SF_2024_data_reactive, 
+          options = list(pageLength = 10),
+                         colnames = c("Gene Name", "Lipid Probe", "Hit Annotation", "LogFC", "p value", "FDR"))
+
+```
+:::
+
+{{< downloadthis DataSets/Sph_Huh7_SF_2024.csv dname="Sph_Huh7_SF_ACS-Chem-Bio_download.csv">}}

### 2025-01-16 LipidProbe/Sphingosine.qmd
Updating individual study pages
checking render of PE page
Updates for Carsten

--- 2025-01-14 LipidProbe/Diacylglycerol.qmd
@@
 
-## Subcellular localization
+![](/LipidProbe/Structures/SphingosineStructure.png)
 
 ## Protein interactome
+
+### Cell background: Huh7
+
+::: {.callout-note collapse="true"}
+
+#### Study details
+
+##### Authors
+Scotland E. Farley, Frank Stein, Per Haberkant, Fikadu G. Tafesse, Carsten Schultz
+
+##### Journal
+ACS Chemical Biology
+
+<https://doi.org/10.1021/acschembio.3c00554>{target="_blank"}
+
+##### Abstract
+
+Functions of the sphingolipids sphingosine and sphinganine in cells are not well established.
+While some signaling roles for sphingosine have been elucidated, the closely related sphinganine has been described only insofar as it does not elicit many of the same signaling responses.
+The underlying mechanisms behind the cell biological differences between these lipids are not well understood.
+Here, we prepared multifunctionalized derivatives of the two lipid species that only differ in a single double bond of the carbon backbone.
+Using these novel probes, we were able to define their spatiotemporal distribution within cells.
+Furthermore, we used these tools to systematically map the protein interactomes of both lipids.
+The lipid-protein conjugates, prepared through photo-crosslinking in live cells and extraction via click chemistry to azide beads, revealed significant differences in the captured proteins, highlighting their distinct roles in various cellular processes.
+This work elucidates mechanistic differences between these critical lipids and sets the foundation for further studies on the functions of sphingosine and sphinganine.
+
+##### Lipid probes utilized
+
+##### Cell line analyzed
+
+[Huh7](https://huh7.com){target="_blank"}
+
+##### Mass spectrometry quantification method
+
+16-channel Tandem Mass Tagging (TMT16)
+
+##### Additional sample preparation <span class="help-symbol" title="e.g. sub-cellular fractionation, depletion, etc.">?</span>
+:::
+
+::: {.panel-tabset}
+
+<!-- Data wrangling to make the plots -->
+
+```{r setup, echo=FALSE, warning=FALSE, include = FALSE}
+## intitialize libraries
+library(dplyr)
+library(tidyr)
+library(plotly)
+library(ggplot2)
+library(grid)
+library(readr)
+library(rmarkdown)
+library(emojifont)
+library(gt)
+library(crosstalk)
+library(DT)
+
+## Set up the source for the standardized ggplot styles
+source("ggplot_styles.R")
+
+#  SF_2024_data <- readr::read_csv("LipidProbe/DataSets/SF_ACS-Chem-Bio_2024_download.csv") |>
+#  	filter(LipidProbe == "Sph")
+
+# 	write.csv(SF_2024_data, "LipidProbe/DataSets/Sph_Huh7_SF_2024.csv")
+
+# Opening the datatable for this page
+SF_2024_data <- readr::read_csv("DataSets/Sph_Huh7_SF_2024.csv") |>
+	filter(LipidProbe == "Sph")
+
+# Organizing the hit annotations as factors
+SF_2024_data$hit_annotation <- factor(pull(SF_2024_data, hit_annotation), levels = c("enriched hit", "hit", "enriched candidate", "candidate", "no hit", "NA"), ordered = TRUE)
+
+# Building an ID column to maintain the order on the x-axis
+ID <- c()
+for(i in 0:(nrow(SF_2024_data))){
+	ID[i] = i
+}
+
+# Applies the ID column to the Spa results
+SF_2024_ranked <- SF_2024_data |>
+    arrange(logFC) |>
+	filter(LipidProbe == "Sph") |>
+	mutate(ID = ID)
+
+```
+
+##### Volcano plot
+
+:::{.border}
+```{r, echo=FALSE, warning=FALSE}
+#| fig-cap: "Data as reported in [Farley et al., 2024](/IndividualStudies/SF_2024.qmd).
+Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV)."
+
+VolcanoPlotStandardized(SF_2024_data)
+```
+:::
+
+##### Ranked order plot
+
+:::{.border}
+```{r, echo=FALSE, warning=FALSE}
+#| fig-cap: "Data as reported in [Farley et al., 2024](/IndividualStudies/SF_2024.qmd).
+Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV)."
+
+RankedOrderPlotStandard(SF_2024_ranked)
+```
+:::
+
+##### MA Plots
+
+:::{.border}
+```{r, echo=FALSE, warning=FALSE}
+#| fig-cap: "Data as reported in [Farley et al., 2024](/IndividualStudies/SF_2024.qmd).
+Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV)."
+
+MAStandard(SF_2024_data)
+
+```
+:::
+:::
+
+Check the boxes below to filter by significance thresholds.
+
+:::{.border}
+```{r, echo=FALSE, warning=FALSE}
+
+# Here is the code to make the filterable lists shown in the crosstalk table below
+
+SF_2024_data <- SF_2024_data |>
+  select(gene_name, LipidProbe, hit_annotation, logFC, pvalue, fdr) |>
+  mutate(logFC = signif(logFC, digits=3),
+          pvalue = signif(pvalue, digits=3),
+          fdr = signif(fdr, digits = 3)) |>
+  arrange(hit_annotation) |>
+  arrange(LipidProbe)
+
+## Creates a reactive dataframe
+SF_2024_data_reactive <- crosstalk::SharedData$new(SF_2024_data)
+
+htmltools::tags$div(
+  class = "filter-container",
+  filter_checkbox(id = "hit_annotation",
+                  label = "Enrichment criteria:", 
+                  sharedData = SF_2024_data_reactive,
+                  group = ~hit_annotation)
+)
+
+## Displays the reactive dataframe
+datatable(SF_2024_data_reactive, 
+          options = list(pageLength = 10),
+                         colnames = c("Gene Name", "Lipid Probe", "Hit Annotation", "LogFC", "p value", "FDR"))
+
+```
+:::
+
+{{< downloadthis DataSets/Sph_Huh7_SF_2024.csv dname="Sph_Huh7_SF_ACS-Chem-Bio_download.csv">}}
+
+### Cell background: HeLa
+
+::: {.callout-note collapse="true"}
+
+#### Study details
+
+##### Authors
+
+Doris Höglinger, André Nadler,  Per Haberkant, Joanna Kirkpatrick, Martina Schifferer, Frank Stein, Sebastian Hauke, Forbes D. Porter, Carsten Schultz
+
+##### Journal
+
+PNAS
+
+<https://doi.org/10.1073/pnas.1611096114>{target="_blank"}
+
+##### Abstract
+
+Lipid-mediated signaling events regulate many cellular processes.
+Investigations of the complex underlying mechanisms are difficult because several different methods need to be used under varying conditions.
+Here we introduce multifunctional lipid derivatives to study lipid metabolism, lipid−protein interactions, and intracellular lipid localization with a single tool per target lipid.
+The probes are equipped with two photoreactive groups to allow photoliberation (uncaging) and photo–cross-linking in a sequential manner, as well as a click-handle for subsequent functionalization.
+We demonstrate the versatility of the design for the signaling lipids sphingosine and diacylglycerol; uncaging of the probe for these two species triggered calcium signaling and intracellular protein translocation events, respectively.
+We performed proteomic screens to map the lipid-interacting proteome for both lipids.
+Finally, we visualized a sphingosine transport deficiency in patient-derived Niemann−Pick disease type C fibroblasts by fluorescence as well as correlative light and electron microscopy, pointing toward the diagnostic potential of such tools.
+We envision that this type of probe will become important for analyzing and ultimately understanding lipid signaling events in a comprehensive manner.
+
+##### Lipid probes utilized
+
+Sphinganine
+
+Diacylglycerol
+
+8-3 Fatty acid
+
+##### Cell line analyzed
+
+[HeLa](https://www.atcc.org/products/ccl-2){target="_blank"}
+
+##### Mass spectrometry quantification method
+
+Peptide spectral counting
+
+:::

### 2025-01-17 LipidProbe/1-10_FattyAcid.qmd
EOD

@@
 
+:::{.border}
+![](/LipidProbe/Structures/1-10_FattyAcid_Structure.png)
+:::
+
 ## Protein interactome
 
-### Cell background: HeLa
+### Cell background: Huh7
 
@@
 
-### Study details
+#### Study details
 
-#### Authors
+##### Authors
 Scotland E. Farley, Frank Stein, Per Haberkant, Fikadu G. Tafesse, Carsten Schultz
 
-#### Journal
+##### Journal
 ACS Chemical Biology
@@
 
-#### Abstract
+##### Abstract
 
@@
 
-#### Lipid probes utilized
+##### Lipid probes utilized
 
@@
 
-#### Cell line analyzed
+##### Cell line analyzed
 
@@
 
-#### Mass spectrometry quantification method
+##### Mass spectrometry quantification method
 
@@
 
-#### Additional sample preparation <span class="help-symbol" title="e.g. sub-cellular fractionation, depletion, etc.">?</span>
+##### Additional sample preparation <span class="help-symbol" title="e.g. sub-cellular fractionation, depletion, etc.">?</span>
 :::
 
-::: {.panel-tabset}
+:::: {.panel-tabset}
 
-## Volcano plot
+##### Volcano plot
 
@@
 
-## Ranked order plot
+##### Ranked order plot
 
@@
 
-## MA Plots
+##### MA Plots
 
@@
 :::
-:::
 
-## Enriched hits
+##### Data
 
@@
 datatable(SF_2024_data_reactive, 
+          caption = "'No hit' proteins are unenriched or depleted in the presence of probe, 'enriched candidates' are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and 'enriched hits' are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV",
           options = list(pageLength = 10),
@@
 
-## Data download
+{{< downloadthis DataSets/1-10_FA_Huh7_SF_2024.csv dname="1-10_FA_Huh7_SF_ACS-Chem-Bio_2024.csv">}}
 
-{{< downloadthis DataSets/1-10_FA_Huh7_SF_2024.csv dname="1-10_FA_Huh7_SF_ACS-Chem-Bio_2024">}}
+::::

### 2025-01-17 LipidProbe/8-3_FattyAcid.qmd
EOD

@@
 
+:::{.border}
+![](/LipidProbe/Structures/8-3_FattyAcid_Structure.png)
+:::
+
 ## Protein interactome
@@
 
-::: {.panel-tabset}
+:::: {.panel-tabset}
 
@@
 #| fig-cap: "Data as reported in [Farley et al., 2024(B)](/IndividualStudies/SF_2024_B.qmd).
-Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV)."
+Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV."
 
@@
 :::
+
+##### Data
+
+:::{.border}
+```{r, echo=FALSE, warning=FALSE}
+
+# Here is the code to make the filterable lists shown in the crosstalk table below
+
+SF_2024_data <- SF_2024_data |>
+  select(gene_name, LipidProbe, hit_annotation, logFC, pvalue, fdr) |>
+  mutate(logFC = signif(logFC, digits=3),
+          pvalue = signif(pvalue, digits=3),
+          fdr = signif(fdr, digits = 3)) |>
+  arrange(hit_annotation) |>
+  arrange(LipidProbe)
+
+## Creates a reactive dataframe
+SF_2024_data_reactive <- crosstalk::SharedData$new(SF_2024_data)
+
+htmltools::tags$div(
+  class = "filter-container",
+  filter_checkbox(id = "hit_annotation",
+                  label = "Enrichment criteria:", 
+                  sharedData = SF_2024_data_reactive,
+                  group = ~hit_annotation,
+									inline=TRUE)
+)
+
+## Displays the reactive dataframe
+datatable(SF_2024_data_reactive,
+				  caption = "'No hit' proteins are unenriched or depleted in the presence of probe, 'enriched candidates' are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and 'enriched hits' are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV",
+          options = list(pageLength = 10),
+                         colnames = c("Gene Name", "Lipid Probe", "Hit Annotation", "LogFC", "p value", "FDR"))
+
+```
 :::
 
-#### Huh7 Data download
+{{< downloadthis DataSets/8-3_FA_Huh7_SF_2024.csv dname="8-3_FA_Huh7_SF_ACS-Chem-Bio_2024.csv">}}
 
-{{< downloadthis DataSets/8-3_FA_Huh7_SF_2024.csv dname="8-3_FA_Huh7_SF_ACS-Chem-Bio_2024">}}
+::::
 
@@
 
-::: {.callout-note collapse="true"}
+:::: {.callout-note collapse="true"}
 
-## Study details
+#### Study details
 
-#### Authors
+##### Authors
 
@@
 
-#### Journal
+##### Journal
 
@@
 
-:::
+::::

### 2025-01-17 LipidProbe/Diacylglycerol.qmd
EOD

@@
 
-## Subcellular localization
+:::{.border}
+:::
 
 ## Protein interactome
+
+### Cell background: HeLa
+
+::: {.callout-note collapse="true"}
+
+### Study details
+
+#### Authors
+
+Doris Höglinger, André Nadler,  Per Haberkant, Joanna Kirkpatrick, Martina Schifferer, Frank Stein, Sebastian Hauke, Forbes D. Porter, Carsten Schultz
+
+#### Journal
+
+PNAS
+
+<https://doi.org/10.1073/pnas.1611096114>{target="_blank"}
+
+#### Abstract
+
+Lipid-mediated signaling events regulate many cellular processes.
+Investigations of the complex underlying mechanisms are difficult because several different methods need to be used under varying conditions.
+Here we introduce multifunctional lipid derivatives to study lipid metabolism, lipid−protein interactions, and intracellular lipid localization with a single tool per target lipid.
+The probes are equipped with two photoreactive groups to allow photoliberation (uncaging) and photo–cross-linking in a sequential manner, as well as a click-handle for subsequent functionalization.
+We demonstrate the versatility of the design for the signaling lipids sphingosine and diacylglycerol; uncaging of the probe for these two species triggered calcium signaling and intracellular protein translocation events, respectively.
+We performed proteomic screens to map the lipid-interacting proteome for both lipids.
+Finally, we visualized a sphingosine transport deficiency in patient-derived Niemann−Pick disease type C fibroblasts by fluorescence as well as correlative light and electron microscopy, pointing toward the diagnostic potential of such tools.
+We envision that this type of probe will become important for analyzing and ultimately understanding lipid signaling events in a comprehensive manner.
+
+#### Lipid probes utilized
+
+Sphinganine
+
+Diacylglycerol
+
+8-3 Fatty acid
+
+#### Cell line analyzed
+
+[HeLa](https://www.atcc.org/products/ccl-2){target="_blank"}
+
+#### Mass spectrometry quantification method
+
+Peptide spectral counting
+
+:::

### 2025-01-17 LipidProbe/FormattingTemplate.qmd
EOD

---
title: "Formatting Template"
subtitle: "HTML page of individual lipid probe data"
---

## Structure

:::{.border}
![]()
:::

## Protein interactome

### Cell background: ???

<!-- Author information likely assembled in the relevant study page as well -->
:::: {.callout-note collapse="true"}

#### Study details

##### Authors

##### Journal

##### Abstract

##### Lipid probes utilized

##### Cell line analyzed

##### Mass spectrometry quantification method

::::

<!-- Below is the default organization of the tabset with the standard Per/Frank TMT16 ratiometric data structure -->

::::{.panel-tabset}

<!-- R setup, reading dataframes and minor data wrangling -->
```{r setup, echo=FALSE, include=FALSE}
## intitialize libraries
library(dplyr)
library(tidyr)
library(plotly)
library(ggplot2)
library(grid)
library(readr)
library(rmarkdown)
library(emojifont)
library(gt)
library(crosstalk)
library(DT)
library(htmltools)

## Opening the source file for the ggplot custom theme
source("ggplot_styles.R")

# # Opening the datatable for this page
# data <- readr::read_csv("/path/to/data")

# # Organizing the hit annotations as factors
# data$hit_annotation <- factor(pull(data, hit_annotation), levels = c("enriched hit", "hit", "enriched candidate", "candidate", "no hit", "NA"), ordered = TRUE)

# # Building an ID column to maintain the order on the x-axis
# ID <- c()
# for(i in 0:(nrow(data))){
# 	ID[i] = i
# }

# # Applies the ID column to the Spa results
# data_ranked <- data |>
#     arrange(logFC) |>
# 	filter(LipidProbe == "1-10 FA") |>
# 	mutate(ID = ID)

```

##### Volcano plot

:::{.border}
```{r, echo=FALSE, warning=FALSE}
#| fig-cap: ""

# VolcanoPlotStandardized(data)
```
:::

##### Ranked order plot

:::{.border}
```{r, echo=FALSE, warning=FALSE}
#| fig-cap: ""

#RankedOrderPlotStandard(data)
```
:::

##### MA plot

:::{.border}
```{r, echo=FALSE, warning=FALSE}
#| fig-cap: ""

#MAStandard(data)

```
:::

##### Data

:::{.border}
```{r, echo=FALSE, warning=FALSE}

# Here is the code to make the filterable lists shown in the crosstalk table below

# data <- data |>
#   select(gene_name, LipidProbe, hit_annotation, logFC, pvalue, fdr) |>
#   mutate(logFC = signif(logFC, digits=3),
#           pvalue = signif(pvalue, digits=3),
#           fdr = signif(fdr, digits = 3)) |>
#   arrange(hit_annotation) |>
#   arrange(LipidProbe)

## Creates a reactive dataframe
# data_reactive <- crosstalk::SharedData$new(data)

# htmltools::tags$div(
#   class = "filter-container",
#   filter_checkbox(id = "hit_annotation",
#                   label = "Enrichment criteria:", 
#                   sharedData = data_reactive,
#                   group = ~hit_annotation,
# 									inline=TRUE)
# )

# ## Displays the reactive dataframe
# datatable(data_reactive, 
#           options = list(pageLength = 10),
#                          colnames = c("Gene Name", "Lipid Probe", "Hit Annotation", "LogFC", "p value", "FDR"))

```
:::

{{< downloadthis /path/to/file dname="filename.csv">}}

::::

<!-- And here is the default organization of a heatmap-based visualization -->

### Cell background: ???

<!-- Author information likely assembled in the relevant study page as well -->

:::: {.callout-note collapse="true"}

#### Study details

##### Authors

##### Journal

##### Abstract

##### Lipid probes utilized

##### Cell line analyzed

##### Mass spectrometry quantification method

::::

::::{.panel-tabset}

<!-- R chunk, reading dataframes and minor data wrangling -->
```{r, echo=FALSE, include=FALSE}

```

##### Heatmap
:::{.border}
```{r, echo=FALSE, warning=FALSE}
#| fig-cap: ""

#RankedOrderPlotStandard(data)
```
:::

##### Data

:::{.border}
```{r, echo=FALSE, warning=FALSE}

# Here is the code to make the filterable lists shown in the crosstalk table below

# data <- data |>
#   select(gene_name, LipidProbe, hit_annotation, logFC, pvalue, fdr) |>
#   mutate(logFC = signif(logFC, digits=3),
#           pvalue = signif(pvalue, digits=3),
#           fdr = signif(fdr, digits = 3)) |>
#   arrange(hit_annotation) |>
#   arrange(LipidProbe)

## Creates a reactive dataframe
# data_reactive <- crosstalk::SharedData$new(data)

# htmltools::tags$div(
#   class = "filter-container",
#   filter_checkbox(id = "hit_annotation",
#                   label = "Enrichment criteria:", 
#                   sharedData = data_reactive,
#                   group = ~hit_annotation,
# 									inline=TRUE)
# )

# ## Displays the reactive dataframe
# datatable(data_reactive, 
#           options = list(pageLength = 10),
#                          colnames = c("Gene Name", "Lipid Probe", "Hit Annotation", "LogFC", "p value", "FDR"))

```
:::

::::

### 2025-01-17 LipidProbe/PhosphatidicAcid.qmd
minor tweaks
EOD

--- 2025-01-14 LipidProbe/Diacylglycerol.qmd
@@
 ---
-title: "Trifunctional Diacylglycerol"
+title: "Trifunctional Phosphatidic Acid"
 ---
@@
 
+:::{.border}
+![](/LipidProbe/Structures/PhosphatidicAcid_Structure.png)
+:::
+
 ## Subcellular localization
 
-## Protein interactome
+### Cell background: HeLa
+
+::: {.callout-note collapse="true"}
+
+#### Study details
+
+##### Authors
+Alix Thomas, Rainer Mueller, Ana Kojic, Scotland E. Farley, Frank Stein, Per Haberkant, Carsten Schultz
+
+##### Journal
+Chemical Communications
+
+<https://doi.org/10.1039/D4CC03599B>{target="_blank"}
+
+##### Abstract
+Phosphatidylethanolamine (PE) is a ubiquitous lipid species in higher eukaryotes which resides preferentially in mitochondria.
+Here, we synthesized a multifunctionalized PE derivative (1) de-signed to identify PE-binding proteins in intact cells through photo-crosslinking and subsequent isolation and proteomic analysis of the PE-protein conjugates.
+Due to its aromatic caging group, 1 is initially concentrating in perinuclear membranes.
+After uncaging, rapid translocation to mitochondria was observed.
+Hence, the tool is useful for tracking PE location and for determining the PE interactome.
+A trifunctional phosphatidic acid (PA) derivative in compari-son was rapidly metabolized and is hence more limited in its use.
+
+##### Lipid probes utilized
+
+##### Cell line analyzed
+
+[HeLa](https://www.atcc.org/products/ccl-2){target="_blank"}
+
+##### Mass spectrometry quantification method
+
+16-channel Tandem Mass Tagging (TMT16)
+
+##### Additional sample preparation <span class="help-symbol" title="e.g. sub-cellular fractionation, depletion, etc.">?</span>
+:::
+
+#### Data visualization
+
+```{r setup, echo=FALSE, include=FALSE}
+
+## intitialize libraries
+library(dplyr)
+library(tidyr)
+library(plotly)
+library(ggplot2)
+library(grid)
+library(readr)
+library(rmarkdown)
+library(emojifont)
+library(gt)
+library(crosstalk)
+library(DT)
+
+## Set up the source for the standardized ggplot styles
+source("ggplot_styles.R")
+```
+
+```{r, echo=FALSE, include=FALSE}
+
+# Data wrangling to prepare Alix's data to the standardized inputs for my plotting functions.
+# Read the data to a df
+
+# AT_2025_Long <- readr::read_csv("LipidProbe/DataSets/AT_ChemicalCommunications_2025_download.csv") |>
+# 	filter(LipidProbe == "PA")
+
+# write.csv(AT_2025_Long, "LipidProbe/DataSets/PA_HeLa_AT_2025.csv")
+
+AT_2025_Long <- readr::read_csv("DataSets/PA_HeLa_AT_2025.csv")
+
+# Organize the hit annotations as factors
+AT_2025_Long$hit_annotation <- factor(pull(AT_2025_Long, hit_annotation), levels = c("enriched hit", "enriched candidate", "no hit", "NA"), ordered=TRUE)
+
+# Building an ID column to maintain the order on the x-axis
+ID <- c()
+for(i in 0:(nrow(AT_2025_Long))){
+	ID[i] = i
+}
+
+# Applies the ID column to the PE results
+AT_2025_ranked <- AT_2025_Long |>
+    arrange(logFC) |>
+	filter(LipidProbe == "PA") |>
+	mutate(ID = ID)
+
+```
+
+::: {.panel-tabset}
+
+##### Volcano plots
+
+:::{.border}
+```{r, echo=FALSE, warning=FALSE}
+#| fig-cap: "Data as reported in [Thomas et al., 2025](/IndividualStudies/AT_2025.qmd).
+Volcano plots depict the relative enrichment of each protein versus non-crosslinked control (x-axis) and the statistical significance of each protein following a Student's t-test (y-axis, -log10 transformed).
+The left panel depicts the results of a pulldown using trifunctionalized phosphatidic acid; the right panel depicts the results of the pulldown using trifunctionalized phosphatidylethanolamine.
+Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV)."
+
+VolcanoPlotStandardized(AT_2025_Long)
+
+```
+:::
+
+##### Ranked-order plots
+
+:::{.border}
+```{r, echo=FALSE, warning=FALSE}
+#| fig-cap: "Data as reported in [Thomas et al., 2025](/IndividualStudies/AT_2025.qmd).
+Ranked-order plots depict the relative enrichment of each protein versus non-crosslinked control (y-axis) from lowest to highest.
+The left panel depicts the results of a pulldown using trifunctionalized phosphatidic acid; the right panel depicts the results of the pulldown using trifunctionalized phosphatidylethanolamine.
+Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV)."
+
+RankedOrderPlotStandard(AT_2025_ranked)
+```
+:::
+
+##### MA Plot
+
+:::{.border}
+```{r, echo=FALSE, warning=FALSE}
+#| fig-cap: "Data as reported in [Thomas et al., 2025](/IndividualStudies/AT_2025.qmd).
+MA plots depict the average abundance of each protein in the crosslinked and uncrosslinked conditions (x-axis) versus the log2-transformed fold-change between the crosslinked and uncrosslinked conditions (y-axis).
+Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV)."
+
+print("Data not yet provided.")
+
+```
+
+:::
+
+##### Data
+
+Check the boxes below to filter the dataset by which lipid probe was used in the pulldown and by significance thresholds.
+
+:::{.border}
+```{r, echo=FALSE}
+
+# Here is the code to make the filterable lists shown in the crosstalk table below
+
+AT_2025_Long <- AT_2025_Long |>
+  select(gene_name, hit_annotation, logFC, pvalue) |>
+  mutate(logFC = signif(logFC, digits=3),
+          pvalue = signif(pvalue, digits=3)) |>
+  arrange(hit_annotation)
+
+## Creates a reactive dataframe
+AT_2025_Long_reactive <- crosstalk::SharedData$new(AT_2025_Long)
+
+htmltools::tags$div(
+  class = "filter-container",
+  filter_checkbox(id = "hit_annotation",
+                  label = "Enrichment criteria:", 
+                  sharedData = AT_2025_Long_reactive,
+                  group = ~hit_annotation,
+                  inline="true")
+)
+
+?crosstalk::filter_checkbox()
+
+## Displays the reactive dataframe
+datatable(AT_2025_Long_reactive,
+          caption = "'No hit' proteins are unenriched or depleted in the presence of probe, 'enriched candidates' are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and 'enriched hits' are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV",
+          options = list(pageLength = 10))
+
+```
+:::
+
+{{< downloadthis DataSets/PA_HeLa_AT_2025.csv dname="PA_HeLa_AT_ChemComm_download.csv">}}
+
+:::

### 2025-01-17 LipidProbe/Phosphatidylethanolamine.qmd
EOD

@@
 
+:::{.border}
 ![](Structures/PhosphatidylethanolamineStructure.png)
+:::
 
@@
 
-##### MA Plots
+##### MA Plot
 
@@
 :::
-:::
 
-#### Enriched proteins
+##### Data
 
@@
 
+AT_2025_Long <- AT_2025_Long |>
+  select(gene_name, hit_annotation, logFC, pvalue) |>
+  mutate(logFC = signif(logFC, digits=3),
+          pvalue = signif(pvalue, digits=3)) |>
+  arrange(hit_annotation)
+
 ## Creates a reactive dataframe
@@
   class = "filter-container",
-  filter_checkbox(id = "LipidProbe",
-                  label = "Lipid probe in pulldown:", 
-                  sharedData = AT_2025_Long_reactive,
-                  group = ~LipidProbe),
   filter_checkbox(id = "hit_annotation",
@@
                   sharedData = AT_2025_Long_reactive,
-                  group = ~hit_annotation)
+                  group = ~hit_annotation,
+                  inline="true")
 )
@@
 ## Displays the reactive dataframe
-datatable(AT_2025_Long_reactive, options = list(pageLength = 10))
-
+datatable(AT_2025_Long_reactive,
+          caption = "'No hit' proteins are unenriched or depleted in the presence of probe, 'enriched candidates' are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and 'enriched hits' are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV",
+          options = list(pageLength = 10))
 ```
@@
 
-#### Data download
+{{< downloadthis DataSets/PE_HeLa_AT_2025.csv dname="PE_HeLa_AT_ChemComm_download.csv">}}
 
-{{< downloadthis DataSets/PE_HeLa_AT_2025.csv dname="PE_HeLa_AT_ChemComm_download.csv">}}
+:::

### 2025-01-17 LipidProbe/Sphinganine.qmd
consolidated data sections for better formatting
EOD

@@
 ## Structure
+
+:::{.border}
+![](/LipidProbe/Structures/SphinganineStructure.png)
+:::
 
@@
 :::
-:::
+
+##### Data
 
@@
 SF_2024_data <- SF_2024_data |>
-  select(gene_name, LipidProbe, hit_annotation, logFC, pvalue, fdr) |>
+  select(gene_name, hit_annotation, logFC, pvalue, fdr) |>
   mutate(logFC = signif(logFC, digits=3),
@@
           fdr = signif(fdr, digits = 3)) |>
-  arrange(hit_annotation) |>
-  arrange(LipidProbe)
+  arrange(hit_annotation)
 
@@
                   sharedData = SF_2024_data_reactive,
-                  group = ~hit_annotation)
+                  group = ~hit_annotation,
+                  inline="true")
 )
@@
 {{< downloadthis DataSets/Sph_Huh7_SF_2024.csv dname="Sph_Huh7_SF_ACS-Chem-Bio_download.csv">}}
+
+:::

### 2025-01-17 LipidProbe/Sphingosine.qmd
consolidated data sections for better formatting
EOD

@@
 
+:::{.border}
 ![](/LipidProbe/Structures/SphingosineStructure.png)
+:::
 
@@
 {{< downloadthis DataSets/Sph_Huh7_SF_2024.csv dname="Sph_Huh7_SF_ACS-Chem-Bio_download.csv">}}
+
+:::
 

### 2025-01-17 about.qmd
Made an email service for the About page

@@
 
-About this site
+This repository is still under construction (as you can probably tell).
+Someday soon this page will have details about the founders of this resource, as well as a data submission form.
+Until then, please contact the site administrators for additional information about protocols, experimental design, and website feedback:
 
-Contact the site administrators for additional information about protocols, experimental design, and website feedback:
-
-(I am working on making a comment submission form which will send an email to a site admin -- something like ContactUs\@LipidInteractome.org)
+ <contact.us@LipidInteractome.org>{target="_blank"}

### 2025-01-17 404.qmd
404 page added

---
---

```{=html}

<div style="text-align: center;">

<h2 style> Ooops! </h2>

<br>

<b> The page you're looking for doesn't (perhaps it was moved or renamed, or perhaps the site is still under construction and you can check back soon).</b>

<br>
<br>

You may want to try again or contact  <a href="site.admin@lipidinteractome.org" target="_blank">Site Admin</a> if you're looking for something specific.

<br>
<br>

<div> <a href="/index.html" target="_blank">Take me back to the Lipid Interactome </a> </div>

</div>

```

### 2025-01-21 TrifunctionalLipidProbesOverview.qmd
Minor formatting changes, overview structure added

@@
 ---
-title: "Trifunctional Lipid Probes Primer"
+title: "Multifunctional Lipid Probes Primer"
 author: "Gaelen Guzman"
@@
 
+## Functional moieties
+
+:::{.border}
+![](/LipidProbe/Structures/SphingosineStructure.png){group="ProbePrimer"}
+:::
+
+### Terminal Alkyne
+
+### Diazirine: A photo-activated crosslinker
+
+### Coumarin Cage: A photo-activated protection moiety
+
+## *P*hoto*a*ctivatable & *C*lickable Probes
+
+## Trifunctional Lipid Probes
+
+## Experimental schema
+
+### Cell treatment
+
+### Protein collection
+
+### Mass spectrometry analysis
+
+#### Spectral counting
+
+#### Isobaric mass tagging
+
 :::{.border}

### 2025-01-21 IndividualStudies/AT_2025.qmd
Updates after weekly meeting

@@
 #### Lipid probes utilized
+
+<a href="/LipidProbe/PhosphatidicAcid.qmd" class="hover-preview">Phosphatidic Acid</a>
+<span class="hover-image">
+  <img src="/LipidProbe/Structures/PhosphatidicAcid_Structure.png" alt="Phosphatidic Acid" />
+</span>
+
+<a href="/LipidProbe/Phosphatidylethanolamine.qmd" class="hover-preview">Phosphatidic Acid</a>
+<span class="hover-image">
+  <img src="/LipidProbe/Structures/PhosphatidylethanolamineStructure.png" alt="Phosphatidic Acid" />
+</span>
 

### 2025-01-21 LipidProbe/PhosphatidicAcid.qmd
Updates after weekly meeting

@@
 ##### Lipid probes utilized
+
+<a href="/LipidProbe/PhosphatidicAcid.qmd" class="hover-preview">Phosphatidic Acid</a>
+<span class="hover-image">
+  <img src="/LipidProbe/Structures/PhosphatidicAcid_Structure.png" alt="Phosphatidic Acid" />
+</span>
+
+<a href="/LipidProbe/Phosphatidylethanolamine.qmd" class="hover-preview">Phosphatidic Acid</a>
+<span class="hover-image">
+  <img src="/LipidProbe/Structures/PhosphatidylethanolamineStructure.png" alt="Phosphatidic Acid" />
+</span>
 

### 2025-01-22 MaintenanceInstructions.qmd
adding hover functionality to structures is hard...

@@
 
-Under the "IndividualStudies" folder are the .qmd files that define the preparation of each corresponding .html page. The data going into these .qmd files is stored under the "DataTables" subfolder.
+Under the "IndividualStudies" folder are the .qmd files that define the preparation of each corresponding .html page.
+The data going into these .qmd files is stored under the "DataTables" subfolder.
+Under the "LipidProbe" folder are the .qmd files that define the pages on each individual probe.
+Much of the information is copied between the two sets of pages, so be careful when making changes to one, as corresponding changes should be made elsewhere!
 
@@
 
-Any changes can then be pushed to the github repository; Netlify will pull the changes and automatically deploy the updated site!
+### GitHub repository
+
+After changes are made to the .qmd files and then rendered, the changes can then be pushed to the GitHub repository: <git@github.com:gaelenDG/LipidInteractomics_Website.git>.
+Netlify will pull the changes and automatically deploy the updated site!
 See site owners for Netlify login information and .git access.
-It will be TBD how GitHub ownership is transferred after I leave.
+
+Cloning the GitHub repository should be sufficient for gaining access to all of the files in this website - though collaborators will need to be added manually by Gaelen, the repository administrator.
+More details will go here once a more formal pull request workflow is in place!
 
@@
 If your data looks at all like [Alix's](https://lipidinteractomicsrepository.netlify.app/individualstudies/at_2025){target="_blank"} or [Scotty's](https://lipidinteractomicsrepository.netlify.app/individualstudies/sf_2024){target="_blank"}, the ggplot functions I built in the ggplot_styles.R file will apply.
-Call the RankedOrderPlotStandard() and VolcanoPlotStandardized() functions to produce these plots with the same standardized formatting.
+Call the RankedOrderPlotStandard(), VolcanoPlotStandardized(), and MAStandard() functions to produce these plots with the same standardized formatting.
 On that note, you can alter the ggplot_styles.R file to change the standardized formatting.

### 2025-01-22 TrifunctionalLipidProbesOverview.qmd
Updates after weekly meeting
adding hover functionality to structures is hard...

@@
 ---
-title: "Multifunctional Lipid Probes Primer"
+title: "Multifunctional Lipid Probes Background"
 author: "Gaelen Guzman"
@@
 
-I could use help writing a succinct article here to describe the use of these probes.
-We can additionally reference prior publications here -- but I think it would be nice to have a novel description with figures for this site.
-
-I have a few example figures, but I am open to using whichever figures seem best -- if that is a new figure, I'll need guidance on what it should look like.
+Functionalized lipid probes are at the intersection of several niche biotechnologies.
+This overview will serve as a brief summary of the capabilities, nuances, and caveats of their utility.
+Additional resources and published review articles will be linked below for greater detail.
 
@@
 :::{.border}
-![](/LipidProbe/Structures/SphingosineStructure.png){group="ProbePrimer"}
+
+```{r setup, echo=FALSE, include=FALSE}
+library(plotly)
+
+library(plotly)
+
+# Load your image
+image_url <- "LipidProbe/Structures/SphingosineStructure.png"
+
+# Define hover regions (as rectangles)
+shapes <- list(
+  list(type = "rect", x0 = 0, x1 = 32, y0 = 50, y1 = 85,
+       line = list(color = "red", width = 2),
+       fillcolor = "rgba(255, 0, 0, 0.1)",  # Transparent fill
+       name = "Region 1", hoverinfo = "none"),
+  list(type = "rect", x0 = 50, x1 = 70, y0 = 40, y1 = 60,
+       line = list(color = "blue", width = 2),
+       fillcolor = "rgba(0, 0, 255, 0.1)",  # Transparent fill
+       name = "Region 2", hoverinfo = "none")
+)
+
+# Define hover annotations
+hover_annotations <- data.frame(
+  x = c(20, 60),  # Midpoints of rectangles
+  y = c(80, 50),
+  text = c("Region 1 Info", "Region 2 Info")
+)
+
+# Create the plot
+plot <- plot_ly() %>%
+  add_trace(
+    data = hover_annotations,
+    x = ~x, y = ~y, text = ~text,
+    mode = "markers",
+    marker = list(opacity = 0),  # Invisible markers
+    hoverinfo = "text"  # Show hover text
+  ) %>%
+  layout(
+    shapes = shapes,
+    images = list(
+      list(
+        source = image_url,
+        xref = "x",
+        yref = "y",
+        x = 0,
+        y = 100,
+        sizex = 100,
+        sizey = 100,
+        xanchor = "left",
+        yanchor = "top",
+        layer = "below"
+      )
+    ),
+    xaxis = list(visible = FALSE, range = c(0, 100)),
+    yaxis = list(visible = FALSE, range = c(0, 100))
+  )
+```
+
+```{r, echo=FALSE, warnings=FALSE}
+# Render the plot
+plot
+
+```
+:::
+
+:::{.border}
+```{=html}
+<div style="position: relative; display: inline-block;">
+  <img src="LipidProbe/Structures/SphingosineStructure.png" alt="Interactive Image" style="width: 500px;">
+
+  <!-- Popup 1 -->
+  <div style="position: absolute; top: 20%; left: 10%; cursor: pointer;">
+    <span class="popup-hover" title="Popup for Point 1">🔴</span>
+  </div>
+
+  <!-- Popup 2 -->
+  <div style="position: absolute; top: 70%; left: 50%; cursor: pointer;">
+    <span class="popup-hover" title="Popup for Point 2">🔵</span>
+  </div>
+
+  <!-- Hover region 1 -->
+  <div style="position: absolute; top: 20%; left: 10%; width: 15%; height: 15%; border: 2px solid red; box-sizing: border-box;"
+       title="Region 1 Info"></div>
+
+  <!-- Hover region 2 -->
+  <div style="position: absolute; top: 50%; left: 50%; width: 20%; height: 20%; border: 2px solid blue; box-sizing: border-box;"
+       title="Region 2 Info"></div>
+</div>
+</div>
+
+<style>
+  .popup-hover:hover::after {
+    content: attr(title);
+    position: absolute;
+    top: -30px;
+    left: 0;
+    background: white;
+    color: black;
+    padding: 5px;
+    border: 1px solid #ccc;
+    border-radius: 5px;
+    white-space: nowrap;
+    box-shadow: 0px 4px 6px rgba(0, 0, 0, 0.1);
+  }
+</style>
+
+```
+
 :::

### 2025-01-22 index.qmd
adding hover functionality to structures is hard...

@@
 
-A blurb about the objective of this site, maybe a gallery of images from select publications to put here.
+The goal of this site is to increase the accessibility of proteomics data utilizing multi-functionalized lipid analogs/probes to identify the lipid::protein interactions of biologically active lipids.
+
+Explore the lipids below to see their published interactomes.
+
+See our [Functional Lipid Probes Overview](/TrifunctionalLipidProbesOverview.qmd) for more details about how these lipid analogs are used.
 

### 2025-01-24 TrifunctionalLipidProbesOverview.qmd
small update to overview text

@@
 This overview will serve as a brief summary of the capabilities, nuances, and caveats of their utility.
-Additional resources and published review articles will be linked below for greater detail.
+Additional resources and published review articles will be referenced throughout and linked below for greater detail.
 
-## Functional moieties
+## Introduction: Why study lipid interactomes?
+
+## Why are functional modifications necessary in studying lipid interactions?
+
+Synthetic lipid analogs have greatly enabled the exploration of lipid biology. However, it may not be obvious why such analogs are such valuable tools.
+
+While, genetic editing has enabled vast advances in the study of nucleic acids and proteins, there has been no obvious parallel for studying lipids.
+Using CRISPR or *de novo* gene synthesis, one can subtly alter a sequence to enable visualization and pulldown without greatly affecting the structure or function of the target gene.
+To name a few examples, one can: mutate the active site of a protein to change substrate specificity, swap in a different subcellular localization sequence to translocate the target protein to a different organelle, swap domains to alter protein::protein binding, fuse the target protein to any number of fluorescent domains to visualize a protein's localization, or add an affinity handle to enable the enrichment of the target protein and any other protein interactors [REF].
+
+Lipids, however, are an entirely different story altogether.
+Foremost of these differences is that lipids are the product of enzymatic synthesis and thus their structure cannot be directly modified within a living biological system.
+For much of the history of lipid research, studies utilized whole gene knockout or knock-in paradigms to alter the global lipid composition of the cell.
+Through these methods, we know much about the localization and broad behavior of lipid classes -- but the biological roles of select lipid species are historically challenging to explore [REF].
+
+Further, lipids are significantly smaller than even the smallest protein -- composed of dozens of atoms, as opposed to hundreds or thousands -- and, thus, their biophysical properties are much more sensitive to modification.
+It is nearly impossible to fuse a lipid with a fluorescent protein (such as GFP) or classical affinity handle (such as an HA tag) without drastically affecting the biological activity of the lipid [REF].
+
+Finally, each of the tens of thousands of distinct lipid structures is a part of a rapidly shifting metabolic network: any given lipid can be cleaved, modified, or converted into other lipid species within short time frames.
+Some lipids, such as sphingosine have half-lives in the minutes [REF].
+
+For these reasons, synthetic analogs to native lipids have been a great utility toward probing the biological function of select lipid species. The chief modifications described in this repository
 
 :::{.border}
-
 ```{r setup, echo=FALSE, include=FALSE}
@@
 </style>
-
 ```
-
 :::

### 2025-01-24 LipidProbe/PhosphatidicAcid.qmd
fleshing out overview

@@
 
-## Subcellular localization
-
 ### Cell background: HeLa
@@
 
-#### Study details
+## Study details
 
-##### Authors
+#### Authors
 Alix Thomas, Rainer Mueller, Ana Kojic, Scotland E. Farley, Frank Stein, Per Haberkant, Carsten Schultz
 
-##### Journal
+#### Journal
 Chemical Communications
@@
 
-##### Abstract
+#### Abstract
 Phosphatidylethanolamine (PE) is a ubiquitous lipid species in higher eukaryotes which resides preferentially in mitochondria.
@@
 
-##### Lipid probes utilized
+#### Lipid probes utilized
 
@@
 
-##### Cell line analyzed
+#### Cell line analyzed
 
@@
 
-##### Mass spectrometry quantification method
+#### Mass spectrometry quantification method
 
@@
 
-##### Additional sample preparation <span class="help-symbol" title="e.g. sub-cellular fractionation, depletion, etc.">?</span>
+::: {.callout-note collapse="true"}
+##### ProteomeXchange details
+
+**ProteomeXchange title:** Trifunctional lipid derivatives: PE’s mi-tochondrial interactome
+
+**ProteomeXchange accession:** PXD059960
+
+**PubMed ID:** Not applicable
+
+**Publication DOI:** 10.1039/D4CC03599B
+
+**Project Webpage:** http://www.ebi.ac.uk/pride/archive/projects/PXD059960
+
+**FTP Download:** https://ftp.pride.ebi.ac.uk/pride/data/archive/2025/01/PXD059960
+:::
+
+#### Additional sample preparation <span class="help-symbol" title="e.g. sub-cellular fractionation, depletion, etc.">?</span>
 :::

### 2025-01-24 TrifunctionalLipidProbesOverview.qmd
fleshing out overview

@@
 standalone: true
+crossref: 
+  ref-hyperlink: true # (default is true)
 ---
+
+**This repository is still under construction, please forgive us for incomplete sections as we build features!**
 
@@
 ## Introduction: Why study lipid interactomes?
+
+* Because at its core biology is just complex chemistry, all biological reactions are mediated through the physical interaction of two or more molecules
+
+* Lipid::Lipid interactomes can provide insight into which of these physical contacts mediate these membrane properties.
+Lipids are most commonly enmeshed within membrane bilayers and lipid-lipid interactions confer membrane properties such as rigidity or detergent resistance.
+
+* In recent decades, many select lipid species have gained recognition for being crucial signaling molecules.
+For one example, the sphingolipid sphingosine-1-phosphate (S1P) is potently recognized by an array of S1P receptors which cause T cells to extravasate and chemotax toward sites of infection.
+
+* Understanding the proteins that a given lipid interacts with can reveal great insight into the wide-ranging cellular signaling effects that a lipid can have.
 
@@
 
-For these reasons, synthetic analogs to native lipids have been a great utility toward probing the biological function of select lipid species. The chief modifications described in this repository
+For these reasons, synthetic analogs to native lipids have been a great utility toward probing the biological function of select lipid species.
+The chief modifications described in this repository (highlighted in the figure below) are:
+1. A diazirine ring 
+2. A terminal alkyne
+3. A coumarin cage.
+
+These modifications allow for the stabilization of protein::lipid interactions and the affinity enrichment of protein::lipid conjugates, all with tight spatiotemporal control.
+These modifications are described in greater detail below.
 
@@
 library(plotly)
-
-library(plotly)
+library(tidyr)
 
@@
 
-# Define hover regions (as rectangles)
-shapes <- list(
-  list(type = "rect", x0 = 0, x1 = 32, y0 = 50, y1 = 85,
-       line = list(color = "red", width = 2),
-       fillcolor = "rgba(255, 0, 0, 0.1)",  # Transparent fill
-       name = "Region 1", hoverinfo = "none"),
-  list(type = "rect", x0 = 50, x1 = 70, y0 = 40, y1 = 60,
-       line = list(color = "blue", width = 2),
-       fillcolor = "rgba(0, 0, 255, 0.1)",  # Transparent fill
-       name = "Region 2", hoverinfo = "none")
-)
-
-# Define hover annotations
-hover_annotations <- data.frame(
-  x = c(20, 60),  # Midpoints of rectangles
-  y = c(80, 50),
+# Define hover regions (rectangles) with coordinates based on the top of the image
+hover_regions <- data.frame(
+  x_start = c(0.0, 0.7),  # Left side of rectangles (fraction of width)
+  x_end = c(0.4, 0.9),    # Right side of rectangles (fraction of width)
+  y_top = c(0.2, 0.3),    # Top side of rectangles (fraction of height, from top of image)
+  y_bottom = c(0.4, 0.4), # Bottom side of rectangles (fraction of height, from top of image)
   text = c("Region 1 Info", "Region 2 Info")
@@
 
+# Create grid lines at every 10% for both x and y
+grid_lines <- list()
+for (i in seq(0, 1, by = 0.1)) {
+  # Add vertical grid line
+  grid_lines <- c(grid_lines, list(
+    list(
+      type = "line",
+      x0 = i, x1 = i,
+      y0 = 0, y1 = 1,
+      line = list(color = "gray", width = 1, dash = "dot")
+    )
+  ))
+
+  # Add horizontal grid line
+  grid_lines <- c(grid_lines, list(
+    list(
+      type = "line",
+      x0 = 0, x1 = 1,
+      y0 = i, y1 = i,
+      line = list(color = "gray", width = 1, dash = "dot")
+    )
+  ))
+}
+
 # Create the plot
-plot <- plot_ly() %>%
+plot <- plot_ly()
+
+# Add each rectangle as a separate trace
+for (i in 1:nrow(hover_regions)) {
+  region <- hover_regions[i, ]
+  x_coords <- c(region$x_start, region$x_end, region$x_end, region$x_start, region$x_start)
+  y_coords <- c(1 - region$y_top, 1 - region$y_top, 1 - region$y_bottom, 1 - region$y_bottom, 1 - region$y_top)
+
+  plot <- plot %>%
     add_trace(
-    data = hover_annotations,
-    x = ~x, y = ~y, text = ~text,
-    mode = "markers",
-    marker = list(opacity = 0),  # Invisible markers
-    hoverinfo = "text"  # Show hover text
-  ) %>%
+      x = x_coords,
+      y = y_coords,
+      type = "scatter",
+      mode = "lines",
+      line = list(
+        color = "blue",     # Border color
+        width = 2           # Border width
+      ),
+      fill = "none",         # No fill color inside the rectangle
+      hoverinfo = "text",    # Show text on hover
+      text = region$text
+    )
+}
+
+# Add the image
+plot <- plot %>%
   layout(
-    shapes = shapes,
     images = list(
@@
         source = image_url,
-        xref = "x",
-        yref = "y",
-        x = 0,
-        y = 100,
-        sizex = 100,
-        sizey = 100,
+        xref = "paper",  # Normalized to percentage
+        yref = "paper",  # Normalized to percentage
+        x = 0,           # Start at 0% of the plot width
+        y = 1,           # Start at 100% of the plot height
+        sizex = 1,       # Cover 100% of the plot width
+        sizey = 1,       # Cover 100% of the plot height
         xanchor = "left",
@@
     ),
-    xaxis = list(visible = FALSE, range = c(0, 100)),
-    yaxis = list(visible = FALSE, range = c(0, 100))
+    xaxis = list(visible = FALSE, range = c(0, 1)),  # Normalized from 0 to 1
+    yaxis = list(visible = FALSE, range = c(0, 1)),
+    shapes = grid_lines # Add the grid lines to the layout
   )
+
 ```
@@
 ```{r, echo=FALSE, warnings=FALSE}
+#| height: 500px
+#| width: 100%
 # Render the plot
@@
 
-:::{.border}
-```{=html}
-<div style="position: relative; display: inline-block;">
-  <img src="LipidProbe/Structures/SphingosineStructure.png" alt="Interactive Image" style="width: 500px;">
-
-  <!-- Popup 1 -->
-  <div style="position: absolute; top: 20%; left: 10%; cursor: pointer;">
-    <span class="popup-hover" title="Popup for Point 1">🔴</span>
-  </div>
-
-  <!-- Popup 2 -->
-  <div style="position: absolute; top: 70%; left: 50%; cursor: pointer;">
-    <span class="popup-hover" title="Popup for Point 2">🔵</span>
-  </div>
-
-  <!-- Hover region 1 -->
-  <div style="position: absolute; top: 20%; left: 10%; width: 15%; height: 15%; border: 2px solid red; box-sizing: border-box;"
-       title="Region 1 Info"></div>
-
-  <!-- Hover region 2 -->
-  <div style="position: absolute; top: 50%; left: 50%; width: 20%; height: 20%; border: 2px solid blue; box-sizing: border-box;"
-       title="Region 2 Info"></div>
-</div>
-</div>
-
-<style>
-  .popup-hover:hover::after {
-    content: attr(title);
-    position: absolute;
-    top: -30px;
-    left: 0;
-    background: white;
-    color: black;
-    padding: 5px;
-    border: 1px solid #ccc;
-    border-radius: 5px;
-    white-space: nowrap;
-    box-shadow: 0px 4px 6px rgba(0, 0, 0, 0.1);
-  }
-</style>
-```
-:::
-
 ### Terminal Alkyne
 
-### Diazirine: A photo-activated crosslinker
+### Diazirine: A photo-activated crosslinker {#sec-DiazirinePlacement}
 
@@
 ## Experimental schema
+
+:::{.border}
+![](SiteFigures/BaselineProteomics_ExperimentalDesign.png){group="Overview_gallery"}
+:::
 
@@
 
-:::{.border}
-![](SiteFigures/BaselineProteomics_ExperimentalDesign.png){group="Overview_gallery"}
-:::
-
 \br

### 2025-01-27 TrifunctionalLipidProbesOverview.qmd
Working on overview page

@@
 2. A terminal alkyne
-3. A coumarin cage.
+3. A coumarin photocage
 
@@
 
+* Affinity handle
+* Affix fluorophore post-hoc
+
 ### Diazirine: A photo-activated crosslinker {#sec-DiazirinePlacement}
 
-### Coumarin Cage: A photo-activated protection moiety
+* Crosslinking motif activated by 355nm UV light. 
+* Irradiation of the ring produces a reactive carbene radical which covalently bonds with any nearby molecule.
+This radical can form linkages by inserting into carbo-hydrogen, heteroatom-hydrogen (SH, NH~2~, or OH) or double bonds[@haberkantFatFabulousBifunctional2014].
+* This chemical group is the smallest available photoactivatable crosslinking motif [@haberkantFatFabulousBifunctional2014]
 
-## *P*hoto*a*ctivatable & *C*lickable Probes
+References to include: 
+* [@schultzFlashClickMultifunctionalized2022a]
+* [@schultzChemicalToolsLipid2023]
+* [@farleyTrifunctionalSphinganineNew2024a]
+* [@hoglingerTrifunctionalLipidProbes2017]
+
+### Coumarin Photocage: A photo-activated protection moiety
+
+* Many native lipids of interest are rapidly synthesized, catabolized, and interconverted throughout the vast lipid metabolic network. 
+* The coumarin cage is a photolabile protection group. Upon stimulation with 400nm light, this group is released to expose the native structure of the lipid headgroup.
+* The exposure of the native headgroup allows for recognition by protein binders.
+For example, Hoglinger et al.
+showed in 2015 that the release of caged sphingosine resulted in potent lysosomal calcium release -- a finding which greatly expanded the understanding of the intracellular sphingosine signaling cascade[@hoglingerIntracellularSphingosineReleases2015a].
+In this and other studies, sub-cellular irradiation using a scanning laser allows for the select spatial control of uncaging.
+While not compatible with large-scale interaction studies, this method enables the assessment of biological activity via fluorescence microscopy.
+* An additional boon of using coumarin as the caging moiety is its inherent fluorescence: one can simply use a fluorescence microscope to rapidly assess the intercalation of the functionalized lipid into the target cell.
+
+## Photoactivatable & Clickable Probes / Bifunctional Lipid Probes
+
+* The conceptual precursor to the so-called trifunctional probes, these typically include only the diazirine and the terminal alkyne moieties.
+
+References to include: 
+* [@haberkantFatFabulousBifunctional2014] - Haberkant et al. 2014
 
@@
 
-## Experimental schema
+References to include:
+*
+
+## Interactomics Experimental schema
 

### 2025-01-27 TrifunctionalLipidProbesOverview.qmd
updates to MS techniques

@@
 Using CRISPR or *de novo* gene synthesis, one can subtly alter a sequence to enable visualization and pulldown without greatly affecting the structure or function of the target gene.
-To name a few examples, one can: mutate the active site of a protein to change substrate specificity, swap in a different subcellular localization sequence to translocate the target protein to a different organelle, swap domains to alter protein::protein binding, fuse the target protein to any number of fluorescent domains to visualize a protein's localization, or add an affinity handle to enable the enrichment of the target protein and any other protein interactors [REF].
+To name a few examples, one can: mutate the active site of a protein to change substrate specificity, swap in a different subcellular localization sequence to translocate the target protein to a different organelle, swap domains to alter protein::protein binding, fuse the target protein to any number of fluorescent domains to visualize a protein's localization, or add an affinity handle to enable the enrichment of the target protein and any other protein interactors [@schultzChemicalToolsLipid2023].
 
@@
 
+* Isolating peptide-like ions in MS1 scan, fragmenting in MS2 scan to record peptide sequence, consolidating the sum total of individual scans for each peptide mapped to each protein.
+This sum can be used as a proxy for the absolute abundance of the protein when comparing two samples prepared in identical manners and run on the same LC-MS/MS protocol.
+
+Pros:
+* Widely used, though not strictly a direct measurement of relative abundance. Highly accessible, as label-free quantification is much less costly and sample preparation is much more simple.
+
+Cons:
+* Co-elution of high- and low-abundance peptides can cause significant issues in the number of peptides can be isolated in MS1. 
+* Samples are necessarily run at different times.
+Instrument calibration can drift, contaminants in the liquid chromatography can build, and errors can accrue in the preparation of each sample.
+Unless great care is taken, substantial differences between MS runs can result in the reporting of artificial differences between the samples.
+
 #### Isobaric mass tagging
+
+* Chemically adding a mass tag to each peptide in a sample, pooling with other samples, running as combined sample group in a single MS run.
+As before, peptide isolation in MS1, fragmentation and sequence identification in MS2.
+Additional identification of fragmented mass tags in MS2 reveals the relative abundances of the peptide in each contributing sample.
+
+Pros:
+* Because many (16+ in the case of Tandem Mass Tags^TM^) samples can be pooled in each experimental group, the total number of MS runs can be reduced.
+Alternatively, the pooled experimental group can be fractionated (typically orthogonally to the reverse phase chromatography used in the LC injection method; e.g.
+cation exchange) so that high-abundance and low-abundance proteins can be spaced out.
+  * For example, instead of performing 16 individual low-depth MS runs using label-free methods, one may run 6 fractionated MS runs of the pooled experimental group, resulting in significantly greater depth of MS1 peptide coverage.
+
+Cons:
+* Cost
+* Increased number of sample preparation steps, higher probability to introduce variation in sample handling.
+* Requirement for normalizing total protein input: when comparing +UV to -UV in diazirine enrichment, one necessarily must artificially combine disproportionate sample quantities.
+[We might not want to mention this here, it's a niche issue...]
+* Need for greater precision in MS scanning -- more expensive instruments and outsourcing of sample analysis.
 

### 2025-01-28 TrifunctionalLipidProbesOverview.qmd
tiny formatting change

@@
 References to include:
+
 * [@schultzFlashClickMultifunctionalized2022a]
@@
 References to include:
+
 * [@haberkantFatFabulousBifunctional2014] - Haberkant et al. 2014
@@
 Pros:
+
 * Widely used, though not strictly a direct measurement of relative abundance. Highly accessible, as label-free quantification is much less costly and sample preparation is much more simple.
@@
 Cons:
+
 * Co-elution of high- and low-abundance peptides can cause significant issues in the number of peptides can be isolated in MS1. 
@@
 Pros:
+
 * Because many (16+ in the case of Tandem Mass Tags^TM^) samples can be pooled in each experimental group, the total number of MS runs can be reduced.
@@
 Cons:
+
 * Cost

### 2025-01-28 LipidProbe/EnrichedHitsComparison.qmd
Added a shiny app

---
title: "Comparing the Enriched Hits of Different Probes"
---

<!-- Data wrangling, will comment out most of this when it's all done. 
Pulling the enriched hits from each probe, then making a long dataframe that can be plopped into a Venn diagram adjacent visualization -->
```{r setup, echo=FALSE,include=FALSE}
library(dplyr)
library(tidyr)
library(readr)

# # Making a big shared dataset with all of the TMT-quantified lipid probes - this is a little hand-wavey because some were run at different times... TBD if we want to keep this.
# PA_data <- read_csv("LipidProbe/DataSets/PA_HeLa_AT_2025.csv") |>
# 	select(LipidProbe, gene_name, logFC, pvalue, hit_annotation)

# PE_data <- read_csv("LipidProbe/DataSets/PE_HeLa_AT_2025.csv") |>
# 	select(LipidProbe, gene_name, logFC, pvalue, hit_annotation)

# Spa_data <- read_csv("LipidProbe/DataSets/Spa_Huh7_SF_2024.csv") |>
# 	select(LipidProbe, gene_name, logFC, pvalue, hit_annotation)

# Sph_data <- read_csv("LipidProbe/DataSets/Sph_Huh7_SF_2024.csv") |>
# 	select(LipidProbe, gene_name, logFC, pvalue, hit_annotation)

# FA_8_3_data <- read_csv("LipidProbe/DataSets/8-3_FA_Huh7_SF_2024.csv") |>
# 	select(LipidProbe, gene_name, logFC, pvalue, hit_annotation)

# FA_1_10_data <- read_csv("LipidProbe/DataSets/1-10_FA_Huh7_SF_2024.csv") |>
# 	select(LipidProbe, gene_name, logFC, pvalue, hit_annotation)

# combinedDataset <- rbind(PA_data, PE_data, Spa_data, Sph_data, FA_8_3_data, FA_1_10_data)

#write.csv(combinedDataset, "LipidProbe/DataSets/combinedProbeDatasets_TMT.csv")
```

:::{.border}
:::{#fig-ShinyEmbed}
```{=html}
<!DOCTYPE html>
<html lang="en">
<head>
  <meta charset="UTF-8">
  <meta name="viewport" content="width=device-width, initial-scale=1.0">
  <title>Shiny App Embedding</title>
  <style>
    iframe {
      width: 100%;
      height: 90vh;
      border: none;
    }
  </style>
</head>
<body>
  <iframe src="https://gaelen-guzman.shinyapps.io/lipidinteractomics_shinyapp/"></iframe>
</body>
</html>
```

Black proteins are unenriched in respect to both probes; Purple proteins are "enriched" with respect to only the probe on the x-axis; Green proteins are "enriched" with respect to only the probe on the y-axis; and Orange proteins are "enriched" in both probes. Depicted are only the proteins present in the datasets of both probes.
:::
:::

### 2025-01-28 LipidProbe/DataSets/LipidInteractomics_ShinyApp/app.R

@@ -1,0 +1,146 @@
+library(dplyr)
+library(tidyr)
+library(ggplot2)
+library(plotly)
+library(readr)
+library(shiny)
+
+df <- read_csv("combinedProbeDatasets_TMT.csv")
+
+probeOptions <- unique(df$LipidProbe)
+
+# Shiny App
+ui <- fluidPage(
+  titlePanel("Interactive LogFC Comparison"),
+  
+  sidebarLayout(
+    sidebarPanel(
+      selectInput("probe1", "Select First LipidProbe:", choices = probeOptions, selected = probeOptions[1]),
+      selectInput("probe2", "Select Second LipidProbe:", choices = probeOptions, selected = probeOptions[2])
+    ),
+    mainPanel(
+      plotlyOutput("logFCPlot")
+    )
+  )
+)
+
+server <- function(input, output, session) {
+	
+	xData <- reactive({
+		xData<- df |>
+			filter(LipidProbe == input$probe1) 
+		return(xData)
+	})
+
+	yData <- reactive({
+		yData<- df |>
+			filter(LipidProbe == input$probe2) 
+		return(yData)
+	})
+
+  output$logFCPlot <- renderPlotly({
+		probe1Name <- input$probe1
+		probe2Name <- input$probe2
+
+		# Create a new dataframe for plotting
+		xData <- xData()
+		yData <- yData()
+
+		plot_data <- merge(xData, yData, by="gene_name") |>
+			mutate(combined_hit_annotation = case_when(hit_annotation.x == "enriched hit" & hit_annotation.y == "enriched hit" ~ "enriched on both axes",
+                                                   hit_annotation.x != "enriched hit" & hit_annotation.y == "enriched hit" ~ "enriched y-axis only",
+                                                   hit_annotation.x == "enriched hit" & hit_annotation.y != "enriched hit" ~ "enriched x-axis only",
+                                                   .default = "enriched on neither axis")) |>
+        mutate_if(is.numeric, ~replace(., is.na(.), 0)) |>
+        mutate_if(is.character, ~replace(., is.na(.), "no id")) |>
+				arrange(combined_hit_annotation) |>
+				glimpse()
+
+		print(head(plot_data))
+
+		plot_data$combined_hit_annotation <- factor(pull(plot_data, combined_hit_annotation),
+                                                     levels = c("enriched on both axes",
+                                                                "enriched x-axis only",
+                                                                "enriched y-axis only",
[…]

### 2025-01-30 LipidProbe/EnrichedHitsComparison.qmd
pre-meeting update

@@
 ---
+
+## Ratiometric data
+
+For a select subset of the lipid probes depicted on this repository, one can directly compare their enrichment of proteins.
+In the case of the trifunctionalized PE, PA, Sph, Spa, 8-3 FA, and 1-10 FA probes, all were analyzed using quantitative mass spectrometry via [Tandem Mass Tagging](@sec-TMT).
+
+Use the dropdown menu below to select two lipid probes to plot against each other and visualize the enriched hits of each probe.
+Black proteins are unenriched in respect to both probes; Purple proteins are "enriched" with respect to only the probe on the x-axis; Green proteins are "enriched" with respect to only the probe on the y-axis; and Orange proteins are "enriched" in both probes.
+Depicted are only the proteins present in the datasets of both probes.
 
@@
 library(readr)
-
+library(ggvenn)
+library(crosstalk)
+library(VennDiagram)
+library(htmlwidgets)
+library(plotly)
+library(DT)
 # # Making a big shared dataset with all of the TMT-quantified lipid probes - this is a little hand-wavey because some were run at different times... TBD if we want to keep this.
@@
 :::{.border}
-:::{#fig-ShinyEmbed}
 ```{=html}
@@
 ```
+:::
 
-Black proteins are unenriched in respect to both probes; Purple proteins are "enriched" with respect to only the probe on the x-axis; Green proteins are "enriched" with respect to only the probe on the y-axis; and Orange proteins are "enriched" in both probes.
-Depicted are only the proteins present in the datasets of both probes.
-:::
-:::
+## Shared hits
+
+```{r, echo=FALSE, warning=FALSE, include=FALSE}
+# Making a dataset for a venn diagram maker! This will all be commented out at the end.
+
+# PA_data <- read_csv("/Users/gaelenguzman/LipidInteractomics_Website_local/LipidInteractomics_Website/LipidProbe/DataSets/PA_HeLa_AT_2025.csv") |>
+#   filter(hit_annotation == "enriched hit") |>
+# 	select(LipidProbe, gene_name)
+
+# PE_data <- read_csv("/Users/gaelenguzman/LipidInteractomics_Website_local/LipidInteractomics_Website/LipidProbe/DataSets/PE_HeLa_AT_2025.csv") |>
+# 	filter(hit_annotation == "enriched hit") |>
+# 	select(LipidProbe, gene_name)
+
+# Spa_data <- read_csv("/Users/gaelenguzman/LipidInteractomics_Website_local/LipidInteractomics_Website/LipidProbe/DataSets/Spa_Huh7_SF_2024.csv") |>
+# 	filter(hit_annotation == "enriched hit") |>
+# 	select(LipidProbe, gene_name)
+
+# Sph_data <- read_csv("/Users/gaelenguzman/LipidInteractomics_Website_local/LipidInteractomics_Website/LipidProbe/DataSets/Sph_Huh7_SF_2024.csv") |>
+# 	filter(hit_annotation == "enriched hit") |>
+# 	select(LipidProbe, gene_name)
+
+# FA_8_3_data <- read_csv("/Users/gaelenguzman/LipidInteractomics_Website_local/LipidInteractomics_Website/LipidProbe/DataSets/8-3_FA_Huh7_SF_2024.csv") |>
+# 	filter(hit_annotation == "enriched hit") |>
+# 	select(LipidProbe, gene_name)
+
+# FA_1_10_data <- read_csv("/Users/gaelenguzman/LipidInteractomics_Website_local/LipidInteractomics_Website/LipidProbe/DataSets/1-10_FA_Huh7_SF_2024.csv") |>
+# 	filter(hit_annotation == "enriched hit") |>
+# 	select(LipidProbe, gene_name)
+
+# combinedDataset <- rbind(PA_data, PE_data, Spa_data, Sph_data, FA_8_3_data, FA_1_10_data)
+
+# write.csv(combinedDataset, "/Users/gaelenguzman/LipidInteractomics_Website_local/LipidInteractomics_Website/LipidProbe/DataSets/combinedProbeDatasets_VennDiagram.csv")
+```

### 2025-01-30 TrifunctionalLipidProbesOverview.qmd
pre-meeting update

--- 2025-01-27 TrifunctionalLipidProbesOverview.qmd
@@
 crossref: 
-  ref-hyperlink: true # (default is true)
+  ref-hyperlink: true
 ---
@@
 
-## Introduction: Why study lipid interactomes?
+## Introduction: Why Study Lipid Interactomes?
 
-* Because at its core biology is just complex chemistry, all biological reactions are mediated through the physical interaction of two or more molecules
+At its core, biology is a complex network of chemical interactions.
+Every biological process—from metabolism to signaling—depends on the physical interactions between molecules, including proteins, nucleic acids, and lipids.
+While proteins have long been the primary focus of interaction studies, lipids play an equally crucial yet often underappreciated role in cellular function.
 
-* Lipid::Lipid interactomes can provide insight into which of these physical contacts mediate these membrane properties.
-Lipids are most commonly enmeshed within membrane bilayers and lipid-lipid interactions confer membrane properties such as rigidity or detergent resistance.
+### Lipid-Lipid Interactions and Membrane Properties
+Lipids are primarily organized within membrane bilayers, where their interactions define critical membrane properties such as rigidity, fluidity, and resistance to detergents.
+By studying lipid-lipid interactomes, researchers can gain deeper insight into how these physical interactions influence membrane architecture and dynamics.
+Understanding these interactions is essential for unraveling fundamental processes like vesicle trafficking, cell signaling, and membrane compartmentalization.
 
-* In recent decades, many select lipid species have gained recognition for being crucial signaling molecules.
-For one example, the sphingolipid sphingosine-1-phosphate (S1P) is potently recognized by an array of S1P receptors which cause T cells to extravasate and chemotax toward sites of infection.
+### Lipids as Signaling Molecules
+Beyond their structural roles, many lipids have been increasingly recognized as key signaling molecules.
+For example, the sphingolipid sphingosine-1-phosphate (S1P) plays a pivotal role in immune function.
+S1P binds to a specific family of receptors, triggering T cell migration (extravasation) and guiding their movement toward sites of infection.
+This highlights how lipid signaling can have far-reaching effects on cellular behavior and physiological responses.
 
-* Understanding the proteins that a given lipid interacts with can reveal great insight into the wide-ranging cellular signaling effects that a lipid can have.
+### Lipid-Protein Interactions: Unlocking Cellular Communication
 
-## Why are functional modifications necessary in studying lipid interactions?
+A single lipid species can interact with a diverse array of proteins, influencing everything from receptor activation to intracellular signaling cascades.
+Mapping these lipid-protein interactions provides a powerful approach to understanding how lipids exert their wide-ranging effects on cellular processes.
+By deciphering lipid interactomes, researchers can uncover novel regulatory mechanisms and potentially identify new therapeutic targets in diseases where lipid signaling is dysregulated.
+
+## Synthetic Lipid Analogs: Powerful Tools for Lipid Biology
+The study of lipid biology has been greatly advanced by synthetic lipid analogs.
+However, it may not be immediately clear why such analogs are so essential.
+Unlike proteins and nucleic acids, lipids present unique challenges that make traditional genetic tools less effective in studying their function.
+
+### Why Lipids Require a Different Approach
+Advances in genetic engineering—such as CRISPR and de novo gene synthesis—have revolutionized the study of nucleic acids and proteins.
+These techniques allow researchers to introduce precise modifications, such as:
+* Altering enzyme activity by mutating active sites to change substrate specificity.
+* Redirecting proteins by swapping subcellular localization sequences.
+* Modifying protein interactions by swapping or removing binding domains.
+* Visualizing proteins by fusing them with fluorescent tags (e.g., GFP).
+
+Isolating protein complexes by adding affinity handles for purification.
+In contrast, lipids pose distinct challenges that make such genetic manipulations impractical:
+Lipids Are Synthesized Enzymatically
+Unlike proteins, whose sequences are encoded in DNA, lipids are the product of enzymatic pathways.
+Their structures cannot be directly altered within a living system in the same way that gene sequences can be modified.
+Early lipid research relied on gene knockouts and knock-ins to globally alter lipid composition, which provided broad insights into lipid classes but was less effective for studying individual lipid species.
+Lipids Are Small and Structurally Sensitive
+Compared to proteins, which consist of hundreds or thousands of atoms, lipids are much smaller (often composed of just a few dozen atoms).
+Because of their size, even small modifications can dramatically alter their biophysical properties and biological function.
+For example, unlike proteins, lipids cannot be tagged with large fluorescent proteins (e.g., GFP) or classical affinity tags (e.g., HA tags) without completely disrupting their activity.
+Lipids Are Metabolically Dynamic
+Lipids exist within a highly dynamic metabolic network, where they can be rapidly modified, cleaved, or converted into other lipid species.
+Some lipids, like sphingosine, have extremely short half-lives—sometimes only minutes—making them difficult to track and study in real time.
+The Role of Synthetic Lipid Analogs
+To overcome these challenges, researchers have developed synthetic analogs of native lipids.
+These modified lipids allow for precise investigation of lipid function while preserving their essential biological properties.
+The key modifications used in this approach include:
+Diazirine Rings – Enable covalent crosslinking to interacting proteins upon UV activation.
+Terminal Alkynes – Allow for affinity enrichment using click chemistry.
+Coumarin Photocages – Provide spatiotemporal control over lipid activity through light-triggered release.
+These modifications stabilize protein-lipid interactions and enable the selective enrichment of lipid-bound proteins, all while maintaining tight spatial and temporal control.
+Each of these tools is described in further detail below.
 
@@
 
-### Terminal Alkyne
+### Diazirine: A photo-activated crosslinker {#sec-DiazirinePlacement}
 
-* Affinity handle
-* Affix fluorophore post-hoc
-
-### Diazirine: A photo-activated crosslinker {#sec-DiazirinePlacement}
+Lipid interactions are typically highly transient -- few opportunities for
 
@@
 * [@hoglingerTrifunctionalLipidProbes2017]
+
+### Terminal Alkyne
+
+* Affinity handle
+* Affix fluorophore post-hoc
 
@@
 
-#### Spectral counting
+#### Label-Free Quantification
+Label-free quantification (LFQ) is a widely used approach in mass spectrometry-based proteomics that estimates protein abundance without the need for chemical labeling.
+Instead, it relies on comparing the summed intensity of detected peptides across different samples analyzed under identical conditions.
 
-#### Isobaric mass tagging
+##### How It Works
+MS1 (Peptide Detection): Peptides are first isolated and detected based on their mass-to-charge ratio (m/z).
+MS2 (Peptide Sequencing): Selected peptide ions are fragmented, and the resulting spectra are used to determine peptide sequences.
+Quantification: The total signal intensity of all identified peptides corresponding to a given protein is summed, serving as a proxy for the protein’s absolute abundance.
+Comparison Across Samples: When two or more samples are prepared and analyzed using the same LC-MS/MS protocol, their relative protein abundances can be compared.
 
-\br
+##### Advantages of Label-Free Quantification
+* *Cost-Effective & Simple Sample Preparation*
+  * Unlike labeling methods (e.g., TMT), LFQ does not require expensive reagents or complex chemical modifications.
+  * Sample preparation is straightforward, making LFQ accessible to a wide range of researchers.
+* *Widely Used & Flexible*
+  * LFQ is a common approach in proteomics, compatible with various experimental designs.
+  * It allows for comparisons across a large number of samples without being limited by multiplexing constraints.
 
-(Here's an example of what references would look like on the site: [@thomasTrifunctionalLipidDerivatives2025; @schultzFlashClickMultifunctionalized2022a; @schultzChemicalToolsLipid2023])
+##### Challenges & Considerations
+* *Potential Bias from Co-Elution:*
+  * In complex samples, high-abundance peptides can overshadow low-abundance peptides, limiting the number of peptides that can be reliably isolated and quantified in the MS1 scan.
+* *Run-to-Run Variability:*
+  * Unlike TMT-based methods, where all samples are analyzed together in a single run, LFQ requires separate MS runs for each sample.
+* Differences in instrument calibration, chromatography conditions, or sample preparation can introduce variability, potentially leading to artificial differences between samples if not carefully controlled.
+
+##### Conclusion
+Label-free quantification is a practical and widely used approach for proteomics research, offering a cost-effective and simple method for estimating protein abundance.
+However, careful experimental design and quality control are essential to minimize variability and ensure reliable quantification across different runs.
+
+#### Quantitative Mass Spectrometry with Tandem Mass Tagging {#sec-TMT}
+
+Tandem Mass Tag (TMT) labeling is a powerful technique in quantitative mass spectrometry (MS) that allows for the simultaneous analysis of multiple samples in a single MS run.
+This method enhances efficiency and enables precise relative quantification of proteins across different experimental conditions.
+
+##### How It Works
+
+* **Chemical Labeling**: Each peptide in a sample is chemically tagged with a unique TMT label, which consists of an identical reactive group that binds to peptides and a mass reporter region that differentiates samples.
+
+* **Sample Pooling:** Once labeled, samples are combined into a single pooled sample group, reducing the need for separate MS runs.
+
+* **Mass Spectrometry Analysis:** 
+  * *MS1 (Peptide Isolation):* Peptides are first separated and detected based on their mass-to-charge ratio (m/z). 
+  * *MS2 (Peptide Sequencing & Tag Fragmentation):* Peptides are fragmented, allowing for sequence identification. At the same time, the mass tags also fragment, producing unique reporter ions. 
+  * *Quantification:* The intensity of these reporter ions reveals the relative abundance of each peptide across the original samples.
+
+##### Advantages of TMT Labeling
+* Increased Throughput & Efficiency
+TMT allows for the multiplexing of many samples (e.g., 16 or more), reducing the number of separate MS runs needed.
+Instead of running 16 individual samples separately, they can be pooled and analyzed together, increasing experimental efficiency.
+* Deeper Proteome Coverage
+The pooled sample can be further fractionated (e.g., using cation exchange chromatography), which helps separate high-abundance and low-abundance peptides before MS analysis.
+This results in greater depth of peptide detection compared to running multiple low-depth, individual label-free MS analyses.
+* Improved Quantification Accuracy
+Since all samples are analyzed together in the same MS run, technical variability between runs is minimized, leading to more accurate relative quantification.
+
+##### Challenges & Considerations
+* Higher Cost
+TMT reagents and the need for higher-end mass spectrometers contribute to increased costs.
+* Complex Sample Preparation
+Additional steps are required for labeling, pooling, and fractionation, which increases the risk of sample handling variability.
+* Normalization Requirement
+Total protein input must be carefully controlled to ensure accurate quantification.
+Unequal sample amounts (e.g., when comparing conditions with highly different protein yields) may require artificial balancing, which can introduce biases.
+* Demanding Instrumentation & Expertise
+The technique requires high-resolution mass spectrometers with precise scanning capabilities, often necessitating outsourcing to specialized facilities.
+
+##### Conclusion
+TMT-based quantitative mass spectrometry is a valuable tool for large-scale proteomics studies, providing high-throughput, precise, and deep proteome coverage.
+While it requires careful sample preparation and advanced instrumentation, its ability to multiplex multiple samples in a single run makes it an attractive option for researchers aiming for high-confidence protein quantification.

### 2025-01-30 LipidProbe/DataSets/LipidInteractomics_ShinyApp/app.R

@@ -4,6 +4,7 @@ library(ggplot2)
 library(plotly)
 library(readr)
 library(shiny)
+library(amVennDiagram5)
 
 df <- read_csv("combinedProbeDatasets_TMT.csv")
 

### 2025-01-30 LipidProbe/DataSets/LipidInteractomics_VennDiagramsApp/app.R

@@ -1,0 +1,71 @@
+library(dplyr)
+library(tidyr)
+library(ggplot2)
+library(plotly)
+library(readr)
+library(shiny)
+library(amVennDiagram5)
+library(ggVennDiagram)
+library(VennDiagram)
+library(ggvenn)
+
+Venn_df <- read_csv("/Users/gaelenguzman/LipidInteractomics_Website_local/LipidInteractomics_Website/LipidProbe/DataSets/LipidInteractomics_VennDiagramsApp/combinedProbeDatasets_VennDiagram.csv")
+
+probeOptions <- unique(Venn_df$LipidProbe)
+
+# Shiny App
+ui <- fluidPage(
+  titlePanel("Interactive Venn Diagrams"),
+  
+  sidebarLayout(
+    sidebarPanel(
+      selectInput("probe1", "Select First Lipid Probe:", choices = probeOptions, selected = probeOptions[1]),
+      selectInput("probe2", "Select Second Lipid Probe:", choices = probeOptions, selected = probeOptions[2]),
+			fluidRow(actionButton(inputId = "PlotVenn", label = "Plot Venn Diagram")
+			)
+    ),
+    mainPanel(
+      plotOutput("VennDiagram")
+    )
+  )
+)
+
+
+server <- function(input, output, session) {
+	Probe1Data <- reactive({
+		Probe1Data <- Venn_df |>
+			filter(LipidProbe == input$probe1)
+		
+		return(Probe1Data)
+	})
+
+
+	Probe2Data <- reactive({
+		Probe2Data <- Venn_df |>
+			filter(LipidProbe == input$probe2)
+		
+		return(Probe2Data)
+	})	
+
+	observeEvent(input$PlotVenn, {
+		Probe1Data <- Probe1Data()
+		Probe2Data <- Probe2Data()
+
+		data <- list(Probe1 = Probe1Data$gene_name, 
+						 Probe2 = Probe2Data$gene_name)
+
+		renderPlot({
+			vennTest<- ggvenn(data,
+				fill_color = c("#0073C2FF", "#EFC000FF"),
+				stroke_size = 0.5,
+				set_name_size = 2)
+
+			vennTest + coord_cartesian(clip="off")
+			#ggplotly(vennTest)
+		})
+	})
+
+}
+
+
+shinyApp(ui, server)

### 2025-01-30 IndividualStudies/AT_2025.qmd
updating with includes structure

--- 2025-01-16 IndividualStudies/AT_2025.qmd
@@
 
-## Study details
+{{< include /StudyInformation_includes/AT_2025_include.qmd >}}
 
-#### Authors
-Alix Thomas, Rainer Mueller, Ana Kojic, Scotland E. Farley, Frank Stein, Per Haberkant, Carsten Schultz
-
-#### Journal
-Chemical Communications
-
-<https://doi.org/10.1039/D4CC03599B>{target="_blank"}
-
-#### Abstract
-Phosphatidylethanolamine (PE) is a ubiquitous lipid species in higher eukaryotes which resides preferentially in mitochondria.
-Here, we synthesized a multifunctionalized PE derivative (1) de-signed to identify PE-binding proteins in intact cells through photo-crosslinking and subsequent isolation and proteomic analysis of the PE-protein conjugates.
-Due to its aromatic caging group, 1 is initially concentrating in perinuclear membranes.
-After uncaging, rapid translocation to mitochondria was observed.
-Hence, the tool is useful for tracking PE location and for determining the PE interactome.
-A trifunctional phosphatidic acid (PA) derivative in compari-son was rapidly metabolized and is hence more limited in its use.
-
-#### Lipid probes utilized
-
-#### Cell line analyzed
-
-[HeLa](https://www.atcc.org/products/ccl-2){target="_blank"}
-
-#### Mass spectrometry quantification method
-
-16-channel Tandem Mass Tagging (TMT16)
-
-#### Additional sample preparation <span class="help-symbol" title="e.g. sub-cellular fractionation, depletion, etc.">?</span>
 :::

### 2025-01-30 IndividualStudies/DH_2017.qmd
updating with includes structure

@@
 
-## Study details
-
-#### Authors
-
-Doris Höglinger, André Nadler,  Per Haberkant, Joanna Kirkpatrick, Martina Schifferer, Frank Stein, Sebastian Hauke, Forbes D. Porter, Carsten Schultz
-
-#### Journal
-
-PNAS
-
-<https://doi.org/10.1073/pnas.1611096114>{target="_blank"}
-
-#### Abstract
-
-Lipid-mediated signaling events regulate many cellular processes.
-Investigations of the complex underlying mechanisms are difficult because several different methods need to be used under varying conditions.
-Here we introduce multifunctional lipid derivatives to study lipid metabolism, lipid−protein interactions, and intracellular lipid localization with a single tool per target lipid.
-The probes are equipped with two photoreactive groups to allow photoliberation (uncaging) and photo–cross-linking in a sequential manner, as well as a click-handle for subsequent functionalization.
-We demonstrate the versatility of the design for the signaling lipids sphingosine and diacylglycerol; uncaging of the probe for these two species triggered calcium signaling and intracellular protein translocation events, respectively.
-We performed proteomic screens to map the lipid-interacting proteome for both lipids.
-Finally, we visualized a sphingosine transport deficiency in patient-derived Niemann−Pick disease type C fibroblasts by fluorescence as well as correlative light and electron microscopy, pointing toward the diagnostic potential of such tools.
-We envision that this type of probe will become important for analyzing and ultimately understanding lipid signaling events in a comprehensive manner.
-
-#### Lipid probes utilized
-
-Sphinganine
-
-Diacylglycerol
-
-8-3 Fatty acid
-
-#### Cell line analyzed
-
-[HeLa](https://www.atcc.org/products/ccl-2){target="_blank"}
-
-#### Mass spectrometry quantification method
-
-Peptide spectral counting
+{{< include /StudyInformation_includes/DH_2017_include.qmd >}}
 

### 2025-01-30 IndividualStudies/RM_2021.qmd
updating with includes structure

@@
 
-## Study details
+{{< include /StudyInformation_includes/RM_2021_include.qmd >}}
 
-#### Authors
-Rainer Muller, Ana Kojic, Mevlut Citir, Carsten Schultz
-
-#### Journal
-Angewandte Chemie
-
-<https://doi.org/10.1002/anie.202103599>{target="_blank"}
-
-#### Abstract
-
-We synthesized the first multifunctionalized phosphoinositide polyphosphate derivatives featuring a photo-removable protecting group (“cage”), a photo-crosslinkable diazirine group, and a terminal alkyne group useful for click chemistry.
-We demonstrate that the lipid derivatives readily enter cells.
-After photo-crosslinking, cell fixation and fluorescent tagging via click chemistry, we determined the intracellular location of the lipid derivatives before and after uncaging of the lipids.
-We find that there is rapid trafficking of PI(3,4)P2 and PI(3,4,5)P3 derivatives to the plasma membrane, opening the intriguing possibility that there is active transport of these lipids involved.
-We employed the photo-crosslinking and click chemistry functions to analyze the proteome of PI(3,4,5)P3-binding proteins.
-From the latter, we validated by RNAi that the putative lipid binding proteins ATP11A and MPP6 are involved in the transport of PI(3,4,5)P3 to the plasma membrane.
-
-#### Lipid probes utilized
-
-[PI(3,4,5)P~3~](/LipidProbe/PhosphatidylinositolTrisphosphate.qmd)
-
-#### Cell line analyzed
-
-[HeLa](https://www.atcc.org/products/ccl-2){target="_blank"}
-
-#### Mass spectrometry quantification method
-
-Peptide spectral counting
-
-#### Additional sample preparation <span class="help-symbol" title="e.g. sub-cellular fractionation, depletion, etc.">?</span>
 :::

### 2025-01-30 IndividualStudies/SF_2024.qmd
updating with includes structure

@@
 
-## Study details
+{{< include /StudyInformation_includes/SF_2024_A_include.qmd >}}
 
-#### Authors
-Scotland E. Farley, Frank Stein, Per Haberkant, Fikadu G. Tafesse, Carsten Schultz
-
-#### Journal
-ACS Chemical Biology
-
-<https://doi.org/10.1021/acschembio.3c00554>{target="_blank"}
-
-#### Abstract
-
-Functions of the sphingolipids sphingosine and sphinganine in cells are not well established.
-While some signaling roles for sphingosine have been elucidated, the closely related sphinganine has been described only insofar as it does not elicit many of the same signaling responses.
-The underlying mechanisms behind the cell biological differences between these lipids are not well understood.
-Here, we prepared multifunctionalized derivatives of the two lipid species that only differ in a single double bond of the carbon backbone.
-Using these novel probes, we were able to define their spatiotemporal distribution within cells.
-Furthermore, we used these tools to systematically map the protein interactomes of both lipids.
-The lipid-protein conjugates, prepared through photo-crosslinking in live cells and extraction via click chemistry to azide beads, revealed significant differences in the captured proteins, highlighting their distinct roles in various cellular processes.
-This work elucidates mechanistic differences between these critical lipids and sets the foundation for further studies on the functions of sphingosine and sphinganine.
-
-#### Lipid probes utilized
-
-#### Cell line analyzed
-
-[Huh7](https://huh7.com){target="_blank"}
-
-#### Mass spectrometry quantification method
-
-16-channel Tandem Mass Tagging (TMT16)
-
-#### Additional sample preparation <span class="help-symbol" title="e.g. sub-cellular fractionation, depletion, etc.">?</span>
 :::

### 2025-01-30 LipidProbe/1-10_FattyAcid.qmd
fleshing out overview
updating with includes structure

@@
 title: "Trifunctional 1-10 Fatty Acid"
+crossref: 
+  ref-hyperlink: true # (default is true)
 ---
@@
 
+*Greater context to the distinction between the 8-3 Fatty Acid and 1-10 Fatty Acid probes in the [Diazirine Overview](/TrifunctionalLipidProbesOverview.qmd#sec-DiazirinePlacement)*
+
 ## Protein interactome
@@
 
-#### Study details
+{{< include /StudyInformation_includes/SF_2024_B_include.qmd >}}
 
-##### Authors
-Scotland E. Farley, Frank Stein, Per Haberkant, Fikadu G. Tafesse, Carsten Schultz
-
-##### Journal
-ACS Chemical Biology
-
-<https://doi.org/10.1021/acschembio.3c00554>{target="_blank"}
-
-##### Abstract
-
-Functions of the sphingolipids sphingosine and sphinganine in cells are not well established.
-While some signaling roles for sphingosine have been elucidated, the closely related sphinganine has been described only insofar as it does not elicit many of the same signaling responses.
-The underlying mechanisms behind the cell biological differences between these lipids are not well understood.
-Here, we prepared multifunctionalized derivatives of the two lipid species that only differ in a single double bond of the carbon backbone.
-Using these novel probes, we were able to define their spatiotemporal distribution within cells.
-Furthermore, we used these tools to systematically map the protein interactomes of both lipids.
-The lipid-protein conjugates, prepared through photo-crosslinking in live cells and extraction via click chemistry to azide beads, revealed significant differences in the captured proteins, highlighting their distinct roles in various cellular processes.
-This work elucidates mechanistic differences between these critical lipids and sets the foundation for further studies on the functions of sphingosine and sphinganine.
-
-##### Lipid probes utilized
-
-1-10 Fatty acid
-
-8-3 Fatty acid
-
-##### Cell line analyzed
-
-[Huh7](https://huh7.com){target="_blank"}
-
-##### Mass spectrometry quantification method
-
-16-channel Tandem Mass Tagging (TMT16)
-
-##### Additional sample preparation <span class="help-symbol" title="e.g. sub-cellular fractionation, depletion, etc.">?</span>
 :::

### 2025-01-30 LipidProbe/8-3_FattyAcid.qmd
updating with includes structure

@@
 
-#### Study details
+{{< include /StudyInformation_includes/SF_2024_A_include.qmd >}}
 
-##### Authors
-Scotland E. Farley, Frank Stein, Per Haberkant, Fikadu G. Tafesse, Carsten Schultz
-
-##### Journal
-ACS Chemical Biology
-
-<https://doi.org/10.1021/acschembio.3c00554>{target="_blank"}
-
-##### Abstract
-
-Functions of the sphingolipids sphingosine and sphinganine in cells are not well established.
-While some signaling roles for sphingosine have been elucidated, the closely related sphinganine has been described only insofar as it does not elicit many of the same signaling responses.
-The underlying mechanisms behind the cell biological differences between these lipids are not well understood.
-Here, we prepared multifunctionalized derivatives of the two lipid species that only differ in a single double bond of the carbon backbone.
-Using these novel probes, we were able to define their spatiotemporal distribution within cells.
-Furthermore, we used these tools to systematically map the protein interactomes of both lipids.
-The lipid-protein conjugates, prepared through photo-crosslinking in live cells and extraction via click chemistry to azide beads, revealed significant differences in the captured proteins, highlighting their distinct roles in various cellular processes.
-This work elucidates mechanistic differences between these critical lipids and sets the foundation for further studies on the functions of sphingosine and sphinganine.
-
-##### Lipid probes utilized
-
-1-10 Fatty acid
-
-8-3 Fatty acid
-
-##### Cell line analyzed
-
-[Huh7](https://huh7.com){target="_blank"}
-
-##### Mass spectrometry quantification method
-
-16-channel Tandem Mass Tagging (TMT16)
-
-##### Additional sample preparation <span class="help-symbol" title="e.g. sub-cellular fractionation, depletion, etc.">?</span>
 :::
@@
 
-#### Study details
-
-##### Authors
-
-Doris Höglinger, André Nadler,  Per Haberkant, Joanna Kirkpatrick, Martina Schifferer, Frank Stein, Sebastian Hauke, Forbes D. Porter, Carsten Schultz
-
-##### Journal
-
-PNAS
-
-<https://doi.org/10.1073/pnas.1611096114>{target="_blank"}
-
-##### Abstract
-
-Lipid-mediated signaling events regulate many cellular processes.
-Investigations of the complex underlying mechanisms are difficult because several different methods need to be used under varying conditions.
-Here we introduce multifunctional lipid derivatives to study lipid metabolism, lipid−protein interactions, and intracellular lipid localization with a single tool per target lipid.
-The probes are equipped with two photoreactive groups to allow photoliberation (uncaging) and photo–cross-linking in a sequential manner, as well as a click-handle for subsequent functionalization.
-We demonstrate the versatility of the design for the signaling lipids sphingosine and diacylglycerol; uncaging of the probe for these two species triggered calcium signaling and intracellular protein translocation events, respectively.
-We performed proteomic screens to map the lipid-interacting proteome for both lipids.
-Finally, we visualized a sphingosine transport deficiency in patient-derived Niemann−Pick disease type C fibroblasts by fluorescence as well as correlative light and electron microscopy, pointing toward the diagnostic potential of such tools.
-We envision that this type of probe will become important for analyzing and ultimately understanding lipid signaling events in a comprehensive manner.
-
-##### Lipid probes utilized
-
-Sphinganine
-
-Diacylglycerol
-
-8-3 Fatty acid
-
-##### Cell line analyzed
-
-[HeLa](https://www.atcc.org/products/ccl-2){target="_blank"}
-
-##### Mass spectrometry quantification method
-
-Peptide spectral counting
+{{< include /StudyInformation_includes/DH_2017_include.qmd >}}
 

### 2025-01-30 LipidProbe/PhosphatidicAcid.qmd
updating with includes structure

--- 2025-01-17 LipidProbe/PhosphatidicAcid.qmd
@@
 
-#### Study details
+{{< include /StudyInformation_includes/AT_2025_include.qmd >}}
 
-##### Authors
-Alix Thomas, Rainer Mueller, Ana Kojic, Scotland E. Farley, Frank Stein, Per Haberkant, Carsten Schultz
-
-##### Journal
-Chemical Communications
-
-<https://doi.org/10.1039/D4CC03599B>{target="_blank"}
-
-##### Abstract
-Phosphatidylethanolamine (PE) is a ubiquitous lipid species in higher eukaryotes which resides preferentially in mitochondria.
-Here, we synthesized a multifunctionalized PE derivative (1) de-signed to identify PE-binding proteins in intact cells through photo-crosslinking and subsequent isolation and proteomic analysis of the PE-protein conjugates.
-Due to its aromatic caging group, 1 is initially concentrating in perinuclear membranes.
-After uncaging, rapid translocation to mitochondria was observed.
-Hence, the tool is useful for tracking PE location and for determining the PE interactome.
-A trifunctional phosphatidic acid (PA) derivative in compari-son was rapidly metabolized and is hence more limited in its use.
-
-##### Lipid probes utilized
-
-##### Cell line analyzed
-
-[HeLa](https://www.atcc.org/products/ccl-2){target="_blank"}
-
-##### Mass spectrometry quantification method
-
-16-channel Tandem Mass Tagging (TMT16)
-
-##### Additional sample preparation <span class="help-symbol" title="e.g. sub-cellular fractionation, depletion, etc.">?</span>
 :::

### 2025-01-30 LipidProbe/Sphinganine.qmd
updating with includes structure

@@
 
-#### Study details
+{{< include /StudyInformation_includes/SF_2024_A_include.qmd >}}
 
-##### Authors
-Scotland E. Farley, Frank Stein, Per Haberkant, Fikadu G. Tafesse, Carsten Schultz
-
-##### Journal
-ACS Chemical Biology
-
-<https://doi.org/10.1021/acschembio.3c00554>{target="_blank"}
-
-##### Abstract
-
-Functions of the sphingolipids sphingosine and sphinganine in cells are not well established.
-While some signaling roles for sphingosine have been elucidated, the closely related sphinganine has been described only insofar as it does not elicit many of the same signaling responses.
-The underlying mechanisms behind the cell biological differences between these lipids are not well understood.
-Here, we prepared multifunctionalized derivatives of the two lipid species that only differ in a single double bond of the carbon backbone.
-Using these novel probes, we were able to define their spatiotemporal distribution within cells.
-Furthermore, we used these tools to systematically map the protein interactomes of both lipids.
-The lipid-protein conjugates, prepared through photo-crosslinking in live cells and extraction via click chemistry to azide beads, revealed significant differences in the captured proteins, highlighting their distinct roles in various cellular processes.
-This work elucidates mechanistic differences between these critical lipids and sets the foundation for further studies on the functions of sphingosine and sphinganine.
-
-##### Lipid probes utilized
-
-##### Cell line analyzed
-
-[Huh7](https://huh7.com){target="_blank"}
-
-##### Mass spectrometry quantification method
-
-16-channel Tandem Mass Tagging (TMT16)
-
-##### Additional sample preparation <span class="help-symbol" title="e.g. sub-cellular fractionation, depletion, etc.">?</span>
 :::

### 2025-01-30 StudyInformation_includes/AT_2025_include.qmd
updating with includes structure

## Study details

#### Authors
Alix Thomas, Rainer Mueller, Ana Kojic, Scotland E. Farley, Frank Stein, Per Haberkant, Carsten Schultz

#### Journal
Chemical Communications

<https://doi.org/10.1039/D4CC03599B>{target="_blank"}

#### Abstract
Phosphatidylethanolamine (PE) is a ubiquitous lipid species in higher eukaryotes which resides preferentially in mitochondria. Here, we synthesized a multifunctionalized PE derivative (1) de-signed to identify PE-binding proteins in intact cells through photo-crosslinking and subsequent isolation and proteomic analysis of the PE-protein conjugates. Due to its aromatic caging group, 1 is initially concentrating in perinuclear membranes. After uncaging, rapid translocation to mitochondria was observed. Hence, the tool is useful for tracking PE location and for determining the PE interactome. A trifunctional phosphatidic acid (PA) derivative in compari-son was rapidly metabolized and is hence more limited in its use.

#### Lipid probes utilized

<a href="/LipidProbe/PhosphatidicAcid.qmd" class="hover-preview">Phosphatidic Acid</a>
<span class="hover-image">
  <img src="/LipidProbe/Structures/PhosphatidicAcid_Structure.png" alt="Phosphatidic Acid" />
</span>

<a href="/LipidProbe/Phosphatidylethanolamine.qmd" class="hover-preview">Phosphatidic Acid</a>
<span class="hover-image">
  <img src="/LipidProbe/Structures/PhosphatidylethanolamineStructure.png" alt="Phosphatidic Acid" />
</span>

#### Cell line analyzed

[HeLa](https://www.atcc.org/products/ccl-2){target="_blank"}

#### Mass spectrometry quantification method

16-channel Tandem Mass Tagging (TMT16)

::: {.callout-note collapse="true"}
##### ProteomeXchange details

**ProteomeXchange title:** Trifunctional lipid derivatives: PE’s mi-tochondrial interactome

**ProteomeXchange accession:** PXD059960

**PubMed ID:** Not applicable

**Publication DOI:** 10.1039/D4CC03599B

**Project Webpage:** http://www.ebi.ac.uk/pride/archive/projects/PXD059960

**FTP Download:** https://ftp.pride.ebi.ac.uk/pride/data/archive/2025/01/PXD059960
:::

#### Additional sample preparation <span class="help-symbol" title="e.g. sub-cellular fractionation, depletion, etc.">?</span>

### 2025-01-30 StudyInformation_includes/DH_2017_include.qmd
updating with includes structure

## Study details

#### Authors

Doris Höglinger, André Nadler,  Per Haberkant, Joanna Kirkpatrick, Martina Schifferer, Frank Stein, Sebastian Hauke, Forbes D. Porter, Carsten Schultz

#### Journal

PNAS

<https://doi.org/10.1073/pnas.1611096114>{target="_blank"}

#### Abstract

Lipid-mediated signaling events regulate many cellular processes. Investigations of the complex underlying mechanisms are difficult because several different methods need to be used under varying conditions. Here we introduce multifunctional lipid derivatives to study lipid metabolism, lipid−protein interactions, and intracellular lipid localization with a single tool per target lipid. The probes are equipped with two photoreactive groups to allow photoliberation (uncaging) and photo–cross-linking in a sequential manner, as well as a click-handle for subsequent functionalization. We demonstrate the versatility of the design for the signaling lipids sphingosine and diacylglycerol; uncaging of the probe for these two species triggered calcium signaling and intracellular protein translocation events, respectively. We performed proteomic screens to map the lipid-interacting proteome for both lipids. Finally, we visualized a sphingosine transport deficiency in patient-derived Niemann−Pick disease type C fibroblasts by fluorescence as well as correlative light and electron microscopy, pointing toward the diagnostic potential of such tools. We envision that this type of probe will become important for analyzing and ultimately understanding lipid signaling events in a comprehensive manner.

#### Lipid probes utilized

[Sphingosine](/LipidProbe/Sphingosine.qmd)

[Diacylglycerol](/LipidProbe/Diacylglycerol.qmd)

[8-3 Fatty acid](/LipidProbe/8-3_FattyAcid.qmd)

#### Cell line analyzed

[HeLa](https://www.atcc.org/products/ccl-2){target="_blank"}

#### Mass spectrometry quantification method

Peptide spectral counting

### 2025-01-30 StudyInformation_includes/RM_2021_include.qmd
updating with includes structure

## Study details

#### Authors
Rainer Muller, Ana Kojic, Mevlut Citir, Carsten Schultz

#### Journal
Angewandte Chemie

<https://doi.org/10.1002/anie.202103599>{target="_blank"}

#### Abstract

We synthesized the first multifunctionalized phosphoinositide polyphosphate derivatives featuring a photo-removable protecting group (“cage”), a photo-crosslinkable diazirine group, and a terminal alkyne group useful for click chemistry. We demonstrate that the lipid derivatives readily enter cells. After photo-crosslinking, cell fixation and fluorescent tagging via click chemistry, we determined the intracellular location of the lipid derivatives before and after uncaging of the lipids. We find that there is rapid trafficking of PI(3,4)P2 and PI(3,4,5)P3 derivatives to the plasma membrane, opening the intriguing possibility that there is active transport of these lipids involved. We employed the photo-crosslinking and click chemistry functions to analyze the proteome of PI(3,4,5)P3-binding proteins. From the latter, we validated by RNAi that the putative lipid binding proteins ATP11A and MPP6 are involved in the transport of PI(3,4,5)P3 to the plasma membrane.

#### Lipid probes utilized

[PI(3,4,5)P~3~](/LipidProbe/PhosphatidylinositolTrisphosphate.qmd)

#### Cell line analyzed

[HeLa](https://www.atcc.org/products/ccl-2){target="_blank"}

#### Mass spectrometry quantification method

Peptide spectral counting

#### Additional sample preparation <span class="help-symbol" title="e.g. sub-cellular fractionation, depletion, etc.">?</span>

### 2025-01-30 StudyInformation_includes/SF_2024_A_include.qmd
updating with includes structure

--- 2025-01-10 SF_2024.qmd
@@
----
-title: "Farley et al. 2024"
-format: 
-  html:
-    embed-resources: true
-standalone: true
----
+## Study details
 
-```{r setup, echo=FALSE, include=FALSE}
+#### Authors
+Scotland E. Farley, Frank Stein, Per Haberkant, Fikadu G. Tafesse, Carsten Schultz
 
-## Publication information
+#### Journal
+ACS Chemical Biology
 
-**Title:** Trifunctional Sphinganine: A New Tool to Dissect Sphingolipid Function
+<https://doi.org/10.1021/acschembio.3c00554>{target="_blank"}
 
-**Authors:** Scotland E. Farley, Frank Stein, Per Haberkant, Fikadu G. Tafesse, Carsten Schultz*
-
-(* corresponding: <schulcar@ohsu.edu>{target="_blank"})
-
-**Date published:**
-
-**Journal, ISSN:** [ACS Chemical Biology](https://pubs.acs.org/doi/10.1021/acschembio.3c00554){target="_blank"}, 1554-8929, 1554-8937
-
-**DOI:** <https://doi.org/10.1021/acschembio.3c00554>{target="_blank"}
-
-## Abstract
+#### Abstract
 
@@
 
-## Data visualization
+#### Lipid probes utilized
 
-#### Ranked-order Log2 Fold-change plots
+#### Cell line analyzed
 
-#### Volcano plots
+[Huh7](https://huh7.com){target="_blank"}
 
-## Enriched Proteins
+#### Mass spectrometry quantification method
+
+16-channel Tandem Mass Tagging (TMT16)
+
+#### Additional sample preparation <span class="help-symbol" title="e.g. sub-cellular fractionation, depletion, etc.">?</span>

### 2025-01-30 TrifunctionalLipidProbesOverview.qmd
updating with includes structure

@@
 Every biological process—from metabolism to signaling—depends on the physical interactions between molecules, including proteins, nucleic acids, and lipids.
-While proteins have long been the primary focus of interaction studies, lipids play an equally crucial yet often underappreciated role in cellular function.
+While proteins have long been the primary focus of interaction studies, lipids play an equally crucial yet often under-appreciated role in cellular function.
 
 ### Lipid-Lipid Interactions and Membrane Properties
+
 Lipids are primarily organized within membrane bilayers, where their interactions define critical membrane properties such as rigidity, fluidity, and resistance to detergents.
@@
 ### Lipids as Signaling Molecules
+
 Beyond their structural roles, many lipids have been increasingly recognized as key signaling molecules.
@@
 ## Synthetic Lipid Analogs: Powerful Tools for Lipid Biology
+
 The study of lipid biology has been greatly advanced by synthetic lipid analogs.
@@
 ### Why Lipids Require a Different Approach
+
 Advances in genetic engineering—such as CRISPR and de novo gene synthesis—have revolutionized the study of nucleic acids and proteins.
 These techniques allow researchers to introduce precise modifications, such as:
-* Altering enzyme activity by mutating active sites to change substrate specificity.
-* Redirecting proteins by swapping subcellular localization sequences.
-* Modifying protein interactions by swapping or removing binding domains.
-* Visualizing proteins by fusing them with fluorescent tags (e.g., GFP).
 
-Isolating protein complexes by adding affinity handles for purification.
+-   Altering enzyme activity by mutating active sites to change substrate specificity.
+-   Redirecting proteins by swapping subcellular localization sequences.
+-   Modifying protein interactions by swapping or removing binding domains.
+-   Visualizing proteins by fusing them with fluorescent tags (e.g., GFP).
+-   Isolating protein complexes by adding affinity handles for purification.
+
 In contrast, lipids pose distinct challenges that make such genetic manipulations impractical:
-Lipids Are Synthesized Enzymatically
-Unlike proteins, whose sequences are encoded in DNA, lipids are the product of enzymatic pathways.
+
+1.  Lipids Are Synthesized Enzymatically
+    -   Unlike proteins, whose sequences are encoded in DNA, lipids are the product of enzymatic pathways.
 Their structures cannot be directly altered within a living system in the same way that gene sequences can be modified.
-Early lipid research relied on gene knockouts and knock-ins to globally alter lipid composition, which provided broad insights into lipid classes but was less effective for studying individual lipid species.
-Lipids Are Small and Structurally Sensitive
-Compared to proteins, which consist of hundreds or thousands of atoms, lipids are much smaller (often composed of just a few dozen atoms).
-Because of their size, even small modifications can dramatically alter their biophysical properties and biological function.
-For example, unlike proteins, lipids cannot be tagged with large fluorescent proteins (e.g., GFP) or classical affinity tags (e.g., HA tags) without completely disrupting their activity.
-Lipids Are Metabolically Dynamic
-Lipids exist within a highly dynamic metabolic network, where they can be rapidly modified, cleaved, or converted into other lipid species.
-Some lipids, like sphingosine, have extremely short half-lives—sometimes only minutes—making them difficult to track and study in real time.
-The Role of Synthetic Lipid Analogs
+    -   Early lipid research relied on gene knockouts and knock-ins to globally alter lipid composition, which provided broad insights into lipid classes but was less effective for studying individual lipid species.
+2.  Lipids Are Small and Structurally Sensitive
+    -   Compared to proteins, which consist of hundreds or thousands of atoms, lipids are much smaller (often composed of just a few dozen atoms).
+    -   Because of their size, even small modifications can dramatically alter their biophysical properties and biological function.
+    -   For example, unlike proteins, lipids cannot be tagged with large fluorescent proteins (e.g., GFP) or classical affinity tags (e.g., HA tags) without completely disrupting their activity.
+3.  Lipids Are Metabolically Dynamic
+    -   Lipids exist within a highly dynamic metabolic network, where they can be rapidly modified, cleaved, or converted into other lipid species.
+    -   Some lipids, like sphingosine, have extremely short half-lives—sometimes only minutes—making them difficult to track and study in real time.
+
+### The Role of Synthetic Lipid Analogs
+
 To overcome these challenges, researchers have developed synthetic analogs of native lipids.
@@
 The key modifications used in this approach include:
-Diazirine Rings – Enable covalent crosslinking to interacting proteins upon UV activation.
-Terminal Alkynes – Allow for affinity enrichment using click chemistry.
-Coumarin Photocages – Provide spatiotemporal control over lipid activity through light-triggered release.
+
+1.  Diazirine Rings – Enable covalent crosslinking to interacting proteins upon UV activation.
+2.  Terminal Alkynes – Allow for affinity enrichment using click chemistry.
+3.  Coumarin Photocages – Provide spatiotemporal control over lipid activity through light-triggered release.
+
 These modifications stabilize protein-lipid interactions and enable the selective enrichment of lipid-bound proteins, all while maintaining tight spatial and temporal control.
 Each of these tools is described in further detail below.
-
-Synthetic lipid analogs have greatly enabled the exploration of lipid biology. However, it may not be obvious why such analogs are such valuable tools.
-
-While, genetic editing has enabled vast advances in the study of nucleic acids and proteins, there has been no obvious parallel for studying lipids.
-Using CRISPR or *de novo* gene synthesis, one can subtly alter a sequence to enable visualization and pulldown without greatly affecting the structure or function of the target gene.
-To name a few examples, one can: mutate the active site of a protein to change substrate specificity, swap in a different subcellular localization sequence to translocate the target protein to a different organelle, swap domains to alter protein::protein binding, fuse the target protein to any number of fluorescent domains to visualize a protein's localization, or add an affinity handle to enable the enrichment of the target protein and any other protein interactors [@schultzChemicalToolsLipid2023].
-
-Lipids, however, are an entirely different story altogether.
-Foremost of these differences is that lipids are the product of enzymatic synthesis and thus their structure cannot be directly modified within a living biological system.
-For much of the history of lipid research, studies utilized whole gene knockout or knock-in paradigms to alter the global lipid composition of the cell.
-Through these methods, we know much about the localization and broad behavior of lipid classes -- but the biological roles of select lipid species are historically challenging to explore [REF].
-
-Further, lipids are significantly smaller than even the smallest protein -- composed of dozens of atoms, as opposed to hundreds or thousands -- and, thus, their biophysical properties are much more sensitive to modification.
-It is nearly impossible to fuse a lipid with a fluorescent protein (such as GFP) or classical affinity handle (such as an HA tag) without drastically affecting the biological activity of the lipid [REF].
-
-Finally, each of the tens of thousands of distinct lipid structures is a part of a rapidly shifting metabolic network: any given lipid can be cleaved, modified, or converted into other lipid species within short time frames.
-Some lipids, such as sphingosine have half-lives in the minutes [REF].
-
-For these reasons, synthetic analogs to native lipids have been a great utility toward probing the biological function of select lipid species.
-The chief modifications described in this repository (highlighted in the figure below) are:
-1. A diazirine ring 
-2. A terminal alkyne
-3. A coumarin photocage
-
-These modifications allow for the stabilization of protein::lipid interactions and the affinity enrichment of protein::lipid conjugates, all with tight spatiotemporal control.
-These modifications are described in greater detail below.
-
-:::{.border}
-```{r setup, echo=FALSE, include=FALSE}
-library(plotly)
-library(tidyr)
-
-# Load your image
-image_url <- "LipidProbe/Structures/SphingosineStructure.png"
-
-# Define hover regions (rectangles) with coordinates based on the top of the image
-hover_regions <- data.frame(
-  x_start = c(0.0, 0.7),  # Left side of rectangles (fraction of width)
-  x_end = c(0.4, 0.9),    # Right side of rectangles (fraction of width)
-  y_top = c(0.2, 0.3),    # Top side of rectangles (fraction of height, from top of image)
-  y_bottom = c(0.4, 0.4), # Bottom side of rectangles (fraction of height, from top of image)
-  text = c("Region 1 Info", "Region 2 Info")
-)
-
-# Create grid lines at every 10% for both x and y
-grid_lines <- list()
-for (i in seq(0, 1, by = 0.1)) {
-  # Add vertical grid line
-  grid_lines <- c(grid_lines, list(
-    list(
-      type = "line",
-      x0 = i, x1 = i,
-      y0 = 0, y1 = 1,
-      line = list(color = "gray", width = 1, dash = "dot")
-    )
-  ))
-
-  # Add horizontal grid line
-  grid_lines <- c(grid_lines, list(
-    list(
-      type = "line",
-      x0 = 0, x1 = 1,
-      y0 = i, y1 = i,
-      line = list(color = "gray", width = 1, dash = "dot")
-    )
-  ))
-}
-
-# Create the plot
-plot <- plot_ly()
-
-# Add each rectangle as a separate trace
-for (i in 1:nrow(hover_regions)) {
-  region <- hover_regions[i, ]
-  x_coords <- c(region$x_start, region$x_end, region$x_end, region$x_start, region$x_start)
-  y_coords <- c(1 - region$y_top, 1 - region$y_top, 1 - region$y_bottom, 1 - region$y_bottom, 1 - region$y_top)
-
-  plot <- plot %>%
-    add_trace(
-      x = x_coords,
-      y = y_coords,
-      type = "scatter",
-      mode = "lines",
-      line = list(
-        color = "blue",     # Border color
-        width = 2           # Border width
-      ),
-      fill = "none",         # No fill color inside the rectangle
-      hoverinfo = "text",    # Show text on hover
-      text = region$text
-    )
-}
-
-# Add the image
-plot <- plot %>%
-  layout(
-    images = list(
-      list(
-        source = image_url,
-        xref = "paper",  # Normalized to percentage
-        yref = "paper",  # Normalized to percentage
-        x = 0,           # Start at 0% of the plot width
-        y = 1,           # Start at 100% of the plot height
-        sizex = 1,       # Cover 100% of the plot width
-        sizey = 1,       # Cover 100% of the plot height
-        xanchor = "left",
-        yanchor = "top",
-        layer = "below"
-      )
-    ),
-    xaxis = list(visible = FALSE, range = c(0, 1)),  # Normalized from 0 to 1
-    yaxis = list(visible = FALSE, range = c(0, 1)),
-    shapes = grid_lines # Add the grid lines to the layout
-  )
-
-```
-
-```{r, echo=FALSE, warnings=FALSE}
-#| height: 500px
-#| width: 100%
-# Render the plot
-plot
-
-```
-:::
 
@@
 
-* Crosslinking motif activated by 355nm UV light. 
-* Irradiation of the ring produces a reactive carbene radical which covalently bonds with any nearby molecule.
+-   Crosslinking motif activated by 355nm UV light.
+-   Irradiation of the ring produces a reactive carbene radical which covalently bonds with any nearby molecule.
 This radical can form linkages by inserting into carbo-hydrogen, heteroatom-hydrogen (SH, NH~2~, or OH) or double bonds[@haberkantFatFabulousBifunctional2014].
-* This chemical group is the smallest available photoactivatable crosslinking motif [@haberkantFatFabulousBifunctional2014]
+-   This chemical group is the smallest available photoactivatable crosslinking motif [@haberkantFatFabulousBifunctional2014]
 
@@
 
-* [@schultzFlashClickMultifunctionalized2022a]
-* [@schultzChemicalToolsLipid2023]
-* [@farleyTrifunctionalSphinganineNew2024a]
-* [@hoglingerTrifunctionalLipidProbes2017]
+-   [@schultzFlashClickMultifunctionalized2022a]
+-   [@schultzChemicalToolsLipid2023]
+-   [@farleyTrifunctionalSphinganineNew2024a]
+-   [@hoglingerTrifunctionalLipidProbes2017]
 
@@
 
-* Affinity handle
-* Affix fluorophore post-hoc
+-   Affinity handle
+-   Affix fluorophore post-hoc
 
@@
 
-* Many native lipids of interest are rapidly synthesized, catabolized, and interconverted throughout the vast lipid metabolic network. 
-* The coumarin cage is a photolabile protection group. Upon stimulation with 400nm light, this group is released to expose the native structure of the lipid headgroup.
-* The exposure of the native headgroup allows for recognition by protein binders.
+-   Many native lipids of interest are rapidly synthesized, catabolized, and interconverted throughout the vast lipid metabolic network.
+-   The coumarin cage is a photolabile protection group. Upon stimulation with 400nm light, this group is released to expose the native structure of the lipid headgroup.
+-   The exposure of the native headgroup allows for recognition by protein binders.
 For example, Hoglinger et al.
@@
 While not compatible with large-scale interaction studies, this method enables the assessment of biological activity via fluorescence microscopy.
-* An additional boon of using coumarin as the caging moiety is its inherent fluorescence: one can simply use a fluorescence microscope to rapidly assess the intercalation of the functionalized lipid into the target cell.
+-   An additional boon of using coumarin as the caging moiety is its inherent fluorescence: one can simply use a fluorescence microscope to rapidly assess the intercalation of the functionalized lipid into the target cell.
 
@@
 
-* The conceptual precursor to the so-called trifunctional probes, these typically include only the diazirine and the terminal alkyne moieties.
+-   The conceptual precursor to the so-called trifunctional probes, these typically include only the diazirine and the terminal alkyne moieties.
 
@@
 
-* [@haberkantFatFabulousBifunctional2014] - Haberkant et al. 2014
+-   [@haberkantFatFabulousBifunctional2014] - Haberkant et al. 2014
 
@@
 
-References to include:
-*
-
 ## Interactomics Experimental schema
 
-:::{.border}
+::: border
 ![](SiteFigures/BaselineProteomics_ExperimentalDesign.png){group="Overview_gallery"}
@@
 #### Label-Free Quantification
+
 Label-free quantification (LFQ) is a widely used approach in mass spectrometry-based proteomics that estimates protein abundance without the need for chemical labeling.
@@
 ##### How It Works
+
 MS1 (Peptide Detection): Peptides are first isolated and detected based on their mass-to-charge ratio (m/z).
@@
 ##### Advantages of Label-Free Quantification
-* *Cost-Effective & Simple Sample Preparation*
-  * Unlike labeling methods (e.g., TMT), LFQ does not require expensive reagents or complex chemical modifications.
-  * Sample preparation is straightforward, making LFQ accessible to a wide range of researchers.
-* *Widely Used & Flexible*
-  * LFQ is a common approach in proteomics, compatible with various experimental designs.
-  * It allows for comparisons across a large number of samples without being limited by multiplexing constraints.
+
+-   *Cost-Effective & Simple Sample Preparation*
+    -   Unlike labeling methods (e.g., TMT), LFQ does not require expensive reagents or complex chemical modifications.
+    -   Sample preparation is straightforward, making LFQ accessible to a wide range of researchers.
+-   *Widely Used & Flexible*
+    -   LFQ is a common approach in proteomics, compatible with various experimental designs.
+    -   It allows for comparisons across a large number of samples without being limited by multiplexing constraints.
 
 ##### Challenges & Considerations
-* *Potential Bias from Co-Elution:*
-  * In complex samples, high-abundance peptides can overshadow low-abundance peptides, limiting the number of peptides that can be reliably isolated and quantified in the MS1 scan.
-* *Run-to-Run Variability:*
-  * Unlike TMT-based methods, where all samples are analyzed together in a single run, LFQ requires separate MS runs for each sample.
-* Differences in instrument calibration, chromatography conditions, or sample preparation can introduce variability, potentially leading to artificial differences between samples if not carefully controlled.
+
+-   *Potential Bias from Co-Elution:*
+    -   In complex samples, high-abundance peptides can overshadow low-abundance peptides, limiting the number of peptides that can be reliably isolated and quantified in the MS1 scan.
+-   *Run-to-Run Variability:*
+    -   Unlike TMT-based methods, where all samples are analyzed together in a single run, LFQ requires separate MS runs for each sample.
+-   Differences in instrument calibration, chromatography conditions, or sample preparation can introduce variability, potentially leading to artificial differences between samples if not carefully controlled.
 
 ##### Conclusion
+
 Label-free quantification is a practical and widely used approach for proteomics research, offering a cost-effective and simple method for estimating protein abundance.
@@
 
-* **Chemical Labeling**: Each peptide in a sample is chemically tagged with a unique TMT label, which consists of an identical reactive group that binds to peptides and a mass reporter region that differentiates samples.
+-   **Chemical Labeling**: Each peptide in a sample is chemically tagged with a unique TMT label, which consists of an identical reactive group that binds to peptides and a mass reporter region that differentiates samples.
 
-* **Sample Pooling:** Once labeled, samples are combined into a single pooled sample group, reducing the need for separate MS runs.
+-   **Sample Pooling:** Once labeled, samples are combined into a single pooled sample group, reducing the need for separate MS runs.
 
-* **Mass Spectrometry Analysis:** 
-  * *MS1 (Peptide Isolation):* Peptides are first separated and detected based on their mass-to-charge ratio (m/z). 
-  * *MS2 (Peptide Sequencing & Tag Fragmentation):* Peptides are fragmented, allowing for sequence identification. At the same time, the mass tags also fragment, producing unique reporter ions. 
-  * *Quantification:* The intensity of these reporter ions reveals the relative abundance of each peptide across the original samples.
+-   **Mass Spectrometry Analysis:**
+
+    -   *MS1 (Peptide Isolation):* Peptides are first separated and detected based on their mass-to-charge ratio (m/z).
+    -   *MS2 (Peptide Sequencing & Tag Fragmentation):* Peptides are fragmented, allowing for sequence identification. At the same time, the mass tags also fragment, producing unique reporter ions.
+    -   *Quantification:* The intensity of these reporter ions reveals the relative abundance of each peptide across the original samples.
 
 ##### Advantages of TMT Labeling
-* Increased Throughput & Efficiency
-TMT allows for the multiplexing of many samples (e.g., 16 or more), reducing the number of separate MS runs needed.
+
+-   Increased Throughput & Efficiency TMT allows for the multiplexing of many samples (e.g., 16 or more), reducing the number of separate MS runs needed.
 Instead of running 16 individual samples separately, they can be pooled and analyzed together, increasing experimental efficiency.
-* Deeper Proteome Coverage
-The pooled sample can be further fractionated (e.g., using cation exchange chromatography), which helps separate high-abundance and low-abundance peptides before MS analysis.
+-   Deeper Proteome Coverage The pooled sample can be further fractionated (e.g., using cation exchange chromatography), which helps separate high-abundance and low-abundance peptides before MS analysis.
 This results in greater depth of peptide detection compared to running multiple low-depth, individual label-free MS analyses.
-* Improved Quantification Accuracy
-Since all samples are analyzed together in the same MS run, technical variability between runs is minimized, leading to more accurate relative quantification.
+-   Improved Quantification Accuracy Since all samples are analyzed together in the same MS run, technical variability between runs is minimized, leading to more accurate relative quantification.
 
 ##### Challenges & Considerations
-* Higher Cost
-TMT reagents and the need for higher-end mass spectrometers contribute to increased costs.
-* Complex Sample Preparation
-Additional steps are required for labeling, pooling, and fractionation, which increases the risk of sample handling variability.
-* Normalization Requirement
-Total protein input must be carefully controlled to ensure accurate quantification.
+
+-   Higher Cost TMT reagents and the need for higher-end mass spectrometers contribute to increased costs.
+-   Complex Sample Preparation Additional steps are required for labeling, pooling, and fractionation, which increases the risk of sample handling variability.
+-   Normalization Requirement Total protein input must be carefully controlled to ensure accurate quantification.
 Unequal sample amounts (e.g., when comparing conditions with highly different protein yields) may require artificial balancing, which can introduce biases.
-* Demanding Instrumentation & Expertise
-The technique requires high-resolution mass spectrometers with precise scanning capabilities, often necessitating outsourcing to specialized facilities.
+-   Demanding Instrumentation & Expertise The technique requires high-resolution mass spectrometers with precise scanning capabilities, often necessitating outsourcing to specialized facilities.
 
 ##### Conclusion
+
 TMT-based quantitative mass spectrometry is a valuable tool for large-scale proteomics studies, providing high-throughput, precise, and deep proteome coverage.

### 2025-01-30 BioinformaticsApplicationNote/GG_2025_applicationNote.qmd
beginning my application note, many small adjustments, big text edits to overview

---
title: "Lipid Interactomics Repository"
subtitle: "An interactive and open access platform for exploring multifunctional lipid interactomes"
authors:
  - name: "Fikadu Tafesse"
    affiliation: "Oregon Health & Science University"
    orcid: 0000-0002-8575-4164
  - name: "Carsten Schultz"
    affiliation: "Oregon Health & Science University"
    orcid: 0000-0002-5824-2171
  - name: "Gaelen Guzman"
    affiliation: "Oregon Health & Science University"
    orcid: 0000-0002-7696-6034
    corresponding: true
    email: gaelenguzman@lipidinteractome.org
page-navigation: false
format: html
---

## Outline

- Abstract
  * Summary
  * Availability: This site can be viewed at [lipidinteractome.org](lipidinteractome.org); all data is available for download. 
  * Data Submission: If you would like to submit a relevant dataset, see [Data Submission](https://www.lipidinteractome.org/DataSubmission.html) for details and instructions.

- Introduction

- Description

- Acknowledgements

### 2025-01-30 DataSubmission.qmd
beginning my application note, many small adjustments, big text edits to overview

---
title: "Submit a dataset to the Lipid Interactome Repository"

---

**This repository is still under construction, please forgive us for incomplete sections as we build features!**

We are in the process of building a data submission form here -- check back soon for this functionality!

In the meantime, email us at <contact.us@LipidInteractome.org>{target="_blank"} to discuss data handoff and study details.

### Data formatting

The ideal dataset to incorporate into this site will have the following columns:

* **gene_name** 
* **LipidProbe** - Which lipid probe was applied in the analysis (especially if there are several)
* **comparison** - The ratiometric comparison reflected by the logFC (i.e. +UV versus -UV)
* **logFC** - the log2 transformed fold-change between the conditions in the comparison
* **pvalue** - the results of an appropriate statistical test. Ideally share the methods used
* **AveExpr** - the average ion intensity between the two conditions in the reported comparison (for MA plots)
* **hit_annotation** - A statistical representation of the significance of each protein. The standardized nomenclature used in Thomas et al. 2025, Farley et al. 2024, and Farley et al. 2024 has the following:
	* **"no hit"** = unenriched or depleted in the presence of probe
	* **"enriched candidates"** are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold
	* **"enriched hits"** are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV.
* **FDR** - The false discovery rate of the protein.

### 2025-01-30 TrifunctionalLipidProbesOverview.qmd
beginning my application note, many small adjustments, big text edits to overview

@@
 
+# Multifunctional Lipid Probes Background
+
 Functionalized lipid probes are at the intersection of several niche biotechnologies.
-This overview will serve as a brief summary of the capabilities, nuances, and caveats of their utility.
-Additional resources and published review articles will be referenced throughout and linked below for greater detail.
+This overview will serve as a summary of the capabilities, nuances, and caveats of their utility.
+Additional resources and published review articles will be referenced and linked below for greater detail.
 
@@
 Every biological process—from metabolism to signaling—depends on the physical interactions between molecules, including proteins, nucleic acids, and lipids.
-While proteins have long been the primary focus of interaction studies, lipids play an equally crucial yet often under-appreciated role in cellular function.
+While proteins have long been the primary focus of interaction studies, lipids play an equally crucial yet often underappreciated role in cellular function.
 
@@
 S1P binds to a specific family of receptors, triggering T cell migration (extravasation) and guiding their movement toward sites of infection.
-This highlights how lipid signaling can have far-reaching effects on cellular behavior and physiological responses.
+This highlights how lipid signaling can affect cellular behavior and physiological responses.
 
@@
 The study of lipid biology has been greatly advanced by synthetic lipid analogs.
-However, it may not be immediately clear why such analogs are so essential.
+However, it may not be immediately clear why such analogs are essential.
 Unlike proteins and nucleic acids, lipids present unique challenges that make traditional genetic tools less effective in studying their function.
@@
 Advances in genetic engineering—such as CRISPR and de novo gene synthesis—have revolutionized the study of nucleic acids and proteins.
-These techniques allow researchers to introduce precise modifications, such as:
+These techniques enable precise modifications, such as altering enzyme activity, redirecting proteins to different subcellular locations, modifying binding domains, and tagging proteins for visualization or isolation.
 
--   Altering enzyme activity by mutating active sites to change substrate specificity.
--   Redirecting proteins by swapping subcellular localization sequences.
--   Modifying protein interactions by swapping or removing binding domains.
--   Visualizing proteins by fusing them with fluorescent tags (e.g., GFP).
--   Isolating protein complexes by adding affinity handles for purification.
+In contrast, lipids present unique challenges that make genetic approaches impractical.
+Unlike proteins, which are directly encoded in DNA, lipids are synthesized enzymatically.
+Their structures cannot be modified in living cells through genetic manipulation alone.
+Traditional approaches, such as gene knockouts or knock-ins, can broadly alter lipid composition but do not allow for precise control over individual lipid species.
 
-In contrast, lipids pose distinct challenges that make such genetic manipulations impractical:
+Lipids are also much smaller than proteins, often composed of just a few dozen atoms.
+Even minor modifications can significantly alter their biophysical properties and biological function.
+Unlike proteins, which can tolerate the addition of large fluorescent or affinity tags, lipids require minimal chemical modifications to preserve their activity.
 
-1.  Lipids Are Synthesized Enzymatically
-    -   Unlike proteins, whose sequences are encoded in DNA, lipids are the product of enzymatic pathways.
-Their structures cannot be directly altered within a living system in the same way that gene sequences can be modified.
-    -   Early lipid research relied on gene knockouts and knock-ins to globally alter lipid composition, which provided broad insights into lipid classes but was less effective for studying individual lipid species.
-2.  Lipids Are Small and Structurally Sensitive
-    -   Compared to proteins, which consist of hundreds or thousands of atoms, lipids are much smaller (often composed of just a few dozen atoms).
-    -   Because of their size, even small modifications can dramatically alter their biophysical properties and biological function.
-    -   For example, unlike proteins, lipids cannot be tagged with large fluorescent proteins (e.g., GFP) or classical affinity tags (e.g., HA tags) without completely disrupting their activity.
-3.  Lipids Are Metabolically Dynamic
-    -   Lipids exist within a highly dynamic metabolic network, where they can be rapidly modified, cleaved, or converted into other lipid species.
-    -   Some lipids, like sphingosine, have extremely short half-lives—sometimes only minutes—making them difficult to track and study in real time.
+Additionally, lipids exist within a highly dynamic metabolic network, where they are continuously synthesized, modified, and degraded.
+Some signaling lipids, such as sphingosine, have extremely short half-lives—sometimes only minutes—making them difficult to track in real-time.
+
+To overcome these challenges, researchers have developed synthetic lipid analogs with chemical modifications that allow for targeted investigation while preserving essential biological properties.
+The following sections detail key modifications used in functional lipid probes.
 
@@
 
-### Diazirine: A photo-activated crosslinker {#sec-DiazirinePlacement}
+#### Diazirine: Stabilizing Lipid-Protein Interactions with Covalent Crosslinking {#sec-DiazirinePlacement}
 
-Lipid interactions are typically highly transient -- few opportunities for
+Lipid-protein interactions are inherently transient and dynamic, making them particularly challenging to capture and study.
+Unlike protein-protein interactions, which often rely on extensive surface interfaces and hydrogen bonding, most lipids have minimal hydrogen bonding potential and lack a substantial structural framework for stable interactions.
+As a result, even biologically relevant lipid-protein contacts may be too fleeting to detect under standard biochemical conditions.
 
--   Crosslinking motif activated by 355nm UV light.
--   Irradiation of the ring produces a reactive carbene radical which covalently bonds with any nearby molecule.
-This radical can form linkages by inserting into carbo-hydrogen, heteroatom-hydrogen (SH, NH~2~, or OH) or double bonds[@haberkantFatFabulousBifunctional2014].
--   This chemical group is the smallest available photoactivatable crosslinking motif [@haberkantFatFabulousBifunctional2014]
+To effectively identify and analyze lipid-binding proteins, it is necessary to stabilize these interactions in a way that allows their subsequent enrichment and detection.
+While affinity enrichment approaches (e.g., lipid pulldown assays) can be used, they often require detergents to solubilize membrane-associated complexes, which can introduce artifacts or disrupt weak lipid-protein interactions.
+Covalent crosslinking, on the other hand, offers a far more reliable method to “freeze” these interactions in place, preserving their native binding state even during rigorous purification steps before mass spectrometry analysis.
 
-References to include:
+##### Why Use Diazirine as a Crosslinking Motif?
 
--   [@schultzFlashClickMultifunctionalized2022a]
--   [@schultzChemicalToolsLipid2023]
--   [@farleyTrifunctionalSphinganineNew2024a]
--   [@hoglingerTrifunctionalLipidProbes2017]
+Several chemical groups can be used for covalent crosslinking, but diazirine rings are particularly well-suited for lipid studies due to their small size and minimal structural interference.
+Other crosslinking motifs may alter the lipid’s physicochemical properties, potentially changing its interaction profile.
+Diazirine, however, is the smallest known photoactivatable crosslinking group, making it an ideal choice for studying delicate lipid-protein interactions.
 
-### Terminal Alkyne
+##### Key properties of diazirine crosslinking:
 
--   Affinity handle
--   Affix fluorophore post-hoc
+Lipid interactions are typically transient, as most lipids lack opportunities for strong hydrogen bonding and are too small to provide a significant binding interface.
+Identifying interacting proteins requires stabilizing these interactions to allow for enrichment and analysis.
+While affinity-based approaches can help, covalent crosslinking is the most effective method, as it enables the removal of impurities and detergents before mass spectrometry analysis.
 
-### Coumarin Photocage: A photo-activated protection moiety
+Among the various crosslinking motifs, the diazirine ring is the smallest, making it the least likely to interfere with a lipid’s natural interactions.
+Upon exposure to 355 nm UV light, the diazirine ring forms a reactive carbene radical, which rapidly covalently bonds with nearby molecules.
+This reaction is highly versatile, as the carbene can insert into carbon-hydrogen, sulfur-hydrogen, nitrogen-hydrogen, oxygen-hydrogen, or double bonds, allowing for broad coverage of potential interaction partners\[\@haberkantFatFabulousBifunctional2014\].
 
--   Many native lipids of interest are rapidly synthesized, catabolized, and interconverted throughout the vast lipid metabolic network.
--   The coumarin cage is a photolabile protection group. Upon stimulation with 400nm light, this group is released to expose the native structure of the lipid headgroup.
--   The exposure of the native headgroup allows for recognition by protein binders.
-For example, Hoglinger et al.
-showed in 2015 that the release of caged sphingosine resulted in potent lysosomal calcium release -- a finding which greatly expanded the understanding of the intracellular sphingosine signaling cascade[@hoglingerIntracellularSphingosineReleases2015a].
-In this and other studies, sub-cellular irradiation using a scanning laser allows for the select spatial control of uncaging.
-While not compatible with large-scale interaction studies, this method enables the assessment of biological activity via fluorescence microscopy.
--   An additional boon of using coumarin as the caging moiety is its inherent fluorescence: one can simply use a fluorescence microscope to rapidly assess the intercalation of the functionalized lipid into the target cell.
+The small size and high reactivity of diazirine crosslinking make it an invaluable tool for capturing lipid-protein interactions while minimizing perturbations to native lipid function.
+
+#### Terminal Alkyne
+
+When studying proteins, researchers often use genetic methods to tag or modify them, making them easier to visualize or isolate.
+For example, adding a green fluorescent protein (GFP) domain to a protein allows it to be seen under a fluorescence microscope, whereas incorporating an HA tag enables enrichment using antibody pulldown techniques.
+These approaches work well for proteins because they are encoded by genes and can be modified at the DNA level.
+
+Lipids, however, cannot be modified in the same way.
+Their synthesis occurs enzymatically, meaning there is no genetic sequence to alter.
+Large additions, like a GFP or HA domain, would drastically change a lipid’s properties, making it unrecognizable to the proteins and pathways that typically interact with it.
+Instead, a much smaller modification is needed—one that allows researchers to track and manipulate lipids without interfering with their biological function.
+
+##### The Terminal Alkyne: A Versatile Bioorthogonal Handle
+
+One of the smallest and most effective modifications for this purpose is the terminal alkyne.
+This functional group consists of a simple triple bond at the end of a carbon chain, a minor structural change that does not significantly alter the lipid’s behavior.
+Despite its small size, the terminal alkyne serves as a powerful chemical handle, allowing researchers to attach various probes after the lipid has been introduced into a biological system.
+
+The terminal alkyne is particularly useful because it undergoes azide-alkyne cycloaddition, a type of click chemistry reaction.
+This reaction is highly specific, rapid, and bio-orthogonal, meaning it does not interfere with natural cellular processes.
+By reacting the alkyne with an azide-containing probe, researchers can introduce fluorescent markers for imaging or affinity tags for isolating lipid-protein complexes.
+
+##### Applications in Lipid Research
+
+One major application of the terminal alkyne is fluorescence labeling.
+A functionalized lipid can be introduced into cells and later reacted with a fluorophore-conjugated azide, allowing researchers to visualize its distribution and movement under a microscope.
+This approach provides insights into lipid localization and trafficking.
+
+Another important use is affinity-based enrichment.
+Lipids containing a terminal alkyne can be captured using azide-functionalized beads, enabling the isolation of lipid-protein complexes for analysis by mass spectrometry.
+This method has been instrumental in identifying proteins that interact with specific lipid species, shedding light on lipid signaling pathways and metabolic networks.
+
+By providing a simple yet effective means of modifying lipids without disrupting their native properties, the terminal alkyne has become an essential tool in lipidomics and chemical biology.
+It bridges the gap between traditional lipid research and modern bioorthogonal chemistry, allowing for precise studies of lipid function in living systems.
+
+### Coumarin Photocage: Controlling Lipid Activity with Light
+
+Lipids play an essential role in cellular signaling, yet their biological study presents unique challenges due to their highly dynamic metabolism.
+Unlike proteins, which are relatively stable once synthesized, many bioactive lipids are continuously synthesized, modified, interconverted, and degraded as part of an extensive and tightly regulated lipid metabolic network.
+This rapid turnover makes it difficult to study the effects of a specific lipid species in isolation, as the lipid of interest may be enzymatically altered before it can exert its intended biological function.
+
+One strategy to overcome this challenge is using photocaged lipid analogs, which remain biologically inert until exposed to a specific wavelength of light.
+Irradiation with this wavelength "uncages" the analog to reveal its native structure.
+This allows researchers to control the timing and location of lipid activation, enabling targeted investigation of lipid function with high spatiotemporal resolution.
+
+#### A Light-Activated Protection Group
+
+One of the most effective tools for photocaging lipids is the coumarin cage, a photolabile protection group that can be removed upon exposure to 400 nm light.
+When attached to a lipid’s headgroup, the coumarin moiety temporarily blocks interactions with proteins, preventing the lipid from participating in its normal biological pathways.
+However, upon photoactivation, the coumarin group is cleaved, restoring the lipid to its native structure and allowing it to engage with its biological targets.
+
+This approach is useful for studying lipid-protein interactions, as uncaging the lipid in a controlled manner ensures that protein binders recognize the native lipid structure only when and where the researcher intends.
+
+#### Applications in Cellular Signaling Studies
+
+The power of coumarin-caged lipids has been demonstrated in studies examining intracellular lipid signaling.
+For example, in 2015, Högliner et al.
+used a caged sphingosine analog to investigate the role of sphingosine in calcium signaling.
+They found that upon photoactivation of the caged sphingosine, lysosomal calcium release was triggered, revealing a crucial link between sphingosine metabolism and intracellular calcium dynamics [@hoglingerIntracellularSphingosineReleases2015a].
+This discovery significantly expanded the understanding of the sphingosine signaling cascade and its downstream effects.
+
+Beyond biochemical studies, coumarin-caged lipids enable live-cell imaging approaches.
+Selectively irradiating specific subcellular regions allows the researcher to uncage lipids in a highly localized manner and assess their effects in real time.
+While this approach is not well-suited for large-scale proteomic studies, it provides a powerful method for investigating lipid function via fluorescence microscopy.
+
+#### An Additional Benefit: Coumarin’s Inherent Fluorescence
+
+A unique advantage of using coumarin as a photocaging group is its intrinsic fluorescence.
+This means that before the lipid is even uncaged, its cellular incorporation can be directly visualized using a fluorescence microscope.
+By tracking fluorescence intensity and distribution, researchers can quickly determine whether a functionalized lipid has successfully intercalated into the target cell’s membrane or accumulated in specific subcellular compartments.
+
+This dual functionality—serving as both a caging group and a fluorescent probe—makes coumarin a useful tool for studying lipid localization, uptake, and bioactivity.
 
@@
 
-Label-free quantification (LFQ) is a widely used approach in mass spectrometry-based proteomics that estimates protein abundance without the need for chemical labeling.
+Label-free quantification (LFQ) is a widely used mass spectrometry-based proteomics approach that estimates protein abundance without chemical labeling.
 Instead, it relies on comparing the summed intensity of detected peptides across different samples analyzed under identical conditions.
@@
 
-MS1 (Peptide Detection): Peptides are first isolated and detected based on their mass-to-charge ratio (m/z).
-MS2 (Peptide Sequencing): Selected peptide ions are fragmented, and the resulting spectra are used to determine peptide sequences.
-Quantification: The total signal intensity of all identified peptides corresponding to a given protein is summed, serving as a proxy for the protein’s absolute abundance.
-Comparison Across Samples: When two or more samples are prepared and analyzed using the same LC-MS/MS protocol, their relative protein abundances can be compared.
+1.  **Peptide Detection (MS1):** Peptides are isolated and detected based on their mass-to-charge ratio (m/z).
+
+2.  **Peptide Sequencing (MS2):** Selected peptide ions are fragmented, and the resulting spectra determine peptide sequences.
+
+3.  **Quantification:** The total signal intensity of all identified peptides corresponding to a protein is summed as a proxy for its abundance.
+
+4.  **Comparison Across Samples:** Samples prepared and analyzed using the same LC-MS/MS protocol can be compared using peptide-spectrum match (PSM) counts as an abundance proxy.
 
@@
 
--   *Cost-Effective & Simple Sample Preparation*
-    -   Unlike labeling methods (e.g., TMT), LFQ does not require expensive reagents or complex chemical modifications.
-    -   Sample preparation is straightforward, making LFQ accessible to a wide range of researchers.
--   *Widely Used & Flexible*
-    -   LFQ is a common approach in proteomics, compatible with various experimental designs.
-    -   It allows for comparisons across a large number of samples without being limited by multiplexing constraints.
+-   **Cost-Effective & Simple Sample Preparation:** Unlike labeling methods (e.g., TMT), LFQ does not require expensive reagents or complex modifications, making it more accessible.
+
+-   **Flexible & Widely Used:** Compatible with various experimental designs and allows for comparisons across many samples without multiplexing constraints.
 
@@
 
--   *Potential Bias from Co-Elution:*
-    -   In complex samples, high-abundance peptides can overshadow low-abundance peptides, limiting the number of peptides that can be reliably isolated and quantified in the MS1 scan.
--   *Run-to-Run Variability:*
-    -   Unlike TMT-based methods, where all samples are analyzed together in a single run, LFQ requires separate MS runs for each sample.
--   Differences in instrument calibration, chromatography conditions, or sample preparation can introduce variability, potentially leading to artificial differences between samples if not carefully controlled.
+-   **Potential Bias from Co-Elution:** High-abundance peptides can overshadow low-abundance ones, reducing the number of reliably quantified peptides.
+
+-   **Run-to-Run Variability:** LFQ requires separate MS runs for each sample, making it susceptible to differences in instrument calibration, chromatography conditions, or sample handling.
+Careful quality control is necessary to minimize artificial differences.
 
@@
 
-Label-free quantification is a practical and widely used approach for proteomics research, offering a cost-effective and simple method for estimating protein abundance.
-However, careful experimental design and quality control are essential to minimize variability and ensure reliable quantification across different runs.
+Label-free quantification is a practical and widely used method for proteomics research.
+While cost-effective and flexible, its accuracy depends on careful experimental design and quality control to reduce variability.
 
@@
 
-Tandem Mass Tag (TMT) labeling is a powerful technique in quantitative mass spectrometry (MS) that allows for the simultaneous analysis of multiple samples in a single MS run.
-This method enhances efficiency and enables precise relative quantification of proteins across different experimental conditions.
+Tandem Mass Tag (TMT) labeling is a powerful quantitative mass spectrometry technique that enables the simultaneous analysis of multiple samples in a single MS run.
+This approach improves efficiency and allows for precise relative quantification of proteins across experimental conditions.
 
@@
 
--   **Chemical Labeling**: Each peptide in a sample is chemically tagged with a unique TMT label, which consists of an identical reactive group that binds to peptides and a mass reporter region that differentiates samples.
+1.  **Chemical Labeling:** Each sample is chemically tagged with a unique TMT label, which consists of a reactive group binding to peptides and a mass reporter for sample differentiation.
 
--   **Sample Pooling:** Once labeled, samples are combined into a single pooled sample group, reducing the need for separate MS runs.
+2.  **Sample Pooling:** Labeled samples are combined into a single pooled group, reducing the need for separate MS runs.
 
--   **Mass Spectrometry Analysis:**
+3.  **Mass Spectrometry Analysis:**
 
-    -   *MS1 (Peptide Isolation):* Peptides are first separated and detected based on their mass-to-charge ratio (m/z).
-    -   *MS2 (Peptide Sequencing & Tag Fragmentation):* Peptides are fragmented, allowing for sequence identification. At the same time, the mass tags also fragment, producing unique reporter ions.
-    -   *Quantification:* The intensity of these reporter ions reveals the relative abundance of each peptide across the original samples.
+    -   **MS1 (Peptide Isolation):** Peptides are separated and detected based on their mass-to-charge ratio (m/z).
+
+    -   **MS2 (Peptide Sequencing & Tag Fragmentation):** Peptides are fragmented for sequence identification, and TMT mass tags fragment to generate reporter ions.
+
+4.  **Quantification:** The intensity of reporter ions reveals the relative abundance of peptides across the original samples.
+
+5.
+**Comparison Across Samples:** Within a TMT cassette (typically 16 samples), relative protein abundance is calculated from the reporter ion intensities.
+A pooled control channel enables comparison across cassettes, allowing up to 30 samples to be analyzed in a single experiment.
 
@@
 
--   Increased Throughput & Efficiency TMT allows for the multiplexing of many samples (e.g., 16 or more), reducing the number of separate MS runs needed.
-Instead of running 16 individual samples separately, they can be pooled and analyzed together, increasing experimental efficiency.
--   Deeper Proteome Coverage The pooled sample can be further fractionated (e.g., using cation exchange chromatography), which helps separate high-abundance and low-abundance peptides before MS analysis.
-This results in greater depth of peptide detection compared to running multiple low-depth, individual label-free MS analyses.
--   Improved Quantification Accuracy Since all samples are analyzed together in the same MS run, technical variability between runs is minimized, leading to more accurate relative quantification.
+-   **Increased Throughput & Efficiency:** Enables multiplexing of many samples (e.g., 16 or more), reducing the number of separate MS runs.
+
+-   **Deeper Proteome Coverage:** Pooled samples can be fractionated (e.g., by cation exchange chromatography), enhancing detection of low-abundance peptides.
+
+-   **Improved Quantification Accuracy:** Since all samples are analyzed in the same MS run, technical variability between runs is minimized.
 
@@
 
--   Higher Cost TMT reagents and the need for higher-end mass spectrometers contribute to increased costs.
--   Complex Sample Preparation Additional steps are required for labeling, pooling, and fractionation, which increases the risk of sample handling variability.
--   Normalization Requirement Total protein input must be carefully controlled to ensure accurate quantification.
-Unequal sample amounts (e.g., when comparing conditions with highly different protein yields) may require artificial balancing, which can introduce biases.
--   Demanding Instrumentation & Expertise The technique requires high-resolution mass spectrometers with precise scanning capabilities, often necessitating outsourcing to specialized facilities.
+-   **Higher Cost:** TMT reagents and high-end mass spectrometers add to the expense.
+
+-   **Complex Sample Preparation:** Requires additional steps for labeling, pooling, and fractionation, increasing the risk of sample handling variability.
+
+-   **Normalization Requirement:** Accurate quantification requires equal protein input across samples to avoid artificial balancing biases.
+
+-   **Demanding Instrumentation & Expertise:** Requires high-resolution mass spectrometers, often necessitating specialized facilities.
 
@@
 
-TMT-based quantitative mass spectrometry is a valuable tool for large-scale proteomics studies, providing high-throughput, precise, and deep proteome coverage.
-While it requires careful sample preparation and advanced instrumentation, its ability to multiplex multiple samples in a single run makes it an attractive option for researchers aiming for high-confidence protein quantification.
+TMT-based mass spectrometry is a valuable tool for large-scale proteomics, offering high-throughput, precise, and deep proteome coverage.
+While it requires advanced instrumentation and careful sample preparation, its ability to multiplex multiple samples in a single run makes it an attractive option for high-confidence protein quantification.

### 2025-01-30 LipidProbe/DataSets/LipidInteractomics_ShinyApp/app.R

@@ -4,9 +4,12 @@ library(ggplot2)
 library(plotly)
 library(readr)
 library(shiny)
-library(amVennDiagram5)
 
-df <- read_csv("combinedProbeDatasets_TMT.csv")
+# File path for testing
+df <- read_csv("/LipidProbe/DataSets/LipidInteractomics_ShinyApp/combinedProbeDatasets_TMT.csv")
+
+# File path for deploying to Shinyapps.io
+#df <- read_csv("combinedProbeDatasets_TMT.csv")
 
 probeOptions <- unique(df$LipidProbe)
 
@@ -27,37 +30,44 @@ ui <- fluidPage(
 
 server <- function(input, output, session) {
 	
+	# Creating filtered datasets for the probes selected
 	xData <- reactive({
-		xData<- df |>
+		xData <- df |>
 			filter(LipidProbe == input$probe1) 
 		return(xData)
 	})
 
 	yData <- reactive({
-		yData<- df |>
+		yData <- df |>
 			filter(LipidProbe == input$probe2) 
 		return(yData)
 	})
 
+	# The output call for making the plot - includes some data wrangling to make sure the selected probes are handled properly. A
+	## Also makes the linear regression line to add to the plot.
   output$logFCPlot <- renderPlotly({
+
+		# Isolating the probes selected by the user
 		probe1Name <- input$probe1
 		probe2Name <- input$probe2
 
 		# Create a new dataframe for plotting
 		xData <- xData()
 		yData <- yData()
-
-		plot_data <- merge(xData, yData, by="gene_name") |>
+    
+		# handles the NAs by placing them on the appropriate axes.
+		plot_data <- full_join(xData,yData,by="gene_name") |>
+			mutate(logFC.x=if_else(is.na(logFC.x),0,logFC.x))|>
+			mutate(logFC.y=if_else(is.na(logFC.y),0,logFC.y)) |>
+			mutate(hit_annotation.x=if_else(is.na(hit_annotation.x),"no hit",hit_annotation.x)) |>
+			mutate(hit_annotation.y=if_else(is.na(hit_annotation.y),"no hit",hit_annotation.y)) |>
 			mutate(combined_hit_annotation = case_when(hit_annotation.x == "enriched hit" & hit_annotation.y == "enriched hit" ~ "enriched on both axes",
[…]

### 2025-01-30 TrifunctionalLipidProbesOverview.qmd
removed naughty docx formatting

@@
 **This repository is still under construction, please forgive us for incomplete sections as we build features!**
-
-# Multifunctional Lipid Probes Background
 
@@
 
-1.  Diazirine Rings – Enable covalent crosslinking to interacting proteins upon UV activation.
-2.  Terminal Alkynes – Allow for affinity enrichment using click chemistry.
-3.  Coumarin Photocages – Provide spatiotemporal control over lipid activity through light-triggered release.
-
-These modifications stabilize protein-lipid interactions and enable the selective enrichment of lipid-bound proteins, all while maintaining tight spatial and temporal control.
-Each of these tools is described in further detail below.
-
-#### Diazirine: Stabilizing Lipid-Protein Interactions with Covalent Crosslinking {#sec-DiazirinePlacement}
+:::{.callout-note collapse="true"}
+#### Diazirine ring
 
@@
 
+##### The effect of Diazirine placement on crosslinking targets {#sec-DiazirinePlacement}
+
+- The reactive carbene produced upon irradiation will bond with whatever molecule is nearest -- thus, the location of the diazirine ring can have a dramatic effect on what protein interactors are stabilized via crosslinking.
+
+- The majority of lipid analogs produced to date were synthesized with the diazirine ring near the terminal end of an acyl chain.
+For example, [8-3 Fatty Acid](/LipidProbe/8-3_FattyAcid.qmd) has the acyl chain only 3 carbons from the end.
+These lipid analogs may be expected to preferentially crosslink to proteins which penetrate far into the hydrophobic region between the leaflets of a membrane bilayer, such as transmembrane proteins.
+
+- In comparison, moving the diazirine ring closer to the hydrophilic headgroup may increase the partiality of crosslinking towards peripheral membrane proteins in addition to transmembrane proteins.
+An example of this shift is [1-10 Fatty Acid](/LipidProbe/1-10_FattyAcid.qmd), in which the diazirine ring was placed 10 carbons from the terminus of the chain.
+:::
+
+:::{.callout-note collapse="true"}
 #### Terminal Alkyne
@@
 
-##### The Terminal Alkyne: A Versatile Bioorthogonal Handle
+##### A Versatile Bioorthogonal Handle
 
@@
 It bridges the gap between traditional lipid research and modern bioorthogonal chemistry, allowing for precise studies of lipid function in living systems.
+:::
 
-### Coumarin Photocage: Controlling Lipid Activity with Light
-
+:::{.callout-note collapse="true"}
+#### Coumarin Photocage
 Lipids play an essential role in cellular signaling, yet their biological study presents unique challenges due to their highly dynamic metabolism.
@@
 
-#### A Light-Activated Protection Group
+##### A Light-Activated Protection Group
 
@@
 
-#### Applications in Cellular Signaling Studies
+##### Applications in Cellular Signaling Studies
 
@@
 
-#### An Additional Benefit: Coumarin’s Inherent Fluorescence
+##### An Additional Benefit: Coumarin’s Inherent Fluorescence
 
@@
 This dual functionality—serving as both a caging group and a fluorescent probe—makes coumarin a useful tool for studying lipid localization, uptake, and bioactivity.
+:::
+
+These modifications stabilize protein-lipid interactions and enable the selective enrichment of lipid-bound proteins, all while maintaining tight spatial and temporal control.
+Each of these tools is described in further detail below.
 
@@
 
+:::{.callout-note collapse="true"}
 #### Label-Free Quantification
@@
 While cost-effective and flexible, its accuracy depends on careful experimental design and quality control to reduce variability.
-
+:::
+:::{.callout-note collapse="true"}
 #### Quantitative Mass Spectrometry with Tandem Mass Tagging {#sec-TMT}
@@
 While it requires advanced instrumentation and careful sample preparation, its ability to multiplex multiple samples in a single run makes it an attractive option for high-confidence protein quantification.
+:::

### 2025-01-31 BioinformaticsApplicationNote/GG_2025_applicationNote.qmd
eod update

@@
     email: gaelenguzman@lipidinteractome.org
+format:
+  html:
+    embed-resources: false
+  docx:
+    fig-height: 5
+    reference-doc: custom-reference-doc.docx
 page-navigation: false
-format: html
+
 ---
@@
   * Summary
-  * Availability: This site can be viewed at [lipidinteractome.org](lipidinteractome.org); all data is available for download. 
-  * Data Submission: If you would like to submit a relevant dataset, see [Data Submission](https://www.lipidinteractome.org/DataSubmission.html) for details and instructions.
+    - Lipid probes are a recent advent of lipid biology which allow for the identification of lipid::protein interactions.
+A growing number of lipid interactomes have been published, but there has not yet been an effort to coordinate or compare the findings between such studies.
+The LipidInteractome is an effort to expand the findability, accessibility, interoperability, and reproducibility of these studies according to the FAIR principles [REF https://www.go-fair.org/fair-principles/].
+This site seeks to enable researchers to explore the biological function of lipids by interrogating their protein interaction partners.
+  * Availability: This site can be viewed at [LipidInteractome.org](lipidinteractome.org); all data is available for download.
+  * Data Submission: If you would like to submit a relevant dataset, see our [Data Submission Page](https://www.lipidinteractome.org/DataSubmission.html) for details, contact info, and instructions.
 
 - Introduction
+  * What is this repository for?
+  * Why did we make it?
+  * Who will benefit from it?
+  * Are there alternatives?
+    - No, there is no centralized repository for lipid interactions data -- the [BioPlex](https://bioplex.hms.harvard.edu) web platform serves as an excellent repository for protein::protein interactions and we have sought to build similar functionality for lipid::protein interactions.
 
 - Description
+  * A site built using [Quarto](https://quarto.org)
+  * FAIR data principles
+  * An interactive discovery platform intended to guide lipid research
+  * Contains data from 5 studies thus far, though framework for expanding to many more.
+  * Enables the direct comparison of different studies, and is an invaluable addition to the understanding of how proteins interact with lipids
+
+  * A summary of the data vis/download modules
+    - Each study which produced data depicted on this site has a dedicated page in which the user can explore the results published therein.
+This includes Volcano, Ranked-Order, and MA plots to visualize the probes reported.
+These plots were built using the R packages plotly and htmlwidgets to enable interactive exploration of these data[REF plotly and htmlwidgets].
+Additionally, the entirety of the data reported can be downloaded.
+    - The data from each study was then broken into the composite lipid probes -- these data are depicted on respectively-named lipid probe pages.
+Each probe page contains information about the contributing studies and is partitioned by cell type analyzed.
+
+    - Where similar study design allows, data is incorporated into a Shiny app for interactive selection of probes for exploration at [Probe vs Probe Comparisons](/LipidProbe/EnrichedHitsComparison.qmd).
+These plots incorporate linear regression analysis to describe the similarity of the datasets, and highlight proteins which were significantly enriched in one or the other dataset -- or both datasets.
+  * The site is a living document and is expected to grow as future studies utilize these functionalized lipid analogs.
 

### 2025-01-31 TrifunctionalLipidProbesOverview.qmd
eod update

@@
     embed-resources: false
+  docx:
+    fig-height: 5
+    reference-doc: custom-reference-doc.docx
+
 standalone: true
@@
 
--   The conceptual precursor to the so-called trifunctional probes, these typically include only the diazirine and the terminal alkyne moieties.
+<!-- -   The conceptual precursor to the so-called trifunctional probes, these typically include only the diazirine and the terminal alkyne moieties.
 
@@
 
--   [@haberkantFatFabulousBifunctional2014] - Haberkant et al. 2014
+-   [@haberkantFatFabulousBifunctional2014] - Haberkant et al. 2014 -->
 

### 2025-01-31 Background/ExperimentalSchemaAndAnalysis.qmd
reorganizing the background sections, text edits

--- 2025-01-30 TrifunctionalLipidProbesOverview.qmd
@@
 ---
-title: "Multifunctional Lipid Probes Background"
-author: "Gaelen Guzman"
-format: 
-  html:
-    embed-resources: false
-standalone: true
-crossref: 
-  ref-hyperlink: true
+title: "Background: Using multifunctional probes for proteomics"
 ---
-
-**This repository is still under construction, please forgive us for incomplete sections as we build features!**
-
-# Multifunctional Lipid Probes Background
-
-Functionalized lipid probes are at the intersection of several niche biotechnologies.
-This overview will serve as a summary of the capabilities, nuances, and caveats of their utility.
-Additional resources and published review articles will be referenced and linked below for greater detail.
-
-## Introduction: Why Study Lipid Interactomes?
-
-At its core, biology is a complex network of chemical interactions.
-Every biological process—from metabolism to signaling—depends on the physical interactions between molecules, including proteins, nucleic acids, and lipids.
-While proteins have long been the primary focus of interaction studies, lipids play an equally crucial yet often underappreciated role in cellular function.
-
-### Lipid-Lipid Interactions and Membrane Properties
-
-Lipids are primarily organized within membrane bilayers, where their interactions define critical membrane properties such as rigidity, fluidity, and resistance to detergents.
-By studying lipid-lipid interactomes, researchers can gain deeper insight into how these physical interactions influence membrane architecture and dynamics.
-Understanding these interactions is essential for unraveling fundamental processes like vesicle trafficking, cell signaling, and membrane compartmentalization.
-
-### Lipids as Signaling Molecules
-
-Beyond their structural roles, many lipids have been increasingly recognized as key signaling molecules.
-For example, the sphingolipid sphingosine-1-phosphate (S1P) plays a pivotal role in immune function.
-S1P binds to a specific family of receptors, triggering T cell migration (extravasation) and guiding their movement toward sites of infection.
-This highlights how lipid signaling can affect cellular behavior and physiological responses.
-
-### Lipid-Protein Interactions: Unlocking Cellular Communication
-
-A single lipid species can interact with a diverse array of proteins, influencing everything from receptor activation to intracellular signaling cascades.
-Mapping these lipid-protein interactions provides a powerful approach to understanding how lipids exert their wide-ranging effects on cellular processes.
-By deciphering lipid interactomes, researchers can uncover novel regulatory mechanisms and potentially identify new therapeutic targets in diseases where lipid signaling is dysregulated.
-
-## Synthetic Lipid Analogs: Powerful Tools for Lipid Biology
-
-The study of lipid biology has been greatly advanced by synthetic lipid analogs.
-However, it may not be immediately clear why such analogs are essential.
-Unlike proteins and nucleic acids, lipids present unique challenges that make traditional genetic tools less effective in studying their function.
-
-### Why Lipids Require a Different Approach
-
-Advances in genetic engineering—such as CRISPR and de novo gene synthesis—have revolutionized the study of nucleic acids and proteins.
-These techniques enable precise modifications, such as altering enzyme activity, redirecting proteins to different subcellular locations, modifying binding domains, and tagging proteins for visualization or isolation.
-
-In contrast, lipids present unique challenges that make genetic approaches impractical.
-Unlike proteins, which are directly encoded in DNA, lipids are synthesized enzymatically.
-Their structures cannot be modified in living cells through genetic manipulation alone.
-Traditional approaches, such as gene knockouts or knock-ins, can broadly alter lipid composition but do not allow for precise control over individual lipid species.
-
-Lipids are also much smaller than proteins, often composed of just a few dozen atoms.
-Even minor modifications can significantly alter their biophysical properties and biological function.
-Unlike proteins, which can tolerate the addition of large fluorescent or affinity tags, lipids require minimal chemical modifications to preserve their activity.
-
-Additionally, lipids exist within a highly dynamic metabolic network, where they are continuously synthesized, modified, and degraded.
-Some signaling lipids, such as sphingosine, have extremely short half-lives—sometimes only minutes—making them difficult to track in real-time.
-
-To overcome these challenges, researchers have developed synthetic lipid analogs with chemical modifications that allow for targeted investigation while preserving essential biological properties.
-The following sections detail key modifications used in functional lipid probes.
-
-### The Role of Synthetic Lipid Analogs
-
-To overcome these challenges, researchers have developed synthetic analogs of native lipids.
-These modified lipids allow for precise investigation of lipid function while preserving their essential biological properties.
-The key modifications used in this approach include:
-
-1.  Diazirine Rings – Enable covalent crosslinking to interacting proteins upon UV activation.
-2.  Terminal Alkynes – Allow for affinity enrichment using click chemistry.
-3.  Coumarin Photocages – Provide spatiotemporal control over lipid activity through light-triggered release.
-
-These modifications stabilize protein-lipid interactions and enable the selective enrichment of lipid-bound proteins, all while maintaining tight spatial and temporal control.
-Each of these tools is described in further detail below.
-
-#### Diazirine: Stabilizing Lipid-Protein Interactions with Covalent Crosslinking {#sec-DiazirinePlacement}
-
-Lipid-protein interactions are inherently transient and dynamic, making them particularly challenging to capture and study.
-Unlike protein-protein interactions, which often rely on extensive surface interfaces and hydrogen bonding, most lipids have minimal hydrogen bonding potential and lack a substantial structural framework for stable interactions.
-As a result, even biologically relevant lipid-protein contacts may be too fleeting to detect under standard biochemical conditions.
-
-To effectively identify and analyze lipid-binding proteins, it is necessary to stabilize these interactions in a way that allows their subsequent enrichment and detection.
-While affinity enrichment approaches (e.g., lipid pulldown assays) can be used, they often require detergents to solubilize membrane-associated complexes, which can introduce artifacts or disrupt weak lipid-protein interactions.
-Covalent crosslinking, on the other hand, offers a far more reliable method to “freeze” these interactions in place, preserving their native binding state even during rigorous purification steps before mass spectrometry analysis.
-
-##### Why Use Diazirine as a Crosslinking Motif?
-
-Several chemical groups can be used for covalent crosslinking, but diazirine rings are particularly well-suited for lipid studies due to their small size and minimal structural interference.
-Other crosslinking motifs may alter the lipid’s physicochemical properties, potentially changing its interaction profile.
-Diazirine, however, is the smallest known photoactivatable crosslinking group, making it an ideal choice for studying delicate lipid-protein interactions.
-
-##### Key properties of diazirine crosslinking:
-
-Lipid interactions are typically transient, as most lipids lack opportunities for strong hydrogen bonding and are too small to provide a significant binding interface.
-Identifying interacting proteins requires stabilizing these interactions to allow for enrichment and analysis.
-While affinity-based approaches can help, covalent crosslinking is the most effective method, as it enables the removal of impurities and detergents before mass spectrometry analysis.
-
-Among the various crosslinking motifs, the diazirine ring is the smallest, making it the least likely to interfere with a lipid’s natural interactions.
-Upon exposure to 355 nm UV light, the diazirine ring forms a reactive carbene radical, which rapidly covalently bonds with nearby molecules.
-This reaction is highly versatile, as the carbene can insert into carbon-hydrogen, sulfur-hydrogen, nitrogen-hydrogen, oxygen-hydrogen, or double bonds, allowing for broad coverage of potential interaction partners\[\@haberkantFatFabulousBifunctional2014\].
-
-The small size and high reactivity of diazirine crosslinking make it an invaluable tool for capturing lipid-protein interactions while minimizing perturbations to native lipid function.
-
-#### Terminal Alkyne
-
-When studying proteins, researchers often use genetic methods to tag or modify them, making them easier to visualize or isolate.
-For example, adding a green fluorescent protein (GFP) domain to a protein allows it to be seen under a fluorescence microscope, whereas incorporating an HA tag enables enrichment using antibody pulldown techniques.
-These approaches work well for proteins because they are encoded by genes and can be modified at the DNA level.
-
-Lipids, however, cannot be modified in the same way.
-Their synthesis occurs enzymatically, meaning there is no genetic sequence to alter.
-Large additions, like a GFP or HA domain, would drastically change a lipid’s properties, making it unrecognizable to the proteins and pathways that typically interact with it.
-Instead, a much smaller modification is needed—one that allows researchers to track and manipulate lipids without interfering with their biological function.
-
-##### The Terminal Alkyne: A Versatile Bioorthogonal Handle
-
-One of the smallest and most effective modifications for this purpose is the terminal alkyne.
-This functional group consists of a simple triple bond at the end of a carbon chain, a minor structural change that does not significantly alter the lipid’s behavior.
-Despite its small size, the terminal alkyne serves as a powerful chemical handle, allowing researchers to attach various probes after the lipid has been introduced into a biological system.
-
-The terminal alkyne is particularly useful because it undergoes azide-alkyne cycloaddition, a type of click chemistry reaction.
-This reaction is highly specific, rapid, and bio-orthogonal, meaning it does not interfere with natural cellular processes.
-By reacting the alkyne with an azide-containing probe, researchers can introduce fluorescent markers for imaging or affinity tags for isolating lipid-protein complexes.
-
-##### Applications in Lipid Research
-
-One major application of the terminal alkyne is fluorescence labeling.
-A functionalized lipid can be introduced into cells and later reacted with a fluorophore-conjugated azide, allowing researchers to visualize its distribution and movement under a microscope.
-This approach provides insights into lipid localization and trafficking.
-
-Another important use is affinity-based enrichment.
-Lipids containing a terminal alkyne can be captured using azide-functionalized beads, enabling the isolation of lipid-protein complexes for analysis by mass spectrometry.
-This method has been instrumental in identifying proteins that interact with specific lipid species, shedding light on lipid signaling pathways and metabolic networks.
-
-By providing a simple yet effective means of modifying lipids without disrupting their native properties, the terminal alkyne has become an essential tool in lipidomics and chemical biology.
-It bridges the gap between traditional lipid research and modern bioorthogonal chemistry, allowing for precise studies of lipid function in living systems.
-
-### Coumarin Photocage: Controlling Lipid Activity with Light
-
-Lipids play an essential role in cellular signaling, yet their biological study presents unique challenges due to their highly dynamic metabolism.
-Unlike proteins, which are relatively stable once synthesized, many bioactive lipids are continuously synthesized, modified, interconverted, and degraded as part of an extensive and tightly regulated lipid metabolic network.
-This rapid turnover makes it difficult to study the effects of a specific lipid species in isolation, as the lipid of interest may be enzymatically altered before it can exert its intended biological function.
-
-One strategy to overcome this challenge is using photocaged lipid analogs, which remain biologically inert until exposed to a specific wavelength of light.
-Irradiation with this wavelength "uncages" the analog to reveal its native structure.
-This allows researchers to control the timing and location of lipid activation, enabling targeted investigation of lipid function with high spatiotemporal resolution.
-
-#### A Light-Activated Protection Group
-
-One of the most effective tools for photocaging lipids is the coumarin cage, a photolabile protection group that can be removed upon exposure to 400 nm light.
-When attached to a lipid’s headgroup, the coumarin moiety temporarily blocks interactions with proteins, preventing the lipid from participating in its normal biological pathways.
-However, upon photoactivation, the coumarin group is cleaved, restoring the lipid to its native structure and allowing it to engage with its biological targets.
-
-This approach is useful for studying lipid-protein interactions, as uncaging the lipid in a controlled manner ensures that protein binders recognize the native lipid structure only when and where the researcher intends.
-
-#### Applications in Cellular Signaling Studies
-
-The power of coumarin-caged lipids has been demonstrated in studies examining intracellular lipid signaling.
-For example, in 2015, Högliner et al.
-used a caged sphingosine analog to investigate the role of sphingosine in calcium signaling.
-They found that upon photoactivation of the caged sphingosine, lysosomal calcium release was triggered, revealing a crucial link between sphingosine metabolism and intracellular calcium dynamics [@hoglingerIntracellularSphingosineReleases2015a].
-This discovery significantly expanded the understanding of the sphingosine signaling cascade and its downstream effects.
-
-Beyond biochemical studies, coumarin-caged lipids enable live-cell imaging approaches.
-Selectively irradiating specific subcellular regions allows the researcher to uncage lipids in a highly localized manner and assess their effects in real time.
-While this approach is not well-suited for large-scale proteomic studies, it provides a powerful method for investigating lipid function via fluorescence microscopy.
-
-#### An Additional Benefit: Coumarin’s Inherent Fluorescence
-
-A unique advantage of using coumarin as a photocaging group is its intrinsic fluorescence.
-This means that before the lipid is even uncaged, its cellular incorporation can be directly visualized using a fluorescence microscope.
-By tracking fluorescence intensity and distribution, researchers can quickly determine whether a functionalized lipid has successfully intercalated into the target cell’s membrane or accumulated in specific subcellular compartments.
-
-This dual functionality—serving as both a caging group and a fluorescent probe—makes coumarin a useful tool for studying lipid localization, uptake, and bioactivity.
-
-## Photoactivatable & Clickable Probes / Bifunctional Lipid Probes
-
--   The conceptual precursor to the so-called trifunctional probes, these typically include only the diazirine and the terminal alkyne moieties.
-
-References to include:
-
--   [@haberkantFatFabulousBifunctional2014] - Haberkant et al. 2014
-
-## Trifunctional Lipid Probes
 
@@
 ::: border
-![](SiteFigures/BaselineProteomics_ExperimentalDesign.png){group="Overview_gallery"}
+![](/Background/BaselineProteomics_ExperimentalDesign.png){group="Overview_gallery"}
 :::
@@
 
-#### Quantitative Mass Spectrometry with Tandem Mass Tagging {#sec-TMT}
+#### Quantitative Mass Spectrometry with Tandem Mass Tagging
 
@@
 **Comparison Across Samples:** Within a TMT cassette (typically 16 samples), relative protein abundance is calculated from the reporter ion intensities.
-A pooled control channel enables comparison across cassettes, allowing up to 30 samples to be analyzed in a single experiment.
+A pooled control channel enables comparison across cassettes, allowing many samples to be analyzed in a single experiment or large-scale study.
 

### 2025-01-31 Background/TrifunctionalLipidProbesOverview.qmd
reorganizing the background sections, text edits

--- 2025-01-31 TrifunctionalLipidProbesOverview.qmd
@@
 ---
-title: "Multifunctional Lipid Probes Background"
+title: "Background: Multifunctional Lipid Probes"
 author: "Gaelen Guzman"

### 2025-01-31 ContactUs/DataSubmission.qmd
reorganizing the background sections, text edits

--- 2025-01-30 DataSubmission.qmd
@@
 
-In the meantime, email us at <contact.us@LipidInteractome.org>{target="_blank"} to discuss data handoff and study details.
+In the meantime, email us at <Contact.Us@LipidInteractome.org>{target="_blank"} to discuss data handoff and study details.
 
-### Data formatting
+### Study metadata
+
+In addition to the DOI and basic details of the study, we will need additional metadata to describe how the study was performed and how the reported data were collected.
+
+In brief, we will need:
+
+* The lipid probes analyzed, and their structure if novel
+* The cell line analyzed
+* The mass spectrometry quantification method (i.e., TMT or PSM)
+* The details of mass spectrometry data acquisition (Instrument, LC gradient)
+* The details of data analysis (e.g., LIMMA analysis, ANOVA testing, etc.)
+
+### Mass spectrometry data formatting
 
@@
 * **FDR** - The false discovery rate of the protein.
+
+If only some of these data are available, reach out to us at <Contact.Us@LipidInteractome.org>{target="_blank"} to discuss the best depictions of your data.

### 2025-01-31 LipidProbe/1-10_FattyAcid.qmd
removed naughty docx formatting
reorganizing the background sections, text edits

@@
   ref-hyperlink: true # (default is true)
+html: default
 ---
@@
 
-*Greater context to the distinction between the 8-3 Fatty Acid and 1-10 Fatty Acid probes in the [Diazirine Overview](/TrifunctionalLipidProbesOverview.qmd#sec-DiazirinePlacement)*
+*Greater context to the distinction between the 8-3 Fatty Acid and 1-10 Fatty Acid probes in the [Diazirine Overview](/Background/TrifunctionalLipidProbesOverview.qmd#sec-DiazirinePlacement)*
 

### 2025-01-31 LipidProbe/EnrichedHitsComparison.qmd
reorganizing the background sections, text edits

@@
 For a select subset of the lipid probes depicted on this repository, one can directly compare their enrichment of proteins.
-In the case of the trifunctionalized PE, PA, Sph, Spa, 8-3 FA, and 1-10 FA probes, all were analyzed using quantitative mass spectrometry via [Tandem Mass Tagging](@sec-TMT).
+In the case of the trifunctionalized PE, PA, Sph, Spa, 8-3 FA, and 1-10 FA probes, all were analyzed using quantitative mass spectrometry via [Tandem Mass Tagging](/TrifunctionalLipidProbesOverview.qmd#sec-TMT).
 

### 2025-01-31 index.qmd
fleshing out overview
reorganizing the background sections, text edits

@@
 
+**This repository is still under construction, please forgive us for incomplete sections as we build features!**
+
 The goal of this site is to increase the accessibility of proteomics data utilizing multi-functionalized lipid analogs/probes to identify the lipid::protein interactions of biologically active lipids.
@@
 
-See our [Functional Lipid Probes Overview](/TrifunctionalLipidProbesOverview.qmd) for more details about how these lipid analogs are used.
+See our [Functional Lipid Probes Overview](/Background/TrifunctionalLipidProbesOverview.qmd) for more details about how these lipid analogs are used.
 

### 2025-01-31 Background/DataAnalysisAndStatistics.qmd
Reorganizing sections, increasing visibility of subsections

---
title: "Data Analysis and Statistics"
---

## TMT quantitative mass spec pipeline

* Studies included in this repository which used identical FRAG Pipe TMT pipeline:
	- Thomas et al., 2025[@thomasTrifunctionalLipidDerivatives2025]
	- Farley et al., 2024 (A)[@farleyTrifunctionalSphinganineNew2024a]
	- Farley et al., 2024 (B)[@farleyTrifunctionalFattyAcid2024]

## PSM quantitative mass spec analysis

* Studies included in this repository which used a PSM-based analysis pipeline
	- Hoglinger et al., 2017[@hoglingerTrifunctionalLipidProbes2017]
	- Muller et al., 2021[@mullerSynthesisCellularLabeling2021]

### 2025-01-31 Background/MultifunctionalLipidProbesOverview.qmd
Reorganizing sections, increasing visibility of subsections

--- 2025-01-31 TrifunctionalLipidProbesOverview.qmd
@@
     fig-height: 5
-    reference-doc: custom-reference-doc.docx
+    reference-doc: /custom-reference-doc.docx
 
@@
 
+## Limitations of multifunctionalized lipid probes
+
+* While significant effort has minimized the effect that each modification has on the biophysical properties of the lipid analogs, it remains the case that adding a diazirine and a terminal alkyne will necessarily affect their physical properties -- perhaps affecting sub-cellular localization and binding.
+* The coumarin cage has been repeatedly shown to protect lipid analogs from premature metabolism, but it should be recognized that this comes with some distinct changes to the behavior of the native lipid.
+  - For example, when a cell is treated with a photocaged lipid probe, every membrane in the cell appears to
+
 ## Interactomics Experimental schema
@@
 ::: border
-![](SiteFigures/BaselineProteomics_ExperimentalDesign.png){group="Overview_gallery"}
+![](/Background/BackgroundFigures/BaselineProteomics_ExperimentalDesign.png){group="Overview_gallery"}
 :::

### 2025-01-31 Background/ProteomicsUsingMultifunctionalProbes.qmd
Reorganizing sections, increasing visibility of subsections

--- 2025-01-31 Background/ExperimentalSchemaAndAnalysis.qmd
@@
 title: "Background: Using multifunctional probes for proteomics"
+format: 
+  html:
+    embed-resources: false
+  docx:
+    fig-height: 5
+    reference-doc: /custom-reference-doc.docx
 ---
@@
 ::: border
-![](/Background/BaselineProteomics_ExperimentalDesign.png){group="Overview_gallery"}
+![](/Background/BackgroundFigures/BaselineProteomics_ExperimentalDesign.png){group="Overview_gallery"}
 :::

### 2025-01-31 BioinformaticsApplicationNote/GG_2025_applicationNote.qmd
Reorganizing sections, increasing visibility of subsections

@@
   html:
-    embed-resources: false
+    embed-resources: true
   docx:
@@
 - Introduction
+  * In recent years, the biological roles that lipids play have garnered significant attention.
+While analyses of protein::protein interactions using proteomics has become nearly routine, it was nearly impossible to assess the protein interactors of lipids because of their small size and sensitive biophysical properties.
+However, the advent of multifunctionalized lipid analogs (lipid probes) has the potential to spur a revolution in the study of bioactive lipids.
+Numerous studies have reported the "interactome" of select lipid species using these lipid probes, though no resource to date has amassed these results for centralized comparison.
+We present here the LipidInteractome repository as a tool to enable lipid biologists to explore and compare the protein interactors of a variety of biologically interesting lipids.
+
   * What is this repository for?
@@
   * FAIR data principles
+    - *Findable:* We sought to create a platform to centralize the studies of this type.
+The site is organized such that one can interact with the results of individual published studies or explore the combined results of all studies which investigated a given lipid.
+Because this site is a living document, we invite researchers to contribute their results by contacting us with the details delineated at our [Data Submission](/ContactUs/DataSubmission.qmd) page.
+    - *Accessible:* To enhance the accessibility of these data, we have made the results of all studies and lipid probes downloadable in .csv format.
+We have provided a [detailed overview of the data production and analysis](/Background/ProteomicsUsingMultifunctionalProbes.qmd), a description of the content in all columns, and a [nuanced discussion about the limitations of these probes](/Background/MultifunctionalLipidProbesOverview.qmd).
+To maximize the reliability of each reported interactome, we have focused on amassing only peer-reviewed proteomics results.
+    - *Interoperable:* We have sought to coordinate the formatting of the data collected from a variety of research teams.
+While many studies utilized identical data analysis pipelines, some of our included publications used distinct mass spectrometry protocols and we have attempted to provide a parallel data structure and visualization -- while also [explaining the differences in methodology](/Background/ProteomicsUsingMultifunctionalProbes.qmd).
+    - *Reusable:* We have provided extensive documentation on the production, analyses, and caveats of these data; in these documentations, we have sought to limit technical language and to give these results an accessible interpretation.
+Additionally, we have referenced numerous publications which go into much greater depth on the synthesis of these lipid probes and the methodology used in each proteomics analysis.
   * An interactive discovery platform intended to guide lipid research

### 2025-01-31 ContactUs/about.qmd
Reorganizing sections, increasing visibility of subsections

---
title: "About"
---

This repository is still under construction (as you can probably tell). Someday soon this page will have details about the founders of this resource, as well as a data submission form. Until then, please contact the site administrators for additional information about protocols, experimental design, and website feedback:

 <contact.us@LipidInteractome.org>{target="_blank"}

<br>
<hr>

### Github repository

This site was written by Gaelen Guzman and was built using Quarto. Find out more about Quarto [here](https://quarto.org){target="_blank"}.

This site can be pulled from GitHub at: <https://github.com/gaelenDG/LipidInteractomics_Website>

### Site structure

::::{.callout-note collapse="true"}

<!-- Run this to get a tree of the file structure, need to do some research on how this is depicted or if this is necessary -->
```{r setup, include=FALSE, echo=FALSE}
library(fs)

tree <- fs::dir_tree(path = ".", recurse = TRUE, depth = 3) |>
  stringr::str_subset("(^\\.|_site/|\\.git|\\.Rproj|\\.quarto|\\.cache)", negate = TRUE)

```

_site                                                
	├── 404.html                                         
	├── Background                                       
	│   ├── BackgroundFigures                            
	│   │   └── BaselineProteomics_ExperimentalDesign.png
	│   ├── BaselineProteomics_ExperimentalDesign.png    
	│   ├── DataAnalysisAndStatistics.html               
	│   ├── MultifunctionalLipidProbesOverview.html      
	│   └── ProteomicsUsingMultifunctionalProbes.html                
	├── ContactUs                                        
	│   ├── DataSubmission.html                          
	│   └── about.html                                   
	├── IndividualStudies                                
	│   ├── AT_2025.html                                 
	│   ├── DH_2017.html                                 
	│   ├── RM_2021.html                                 
	│   ├── SF_2024.html                                 
	│   ├── SF_2024_B.html                               
	│   └── StudyOverview.html                           
	├── LipidProbe                                       
	│   ├── 1-10_FattyAcid.html                          
	│   ├── 8-3_FattyAcid.html                           
	│   ├── Diacylglycerol.html                          
	│   ├── EnrichedHitsComparison.html                  
	│   ├── FormattingTemplate.html                      
	│   ├── PhosphatidicAcid.html                        
	│   ├── Phosphatidylethanolamine.html                
	│   ├── PhosphatidylinositolBisphosphate.html        
	│   ├── PhosphatidylinositolTrisphosphate.html       
	│   ├── Sphinganine.html                             
	│   ├── Sphingosine.html                             
	│   └── Structures                                   
	│       ├── 1-10_FattyAcid_Structure.png             
	│       ├── 8-3_FattyAcid_Structure.png              
	│       ├── PIP3_Structure.png                       
	│       ├── PhosphatidicAcid_Structure.png           
	│       ├── PhosphatidylethanolamineStructure.png    
	│       ├── SphinganineStructure.png                 
	│       └── SphingosineStructure.png                 
	├── MaintenanceInstructions.html                     
	├── Resources                                        
	│   └── styles.css                                   
	├── index.html

::::

### 2025-01-31 LipidProbe/1-10_FattyAcid.qmd
Reorganizing sections, increasing visibility of subsections

@@
 
+*Greater context to the distinction between the 8-3 Fatty Acid and 1-10 Fatty Acid probes can be found in the [Diazirine Overview](/Background/MultifunctionalLipidProbesOverview.qmd#sec-DiazirinePlacement)*
+
 ## Structure
@@
 :::
-
-*Greater context to the distinction between the 8-3 Fatty Acid and 1-10 Fatty Acid probes in the [Diazirine Overview](/Background/TrifunctionalLipidProbesOverview.qmd#sec-DiazirinePlacement)*
 

### 2025-01-31 LipidProbe/EnrichedHitsComparison.qmd
Reorganizing sections, increasing visibility of subsections

--- 2025-01-30 LipidProbe/EnrichedHitsComparison.qmd
@@
 For a select subset of the lipid probes depicted on this repository, one can directly compare their enrichment of proteins.
-In the case of the trifunctionalized PE, PA, Sph, Spa, 8-3 FA, and 1-10 FA probes, all were analyzed using quantitative mass spectrometry via [Tandem Mass Tagging](@sec-TMT).
+In the case of the trifunctionalized PE, PA, Sph, Spa, 8-3 FA, and 1-10 FA probes, all were analyzed using quantitative mass spectrometry via [Tandem Mass Tagging](/Background/MultifunctionalLipidProbesOverview.qmd#sec-TMT).
 

### 2025-01-31 index.qmd
Reorganizing sections, increasing visibility of subsections

@@
   html:
-    embed-resources: false
-standalone: false
+    embed-resources: true
+standalone: true
 ---
@@
 
-See our [Functional Lipid Probes Overview](/Background/TrifunctionalLipidProbesOverview.qmd) for more details about how these lipid analogs are used.
+See our [Functional Lipid Probes Overview](/Background/MultifunctionalLipidProbesOverview.qmd) for more details about how these lipid analogs are used.
 

### 2025-01-31 LipidProbe/EnrichedHitsComparison.qmd
eod update, messing around with 3d plots

@@
 Pulling the enriched hits from each probe, then making a long dataframe that can be plopped into a Venn diagram adjacent visualization -->
-```{r setup, echo=FALSE,include=FALSE}
+```{r setup, echo=FALSE, include=FALSE}
 library(dplyr)

### 2025-01-31 LipidProbe/3-DplotExample_Sandbox.R

@@ -1,0 +1,178 @@
+library(dplyr)
+library(tidyr)
+library(ggplot2)
+library(plotly)
+library(readr)
+library(shiny)
+
+df <- read_csv("LipidProbe/DataSets/LipidInteractomics_ShinyApp/combinedProbeDatasets_TMT.csv")
+
+
+probeOptions <- unique(df$LipidProbe)
+
+
+
+ProbeVSProbePlotter <- function(data, probe1Name, probe2Name, probe3Name) {
+
+	
+
+	limits <- max(abs(max(data$logFC.x, na.rm = TRUE)),
+							abs(max(data$logFC.y, na.rm = TRUE)),
+							abs(max(data$logFC.z, na.rm = TRUE)))
+
+	ggplotter <- data |>
+			ggplot(aes(x = logFC.x,
+								 y = logFC.y,
+								 color = factor(combined_hit_annotation),
+								 fill = factor(combined_hit_annotation),
+								 shape = factor(combined_hit_annotation),
+								 size = factor(combined_hit_annotation),
+								 alpha = factor(combined_hit_annotation))) +
+			geom_point(aes(text = paste0("Gene name: ", gene_name))) +
+			geom_hline(yintercept = 0, linetype = 2) +
+			geom_vline(xintercept = 0, linetype = 2) +
+			scale_x_continuous(limits= c(-1.1*limits, 1.1*limits)) +
+			scale_y_continuous(limits= c(-1.1*limits, 1.1*limits)) +
+			scale_shape_manual(values = c("enriched on neither axis" = 22, 
+																		"enriched x-axis only" = 24,
+																		"enriched y-axis only" = 24,
+																		"enriched on both axes" = 21),
+													name = "Statistical Annotation") +
+			scale_fill_manual(values=c("enriched on neither axis" = "grey50", 
+																	"enriched x-axis only" = "purple",
+																	"enriched y-axis only" = "green",
+																	"enriched on both axes" = "orange"),
+												name = "Statistical Annotation") +
+			scale_color_manual(values = c("enriched on neither axis" = "black", 
+																		"enriched x-axis only" = "black",
+																		"enriched y-axis only" = "black",
+																		"enriched on both axes" = "black"),
+													name = "Statistical Annotation") +
+			scale_size_manual(values = c("enriched on neither axis" = 2, 
+																		"enriched x-axis only" = 4,
+																		"enriched y-axis only" = 4,
+																		"enriched on both axes" = 4),
[…]

### 2025-01-31 LipidProbe/DataSets/LipidInteractomics_ShinyApp/app.R

@@ -6,7 +6,7 @@ library(readr)
 library(shiny)
 
 # File path for testing
-df <- read_csv("/LipidProbe/DataSets/LipidInteractomics_ShinyApp/combinedProbeDatasets_TMT.csv")
+df <- read_csv("LipidProbe/DataSets/LipidInteractomics_ShinyApp/combinedProbeDatasets_TMT.csv")
 
 # File path for deploying to Shinyapps.io
 #df <- read_csv("combinedProbeDatasets_TMT.csv")
@@ -20,10 +20,13 @@ ui <- fluidPage(
   sidebarLayout(
     sidebarPanel(
       selectInput("probe1", "Select First LipidProbe:", choices = probeOptions, selected = probeOptions[1]),
-      selectInput("probe2", "Select Second LipidProbe:", choices = probeOptions, selected = probeOptions[2])
+      selectInput("probe2", "Select Second LipidProbe:", choices = probeOptions, selected = probeOptions[2]),
+			selectInput("probe3", "Select Third LipidProbe (Beta):", choices = probeOptions, selected = probeOptions[3])
     ),
     mainPanel(
-      plotlyOutput("logFCPlot")
+      plotlyOutput("logFCPlot"),
+
+			plotlyOutput("logFCPlot3dDemo")
     )
   )
 )
@@ -41,6 +44,12 @@ server <- function(input, output, session) {
 		yData <- df |>
 			filter(LipidProbe == input$probe2) 
 		return(yData)
+	})
+
+	zData <- reactive({
+		zData <- df |>
+			filter(LipidProbe == input$probe3) 
+		return(zData)
 	})
 
 	# The output call for making the plot - includes some data wrangling to make sure the selected probes are handled properly. A
@@ -78,6 +87,103 @@ server <- function(input, output, session) {
 
 		ProbeVSProbePlotter(plot_data, probe1Name, probe2Name)
     
+  })
+
+	output$logFCPlot3dDemo <- renderPlotly({
+
+		# Isolating the probes selected by the user
+		probe1Name <- input$probe1
+		probe2Name <- input$probe2
+		probe3Name <- input$probe3
+
+		# Create a new dataframe for plotting
+		xData <- xData()
+		yData <- yData()
+		zData <- zData()
+    
+		# handles the NAs by placing them on the appropriate axes.
+		plot_data <- xData |> 
+			full_join(yData, by="gene_name") |>
+			full_join(zData, by="gene_name") |>
[…]

### 2025-02-03 BioinformaticsApplicationNote/GG_2025_applicationNote.qmd
Minor updates

@@
   - name: "Fikadu Tafesse"
-    affiliation: "Oregon Health & Science University"
+    affiliations:
+      - name:  "Oregon Health & Science University"
+        address: 3222 SW Research Dr
+        city: Portland
+        state: OR
+        postal-code: 97239
     orcid: 0000-0002-8575-4164
   - name: "Carsten Schultz"
-    affiliation: "Oregon Health & Science University"
+    affiliations:
+      - name:  "Oregon Health & Science University"
+        address: 3222 SW Research Dr
+        city: Portland
+        state: OR
+        postal-code: 97239
     orcid: 0000-0002-5824-2171
   - name: "Gaelen Guzman"
-    affiliation: "Oregon Health & Science University"
+    affiliations:
+      - name:  "Oregon Health & Science University"
+        address: 3222 SW Research Dr
+        city: Portland
+        state: OR
+        postal-code: 97239
     orcid: 0000-0002-7696-6034
@@
     fig-height: 5
-    reference-doc: custom-reference-doc.docx
+    reference-doc: /Users/gaelenguzman/LipidInteractomics_Website_local/LipidInteractomics_Website/Resources/custom-reference-doc.docx
 page-navigation: false
@@
 - Description
-  * A site built using [Quarto](https://quarto.org)
+  * A site built using [Quarto](https://quarto.org). The R scripts which define the rendered figures is embedded in the source material for each page.
   * FAIR data principles
@@
     - Where similar study design allows, data is incorporated into a Shiny app for interactive selection of probes for exploration at [Probe vs Probe Comparisons](/LipidProbe/EnrichedHitsComparison.qmd).
-These plots incorporate linear regression analysis to describe the similarity of the datasets, and highlight proteins which were significantly enriched in one or the other dataset -- or both datasets.
+These plots incorporate linear regression analysis to describe the similarity of the datasets, and highlight proteins which were significantly enriched in one or the other dataset -- or in both datasets.
+We seek for this functionality to enable researchers to identify targets of interest when studying bioactive lipids.
   * The site is a living document and is expected to grow as future studies utilize these functionalized lipid analogs.
+We have prepared a [Data Submission page](/ContactUs/DataSubmission.qmd) for any researchers with similar datasets who wish to contribute to this repository.
+
+- Discussion
+  *	What we hope this resource enables researchers to do
+  *	Longevity – this site is designed to expand with the acquisition of this types of proteomics analyses
 
 - Acknowledgements
+  * Andre Nadler
+  * Frank Stein
+  * Per Haberkant
+  *
+
+- Conflicts of Interest
+  * None
+
+- References

### 2025-02-03 LipidProbe/DataSets/LipidInteractomics_ShinyApp/app.R

@@ -141,11 +141,11 @@ server <- function(input, output, session) {
 
 		# Corrected opacity mapping (now properly ordered)
 		plot_data$opacity <- case_when(
-			plot_data$combined_hit_annotation == "enriched on all axes" ~ 1.0,
-			plot_data$combined_hit_annotation %in% c("enriched on x- and y- axes", "enriched on x- and z- axes", "enriched on y- and z- axes") ~ 0.75,
-			plot_data$combined_hit_annotation %in% c("enriched x-axis only", "enriched y-axis only", "enriched z-axis only") ~ 0.5,
-			plot_data$combined_hit_annotation == "enriched on no axes" ~ 0.25,
-			TRUE ~ 0.25 # Default case
+			plot_data$combined_hit_annotation == "enriched on all axes" ~ 0.25,
+			plot_data$combined_hit_annotation %in% c("enriched on x- and y- axes", "enriched on x- and z- axes", "enriched on y- and z- axes") ~ 0.5,
+			plot_data$combined_hit_annotation %in% c("enriched x-axis only", "enriched y-axis only", "enriched z-axis only") ~ 0.75,
+			plot_data$combined_hit_annotation == "enriched on no axes" ~ 1.0,
+			TRUE ~ 0.75 # Default case
 		)
 		# Define color mapping similar to ggplot
 		color_mapping <- c(

### 2025-02-04 BioinformaticsApplicationNote/GG_2025_applicationNote.qmd
Pre-weekly meeting commit

@@
     corresponding: true
-    email: gaelenguzman@lipidinteractome.org
+    email: gaelen.guzman@lipidinteractome.org
 format:
@@
 
-## Outline
+## Summary
+### Abstract
+Lipid probes are a recent advent of lipid biology which allow for the identification of lipid::protein interactions.
+A growing number of lipid interactomes have been published, but there has not yet been an effort to coordinate or compare the findings between such studies.
+The LipidInteractome is an effort to expand the findability, accessibility, interoperability, and reproducibility of these studies according to the FAIR principles [REF <https://www.go-fair.org/fair-principles/>].
+This site seeks to enable researchers to explore the biological function of lipids by interrogating their protein interaction partners.
 
-- Abstract
-  * Summary
-    - Lipid probes are a recent advent of lipid biology which allow for the identification of lipid::protein interactions.
-A growing number of lipid interactomes have been published, but there has not yet been an effort to coordinate or compare the findings between such studies.
-The LipidInteractome is an effort to expand the findability, accessibility, interoperability, and reproducibility of these studies according to the FAIR principles [REF https://www.go-fair.org/fair-principles/].
-This site seeks to enable researchers to explore the biological function of lipids by interrogating their protein interaction partners.
-  * Availability: This site can be viewed at [LipidInteractome.org](lipidinteractome.org); all data is available for download.
-  * Data Submission: If you would like to submit a relevant dataset, see our [Data Submission Page](https://www.lipidinteractome.org/DataSubmission.html) for details, contact info, and instructions.
+### Availability
+This site can be viewed at [LipidInteractome.org](lipidinteractome.org); all data is available for download.
 
-- Introduction
+### Data Submission
+If you would like to submit a relevant dataset, see our [Data Submission Page](https://www.lipidinteractome.org/DataSubmission.html) for details, contact info, and instructions.
+
+## Introduction
 * In recent years, the biological roles that lipids play have garnered significant attention.
-While analyses of protein::protein interactions using proteomics has become nearly routine, it was nearly impossible to assess the protein interactors of lipids because of their small size and sensitive biophysical properties.
-However, the advent of multifunctionalized lipid analogs (lipid probes) has the potential to spur a revolution in the study of bioactive lipids.
+While analyses of protein::protein interactions using proteomics has become nearly routine, it was very nearly impossible to assess the protein interactors of lipids because of their small size and sensitive biophysical properties.
+However, the advent of synthetic, multifunctionalized lipid analogs (lipid probes) has the potential to spur a revolution in the study of bioactive lipids.
 Numerous studies have reported the "interactome" of select lipid species using these lipid probes, though no resource to date has amassed these results for centralized comparison.
 We present here the LipidInteractome repository as a tool to enable lipid biologists to explore and compare the protein interactors of a variety of biologically interesting lipids.
+* This growing family of multifunctionalized lipid probes incorporates two to three of the following synthetic chemical additions: (1) A diazirine ring, which enables photoactivatable crosslinking to stabilize lipid::protein interactions upon irradiation with 355 nm light; (2) A terminal alkyne, which enables post-hoc azide cycloaddition (click chemistry) to affix an affinity handle for enrichment; and (3) A coumarin photocage, which protects the lipid analog from premature enzymatic modification until the sample is irradiated with 405 nm light (present only in the so-called "trifunctional" lipid probes) [@haberkantFatFabulousBifunctional2014; @schultzChemicalToolsLipid2023; @farleyTrifunctionalSphinganineNew2024a].
+* This repository serves as a centralized point for access, interactive exploration, and download of publicly-available proteomics datasets utilizing multifunctionalized lipid analogs to identify the protein interactors of select bioactive lipids.
+At present, analyses of trifunctionalized phosphatidic acid, phosphatidylethanolamine, sphingosine, and sphinganine are presented in our repository, with the interactomes of either HeLa or Huh7 cells[@thomasTrifunctionalLipidDerivatives2025; @farleyTrifunctionalSphinganineNew2024a].
+Additionally, we have presented the results of two fatty acid probes which serves as a control for non-specific lipid-binding proteins[@farleyTrifunctionalFattyAcid2024].
+* Previously, there was no centralized repository for lipid interactions data.
+This database enables comparative analysis of the interactomes of these lipid probes, significantly reducing the barriers to target selection for researchers who seek to explore the signaling roles that lipids such as sphingosine, phosphatidylethanolamine, and diacylglycerol play throughout the cell.
 
-  * What is this repository for?
-  * Why did we make it?
-  * Who will benefit from it?
-  * Are there alternatives?
-    - No, there is no centralized repository for lipid interactions data -- the [BioPlex](https://bioplex.hms.harvard.edu) web platform serves as an excellent repository for protein::protein interactions and we have sought to build similar functionality for lipid::protein interactions.
+## Description
 
-- Description
+### Overview
 * A site built using [Quarto](https://quarto.org). The R scripts which define the rendered figures is embedded in the source material for each page.
-  * FAIR data principles
+* An interactive discovery platform intended to guide lipid research
+* Contains data from 5 studies thus far, though framework for expanding to many more.
+* Enables the direct comparison of different studies, and is an invaluable addition to the understanding of how proteins interact with lipids
+* The site is a living document and is expected to grow as future studies utilize these functionalized lipid analogs.
+We have prepared a [Data Submission page](/ContactUs/DataSubmission.qmd) for any researchers with similar datasets who wish to contribute to this repository.
+
+### FAIR data principles
 - *Findable:* We sought to create a platform to centralize the studies of this type.
@@
 Additionally, we have referenced numerous publications which go into much greater depth on the synthesis of these lipid probes and the methodology used in each proteomics analysis.
-  * An interactive discovery platform intended to guide lipid research
-  * Contains data from 5 studies thus far, though framework for expanding to many more.
-  * Enables the direct comparison of different studies, and is an invaluable addition to the understanding of how proteins interact with lipids
 
-  * A summary of the data vis/download modules
+### A summary of the data vis/download modules
 - Each study which produced data depicted on this site has a dedicated page in which the user can explore the results published therein.
@@
 Additionally, the entirety of the data reported can be downloaded.
+
 - The data from each study was then broken into the composite lipid probes -- these data are depicted on respectively-named lipid probe pages.
 Each probe page contains information about the contributing studies and is partitioned by cell type analyzed.
+In the future, we intend to enable the user to perform comparisons between the interactomes of different cell types with the same lipid probe.
 
@@
 We seek for this functionality to enable researchers to identify targets of interest when studying bioactive lipids.
-  * The site is a living document and is expected to grow as future studies utilize these functionalized lipid analogs.
-We have prepared a [Data Submission page](/ContactUs/DataSubmission.qmd) for any researchers with similar datasets who wish to contribute to this repository.
 
-- Discussion
-  *	What we hope this resource enables researchers to do
-  *	Longevity – this site is designed to expand with the acquisition of this types of proteomics analyses
+## Discussion
+*	What we hope this resource enables researchers to do:
+  - Explore previously-published results and guide ongoing research.
+  - Orthogonally verify and characterize the interactions of bioactive lipid species and enriched proteins.
+*	Longevity – this site is designed to expand as more researchers utilize functionalized lipid probes as targets for interactomics. 
+  * We plan to incorporate a section for each lipid interactome in which validating studies may be referenced -- allowing rapid cross-referencing of research which has already been done. 
+  * Data submission - with the provided [data submission format](/ContactUs/DataSubmission.qmd), researchers can submit their data for inclusion in this database.
 
-- Acknowledgements
+## Acknowledgements
 * Andre Nadler
@@
 
-- Conflicts of Interest
-  * None
-
-- References
+## Conflicts of Interest
+The authors have no conflicts of interest to declare.

### 2025-02-05 BioinformaticsApplicationNote/GG_2025_applicationNote.qmd
minor updates to manuscript before meeting
Edits to manuscript, working on adding more metadata to downloads.

--- 2025-01-31 BioinformaticsApplicationNote/GG_2025_applicationNote.qmd
@@
 ---
-title: "Lipid Interactomics Repository"
-subtitle: "An interactive and open access platform for exploring multifunctional lipid interactomes"
+title: "The Lipid Interactome"
+subtitle: "An interactive and open access platform for exploring cellular lipid-protein interactomes"
+date: 2025-02-04
+keywords:
+  - Lipid-protein interactions
+  - Proteomics
+  - Interactomics
+  - Database
+  - Multifunctionalized lipids
+
+copyright:
+  holder: "Gaelen Guzman"
+  year: 2025
 authors:
   - name: "Fikadu Tafesse"
-    affiliation: "Oregon Health & Science University"
+    affiliations:
+      - name:  "Oregon Health & Science University"
+        address: 3222 SW Research Dr
+        city: Portland
+        state: OR
+        postal-code: 97239
     orcid: 0000-0002-8575-4164
   - name: "Carsten Schultz"
-    affiliation: "Oregon Health & Science University"
+    affiliations:
+      - name:  "Oregon Health & Science University"
+        address: 3222 SW Research Dr
+        city: Portland
+        state: OR
+        postal-code: 97239
     orcid: 0000-0002-5824-2171
   - name: "Gaelen Guzman"
-    affiliation: "Oregon Health & Science University"
+    affiliations:
+      - name:  "Oregon Health & Science University"
+        address: 3222 SW Research Dr
+        city: Portland
+        state: OR
+        postal-code: 97239
     orcid: 0000-0002-7696-6034
     corresponding: true
-    email: gaelenguzman@lipidinteractome.org
+    email: gaelen.guzman@lipidinteractome.org
 format:
@@
     fig-height: 5
-    reference-doc: custom-reference-doc.docx
+    reference-doc: /Users/gaelenguzman/LipidInteractomics_Website_local/LipidInteractomics_Website/Resources/custom-reference-doc.docx
 page-navigation: false
-
 ---
 
-## Outline
+## Summary
 
-- Abstract
-  * Summary
-    - Lipid probes are a recent advent of lipid biology which allow for the identification of lipid::protein interactions.
-A growing number of lipid interactomes have been published, but there has not yet been an effort to coordinate or compare the findings between such studies.
-The LipidInteractome is an effort to expand the findability, accessibility, interoperability, and reproducibility of these studies according to the FAIR principles [REF https://www.go-fair.org/fair-principles/].
-This site seeks to enable researchers to explore the biological function of lipids by interrogating their protein interaction partners.
-  * Availability: This site can be viewed at [LipidInteractome.org](lipidinteractome.org); all data is available for download.
-  * Data Submission: If you would like to submit a relevant dataset, see our [Data Submission Page](https://www.lipidinteractome.org/DataSubmission.html) for details, contact info, and instructions.
+### Abstract
 
-- Introduction
-  * In recent years, the biological roles that lipids play have garnered significant attention.
-While analyses of protein::protein interactions using proteomics has become nearly routine, it was nearly impossible to assess the protein interactors of lipids because of their small size and sensitive biophysical properties.
-However, the advent of multifunctionalized lipid analogs (lipid probes) has the potential to spur a revolution in the study of bioactive lipids.
-Numerous studies have reported the "interactome" of select lipid species using these lipid probes, though no resource to date has amassed these results for centralized comparison.
-We present here the LipidInteractome repository as a tool to enable lipid biologists to explore and compare the protein interactors of a variety of biologically interesting lipids.
+Lipid–protein interactions play essential roles in cellular signaling and membrane dynamics, yet their systematic characterization has long been hindered by the inherent biochemical properties of lipids.
+Recent advances in functionalized lipid probes -- equipped with photoactivatable crosslinkers, affinity handles, and photocleavable protecting groups -- have enabled proteomics-based identification of lipid interacting proteins with unprecedented specificity and resolution.
+Despite the growing number of published lipid interactomes, there remains no centralized effort to harmonize, compare, or integrate these datasets.
 
-  * What is this repository for?
-  * Why did we make it?
-  * Who will benefit from it?
-  * Are there alternatives?
-    - No, there is no centralized repository for lipid interactions data -- the [BioPlex](https://bioplex.hms.harvard.edu) web platform serves as an excellent repository for protein::protein interactions and we have sought to build similar functionality for lipid::protein interactions.
+The Lipid Interactome addresses this gap by providing a structured, interactive site that adheres to FAIR data principles -- ensuring that lipid interactome studies are Findable, Accessible, Interoperable, and Reusable.
+Through standardized data formatting, interactive visualizations, and direct cross-study comparisons, this resource enables researchers to systematically explore the protein-binding partners of diverse bioactive lipids.
+By consolidating and curating lipid interactome proteomics data from multiple studies, the Lipid Interactome database serves as a critical tool for deciphering the biological functions of lipids in cellular systems.
 
-- Description
-  * A site built using [Quarto](https://quarto.org)
-  * FAIR data principles
-    - *Findable:* We sought to create a platform to centralize the studies of this type.
-The site is organized such that one can interact with the results of individual published studies or explore the combined results of all studies which investigated a given lipid.
-Because this site is a living document, we invite researchers to contribute their results by contacting us with the details delineated at our [Data Submission](/ContactUs/DataSubmission.qmd) page.
-    - *Accessible:* To enhance the accessibility of these data, we have made the results of all studies and lipid probes downloadable in .csv format.
-We have provided a [detailed overview of the data production and analysis](/Background/ProteomicsUsingMultifunctionalProbes.qmd), a description of the content in all columns, and a [nuanced discussion about the limitations of these probes](/Background/MultifunctionalLipidProbesOverview.qmd).
-To maximize the reliability of each reported interactome, we have focused on amassing only peer-reviewed proteomics results.
-    - *Interoperable:* We have sought to coordinate the formatting of the data collected from a variety of research teams.
-While many studies utilized identical data analysis pipelines, some of our included publications used distinct mass spectrometry protocols and we have attempted to provide a parallel data structure and visualization -- while also [explaining the differences in methodology](/Background/ProteomicsUsingMultifunctionalProbes.qmd).
-    - *Reusable:* We have provided extensive documentation on the production, analyses, and caveats of these data; in these documentations, we have sought to limit technical language and to give these results an accessible interpretation.
-Additionally, we have referenced numerous publications which go into much greater depth on the synthesis of these lipid probes and the methodology used in each proteomics analysis.
-  * An interactive discovery platform intended to guide lipid research
-  * Contains data from 5 studies thus far, though framework for expanding to many more.
-  * Enables the direct comparison of different studies, and is an invaluable addition to the understanding of how proteins interact with lipids
+### Availability
 
-  * A summary of the data vis/download modules
-    - Each study which produced data depicted on this site has a dedicated page in which the user can explore the results published therein.
-This includes Volcano, Ranked-Order, and MA plots to visualize the probes reported.
-These plots were built using the R packages plotly and htmlwidgets to enable interactive exploration of these data[REF plotly and htmlwidgets].
-Additionally, the entirety of the data reported can be downloaded.
-    - The data from each study was then broken into the composite lipid probes -- these data are depicted on respectively-named lipid probe pages.
-Each probe page contains information about the contributing studies and is partitioned by cell type analyzed.
+This site can be viewed at [LipidInteractome.org](lipidinteractome.org) all data is available for download. No user information is collected or necessary for data navigation and interaction.
 
-    - Where similar study design allows, data is incorporated into a Shiny app for interactive selection of probes for exploration at [Probe vs Probe Comparisons](/LipidProbe/EnrichedHitsComparison.qmd).
-These plots incorporate linear regression analysis to describe the similarity of the datasets, and highlight proteins which were significantly enriched in one or the other dataset -- or both datasets.
-  * The site is a living document and is expected to grow as future studies utilize these functionalized lipid analogs.
+### Data Submission
 
-- Acknowledgements
+If you would like to submit a relevant dataset, see our [Data Submission Page](https://www.lipidinteractome.org/DataSubmission.html) for details, contact info, and instructions.
+
+### Keywords
+
+Lipid-protein interactions, proteomics, interactomics, database, multifunctionalized lipids
+
+## Introduction
+
+Lipids are more than passive structural components of cellular membranes—they are active participants in signaling pathways, cellular homeostasis, organellar communications, and membrane dynamics.
+Despite their critical biological roles, lipid–protein interactions have historically been challenging to study.
+The small size and biophysical properties of lipids make conventional proteomics approaches unsuitable for mapping their interactors.
+Unlike proteins, which can be readily tagged or immobilized for affinity-based interaction studies, lipids require specialized chemical modifications to enable selective and controlled interaction profiling.
+
+Recent advances in developing multifunctionalized lipid analogs have revolutionized the field, enabling the systematic interrogation of lipid interactomes.
+These probes incorporate strategically designed functional groups that enable covalent crosslinking, affinity enrichment, and controlled activation.
+Most commonly, these include: (1) a diazirine ring for photoactivatable crosslinking upon exposure to 355 nm UV light, stabilizing lipid–protein interactions; (2) a terminal alkyne, permitting click chemistry-based enrichment; and, in some cases, (3) a coumarin photocage, which shields the lipid probe from premature enzymatic modification until selectively released by 405 nm light.
+Together, these modifications enable direct proteomic identification of lipid interactors, distinguishing true binding partners from transient or non-specific associations[@haberkantFatFabulousBifunctional2014; @schultzChemicalToolsLipid2023; @farleyTrifunctionalSphinganineNew2024a].
+
+Several studies have already employed these lipid probes to elucidate the interactomes of key bioactive lipids, including diacylglycerol, sphingosine, sphinganine, phosphatidic acid, and phosphatidylethanolamine[@hoglingerTrifunctionalLipidProbes2017; @farleyTrifunctionalSphinganineNew2024a; @farleyTrifunctionalFattyAcid2024; @thomasTrifunctionalLipidDerivatives2025].
+These studies have followed a comparative proteomics workflow, wherein crosslinked (“+UV”) and non-crosslinked (“-UV”) samples are analyzed side by side to minimize artifacts and confirm specificity[@haberkantFatFabulousBifunctional2014; @schultzChemicalToolsLipid2023].
+However, despite the growing number of lipid interactome datasets, no centralized resource has existed to compile, compare, and standardize these findings.
+
+To address this gap, we present the Lipid Interactome database -- a curated repository designed to facilitate the comparative analysis of lipid–protein interactions from multiple studies.
+This resource consolidates proteomics data from multifunctional lipid probes, enabling researchers to efficiently explore and contextualize lipid-binding proteins across different lipid species and cellular models.
+Currently, the repository hosts interactomes derived from trifunctionalized phosphatidic acid, phosphatidylethanolamine, sphingosine, and sphinganine in HeLa and Huh7 cells[@thomasTrifunctionalLipidDerivatives2025; @farleyTrifunctionalSphinganineNew2024a].
+Additionally, it includes control datasets from two fatty acid probes to distinguish specific from non-specific lipid-binding proteins[@farleyTrifunctionalFattyAcid2024].
+
+By providing a centralized platform for lipid interactome data, the Lipid Interactome significantly lowers the barriers to entry for researchers investigating lipid signaling pathways.
+This repository represents a necessary step toward systematizing lipid–protein interaction studies, ensuring that bioactive lipids are afforded the same level of proteomic scrutiny as their protein counterparts.
+
+## Description
+
+### Overview
+
+The Lipid Interactome is an interactive discovery platform built using Quarto, designed to centralize and enhance the study of lipid–protein interactions through curated datasets and dynamic visualization tools.
+Each page seamlessly integrates R-generated figures, embedding scripts directly into the source material to ensure reproducibility and transparency.
+The repository currently hosts data from five published studies, with an expandable framework that supports the incorporation of future datasets as the field progresses.
+
+At its core, the Lipid Interactome enables the direct comparison of lipid interactomes across studies, providing researchers with invaluable insights into the diverse roles that bioactive lipids play in cellular processes.
+By leveraging standardized data formatting and interactive visualization—including study-specific analysis pages, lipid probe aggregation, and cross-study comparisons via a Shiny application—the platform facilitates intuitive exploration of protein–lipid interactions.
+As a living repository, we actively encourage researchers to contribute their findings through our [Data Submission](#) page, ensuring that this resource continues to evolve alongside advancements in lipidomics research.
+
+### FAIR data principles
+
+The Lipid Interactome database was developed with the FAIR (Findable, Accessible, Interoperable, and Reusable) data principles in mind, ensuring that lipid–protein interaction data can be systematically explored, compared, and reused by the research community.
+Given the historical inconsistency in proteomics data curation, we have taken deliberate steps to standardize, annotate, and document our datasets for maximum utility.
+
+#### Findable
+
+To address the fragmented nature of lipid interactome studies, we have established a centralized platform where researchers can interact with the results of individual studies or explore aggregated findings across multiple studies on a given lipid.
+The repository is structured to facilitate intuitive navigation between experimental datasets, offering clear entry points for study-specific and lipid-specific analyses.
+Because this resource is intended as a living repository, we actively invite researchers to contribute their findings following the submission guidelines detailed on our [Data Submission](https://www.lipidinteractome.org/contactus/datasubmission) page.
+
+#### Accessible
+
+All datasets within the Lipid Interactome are available for download in standardized `.csv` format, ensuring broad accessibility across different computational environments.
+To further enhance usability, we provide a [detailed overview of data generation and analysis](https://www.lipidinteractome.org/background/multifunctionallipidprobesoverview), including explicit descriptions of dataset structure, column definitions, and the inherent limitations of multifunctional lipid probes.
+Only peer-reviewed proteomics datasets are included in this repository to maintain high data quality and reliability.
+
+#### Interoperable
+
+Given the diversity of methodologies employed across lipid interactome studies, we have taken care to harmonize data formats and metadata annotations.
+While many studies share common analytical pipelines, others employ distinct mass spectrometry workflows.
+To ensure consistency, we have structured the data to allow parallel comparisons and provided [documentation on methodological differences](https://www.lipidinteractome.org/background/proteomicsusingmultifunctionalprobes).
+This standardization effort facilitates direct cross-study comparisons without requiring extensive reformatting by the end user.
+
+#### Reusable
+
+To maximize the utility of these datasets, we provide extensive documentation detailing data acquisition, analysis workflows, and potential limitations.
+Wherever possible, technical jargon has been minimized to ensure accessibility to a broad audience, from lipid biologists to computational scientists.
+Additionally, we reference key publications that delve deeper into the synthesis of lipid probes and the specifics of each proteomics workflow, allowing researchers to further contextualize and validate their findings.
+
+By adhering to these FAIR principles, the Lipid Interactome database aims to serve as a robust and enduring resource for the lipid biology community, reducing redundancy, improving data transparency, and accelerating the study of lipid-mediated signaling.
+
+### Data Visualization and Download Modules
+
+To facilitate efficient exploration and analysis of lipid–protein interaction data, the Lipid Interactome repository incorporates a suite of interactive visualization and data access tools.
+These modules are designed to enhance user engagement, provide clear interpretability of experimental findings, and streamline data retrieval for further computational analysis.
+
+#### Study-Specific Data Exploration
+
+Each study contributing to the repository is provided with a dedicated results page, allowing users to examine its findings in detail.
+These pages include interactive Volcano, Ranked-Order, and MA plots, which enable visualization of differential protein enrichment across experimental conditions.
+The plots are rendered using the Plotly and htmlwidgetsR packages, ensuring a responsive, client-side experience that supports zooming, hovering, and data filtering \[REF: Plotly, htmlwidgets\].
+For transparency and reproducibility, all datasets associated with a given study are available for direct download.
+
+#### Lipid Probe-Specific Pages
+
+Beyond individual study pages, datasets are further organized by lipid probe, providing a consolidated view of protein interactors detected across multiple experiments.
+Each lipid-specific page includes study metadata, cell type, and facilitates cross-study comparisons.
+Future iterations of the repository will extend this functionality by enabling direct comparisons of interactomes obtained from different cell lines treated with the same lipid probe, further refining the contextual understanding of lipid–protein interactions.
+
+#### Comparative Analysis via Shiny Application
+
+Where study design permits, data has been integrated into an interactive Shiny application, allowing users to perform direct probe-to-probe comparisons ([Probe vs Probe Comparisons](https://www.lipidinteractome.org/lipidprobe/enrichedhitscomparison)).
+This tool enables researchers to explore the similarity of lipid interactomes across experimental conditions via linear regression analysis, highlighting proteins that are significantly enriched in one dataset, both datasets, or neither.
+By providing an intuitive framework for interactome comparison, this feature aids in the identification of promising targets for further investigation.
+
+These data access and visualization tools are designed to ensure that the Lipid Interactome is not merely a static repository, but rather a dynamic and evolving resource for lipid biologists and bioinformaticians alike.
+
+### Data format
+
+While there are numerous ways to quantify the mass spectrometry (MS) data, the studies included in our repository have utilized the same (or highly similar) quantitative MS pipeline using Tandem Mass Tagging\[REF\].
+These datasets include those reported by Farley et al.
+(2024), Farley et al.
+(2024), and Thomas et al.
+(2025)[@farleyTrifunctionalSphinganineNew2024a; @farleyTrifunctionalFattyAcid2024; @thomasTrifunctionalLipidDerivatives2025].
+Correspondingly, the ideal data structure for incorporation into our repository will include the following:
+
+:::{.border}
+
+| Gene name | Enrichment value (logFC) | p value |  AveExpr   |  FDR   |
+|:----------|:------------------------:|:-------:|:----------:|:------:|
+| GeneA     |           1.2            |  0.001  | 1.0x10^18^ | 0.0001 |
+| GeneB     |           0.1            |   0.6   | 1.0x10^5^  | 0.005  |
+| ...       |           ...            |   ...   |    ...     |  ...   |
+: Example data table for smooth incorporation into Lipid Interactome. {#tbl-1 .striped}
+
+:::
+
+-   Column descriptions:
+    -   Gene name or Accession Number
+    -   Enrichment value (Experimental versus Control fold-change, typically log2-transformed)
+    -   p value: the results of an ANOVA or LIMMA analysis, corrected for multiple hypothesis testing
+    -   AveExpr: An averaged value of the m/z ion intensity of the Experimental condition and Control condition used for the enrichment value (used to prepare MA plots for quality control)
+    -   False-discovery rate of protein identification
+-   We are working on providing visualization functionality for studies which utilized Peptide Spectral Matching to report enrichment toward lipid probes.
+
+## Discussion
+
+- What we hope this resource enables researchers to do:
+  - Explore previously-published results and guide ongoing research.
+  - Orthogonally verify and characterize the interactions of bioactive lipid species and enriched proteins.
+-   Longevity – this site is designed to expand as more researchers utilize functionalized lipid probes as targets for interactomics.
+  - We plan to incorporate a section for each lipid interactome in which validating studies may be referenced -- allowing rapid cross-referencing of research which has already been done.
+  - Data submission - with the provided [data submission format](/ContactUs/DataSubmission.qmd), researchers can submit their data for inclusion in this database.
+
+## Abbreviations
+MS
+
+## Acknowledgements
+
+-   Andre Nadler
+-   Frank Stein
+-   Per Haberkant
+
+## Conflicts of Interest
+
+The authors have no conflicts of interest to declare.
+
+{{< pagebreak >}}
+
+## References

### 2025-02-05 Background/ProteomicsUsingMultifunctionalProbes.qmd
EOD, updates to overview pages

--- 2025-01-31 Background/ExperimentalSchemaAndAnalysis.qmd
@@
 title: "Background: Using multifunctional probes for proteomics"
+format: 
+  html:
+    embed-resources: false
+    toc: true
+    toc-depth: 4
+  docx:
+    fig-height: 5
+    reference-doc: /Users/gaelenguzman/LipidInteractomics_Website_local/LipidInteractomics_Website/Resources/custom-reference-doc.docx
 ---
@@
 
+In this overview, we aim to explain the fundamental procedures of utilizing lipid probes in proteomics analysis. [@fig-ExperimentalSchema] depicts the steps described below
+
 ::: border
-![](/Background/BaselineProteomics_ExperimentalDesign.png){group="Overview_gallery"}
+![](/Background/BackgroundFigures/BaselineProteomics_ExperimentalDesign.png){#fig-ExperimentalSchema group="Overview_gallery"}
 :::
@@
 
+As has been reported previously by Höglinger et al.
+(2017), Muller et al.
+(2021), Farley et al.
+(2024), Farley et al.
+(2024), and Thomas et al.
+(2025), lipid probes are readily taken up by cell membranes within minutes upon treatment with lipid probes at concentrations ranging from 2 \muM (as for trifunctional sphingosine and sphinganine) to 5 \muM (as for trifunctional phosphatidic acid and phosphatidylethanolamine) to 100 \muM (as for trifunctional diacylglycerol)[@hoglingerTrifunctionalLipidProbes2017; @mullerSynthesisCellularLabeling2021; @farleyTrifunctionalFattyAcid2024; @farleyTrifunctionalSphinganineNew2024a; @thomasTrifunctionalLipidDerivatives2025].
+These studies utilized the inherent fluorescence of the coumarin cage to validate the uptake and wide intercalation of the lipid probes throughout the cell[@schultzChemicalToolsLipid2023].
+
+### Uncaging
+
+- Irradiation with 405 nm wavelength light induces the release of the coumarin photocage and thus allows for the recognition and metabolism of the headgroup of the lipid probe.
+
+- Substantial work has validated that these lipid probes are recognized by the cell as their native counterparts, as the remaining functional groups have minimal effect on the probes'  biophysical properties.
+This has been validated in numerous studies, including Höglinger et al.
+(2015) and Höglinger et al.
+(2017), Muller et al.
+(2020) and Muller et al.
+(2020), and Farley et al.
+(2024) and Farley et al.
+(2024)[@hoglingerIntracellularSphingosineReleases2015a; @hoglingerTrifunctionalLipidProbes2017; @mullerSynthesisCellularLabeling2020; @mullerSynthesisCellularLabeling2021].
+
+### Crosslinking
+
+- Irradiation with 355 nm wavelength light ()
+
 ### Protein collection
 
+- Cell lysis
+
+- Affinity purification of probe-conjugated proteins
+  * Example using azide beads: Perform click chemistry reaction in presence of beads coated with picolyl-azide functional groups for covalent capture
+  * Conjugates of protein-lipid-bead are covalently bound and can thus be stringently washed with detergent solutions to remove non-specific proteins.
+Detergent can then be removed with repeated washes of 8 M urea and 20 % acetonitrile.
+* Captured proteins can be reduced and alkylated on-bead. 
+* Peptides can be digested off the protein-lipid-bead conjugates via tryptic digest. Digested peptides are then desalted to remove any remaining contaminants using reverse phase desalting columns.
+
 ### Mass spectrometry analysis
+
+Broadly, all mass spectrometry techniques for proteomic identification of differentially-enriched proteins will involve injection into a mass spectrometer via liquid chromatography.
+Within the mass spectrometer, individual peptides can be isolated and fragmented to determine their sequence.
+
+There are several methodologies commonly used to quantify mass spectrometry data.
+At the highest level, these may be separated into label-free and label-based quantification techniques.
+Both categories are valid for reporting differential enrichment, and each has pros and cons -- discussed in detail below.
 
@@
 
-#### Quantitative Mass Spectrometry with Tandem Mass Tagging
+#### Label-based quantification
 
-Tandem Mass Tag (TMT) labeling is a powerful quantitative mass spectrometry technique that enables the simultaneous analysis of multiple samples in a single MS run.
+All label-based mass spectrometry quantification methods use stable isotopes to distinguish the source of proteins within a pooled collective of several experimental samples.
+Previously, the technique known as Stable Isotope Labeling with Amino acids in Cell Culture (SILAC) was common, though this has fallen out of use due to cost and difficult sample preparation.
+
+Modern label-based techniques such as iTRAQ (isotopic Tagging for Relative and Absolute  Quantification) and TMT (Tandem Mass Tagging) have become the norm.
+For the purposes of this overview, we will focus on TMT as it has greater capacity for samples per experiment (16+ as opposed to 8), and the techniques are fundamentally similar.
+
+TMT labeling is a powerful quantitative mass spectrometry technique that enables the simultaneous analysis of multiple samples in a single MS run.
 This approach improves efficiency and allows for precise relative quantification of proteins across experimental conditions.

### 2025-02-05 BioinformaticsApplicationNote/GG_2025_applicationNote.qmd
EOD, updates to overview pages

@@
 These probes incorporate strategically designed functional groups that enable covalent crosslinking, affinity enrichment, and controlled activation.
-Most commonly, these include: (1) a diazirine ring for photoactivatable crosslinking upon exposure to 355 nm UV light, stabilizing lipid–protein interactions; (2) a terminal alkyne, permitting click chemistry-based enrichment; and, in some cases, (3) a coumarin photocage, which shields the lipid probe from premature enzymatic modification until selectively released by 405 nm light.
+Most commonly, these include: (1) a diazirine ring for photoactivatable crosslinking upon exposure to 355 nm ultraviolet (UV) light, stabilizing lipid–protein interactions; (2) a terminal alkyne, permitting click chemistry-based enrichment; and, in some cases, (3) a coumarin photocage, which shields the lipid probe from premature enzymatic modification until selectively released by 405 nm light.
 Together, these modifications enable direct proteomic identification of lipid interactors, distinguishing true binding partners from transient or non-specific associations[@haberkantFatFabulousBifunctional2014; @schultzChemicalToolsLipid2023; @farleyTrifunctionalSphinganineNew2024a].
@@
 -   Column descriptions:
-    -   Gene name or Accession Number
-    -   Enrichment value (Experimental versus Control fold-change, typically log2-transformed)
-    -   p value: the results of an ANOVA or LIMMA analysis, corrected for multiple hypothesis testing
-    -   AveExpr: An averaged value of the m/z ion intensity of the Experimental condition and Control condition used for the enrichment value (used to prepare MA plots for quality control)
-    -   False-discovery rate of protein identification
+    -   *Gene name or Accession Number*
+    -   *Enrichment value*: Fold change of Experimental versus Control fold-change, typically log2-transformed -- ideally the product of TMT or other quantitative mass spectrometry methods.
+    -   *p value*: the results of an ANOVA or LIMMA analysis, corrected for multiple hypothesis testing
+    -   *AveExpr*: An averaged value of the m/z ion intensity of the Experimental condition and Control condition used for the enrichment value (used to prepare MA plots for quality control)
+    -   *FDR*: False-discovery rate of protein identification
 -   We are working on providing visualization functionality for studies which utilized Peptide Spectral Matching to report enrichment toward lipid probes.
@@
 
-- What we hope this resource enables researchers to do:
-  - Explore previously-published results and guide ongoing research.
-  - Orthogonally verify and characterize the interactions of bioactive lipid species and enriched proteins.
--   Longevity – this site is designed to expand as more researchers utilize functionalized lipid probes as targets for interactomics.
-  - We plan to incorporate a section for each lipid interactome in which validating studies may be referenced -- allowing rapid cross-referencing of research which has already been done.
-  - Data submission - with the provided [data submission format](/ContactUs/DataSubmission.qmd), researchers can submit their data for inclusion in this database.
+The advent of functionalized lipid probes has fundamentally transformed lipid biology by enabling the proteomic identification of lipid-binding proteins with unprecedented specificity.
+However, as the number of published lipid interactome studies grows, the lack of a centralized framework for comparing and integrating these datasets presents a significant challenge.
+The Lipid Interactome was developed to address this need by providing researchers with a structured platform to explore, cross-reference, and build upon previous findings.
+By aggregating and standardizing lipid–protein interaction data, this resource facilitates the rapid identification of candidate lipid-binding proteins and supports orthogonal validation efforts.
+
+Designed as a continuously expanding repository, the Lipid Interactome will evolve alongside advances in lipid probe technologies and interactomics.
+Future iterations will incorporate validation studies for each lipid probe, offering researchers a dedicated space to compare findings across experimental contexts.
+This functionality will not only reduce redundancy in experimental design but also strengthen the reproducibility and biological interpretation of lipid interactome research.
+To support this vision, we invite researchers to contribute their datasets via our [Data Submission page](https://www.lipidinteractome.org/DataSubmission.html), fostering a collaborative and transparent approach to lipid biology.
 
 ## Abbreviations
+
+UV
+: *U*ltra *V*iolet
+
 MS
+: *M*ass *S*pectrometry
+
+LIMMA
+: *Li*near *M*odels for *M*icro*a*rray and RNA-Seq Data
+
+ANOVA
+: *An*alysis *o*f *Va*riance
 

### 2025-02-07 IndividualStudies/AT_2025.qmd
adding protein search page, though still work in progress

@@
 library(DT)
+library(here)
 
-## Set up the source for the standardized ggplot styles
-source("ggplot_styles.R")
+## Opening the source file for the ggplot custom theme
+source(paste0(here(), "/Resources/ggplot_styles.R"))
+
 ```

### 2025-02-07 IndividualStudies/DH_2017.qmd
adding protein search page, though still work in progress

@@
 library(pheatmap)
+library(here)
+
+## Opening the source file for the ggplot custom theme
+source(paste0(here(), "/Resources/ggplot_styles.R"))
 

### 2025-02-07 IndividualStudies/RM_2021.qmd
adding protein search page, though still work in progress

@@
 library(htmltools)
+library(here)
 
 ## Opening the source file for the ggplot custom theme
-source("ggplot_styles.R")
+source(paste0(here(), "/Resources/ggplot_styles.R"))
 

### 2025-02-07 IndividualStudies/SF_2024.qmd
adding protein search page, though still work in progress

@@
 library(scales)
+library(here)
 
 ## Opening the source file for the ggplot custom theme
-source("ggplot_styles.R")
+source(paste0(here(), "/Resources/ggplot_styles.R"))
 

### 2025-02-07 IndividualStudies/SF_2024_B.qmd
adding protein search page, though still work in progress

@@
 library(DT)
-library(htmltools)
+library(here)
 
 ## Opening the source file for the ggplot custom theme
-source("ggplot_styles.R")
+source(paste0(here(), "/Resources/ggplot_styles.R"))
 

### 2025-02-07 LipidProbe/8-3_FattyAcid.qmd
removed naughty docx formatting
Reorganizing sections, increasing visibility of subsections
adding protein search page, though still work in progress

@@
 title: "Trifunctional 8-3 Fatty Acid"
+html: default
 ---
@@
 ## Opening the source file for the ggplot custom theme
-source("ggplot_styles.R")
+source("/Users/gaelenguzman/LipidInteractomics_Website_local/LipidInteractomics_Website/Resources/ggplot_styles.R")
 
@@
 ```
+
+*Greater context to the distinction between the 8-3 Fatty Acid and 1-10 Fatty Acid probes can be found in the [Diazirine Overview](/Background/MultifunctionalLipidProbesOverview.qmd#sec-DiazirinePlacement)*
 

### 2025-02-07 LipidProbe/EnrichedHitsComparison.qmd
adding protein search page, though still work in progress

@@
 # # Making a big shared dataset with all of the TMT-quantified lipid probes - this is a little hand-wavey because some were run at different times... TBD if we want to keep this.
+
 # PA_data <- read_csv("LipidProbe/DataSets/PA_HeLa_AT_2025.csv") |>
-# 	select(LipidProbe, gene_name, logFC, pvalue, hit_annotation)
+# 	select(LipidProbe, gene_name, hit_annotation, logFC, pvalue) |>
+#   mutate(fdr = "Data not available")
 
 # PE_data <- read_csv("LipidProbe/DataSets/PE_HeLa_AT_2025.csv") |>
-# 	select(LipidProbe, gene_name, logFC, pvalue, hit_annotation)
+# 	select(LipidProbe, gene_name, hit_annotation, logFC, pvalue) |>
+#   mutate(fdr = "Data not available")
 
 # Spa_data <- read_csv("LipidProbe/DataSets/Spa_Huh7_SF_2024.csv") |>
-# 	select(LipidProbe, gene_name, logFC, pvalue, hit_annotation)
+# 	select(LipidProbe, gene_name, hit_annotation, logFC, pvalue, fdr)
 
 # Sph_data <- read_csv("LipidProbe/DataSets/Sph_Huh7_SF_2024.csv") |>
-# 	select(LipidProbe, gene_name, logFC, pvalue, hit_annotation)
+# 	select(LipidProbe, gene_name, hit_annotation, logFC, pvalue, fdr)
 
 # FA_8_3_data <- read_csv("LipidProbe/DataSets/8-3_FA_Huh7_SF_2024.csv") |>
-# 	select(LipidProbe, gene_name, logFC, pvalue, hit_annotation)
+# 	select(LipidProbe, gene_name, hit_annotation, logFC, pvalue, fdr)
 
 # FA_1_10_data <- read_csv("LipidProbe/DataSets/1-10_FA_Huh7_SF_2024.csv") |>
-# 	select(LipidProbe, gene_name, logFC, pvalue, hit_annotation)
+# 	select(LipidProbe, gene_name, hit_annotation, logFC, pvalue, fdr)
 
@@
 
-#write.csv(combinedDataset, "LipidProbe/DataSets/combinedProbeDatasets_TMT.csv")
+# write.csv(combinedDataset, "LipidProbe/DataSets/combinedProbeDatasets_TMT.csv")
 ```

### 2025-02-07 LipidProbe/FormattingTemplate.qmd
updating with includes structure
adding protein search page, though still work in progress

@@
 
-#### Study details
-
-##### Authors
-
-##### Journal
-
-##### Abstract
-
-##### Lipid probes utilized
-
-##### Cell line analyzed
-
-##### Mass spectrometry quantification method
+{{< include /StudyInformation_includes/template_include.qmd >}}
 
@@
 library(plotly)
-library(ggplot2)
+library(ggplot2)git
 library(grid)

### 2025-02-07 LipidProbe/PhosphatidicAcid.qmd
adding protein search page, though still work in progress

@@
 The left panel depicts the results of a pulldown using trifunctionalized phosphatidic acid; the right panel depicts the results of the pulldown using trifunctionalized phosphatidylethanolamine.
-Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV)."
+Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV."
 
@@
 MA plots depict the average abundance of each protein in the crosslinked and uncrosslinked conditions (x-axis) versus the log2-transformed fold-change between the crosslinked and uncrosslinked conditions (y-axis).
-Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV)."
+Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV."
 
@@
 
-?crosstalk::filter_checkbox()
-
 ## Displays the reactive dataframe

### 2025-02-07 LipidProbe/Sphinganine.qmd
adding protein search page, though still work in progress

@@
 library(DT)
+library(here)
 
-## Set up the source for the standardized ggplot styles
-source("ggplot_styles.R")
+## Opening the source file for the ggplot custom theme
+source(paste0(here(), "/Resources/ggplot_styles.R"))
 

### 2025-02-07 LipidProbe/Sphingosine.qmd
beginning my application note, many small adjustments, big text edits to overview
adding protein search page, though still work in progress

@@
 title: "Trifunctional Sphingosine"
+format: html
 ---

### 2025-02-07 SearchByProtein/SearchByProtein.qmd
adding protein search page, though still work in progress

---
title: "Search enrichment by protein"
---

```{r setup, include=FALSE}
library(DT)
library(crosstalk)
library(tidyverse)
library(readr)
library(ggplot2)
library(plotly)

source("/Users/gaelenguzman/LipidInteractomics_Website_local/LipidInteractomics_Website/Resources/ggplot_styles.R")

# Read call for testing, comment out for rendering
data <- read_csv("combinedProbeDatasets_TMT.csv")

data <- data |>
	select(gene_name, LipidProbe, hit_annotation, logFC, pvalue, fdr) |>
	mutate(logFC = signif(logFC, digits=3),
          pvalue = signif(pvalue, digits=3),
					Study = case_when(LipidProbe == "1-10 FA" ~ "Farley et al. 2024 B; DOI: 10.1021/acschembio.3c00554",
														LipidProbe == "8-3 FA" ~ "Farley et al. 2024 B; DOI: 10.1021/acschembio.3c00554",
														LipidProbe == "Sph" ~ "Farley et al. 2024 A; DOI: 10.1021/acschembio.3c00554",
														LipidProbe == "Spa" ~ "Farley et al. 2024 A; DOI: 10.1021/acschembio.3c00554",
														LipidProbe == "PE" ~ "Thomas et al. 2025; DOI: 10.1039/D4CC03599B",
														LipidProbe == "PA" ~ "Thomas et al. 2025; DOI: 10.1039/D4CC03599B",
														LipidProbe == "PA" ~ "Thomas et al. 2025; DOI: 10.1039/D4CC03599B",
														)) |>
  arrange(hit_annotation) |>
  arrange(LipidProbe) |>
	glimpse()

	## Creates a reactive dataframe
data_reactive <- crosstalk::SharedData$new(data)

```

**Use the search bar below to filter for a protein among the results of all studies which utilized TMT-based quantification**

```{r, echo=FALSE}
htmltools::tags$div(
  class = "filter-container",
  filter_select(id = "gene_name",
                  label = "Protein name:", 
                  sharedData = data_reactive,
                  group = ~gene_name)
)

## Displays the reactive dataframe
datatable(data_reactive,
          caption = "'No hit' proteins are unenriched or depleted in the presence of probe, 'enriched candidates' are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and 'enriched hits' are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV", 
          options = list(pageLength = 10,
												 dom = "l<t>ipr"))

```

**Still in beta: a plot that highlights the selected protein out of all the datasets on our site**
```{r, warning=FALSE, echo=FALSE}
data |>
	VolcanoPlotStandardized()

```

### 2025-02-07 LipidProbe/FormattingTemplate.qmd
my best version of the filterable plot

@@
 library(plotly)
-library(ggplot2)git
+library(ggplot2)
 library(grid)

### 2025-02-07 SearchByProtein/SearchByProtein.qmd
my best version of the filterable plot

@@
 library(plotly)
+library(here)
 
-source("/Users/gaelenguzman/LipidInteractomics_Website_local/LipidInteractomics_Website/Resources/ggplot_styles.R")
+## Opening the source file for the ggplot custom theme
+source(paste0(here(), "/Resources/ggplot_styles.R"))
 
 # Read call for testing, comment out for rendering
-data <- read_csv("combinedProbeDatasets_TMT.csv")
+data <- read_csv(paste0(here(), "/SearchByProtein/combinedProbeDatasets_TMT.csv"))
 
-data <- data |>
+datawhole <- data |>
 	select(gene_name, LipidProbe, hit_annotation, logFC, pvalue, fdr) |>
@@
 
+limits <- c(max(abs(datawhole$logFC), na.rm=TRUE) , max(-log10(datawhole$pvalue), na.rm=TRUE))
+
+datawhole$LipidProbe <- factor(pull(data, LipidProbe), levels = c("PA", "PE", "Sph", "Spa", "1-10 FA", "8-3 FA"), ordered = TRUE)
+
 	## Creates a reactive dataframe
-data_reactive <- crosstalk::SharedData$new(data)
+datawhole_reactive <- crosstalk::SharedData$new(datawhole)
 
@@
                   label = "Protein name:", 
-                  sharedData = data_reactive,
+                  sharedData = datawhole_reactive,
                   group = ~gene_name)
@@
 ## Displays the reactive dataframe
-datatable(data_reactive,
+datatable(datawhole_reactive,
           caption = "'No hit' proteins are unenriched or depleted in the presence of probe, 'enriched candidates' are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and 'enriched hits' are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV",
-          options = list(pageLength = 10,
+          options = list(pageLength = 6,
 												 dom = "l<t>ipr"))
@@
 
+## Data vis of selected proteins
+
 **Still in beta: a plot that highlights the selected protein out of all the datasets on our site**
 ```{r, warning=FALSE, echo=FALSE}
-data |>
-	VolcanoPlotStandardized()
+
+VolcanoPlotStandardized(datawhole_reactive)
 

### 2025-02-07 Resources/ggplot_styles.R

@@ -6,6 +6,25 @@ library(emojifont)
 library(dplyr)
 library(tidyr)
 
+# Define a helper function that safely applies abs()
+safe_abs <- function(x, default = NA) {
+  tryCatch({
+    # Ensure that x is numeric before taking abs()
+    abs(as.numeric(x))
+  }, error = function(e) {
+    default
+  })
+}
+
+safe_log10 <- function(x, default = NA) {
+    tryCatch({
+        # Ensure that x is numeric before taking log10()
+        log10(as.numeric(x))
+    }, error = function(e) {
+        default
+    })
+}
+
 # A standardized MA plot function
 
 MAStandard <- function(data) {
@@ -153,6 +172,10 @@ RankedOrderPlotStandard <- function(data) {
 # A standardized Volcano plot theme
 
 VolcanoPlotStandardized <- function(data) {
+
+    limits <- c(max(c(safe_abs(data$logFC), 4), na.rm=TRUE) , max(c(-safe_log10(data$pvalue), 6), na.rm=TRUE))
+
+
     VolcanoPlots <- data |>
         ggplot(aes(x = logFC,
                    y = -log10(pvalue),
@@ -166,8 +189,8 @@ VolcanoPlotStandardized <- function(data) {
                                      "p-value: ", pvalue, "\n"))) +
         geom_hline(yintercept = 0, linetype = 2) +
         geom_vline(xintercept = 0, linetype = 2) +
-        scale_x_continuous(limits=c(-1.1 * max(abs(data$logFC)), 1.1* max(abs(data$logFC)))) +
-        scale_y_continuous(limits=c(0, max(-log10(data$pvalue)))) +
+        scale_x_continuous(limits=c(-1.1 * limits[1], 1.1* limits[1])) +
+        scale_y_continuous(limits=c(0, 1.1 * limits[2])) +
         scale_shape_manual(values = c("enriched hit" = 21,
                                     "hit" = 21,
                                     "enriched candidate" = 24,
@@ -198,7 +221,7 @@ VolcanoPlotStandardized <- function(data) {
                                     "candidate" = 2, 
                                     "no hit" = 0.75), 
                         name = "Trend") +
-        facet_wrap(~LipidProbe) +
+        facet_wrap(~LipidProbe, ncol = 2) +
         xlab("Log2 fold-change") +
         ylab("-log10(p-value)") +
         theme_minimal() +

### 2025-02-07 LipidProbe/EnrichedHitsComparison.qmd
big issue in data wrangling -- fixed now'

--- 2025-01-31 LipidProbe/EnrichedHitsComparison.qmd
@@
 library(DT)
-# # Making a big shared dataset with all of the TMT-quantified lipid probes - this is a little hand-wavey because some were run at different times... TBD if we want to keep this.
-# PA_data <- read_csv("LipidProbe/DataSets/PA_HeLa_AT_2025.csv") |>
-# 	select(LipidProbe, gene_name, logFC, pvalue, hit_annotation)
+# Making a big shared dataset with all of the TMT-quantified lipid probes - this is a little hand-wavey because some were run at different times... TBD if we want to keep this.
 
-# PE_data <- read_csv("LipidProbe/DataSets/PE_HeLa_AT_2025.csv") |>
-# 	select(LipidProbe, gene_name, logFC, pvalue, hit_annotation)
+PA_data <- read_csv("LipidProbe/DataSets/PA_HeLa_AT_2025.csv") |>
+	select(LipidProbe, gene_name, hit_annotation, logFC, pvalue) |>
+  mutate(fdr = "Data not available")
 
-# Spa_data <- read_csv("LipidProbe/DataSets/Spa_Huh7_SF_2024.csv") |>
-# 	select(LipidProbe, gene_name, logFC, pvalue, hit_annotation)
+PE_data <- read_csv("LipidProbe/DataSets/PE_HeLa_AT_2025.csv") |>
+	select(LipidProbe, gene_name, hit_annotation, logFC, pvalue) |>
+  mutate(fdr = "Data not available")
 
-# Sph_data <- read_csv("LipidProbe/DataSets/Sph_Huh7_SF_2024.csv") |>
-# 	select(LipidProbe, gene_name, logFC, pvalue, hit_annotation)
+Spa_data <- read_csv("LipidProbe/DataSets/Spa_Huh7_SF_2024.csv") |>
+	select(LipidProbe, gene_name, hit_annotation, logFC, pvalue, fdr)
 
-# FA_8_3_data <- read_csv("LipidProbe/DataSets/8-3_FA_Huh7_SF_2024.csv") |>
-# 	select(LipidProbe, gene_name, logFC, pvalue, hit_annotation)
+Sph_data <- read_csv("LipidProbe/DataSets/Sph_Huh7_SF_2024.csv") |>
+	select(LipidProbe, gene_name, hit_annotation, logFC, pvalue, fdr)
 
-# FA_1_10_data <- read_csv("LipidProbe/DataSets/1-10_FA_Huh7_SF_2024.csv") |>
-# 	select(LipidProbe, gene_name, logFC, pvalue, hit_annotation)
+FA_8_3_data <- read_csv("LipidProbe/DataSets/8-3_FA_Huh7_SF_2024.csv") |>
+	select(LipidProbe, gene_name, hit_annotation, logFC, pvalue, fdr)
 
-# combinedDataset <- rbind(PA_data, PE_data, Spa_data, Sph_data, FA_8_3_data, FA_1_10_data)
+FA_1_10_data <- read_csv("LipidProbe/DataSets/1-10_FA_Huh7_SF_2024.csv") |>
+	select(LipidProbe, gene_name, hit_annotation, logFC, pvalue, fdr)
 
-#write.csv(combinedDataset, "LipidProbe/DataSets/combinedProbeDatasets_TMT.csv")
+combinedDataset <- rbind(PA_data, PE_data, Spa_data, Sph_data, FA_8_3_data, FA_1_10_data)
+
+# write.csv(combinedDataset, "LipidProbe/DataSets/combinedProbeDatasets_TMT.csv")
+
+write.csv(combinedDataset, "/Users/gaelenguzman/LipidInteractomics_Website_local/LipidInteractomics_Website/SearchByProtein/combinedProbeDatasets_TMT.csv")
 ```

### 2025-02-07 IndividualStudies/ggplot_styles.R

@@ -1,225 +1,0 @@
-# A centralized spot to save a custom theme across the whole site
-
-library(ggplot2)
-library(ggrepel)
-library(emojifont)
-library(dplyr)
-library(tidyr)
-
-# A standardized MA plot function
-
-MAStandard <- function(data) {
-
-    MAPlots <- data |>
-        ggplot(aes(x = AveExpr,
-                   y = logFC,
-                   color = factor(hit_annotation),
-                   fill = factor(hit_annotation),
-                   shape = factor(hit_annotation),
-                   alpha = factor(hit_annotation),
-                   size = factor(hit_annotation))) +
-        geom_point(aes(text = paste0("Gene name: ", gene_name, "\n",
-                                    "LogFC: ", logFC, "\n",
-                                    "p-value: ", pvalue, "\n"))) +
-        geom_hline(yintercept = 0, linetype = 2) +
-        geom_vline(xintercept = 0, linetype = 2) +
-        scale_x_continuous(limits=c(0.9 * min(abs(data$AveExpr)), 1.1* max(abs(data$AveExpr))))+
-        scale_y_continuous(limits=c(-1.1 * max(abs(data$logFC)), 1.1* max(abs(data$logFC))))+
-        scale_shape_manual(values = c("enriched hit" = 21,
-                                    "hit" = 21,
-                                    "enriched candidate" = 24,
-                                    "candidate" = 24,
-                                    "no hit" = 22), 
-                        name = "Trend") +
-        scale_color_manual(values = c("enriched hit" = "black",
-                                    "hit" = "black",
-                                    "enriched candidate" = "black",
-                                    "candidate" = "black",
-                                    "no hit" = "black"), 
-                        name = "Trend") +
-        scale_fill_manual(values = c("enriched hit" = "orange",
-                                    "hit" = "orange",
-                                    "enriched candidate" = "purple",
-                                    "candidate" = "purple",
-                                    "no hit" = "black"), 
-                        name = "Trend") +
-        scale_alpha_manual(values = c("enriched hit" = 0.8,
-                                    "hit" = 0.8,
-                                    "enriched candidate" = 0.5,
-                                    "candidate" = 0.5,
-                                    "no hit" = 0.25), 
-                        name = "Trend") +
-        scale_size_manual(values = c("enriched hit" = 4,
-                                    "hit" = 4,
-                                    "enriched candidate" = 2,
-                                    "candidate" = 2, 
[…]

### 2025-02-07 LipidProbe/EnrichedHitsComparison.qmd
tiny change to plot on search page

--- 2025-01-31 LipidProbe/EnrichedHitsComparison.qmd
@@
 library(DT)
-# # Making a big shared dataset with all of the TMT-quantified lipid probes - this is a little hand-wavey because some were run at different times... TBD if we want to keep this.
-# PA_data <- read_csv("LipidProbe/DataSets/PA_HeLa_AT_2025.csv") |>
-# 	select(LipidProbe, gene_name, logFC, pvalue, hit_annotation)
+library(here)
 
-# PE_data <- read_csv("LipidProbe/DataSets/PE_HeLa_AT_2025.csv") |>
-# 	select(LipidProbe, gene_name, logFC, pvalue, hit_annotation)
+# Making a big shared dataset with all of the TMT-quantified lipid probes - this is a little hand-wavey because some were run at different times... TBD if we want to keep this.
 
-# Spa_data <- read_csv("LipidProbe/DataSets/Spa_Huh7_SF_2024.csv") |>
-# 	select(LipidProbe, gene_name, logFC, pvalue, hit_annotation)
+# PA_data <- read_csv(paste0(here(), "/LipidProbe/DataSets/PA_HeLa_AT_2025.csv")) |>
+# 	select(LipidProbe, gene_name, hit_annotation, logFC, pvalue) |>
+#   mutate(fdr = "Data not available")
 
-# Sph_data <- read_csv("LipidProbe/DataSets/Sph_Huh7_SF_2024.csv") |>
-# 	select(LipidProbe, gene_name, logFC, pvalue, hit_annotation)
+# PE_data <- read_csv(paste0(here(), "/LipidProbe/DataSets/PE_HeLa_AT_2025.csv")) |>
+# 	select(LipidProbe, gene_name, hit_annotation, logFC, pvalue) |>
+#   mutate(fdr = "Data not available")
 
-# FA_8_3_data <- read_csv("LipidProbe/DataSets/8-3_FA_Huh7_SF_2024.csv") |>
-# 	select(LipidProbe, gene_name, logFC, pvalue, hit_annotation)
+# Spa_data <- read_csv(paste0(here(), "/LipidProbe/DataSets/Spa_Huh7_SF_2024.csv")) |>
+# 	select(LipidProbe, gene_name, hit_annotation, logFC, pvalue, fdr)
 
-# FA_1_10_data <- read_csv("LipidProbe/DataSets/1-10_FA_Huh7_SF_2024.csv") |>
-# 	select(LipidProbe, gene_name, logFC, pvalue, hit_annotation)
+# Sph_data <- read_csv(paste0(here(), "/LipidProbe/DataSets/Sph_Huh7_SF_2024.csv")) |>
+# 	select(LipidProbe, gene_name, hit_annotation, logFC, pvalue, fdr)
+
+# FA_8_3_data <- read_csv(paste0(here(), "/LipidProbe/DataSets/8-3_FA_Huh7_SF_2024.csv")) |>
+# 	select(LipidProbe, gene_name, hit_annotation, logFC, pvalue, fdr)
+
+# FA_1_10_data <- read_csv(paste0(here(), "/LipidProbe/DataSets/1-10_FA_Huh7_SF_2024.csv")) |>
+# 	select(LipidProbe, gene_name, hit_annotation, logFC, pvalue, fdr)
 
@@
 
-#write.csv(combinedDataset, "LipidProbe/DataSets/combinedProbeDatasets_TMT.csv")
+# # write.csv(combinedDataset, "LipidProbe/DataSets/combinedProbeDatasets_TMT.csv")
+
+# write.csv(combinedDataset, paste0(here(), "/SearchByProtein/combinedProbeDatasets_TMT.csv"))
 ```
@@
 
-# PA_data <- read_csv("/Users/gaelenguzman/LipidInteractomics_Website_local/LipidInteractomics_Website/LipidProbe/DataSets/PA_HeLa_AT_2025.csv") |>
-#   filter(hit_annotation == "enriched hit") |>
-# 	select(LipidProbe, gene_name)
+PA_data <- read_csv(paste0(here(), "/LipidProbe/DataSets/PA_HeLa_AT_2025.csv")) |>
+  filter(hit_annotation == "enriched hit") |>
+	select(LipidProbe, gene_name)
 
-# PE_data <- read_csv("/Users/gaelenguzman/LipidInteractomics_Website_local/LipidInteractomics_Website/LipidProbe/DataSets/PE_HeLa_AT_2025.csv") |>
-# 	filter(hit_annotation == "enriched hit") |>
-# 	select(LipidProbe, gene_name)
+PE_data <- read_csv(paste0(here(), "/LipidProbe/DataSets/PE_HeLa_AT_2025.csv")) |>
+	filter(hit_annotation == "enriched hit") |>
+	select(LipidProbe, gene_name)
 
-# Spa_data <- read_csv("/Users/gaelenguzman/LipidInteractomics_Website_local/LipidInteractomics_Website/LipidProbe/DataSets/Spa_Huh7_SF_2024.csv") |>
-# 	filter(hit_annotation == "enriched hit") |>
-# 	select(LipidProbe, gene_name)
+Spa_data <- read_csv(paste0(here(), "/LipidProbe/DataSets/Spa_Huh7_SF_2024.csv")) |>
+	filter(hit_annotation == "enriched hit") |>
+	select(LipidProbe, gene_name)
 
-# Sph_data <- read_csv("/Users/gaelenguzman/LipidInteractomics_Website_local/LipidInteractomics_Website/LipidProbe/DataSets/Sph_Huh7_SF_2024.csv") |>
-# 	filter(hit_annotation == "enriched hit") |>
-# 	select(LipidProbe, gene_name)
+Sph_data <- read_csv(paste0(here(), "/LipidProbe/DataSets/Sph_Huh7_SF_2024.csv")) |>
+	filter(hit_annotation == "enriched hit") |>
+	select(LipidProbe, gene_name)
 
-# FA_8_3_data <- read_csv("/Users/gaelenguzman/LipidInteractomics_Website_local/LipidInteractomics_Website/LipidProbe/DataSets/8-3_FA_Huh7_SF_2024.csv") |>
-# 	filter(hit_annotation == "enriched hit") |>
-# 	select(LipidProbe, gene_name)
+FA_8_3_data <- read_csv(paste0(here(), "/LipidProbe/DataSets/8-3_FA_Huh7_SF_2024.csv")) |>
+	filter(hit_annotation == "enriched hit") |>
+	select(LipidProbe, gene_name)
 
-# FA_1_10_data <- read_csv("/Users/gaelenguzman/LipidInteractomics_Website_local/LipidInteractomics_Website/LipidProbe/DataSets/1-10_FA_Huh7_SF_2024.csv") |>
-# 	filter(hit_annotation == "enriched hit") |>
-# 	select(LipidProbe, gene_name)
+FA_1_10_data <- read_csv(paste0(here(), "/LipidProbe/DataSets/1-10_FA_Huh7_SF_2024.csv")) |>
+	filter(hit_annotation == "enriched hit") |>
+	select(LipidProbe, gene_name)
 
-# combinedDataset <- rbind(PA_data, PE_data, Spa_data, Sph_data, FA_8_3_data, FA_1_10_data)
+combinedDataset <- rbind(PA_data, PE_data, Spa_data, Sph_data, FA_8_3_data, FA_1_10_data)
 
-# write.csv(combinedDataset, "/Users/gaelenguzman/LipidInteractomics_Website_local/LipidInteractomics_Website/LipidProbe/DataSets/combinedProbeDatasets_VennDiagram.csv")
+# write.csv(combinedDataset, paste0(here(), "/LipidProbe/DataSets/combinedProbeDatasets_VennDiagram.csv"))
 ```

### 2025-02-07 SearchByProtein/SearchByProtein.qmd
big issue in data wrangling -- fixed now'
tiny change to plot on search page

@@
 
-datawhole$LipidProbe <- factor(pull(data, LipidProbe), levels = c("PA", "PE", "Sph", "Spa", "1-10 FA", "8-3 FA"), ordered = TRUE)
+# datawhole$LipidProbe <- factor(pull(data, LipidProbe), levels = c("PA", "PE", "Sph", "Spa", "1-10 FA", "8-3 FA"), ordered = TRUE)
 
@@
 **Still in beta: a plot that highlights the selected protein out of all the datasets on our site**
-```{r, warning=FALSE, echo=FALSE}
+```{r, warning=FALSE, echo=FALSE, fig.height=10}
 

### 2025-02-07 Resources/ggplot_styles.R

@@ -173,7 +173,7 @@ RankedOrderPlotStandard <- function(data) {
 
 VolcanoPlotStandardized <- function(data) {
 
-    limits <- c(max(c(safe_abs(data$logFC), 4), na.rm=TRUE) , max(c(-safe_log10(data$pvalue), 6), na.rm=TRUE))
+    limits <- c(max(c(safe_abs(data$logFC), 4), na.rm=TRUE) , max(c(-safe_log10(data$pvalue), 8), na.rm=TRUE))
 
 
     VolcanoPlots <- data |>

### 2025-02-07 Background/MultifunctionalLipidProbesOverview.qmd
EOD push - updates to overview pages, small changes to protein search

@@
 
+<!--
 ## Photoactivatable & Clickable Probes / Bifunctional Lipid Probes
 
-<!-- -   The conceptual precursor to the so-called trifunctional probes, these typically include only the diazirine and the terminal alkyne moieties.
+ -   The conceptual precursor to the so-called trifunctional probes, these typically include only the diazirine and the terminal alkyne moieties.
 
@@
 
--   [@haberkantFatFabulousBifunctional2014] - Haberkant et al. 2014 -->
+-   [@haberkantFatFabulousBifunctional2014] - Haberkant et al. 2014
 
 ## Trifunctional Lipid Probes
+-->
 
@@
 * The coumarin cage has been repeatedly shown to protect lipid analogs from premature metabolism, but it should be recognized that this comes with some distinct changes to the behavior of the native lipid.
-  - For example, when a cell is treated with a photocaged lipid probe, every membrane in the cell appears to
-
-## Interactomics Experimental schema
-
-::: border
-![](/Background/BackgroundFigures/BaselineProteomics_ExperimentalDesign.png){group="Overview_gallery"}
-:::
-
-### Cell treatment
-
-### Protein collection
-
-### Mass spectrometry analysis
-
-:::{.callout-note collapse="true"}
-#### Label-Free Quantification
-
-Label-free quantification (LFQ) is a widely used mass spectrometry-based proteomics approach that estimates protein abundance without chemical labeling.
-Instead, it relies on comparing the summed intensity of detected peptides across different samples analyzed under identical conditions.
-
-##### How It Works
-
-1.  **Peptide Detection (MS1):** Peptides are isolated and detected based on their mass-to-charge ratio (m/z).
-
-2.  **Peptide Sequencing (MS2):** Selected peptide ions are fragmented, and the resulting spectra determine peptide sequences.
-
-3.  **Quantification:** The total signal intensity of all identified peptides corresponding to a protein is summed as a proxy for its abundance.
-
-4.  **Comparison Across Samples:** Samples prepared and analyzed using the same LC-MS/MS protocol can be compared using peptide-spectrum match (PSM) counts as an abundance proxy.
-
-##### Advantages of Label-Free Quantification
-
--   **Cost-Effective & Simple Sample Preparation:** Unlike labeling methods (e.g., TMT), LFQ does not require expensive reagents or complex modifications, making it more accessible.
-
--   **Flexible & Widely Used:** Compatible with various experimental designs and allows for comparisons across many samples without multiplexing constraints.
-
-##### Challenges & Considerations
-
--   **Potential Bias from Co-Elution:** High-abundance peptides can overshadow low-abundance ones, reducing the number of reliably quantified peptides.
-
--   **Run-to-Run Variability:** LFQ requires separate MS runs for each sample, making it susceptible to differences in instrument calibration, chromatography conditions, or sample handling.
-Careful quality control is necessary to minimize artificial differences.
-
-##### Conclusion
-
-Label-free quantification is a practical and widely used method for proteomics research.
-While cost-effective and flexible, its accuracy depends on careful experimental design and quality control to reduce variability.
-:::
-:::{.callout-note collapse="true"}
-#### Quantitative Mass Spectrometry with Tandem Mass Tagging {#sec-TMT}
-
-Tandem Mass Tag (TMT) labeling is a powerful quantitative mass spectrometry technique that enables the simultaneous analysis of multiple samples in a single MS run.
-This approach improves efficiency and allows for precise relative quantification of proteins across experimental conditions.
-
-##### How It Works
-
-1.  **Chemical Labeling:** Each sample is chemically tagged with a unique TMT label, which consists of a reactive group binding to peptides and a mass reporter for sample differentiation.
-
-2.  **Sample Pooling:** Labeled samples are combined into a single pooled group, reducing the need for separate MS runs.
-
-3.  **Mass Spectrometry Analysis:**
-
-    -   **MS1 (Peptide Isolation):** Peptides are separated and detected based on their mass-to-charge ratio (m/z).
-
-    -   **MS2 (Peptide Sequencing & Tag Fragmentation):** Peptides are fragmented for sequence identification, and TMT mass tags fragment to generate reporter ions.
-
-4.  **Quantification:** The intensity of reporter ions reveals the relative abundance of peptides across the original samples.
-
-5.
-**Comparison Across Samples:** Within a TMT cassette (typically 16 samples), relative protein abundance is calculated from the reporter ion intensities.
-A pooled control channel enables comparison across cassettes, allowing up to 30 samples to be analyzed in a single experiment.
-
-##### Advantages of TMT Labeling
-
--   **Increased Throughput & Efficiency:** Enables multiplexing of many samples (e.g., 16 or more), reducing the number of separate MS runs.
-
--   **Deeper Proteome Coverage:** Pooled samples can be fractionated (e.g., by cation exchange chromatography), enhancing detection of low-abundance peptides.
-
--   **Improved Quantification Accuracy:** Since all samples are analyzed in the same MS run, technical variability between runs is minimized.
-
-##### Challenges & Considerations
-
--   **Higher Cost:** TMT reagents and high-end mass spectrometers add to the expense.
-
--   **Complex Sample Preparation:** Requires additional steps for labeling, pooling, and fractionation, increasing the risk of sample handling variability.
-
--   **Normalization Requirement:** Accurate quantification requires equal protein input across samples to avoid artificial balancing biases.
-
--   **Demanding Instrumentation & Expertise:** Requires high-resolution mass spectrometers, often necessitating specialized facilities.
-
-##### Conclusion
-
-TMT-based mass spectrometry is a valuable tool for large-scale proteomics, offering high-throughput, precise, and deep proteome coverage.
-While it requires advanced instrumentation and careful sample preparation, its ability to multiplex multiple samples in a single run makes it an attractive option for high-confidence protein quantification.
-:::
+  - For example, when a cell is treated with a photocaged lipid probe, the probe intercalates into every membrane in the cell -- including membranes which the native lipid would not enter.
+This may lead to the identification of non-biologically-relevant hits.
+* Similarly, the diazirine and alkyne groups may have minor effects on the biophysical properties of the lipid probe as it interacts with other lipids and proteins within the membrane bilayer.
+This may be more relevant for proteins which preferentially bind to the acyl chain.
+  - For example, Some work has been done to demonstrate that the placement of the diazirine ring along the length of the acyl chain can have impacts on the interactome of the lipid probe[@farleyTrifunctionalFattyAcid2024].
+Farley et al (2024) demonstrated this using trifunctional Fatty Acid probes by placing the diazirine either 3 carbons from the terminus (8-3 FA) or 10 carbons from the terminus (1-10 FA).
+They identified several proteins with distinct enrichment profiles, including VDAC1 and VDAC2 (which are preferentially enriched to the 8-3 FA probe), and ACAD9 and UBB (which are preferentially enriched to the 1-10 FA probe).
+* Quantification of +UV versus -UV
+  - The details of the quantitative mass spectrometry are describe in our [Overview of Proteomics Methods](Background/ProteomicsUsingMultifunctionalProbes.qmd), however, we hope to succinctly describe that quantitative mass spectrometry techniques necessarily require normalization at sample input level -- thereby exaggerating the abundance of proteins in the -UV control samples.
+  - It should be noted, therefore, that there is little meaning to a protein which is "enriched" toward the -UV condition.
+For this reason, all proteins which are "depleted" following irradiation with UV have been designated as "no hit" in our analyses.

### 2025-02-07 Background/ProteomicsUsingMultifunctionalProbes.qmd
EOD push - updates to overview pages, small changes to protein search

@@
 
-- Irradiation with 355 nm wavelength light ()
+- Irradiation with 355 nm wavelength light induces the production of a reactive carbene which readily inserts itself into any nearby biochemical bond. 
+  - Notably, the majority of probes will likely crosslink with either water or with neighboring lipids.
+Quantitative proteomics analysis will fully ignore these conjugates, as only enriched peptides will be measured in the final mass spectrometry analysis (described below in [@sec-MassSpectrometryAnalysis]).
+- The covalently bound lipid protein conjugates which form after crosslinking are highly stable and thus are ideally amenable toward stringent enrichment and washing, producing a high-quality sample with few non-specific proteins tagging along.
 
@@
 - Cell lysis 
+  - Depending on application, may want to perform a membrane prep or otherwise isolate an organelle of interest (e.g. mitochondrial enrichment, if one is seeking mitochondrial interactions)
+  - Due to the high stability of the diazirine crosslinking bond, no extra steps need to be taken to ensure that interactions are maintained -- lysis can be as aggressive as one wishes.
+  - In general, samples due for mass spectrometry analysis should be kept with as little detergent as possible to protect the instrument -- however, because the crosslinking bond is covalent and the downstream affinity purification is covalent, these samples may be washed very stringently and thus remove effectively all contaminating detergents.
+Thus, a mild detergent such as NP-40 can be included in the lysis buffer of these samples.
 
@@
   * Conjugates of protein-lipid-bead are covalently bound and can thus be stringently washed with detergent solutions to remove non-specific proteins.
-Detergent can then be removed with repeated washes of 8 M urea and 20 % acetonitrile.
-* Captured proteins can be reduced and alkylated on-bead. 
-* Peptides can be digested off the protein-lipid-bead conjugates via tryptic digest. Digested peptides are then desalted to remove any remaining contaminants using reverse phase desalting columns.
+Detergent can then be removed with repeated high volume washes of 8 M urea and 20 % acetonitrile.
+* Captured proteins are then reduced and alkylated on-bead. 
+* Peptides are digested off the protein-lipid-bead conjugates via tryptic digest. Digested peptides are then desalted to remove any remaining contaminants using reverse phase desalting columns.
 
-### Mass spectrometry analysis
+### Mass spectrometry analysis {#sec-MassSpectrometryAnalysis}
 

### 2025-02-07 SearchByProtein/SearchByProtein.qmd
EOD push - updates to overview pages, small changes to protein search

@@
 datatable(datawhole_reactive, 
-          caption = "'No hit' proteins are unenriched or depleted in the presence of probe, 'enriched candidates' are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and 'enriched hits' are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV",
           options = list(pageLength = 6,
-												 dom = "l<t>ipr"))
+												 dom = "l<t>ipr"),
+												 colnames = c("Gene Name", "Lipid Probe", "Hit Annotation", "logFC", "pvalue", "FDR", "Study Details"))
 
 ```
+
+"No hit" proteins are unenriched or depleted in the presence of probe, "enriched candidates" are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and "enriched hits" are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV
 

### 2025-02-10 Background/MultifunctionalLipidProbesOverview.qmd
eod update, updated drafts of overview pages

@@
     fig-height: 5
-    reference-doc: /custom-reference-doc.docx
+    reference-doc: /Users/gaelenguzman/LipidInteractomics_Website_local/LipidInteractomics_Website/Resources/custom-reference-doc.docx
 
@@
 
-:::{.callout-note collapse="true"}
-#### Diazirine ring
+#### Diazirine ring {#sec-Diazirine}
 
@@
 
-- The reactive carbene produced upon irradiation will bond with whatever molecule is nearest -- thus, the location of the diazirine ring can have a dramatic effect on what protein interactors are stabilized via crosslinking.
+The reactive carbene produced upon irradiation will bond with whatever molecule is nearest -- thus, the location of the diazirine ring can have a dramatic effect on what protein interactors are stabilized via crosslinking.
 
-- The majority of lipid analogs produced to date were synthesized with the diazirine ring near the terminal end of an acyl chain.
+The majority of lipid analogs produced to date were synthesized with the diazirine ring near the terminal end of an acyl chain.
 For example, [8-3 Fatty Acid](/LipidProbe/8-3_FattyAcid.qmd) has the acyl chain only 3 carbons from the end.
@@
 
-- In comparison, moving the diazirine ring closer to the hydrophilic headgroup may increase the partiality of crosslinking towards peripheral membrane proteins in addition to transmembrane proteins.
+In comparison, moving the diazirine ring closer to the hydrophilic headgroup may increase the partiality of crosslinking towards peripheral membrane proteins in addition to transmembrane proteins.
 An example of this shift is [1-10 Fatty Acid](/LipidProbe/1-10_FattyAcid.qmd), in which the diazirine ring was placed 10 carbons from the terminus of the chain.
-:::
 
-:::{.callout-note collapse="true"}
-#### Terminal Alkyne
+#### Terminal Alkyne {#sec-Alkyne}
 
@@
 It bridges the gap between traditional lipid research and modern bioorthogonal chemistry, allowing for precise studies of lipid function in living systems.
-:::
 
-:::{.callout-note collapse="true"}
-#### Coumarin Photocage
+#### Coumarin Photocage {#sec-Coumarin}
 Lipids play an essential role in cellular signaling, yet their biological study presents unique challenges due to their highly dynamic metabolism.
@@
 This dual functionality—serving as both a caging group and a fluorescent probe—makes coumarin a useful tool for studying lipid localization, uptake, and bioactivity.
-:::
 
@@
 * Quantification of +UV versus -UV
-  - The details of the quantitative mass spectrometry are describe in our [Overview of Proteomics Methods](Background/ProteomicsUsingMultifunctionalProbes.qmd), however, we hope to succinctly describe that quantitative mass spectrometry techniques necessarily require normalization at sample input level -- thereby exaggerating the abundance of proteins in the -UV control samples.
+  - The details of the quantitative mass spectrometry are describe in our [Overview of Proteomics Methods](ProteomicsUsingMultifunctionalProbes.qmd), however, we hope to succinctly describe that quantitative mass spectrometry techniques necessarily require normalization at sample input level -- thereby exaggerating the abundance of proteins in the -UV control samples.
   - It should be noted, therefore, that there is little meaning to a protein which is "enriched" toward the -UV condition.

### 2025-02-10 Background/ProteomicsUsingMultifunctionalProbes.qmd
eod update, updated drafts of overview pages

--- 2025-02-05 Background/ProteomicsUsingMultifunctionalProbes.qmd
@@
 ---
-title: "Background: Using multifunctional probes for proteomics"
+title: "Background: Proteomics with multifunctionalized lipid probes"
 format: 
@@
 ---
+
+**This repository is still under construction, please forgive us for incomplete sections as we build features!**
 
@@
 
-- Irradiation with 405 nm wavelength light induces the release of the coumarin photocage and thus allows for the recognition and metabolism of the headgroup of the lipid probe.
+Irradiation with 405 nm wavelength light induces the release of the coumarin photocage and thus allows for the recognition and metabolism of the headgroup of the lipid probe (See our [Coumarin overview](/Background/MultifunctionalLipidProbesOverview.qmd#sec-Coumarin) for more background on using the coumarin photocage).
 
-- Substantial work has validated that these lipid probes are recognized by the cell as their native counterparts, as the remaining functional groups have minimal effect on the probes'  biophysical properties.
+Substantial work has validated that these lipid probes are recognized by the cell as their native counterparts, as the remaining functional groups have minimal effect on the probes'  biophysical properties.
 This has been validated in numerous studies, including Höglinger et al.
@@
 
-- Irradiation with 355 nm wavelength light ()
+Irradiation with 355 nm wavelength light induces the production of a reactive carbene which readily inserts itself into any nearby biochemical bond (See our [Diazirine overview](/Background/MultifunctionalLipidProbesOverview.qmd#sec-Diazirine) for more background on diazirine crosslinking).
+Notably, the majority of probes will likely crosslink with either water or with neighboring lipids.
+Quantitative proteomics analysis will fully ignore these conjugates, as only enriched peptides will be measured in the final mass spectrometry analysis (described below in our [Mass spectrometry overview](@sec-MassSpectrometryAnalysis)).
 
-### Protein collection
+The covalently bound lipid protein conjugates which form after crosslinking are highly stable and thus are ideally amenable toward stringent enrichment and washing, producing a high-quality sample with few non-specific proteins tagging along.
 
-- Cell lysis
+### Cell lysis and sample collection
 
-- Affinity purification of probe-conjugated proteins
+Depending on application, may want to perform a membrane prep or otherwise isolate an organelle of interest (e.g. mitochondrial enrichment, if one is seeking mitochondrial interactions)
+
+Due to the high stability of the diazirine crosslinking bond, no extra steps need to be taken to ensure that interactions are maintained -- lysis can be as aggressive as one wishes.
+
+In general, samples due for mass spectrometry analysis should be kept with as little detergent as possible to protect the instrument -- however, because the crosslinking bond is covalent and the downstream affinity purification is covalent, these samples may be washed very stringently and thus remove effectively all contaminating detergents.
+Thus, a mild detergent such as NP-40 can be included in the lysis buffer of these samples.
+
+### Affinity purification of probe-conjugated proteins
+
+(See our [Alkyne overview](/Background/MultifunctionalLipidProbesOverview.qmd#sec-Alkyne) for more background on alkyne click chemistry)
+
 * Example using azide beads: Perform click chemistry reaction in presence of beads coated with picolyl-azide functional groups for covalent capture
 * Conjugates of protein-lipid-bead are covalently bound and can thus be stringently washed with detergent solutions to remove non-specific proteins.
-Detergent can then be removed with repeated washes of 8 M urea and 20 % acetonitrile.
-* Captured proteins can be reduced and alkylated on-bead. 
-* Peptides can be digested off the protein-lipid-bead conjugates via tryptic digest. Digested peptides are then desalted to remove any remaining contaminants using reverse phase desalting columns.
+Detergent can then be removed with repeated high volume washes of 8 M urea and 20 % acetonitrile.
+* Captured proteins are then reduced and alkylated on-bead. 
+* Peptides are digested off the protein-lipid-bead conjugates via tryptic digest. Digested peptides are then desalted to remove any remaining contaminants using reverse phase desalting columns.
 
-### Mass spectrometry analysis
+### Mass spectrometry analysis {#sec-MassSpectrometryAnalysis}
 
@@
 
-#### Label-based quantification
+#### Isotopic Label-based quantification
 
 All label-based mass spectrometry quantification methods use stable isotopes to distinguish the source of proteins within a pooled collective of several experimental samples.
-Previously, the technique known as Stable Isotope Labeling with Amino acids in Cell Culture (SILAC) was common, though this has fallen out of use due to cost and difficult sample preparation.
+Previously, the technique known as Stable Isotope Labeling with Amino acids in Cell Culture (SILAC) was common, though this has fallen out of use due to significant cost and difficult sample preparation.
 
-Modern label-based techniques such as iTRAQ (isotopic Tagging for Relative and Absolute  Quantification) and TMT (Tandem Mass Tagging) have become the norm.
+Modern isotopic label-based techniques such as iTRAQ (isotopic Tagging for Relative and Absolute  Quantification) and TMT (Tandem Mass Tagging) have become the norm.
+Isotopic labeling is a powerful quantitative mass spectrometry technique that enables the simultaneous analysis of multiple samples in a single MS run.
+This approach improves efficiency and allows for precise relative quantification of proteins across experimental conditions.
 For the purposes of this overview, we will focus on TMT as it has greater capacity for samples per experiment (16+ as opposed to 8), and the techniques are fundamentally similar.
-
-TMT labeling is a powerful quantitative mass spectrometry technique that enables the simultaneous analysis of multiple samples in a single MS run.
-This approach improves efficiency and allows for precise relative quantification of proteins across experimental conditions.
 

### 2025-02-10 BioinformaticsApplicationNote/GG_2025_applicationNote.qmd
eod update, updated drafts of overview pages

@@
 :::
+</br>
 
--   Column descriptions:
+**Column descriptions:**
+
   -   *Gene name or Accession Number*
@@
   -   *FDR*: False-discovery rate of protein identification
--   We are working on providing visualization functionality for studies which utilized Peptide Spectral Matching to report enrichment toward lipid probes.
+
+We are working on providing visualization functionality for studies which utilized Peptide Spectral Matching to report enrichment toward lipid probes.
 

### 2025-02-11 Background/MultifunctionalLipidProbesOverview.qmd
Incorporating CS edits to prove overview

@@
 Functionalized lipid probes are at the intersection of several niche biotechnologies.
-This overview will serve as a summary of the capabilities, nuances, and caveats of their utility.
+This overview will serve as a summary of the capabilities, nuances, and limitations of their utility.
 Additional resources and published review articles will be referenced and linked below for greater detail.
@@
 While proteins have long been the primary focus of interaction studies, lipids play an equally crucial yet often underappreciated role in cellular function.
+Therefore, there is a need for detailed knowledge of lipid-protein interactions (the lipid interactome), in healthy and diseased cells and tissue.
 
@@
 Lipids are primarily organized within membrane bilayers, where their interactions define critical membrane properties such as rigidity, fluidity, and resistance to detergents.
-By studying lipid-lipid interactomes, researchers can gain deeper insight into how these physical interactions influence membrane architecture and dynamics.
-Understanding these interactions is essential for unraveling fundamental processes like vesicle trafficking, cell signaling, and membrane compartmentalization.
+By studying lipid-lipid interactions and lipid interactomes, researchers will gain deeper insight into how these molecular interactions influence local and global membrane architecture and dynamics.
+Understanding these interactions and interactomes is essential for unraveling fundamental processes like vesicle trafficking, cell signaling, and membrane compartmentalization.
 
@@
 S1P binds to a specific family of receptors, triggering T cell migration (extravasation) and guiding their movement toward sites of infection.
-This highlights how lipid signaling can affect cellular behavior and physiological responses.
+Rapidly turned-over phosphatidylinositol 3,4,5-*tris*phosphate triggers cell survival, growth, movement, and proliferation.
+These examples  highlights how lipid signaling can affect cellular behavior and physiological responses.
 
@@
 The study of lipid biology has been greatly advanced by synthetic lipid analogs.
-However, it may not be immediately clear why such analogs are essential.
+However, it may not be immediately clear why such analogs are essential research tools.
 Unlike proteins and nucleic acids, lipids present unique challenges that make traditional genetic tools less effective in studying their function.
+In addition, synthetic lipid tools are designed to provide a defined composition of fatty acids and carbon backbones connected to a specific head group while genetic and pharmacological methods are more likely to produce a diverse group of lipid species.
 
@@
 Even minor modifications can significantly alter their biophysical properties and biological function.
-Unlike proteins, which can tolerate the addition of large fluorescent or affinity tags, lipids require minimal chemical modifications to preserve their activity.
+Unlike proteins, which can tolerate the addition of large fluorescent or affinity tags, lipids tolerate only minimal chemical modifications to preserve their activity.
 
 Additionally, lipids exist within a highly dynamic metabolic network, where they are continuously synthesized, modified, and degraded.
-Some signaling lipids, such as sphingosine, have extremely short half-lives—sometimes only minutes—making them difficult to track in real-time.
+Some signaling lipids, such as sphingosine, ceramide, and phosphatidic acid, have extremely short half-lives -- sometimes less than a minute -— making them difficult to track in real-time.
 
@@
 These modified lipids allow for precise investigation of lipid function while preserving their essential biological properties.
-The key modifications used in this approach include:
+The key modifications used in this approach include a photo-crosslinking group (usually a diazirine), an alkyne group for click chemistry, and a photo-removable (cage) group for preventing premature probe metabolism.:
 
-#### Diazirine ring {#sec-Diazirine}
+#### Diazirine group {#sec-Diazirine}
 
@@
 Several chemical groups can be used for covalent crosslinking, but diazirine rings are particularly well-suited for lipid studies due to their small size and minimal structural interference.
-Other crosslinking motifs may alter the lipid’s physicochemical properties, potentially changing its interaction profile.
-Diazirine, however, is the smallest known photoactivatable crosslinking group, making it an ideal choice for studying delicate lipid-protein interactions.
+Other crosslinking devices are mostly aromatic and hence may alter the lipid’s physicochemical properties, potentially changing its location and interaction profile.
+Non-aromatic diazirine, however, is the smallest known photoactivatable crosslinking group, making it an ideal choice for studying delicate lipid-protein interactions.
 
@@
 
-Lipid interactions are typically transient, as most lipids lack opportunities for strong hydrogen bonding and are too small to provide a significant binding interface.
+Lipid interactions are typically transient, as most lipid backbones lack opportunities for strong hydrogen bonding and are too small to provide a significant binding interface.
 Identifying interacting proteins requires stabilizing these interactions to allow for enrichment and analysis.
@@
 Upon exposure to 355 nm UV light, the diazirine ring forms a reactive carbene radical, which rapidly covalently bonds with nearby molecules.
-This reaction is highly versatile, as the carbene can insert into carbon-hydrogen, sulfur-hydrogen, nitrogen-hydrogen, oxygen-hydrogen, or double bonds, allowing for broad coverage of potential interaction partners\[\@haberkantFatFabulousBifunctional2014\].
+This reaction is highly versatile, as the carbene can insert into carbon-hydrogen, sulfur-hydrogen, nitrogen-hydrogen, oxygen-hydrogen, or double bonds, allowing for broad coverage of potential interaction partners[@haberkantFatFabulousBifunctional2014].Despite these numerous options, reaction with glutamate seems to be modestly preferred [@westDesignEvaluationCyclobutane2022].
 
@@
 
-##### The effect of Diazirine placement on crosslinking targets {#sec-DiazirinePlacement}
+##### The effect of diazirine placement on crosslinking targets {#sec-DiazirinePlacement}
 
@@
 The majority of lipid analogs produced to date were synthesized with the diazirine ring near the terminal end of an acyl chain.
-For example, [8-3 Fatty Acid](/LipidProbe/8-3_FattyAcid.qmd) has the acyl chain only 3 carbons from the end.
+For example, [8-3 Fatty Acid](/LipidProbe/8-3_FattyAcid.qmd) has diazirine on carbon 10 of the fatty acid.
 These lipid analogs may be expected to preferentially crosslink to proteins which penetrate far into the hydrophobic region between the leaflets of a membrane bilayer, such as transmembrane proteins.
@@
 In comparison, moving the diazirine ring closer to the hydrophilic headgroup may increase the partiality of crosslinking towards peripheral membrane proteins in addition to transmembrane proteins.
-An example of this shift is [1-10 Fatty Acid](/LipidProbe/1-10_FattyAcid.qmd), in which the diazirine ring was placed 10 carbons from the terminus of the chain.
+An example of this shift is [1-10 Fatty Acid](/LipidProbe/1-10_FattyAcid.qmd), in which the diazirine ring was diazirine on carbon 3 of the fatty acid.
 
@@
 
-The terminal alkyne is particularly useful because it undergoes azide-alkyne cycloaddition, a type of click chemistry reaction.
+The terminal alkyne is particularly useful because it undergoes azide-alkyne cycloaddition, the prototypical click chemistry reaction.
 This reaction is highly specific, rapid, and bio-orthogonal, meaning it does not interfere with natural cellular processes.
 By reacting the alkyne with an azide-containing probe, researchers can introduce fluorescent markers for imaging or affinity tags for isolating lipid-protein complexes.
+The reaction requires catalysis by copper (I) ions and is therefore usually not suitable for intact cells and tissues but works well in fixed or lysed samples.
 
@@
 
+By providing a simple yet effective means of modifying lipids without disrupting their native properties, the terminal alkyne has become an essential tool in lipidomics and chemical biology.
 One major application of the terminal alkyne is fluorescence labeling.
-A functionalized lipid can be introduced into cells and later reacted with a fluorophore-conjugated azide, allowing researchers to visualize its distribution and movement under a microscope.
-This approach provides insights into lipid localization and trafficking.
+A functionalized lipid can be introduced into cells and later reacted with a fluorophore-conjugated, ideally fluorogenic,  azide, allowing researchers to visualize the lipid's location in fixed cells.
+By using pulse-chase experiments, lipid movement is also trackable.
 
 Another important use is affinity-based enrichment.
-Lipids containing a terminal alkyne can be captured using azide-functionalized beads, enabling the isolation of lipid-protein complexes for analysis by mass spectrometry.
+Lipids containing a terminal alkyne can be captured using azide-functionalized beads, enabling the isolation of lipid-protein complexes after photo-crosslinking for analysis by mass spectrometry.
 This method has been instrumental in identifying proteins that interact with specific lipid species, shedding light on lipid signaling pathways and metabolic networks.
 
-By providing a simple yet effective means of modifying lipids without disrupting their native properties, the terminal alkyne has become an essential tool in lipidomics and chemical biology.
-It bridges the gap between traditional lipid research and modern bioorthogonal chemistry, allowing for precise studies of lipid function in living systems.
-
 #### Coumarin Photocage {#sec-Coumarin}
-Lipids play an essential role in cellular signaling, yet their biological study presents unique challenges due to their highly dynamic metabolism.
+Lipids play an essential role in cellular signaling which often relies on transient abundance of lipid species.
+Hence, studying lipids in intact cells presents unique challenges due to their highly dynamic metabolism.
 Unlike proteins, which are relatively stable once synthesized, many bioactive lipids are continuously synthesized, modified, interconverted, and degraded as part of an extensive and tightly regulated lipid metabolic network.
-This rapid turnover makes it difficult to study the effects of a specific lipid species in isolation, as the lipid of interest may be enzymatically altered before it can exert its intended biological function.
+Even lipids so far not associated with cellular signaling show rapid turnover, which makes it difficult to study the effects of a specific lipid species in isolation, as the lipid of interest may be enzymatically altered before it can exert its intended biological function.
 
 One strategy to overcome this challenge is using photocaged lipid analogs, which remain biologically inert until exposed to a specific wavelength of light.
-Irradiation with this wavelength "uncages" the analog to reveal its native structure.
+Irradiation with this wavelength "uncages" the lipid derivative within seconds to reveal its native structure.
 This allows researchers to control the timing and location of lipid activation, enabling targeted investigation of lipid function with high spatiotemporal resolution.
 
-##### A Light-Activated Protection Group
+##### A light-activated protection group
 
-One of the most effective tools for photocaging lipids is the coumarin cage, a photolabile protection group that can be removed upon exposure to 400 nm light.
+One of the most effective tools for photocaging lipids is based on 7-diethylamino-4-methylene coumarin, a photolabile protection group that can be removed upon exposure to 400 nm light.
 When attached to a lipid’s headgroup, the coumarin moiety temporarily blocks interactions with proteins, preventing the lipid from participating in its normal biological pathways.
@@
 This approach is useful for studying lipid-protein interactions, as uncaging the lipid in a controlled manner ensures that protein binders recognize the native lipid structure only when and where the researcher intends.
+
+An alternative to coumarin-based caging groups are o-nitrobenzyl.
 

### 2025-02-11 BioinformaticsApplicationNote/GG_2025_applicationNote.qmd
Incorporating CS edits to prove overview

@@
 authors:
-  - name: "Fikadu Tafesse"
-    affiliations:
-      - name:  "Oregon Health & Science University"
-        address: 3222 SW Research Dr
-        city: Portland
-        state: OR
-        postal-code: 97239
-    orcid: 0000-0002-8575-4164
-  - name: "Carsten Schultz"
-    affiliations:
-      - name:  "Oregon Health & Science University"
-        address: 3222 SW Research Dr
-        city: Portland
-        state: OR
-        postal-code: 97239
-    orcid: 0000-0002-5824-2171
   - name: "Gaelen Guzman"
@@
     email: gaelen.guzman@lipidinteractome.org
+  - name: "Carsten Schultz"
+    affiliations:
+      - name:  "Oregon Health & Science University"
+        address: 3222 SW Research Dr
+        city: Portland
+        state: OR
+        postal-code: 97239
+    orcid: 0000-0002-5824-2171
+  - name: "Fikadu Tafesse"
+    affiliations:
+      - name:  "Oregon Health & Science University"
+        address: 3222 SW Research Dr
+        city: Portland
+        state: OR
+        postal-code: 97239
+    orcid: 0000-0002-8575-4164
 format:
@@
 ---
+
+:::{.content-hidden when-format="html"}
+
+___
+<br>
+
+## Authors
+
+Gaelen Guzman^1,^*, Carsten Schulz^1^, Fikadu G. Tafesse^1^
+
+^1^ = Oregon Health & Science University; * = Corresponding author: <gaelen.guzman@lipidinteractome.org>
+:::
 

### 2025-02-11 Background/MultifunctionalLipidProbesOverview.qmd
Incorporating minor changes after weekly meeting

@@
 Every biological process—from metabolism to signaling—depends on the physical interactions between molecules, including proteins, nucleic acids, and lipids.
-While proteins have long been the primary focus of interaction studies, lipids play an equally crucial yet often underappreciated role in cellular function.
+While proteins have long been the primary focus of interaction studies, lipids play an equally crucial yet often under-appreciated role in cellular function.
 Therefore, there is a need for detailed knowledge of lipid-protein interactions (the lipid interactome), in healthy and diseased cells and tissue.
@@
 These modified lipids allow for precise investigation of lipid function while preserving their essential biological properties.
-The key modifications used in this approach include a photo-crosslinking group (usually a diazirine), an alkyne group for click chemistry, and a photo-removable (cage) group for preventing premature probe metabolism.:
+The key modifications used in this approach include a photo-crosslinking group (usually a diazirine), an alkyne group for click chemistry, and a photo-removable (cage) group for preventing premature probe metabolism.
 
@@
 
-##### A Versatile Bioorthogonal Handle
+##### A versatile bioorthogonal handle
 
@@
 The power of coumarin-caged lipids has been demonstrated in studies examining intracellular lipid signaling.
-For example, in 2015, Högliner et al.
+For example, in 2015, Höglinger et al.
 used a caged sphingosine analog to investigate the role of sphingosine in calcium signaling.
@@
 
-<!--
-## Photoactivatable & Clickable Probes / Bifunctional Lipid Probes
-
- -   The conceptual precursor to the so-called trifunctional probes, these typically include only the diazirine and the terminal alkyne moieties.
-
-References to include:
-
--   [@haberkantFatFabulousBifunctional2014] - Haberkant et al. 2014
-
-## Trifunctional Lipid Probes
--->
-
 ## Limitations of multifunctionalized lipid probes

### 2025-02-11 BioinformaticsApplicationNote/GG_2025_applicationNote.qmd
Incorporating minor changes after weekly meeting

@@
     orcid: 0000-0002-8575-4164
-format:
-  html:
-    embed-resources: true
-  docx:
-    fig-height: 5
-    reference-doc: /Users/gaelenguzman/LipidInteractomics_Website_local/LipidInteractomics_Website/Resources/custom-reference-doc.docx
+
 page-navigation: false
@@
 
-### Data Submission
+### Data Submission & Contact
 
 If you would like to submit a relevant dataset, see our [Data Submission Page](https://www.lipidinteractome.org/DataSubmission.html) for details, contact info, and instructions.
+For site feedback and additional questions, please email the site administrators at <Contact.Us@lipidinteractome.org>
 
@@
 | ...       |           ...            |   ...   |    ...     |  ...   |
-: Example data table for smooth incorporation into Lipid Interactome. {#tbl-1 .striped}
+: **Example data table for smooth incorporation into Lipid Interactome.** ***Column descriptions:*** *Gene name*: The identifier for genes identified in the dataset (or Accession Number).
+*Enrichment value*: Fold change of Experimental versus Control fold-change, typically log2-transformed -- ideally the product of TMT or other quantitative mass spectrometry methods.
+*p value*: the results of an ANOVA or LIMMA analysis, corrected for multiple hypothesis testing.
+*AveExpr*: An averaged value of the m/z ion intensity of the Experimental condition and Control condition used for the enrichment value (used to prepare MA plots for quality control).
+*FDR*: False-discovery rate of protein identification.
+{#tbl-1 .striped}
 
@@
 </br>
-
-**Column descriptions:**
-
-  -   *Gene name or Accession Number*
-  -   *Enrichment value*: Fold change of Experimental versus Control fold-change, typically log2-transformed -- ideally the product of TMT or other quantitative mass spectrometry methods.
-  -   *p value*: the results of an ANOVA or LIMMA analysis, corrected for multiple hypothesis testing
-  -   *AveExpr*: An averaged value of the m/z ion intensity of the Experimental condition and Control condition used for the enrichment value (used to prepare MA plots for quality control)
-  -   *FDR*: False-discovery rate of protein identification
 
@@
 
-## Acknowledgements
+## Contributions
 
--   Andre Nadler
--   Frank Stein
--   Per Haberkant
+GG designed, implemented, and wrote the majority of the LipidInteractome site and manuscript.
+FS wrote the data analysis section of the site, provided significant intellectual contribution to the site design, and edited the manuscript.
+AN provided substantial editing of the site and manuscript.
+CS and FT provided significant intellectual contribution and text editing of the site and manuscript, and oversaw the site development.
 
@@
 The authors have no conflicts of interest to declare.
-
-{{< pagebreak >}}
-
-## References

### 2025-02-12 Background/DataAnalysisAndStatistics.qmd
updated data analysis background page

@@
 
-* Studies included in this repository which used identical FRAG Pipe TMT pipeline:
-	- Thomas et al., 2025[@thomasTrifunctionalLipidDerivatives2025]
-	- Farley et al., 2024 (A)[@farleyTrifunctionalSphinganineNew2024a]
-	- Farley et al., 2024 (B)[@farleyTrifunctionalFattyAcid2024]
+Dr.
+Frank Stein developed and implemented the data analysis pipeline at the European Molecular Biosciences Laboratories in Heidelberg, Germany.
+The mass spectrometry (MS) data were processed using IsobarQuant[@mateusThermalProteomeProfiling2016] and Mascot V.24 (Matrix Science), following the methodology previously described by Farley et al.
+(2024, A), Farley et al.
+(2024, B), and Thomas et al (2025)[@farleyTrifunctionalSphinganineNew2024a; @farleyTrifunctionalFattyAcid2024; @thomasTrifunctionalLipidDerivatives2025].
+To ensure robust protein identification, the analysis utilized a reverse UniProt FASTA database that included common contaminants.
+Proteins were only included in the final analysis if they contained at least two unique peptides, each with a minimum length of seven amino acids, and met a stringent false discovery rate (FDR) threshold of 0.01.
+
+The acquired MS spectra were searched for specific peptide modifications, including fixed modifications (carbamidomethylation of cysteine and TMT-16-plex labeling of lysine) and variable modifications (N-terminal acetylation, methionine oxidation, and N-terminal TMT-16-plex labeling).
+Mass error tolerances were set to 10 ppm for full-scan MS spectra and 0.02 Da for MS/MS spectra, with a maximum of two missed cleavage sites permitted.
+To correct for batch effects across experimental replicates, a variance stabilization normalization was applied to log~2~-transformed raw data[@huberVarianceStabilizationApplied2002].
+Changes in protein abundance between experimental and control conditions were assessed using LIMMA analysis[@ritchieLimmaPowersDifferential2015].
+
+For the protein-lipid probe interaction experiments presented here (+/- UV exposure), proteins were classified as "enriched hits” if they showed at least a log~2~ fold-change of 1 toward the +UV condition with a p-value < 0.05.
+Proteins enriched under +UV conditions but with p-values > 0.05 were labeled as “enriched candidates.”
 
@@
 	- Muller et al., 2021[@mullerSynthesisCellularLabeling2021]
+
+* Need these details.

### 2025-02-12 BioinformaticsApplicationNote/GG_2025_applicationNote.qmd
updated data analysis background page

@@
 
-| Gene name | Enrichment value (logFC) | p value |  AveExpr   |  FDR   |
+| Gene name | logFC | p value |  AveExpr   |  FDR   |
 |:----------|:------------------------:|:-------:|:----------:|:------:|
@@
 : **Example data table for smooth incorporation into Lipid Interactome.** ***Column descriptions:*** *Gene name*: The identifier for genes identified in the dataset (or Accession Number).
-*Enrichment value*: Fold change of Experimental versus Control fold-change, typically log2-transformed -- ideally the product of TMT or other quantitative mass spectrometry methods.
+*logFC*: Fold change of Experimental versus Control fold-change, typically log2-transformed -- ideally the product of TMT or other quantitative mass spectrometry methods.
 *p value*: the results of an ANOVA or LIMMA analysis, corrected for multiple hypothesis testing.

### 2025-02-18 Background/DataAnalysisAndStatistics.qmd
First commit of the week

--- 2025-01-31 Background/DataAnalysisAndStatistics.qmd
@@
 
-* Studies included in this repository which used identical FRAG Pipe TMT pipeline:
-	- Thomas et al., 2025[@thomasTrifunctionalLipidDerivatives2025]
-	- Farley et al., 2024 (A)[@farleyTrifunctionalSphinganineNew2024a]
-	- Farley et al., 2024 (B)[@farleyTrifunctionalFattyAcid2024]
+To ensure consistency across all publicly available mass spectrometry datasets that used TMT isobaric mass tagging, we applied the same standardized analysis pipeline previously published.
+This approach allows for better comparability between datasets.
+Several of the datasets included in this repository were generated and analyzed at the European Molecular Biosciences Laboratories (EMBL) in Heidelberg, Germany, where Dr.
+Frank Stein developed and implemented the data analysis pipeline.
+In summary, we processed the mass spectrometry (MS) data using FragPipe[@yuAnalysisDIAProteomics2023], following established methodologies outlined in Farley et al.
+(2024, A), Farley et al.
+(2024, B), and Thomas et al.
+(2025)[@farleyTrifunctionalSphinganineNew2024a; @farleyTrifunctionalFattyAcid2024; @thomasTrifunctionalLipidDerivatives2025].
+To ensure accurate protein identification, we used a UniProt FASTA database that included common contaminants and reversed sequences for validation.
+Proteins were included in the final dataset only if they contained at least two unique peptides, each at least seven amino acids long.
+
+To account for potential technical variations across experiments, we applied a normalization step using the 'removeBatchEffect' function from the limma package, stabilizing variance in log2-transformed TMT reporter ion intensities[@huberVarianceStabilizationApplied2002; @ritchieLimmaPowersDifferential2015].
+Further normalization was carried out using the 'normalizeVSN' function of the same package.
+We identified differentially expressed proteins using the moderated t-test within limma, incorporating replicate information into the statistical model through the 'lmFit' function.
+
+For the protein-lipid probe interaction experiments (+/- UV exposure), proteins were categorized based on their enrichment in the +UV condition.
+Proteins showing a log2 fold-change of at least 1 and a p-value below 0.05 were classified as "enriched hits," while those showing similar enrichment trends but with p-values above 0.05 were labeled as “enriched candidates.”
+
+To better understand the biological significance of the detected proteins, we conducted gene ontology (GO) enrichment analysis using the 'compareCluster' function from the 'clusterProfiler' package[@yuClusterProfilerPackageComparing2012].
+This method evaluates whether specific GO terms are overrepresented in the dataset compared to a background gene set.
+We performed enrichment analysis for three GO categories: Cellular Component (CC), Molecular Function (MF), and Biological Process (BP).
+The reference database used was 'org.Pf.plasmo.db.' To quantify enrichment, we calculated the odds ratio by comparing the proportion of genes associated with each GO term in our dataset ('GeneRatio') with the proportion in the reference background set ('BgRatio').
+A value greater than 1 suggests that a given GO term is more prevalent in our dataset than expected by chance.
 

### 2025-02-18 BioinformaticsApplicationNote/GG_2025_applicationNote.qmd
First commit of the week

@@
 : **Example data table for smooth incorporation into Lipid Interactome.** ***Column descriptions:*** *Gene name*: The identifier for genes identified in the dataset (or Accession Number).
-*logFC*: Fold change of Experimental versus Control fold-change, typically log2-transformed -- ideally the product of TMT or other quantitative mass spectrometry methods.
+*Enrichment value*: Fold change of Experimental versus Control fold-change, typically log2-transformed -- ideally the product of TMT or other quantitative mass spectrometry methods.
 *p value*: the results of an ANOVA or LIMMA analysis, corrected for multiple hypothesis testing.

### 2025-02-18 Resources/R_sandbox.R

@@ -1,0 +1,48 @@
+library(BiocManager)
+library(limma)
+library(GEOquery)
+library(msigdbr)
+library(fgsea)
+library(clusterProfiler)
+
+# install.packages("clusterProfiler")
+# BiocManager::install(c("GenomicFeatures", "AnnotationDbi"))
+# BiocManager::install("clusterProfiler")
+# BiocManager::install("fgsea")
+# BiocManager::install("limma")
+# BiocManager::install("GEOquery")
+
+
+gse200250 <- getGEO("GSE200250", AnnotGPL = TRUE)[[1]]
+
+es <- gse200250
+es <- es[, grep("Th2_", es$title)]
+es$time <- as.numeric(gsub(" hours", "", es$`time point:ch1`))
+es <- es[, order(es$time)]
+
+exprs(es) <- normalizeBetweenArrays(log2(exprs(es)), method="quantile")
+
+es <- es[order(rowMeans(exprs(es)), decreasing=TRUE), ]
+es <- es[!duplicated(fData(es)$`Gene ID`), ]
+rownames(es) <- fData(es)$`Gene ID`
+es <- es[!grepl("///", rownames(es)), ]
+es <- es[rownames(es) != "", ]
+
+fData(es) <- fData(es)[, c("ID", "Gene ID", "Gene symbol")]
+
+head(fData(es))
+
+es <- es[head(order(rowMeans(exprs(es)), decreasing=TRUE), 12000), ]
+
+head(exprs(es))
+
+pathwaysDF <- msigdbr("mouse", category="H")
+pathways <- split(as.character(pathwaysDF$entrez_gene), pathwaysDF$gs_name)
+head(pathways)
+
+set.seed(1)
+gesecaRes <- geseca(pathways, exprs(es), minSize = 15, maxSize = 500)
+
+head(gesecaRes, 10)
+
+

### 2025-02-20 IndividualStudies/DH_2017.qmd
Spent all day learning how to make my heatmap look less bad

@@
 library(here)
+library(heatmaply)
+library(ggvenn)
+library(scales)
 
@@
 
-DH_2017_data <- read.csv("DataTables/DH_PNAS_2017_download.csv") |>
+DH_2017_data <- read.csv(paste0(here(),"/IndividualStudies/DataTables/DH_PNAS_2017_download.csv")) |>
   mutate(gene_name = str_extract(Description, "GN=([^\\s]+)") |> str_remove("GN=")) |>
@@
   select(gene_name, PSM_Sph, PSM_FA, PSM_DAG) |>
-
-  glimpse()
-
+  arrange(gene_name) |>
+  group_by(gene_name) |>
+  summarise(PSM_DAG = mean(PSM_DAG),
+            PSM_FA = mean(PSM_FA),
+            PSM_Sph = mean(PSM_Sph))
 ```
@@
 #### Heat map
+:::{.border}
+```{r, echo=FALSE, fig.height=10}
 
-```{r, echo=FALSE, warning=FALSE, fig.height=15}
+DH_2017_data_long <- DH_2017_data |>
+  pivot_longer(cols = starts_with("PSM_"),
+              names_to = "variable",
+              names_prefix = "PSM_",
+              values_to = "value") |>
+  mutate(name = gene_name) |>
+  select(name, variable, value)
+  # mutate(OriginalValues = value) |>
+  # mutate(value = case_when(value < 20 ~ value,
+  #                           value >= 20 ~ 20))
 
-DH_2017_data_long <- read.csv("DataTables/DH_PNAS_2017_long.csv") |>
-  mutate(PSM = value, sample = name) |>
-  group_by(gene_name, sample) |>
-  summarise(PSM = mean(PSM, na.rm = TRUE), .groups = "drop") |>
-  distinct()
+DH_2017_data_long$variable <- factor(pull(DH_2017_data_long, variable), ordered = TRUE, levels = c("Sph", "FA", "DAG"))
 
-DH_2017_data_long$sample <- factor(pull(DH_2017_data_long, sample), ordered = TRUE, levels = c("Sph", "FA", "DAG"))
-
-heatmap <- DH_2017_data_long |>
-  ggplot(aes(y = gene_name, x = sample)) +
-  theme(panel.border = element_rect(color = NA, fill = "grey25")) +
-  geom_tile(aes(fill = PSM, text = paste0("Gene name: ", gene_name, '\n', "Lipid Probe:", sample, "\n", "PSM: ", PSM))) +
-  scale_fill_gradientn(colors = c("grey95", "purple", "orange"),
-  values = scales::rescale(c(0, 10, 25))) +
-  ylab("Gene") +
-  xlab("Lipid Probe") +
-  theme_minimal() +
-  theme(text = element_text(family = "serif")) +
-  theme(legend.title = element_text(size = 12, face = "bold")) +
-  theme(axis.title = element_text(size = 12, face = "bold")) +
-  theme(legend.text = element_text(size = 12))
-
-m <- list(l=50, r = 50, b= 100, pad = 4)
-
-ggplotly(heatmap,
-        tooltip = c("text", dynamicTicks = TRUE),
-        hovermode = "closest",
-        autosize = T,
-        margin = m) |>
-  layout(showlegend = FALSE)
+# Create the heatmap
+heatmaply(long_data = DH_2017_data_long,
+          xlab = "Probe",
+          ylab = "Gene name",
+          label_names = c("Gene name", "Probe", "PSM count"),
+          scale_fill_gradient_fun = ggplot2::scale_fill_gradientn(colours = c("grey95", "purple", "orange", "orange", "orange", "orange", "orange", "red", "red","red"), breaks = c(0, 5, 20, 200)),
+          showticklabels = F)
 
 ```
+:::
+
+<hr>
 
 #### Venn Diagram
+
+:::{.border}
+```{r, echo=FALSE, warning=FALSE, height = 5}
+
+# Ensure the data is in the correct format
+DH_2017_data <- as.data.frame(DH_2017_data)
+rownames(DH_2017_data) <- DH_2017_data[,1]
+DH_2017_data[,1] <- NULL
+
+Sph_proteins <- DH_2017_data |>
+  filter(PSM_Sph > 0) |>
+  select(PSM_Sph)
+
+FA_proteins <- DH_2017_data |>
+  filter(PSM_FA > 0) |>
+  select(PSM_FA)
+
+DAG_proteins <- DH_2017_data |>
+  filter(PSM_DAG > 0) |>
+  select(PSM_DAG)
+
+combined_venn_proteins <- list("Sph proteins" = rownames(Sph_proteins), "FA proteins" = rownames(FA_proteins), "DAG proteins" = rownames(DAG_proteins))
+
+ggvenn(combined_venn_proteins)
+
+```
+:::
 

### 2025-02-20 LipidProbe/1-10_FattyAcid.qmd
adding protein search page, though still work in progress
Spent all day learning how to make my heatmap look less bad

@@
   ref-hyperlink: true # (default is true)
+prefer-html: true
 html: default

### 2025-02-20 Resources/ggplot_styles.R

@@ -5,11 +5,16 @@ library(ggrepel)
 library(emojifont)
 library(dplyr)
 library(tidyr)
+library(docstring)
 
 # Define a helper function that safely applies abs()
 safe_abs <- function(x, default = NA) {
+  #' Performs some error handling in the event of NA in joined datasets -- intended to be used while finding the limits of ggplots, as in VolcanoPlotStandardized.
+  #' Takes an input, tries to coerce it into a numeric, performs the abs() operation on it
+  #' Returns an input default value so the user can use trial and error.
+ 
   tryCatch({
-    # Ensure that x is numeric before taking abs()
+    # Ensures that x is numeric before taking abs()
     abs(as.numeric(x))
   }, error = function(e) {
     default
@@ -17,17 +22,25 @@ safe_abs <- function(x, default = NA) {
 }
 
 safe_log10 <- function(x, default = NA) {
-    tryCatch({
-        # Ensure that x is numeric before taking log10()
+  #' Takes an input, tries to coerce it into a numeric, performs the  log10() operation on it
+  #' Performs some error handling in the event of NA in joined datasets -- intended to be used while finding the limits of ggplots, as in VolcanoPlotStandardized.
+  #' Returns an input default value so the user can use trial and error.
+  
+     tryCatch({
+        # Ensures that x is numeric before taking log10()
         log10(as.numeric(x))
     }, error = function(e) {
         default
     })
 }
 
-# A standardized MA plot function
+
 
 MAStandard <- function(data) {
+    #' A standardized MA plot function
+    #' Receives a dataframe. Needs to have the following columns for the aes() to work: AveExpr, logFC, hit_annotation, gene_name.
+    #' Dynamically determines the limits of the plot under the scale_x/y_scontinuous calls
+    #' Produces first a facet-wrapped ggplot, then converts it to a plotly plot.
 
     MAPlots <- data |>
         ggplot(aes(x = AveExpr,
@@ -39,11 +52,12 @@ MAStandard <- function(data) {
                    size = factor(hit_annotation))) +
         geom_point(aes(text = paste0("Gene name: ", gene_name, "\n",
                                     "LogFC: ", logFC, "\n",
-                                    "p-value: ", pvalue, "\n"))) +
+                                    "p-value: ", pvalue, "\n",
+                                    "AveExper: ", AveExpr, "\n"))) +
[…]

### 2025-02-20 IndividualStudies/DH_2017.qmd
Spent forever tweaking venn and table for dh_2017, now done

@@
 <!-- R setup, reading data tables, wrangling data -->
-```{r setup, echo=FALSE, include=FALSE}
+```{r setup, echo=FALSE, include=FALSE, warning=FALSE}
 
@@
 :::{.border}
-```{r, echo=FALSE, fig.height=10}
+```{r, echo=FALSE, fig.height=10, warning=FALSE}
 
@@
 :::{.border}
-```{r, echo=FALSE, warning=FALSE, height = 5}
+```{r, echo=FALSE, warning=FALSE, width = 8}
 
 # Ensure the data is in the correct format
-DH_2017_data <- as.data.frame(DH_2017_data)
-rownames(DH_2017_data) <- DH_2017_data[,1]
-DH_2017_data[,1] <- NULL
+DH_2017_data_AddingRownames <- as.data.frame(DH_2017_data)
+rownames(DH_2017_data_AddingRownames) <- DH_2017_data_AddingRownames[,1]
+DH_2017_data_AddingRownames[,1] <- NULL
 
-Sph_proteins <- DH_2017_data |>
+Sph_proteins <- DH_2017_data_AddingRownames |>
   filter(PSM_Sph > 0) |>
@@
 
-FA_proteins <- DH_2017_data |>
+FA_proteins <- DH_2017_data_AddingRownames |>
   filter(PSM_FA > 0) |>
@@
 
-DAG_proteins <- DH_2017_data |>
+DAG_proteins <- DH_2017_data_AddingRownames |>
   filter(PSM_DAG > 0) |>
@@
 
-ggvenn(combined_venn_proteins)
+ggvenn <- ggvenn(combined_venn_proteins,
+                      show_percentage = FALSE,
+                      show_elements = FALSE,
+                      fill_color = c("orange", "purple", "blue")) +
+        labs(x = "", y = "") +
+        theme_minimal()
+
+ggvenn
 
 ```
+
+```{r, echo=FALSE, warning=FALSE}
+
+DH_2017_data <- DH_2017_data |>
+  mutate(VennRegion = case_when(
+    (PSM_Sph > 0 & PSM_DAG > 0 & PSM_FA > 0) ~ "Enriched to all probes",
+    (PSM_Sph > 0 & PSM_DAG == 0 & PSM_FA == 0) ~ "Enriched to Sph only",
+    (PSM_Sph == 0 & PSM_DAG > 0 & PSM_FA == 0) ~ "Enriched to DAG only",
+    (PSM_Sph == 0 & PSM_DAG == 0 & PSM_FA > 0) ~ "Enriched to FA only",
+    (PSM_Sph > 0 & PSM_DAG > 0 & PSM_FA == 0) ~ "Enriched to Sph and DAG",
+    (PSM_Sph > 0 & PSM_DAG == 0 & PSM_FA > 0) ~ "Enriched to Sph and FA",
+    (PSM_Sph == 0 & PSM_DAG > 0 & PSM_FA > 0) ~ "Enriched to DAG and FA"))
+
+DH_2017_data$VennRegion <- factor(pull(DH_2017_data, VennRegion), ordered = TRUE, levels = c("Enriched to Sph only", "Enriched to DAG only", "Enriched to FA only", "Enriched to Sph and DAG", "Enriched to Sph and FA", "Enriched to DAG and FA", "Enriched to all probes"))
+
+DH_2017_data_reactive <- crosstalk::SharedData$new(DH_2017_data)
+
+htmltools::tags$div(
+  class = "filter-container",
+  filter_checkbox(id = "Overlap",
+                  label = "Select overlap regions to see co-enriched proteins:",
+                  sharedData = DH_2017_data_reactive,
+                  group = ~VennRegion,
+                  inline = TRUE)
+)
+
+## Displays the reactive dataframe
+datatable(DH_2017_data_reactive, options = list(pageLength = 20))
+
+```
+
 :::

### 2025-02-20 ShinyApps/LipidInteractomics_ShinyApp/app.R

@@ -4,9 +4,10 @@ library(ggplot2)
 library(plotly)
 library(readr)
 library(shiny)
+library(here)
 
 # File path for testing
-df <- read_csv("LipidProbe/DataSets/LipidInteractomics_ShinyApp/combinedProbeDatasets_TMT.csv")
+df <- read_csv(paste0(here(), "/ShinyApps/LipidInteractomics_ShinyApp/combinedProbeDatasets_TMT.csv"))
 
 # File path for deploying to Shinyapps.io
 #df <- read_csv("combinedProbeDatasets_TMT.csv")
@@ -20,13 +21,11 @@ ui <- fluidPage(
   sidebarLayout(
     sidebarPanel(
       selectInput("probe1", "Select First LipidProbe:", choices = probeOptions, selected = probeOptions[1]),
-      selectInput("probe2", "Select Second LipidProbe:", choices = probeOptions, selected = probeOptions[2]),
-			selectInput("probe3", "Select Third LipidProbe (Beta):", choices = probeOptions, selected = probeOptions[3])
+      selectInput("probe2", "Select Second LipidProbe:", choices = probeOptions, selected = probeOptions[2])
     ),
     mainPanel(
       plotlyOutput("logFCPlot"),
 
-			plotlyOutput("logFCPlot3dDemo")
     )
   )
 )

### 2025-02-20 ShinyApps/LipidInteractomics_VennDiagramsApp/app.R

@@ -8,8 +8,9 @@ library(amVennDiagram5)
 library(ggVennDiagram)
 library(VennDiagram)
 library(ggvenn)
+library(here)
 
-Venn_df <- read_csv("/Users/gaelenguzman/LipidInteractomics_Website_local/LipidInteractomics_Website/LipidProbe/DataSets/LipidInteractomics_VennDiagramsApp/combinedProbeDatasets_VennDiagram.csv")
+Venn_df <- read_csv(paste0(here(), "/ShinyApps/LipidInteractomics_VennDiagramsApp/combinedProbeDatasets_VennDiagram.csv"))
 
 probeOptions <- unique(Venn_df$LipidProbe)
 

### 2025-02-20 ShinyApps/VennDiagram_DH/app.R

@@ -1,0 +1,202 @@
+
+## intitialize libraries
+library(dplyr)
+library(tidyr)
+library(plotly)
+library(ggplot2)
+library(grid)
+library(readr)
+library(rmarkdown)
+library(emojifont)
+library(gt)
+library(crosstalk)
+library(DT)
+library(stringr)
+library(pheatmap)
+library(here)
+library(heatmaply)
+library(ggvenn)
+library(scales)
+library(shiny)
+
+## Opening the source file for the ggplot custom theme
+source(paste0(here(), "/Resources/ggplot_styles.R"))
+
+DH_2017_data <- read.csv(paste0(here(),"/IndividualStudies/DataTables/DH_PNAS_2017_download.csv")) |>
+  mutate(gene_name = str_extract(Description, "GN=([^\\s]+)") |> str_remove("GN=")) |>
+  mutate(Species = str_extract(Description, "OS=([^=]+?)\\sGN=") |> str_remove("OS=") |> str_remove("GN=")) |>
+  filter(Species == "Homo sapiens ") |>
+  mutate(PSM_Sph = (PSM_Sph1 + PSM_Sph2) / 2,
+         PSM_FA = (PSM_FA1 + PSM_FA2) / 2,
+         PSM_DAG = (PSM_DAG1 + PSM_DAG2) /2) |>
+  select(gene_name, PSM_Sph, PSM_FA, PSM_DAG) |>
+  arrange(gene_name) |>
+  group_by(gene_name) |>
+  summarise(PSM_DAG = mean(PSM_DAG),
+            PSM_FA = mean(PSM_FA),
+            PSM_Sph = mean(PSM_Sph))
+
+	
+# Ensure the data is in the correct format
+DH_2017_data_AddingRownames <- as.data.frame(DH_2017_data)
+rownames(DH_2017_data_AddingRownames) <- DH_2017_data_AddingRownames[,1]
+DH_2017_data_AddingRownames[,1] <- NULL
+
+Sph_proteins <- DH_2017_data_AddingRownames |>
+  filter(PSM_Sph > 0) |>
+  select(PSM_Sph)
+
+FA_proteins <- DH_2017_data_AddingRownames |>
+  filter(PSM_FA > 0) |>
+  select(PSM_FA)
+
+DAG_proteins <- DH_2017_data_AddingRownames |>
+  filter(PSM_DAG > 0) |>
+  select(PSM_DAG)
+
+
[…]

### 2025-02-21 IndividualStudies/AT_2025.qmd
Adding Gene Ontology search

@@
 
+## Gene Ontology enrichment
+
+**In beta: GO analysis still under development**
+
+::: {.panel-tabset}
+
+#### Cell Compartment
+
+:::{.border}
+```{r, echo=FALSE, warning=FALSE}
+
+suppressMessages(CC_enrichment_plots(AT_2025_Long, "dot"))
+
+suppressMessages(CC_enrichment_plots(AT_2025_Long, "cnet"))
+```
+:::
+
+#### Molecular Function
+
+:::{.border}
+```{r, echo=FALSE, warning=FALSE}
+
+suppressMessages(MF_enrichment_plots(AT_2025_Long, "dot"))
+
+suppressMessages(MF_enrichment_plots(AT_2025_Long, "cnet"))
+
+```
+:::
+
+#### Biological Process
+
+:::{.border}
+```{r, echo=FALSE, warning=FALSE}
+
+suppressMessages(BP_enrichment_plots(AT_2025_Long, "dot"))
+
+suppressMessages(BP_enrichment_plots(AT_2025_Long, "cnet"))
+
+```
+:::
+
+:::
+
 ## Enriched proteins

### 2025-02-21 IndividualStudies/DH_2017.qmd
Adding Gene Ontology search

@@
 library(stringr)
-library(pheatmap)
 library(here)
@@
 library(scales)
-
 ## Opening the source file for the ggplot custom theme
@@
          PSM_DAG = (PSM_DAG1 + PSM_DAG2) /2) |>
-  select(gene_name, PSM_Sph, PSM_FA, PSM_DAG) |>
+  dplyr::select(gene_name, PSM_Sph, PSM_FA, PSM_DAG) |>
   arrange(gene_name) |>
@@
 #### Heat map
+
+Depicted below are the average PSM count for two replicates each of UV-irradiated samples treated with trifunctionalized Sph, DAG, and FA.
 :::{.border}
@@
   mutate(name = gene_name) |>
-  select(name, variable, value)
+  dplyr::select(name, variable, value)
   # mutate(OriginalValues = value) |>
@@
   filter(PSM_Sph > 0) |>
-  select(PSM_Sph)
+  dplyr::select(PSM_Sph)
 
@@
   filter(PSM_FA > 0) |>
-  select(PSM_FA)
+  dplyr::select(PSM_FA)
 
@@
   filter(PSM_DAG > 0) |>
-  select(PSM_DAG)
+  dplyr::select(PSM_DAG)
 

### 2025-02-21 IndividualStudies/SF_2024.qmd
Adding Gene Ontology search

@@
 :::
+:::
+
+## Gene Ontology enrichment
+
+**In beta: GO analysis still under development**
+
+::: {.panel-tabset}
+
+#### Cell Compartment
+
+:::{.border}
+```{r, echo=FALSE, warning=FALSE}
+
+suppressMessages(CC_enrichment_plots(SF_2024_data, "dot"))
+
+suppressMessages(CC_enrichment_plots(SF_2024_data, "cnet"))
+```
+:::
+
+#### Molecular Function
+
+:::{.border}
+```{r, echo=FALSE, warning=FALSE}
+
+suppressMessages(MF_enrichment_plots(SF_2024_data, "dot"))
+
+suppressMessages(MF_enrichment_plots(SF_2024_data, "cnet"))
+
+```
+:::
+
+#### Biological Process
+
+:::{.border}
+```{r, echo=FALSE, warning=FALSE}
+
+suppressMessages(BP_enrichment_plots(SF_2024_data, "dot"))
+
+suppressMessages(BP_enrichment_plots(SF_2024_data, "cnet"))
+
+```
+:::
 
@@
 
-## Enriched Proteins
+## Data exploration and download
 
@@
 SF_2024_data <- SF_2024_data |>
-  select(gene_name, LipidProbe, hit_annotation, logFC, pvalue, fdr) |>
+  dplyr::select(gene_name, LipidProbe, hit_annotation, logFC, pvalue, fdr) |>
   mutate(logFC = signif(logFC, digits=3),

### 2025-02-21 IndividualStudies/SF_2024_B.qmd
Adding Gene Ontology search

@@
 # Opening the datatable for this page IN FINAL RENDER
-SF_2024_data <- readr::read_csv("DataTables/SF_Chem_Comm_2024_download.csv")
+SF_2024_data <- readr::read_csv(paste0(here(), "/IndividualStudies//DataTables/SF_Chem_Comm_2024_download.csv"))
 
@@
 
-## Enriched Proteins
+## Gene Ontology enrichment
+
+**In beta: GO analysis still under development**
+
+::: {.panel-tabset}
+
+#### Cell Compartment
+
+:::{.border}
+```{r, echo=FALSE, warning=FALSE}
+
+suppressMessages(CC_enrichment_plots(SF_2024_data, "dot"))
+
+suppressMessages(CC_enrichment_plots(SF_2024_data, "cnet"))
+```
+:::
+
+#### Molecular Function
+
+:::{.border}
+```{r, echo=FALSE, warning=FALSE}
+
+suppressMessages(MF_enrichment_plots(SF_2024_data, "dot"))
+
+suppressMessages(MF_enrichment_plots(SF_2024_data, "cnet"))
+
+```
+:::
+
+#### Biological Process
+
+:::{.border}
+```{r, echo=FALSE, warning=FALSE}
+
+suppressMessages(BP_enrichment_plots(SF_2024_data, "dot"))
+
+suppressMessages(BP_enrichment_plots(SF_2024_data, "cnet"))
+
+```
+:::
+
+:::
+
+## Data exploration and download
 

### 2025-02-21 LipidProbe/1-10_FattyAcid.qmd
Adding Gene Ontology search

@@
 :::
+:::
 
-##### Data
+## Gene Ontology enrichment
+
+**In beta: GO analysis still under development**
+
+::: {.panel-tabset}
+
+#### Cell Compartment
+
+:::{.border}
+```{r, echo=FALSE, warning=FALSE}
+
+suppressMessages(CC_enrichment_plots(SF_2024_data, "dot"))
+
+suppressMessages(CC_enrichment_plots(SF_2024_data, "cnet"))
+```
+:::
+
+#### Molecular Function
+
+:::{.border}
+```{r, echo=FALSE, warning=FALSE}
+
+suppressMessages(MF_enrichment_plots(SF_2024_data, "dot"))
+
+suppressMessages(MF_enrichment_plots(SF_2024_data, "cnet"))
+
+```
+:::
+
+#### Biological Process
+
+:::{.border}
+```{r, echo=FALSE, warning=FALSE}
+
+suppressMessages(BP_enrichment_plots(SF_2024_data, "dot"))
+
+suppressMessages(BP_enrichment_plots(SF_2024_data, "cnet"))
+
+```
+:::
+:::
+
+## Data exploration and download
 

### 2025-02-21 LipidProbe/8-3_FattyAcid.qmd
Spent all day learning how to make my heatmap look less bad
Adding Gene Ontology search

@@
 title: "Trifunctional 8-3 Fatty Acid"
+crossref: 
+  ref-hyperlink: true # (default is true)
+prefer-html: true
 html: default
@@
 :::
+:::
 
-##### Data
+## Gene Ontology enrichment
+
+**In beta: GO analysis still under development**
+
+::: {.panel-tabset}
+
+#### Cell Compartment
 
@@
 
+suppressMessages(CC_enrichment_plots(SF_2024_data, "dot"))
+
+suppressMessages(CC_enrichment_plots(SF_2024_data, "cnet"))
+```
+:::
+
+#### Molecular Function
+
+:::{.border}
+```{r, echo=FALSE, warning=FALSE}
+
+suppressMessages(MF_enrichment_plots(SF_2024_data, "dot"))
+
+suppressMessages(MF_enrichment_plots(SF_2024_data, "cnet"))
+
+```
+:::
+
+#### Biological Process
+
+:::{.border}
+```{r, echo=FALSE, warning=FALSE}
+
+suppressMessages(BP_enrichment_plots(SF_2024_data, "dot"))
+
+suppressMessages(BP_enrichment_plots(SF_2024_data, "cnet"))
+
+```
+:::
+:::
+
+## Data exploration and download
+
+:::{.border}
+```{r, echo=FALSE, warning=FALSE}
 # Here is the code to make the filterable lists shown in the crosstalk table below

### 2025-02-21 LipidProbe/PhosphatidicAcid.qmd
Spent all day learning how to make my heatmap look less bad
Adding Gene Ontology search

@@
 title: "Trifunctional Phosphatidic Acid"
+prefer-html: true
 ---
@@
 :::
+:::
 
-##### Data
+## Gene Ontology enrichment
+
+**In beta: GO analysis still under development**
+
+::: {.panel-tabset}
+
+#### Cell Compartment
+
+:::{.border}
+```{r, echo=FALSE, warning=FALSE}
+
+suppressMessages(CC_enrichment_plots(AT_2025_Long, "dot"))
+
+suppressMessages(CC_enrichment_plots(AT_2025_Long, "cnet"))
+```
+:::
+
+#### Molecular Function
+
+:::{.border}
+```{r, echo=FALSE, warning=FALSE}
+
+suppressMessages(MF_enrichment_plots(AT_2025_Long, "dot"))
+
+suppressMessages(MF_enrichment_plots(AT_2025_Long, "cnet"))
+
+```
+:::
+
+#### Biological Process
+
+:::{.border}
+```{r, echo=FALSE, warning=FALSE}
+
+suppressMessages(BP_enrichment_plots(AT_2025_Long, "dot"))
+
+suppressMessages(BP_enrichment_plots(AT_2025_Long, "cnet"))
+
+```
+:::
+:::
+
+## Data exploration and download
 
@@
 AT_2025_Long <- AT_2025_Long |>
-  select(gene_name, hit_annotation, logFC, pvalue) |>
+  dplyr::select(gene_name, hit_annotation, logFC, pvalue) |>
   mutate(logFC = signif(logFC, digits=3),
@@
 {{< downloadthis DataSets/PA_HeLa_AT_2025.csv dname="PA_HeLa_AT_ChemComm_download.csv">}}
-
-:::

### 2025-02-21 LipidProbe/Phosphatidylethanolamine.qmd
Spent all day learning how to make my heatmap look less bad
Adding Gene Ontology search

@@
 title: "Trifunctional Phosphatidylethanolamine"
+prefer-html: true
 ---
@@
 ```
-
+:::
 :::
 
-##### Data
+## Gene Ontology enrichment
+
+**In beta: GO analysis still under development**
+
+::: {.panel-tabset}
+
+#### Cell Compartment
+
+:::{.border}
+```{r, echo=FALSE, warning=FALSE}
+
+suppressMessages(CC_enrichment_plots(AT_2025_Long, "dot"))
+
+suppressMessages(CC_enrichment_plots(AT_2025_Long, "cnet"))
+```
+:::
+
+#### Molecular Function
+
+:::{.border}
+```{r, echo=FALSE, warning=FALSE}
+
+suppressMessages(MF_enrichment_plots(AT_2025_Long, "dot"))
+
+suppressMessages(MF_enrichment_plots(AT_2025_Long, "cnet"))
+
+```
+:::
+
+#### Biological Process
+
+:::{.border}
+```{r, echo=FALSE, warning=FALSE}
+
+suppressMessages(BP_enrichment_plots(AT_2025_Long, "dot"))
+
+suppressMessages(BP_enrichment_plots(AT_2025_Long, "cnet"))
+
+```
+:::
+:::
+
+## Data exploration and download
 
@@
 {{< downloadthis DataSets/PE_HeLa_AT_2025.csv dname="PE_HeLa_AT_ChemComm_download.csv">}}
-
-:::

### 2025-02-21 LipidProbe/Sphinganine.qmd
Spent all day learning how to make my heatmap look less bad
Adding Gene Ontology search

@@
 title: "Trifunctional sphinganine"
+prefer-html: true
 ---
@@
 SF_2024_data <- SF_2024_data |>
-  select(gene_name, hit_annotation, logFC, pvalue, fdr) |>
+  dplyr::select(gene_name, hit_annotation, logFC, pvalue, fdr) |>
   mutate(logFC = signif(logFC, digits=3),

### 2025-02-21 LipidProbe/Sphingosine.qmd
Spent all day learning how to make my heatmap look less bad
Adding Gene Ontology search

@@
 format: html
+prefer-html: true
 ---

### 2025-02-21 SearchByProtein/SearchByProtein.qmd
Adding Gene Ontology search

@@
 datawhole <- data |>
-	select(gene_name, LipidProbe, hit_annotation, logFC, pvalue, fdr) |>
+	dplyr::select(gene_name, LipidProbe, hit_annotation, logFC, pvalue, fdr) |>
 	mutate(logFC = signif(logFC, digits=3),

### 2025-02-21 Resources/R_sandbox.R

@@ -1,9 +1,17 @@
+library(here)
 library(BiocManager)
 library(limma)
 library(GEOquery)
 library(msigdbr)
 library(fgsea)
 library(clusterProfiler)
+library(org.Hs.eg.db)
+library(docstring)
+
+## Opening the source file for the ggplot custom theme
+source(paste0(here(), "/Resources/ggplot_styles.R"))
+
+
 
 # install.packages("clusterProfiler")
 # BiocManager::install(c("GenomicFeatures", "AnnotationDbi"))
@@ -11,7 +19,7 @@ library(clusterProfiler)
 # BiocManager::install("fgsea")
 # BiocManager::install("limma")
 # BiocManager::install("GEOquery")
-
+BiocManager::install(c("org.Hs.eg.db"))
 
 gse200250 <- getGEO("GSE200250", AnnotGPL = TRUE)[[1]]
 
@@ -45,4 +53,218 @@ gesecaRes <- geseca(pathways, exprs(es), minSize = 15, maxSize = 500)
 
 head(gesecaRes, 10)
 
+####################################################
+# Modifying Frank's script to get GO outputs for genesets
+
+library(clusterProfiler)
+library(org.Hs.eg.db)
+library(here)
+
+calculateFE <- function(GeneRatio, BgRatio)
+{
+  GeneRatio <- as.numeric(unlist(str_split(GeneRatio, pattern = "/")))
+  BgRatio <- as.numeric(unlist(str_split(BgRatio, pattern = "/")))
+  odds_ratio <- (GeneRatio[1] / GeneRatio[2]) / (BgRatio[1] / BgRatio[2])
+  return(odds_ratio)
+}
+
+customPlot <- list(
+  theme_bw(base_size = 12), 
+  scale_fill_brewer(palette = "Set1"), 
+  scale_colour_brewer(palette = "Set1")
+)
+
+# Data extraction Doris's
+DH_2017_data <- read.csv(paste0(here(),"/IndividualStudies/DataTables/DH_PNAS_2017_download.csv")) |>
+  mutate(gene_name = str_extract(Description, "GN=([^\\s]+)") |> str_remove("GN=")) |>
+  mutate(Species = str_extract(Description, "OS=([^=]+?)\\sGN=") |> str_remove("OS=") |> str_remove("GN=")) |>
[…]

### 2025-02-21 Resources/ggplot_styles.R

@@ -1,4 +1,4 @@
-# A centralized spot to save a custom theme across the whole site
+################ Library Initialization ################
 
 library(ggplot2)
 library(ggrepel)
@@ -6,8 +6,15 @@ library(emojifont)
 library(dplyr)
 library(tidyr)
 library(docstring)
+library(clusterProfiler)
+library(org.Hs.eg.db)
+library(enrichplot)
+library(igraph)
+library(ggtangle)
+library(stringr)
 
-# Define a helper function that safely applies abs()
+################ Helper Functions ################
+
 safe_abs <- function(x, default = NA) {
   #' Performs some error handling in the event of NA in joined datasets -- intended to be used while finding the limits of ggplots, as in VolcanoPlotStandardized.
   #' Takes an input, tries to coerce it into a numeric, performs the abs() operation on it
@@ -34,13 +41,31 @@ safe_log10 <- function(x, default = NA) {
     })
 }
 
+calculateFE <- function(GeneRatio, BgRatio)
+{
+  GeneRatio <- as.numeric(unlist(str_split(GeneRatio, pattern = "/")))
+  BgRatio <- as.numeric(unlist(str_split(BgRatio, pattern = "/")))
+  odds_ratio <- (GeneRatio[1] / GeneRatio[2]) / (BgRatio[1] / BgRatio[2])
+  return(odds_ratio)
+}
 
+customPlot <- list(
+  theme_bw(base_size = 12), 
+  scale_fill_brewer(palette = "Set1"), 
+  scale_colour_brewer(palette = "Set1")
+)
+
+
+################ Plotting Functions ################
 
 MAStandard <- function(data) {
+
+    ################
     #' A standardized MA plot function
     #' Receives a dataframe. Needs to have the following columns for the aes() to work: AveExpr, logFC, hit_annotation, gene_name.
     #' Dynamically determines the limits of the plot under the scale_x/y_scontinuous calls
     #' Produces first a facet-wrapped ggplot, then converts it to a plotly plot.
+    ################
 
     MAPlots <- data |>
         ggplot(aes(x = AveExpr,
@@ -113,9 +138,15 @@ MAStandard <- function(data) {
 }
 
 
-# A standardized Ranked Order plot theme
+# 
 
 RankedOrderPlotStandard <- function(data) {
+    ################
+    #' A standardized Ranked Order plot theme
[…]

### 2025-02-22 Resources/ggplot_styles.R
Minor changes

@@ -362,7 +362,7 @@ CC_enrichment_plots <- function(data, plotReturnType){
 
     try(
 			# Makes the cnet plot
-		cnet <- clusterProfiler::cnetplot(ego_results_Identification_MF, categorySize = "pvalue") +
+		cnet <- clusterProfiler::cnetplot(ego_results_Identification_CC, categorySize = "pvalue") +
 		# ggtitle("Cellular compartment") +
 		customPlot
     )
@@ -550,7 +550,7 @@ BP_enrichment_plots <- function(data, plotReturnType){
 
     try(
 			# Makes the cnet plot
-		cnet <- clusterProfiler::cnetplot(ego_results_Identification_MF, categorySize = "pvalue") +
+		cnet <- clusterProfiler::cnetplot(ego_results_Identification_BP, categorySize = "pvalue") +
 		# ggtitle("Cellular compartment") +
 		customPlot
     )

### 2025-02-23 IndividualStudies/AT_2025.qmd
Pre-rendering GO analysis so rendering is faster

--- 2025-02-07 IndividualStudies/AT_2025.qmd
@@
 
-AT_2025_Long <- readr::read_csv("DataTables/AT_ChemicalCommunications_2025_download.csv")
+AT_2025_Long <- readr::read_csv(paste0(here(), "/IndividualStudies/DataTables/AT_ChemicalCommunications_2025_download.csv"))
 
@@
 
+## Gene Ontology enrichment
+
+**In beta: GO analysis still under development**
+
+::: {.panel-tabset}
+
+#### Cell Compartment
+
+:::{.border}
+```{r, echo=FALSE, warning=FALSE}
+# #### These functions make the plots to be displayed in this div - uncomment them to run them again
+# CC_enrichment_plots(AT_2025_Long, "dot", "PE-PA_AT_2025_CC-DOTplot")
+# CC_enrichment_plots(AT_2025_Long, "cnet", "PE-PA_AT_2025_CC-CNETplot")
+```
+
+<iframe src="/IndividualStudies/GO_plots/PE-PA_AT_2025_CC-DOTplot.html" width="100%" height="500px"></iframe>
+
+![](/IndividualStudies/GO_plots/PE-PA_AT_2025_CC-CNETplot.png)
+
+:::
+
+#### Molecular Function
+
+:::{.border}
+```{r, echo=FALSE, warning=FALSE}
+#### These functions make the plots to be displayed in this div - uncomment them to run them again
+# MF_enrichment_plots(AT_2025_Long, "dot", "PE-PA_AT_2025_MF-DOTplot")
+# MF_enrichment_plots(AT_2025_Long, "cnet", "PE-PA_AT_2025_MF-CNETplot")
+```
+
+<iframe src="/IndividualStudies/GO_plots/PE-PA_AT_2025_MF-DOTplot.html" width="100%" height="500px"></iframe>
+
+![](/IndividualStudies/GO_plots/PE-PA_AT_2025_MF-CNETplot.png)
+
+:::
+
+#### Biological Process
+
+:::{.border}
+```{r, echo=FALSE, warning=FALSE}
+#### These functions make the plots to be displayed in this div - uncomment them to run them again
+# BP_enrichment_plots(AT_2025_Long, "dot", "PE-PA_AT_2025_BP-DOTplot")
+# BP_enrichment_plots(AT_2025_Long, "cnet", "PE-PA_AT_2025_BP-CNETplot")
+```
+
+<iframe src="/IndividualStudies/GO_plots/PE-PA_AT_2025_BP-DOTplot.html" width="100%" height="500px"></iframe>
+
+![](/IndividualStudies/GO_plots/PE-PA_AT_2025_BP-CNETplot.png)
+
+:::
+
+:::
+
 ## Enriched proteins

### 2025-02-23 IndividualStudies/SF_2024.qmd
Pre-rendering GO analysis so rendering is faster

@@
 # Opening the datatable for this page IN FINAL RENDER
-SF_2024_data <- readr::read_csv("DataTables/SF_ACS-Chem-Bio_2024_download.csv")
+SF_2024_data <- readr::read_csv(paste0(here(), "/IndividualStudies/DataTables/SF_ACS-Chem-Bio_2024_download.csv"))
 
@@
 ```{r, echo=FALSE, warning=FALSE}
+# #### These functions make the plots to be displayed in this div - uncomment them to run them again
+# CC_enrichment_plots(SF_2024_data, "dot", "/IndividualStudies/GO_plots/Sph-Spa_SF_2024_CC-DOTplot")
+# CC_enrichment_plots(SF_2024_data, "cnet", "/IndividualStudies/GO_plots/Sph-Spa_SF_2024_CC-CNETplot")
+```
 
-suppressMessages(CC_enrichment_plots(SF_2024_data, "dot"))
+<iframe src="/IndividualStudies/GO_plots/Sph-Spa_SF_2024_CC-DOTplot.html" width="100%" height="500px"></iframe>
 
-suppressMessages(CC_enrichment_plots(SF_2024_data, "cnet"))
-```
+![](/IndividualStudies/GO_plots/Sph-Spa_SF_2024_CC-CNETplot.png)
+
 :::
@@
 ```{r, echo=FALSE, warning=FALSE}
+#### These functions make the plots to be displayed in this div - uncomment them to run them again
+# MF_enrichment_plots(SF_2024_data, "dot", "/IndividualStudies/GO_plots/Sph-Spa_SF_2024_MF-DOTplot")
+# MF_enrichment_plots(SF_2024_data, "cnet", "/IndividualStudies/GO_plots/Sph-Spa_SF_2024_MF-CNETplot")
+```
 
-suppressMessages(MF_enrichment_plots(SF_2024_data, "dot"))
+<iframe src="/IndividualStudies/GO_plots/Sph-Spa_SF_2024_MF-DOTplot.html" width="100%" height="500px"></iframe>
 
-suppressMessages(MF_enrichment_plots(SF_2024_data, "cnet"))
-
-```
+(MF CNET plot failed in production)
 :::
@@
 ```{r, echo=FALSE, warning=FALSE}
+#### These functions make the plots to be displayed in this div - uncomment them to run them again
+# BP_enrichment_plots(SF_2024_data, "dot", "/IndividualStudies/GO_plots/Sph-Spa_SF_2024_BP-DOTplot")
+# BP_enrichment_plots(SF_2024_data, "cnet", "/IndividualStudies/GO_plots/Sph-Spa_SF_2024_BP-CNETplot")
+```
 
-suppressMessages(BP_enrichment_plots(SF_2024_data, "dot"))
+(No BP pathways identified among enriched hits and candidates.)
 
-suppressMessages(BP_enrichment_plots(SF_2024_data, "cnet"))
-
-```
+(BP CNET plot failed in production)
 :::

### 2025-02-23 IndividualStudies/SF_2024_B.qmd
Pre-rendering GO analysis so rendering is faster

@@
 # Opening the datatable for this page IN FINAL RENDER
-SF_2024_data <- readr::read_csv(paste0(here(), "/IndividualStudies//DataTables/SF_Chem_Comm_2024_download.csv"))
+SF_2024_data <- readr::read_csv(paste0(here(), "/IndividualStudies/DataTables/SF_Chem_Comm_2024_download.csv"))
 
@@
 ```{r, echo=FALSE, warning=FALSE}
+# #### These functions make the plots to be displayed in this div - uncomment them to run them again
+# CC_enrichment_plots(SF_2024_data, "dot", "/IndividualStudies/GO_plots/8-3FA-1-10FA_SF_2024_CC-DOTplot")
+# CC_enrichment_plots(SF_2024_data, "cnet", "/IndividualStudies/GO_plots/8-3FA-1-10FA_SF_2024_CC-CNETplot")
+```
 
-suppressMessages(CC_enrichment_plots(SF_2024_data, "dot"))
+<iframe src="/IndividualStudies/GO_plots/8-3FA-1-10FA_SF_2024_CC-DOTplot.html" width="100%" height="500px"></iframe>
 
-suppressMessages(CC_enrichment_plots(SF_2024_data, "cnet"))
-```
+![](/IndividualStudies/GO_plots/8-3FA-1-10FA_SF_2024_CC-CNETplot.png)
+
 :::
@@
 ```{r, echo=FALSE, warning=FALSE}
+#### These functions make the plots to be displayed in this div - uncomment them to run them again
+# MF_enrichment_plots(SF_2024_data, "dot", "/IndividualStudies/GO_plots/8-3FA-1-10FA_SF_2024_MF-DOTplot")
+# MF_enrichment_plots(SF_2024_data, "cnet", "/IndividualStudies/GO_plots/8-3FA-1-10FA_SF_2024_MF-CNETplot")
+```
 
-suppressMessages(MF_enrichment_plots(SF_2024_data, "dot"))
+<iframe src="/IndividualStudies/GO_plots/8-3FA-1-10FA_SF_2024_MF-DOTplot.html" width="100%" height="500px"></iframe>
 
-suppressMessages(MF_enrichment_plots(SF_2024_data, "cnet"))
-
-```
+(MF CNET plot failed in production)
 :::
@@
 ```{r, echo=FALSE, warning=FALSE}
+#### These functions make the plots to be displayed in this div - uncomment them to run them again
+# BP_enrichment_plots(SF_2024_data, "dot", "/IndividualStudies/GO_plots/8-3FA-1-10FA_SF_2024_BP-DOTplot")
+# BP_enrichment_plots(SF_2024_data, "cnet", "/IndividualStudies/GO_plots/8-3FA-1-10FA_SF_2024_BP-CNETplot")
+```
 
-suppressMessages(BP_enrichment_plots(SF_2024_data, "dot"))
+<iframe src="/IndividualStudies/GO_plots/8-3FA-1-10FA_SF_2024_BP-DOTplot.html" width="100%" height="500px"></iframe>
 
-suppressMessages(BP_enrichment_plots(SF_2024_data, "cnet"))
-
-```
+(BP CNET plot failed in production)
 :::

### 2025-02-23 LipidProbe/1-10_FattyAcid.qmd
Pre-rendering GO analysis so rendering is faster

@@
 library(htmltools)
+library(here)
 
 ## Opening the source file for the ggplot custom theme
-source("/Users/gaelenguzman/LipidInteractomics_Website_local/LipidInteractomics_Website/Resources/ggplot_styles.R")
+source(paste0(here(), "/Resources/ggplot_styles.R"))
 
@@
 # Opening the datatable for this page
-SF_2024_data <- readr::read_csv("DataSets/1-10_FA_Huh7_SF_2024.csv") |>
+SF_2024_data <- readr::read_csv(paste0(here(), "/LipidProbe/DataSets/1-10_FA_Huh7_SF_2024.csv")) |>
 	filter(LipidProbe == "1-10 FA")
@@
 ```{r, echo=FALSE, warning=FALSE}
+# #### These functions make the plots to be displayed in this div - uncomment them to run them again
+# CC_enrichment_plots(SF_2024_data, "dot", "/LipidProbe/GO_plots/1-10FA_SF_2024_CC-DOTplot")
+# CC_enrichment_plots(SF_2024_data, "cnet", "/LipidProbe/GO_plots/1-10FA_SF_2024_CC-CNETplot")
+```
 
-suppressMessages(CC_enrichment_plots(SF_2024_data, "dot"))
+<iframe src="/LipidProbe/GO_plots/1-10FA_SF_2024_CC-DOTplot.html" width="100%" height="500px"></iframe>
 
-suppressMessages(CC_enrichment_plots(SF_2024_data, "cnet"))
-```
+(CC CNET plot failed in production)
 :::
@@
 ```{r, echo=FALSE, warning=FALSE}
+#### These functions make the plots to be displayed in this div - uncomment them to run them again
+# MF_enrichment_plots(SF_2024_data, "dot", "/LipidProbe/GO_plots/1-10FA_SF_2024_MF-DOTplot")
+# MF_enrichment_plots(SF_2024_data, "cnet", "/LipidProbe/GO_plots/1-10FA_SF_2024_MF-CNETplot")
+```
 
-suppressMessages(MF_enrichment_plots(SF_2024_data, "dot"))
+(No MF pathways identified among enriched hits and candidates.)
 
-suppressMessages(MF_enrichment_plots(SF_2024_data, "cnet"))
-
-```
+(MF CNET plot failed in production)
 :::
@@
 ```{r, echo=FALSE, warning=FALSE}
+#### These functions make the plots to be displayed in this div - uncomment them to run them again
+# BP_enrichment_plots(SF_2024_data, "dot", "/LipidProbe/GO_plots/1-10FA_SF_2024_BP-DOTplot")
+# BP_enrichment_plots(SF_2024_data, "cnet", "/LipidProbe/GO_plots/1-10FA_SF_2024_BP-CNETplot")
+```
 
-suppressMessages(BP_enrichment_plots(SF_2024_data, "dot"))
+(No BP pathways identified among enriched hits and candidates.)
 
-suppressMessages(BP_enrichment_plots(SF_2024_data, "cnet"))
-
-```
+(BP CNET plot failed in production)
 :::

### 2025-02-23 LipidProbe/8-3_FattyAcid.qmd
Pre-rendering GO analysis so rendering is faster

@@
 # Opening the datatable for this page
-SF_2024_data <- readr::read_csv("DataSets/8-3_FA_Huh7_SF_2024.csv") |>
+SF_2024_data <- readr::read_csv(paste0(here(), "/LipidProbe/DataSets/8-3_FA_Huh7_SF_2024.csv")) |>
 	filter(LipidProbe == "8-3 FA")
@@
 ```{r, echo=FALSE, warning=FALSE}
+# #### These functions make the plots to be displayed in this div - uncomment them to run them again
+# CC_enrichment_plots(SF_2024_data, "dot", "/LipidProbe/GO_plots/8-3FA_SF_2024_CC-DOTplot")
+# CC_enrichment_plots(SF_2024_data, "cnet", "/LipidProbe/GO_plots/8-3FA_SF_2024_CC-CNETplot")
+```
 
-suppressMessages(CC_enrichment_plots(SF_2024_data, "dot"))
+<iframe src="/LipidProbe/GO_plots/8-3FA_SF_2024_CC-DOTplot.html" width="100%" height="500px"></iframe>
 
-suppressMessages(CC_enrichment_plots(SF_2024_data, "cnet"))
-```
+(CC CNET plot failed in production)
 :::
@@
 ```{r, echo=FALSE, warning=FALSE}
+#### These functions make the plots to be displayed in this div - uncomment them to run them again
+# MF_enrichment_plots(SF_2024_data, "dot", "/LipidProbe/GO_plots/8-3FA_SF_2024_MF-DOTplot")
+# MF_enrichment_plots(SF_2024_data, "cnet", "/LipidProbe/GO_plots/8-3FA_SF_2024_MF-CNETplot")
+```
 
-suppressMessages(MF_enrichment_plots(SF_2024_data, "dot"))
+<iframe src="/LipidProbe/GO_plots/8-3FA_SF_2024_MF-DOTplot.html" width="100%" height="500px"></iframe>
 
-suppressMessages(MF_enrichment_plots(SF_2024_data, "cnet"))
-
-```
+(MF CNET plot failed in production)
 :::
@@
 ```{r, echo=FALSE, warning=FALSE}
+#### These functions make the plots to be displayed in this div - uncomment them to run them again
+# BP_enrichment_plots(SF_2024_data, "dot", "/LipidProbe/GO_plots/8-3FA_SF_2024_BP-DOTplot")
+# BP_enrichment_plots(SF_2024_data, "cnet", "/LipidProbe/GO_plots/8-3FA_SF_2024_BP-CNETplot")
+```
 
-suppressMessages(BP_enrichment_plots(SF_2024_data, "dot"))
+<iframe src="/LipidProbe/GO_plots/8-3FA_SF_2024_BP-DOTplot.html" width="100%" height="500px"></iframe>
 
-suppressMessages(BP_enrichment_plots(SF_2024_data, "cnet"))
-
-```
+(BP CNET plot failed in production)
 :::

### 2025-02-23 LipidProbe/PhosphatidicAcid.qmd
Minor changes
Pre-rendering GO analysis so rendering is faster

@@
 prefer-html: true
+format:
+  html: default
+
 ---
@@
 
-AT_2025_Long <- readr::read_csv("DataSets/PA_HeLa_AT_2025.csv")
+AT_2025_Long <- readr::read_csv(paste0(here(), "/LipidProbe/DataSets/PA_HeLa_AT_2025.csv"))
 
@@
 ```{r, echo=FALSE, warning=FALSE}
+# #### These functions make the plots to be displayed in this div - uncomment them to run them again
+# CC_enrichment_plots(AT_2025_Long, "dot", "/LipidProbe/GO_plots/PA_AT_2025_CC-DOTplot")
+# CC_enrichment_plots(AT_2025_Long, "cnet", "/LipidProbe/GO_plots/PA_AT_2025_CC-CNETplot")
+```
 
-suppressMessages(CC_enrichment_plots(AT_2025_Long, "dot"))
+<iframe src="/LipidProbe/GO_plots/PA_AT_2025_CC-DOTplot.html" width="100%" height="500px"></iframe>
 
-suppressMessages(CC_enrichment_plots(AT_2025_Long, "cnet"))
-```
+(CC CNET plot failed in production)
 :::
@@
 ```{r, echo=FALSE, warning=FALSE}
+#### These functions make the plots to be displayed in this div - uncomment them to run them again
+# MF_enrichment_plots(AT_2025_Long, "dot", "/LipidProbe/GO_plots/PA_AT_2025_MF-DOTplot")
+# MF_enrichment_plots(AT_2025_Long, "cnet", "/LipidProbe/GO_plots/PA_AT_2025_MF-CNETplot")
+```
 
-suppressMessages(MF_enrichment_plots(AT_2025_Long, "dot"))
+<iframe src="/LipidProbe/GO_plots/PA_AT_2025_MF-DOTplot.html" width="100%" height="500px"></iframe>
 
-suppressMessages(MF_enrichment_plots(AT_2025_Long, "cnet"))
-
-```
+(MF CNET plot failed in production)
 :::
@@
 ```{r, echo=FALSE, warning=FALSE}
+#### These functions make the plots to be displayed in this div - uncomment them to run them again
+# BP_enrichment_plots(AT_2025_Long, "dot", "/LipidProbe/GO_plots/PA_AT_2025_BP-DOTplot")
+# BP_enrichment_plots(AT_2025_Long, "cnet", "/LipidProbe/GO_plots/PA_AT_2025_BP-CNETplot")
+```
 
-suppressMessages(BP_enrichment_plots(AT_2025_Long, "dot"))
+<iframe src="/LipidProbe/GO_plots/PA_AT_2025_BP-DOTplot.html" width="100%" height="500px"></iframe>
 
-suppressMessages(BP_enrichment_plots(AT_2025_Long, "cnet"))
-
-```
+(BP CNET plot failed in production)
 :::

### 2025-02-23 LipidProbe/Phosphatidylethanolamine.qmd
Minor changes
Pre-rendering GO analysis so rendering is faster

@@
 
-AT_2025_Long <- readr::read_csv("DataSets/PE_HeLa_AT_2025.csv")
+AT_2025_Long <- readr::read_csv(paste0(here(), "/LipidProbe/DataSets/PE_HeLa_AT_2025.csv"))
 
@@
 ```{r, echo=FALSE, warning=FALSE}
+# #### These functions make the plots to be displayed in this div - uncomment them to run them again
+# CC_enrichment_plots(AT_2025_Long, "dot", "/LipidProbe/GO_plots/PE_AT_2025_CC-DOTplot")
+# CC_enrichment_plots(AT_2025_Long, "cnet", "/LipidProbe/GO_plots/PE_AT_2025_CC-CNETplot")
+```
 
-suppressMessages(CC_enrichment_plots(AT_2025_Long, "dot"))
+<iframe src="/LipidProbe/GO_plots/PE_AT_2025_CC-DOTplot.html" width="100%" height="500px"></iframe>
 
-suppressMessages(CC_enrichment_plots(AT_2025_Long, "cnet"))
-```
+(CC CNET plot failed in production)
 :::
@@
 ```{r, echo=FALSE, warning=FALSE}
+#### These functions make the plots to be displayed in this div - uncomment them to run them again
+# MF_enrichment_plots(AT_2025_Long, "dot", "/LipidProbe/GO_plots/PE_AT_2025_MF-DOTplot")
+# MF_enrichment_plots(AT_2025_Long, "cnet", "/LipidProbe/GO_plots/PE_AT_2025_MF-CNETplot")
+```
 
-suppressMessages(MF_enrichment_plots(AT_2025_Long, "dot"))
+<iframe src="/LipidProbe/GO_plots/PE_AT_2025_MF-DOTplot.html" width="100%" height="500px"></iframe>
 
-suppressMessages(MF_enrichment_plots(AT_2025_Long, "cnet"))
-
-```
+(MF CNET plot failed in production)
 :::
@@
 ```{r, echo=FALSE, warning=FALSE}
+#### These functions make the plots to be displayed in this div - uncomment them to run them again
+# BP_enrichment_plots(AT_2025_Long, "dot", "/LipidProbe/GO_plots/PE_AT_2025_BP-DOTplot")
+# BP_enrichment_plots(AT_2025_Long, "cnet", "/LipidProbe/GO_plots/PE_AT_2025_BP-CNETplot")
+```
 
-suppressMessages(BP_enrichment_plots(AT_2025_Long, "dot"))
+<iframe src="/LipidProbe/GO_plots/PE_AT_2025_BP-DOTplot.html" width="100%" height="500px"></iframe>
 
-suppressMessages(BP_enrichment_plots(AT_2025_Long, "cnet"))
-
-```
+(BP CNET plot failed in production)
 :::

### 2025-02-23 LipidProbe/Sphinganine.qmd
Pre-rendering GO analysis so rendering is faster

@@
 prefer-html: true
+format: html
 ---
@@
 # Opening the datatable for this page
-SF_2024_data <- readr::read_csv("DataSets/Spa_Huh7_SF_2024.csv") |>
+SF_2024_data <- readr::read_csv(paste0(here(), "/LipidProbe/DataSets/Spa_Huh7_SF_2024.csv")) |>
 	filter(LipidProbe == "Spa")
@@
 ```{r, echo=FALSE, warning=FALSE}
+# #### These functions make the plots to be displayed in this div - uncomment them to run them again
+# CC_enrichment_plots(SF_2024_data, "dot", "/LipidProbe/GO_plots/Spa_SF_2024_CC-DOTplot")
+# CC_enrichment_plots(SF_2024_data, "cnet", "/LipidProbe/GO_plots/Spa_SF_2024_CC-CNETplot")
+```
 
-suppressMessages(CC_enrichment_plots(SF_2024_data, "dot"))
+<iframe src="/LipidProbe/GO_plots/Spa_SF_2024_CC-DOTplot.html" width="100%" height="500px"></iframe>
 
-suppressMessages(CC_enrichment_plots(SF_2024_data, "cnet"))
-```
+(CC CNET plot failed in production)
 :::
@@
 ```{r, echo=FALSE, warning=FALSE}
+#### These functions make the plots to be displayed in this div - uncomment them to run them again
+# MF_enrichment_plots(SF_2024_data, "dot", "/LipidProbe/GO_plots/Spa_SF_2024_MF-DOTplot")
+# MF_enrichment_plots(SF_2024_data, "cnet", "/LipidProbe/GO_plots/Spa_SF_2024_MF-CNETplot")
+```
 
-suppressMessages(MF_enrichment_plots(SF_2024_data, "dot"))
+<iframe src="/LipidProbe/GO_plots/Spa_SF_2024_MF-DOTplot.html" width="100%" height="500px"></iframe>
 
-suppressMessages(MF_enrichment_plots(SF_2024_data, "cnet"))
-
-```
+(MF CNET plot failed in production)
 :::
@@
 ```{r, echo=FALSE, warning=FALSE}
+#### These functions make the plots to be displayed in this div - uncomment them to run them again
+# BP_enrichment_plots(SF_2024_data, "dot", "/LipidProbe/GO_plots/Spa_SF_2024_BP-DOTplot")
+# BP_enrichment_plots(SF_2024_data, "cnet", "/LipidProbe/GO_plots/Spa_SF_2024_BP-CNETplot")
+```
 
-suppressMessages(BP_enrichment_plots(SF_2024_data, "dot"))
+(No BP pathways identified among enriched hits and candidates.)
 
-suppressMessages(BP_enrichment_plots(SF_2024_data, "cnet"))
-
-```
+(BP CNET plot failed in production)
 :::

### 2025-02-23 LipidProbe/Sphingosine.qmd
Pre-rendering GO analysis so rendering is faster

@@
 # Opening the datatable for this page
-SF_2024_data <- readr::read_csv("DataSets/Sph_Huh7_SF_2024.csv") |>
+SF_2024_data <- readr::read_csv(paste0(here(), "/LipidProbe/DataSets/Sph_Huh7_SF_2024.csv")) |>
 	filter(LipidProbe == "Sph")
@@
 
-# Applies the ID column to the Spa results
+# Applies the ID column to the Sph results
 SF_2024_ranked <- SF_2024_data |>
@@
 ```{r, echo=FALSE, warning=FALSE}
+# #### These functions make the plots to be displayed in this div - uncomment them to run them again
+# CC_enrichment_plots(SF_2024_data, "dot", "/LipidProbe/GO_plots/Sph_SF_2024_CC-DOTplot")
+# CC_enrichment_plots(SF_2024_data, "cnet", "/LipidProbe/GO_plots/Sph_SF_2024_CC-CNETplot")
+```
 
-suppressMessages(CC_enrichment_plots(SF_2024_data, "dot"))
+<iframe src="/LipidProbe/GO_plots/Sph_SF_2024_CC-DOTplot.html" width="100%" height="500px"></iframe>
 
-suppressMessages(CC_enrichment_plots(SF_2024_data, "cnet"))
-```
+(CC CNET plot failed in production)
 :::
@@
 ```{r, echo=FALSE, warning=FALSE}
+#### These functions make the plots to be displayed in this div - uncomment them to run them again
+# MF_enrichment_plots(SF_2024_data, "dot", "/LipidProbe/GO_plots/Sph_SF_2024_MF-DOTplot")
+# MF_enrichment_plots(SF_2024_data, "cnet", "/LipidProbe/GO_plots/Sph_SF_2024_MF-CNETplot")
+```
 
-suppressMessages(MF_enrichment_plots(SF_2024_data, "dot"))
+(No MF pathways identified among enriched hits and candidates.)
 
-suppressMessages(MF_enrichment_plots(SF_2024_data, "cnet"))
-
-```
+(MF CNET plot failed in production)
 :::
@@
 ```{r, echo=FALSE, warning=FALSE}
+#### These functions make the plots to be displayed in this div - uncomment them to run them again
+# BP_enrichment_plots(SF_2024_data, "dot", "/LipidProbe/GO_plots/Sph_SF_2024_BP-DOTplot")
+# BP_enrichment_plots(SF_2024_data, "cnet", "/LipidProbe/GO_plots/Sph_SF_2024_BP-CNETplot")
+```
 
-suppressMessages(BP_enrichment_plots(SF_2024_data, "dot"))
+(No BP pathways identified among enriched hits and candidates.)
 
-suppressMessages(BP_enrichment_plots(SF_2024_data, "cnet"))
-
-```
+(BP CNET plot failed in production)
 :::

### 2025-02-23 Resources/R_sandbox.R

@@ -8,6 +8,25 @@ library(clusterProfiler)
 library(org.Hs.eg.db)
 library(docstring)
 
+library(ggplot2)
+library(ggrepel)
+library(emojifont)
+library(dplyr)
+library(tidyr)
+library(docstring)
+library(clusterProfiler)
+library(org.Hs.eg.db)
+library(enrichplot)
+library(igraph)
+library(ggtangle)
+library(stringr)
+library(clusterProfiler)
+library(enrichplot)
+library(igraph)
+library(ggtangle)
+library(htmlwidgets)
+library(plotly)
+
 ## Opening the source file for the ggplot custom theme
 source(paste0(here(), "/Resources/ggplot_styles.R"))
 
@@ -60,6 +79,13 @@ library(clusterProfiler)
 library(org.Hs.eg.db)
 library(here)
 
+
+customPlot <- list(
+  theme_bw(base_size = 12), 
+  scale_fill_brewer(palette = "Set1"), 
+  scale_colour_brewer(palette = "Set1")
+)
+
 calculateFE <- function(GeneRatio, BgRatio)
 {
   GeneRatio <- as.numeric(unlist(str_split(GeneRatio, pattern = "/")))
@@ -68,11 +94,6 @@ calculateFE <- function(GeneRatio, BgRatio)
   return(odds_ratio)
 }
 
-customPlot <- list(
-  theme_bw(base_size = 12), 
-  scale_fill_brewer(palette = "Set1"), 
-  scale_colour_brewer(palette = "Set1")
-)
 
 # Data extraction Doris's
 DH_2017_data <- read.csv(paste0(here(),"/IndividualStudies/DataTables/DH_PNAS_2017_download.csv")) |>
@@ -82,7 +103,7 @@ DH_2017_data <- read.csv(paste0(here(),"/IndividualStudies/DataTables/DH_PNAS_20
   mutate(PSM_Sph = (PSM_Sph1 + PSM_Sph2) / 2,
          PSM_FA = (PSM_FA1 + PSM_FA2) / 2,
          PSM_DAG = (PSM_DAG1 + PSM_DAG2) /2) |>
-  select(gene_name, PSM_Sph, PSM_FA, PSM_DAG) |>
+  dplyr::select(gene_name, PSM_Sph, PSM_FA, PSM_DAG) |>
   arrange(gene_name) |>
   group_by(gene_name) |>
[…]

### 2025-02-23 Resources/ggplot_styles.R

@@ -296,7 +296,7 @@ VolcanoPlotStandardized <- function(data) {
 }
 
 
-CC_enrichment_plots <- function(data, plotReturnType){
+CC_enrichment_plots <- function(data, plotReturnType, filename){
 
 	################
 	#' Makes some GO enrichment plots of the Cellular Compartment
@@ -354,25 +354,25 @@ CC_enrichment_plots <- function(data, plotReturnType){
 			group_by(sample) %>%
 			slice_head(n = 10)
 		
-		
-
 	
 	if(plotReturnType == "cnet") {
 		cnet <- NULL
 
-    try(
+		try(
 			# Makes the cnet plot
-		cnet <- clusterProfiler::cnetplot(ego_results_Identification_CC, categorySize = "pvalue") +
-		# ggtitle("Cellular compartment") +
-		customPlot
+    cnet <- clusterProfiler::cnetplot(ego_results_Identification_CC, categorySize = "pvalue") +
+      # ggtitle("Cellular compartment") +
+        customPlot
     )
 
     if(!is.null(cnet)){
-      cnet
+      ggsave(paste0(here(), filename, ".png"),
+           width = 12, height = 12)
     } else {
       return("Cnet plot failed in production.")
     }
-    
+
+
 	} else {
 			# Makes the dot plot
 			dot <- ggplot(data = ego_sub, aes(sample, Description)) +
@@ -383,14 +383,18 @@ CC_enrichment_plots <- function(data, plotReturnType){
 				ylab("") +
 				xlab("LipidProbe")
 				theme(axis.text.x = element_text(angle = 0, vjust = 0.5, hjust = 1))
-			ggplotly(dot)
+
+			dot <- ggplotly(dot)
+      # Save as HTML (adjust the path as needed)
+      saveWidget(dot, file = paste0(here(), filename, ".html"), selfcontained = TRUE)
+
 		}
 	}
 }
 
 
 
-MF_enrichment_plots <- function(data, plotReturnType){
+MF_enrichment_plots <- function(data, plotReturnType, filename){
 
 	################
 	#' Makes some GO enrichment plots of the molecular function
@@ -452,20 +456,22 @@ MF_enrichment_plots <- function(data, plotReturnType){
 
 	
 	if(plotReturnType == "cnet") {
-    cnet <- NULL
+		cnet <- NULL
 
-    try(
+		try(
 			# Makes the cnet plot
[…]

### 2025-02-24 IndividualStudies/AT_2025.qmd
Trying to adjust formatting of Dot Plots

--- 2025-02-07 IndividualStudies/AT_2025.qmd
@@
 
-```
-
-```{r, echo=FALSE, include=FALSE}
-
 # Data wrangling to prepare Alix's data to the standardized inputs for my plotting functions.
@@
 
-AT_2025_Long <- readr::read_csv("DataTables/AT_ChemicalCommunications_2025_download.csv")
+AT_2025 <- readr::read_csv(paste0(here(), "/IndividualStudies/DataTables/AT_ChemicalCommunications_2025_download.csv"))
 
 # Organize the hit annotations as factors
-AT_2025_Long$hit_annotation <- factor(pull(AT_2025_Long, hit_annotation), levels = c("enriched hit", "enriched candidate", "no hit", "NA"), ordered=TRUE)
+AT_2025$hit_annotation <- factor(pull(AT_2025, hit_annotation), levels = c("enriched hit", "enriched candidate", "no hit", "NA"), ordered=TRUE)
 
@@
 ID <- c()
-for(i in 0:(nrow(AT_2025_Long)/2)){
+for(i in 0:(nrow(AT_2025)/2)){
 	ID[i] = i
@@
 # Applies the ID column to the PE results
-AT_2025_ranked_PE <- AT_2025_Long |>
+AT_2025_ranked_PE <- AT_2025 |>
     arrange(logFC) |>
@@
 # Applies the ID column to the PA results
-AT_2025_ranked_PA <- AT_2025_Long |>
+AT_2025_ranked_PA <- AT_2025 |>
     arrange(logFC) |>
@@
 
-VolcanoPlotStandardized(AT_2025_Long)
+VolcanoPlotStandardized(AT_2025)
 
@@
 
-## Enriched proteins
+## Gene Ontology enrichment
+
+**In beta: GO analysis still under development**
+
+::: {.panel-tabset}
+
+#### Cell Compartment
+
+:::{.border}
+
+<iframe src="/IndividualStudies/GO_plots/PE-PA_AT_2025_CC-DOTplot.html" width="100%" height="500px"></iframe>
+
+![](/IndividualStudies/GO_plots/PE-PA_AT_2025_CC-CNETplot.png)
+
+:::
+
+#### Molecular Function
+
+:::{.border}
+
+<iframe src="/IndividualStudies/GO_plots/PE-PA_AT_2025_MF-DOTplot.html" width="100%" height="500px"></iframe>
+
+![](/IndividualStudies/GO_plots/PE-PA_AT_2025_MF-CNETplot.png)
+
+:::
+
+#### Biological Process
+
+:::{.border}
+
+<iframe src="/IndividualStudies/GO_plots/PE-PA_AT_2025_BP-DOTplot.html" width="100%" height="500px"></iframe>
+
+![](/IndividualStudies/GO_plots/PE-PA_AT_2025_BP-CNETplot.png)
+
+:::
+
+:::
+
+## Data exploration and download
 
@@
 ## Creates a reactive dataframe
-AT_2025_Long_reactive <- crosstalk::SharedData$new(AT_2025_Long)
+AT_2025_reactive <- crosstalk::SharedData$new(AT_2025)
 
@@
                   label = "Lipid probe in pulldown:", 
-                  sharedData = AT_2025_Long_reactive,
+                  sharedData = AT_2025_reactive,
                   group = ~LipidProbe),
@@
                   label = "Enrichment criteria:", 
-                  sharedData = AT_2025_Long_reactive,
+                  sharedData = AT_2025_reactive,
                   group = ~hit_annotation)
@@
 ## Displays the reactive dataframe
-datatable(AT_2025_Long_reactive, options = list(pageLength = 20))
+datatable(AT_2025_reactive, options = list(pageLength = 20))
 

### 2025-02-24 Resources/Re-run_GO_plots.R

@@ -1,0 +1,141 @@
+#######################################
+#' The purpose of this R script is to re-run the GO plotting functions and re-render all of the plots displayed on the IndividualStudies and LipidProbe pages.
+	#' Uncomment some or all of the sections below if any changes are made.
+	#' Add new sections for new datasets using the frameworks below.
+#######################################
+
+## intitialize libraries
+library(here)
+library(dplyr)
+library(tidyr)
+library(readr)
+library(crosstalk)
+
+## Opening the source file for the ggplot custom theme
+source(paste0(here(), "/Resources/ggplot_styles.R"))
+
+## Sphingosine
+# Sph_data <- readr::read_csv(paste0(here(), "/LipidProbe/DataSets/Sph_Huh7_SF_2024.csv")) |>
+# 	filter(LipidProbe == "Sph")
+
+# CC_enrichment_plots(Sph_data, "dot", "/LipidProbe/GO_plots/Sph_SF_2024_CC-DOTplot")
+# CC_enrichment_plots(Sph_data, "cnet", "/LipidProbe/GO_plots/Sph_SF_2024_CC-CNETplot")
+
+# MF_enrichment_plots(Sph_data, "dot", "/LipidProbe/GO_plots/Sph_SF_2024_MF-DOTplot")
+# MF_enrichment_plots(Sph_data, "cnet", "/LipidProbe/GO_plots/Sph_SF_2024_MF-CNETplot")
+
+# BP_enrichment_plots(Sph_data, "dot", "/LipidProbe/GO_plots/Sph_SF_2024_BP-DOTplot")
+# BP_enrichment_plots(Sph_data, "cnet", "/LipidProbe/GO_plots/Sph_SF_2024_BP-CNETplot")
+
+
+## Sphinganine
+
+# Spa_data <- readr::read_csv(paste0(here(), "/LipidProbe/DataSets/Spa_Huh7_SF_2024.csv")) |>
+# 	filter(LipidProbe == "Spa")
+
[…]

### 2025-02-24 Resources/ggplot_styles.R

@@ -137,9 +137,6 @@ MAStandard <- function(data) {
     return(MAPlotly)
 }
 
-
-# 
-
 RankedOrderPlotStandard <- function(data) {
     ################
     #' A standardized Ranked Order plot theme
@@ -295,7 +292,6 @@ VolcanoPlotStandardized <- function(data) {
     return(VolcanoPlotly)
 }
 
-
 CC_enrichment_plots <- function(data, plotReturnType, filename){
 
 	################
@@ -382,9 +378,15 @@ CC_enrichment_plots <- function(data, plotReturnType, filename){
 				# ggtitle("Cellular compartment") +
 				ylab("") +
 				xlab("LipidProbe")
-				theme(axis.text.x = element_text(angle = 0, vjust = 0.5, hjust = 1))
+				theme(axis.text.x = element_text(angle = 0, vjust = 0.5, hjust = 1, size = 12, face = "bold"),
+              axis.text.y = element_text(size = 12))
 
-			dot <- ggplotly(dot)
+      m <- list(l=50, r = 50, b= 100, pad = 10)
+
+			dot <- ggplotly(dot,
+                      autosize = T,
+                      margin = m)
+
       # Save as HTML (adjust the path as needed)
       saveWidget(dot, file = paste0(here(), filename, ".html"), selfcontained = TRUE)
 

### 2025-02-24 Resources/ggplot_styles.R
Found a silly mistake in my Volcano limits function

@@ -218,7 +218,7 @@ VolcanoPlotStandardized <- function(data) {
     #' Requires an input dataframe with the columns "gene_name", "LipidProbe", "logFC", "pvalue", and "hit_annotation"
     ################
 
-    limits <- c(max(c(safe_abs(data$logFC), 4), na.rm=TRUE) , max(c(-safe_log10(data$pvalue), 8), na.rm=TRUE))
+    limits <- c(max(c(safe_abs(data$logFC, 4)), na.rm=TRUE) , max(c(-safe_log10(data$pvalue, 8)), na.rm=TRUE))
 
 
     VolcanoPlots <- data |>

### 2025-02-24 IndividualStudies/AT_2025.qmd
Added documentation to MaintenanceInstructions, improved standardization

@@
 
-AT_2025 <- readr::read_csv(paste0(here(), "/IndividualStudies/DataTables/AT_ChemicalCommunications_2025_download.csv"))
+data <- readr::read_csv(paste0(here(), "/IndividualStudies/DataTables/AT_ChemicalCommunications_2025_download.csv"))
 
 # Organize the hit annotations as factors
-AT_2025$hit_annotation <- factor(pull(AT_2025, hit_annotation), levels = c("enriched hit", "enriched candidate", "no hit", "NA"), ordered=TRUE)
-
-# Building an ID column to maintain the order on the x-axis
-ID <- c()
-for(i in 0:(nrow(AT_2025)/2)){
-	ID[i] = i
-}
-
-# Applies the ID column to the PE results
-AT_2025_ranked_PE <- AT_2025 |>
-    arrange(logFC) |>
-	filter(LipidProbe == "PE") |>
-	mutate(ID = ID)
-
-# Applies the ID column to the PA results
-AT_2025_ranked_PA <- AT_2025 |>
-    arrange(logFC) |>
-	filter(LipidProbe == "PA") |>
-	mutate(ID = ID)
-
-# Assembles the dataset to plot
-AT_2025_ranked <- rbind(AT_2025_ranked_PE, AT_2025_ranked_PA)
+data$hit_annotation <- factor(pull(data, hit_annotation), levels = c("enriched hit", "enriched candidate", "no hit", "NA"), ordered=TRUE)
 
@@
 
-VolcanoPlotStandardized(AT_2025)
+VolcanoPlotStandardized(data)
 
@@
 
-RankedOrderPlotStandard(AT_2025_ranked)
+RankedOrderPlotStandard(data)
 ```
@@
 ## Creates a reactive dataframe
-AT_2025_reactive <- crosstalk::SharedData$new(AT_2025)
+data_reactive <- crosstalk::SharedData$new(data)
 
@@
                   label = "Lipid probe in pulldown:", 
-                  sharedData = AT_2025_reactive,
+                  sharedData = data_reactive,
                   group = ~LipidProbe),
@@
                   label = "Enrichment criteria:", 
-                  sharedData = AT_2025_reactive,
+                  sharedData = data_reactive,
                   group = ~hit_annotation)
@@
 ## Displays the reactive dataframe
-datatable(AT_2025_reactive, options = list(pageLength = 20))
+datatable(data_reactive, options = list(pageLength = 20))
 

### 2025-02-24 IndividualStudies/SF_2024.qmd
Added documentation to MaintenanceInstructions, improved standardization

--- 2025-02-07 IndividualStudies/SF_2024.qmd
@@
 # Opening the datatable for this page IN FINAL RENDER
-SF_2024_data <- readr::read_csv("DataTables/SF_ACS-Chem-Bio_2024_download.csv")
+data <- readr::read_csv(paste0(here(), "/IndividualStudies/DataTables/SF_ACS-Chem-Bio_2024_download.csv"))
 
 # # # Opening the datatable for this page WHILE EDITING
-# SF_2024_data <- readr::read_csv("IndividualStudies/DataTables/SF_ACS-Chem-Bio_2024_download.csv")
+# data <- readr::read_csv("IndividualStudies/DataTables/SF_ACS-Chem-Bio_2024_download.csv")
 
 # Organize the hit annotations as factors
-SF_2024_data$hit_annotation <- factor(pull(SF_2024_data, hit_annotation), levels = c("enriched hit", "hit", "enriched candidate", "candidate", "no hit", "NA"), ordered = TRUE)
+data$hit_annotation <- factor(pull(data, hit_annotation), levels = c("enriched hit", "hit", "enriched candidate", "candidate", "no hit", "NA"), ordered = TRUE)
 
 # Organize the probes as factors
-SF_2024_data$LipidProbe <- factor(pull(SF_2024_data, LipidProbe), levels = c("Sph", "Spa", "8-3 FA", "1-10 FA"), ordered = TRUE)
+data$LipidProbe <- factor(pull(data, LipidProbe), levels = c("Sph", "Spa", "8-3 FA", "1-10 FA"), ordered = TRUE)
 
-# Building an ID column to maintain the order on the x-axis
-ID <- c()
-for(i in 0:(nrow(SF_2024_data)/2)){
-	ID[i] = i
-}
-
-# Applies the ID column to the Spa results
-SF_2024_ranked_Spa <- SF_2024_data |>
-    arrange(logFC) |>
-	filter(LipidProbe == "Spa") |>
-	mutate(ID = ID)
-
-# Applies the ID column to the Sph results
-SF_2024_ranked_Sph <- SF_2024_data |>
-    arrange(logFC) |>
-	filter(LipidProbe == "Sph") |>
-	mutate(ID = ID)
-
-# Assembles the dataset to plot
-SF_2024_ranked <- rbind(SF_2024_ranked_Sph, SF_2024_ranked_Spa)
 ```
@@
 
-VolcanoPlotStandardized(SF_2024_data)
+VolcanoPlotStandardized(data)
 
@@
 
-RankedOrderPlotStandard(SF_2024_ranked)
+RankedOrderPlotStandard(data)
 ```
@@
 
-MAStandard(SF_2024_data)
+MAStandard(data)
 
@@
 :::
+:::
+
+## Gene Ontology enrichment
+
+**In beta: GO analysis still under development**
+
+::: {.panel-tabset}
+
+#### Cell Compartment
+
+:::{.border}
+
+<iframe src="/IndividualStudies/GO_plots/Sph-Spa_SF_2024_CC-DOTplot.html" width="100%" height="500px"></iframe>
+
+![](/IndividualStudies/GO_plots/Sph-Spa_SF_2024_CC-CNETplot.png)
 
@@
 
-## Enriched Proteins
+#### Molecular Function
+
+:::{.border}
+
+<iframe src="/IndividualStudies/GO_plots/Sph-Spa_SF_2024_MF-DOTplot.html" width="100%" height="500px"></iframe>
+
+(MF CNET plot failed in production)
+:::
+
+#### Biological Process
+
+:::{.border}
+
+(No BP pathways identified among enriched hits and candidates.)
+
+(BP CNET plot failed in production)
+:::
+
+:::
+
+## Data exploration and download
 
@@
 
-SF_2024_data <- SF_2024_data |>
-  select(gene_name, LipidProbe, hit_annotation, logFC, pvalue, fdr) |>
+data <- data |>
+  dplyr::select(gene_name, LipidProbe, hit_annotation, logFC, pvalue, fdr) |>
   mutate(logFC = signif(logFC, digits=3),
@@
 ## Creates a reactive dataframe
-SF_2024_data_reactive <- crosstalk::SharedData$new(SF_2024_data)
+data_reactive <- crosstalk::SharedData$new(data)
 
@@
                   label = "Lipid probe in pulldown:", 
-                  sharedData = SF_2024_data_reactive,
+                  sharedData = data_reactive,
                   group = ~LipidProbe),
@@
                   label = "Enrichment criteria:", 
-                  sharedData = SF_2024_data_reactive,
+                  sharedData = data_reactive,
                   group = ~hit_annotation)
@@
 ## Displays the reactive dataframe
-datatable(SF_2024_data_reactive, 
+datatable(data_reactive, 
           options = list(pageLength = 15),

### 2025-02-24 IndividualStudies/SF_2024_B.qmd
Added documentation to MaintenanceInstructions, improved standardization

--- 2025-02-07 IndividualStudies/SF_2024_B.qmd
@@
 # Opening the datatable for this page IN FINAL RENDER
-SF_2024_data <- readr::read_csv("DataTables/SF_Chem_Comm_2024_download.csv")
-
-# # # Opening the datatable for this page WHILE EDITING
-# SF_2024_data <- readr::read_csv("IndividualStudies/DataTables/SF_Chem_Comm_2024_download.csv")
+data <- readr::read_csv(paste0(here(), "/IndividualStudies/DataTables/SF_Chem_Comm_2024_download.csv"))
 
 # Organizing the hit annotations as factors
-SF_2024_data$hit_annotation <- factor(pull(SF_2024_data, hit_annotation), levels = c("enriched hit", "hit", "enriched candidate", "candidate", "no hit", "NA"), ordered = TRUE)
+data$hit_annotation <- factor(pull(data, hit_annotation), levels = c("enriched hit", "hit", "enriched candidate", "candidate", "no hit", "NA"), ordered = TRUE)
 
 # Organize the probes as factors
-SF_2024_data$LipidProbe <- factor(pull(SF_2024_data, LipidProbe), levels = c("Spa", "Sph", "8-3 FA", "1-10 FA"), ordered = TRUE)
+data$LipidProbe <- factor(pull(data, LipidProbe), levels = c("Spa", "Sph", "8-3 FA", "1-10 FA"), ordered = TRUE)
 
-#write.csv(SF_2024_data, "IndividualStudies/DataTables/SF_Chem_Comm_2024_download.csv")
-
-# Building an ID column to maintain the order on the x-axis
-ID <- c()
-for(i in 0:(nrow(SF_2024_data)/2)){
-	ID[i] = i
-}
-
-# Applies the ID column to the 1-10 FA results
-SF_2024_ranked_1_10_FA <- SF_2024_data |>
-    arrange(logFC) |>
-	filter(LipidProbe == "1-10 FA") |>
-	mutate(ID = ID)
-
-# Applies the ID column to the 8-3 FA results
-SF_2024_ranked_8_3_FA <- SF_2024_data |>
-    arrange(logFC) |>
-	filter(LipidProbe == "8-3 FA") |>
-	mutate(ID = ID)
-
-# Assembles the dataset to plot
-SF_2024_ranked <- rbind(SF_2024_ranked_8_3_FA, SF_2024_ranked_1_10_FA)
 ```
@@
 
-## Study details
+{{< include /StudyInformation_includes/SF_2024_B_include.qmd >}}
 
-#### Authors
-Scotland E. Farley, Ryu Hashimoto, Judah Evangelista, Frank Stein, Per Haberkant, Kazuya Kikuchi, Fikadu G. Tafesse, Carsten Schultz
-
-#### Journal
-Chemical Communications
-
-<https://doi.org/10.1021/acschembio.3c00554>{target="_blank"}
-
-#### Abstract
-
-Functionalized lipid probes are a critical new tool to interrogate the function of individual lipid species, but the structural parameters that constrain their utility have not been thoroughly described.
-Functionalized lipid probes are a critical new tool to interrogate the function of individual lipid species, but the structural parameters that constrain their utility have not been thoroughly described.
-Here, we synthesize three palmitic acid derivatives with a diazirine at different positions on the acyl chain and examine their metabolism, subcellular localization, and protein interactions.
-We demonstrate that while they produce very similar metabolites and subcellular distributions, probes with the diazirine at either end pulldown distinct subsets of proteins after photo-crosslinking.
-This highlights the importance of thoughtful diazirine placement when developing probes based on biological molecules.
-
-#### Lipid probes utilized
-
-[8-3 Fatty Acid](/LipidProbe/8-3_FattyAcid.qmd)
-
-#### Cell line analyzed
-
-[Huh7](https://huh7.com){target="_blank"}
-
-#### Mass spectrometry quantification method
-
-16-channel Tandem Mass Tagging (TMT16)
-
-#### Additional sample preparation <span class="help-symbol" title="e.g. sub-cellular fractionation, depletion, etc.">?</span>
 :::
@@
 
-## Enriched Proteins
+## Gene Ontology enrichment
+
+**In beta: GO analysis still under development**
+
+::: {.panel-tabset}
+
+#### Cell Compartment
+
+:::{.border}
+
+<iframe src="/IndividualStudies/GO_plots/8-3FA-1-10FA_SF_2024_CC-DOTplot.html" width="100%" height="500px"></iframe>
+
+![](/IndividualStudies/GO_plots/8-3FA-1-10FA_SF_2024_CC-CNETplot.png)
+
+:::
+
+#### Molecular Function
+
+:::{.border}
+
+<iframe src="/IndividualStudies/GO_plots/8-3FA-1-10FA_SF_2024_MF-DOTplot.html" width="100%" height="500px"></iframe>
+
+(MF CNET plot failed in production)
+:::
+
+#### Biological Process
+
+:::{.border}
+
+<iframe src="/IndividualStudies/GO_plots/8-3FA-1-10FA_SF_2024_BP-DOTplot.html" width="100%" height="500px"></iframe>
+
+(BP CNET plot failed in production)
+:::
+
+:::
+
+## Data exploration and download
 
@@
 ## Displays the reactive dataframe
-datatable(SF_2024_data_reactive, options = list(pageLength = 15))
+datatable(data_reactive, options = list(pageLength = 15))
 

### 2025-02-24 LipidProbe/1-10_FattyAcid.qmd
Added documentation to MaintenanceInstructions, improved standardization

@@
 prefer-html: true
-html: default
 ---
@@
 
-# SF_2024_data <- readr::read_csv("LipidProbe/DataSets/SF_Chem_Comm_2024_download.csv") |>
-# 	filter(LipidProbe == "1-10 FA")
-
-# write.csv(SF_2024_data, "LipidProbe/DataSets/1-10_FA_Huh7_SF_2024.csv")
-
 # Opening the datatable for this page
-SF_2024_data <- readr::read_csv(paste0(here(), "/LipidProbe/DataSets/1-10_FA_Huh7_SF_2024.csv")) |>
+data <- readr::read_csv(paste0(here(), "/LipidProbe/DataSets/1-10_FA_Huh7_SF_2024.csv")) |>
 	filter(LipidProbe == "1-10 FA")
@@
 # Organizing the hit annotations as factors
-SF_2024_data$hit_annotation <- factor(pull(SF_2024_data, hit_annotation), levels = c("enriched hit", "hit", "enriched candidate", "candidate", "no hit", "NA"), ordered = TRUE)
-
-# Building an ID column to maintain the order on the x-axis
-ID <- c()
-for(i in 0:(nrow(SF_2024_data))){
-	ID[i] = i
-}
-
-# Applies the ID column to the Spa results
-SF_2024_ranked <- SF_2024_data |>
-    arrange(logFC) |>
-	filter(LipidProbe == "1-10 FA") |>
-	mutate(ID = ID)
+data$hit_annotation <- factor(pull(data, hit_annotation), levels = c("enriched hit", "hit", "enriched candidate", "candidate", "no hit", "NA"), ordered = TRUE)
 
@@
 
-VolcanoPlotStandardized(SF_2024_data)
+VolcanoPlotStandardized(data)
 ```
@@
 :::{.border}
-```{r, echo=FALSE, warning=FALSE}
-# #### These functions make the plots to be displayed in this div - uncomment them to run them again
-# CC_enrichment_plots(SF_2024_data, "dot", "/LipidProbe/GO_plots/1-10FA_SF_2024_CC-DOTplot")
-# CC_enrichment_plots(SF_2024_data, "cnet", "/LipidProbe/GO_plots/1-10FA_SF_2024_CC-CNETplot")
-```
 
@@
 :::{.border}
-```{r, echo=FALSE, warning=FALSE}
-#### These functions make the plots to be displayed in this div - uncomment them to run them again
-# MF_enrichment_plots(SF_2024_data, "dot", "/LipidProbe/GO_plots/1-10FA_SF_2024_MF-DOTplot")
-# MF_enrichment_plots(SF_2024_data, "cnet", "/LipidProbe/GO_plots/1-10FA_SF_2024_MF-CNETplot")
-```
 
@@
 :::{.border}
-```{r, echo=FALSE, warning=FALSE}
-#### These functions make the plots to be displayed in this div - uncomment them to run them again
-# BP_enrichment_plots(SF_2024_data, "dot", "/LipidProbe/GO_plots/1-10FA_SF_2024_BP-DOTplot")
-# BP_enrichment_plots(SF_2024_data, "cnet", "/LipidProbe/GO_plots/1-10FA_SF_2024_BP-CNETplot")
-```
 
@@
 
-SF_2024_data <- SF_2024_data |>
+data <- data |>
   dplyr::select(gene_name, LipidProbe, hit_annotation, logFC, pvalue, fdr) |>
@@
                   label = "Enrichment criteria:", 
-                  sharedData = SF_2024_data_reactive,
+                  sharedData = data_reactive,
                   group = ~hit_annotation,
@@
 ## Displays the reactive dataframe
-datatable(SF_2024_data_reactive, 
+datatable(data_reactive, 
           caption = "'No hit' proteins are unenriched or depleted in the presence of probe, 'enriched candidates' are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and 'enriched hits' are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV",
@@
 
-{{< downloadthis DataSets/1-10_FA_Huh7_SF_2024.csv dname="1-10_FA_Huh7_SF_ACS-Chem-Bio_2024.csv">}}
+{{< downloadthis DataSets/1-10_FA_Huh7_SF_2024.csv dname="1-10_FA_Huh7_SF_ACS-Chem-Bio_2024">}}
 

### 2025-02-24 LipidProbe/8-3_FattyAcid.qmd
Added documentation to MaintenanceInstructions, improved standardization

@@
 
-# SF_2024_data <- readr::read_csv("LipidProbe/DataSets/SF_Chem_Comm_2024_download.csv") |>
-# 	filter(LipidProbe == "8-3 FA")
-
-# write.csv(SF_2024_data, "LipidProbe/DataSets/8-3_FA_Huh7_SF_2024.csv")
-
 # Opening the datatable for this page
-SF_2024_data <- readr::read_csv(paste0(here(), "/LipidProbe/DataSets/8-3_FA_Huh7_SF_2024.csv")) |>
+data <- readr::read_csv(paste0(here(), "/LipidProbe/DataSets/8-3_FA_Huh7_SF_2024.csv")) |>
 	filter(LipidProbe == "8-3 FA")
@@
 # Organizing the hit annotations as factors
-SF_2024_data$hit_annotation <- factor(pull(SF_2024_data, hit_annotation), levels = c("enriched hit", "hit", "enriched candidate", "candidate", "no hit", "NA"), ordered = TRUE)
-
-# Building an ID column to maintain the order on the x-axis
-ID <- c()
-for(i in 0:(nrow(SF_2024_data))){
-	ID[i] = i
-}
-
-# Applies the ID column to the Spa results
-SF_2024_ranked <- SF_2024_data |>
-    arrange(logFC) |>
-	filter(LipidProbe == "8-3 FA") |>
-	mutate(ID = ID)
+data$hit_annotation <- factor(pull(data, hit_annotation), levels = c("enriched hit", "hit", "enriched candidate", "candidate", "no hit", "NA"), ordered = TRUE)
 
@@
 :::{.border}
-```{r, echo=FALSE, warning=FALSE}
-# #### These functions make the plots to be displayed in this div - uncomment them to run them again
-# CC_enrichment_plots(SF_2024_data, "dot", "/LipidProbe/GO_plots/8-3FA_SF_2024_CC-DOTplot")
-# CC_enrichment_plots(SF_2024_data, "cnet", "/LipidProbe/GO_plots/8-3FA_SF_2024_CC-CNETplot")
-```
 
@@
 :::{.border}
-```{r, echo=FALSE, warning=FALSE}
-#### These functions make the plots to be displayed in this div - uncomment them to run them again
-# MF_enrichment_plots(SF_2024_data, "dot", "/LipidProbe/GO_plots/8-3FA_SF_2024_MF-DOTplot")
-# MF_enrichment_plots(SF_2024_data, "cnet", "/LipidProbe/GO_plots/8-3FA_SF_2024_MF-CNETplot")
-```
 
@@
 :::{.border}
-```{r, echo=FALSE, warning=FALSE}
-#### These functions make the plots to be displayed in this div - uncomment them to run them again
-# BP_enrichment_plots(SF_2024_data, "dot", "/LipidProbe/GO_plots/8-3FA_SF_2024_BP-DOTplot")
-# BP_enrichment_plots(SF_2024_data, "cnet", "/LipidProbe/GO_plots/8-3FA_SF_2024_BP-CNETplot")
-```
 
@@
 ## Displays the reactive dataframe
-datatable(SF_2024_data_reactive,
+datatable(data_reactive,
 				  caption = "'No hit' proteins are unenriched or depleted in the presence of probe, 'enriched candidates' are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and 'enriched hits' are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV",
@@
 
-{{< downloadthis DataSets/8-3_FA_Huh7_SF_2024.csv dname="8-3_FA_Huh7_SF_ACS-Chem-Bio_2024.csv">}}
+{{< downloadthis DataSets/8-3_FA_Huh7_SF_2024.csv dname="8-3_FA_Huh7_SF_ACS-Chem-Bio_2024">}}
 

### 2025-02-24 LipidProbe/PhosphatidicAcid.qmd
Added documentation to MaintenanceInstructions, improved standardization

--- 2025-02-07 LipidProbe/PhosphatidicAcid.qmd
@@
 title: "Trifunctional Phosphatidic Acid"
+prefer-html: true
+format:
+  html: default
+
 ---
@@
 
-# AT_2025_Long <- readr::read_csv("LipidProbe/DataSets/AT_ChemicalCommunications_2025_download.csv") |>
+# AT_2025 <- readr::read_csv("LipidProbe/DataSets/AT_ChemicalCommunications_2025_download.csv") |>
 # 	filter(LipidProbe == "PA")
 
-# write.csv(AT_2025_Long, "LipidProbe/DataSets/PA_HeLa_AT_2025.csv")
+# write.csv(AT_2025, "LipidProbe/DataSets/PA_HeLa_AT_2025.csv")
 
-AT_2025_Long <- readr::read_csv("DataSets/PA_HeLa_AT_2025.csv")
+data <- readr::read_csv(paste0(here(), "/LipidProbe/DataSets/PA_HeLa_AT_2025.csv"))
 
 # Organize the hit annotations as factors
-AT_2025_Long$hit_annotation <- factor(pull(AT_2025_Long, hit_annotation), levels = c("enriched hit", "enriched candidate", "no hit", "NA"), ordered=TRUE)
-
-# Building an ID column to maintain the order on the x-axis
-ID <- c()
-for(i in 0:(nrow(AT_2025_Long))){
-	ID[i] = i
-}
-
-# Applies the ID column to the PE results
-AT_2025_ranked <- AT_2025_Long |>
-    arrange(logFC) |>
-	filter(LipidProbe == "PA") |>
-	mutate(ID = ID)
+data$hit_annotation <- factor(pull(data, hit_annotation), levels = c("enriched hit", "enriched candidate", "no hit", "NA"), ordered=TRUE)
 
@@
 
-VolcanoPlotStandardized(AT_2025_Long)
+VolcanoPlotStandardized(data)
 
@@
 :::
+:::
 
-##### Data
+## Gene Ontology enrichment
+
+**In beta: GO analysis still under development**
+
+::: {.panel-tabset}
+
+#### Cell Compartment
+
+:::{.border}
+
+<iframe src="/LipidProbe/GO_plots/PA_AT_2025_CC-DOTplot.html" width="100%" height="500px"></iframe>
+
+(CC CNET plot failed in production)
+:::
+
+#### Molecular Function
+
+:::{.border}
+
+<iframe src="/LipidProbe/GO_plots/PA_AT_2025_MF-DOTplot.html" width="100%" height="500px"></iframe>
+
+(MF CNET plot failed in production)
+:::
+
+#### Biological Process
+
+:::{.border}
+
+<iframe src="/LipidProbe/GO_plots/PA_AT_2025_BP-DOTplot.html" width="100%" height="500px"></iframe>
+
+(BP CNET plot failed in production)
+:::
+:::
+
+## Data exploration and download
 
@@
 
-AT_2025_Long <- AT_2025_Long |>
-  select(gene_name, hit_annotation, logFC, pvalue) |>
+data <- data |>
+  dplyr::select(gene_name, hit_annotation, logFC, pvalue) |>
   mutate(logFC = signif(logFC, digits=3),
@@
 ## Creates a reactive dataframe
-AT_2025_Long_reactive <- crosstalk::SharedData$new(AT_2025_Long)
+data_reactive <- crosstalk::SharedData$new(data)
 
@@
                   label = "Enrichment criteria:", 
-                  sharedData = AT_2025_Long_reactive,
+                  sharedData = data_reactive,
                   group = ~hit_annotation,
@@
 ## Displays the reactive dataframe
-datatable(AT_2025_Long_reactive,
+datatable(data_reactive,
           caption = "'No hit' proteins are unenriched or depleted in the presence of probe, 'enriched candidates' are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and 'enriched hits' are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV",
@@
 
-{{< downloadthis DataSets/PA_HeLa_AT_2025.csv dname="PA_HeLa_AT_ChemComm_download.csv">}}
-
-:::
+{{< downloadthis DataSets/PA_HeLa_AT_2025.csv dname="PA_HeLa_AT_ChemComm_download">}}

### 2025-02-24 LipidProbe/Phosphatidylethanolamine.qmd
Added documentation to MaintenanceInstructions, improved standardization

--- 2025-02-07 LipidProbe/Phosphatidylethanolamine.qmd
@@
 title: "Trifunctional Phosphatidylethanolamine"
+prefer-html: true
+format:
+  html: default
+
 ---
@@
 # Data wrangling to prepare Alix's data to the standardized inputs for my plotting functions.
+
 # Read the data to a df
-
-# AT_2025_Long <- readr::read_csv("LipidProbe/DataSets/AT_ChemicalCommunications_2025_download.csv") |>
-# 	filter(LipidProbe == "PE")
-
-# write.csv(AT_2025_Long, "LipidProbe/DataSets/PE_HeLa_AT_2025.csv")
-
-AT_2025_Long <- readr::read_csv("DataSets/PE_HeLa_AT_2025.csv")
+data <- readr::read_csv(paste0(here(), "/LipidProbe/DataSets/PE_HeLa_AT_2025.csv"))
 
 # Organize the hit annotations as factors
-AT_2025_Long$hit_annotation <- factor(pull(AT_2025_Long, hit_annotation), levels = c("enriched hit", "enriched candidate", "no hit", "NA"), ordered=TRUE)
+data$hit_annotation <- factor(pull(data, hit_annotation), levels = c("enriched hit", "enriched candidate", "no hit", "NA"), ordered=TRUE)
 
@@
 ID <- c()
-for(i in 0:(nrow(AT_2025_Long))){
+for(i in 0:(nrow(data))){
 	ID[i] = i
@@
 # Applies the ID column to the PE results
-AT_2025_ranked <- AT_2025_Long |>
+AT_2025_ranked <- data |>
     arrange(logFC) |>
@@
 ```
-
+:::
 :::
 
-##### Data
+## Gene Ontology enrichment
+
+**In beta: GO analysis still under development**
+
+::: {.panel-tabset}
+
+#### Cell Compartment
+
+:::{.border}
+
+<iframe src="/LipidProbe/GO_plots/PE_AT_2025_CC-DOTplot.html" width="100%" height="500px"></iframe>
+
+(CC CNET plot failed in production)
+:::
+
+#### Molecular Function
+
+:::{.border}
+
+<iframe src="/LipidProbe/GO_plots/PE_AT_2025_MF-DOTplot.html" width="100%" height="500px"></iframe>
+
+(MF CNET plot failed in production)
+:::
+
+#### Biological Process
+
+:::{.border}
+
+<iframe src="/LipidProbe/GO_plots/PE_AT_2025_BP-DOTplot.html" width="100%" height="500px"></iframe>
+
+(BP CNET plot failed in production)
+:::
+:::
+
+## Data exploration and download
 
@@
 
-{{< downloadthis DataSets/PE_HeLa_AT_2025.csv dname="PE_HeLa_AT_ChemComm_download.csv">}}
-
-:::
+{{< downloadthis DataSets/PE_HeLa_AT_2025.csv dname="PE_HeLa_AT_ChemComm_download">}}

### 2025-02-24 LipidProbe/Sphinganine.qmd
Added documentation to MaintenanceInstructions, improved standardization

--- 2025-02-07 LipidProbe/Sphinganine.qmd
@@
 title: "Trifunctional sphinganine"
+prefer-html: true
+format: html
 ---
@@
 # Opening the datatable for this page
-SF_2024_data <- readr::read_csv("DataSets/Spa_Huh7_SF_2024.csv") |>
+data <- readr::read_csv(paste0(here(), "/LipidProbe/DataSets/Spa_Huh7_SF_2024.csv")) |>
 	filter(LipidProbe == "Spa")
@@
 # Organizing the hit annotations as factors
-SF_2024_data$hit_annotation <- factor(pull(SF_2024_data, hit_annotation), levels = c("enriched hit", "hit", "enriched candidate", "candidate", "no hit", "NA"), ordered = TRUE)
-
-# Building an ID column to maintain the order on the x-axis
-ID <- c()
-for(i in 0:(nrow(SF_2024_data))){
-	ID[i] = i
-}
-
-# Applies the ID column to the Spa results
-SF_2024_ranked <- SF_2024_data |>
-    arrange(logFC) |>
-	filter(LipidProbe == "Spa") |>
-	mutate(ID = ID)
+data$hit_annotation <- factor(pull(data, hit_annotation), levels = c("enriched hit", "hit", "enriched candidate", "candidate", "no hit", "NA"), ordered = TRUE)
 
@@
 :::
+:::
 
-##### Data
+## Gene Ontology enrichment
+
+**In beta: GO analysis still under development**
+
+::: {.panel-tabset}
+
+#### Cell Compartment
+
+:::{.border}
+
+<iframe src="/LipidProbe/GO_plots/Spa_SF_2024_CC-DOTplot.html" width="100%" height="500px"></iframe>
+
+(CC CNET plot failed in production)
+:::
+
+#### Molecular Function
+
+:::{.border}
+
+<iframe src="/LipidProbe/GO_plots/Spa_SF_2024_MF-DOTplot.html" width="100%" height="500px"></iframe>
+
+(MF CNET plot failed in production)
+:::
+
+#### Biological Process
+
+:::{.border}
+
+(No BP pathways identified among enriched hits and candidates.)
+
+(BP CNET plot failed in production)
+:::
+:::
+
+## Data exploration and download
 
@@
 
-SF_2024_data <- SF_2024_data |>
-  select(gene_name, hit_annotation, logFC, pvalue, fdr) |>
+data <- data |>
+  dplyr::select(gene_name, hit_annotation, logFC, pvalue, fdr) |>
   mutate(logFC = signif(logFC, digits=3),
@@
 
-{{< downloadthis DataSets/Sph_Huh7_SF_2024.csv dname="Sph_Huh7_SF_ACS-Chem-Bio_download.csv">}}
+{{< downloadthis DataSets/Sph_Huh7_SF_2024.csv dname="Sph_Huh7_SF_ACS-Chem-Bio_download">}}
 

### 2025-02-24 LipidProbe/Sphingosine.qmd
Added documentation to MaintenanceInstructions, improved standardization

--- 2025-02-07 LipidProbe/Sphingosine.qmd
@@
 # Opening the datatable for this page
-SF_2024_data <- readr::read_csv("DataSets/Sph_Huh7_SF_2024.csv") |>
+data <- readr::read_csv(paste0(here(), "/LipidProbe/DataSets/Sph_Huh7_SF_2024.csv")) |>
 	filter(LipidProbe == "Sph")
@@
 # Organizing the hit annotations as factors
-SF_2024_data$hit_annotation <- factor(pull(SF_2024_data, hit_annotation), levels = c("enriched hit", "hit", "enriched candidate", "candidate", "no hit", "NA"), ordered = TRUE)
-
-# Building an ID column to maintain the order on the x-axis
-ID <- c()
-for(i in 0:(nrow(SF_2024_data))){
-	ID[i] = i
-}
-
-# Applies the ID column to the Spa results
-SF_2024_ranked <- SF_2024_data |>
-    arrange(logFC) |>
-	filter(LipidProbe == "Sph") |>
-	mutate(ID = ID)
+data$hit_annotation <- factor(pull(data, hit_annotation), levels = c("enriched hit", "hit", "enriched candidate", "candidate", "no hit", "NA"), ordered = TRUE)
 
@@
 :::
+:::
 
-##### Data
+## Gene Ontology enrichment
+
+**In beta: GO analysis still under development**
+
+::: {.panel-tabset}
+
+#### Cell Compartment
+
+:::{.border}
+
+<iframe src="/LipidProbe/GO_plots/Sph_SF_2024_CC-DOTplot.html" width="100%" height="500px"></iframe>
+
+(CC CNET plot failed in production)
+:::
+
+#### Molecular Function
+
+:::{.border}
+
+(No MF pathways identified among enriched hits and candidates.)
+
+(MF CNET plot failed in production)
+:::
+
+#### Biological Process
+
+:::{.border}
+
+(No BP pathways identified among enriched hits and candidates.)
+
+(BP CNET plot failed in production)
+:::
+:::
+
+## Data exploration and download
 
@@
 ```
-:::
 
-{{< downloadthis DataSets/Sph_Huh7_SF_2024.csv dname="Sph_Huh7_SF_ACS-Chem-Bio_download.csv">}}
+{{< downloadthis DataSets/Sph_Huh7_SF_2024.csv dname="Sph_Huh7_SF_ACS-Chem-Bio_download">}}
 

### 2025-02-24 LipidProbe/3-DplotExample_Sandbox.R

@@ -1,178 +1,0 @@
-library(dplyr)
-library(tidyr)
-library(ggplot2)
-library(plotly)
-library(readr)
-library(shiny)
-
-df <- read_csv("LipidProbe/DataSets/LipidInteractomics_ShinyApp/combinedProbeDatasets_TMT.csv")
-
-
-probeOptions <- unique(df$LipidProbe)
-
-
-
-ProbeVSProbePlotter <- function(data, probe1Name, probe2Name, probe3Name) {
-
-	
-
-	limits <- max(abs(max(data$logFC.x, na.rm = TRUE)),
-							abs(max(data$logFC.y, na.rm = TRUE)),
-							abs(max(data$logFC.z, na.rm = TRUE)))
-
-	ggplotter <- data |>
-			ggplot(aes(x = logFC.x,
-								 y = logFC.y,
-								 color = factor(combined_hit_annotation),
-								 fill = factor(combined_hit_annotation),
-								 shape = factor(combined_hit_annotation),
-								 size = factor(combined_hit_annotation),
-								 alpha = factor(combined_hit_annotation))) +
-			geom_point(aes(text = paste0("Gene name: ", gene_name))) +
-			geom_hline(yintercept = 0, linetype = 2) +
-			geom_vline(xintercept = 0, linetype = 2) +
-			scale_x_continuous(limits= c(-1.1*limits, 1.1*limits)) +
-			scale_y_continuous(limits= c(-1.1*limits, 1.1*limits)) +
-			scale_shape_manual(values = c("enriched on neither axis" = 22, 
-																		"enriched x-axis only" = 24,
-																		"enriched y-axis only" = 24,
-																		"enriched on both axes" = 21),
-													name = "Statistical Annotation") +
-			scale_fill_manual(values=c("enriched on neither axis" = "grey50", 
-																	"enriched x-axis only" = "purple",
-																	"enriched y-axis only" = "green",
-																	"enriched on both axes" = "orange"),
-												name = "Statistical Annotation") +
-			scale_color_manual(values = c("enriched on neither axis" = "black", 
-																		"enriched x-axis only" = "black",
-																		"enriched y-axis only" = "black",
-																		"enriched on both axes" = "black"),
-													name = "Statistical Annotation") +
-			scale_size_manual(values = c("enriched on neither axis" = 2, 
-																		"enriched x-axis only" = 4,
-																		"enriched y-axis only" = 4,
-																		"enriched on both axes" = 4),
[…]

### 2025-02-24 Resources/R_sandbox.R

@@ -153,6 +153,8 @@ ego_Identification_data <- AT_2025_Long %>%
 ego_Identification_data_enriched <- ego_Identification_data |>
 	filter((hit_annotation == "enriched candidate" | hit_annotation == "enriched hit"))
 
+	
+
 ego_results_Identification_CC <- NULL
 
 try(
@@ -303,3 +305,88 @@ CellCompartment_enrichment_plots(AT_2025_Long, "dot", "PE-PA_AT_2025_CC-DOTplot"
 data <- AT_2025_Long
 plotReturnType <- "dot"
 filename <- "PE-PA_AT_2025_CC-DOTplot"
+
+
+########### Trying the enrichDGN method instead of 
+
+# Making lookup table with ENTREZID identifiers from data
+ID_LUT <- clusterProfiler::bitr(geneID = AT_2025_Long$gene_name, fromType = "SYMBOL", toType = "ENTREZID", OrgDb = org.Hs.eg.db)
+names(ID_LUT) <- c("gene_name", "ENTREZID")
+
+glimpse(ID_LUT)
+
+# Merging ENTREZIDs to data
+AT_2025_Long <- left_join(AT_2025_Long, ID_LUT)
+
+ego_Identification_data <- AT_2025_Long %>%
+	mutate(sample = LipidProbe) |>
+  dplyr::select(ENTREZID, sample, hit_annotation, logFC) %>%
+  unique()
+
+ego_Identification_data_enriched <- ego_Identification_data |>
+	filter((hit_annotation == "enriched candidate" | hit_annotation == "enriched hit"))
+
+try(
+	ego_results_Identification_CC <- clusterProfiler::compareCluster(ENTREZID ~ sample,
+                                    data = ego_Identification_data_enriched, fun = "enrichGO",
+                                    OrgDb = org.Hs.eg.db,
+                                    keyType = "ENTREZID",
+                                    ont = "CC",
+                                    readable = TRUE,
+                                    universe = ID_LUT$ENTREZID)
+
+	ego_results_Identification_CC <- enrichGO(gene = ego_Identification_data_enriched, 
+																						universe = names(ego_Identification_data_enriched |> tibble::deframe() |> na.),
+																						OrgDb = org.Hs.eg.db,
+																						ont = "CC",
+																						pAdjustMethod = "BH",
[…]

### 2025-02-24 Resources/Re-run_GO_plots.R

@@ -1,6 +1,7 @@
 #######################################
 #' The purpose of this R script is to re-run the GO plotting functions and re-render all of the plots displayed on the IndividualStudies and LipidProbe pages.
-	#' Uncomment some or all of the sections below if any changes are made.
+#' Saves a ton of time in each render because these functions take a while to run.
+	#' Uncomment some or all of the sections below if any changes to the plotting functions are made.
 	#' Add new sections for new datasets using the frameworks below.
 #######################################
 

### 2025-02-24 Resources/ggplot_styles.R

@@ -142,7 +142,14 @@ RankedOrderPlotStandard <- function(data) {
     #' A standardized Ranked Order plot theme
     #' Requires an input dataframe with the columns "gene_name", "LipidProbe", "logFC", "pvalue", and "hit_annotation"
     ################
-    
+
+    # Applies ID column to each probe
+    data <- data |>
+      group_by(LipidProbe) |>
+      arrange(logFC, .by_group = TRUE) |>
+      mutate(ID = row_number()) |>
+      ungroup()
+
     # First makes a ggplot template to later apply ggplotly
     RankedOrderPlots <- data |>
         ggplot(aes(x = ID,

### 2025-02-25 BioinformaticsApplicationNote/GG_2025_applicationNote.qmd
minor updates to background sections

@@
     email: gaelen.guzman@lipidinteractome.org
+  - name: "Frank Stein"
+    affiliations:
+      - name: "European Molecular Biology Laboratory"
+        city: Heidelberg
+        country: Germany
+        postal-code: 69117
+    orcid: 0000-0001-9695-1692
   - name: "Carsten Schultz"
@@
 
-Gaelen Guzman^1,^*, Carsten Schulz^1^, Fikadu G. Tafesse^1^
+Gaelen Guzman^1,^*, Frank Stein^2^, Carsten Schulz^1^, Fikadu G. Tafesse^1^
 
-^1^ = Oregon Health & Science University; * = Corresponding author: <gaelen.guzman@lipidinteractome.org>
+^1^ = Oregon Health & Science University, Portland, OR, USA; ^2^ = European Molecular Biology Laboratory, Heidelberg, Germany * = Corresponding author: <gaelen.guzman@lipidinteractome.org>
 :::

### 2025-02-25 IndividualStudies/DH_2017.qmd
Found a silly mistake in my Volcano limits function
Adding GO analysis to DH_2017

--- 2025-02-20 IndividualStudies/DH_2017.qmd
@@
 
+###### Wrangling the raw dataset ######
 DH_2017_data <- read.csv(paste0(here(),"/IndividualStudies/DataTables/DH_PNAS_2017_download.csv")) |>
@@
             PSM_Sph = mean(PSM_Sph))
+
+###### Wrangling for the DataTable and the GO ######
+
+DH_2017_data <- DH_2017_data |>
+  mutate(VennRegion = case_when(
+    (PSM_Sph > 0 & PSM_DAG > 0 & PSM_FA > 0) ~ "Enriched to all probes",
+    (PSM_Sph > 0 & PSM_DAG == 0 & PSM_FA == 0) ~ "Enriched to Sph only",
+    (PSM_Sph == 0 & PSM_DAG > 0 & PSM_FA == 0) ~ "Enriched to DAG only",
+    (PSM_Sph == 0 & PSM_DAG == 0 & PSM_FA > 0) ~ "Enriched to FA only",
+    (PSM_Sph > 0 & PSM_DAG > 0 & PSM_FA == 0) ~ "Enriched to Sph and DAG",
+    (PSM_Sph > 0 & PSM_DAG == 0 & PSM_FA > 0) ~ "Enriched to Sph and FA",
+    (PSM_Sph == 0 & PSM_DAG > 0 & PSM_FA > 0) ~ "Enriched to DAG and FA"))
+
+DH_2017_data$VennRegion <- factor(pull(DH_2017_data, VennRegion), ordered = TRUE, levels = c("Enriched to Sph only", "Enriched to DAG only", "Enriched to FA only", "Enriched to Sph and DAG", "Enriched to Sph and FA", "Enriched to DAG and FA", "Enriched to all probes"))
+
+###### Wrangling for the HeatMap ######
+
+DH_2017_data_HeatMap <- DH_2017_data |>
+  pivot_longer(cols = starts_with("PSM_"),
+              names_to = "variable",
+              names_prefix = "PSM_",
+              values_to = "value") |>
+  mutate(name = gene_name) |>
+  dplyr::select(name, variable, value)
+
+DH_2017_data_HeatMap$variable <- factor(pull(DH_2017_data_HeatMap, variable), ordered = TRUE, levels = c("Sph", "FA", "DAG"))
+
+###### Wrangling for the Venn Diagram ######
+
+# Separates out each of the genesets, then forces them back together in a vectorized list.
+Sph_proteins <- DH_2017_data |>
+  filter(PSM_Sph > 0) |>
+  dplyr::select(gene_name)
+
+FA_proteins <- DH_2017_data |>
+  filter(PSM_FA > 0) |>
+  dplyr::select(gene_name)
+
+DAG_proteins <- DH_2017_data |>
+  filter(PSM_DAG > 0) |>
+  dplyr::select(gene_name)
+
+DH_2017_VennData <- list("Sph proteins" = as.list(Sph_proteins$gene_name), "FA proteins" = as.list(FA_proteins$gene_name), "DAG proteins" = as.list(DAG_proteins$gene_name))
+
 ```
@@
 #### Heat map
+
+Depicted below are the average PSM count for two replicates each of UV-irradiated samples treated with trifunctionalized Sph, DAG, and FA.
+
 :::{.border}
-```{r, echo=FALSE, fig.height=10, warning=FALSE}
 
-DH_2017_data_long <- DH_2017_data |>
-  pivot_longer(cols = starts_with("PSM_"),
-              names_to = "variable",
-              names_prefix = "PSM_",
-              values_to = "value") |>
-  mutate(name = gene_name) |>
-  select(name, variable, value)
-  # mutate(OriginalValues = value) |>
-  # mutate(value = case_when(value < 20 ~ value,
-  #                           value >= 20 ~ 20))
-
-DH_2017_data_long$variable <- factor(pull(DH_2017_data_long, variable), ordered = TRUE, levels = c("Sph", "FA", "DAG"))
+```{r Making Heat Map, echo=FALSE, fig.height=10, warning=FALSE}
 
 # Create the heatmap
-heatmaply(long_data = DH_2017_data_long,
+heatmaply(long_data = DH_2017_data_HeatMap,
           xlab = "Probe",
@@
 :::{.border}
-```{r, echo=FALSE, warning=FALSE, width = 8}
 
-# Ensure the data is in the correct format
-DH_2017_data_AddingRownames <- as.data.frame(DH_2017_data)
-rownames(DH_2017_data_AddingRownames) <- DH_2017_data_AddingRownames[,1]
-DH_2017_data_AddingRownames[,1] <- NULL
+```{r Making Venn Diagram, echo=FALSE, warning=FALSE, width = 8}
 
-Sph_proteins <- DH_2017_data_AddingRownames |>
-  filter(PSM_Sph > 0) |>
-  select(PSM_Sph)
-
-FA_proteins <- DH_2017_data_AddingRownames |>
-  filter(PSM_FA > 0) |>
-  select(PSM_FA)
-
-DAG_proteins <- DH_2017_data_AddingRownames |>
-  filter(PSM_DAG > 0) |>
-  select(PSM_DAG)
-
-combined_venn_proteins <- list("Sph proteins" = rownames(Sph_proteins), "FA proteins" = rownames(FA_proteins), "DAG proteins" = rownames(DAG_proteins))
-
-ggvenn <- ggvenn(combined_venn_proteins,
+ggvenn <- ggvenn(DH_2017_VennData,
                       show_percentage = FALSE,
@@
 
-```{r, echo=FALSE, warning=FALSE}
+:::
 
-DH_2017_data <- DH_2017_data |>
-  mutate(VennRegion = case_when(
-    (PSM_Sph > 0 & PSM_DAG > 0 & PSM_FA > 0) ~ "Enriched to all probes",
-    (PSM_Sph > 0 & PSM_DAG == 0 & PSM_FA == 0) ~ "Enriched to Sph only",
-    (PSM_Sph == 0 & PSM_DAG > 0 & PSM_FA == 0) ~ "Enriched to DAG only",
-    (PSM_Sph == 0 & PSM_DAG == 0 & PSM_FA > 0) ~ "Enriched to FA only",
-    (PSM_Sph > 0 & PSM_DAG > 0 & PSM_FA == 0) ~ "Enriched to Sph and DAG",
-    (PSM_Sph > 0 & PSM_DAG == 0 & PSM_FA > 0) ~ "Enriched to Sph and FA",
-    (PSM_Sph == 0 & PSM_DAG > 0 & PSM_FA > 0) ~ "Enriched to DAG and FA"))
+## Gene Ontology Analysis
 
-DH_2017_data$VennRegion <- factor(pull(DH_2017_data, VennRegion), ordered = TRUE, levels = c("Enriched to Sph only", "Enriched to DAG only", "Enriched to FA only", "Enriched to Sph and DAG", "Enriched to Sph and FA", "Enriched to DAG and FA", "Enriched to all probes"))
+```{r GO data wrangling, echo=FALSE, warning=FALSE}
 
+# ID_LUT <- clusterProfiler::bitr(geneID= DH_2017_data$gene_name, 
+#                                 fromType = "SYMBOL",
+#                                 toType = "ENTREZID",
+#                                 OrgDb = org.Hs.eg.db
+# )
+
+# names(ID_LUT) <- c("gene_name", "ENTREZID")
+
+# # Merging ENTREZIDs to data
+# DH_2017_data_GO <- left_join(DH_2017_data, ID_LUT)
+
+# ego_results_Identification_CC <- NULL
+
+# # Attempts to identify pathways in the dataset
+# try(
+#   ego_results_Identification_CC <- clusterProfiler::compareCluster(ENTREZID ~ VennRegion,
+#                                     data = DH_2017_data_GO, fun = "enrichGO",
+#                                     OrgDb = org.Hs.eg.db,
+#                                     keyType = "ENTREZID",
+#                                     ont = "CC",
+#                                     readable = TRUE,
+#                                     universe = ID_LUT$ENTREZID)
+#                                     )
+
+# # If no pathway identified, returns text warning user.
+# if (is.null(ego_results_Identification_CC)) {
+#   print("No pathways identified among enriched hits and candidates.")
+# }
+
+# # If pathways identified, produces both plots for viewing.
+# if (!is.null(ego_results_Identification_CC))
+#   {
+#   ego_results_Identification_CC_table <- ego_results_Identification_CC@compareClusterResult
+#   ego_results_Identification_CC_table <- ego_results_Identification_CC_table %>% 
+#     group_by(ID, VennRegion) %>%
+#     mutate(odds_ratio = calculateFE(GeneRatio, BgRatio))
+#   ego_results_Identification_CC_table$Description <- factor(ego_results_Identification_CC_table$Description, levels = unique(rev(ego_results_Identification_CC_table$Description)))
+
+#   ego_sub <- ego_results_Identification_CC_table %>% 
+#     group_by(VennRegion) %>%
+#     slice_head(n = 10)
+
+#   # Makes the dot plot
+#   dot <- ggplot(data = ego_sub, aes(VennRegion, Description)) +
+#     geom_point(aes(size = odds_ratio, colour = -log10(p.adjust))) +
+#     theme_bw(base_size = 12) +
+#     scale_colour_gradientn(colours = c("#377eb8", "#984ea3", "#e41a1c", "#ff7f00", "#ffff33"), ) +
+#     # ggtitle("Cellular compartment") +
+#     ylab("") +
+#     xlab("Enrichment Profile") +
+#     theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust = 1))
+
+#   dot <- ggplotly(dot)
+#   # Save as HTML (adjust the path as needed)
+#   saveWidget(dot, file = paste0(here(), "/IndividualStudies/GO_plots/DH_2017_CC_DOTPLOT.html"), selfcontained = TRUE)
+
+#   try(
+# 			# Makes the cnet plot
+#     cnet <- clusterProfiler::cnetplot(ego_results_Identification_CC, categorySize = "pvalue") +
+#       # ggtitle("Cellular compartment") +
+#         customPlot
+#     )
+
+#   if(!is.null(cnet)){
+#       ggsave(paste0(here(), "/IndividualStudies/GO_plots/DH_2017_CC_CNET.png"),
+#            width = 12, height = 12)
+#   } else {
+#     print("Cnet plot failed in production.")
+#   }
+# }
+
+# ego_results_Identification_MF <- NULL
+
+# # Attempts to identify pathways in the dataset
+# try(
+#   ego_results_Identification_MF <- clusterProfiler::compareCluster(ENTREZID ~ VennRegion,
+#                                     data = DH_2017_data_GO, fun = "enrichGO",
+#                                     OrgDb = org.Hs.eg.db,
+#                                     keyType = "ENTREZID",
+#                                     ont = "MF",
+#                                     readable = TRUE,
+#                                     universe = ID_LUT$ENTREZID)
+#                                     )
+
+# # If no pathway identified, returns text warning user.
+# if (is.null(ego_results_Identification_MF)) {
+#   print("No pathways identified among enriched hits and candidates.")
+# }
+
+# # If pathways identified, produces both plots for viewing.
+# if (!is.null(ego_results_Identification_MF))
+#   {
+  # ego_results_Identification_MF_table <- ego_results_Identification_MF@compareClusterResult
+  # ego_results_Identification_MF_table <- ego_results_Identification_MF_table %>% 
+  #   group_by(ID, VennRegion) %>%
+  #   mutate(odds_ratio = calculateFE(GeneRatio, BgRatio))
+  # ego_results_Identification_MF_table$Description <- factor(ego_results_Identification_MF_table$Description, levels = unique(rev(ego_results_Identification_MF_table$Description)))
+
+  # ego_sub <- ego_results_Identification_MF_table %>% 
+  #   group_by(VennRegion) %>%
+  #   slice_head(n = 10)
+
+  # # Makes the dot plot
+  # dot <- ggplot(data = ego_sub, aes(VennRegion, Description)) +
+  #   geom_point(aes(size = odds_ratio, colour = -log10(p.adjust))) +
+  #   theme_bw(base_size = 12) +
+  #   scale_colour_gradientn(colours = c("#377eb8", "#984ea3", "#e41a1c", "#ff7f00", "#ffff33"), ) +
+  #   # ggtitle("Cellular compartment") +
+  #   ylab("") +
+  #   xlab("Enrichment Profile") +
+  #   theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust = 1))
+
+  # dot <- ggplotly(dot)
+  # # Save as HTML (adjust the path as needed)
+  # saveWidget(dot, file = paste0(here(), "/IndividualStudies/GO_plots/DH_2017_MF_DOTPLOT.html"), selfcontained = TRUE)
+
+#   try(
+# 			# Makes the cnet plot
+#     cnet <- clusterProfiler::cnetplot(ego_results_Identification_MF, categorySize = "pvalue") +
+#       # ggtitle("Cellular compartment") +
+#         customPlot
+#     )
+
+#   if(!is.null(cnet)){
+#       ggsave(paste0(here(), "/IndividualStudies/GO_plots/DH_2017_MF_CNET.png"),
+#            width = 12, height = 12)
+#   } else {
+#     print("Cnet plot failed in production.")
+#   }
+# }
+
+# ego_results_Identification_BP <- NULL
+
+# # Attempts to identify pathways in the dataset
+# try(
+#   ego_results_Identification_BP <- clusterProfiler::compareCluster(ENTREZID ~ VennRegion,
+#                                     data = DH_2017_data_GO, fun = "enrichGO",
+#                                     OrgDb = org.Hs.eg.db,
+#                                     keyType = "ENTREZID",
+#                                     ont = "BP",
+#                                     readable = TRUE,
+#                                     universe = ID_LUT$ENTREZID)
+#                                     )
+
+# # If no pathway identified, returns text warning user.
+# if (is.null(ego_results_Identification_BP)) {
+#   print("No pathways identified among enriched hits and candidates.")
+# }
+
+# If pathways identified, produces both plots for viewing.
+# if (!is.null(ego_results_Identification_BP))
+#   {
+#   ego_results_Identification_BP_table <- ego_results_Identification_BP@compareClusterResult
+#   ego_results_Identification_BP_table <- ego_results_Identification_BP_table %>% 
+#     group_by(ID, VennRegion) %>%
+#     mutate(odds_ratio = calculateFE(GeneRatio, BgRatio))
+#   ego_results_Identification_BP_table$Description <- factor(ego_results_Identification_BP_table$Description, levels = unique(rev(ego_results_Identification_BP_table$Description)))
+
+#   ego_sub <- ego_results_Identification_BP_table %>% 
+#     group_by(VennRegion) %>%
+#     slice_head(n = 10)
+
+#   # Makes the dot plot
+#   dot <- ggplot(data = ego_sub, aes(VennRegion, Description)) +
+#     geom_point(aes(size = odds_ratio, colour = -log10(p.adjust))) +
+#     theme_bw(base_size = 12) +
+#     scale_colour_gradientn(colours = c("#377eb8", "#984ea3", "#e41a1c", "#ff7f00", "#ffff33"), ) +
+#     # ggtitle("Cellular compartment") +
+#     ylab("") +
+#     xlab("Enrichment Profile") +
+#     theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust = 1))
+
+#   dot <- ggplotly(dot)
+#   # Save as HTML (adjust the path as needed)
+#   saveWidget(dot, file = paste0(here(), "/IndividualStudies/GO_plots/DH_2017_BP_DOTPLOT.html"), selfcontained = TRUE)
+
+#   try(
+# 			# Makes the cnet plot
+#     cnet <- clusterProfiler::cnetplot(ego_results_Identification_BP, categorySize = "pvalue") +
+#       # ggtitle("Cellular compartment") +
+#         customPlot
+#     )
+
+#   if(!is.null(cnet)){
+#       ggsave(paste0(here(), "/IndividualStudies/GO_plots/DH_2017_BP_CNET.png"),
+#            width = 12, height = 12)
+#   } else {
+#     print("Cnet plot failed in production.")
+#   }
+# }
+```
+
+**In beta: GO analysis still under development**
+
+:::: {.panel-tabset}
+
+#### Cell Compartment
+:::{.border}
+<iframe src="/IndividualStudies/GO_plots/DH_2017_CC_DOTPLOT.html" width="100%" height="500px"></iframe>
+
+:::
+
+#### Molecular Function
+:::{.border}
+<iframe src="/IndividualStudies/GO_plots/DH_2017_MF_DOTPLOT.html" width="100%" height="500px"></iframe>
+
+:::
+
+#### Biological Process
+:::{.border}
+<iframe src="/IndividualStudies/GO_plots/DH_2017_BP_DOTPLOT.html" width="100%" height="500px"></iframe>
+
+:::
+::::
+
+:::{.border}
+```{r Building Datatable, echo=FALSE, warning=FALSE}
 DH_2017_data_reactive <- crosstalk::SharedData$new(DH_2017_data)
@@
 datatable(DH_2017_data_reactive, options = list(pageLength = 20))
-
 ```

### 2025-02-25 IndividualStudies/RM_2021.qmd
new links on index.qmd, reduced library redundancy

@@
 ## intitialize libraries
-library(dplyr)
-library(tidyr)
-library(plotly)
-library(ggplot2)
-library(grid)
-library(readr)
-library(rmarkdown)
-library(emojifont)
-library(gt)
-library(crosstalk)
-library(DT)
-library(htmltools)
 library(here)

### 2025-02-25 IndividualStudies/SF_2024.qmd
new links on index.qmd, reduced library redundancy

@@
 ## intitialize libraries
-library(dplyr)
-library(tidyr)
-library(plotly)
-library(ggplot2)
-library(grid)
-library(readr)
-library(rmarkdown)
-library(emojifont)
-library(gt)
-library(crosstalk)
-library(DT)
-library(htmltools)
-library(scales)
 library(here)

### 2025-02-25 IndividualStudies/SF_2024_B.qmd
new links on index.qmd, reduced library redundancy

@@
 ## intitialize libraries
-library(dplyr)
-library(tidyr)
-library(plotly)
-library(ggplot2)
-library(grid)
-library(readr)
-library(rmarkdown)
-library(emojifont)
-library(gt)
-library(crosstalk)
-library(DT)
 library(here)

### 2025-02-25 index.qmd
new links on index.qmd, reduced library redundancy

@@
 
+## Need more info?
+
 See our [Functional Lipid Probes Overview](/Background/MultifunctionalLipidProbesOverview.qmd) for more details about how these lipid analogs are used.
+
+See our [Proteomics Methodology Overview](/Background/ProteomicsUsingMultifunctionalProbes.qmd) for more details about the quantification methods used in the data presented in this repository.
+
+See our [Data Analysis Overview](/Background/DataAnalysisAndStatistics.qmd) for more details about the data analysis between the raw mass spectrometry data and the final data presented here.
 

### 2025-02-25 Resources/ggplot_styles.R

@@ -1,5 +1,4 @@
 ################ Library Initialization ################
-
 library(ggplot2)
 library(ggrepel)
 library(emojifont)
@@ -12,6 +11,17 @@ library(enrichplot)
 library(igraph)
 library(ggtangle)
 library(stringr)
+library(crosstalk)
+library(plotly)
+library(grid)
+library(readr)
+library(rmarkdown)
+library(gt)
+library(DT)
+library(heatmaply)
+library(ggvenn)
+library(scales)
+library(htmltools)
 
 ################ Helper Functions ################
 

### 2025-02-25 Background/DataAnalysisAndStatistics.qmd
EOD push
Adding detail to Data Analysis background page

@@
 
-## TMT quantitative mass spec pipeline
+## TMT quantitative mass spec pipeline {#sec-DataAnalysis_TMTPipeline}
 
@@
 
+<!-- 
 ## PSM quantitative mass spec analysis
@@
 
-* Need these details.
+* Need these details. -->
+
+## Visualizing proteomics data {#sec-DataAnalysis_visualization}
+
+### Volcano Plots
+
+* Visualize enrichment data versus the statistical p value associated with every protein identified in a dataset. 
+* In each of the datasets depicted on this site, data points to the right of the x-axis (logFC > 0) denote proteins which were enriched when the lipid probe was irradiated with UV light -- stimulating chemical crosslinking.
+* The p value of each protein was -log10 transformed, meaning that the smaller the p value, the higher the point is. 
+* In the datasets depicted on this site, there is little meaning to points with logFC < 0; as such, these proteins are ignored regardless of their statistical significance
+
+### Rank-ordered Plots
+
+* Line up each protein identified in the data set from lowest logFC to highest.
+* Enables the viewer to see the shape of the dataset -- for example, some datasets will have only a few proteins substantially enriched, and this is reflected by a sharp "elbow" at the edges of the plot.
+* This can be helpful in selecting logFC cutoffs when determining significance cutoffs.
+
+### MA Plots
+
+* Depict the logFC of each protein (**M**) versus the average m/z intensity of the peptides (**A**) that contributed to that proteins identification.
+* Gives greater insight into the quality of a datapoint.
+For example, a point on the far left of the MA plot had relatively low total abundance and may be more sensitive to dramatic changes in enrichment -- whereas points to the right were substantially more abundant in the sample and will be less sensitive to change.
+* Thus, "significantly enriched" proteins with higher **A** intensity may be more trustworthy than those with lower **A** values.
+
+### Heat Maps
+
+### Gene Ontology Overview {#sec-DataAnalysis_GeneOntology}
+
+* Gene Ontology (GO) analyses take a list of proteins and determines whether there is a greater than random enrichment of a biological feature.
+These features can include pathways, molecular functions, cellular compartments or biological processes.
+* In each of the GO analyses presented on this site, we filtered according to a significance cutoff -- these cutoffs are explained on the respective data pages (either "enriched candidates" or "enriched hits", as in the TMT-based datasets, or unique subsets of probe enrichment, as in the PSM-based datasets).
+* Enriched pathways are given statistical significance by assessing the likelihood that a pathway would be overrepresented through random chance.
+
+#### Gene Ontology Dot Plots
+
+#### Gene Ontology CNET maps

### 2025-02-26 Background/DataAnalysisAndStatistics.qmd
Berit made us new structure figures, new text in data background section

@@
 
-#### Gene Ontology CNET maps
+#### Gene Ontology Concept Network (CNET) Plots
+
+* Visualizes the relationships between genes and biological gene ontology terms as a network.
+Concepts (cellular compartment, molecular function, biological process) are arranged as hub nodes with all related genes arrayed as connecting nodes.
+Genes associated with multiple concepts can be connected to several concept nodes, highlighting the intersection of the concepts.

### 2025-02-26 LipidProbe/PhosphatidicAcid.qmd
new links on index.qmd, reduced library redundancy
Berit made us new structure figures, new text in data background section

@@
 :::{.border}
-![](/LipidProbe/Structures/PhosphatidicAcid_Structure.png)
+![Trifunctional Phosphatidic Acid](/LipidProbe/Structures/TF_PA.png)
 :::

### 2025-02-26 LipidProbe/Phosphatidylethanolamine.qmd
new links on index.qmd, reduced library redundancy
Berit made us new structure figures, new text in data background section

@@
 :::{.border}
-![](Structures/PhosphatidylethanolamineStructure.png)
+![Trifunctional Phosphatidylethanolamine](/LipidProbe/Structures/TF_PE.png)
 :::

### 2025-02-26 LipidProbe/PhosphatidylinositolTrisphosphate.qmd
EOD
Spent all day learning how to make my heatmap look less bad
Berit made us new structure figures, new text in data background section

@@
 subtitle: "PI(3,4,5)P~3~"
+prefer-html: true
 ---
@@
 
+:::{.border}
+![Trifunctional Phosphatidylinositol 3,4,5-*bis*phosphate](/LipidProbe/Structures/TF_PI(3,4,5)P3.png)
+:::
+
 ## Protein interactome

### 2025-02-26 Resources/ggplot_styles.R

@@ -442,6 +442,8 @@ MF_enrichment_plots <- function(data, plotReturnType, filename){
 	# Initializes a ego results vector as NULL in the event that no pathways get identified
 	ego_results_Identification_MF <- NULL
 
+  clusterProfiler::gseKEGG()
+
 	# Attempts to identify pathways in the dataset
 	try(
 		ego_results_Identification_MF <- clusterProfiler::compareCluster(ENTREZID ~ sample,

### 2025-02-26 LipidProbe/Sphinganine.qmd
Berit made us new structure figures, new text in data background section
minor changes to study info

@@
 ---
-title: "Trifunctional sphinganine"
+title: "Trifunctional Sphinganine"
 prefer-html: true
@@
 :::{.border}
-![](/LipidProbe/Structures/SphinganineStructure.png)
+![Trifunctional Sphinganine](/LipidProbe/Structures/TF_Sphinganine.png)
 :::
@@
 
-## Gene Ontology enrichment
+## Gene Ontology Analysis
 
 **In beta: GO analysis still under development**
+
+[Click here for more information about Gene Ontology analysis.](/Background/DataAnalysisAndStatistics.qmd#gene-ontology-overview)
 

### 2025-02-26 StudyInformation_includes/SF_2024_A_include.qmd
minor changes to study info

@@
 
+<a href="/LipidProbe/Sphingosine.qmd" class="hover-preview">Trifunctional Sphingosine</a>
+<span class="hover-image">
+  <img src="/LipidProbe/Structures/TF_Sphingosine.png" alt="Trifunctional Sphingosine" />
+</span>
+
+<a href="/LipidProbe/Sphinganine.qmd" class="hover-preview">Trifunctional Sphinganine</a>
+<span class="hover-image">
+  <img src="/LipidProbe/Structures/TF_Sphinganine.png" alt="Trifunctional Sphinganine" />
+</span>
+
 #### Cell line analyzed
@@
 [Huh7](https://huh7.com){target="_blank"}
+
+#### Uncaging & Crosslinking timeline
+
+| Lipid Probe | Uptake time | Uncaging time | Interaction time | Crosslinking time |
+|:-------|:------:|:------:|:------:|:------:|
+| Sph    | 60 min | 5 min  | 15 min | 5 min  |
+| Spa    | 60 min | 5 min  | 15 min | 5 min  |
 

### 2025-02-26 StudyInformation_includes/SF_2024_B_include.qmd
updating with includes structure
minor changes to study info

--- 2025-01-30 StudyInformation_includes/SF_2024_A_include.qmd
@@
-## Study details
+#### Study details
 
-#### Authors
+##### Authors
 Scotland E. Farley, Frank Stein, Per Haberkant, Fikadu G. Tafesse, Carsten Schultz
 
-#### Journal
+##### Journal
 ACS Chemical Biology
 
-<https://doi.org/10.1021/acschembio.3c00554>{target="_blank"}
+<https://doi.org/10.1039/D4CC00974F>{target="_blank"}
 
-#### Abstract
+##### Abstract
 
@@
 
-#### Lipid probes utilized
+##### Lipid probes utilized
 
-#### Cell line analyzed
+<a href="/LipidProbe/1-10_FattyAcid.qmd" class="hover-preview">Trifunctional 1-10 Fatty Acid</a>
+<span class="hover-image">
+  <img src="/LipidProbe/Structures/TF_1-10_fatty_acid.png" alt="Trifunctional 1-10 Fatty Acid" />
+</span>
+
+<a href="/LipidProbe/8-3_FattyAcid.qmd" class="hover-preview">Trifunctional 8-3 Fatty Acid</a>
+<span class="hover-image">
+  <img src="/LipidProbe/Structures/TF_8-3_fatty_acid.png" alt="Trifunctional 8-3 Fatty Acide" />
+</span>
+
+##### Cell line analyzed
 
@@
 
-#### Mass spectrometry quantification method
+#### Uncaging & Crosslinking timeline
+
+| Lipid Probe | Uptake time | Uncaging time | Interaction time | Crosslinking time |
+|:-------|:------:|:------:|:------:|:------:|
+| 1-10 FA|  min |  min  |  min |  min  |
+| 8-3 FA |  min |  min  |  min |  min  |
+
+##### Mass spectrometry quantification method
 
@@
 
-#### Additional sample preparation <span class="help-symbol" title="e.g. sub-cellular fractionation, depletion, etc.">?</span>
+##### Additional sample preparation <span class="help-symbol" title="e.g. sub-cellular fractionation, depletion, etc.">?</span>

### 2025-02-26 LipidProbe/8-3_FattyAcid.qmd
Berit made us new structure figures, new text in data background section
Keep finding small inconsistencies between pages

@@
 ---
+
+*Greater context to the distinction between the 8-3 Fatty Acid and 1-10 Fatty Acid probes can be found in the [Diazirine Overview](/Background/MultifunctionalLipidProbesOverview.qmd#sec-DiazirinePlacement)*
+
+## Structure
+
+:::{.border}
+![Trifunctional 8-3 Fatty Acid](/LipidProbe/Structures/TF_8-3_fatty_acid.png)
+:::
+
+## Protein interactome
+
+### Cell background: Huh7
 
@@
 
-*Greater context to the distinction between the 8-3 Fatty Acid and 1-10 Fatty Acid probes can be found in the [Diazirine Overview](/Background/MultifunctionalLipidProbesOverview.qmd#sec-DiazirinePlacement)*
-
-## Structure
-
-:::{.border}
-![](/LipidProbe/Structures/8-3_FattyAcid_Structure.png)
-:::
-
-## Protein interactome
-
-### Cell background: Huh7
-
 ::: {.callout-note collapse="true"}
 
-{{< include /StudyInformation_includes/SF_2024_A_include.qmd >}}
+{{< include /StudyInformation_includes/SF_2024_B_include.qmd >}}
 
@@
 **In beta: GO analysis still under development**
+
+[Click here for more information about Gene Ontology analysis.](/Background/DataAnalysisAndStatistics.qmd#gene-ontology-overview)
 

### 2025-02-27 LipidProbe/1-10_FattyAcid.qmd
Berit made us new structure figures, new text in data background section
Keep finding small inconsistencies between pages
Trying to fix the dotplot framing on mobile, not much luck yet

@@
 title: "Trifunctional 1-10 Fatty Acid"
-crossref: 
-  ref-hyperlink: true # (default is true)
 prefer-html: true
 ---
+
+:::{.content-hidden unless-format="html"}
+
+*Greater context to the distinction between the 8-3 Fatty Acid and 1-10 Fatty Acid probes can be found in the [Diazirine Overview](/Background/MultifunctionalLipidProbesOverview.qmd#sec-DiazirinePlacement)*
+
+## Structure
+
+:::{.border}
+![Trifunctional 1-10 Fatty Acid](/LipidProbe/Structures/TF_1-10_fatty_acid.png)
+:::
+
+## Protein interactome
+
+### Cell background: Huh7
 
@@
 ```
-
-*Greater context to the distinction between the 8-3 Fatty Acid and 1-10 Fatty Acid probes can be found in the [Diazirine Overview](/Background/MultifunctionalLipidProbesOverview.qmd#sec-DiazirinePlacement)*
-
-## Structure
-
-:::{.border}
-![](/LipidProbe/Structures/1-10_FattyAcid_Structure.png)
-:::
-
-## Protein interactome
-
-### Cell background: Huh7
 
@@
 ::::
+
+:::

### 2025-02-27 StudyInformation_includes/SF_2024_B_include.qmd
Trying to fix the dotplot framing on mobile, not much luck yet

@@
 |:-------|:------:|:------:|:------:|:------:|
-| 1-10 FA|  min |  min  |  min |  min  |
-| 8-3 FA |  min |  min  |  min |  min  |
+| 1-10 FA|  60 min | 5 min  | 60 min | 5 min  |
+| 8-3 FA |  60 min | 5 min  | 60 min | 5 min  |
 

### 2025-02-27 IndividualStudies/AT_2025.qmd
Adding GO analysis to DH_2017
new links on index.qmd, reduced library redundancy
Updated the GO box, made uniform across all pages

@@
 
-## Gene Ontology enrichment
+## Gene Ontology Analysis
 
@@
 
+[Click here for more information about Gene Ontology analysis.](/Background/DataAnalysisAndStatistics.qmd#gene-ontology-overview)
+
+:::::{.border}
+::::{#fig-PE_GOplots}
 ::: {.panel-tabset}
@@
 #### Cell Compartment
-
-:::{.border}
 
@@
 
-:::
-
 #### Molecular Function
-
-:::{.border}
 
@@
 
-:::
-
 #### Biological Process
-
-:::{.border}
 
@@
 ![](/IndividualStudies/GO_plots/PE-PA_AT_2025_BP-CNETplot.png)
-
 :::
 
-:::
+GO Dot plots display the enrichment of GO terms among the proteins enriched to the probe.
+For these analyses, only proteins categorized as "enriched candidates" and "enriched hits" were subject to GO analysis.
+The Cell Compartment analysis assesses whether the list of enriched proteins contains a statistically significant number of proteins in the same cellular region; appropriately, the Molecular Function and Biological Process analyses does the same for molecular function and biological process, respectively.
+[Click here for more information about GO dot plots.](/Background/DataAnalysisAndStatistics.qmd#gene-ontology-overview)
+::::
+:::::
 

### 2025-02-27 IndividualStudies/DH_2017.qmd
new links on index.qmd, reduced library redundancy
Updated the GO box, made uniform across all pages

--- 2025-02-20 IndividualStudies/DH_2017.qmd
@@
 ## intitialize libraries
-library(dplyr)
-library(tidyr)
-library(plotly)
-library(ggplot2)
-library(grid)
-library(readr)
-library(rmarkdown)
-library(emojifont)
-library(gt)
-library(crosstalk)
-library(DT)
-library(stringr)
-library(pheatmap)
 library(here)
-library(heatmaply)
-library(ggvenn)
-library(scales)
 
@@
 
-```{r, echo=FALSE, warning=FALSE}
+:::
 
-DH_2017_data <- DH_2017_data |>
-  mutate(VennRegion = case_when(
-    (PSM_Sph > 0 & PSM_DAG > 0 & PSM_FA > 0) ~ "Enriched to all probes",
-    (PSM_Sph > 0 & PSM_DAG == 0 & PSM_FA == 0) ~ "Enriched to Sph only",
-    (PSM_Sph == 0 & PSM_DAG > 0 & PSM_FA == 0) ~ "Enriched to DAG only",
-    (PSM_Sph == 0 & PSM_DAG == 0 & PSM_FA > 0) ~ "Enriched to FA only",
-    (PSM_Sph > 0 & PSM_DAG > 0 & PSM_FA == 0) ~ "Enriched to Sph and DAG",
-    (PSM_Sph > 0 & PSM_DAG == 0 & PSM_FA > 0) ~ "Enriched to Sph and FA",
-    (PSM_Sph == 0 & PSM_DAG > 0 & PSM_FA > 0) ~ "Enriched to DAG and FA"))
+## Gene Ontology Analysis
 
-DH_2017_data$VennRegion <- factor(pull(DH_2017_data, VennRegion), ordered = TRUE, levels = c("Enriched to Sph only", "Enriched to DAG only", "Enriched to FA only", "Enriched to Sph and DAG", "Enriched to Sph and FA", "Enriched to DAG and FA", "Enriched to all probes"))
+**In beta: GO analysis still under development**
 
+[Click here for more information about Gene Ontology analysis.](/Background/DataAnalysisAndStatistics.qmd#gene-ontology-overview)
+
+:::::{.border}
+::::{#fig-PE_GOplots}
+::: {.panel-tabset}
+
+#### Cell Compartment
+
+<iframe src="/IndividualStudies/GO_plots/DH_2017_CC_DOTPLOT.html" width="100%" height="500px"></iframe>
+
+#### Molecular Function
+
+<iframe src="/IndividualStudies/GO_plots/DH_2017_MF_DOTPLOT.html" width="100%" height="500px"></iframe>
+
+#### Biological Process
+
+<iframe src="/IndividualStudies/GO_plots/DH_2017_BP_DOTPLOT.html" width="100%" height="500px"></iframe>
+:::
+
+GO Dot plots display the enrichment of GO terms among the proteins enriched to the probe.
+For these analyses, only proteins categorized as "enriched candidates" and "enriched hits" were subject to GO analysis.
+The Cell Compartment analysis assesses whether the list of enriched proteins contains a statistically significant number of proteins in the same cellular region; appropriately, the Molecular Function and Biological Process analyses does the same for molecular function and biological process, respectively.
+[Click here for more information about GO dot plots.](/Background/DataAnalysisAndStatistics.qmd#gene-ontology-overview)
+::::
+:::::
+
+:::{.border}
+```{r Building Datatable, echo=FALSE, warning=FALSE}
 DH_2017_data_reactive <- crosstalk::SharedData$new(DH_2017_data)

### 2025-02-27 IndividualStudies/SF_2024.qmd
Updated the GO box, made uniform across all pages

@@
 (MF CNET plot failed in production)
-:::
 
 #### Biological Process
-
-:::{.border}
 
@@
 (BP CNET plot failed in production)
+
+(BP CNET plot failed in production)
 :::
 
-:::
+GO Dot plots display the enrichment of GO terms among the proteins enriched to the probe.
+For these analyses, only proteins categorized as "enriched candidates" and "enriched hits" were subject to GO analysis.
+The Cell Compartment analysis assesses whether the list of enriched proteins contains a statistically significant number of proteins in the same cellular region; appropriately, the Molecular Function and Biological Process analyses does the same for molecular function and biological process, respectively.
+[Click here for more information about GO dot plots.](/Background/DataAnalysisAndStatistics.qmd#gene-ontology-overview)
+::::
+:::::
 

### 2025-02-27 IndividualStudies/SF_2024_B.qmd
Updated the GO box, made uniform across all pages

@@
 
-:::
+GO Dot plots display the enrichment of GO terms among the proteins enriched to the probe.
+For these analyses, only proteins categorized as "enriched candidates" and "enriched hits" were subject to GO analysis.
+The Cell Compartment analysis assesses whether the list of enriched proteins contains a statistically significant number of proteins in the same cellular region; appropriately, the Molecular Function and Biological Process analyses does the same for molecular function and biological process, respectively.
+[Click here for more information about GO dot plots.](/Background/DataAnalysisAndStatistics.qmd#gene-ontology-overview)
+::::
+:::::
 

### 2025-02-27 LipidProbe/1-10_FattyAcid.qmd
Updated the GO box, made uniform across all pages

@@
 
+:::::{.border}
+::::{#fig-PE_GOplots}
 ::: {.panel-tabset}
@@
 
-:::{.border}
-
 <iframe src="/LipidProbe/GO_plots/1-10FA_SF_2024_CC-DOTplot.html" width="100%" height="500px"></iframe>
@@
 (CC CNET plot failed in production)
-:::
 
 #### Molecular Function
-
-:::{.border}
 
@@
 :::
-:::
+
+GO Dot plots display the enrichment of GO terms among the proteins enriched to the probe.
+For these analyses, only proteins categorized as "enriched candidates" and "enriched hits" were subject to GO analysis.
+The Cell Compartment analysis assesses whether the list of enriched proteins contains a statistically significant number of proteins in the same cellular region; appropriately, the Molecular Function and Biological Process analyses does the same for molecular function and biological process, respectively.
+[Click here for more information about GO dot plots.](/Background/DataAnalysisAndStatistics.qmd#gene-ontology-overview)
+::::
+:::::
 

### 2025-02-27 LipidProbe/8-3_FattyAcid.qmd
Trying to fix the dotplot framing on mobile, not much luck yet
Updated the GO box, made uniform across all pages

@@
 title: "Trifunctional 8-3 Fatty Acid"
-crossref: 
-  ref-hyperlink: true # (default is true)
 prefer-html: true
@@
 
-:::{.border}
+<iframe src="/LipidProbe/GO_plots/8-3FA_SF_2024_CC-DOTplot.html" width="100%" height="500px"></iframe>
+
+(CC CNET plot failed in production)
+
+#### Molecular Function
 
@@
 (CC CNET plot failed in production)
-:::
 
-#### Molecular Function
-
-:::{.border}
+#### Biological Process
 
@@
 
-#### Biological Process
-
-:::{.border}
-
-<iframe src="/LipidProbe/GO_plots/8-3FA_SF_2024_BP-DOTplot.html" width="100%" height="500px"></iframe>
-
-(BP CNET plot failed in production)
-:::
-:::
+GO Dot plots display the enrichment of GO terms among the proteins enriched to the probe.
+For these analyses, only proteins categorized as "enriched candidates" and "enriched hits" were subject to GO analysis.
+The Cell Compartment analysis assesses whether the list of enriched proteins contains a statistically significant number of proteins in the same cellular region; appropriately, the Molecular Function and Biological Process analyses does the same for molecular function and biological process, respectively.
+[Click here for more information about GO dot plots.](/Background/DataAnalysisAndStatistics.qmd#gene-ontology-overview)
+::::
+:::::
 
@@
 
-::::
-
 ### Cell background: HeLa

### 2025-02-27 LipidProbe/PhosphatidicAcid.qmd
Keep finding small inconsistencies between pages
Updated the GO box, made uniform across all pages

@@
 
-:::{.border}
-
 <iframe src="/LipidProbe/GO_plots/PA_AT_2025_CC-DOTplot.html" width="100%" height="500px"></iframe>

### 2025-02-27 LipidProbe/Phosphatidylethanolamine.qmd
Keep finding small inconsistencies between pages
Updated the GO box, made uniform across all pages

@@
 
-:::{.border}
-
 <iframe src="/LipidProbe/GO_plots/PE_AT_2025_CC-DOTplot.html" width="100%" height="500px"></iframe>

### 2025-02-27 LipidProbe/Sphinganine.qmd
oops, failed to actually render the updates at last commit
Updated the GO box, made uniform across all pages

@@
 
-:::{.border}
-
 <iframe src="/LipidProbe/GO_plots/Spa_SF_2024_CC-DOTplot.html" width="100%" height="500px"></iframe>

### 2025-02-27 LipidProbe/Sphingosine.qmd
Berit made us new structure figures, new text in data background section
Keep finding small inconsistencies between pages
Updated the GO box, made uniform across all pages

@@
 :::{.border}
-![](/LipidProbe/Structures/SphingosineStructure.png)
+![Trifunctional Sphingosine](/LipidProbe/Structures/TF_Sphingosine.png)
 :::
@@
 
-:::{.border}
-
 <iframe src="/LipidProbe/GO_plots/Sph_SF_2024_CC-DOTplot.html" width="100%" height="500px"></iframe>

### 2025-02-27 StudyInformation_includes/AT_2025_include.qmd
minor changes to study info
Updated the GO box, made uniform across all pages

@@
 <span class="hover-image">
-  <img src="/LipidProbe/Structures/PhosphatidicAcid_Structure.png" alt="Phosphatidic Acid" />
+  <img src="/LipidProbe/Structures/TF_PA.png" alt="Phosphatidic Acid" />
 </span>
 
-<a href="/LipidProbe/Phosphatidylethanolamine.qmd" class="hover-preview">Phosphatidic Acid</a>
+<a href="/LipidProbe/Phosphatidylethanolamine.qmd" class="hover-preview">Phosphatidylethanolamine</a>
 <span class="hover-image">
-  <img src="/LipidProbe/Structures/PhosphatidylethanolamineStructure.png" alt="Phosphatidic Acid" />
+  <img src="/LipidProbe/Structures/TF_PE.png" alt="PPhosphatidylethanolamine" />
 </span>
@@
 [HeLa](https://www.atcc.org/products/ccl-2){target="_blank"}
+
+#### Uncaging & Crosslinking timeline
+
+| Lipid Probe | Uptake time | Uncaging time | Interaction time | Crosslinking time |
+|:-------|:------:|:------:|:------:|:------:|
+| PA    | 60 min | 5 min  | 15 min | 5 min  |
+| PE    | 60 min | 5 min  | 15 min | 5 min  |
 

### 2025-02-27 IndividualStudies/AT_2025.qmd
trying to distinguish cell types more effectively on individual probe pages

@@
 
-[Click here for more information about Gene Ontology analysis.](/Background/DataAnalysisAndStatistics.qmd#gene-ontology-overview)
-
 :::::{.border}
@@
 The Cell Compartment analysis assesses whether the list of enriched proteins contains a statistically significant number of proteins in the same cellular region; appropriately, the Molecular Function and Biological Process analyses does the same for molecular function and biological process, respectively.
-[Click here for more information about GO dot plots.](/Background/DataAnalysisAndStatistics.qmd#gene-ontology-overview)
+[Click here for more information about Gene Ontology analysis.](/Background/DataAnalysisAndStatistics.qmd#gene-ontology-overview)
 ::::

### 2025-02-27 LipidProbe/1-10_FattyAcid.qmd
trying to distinguish cell types more effectively on individual probe pages

@@
 prefer-html: true
+callout-icon: false
 ---
@@
 ## Protein interactome
+
+:::: {.callout-tip}
 
@@
 data$hit_annotation <- factor(pull(data, hit_annotation), levels = c("enriched hit", "hit", "enriched candidate", "candidate", "no hit", "NA"), ordered = TRUE)
-
 ```
@@
 :::{.border}
-```{r, echo=FALSE, warning=FALSE}
+```{r volcano_plot, echo=FALSE, warning=FALSE}
 #| fig-cap: "Data as reported in [Farley et al., 2024(B)](/IndividualStudies/SF_2024_B.qmd).
@@
 :::{.border}
-```{r, echo=FALSE, warning=FALSE}
+```{r ro_plot, echo=FALSE, warning=FALSE}
 #| fig-cap: "Data as reported in [Farley et al., 2024(B)](/IndividualStudies/SF_2024_B.qmd).
@@
 :::{.border}
-```{r, echo=FALSE, warning=FALSE}
+```{r MA_plot, echo=FALSE, warning=FALSE}
 #| fig-cap: "Data as reported in [Farley et al., 2024(B)](/IndividualStudies/SF_2024_B.qmd).
@@
 **In beta: GO analysis still under development**
-
-[Click here for more information about Gene Ontology analysis.](/Background/DataAnalysisAndStatistics.qmd#gene-ontology-overview)
 
@@
 The Cell Compartment analysis assesses whether the list of enriched proteins contains a statistically significant number of proteins in the same cellular region; appropriately, the Molecular Function and Biological Process analyses does the same for molecular function and biological process, respectively.
-[Click here for more information about GO dot plots.](/Background/DataAnalysisAndStatistics.qmd#gene-ontology-overview)
+[Click here for more information about Gene Ontology analysis.](/Background/DataAnalysisAndStatistics.qmd#gene-ontology-overview)
+
 ::::
@@
 :::{.border}
-```{r, echo=FALSE, warning=FALSE}
+```{r datatable, echo=FALSE, warning=FALSE}
 
@@
 
+<br>
+
 {{< downloadthis DataSets/1-10_FA_Huh7_SF_2024.csv dname="1-10_FA_Huh7_SF_ACS-Chem-Bio_2024">}}

### 2025-02-27 LipidProbe/8-3_FattyAcid.qmd
trying to distinguish cell types more effectively on individual probe pages

@@
 html: default
+callout-icon: false
 ---
@@
 
+::::{.callout-tip}
 ### Cell background: Huh7
@@
 
+<br>
+
 {{< downloadthis DataSets/8-3_FA_Huh7_SF_2024.csv dname="8-3_FA_Huh7_SF_ACS-Chem-Bio_2024">}}
+::::
 
+::::{.callout-tip}
 ### Cell background: HeLa
@@
 ::::
+
+::::

### 2025-02-27 LipidProbe/PhosphatidicAcid.qmd
trying to distinguish cell types more effectively on individual probe pages

@@
   html: default
-
+callout-icon: false
 ---
@@
 
+## Protein Interactome
+
+::::{.callout-tip}
 ### Cell background: HeLa
@@
 The Cell Compartment analysis assesses whether the list of enriched proteins contains a statistically significant number of proteins in the same cellular region; appropriately, the Molecular Function and Biological Process analyses does the same for molecular function and biological process, respectively.
-[Click here for more information about GO dot plots.](/Background/DataAnalysisAndStatistics.qmd#gene-ontology-overview)
+[Click here for more information about Gene Ontology Analysis.](/Background/DataAnalysisAndStatistics.qmd#gene-ontology-overview)
 ::::
@@
 
+<br>
+
 {{< downloadthis DataSets/PA_HeLa_AT_2025.csv dname="PA_HeLa_AT_ChemComm_download">}}
+
+::::

### 2025-02-27 LipidProbe/Phosphatidylethanolamine.qmd
trying to distinguish cell types more effectively on individual probe pages

@@
   html: default
+callout-icon: false
 
@@
 
-## Protein interactome
+## Protein Interactome
+
+:::: {.callout-tip}
 
@@
 {{< downloadthis DataSets/PE_HeLa_AT_2025.csv dname="PE_HeLa_AT_ChemComm_download">}}
+
+::::

### 2025-02-27 Resources/ggplot_styles.R

@@ -215,7 +215,7 @@ RankedOrderPlotStandard <- function(data) {
         theme(legend.text = element_text(size = 12))  +
         theme(strip.text = element_text(
     size = 20))
-
+clusterProfiler::gs
     m <- list(l=50, r = 50, b= 100, pad = 4)
 	
     RankedOrderPlotly <- ggplotly(RankedOrderPlots,
@@ -313,11 +313,14 @@ CC_enrichment_plots <- function(data, plotReturnType, filename){
 
 	################
 	#' Makes some GO enrichment plots of the Cellular Compartment
-	#' data must have at least the columns "gene_name", "LipidProbe" and "hit_annotation"
-	#' User must select either a dotplot or a cnet plot to return
-	#' Selects only the proteins which are "enriched candidate" and "enriched hit" and seeks the enriched pathways among them.
+  #' Selects only the proteins which are "enriched candidate" and "enriched hit" and seeks the enriched pathways among them.
 	#' If no pathways enriched, returns a text response to put in the output box
 	#' Basically uses Frank's analysis pipeline to make these plots fresh on each call.
+  #' 
+	#' ARGUMENTS:
+    #' User inputs the dataframe to apply the function to. Data must have at least the columns "gene_name", "LipidProbe" and "hit_annotation"
+    #' User must select either a dotplot or a cnet plot to return
+    #' User then must input the filename to append to the saved files, with the appropriate filepath.
 	################
 
 	# Making lookup table with ENTREZID identifiers from data

### 2025-03-04 Resources/ggplot_styles.R
first commit in a bit

@@ -215,7 +215,6 @@ RankedOrderPlotStandard <- function(data) {
         theme(legend.text = element_text(size = 12))  +
         theme(strip.text = element_text(
     size = 20))
-clusterProfiler::gs
     m <- list(l=50, r = 50, b= 100, pad = 4)
 	
     RankedOrderPlotly <- ggplotly(RankedOrderPlots,

### 2025-03-04 LipidProbe/Sphinganine.qmd
trying to distinguish cell types more effectively on individual probe pages
adding credit to Berit for the structures

@@
 format: html
+callout-icon: false
 ---
@@
 :::{.border}
-![Trifunctional Sphinganine](/LipidProbe/Structures/TF_Sphinganine.png)
+![Trifunctional Sphinganine. Chemical structure drawn by Berit Blume.](/LipidProbe/Structures/TF_Sphinganine.png)
 :::
@@
 
+<br>
+
 {{< downloadthis DataSets/Sph_Huh7_SF_2024.csv dname="Sph_Huh7_SF_ACS-Chem-Bio_download">}}
 
-:::
+::::

### 2025-03-04 LipidProbe/Sphingosine.qmd
trying to distinguish cell types more effectively on individual probe pages
adding credit to Berit for the structures

@@
 :::{.border}
-![Trifunctional Sphingosine](/LipidProbe/Structures/TF_Sphingosine.png)
+![Trifunctional Sphingosine. Chemical structure drawn by Berit Blume.](/LipidProbe/Structures/TF_Sphingosine.png)
 :::
@@
 
+:::
+
+<br>
+
 {{< downloadthis DataSets/Sph_Huh7_SF_2024.csv dname="Sph_Huh7_SF_ACS-Chem-Bio_download">}}
 
-:::
+::::
+
+:::: {.callout-tip}
 
@@
 :::
+
+::::

### 2025-03-07 Background/DataAnalysisAndStatistics.qmd
editing from Frank's suggestions, removing CNET

--- 2025-02-25 Background/DataAnalysisAndStatistics.qmd
@@
 
-To ensure consistency across all publicly available mass spectrometry datasets that used TMT isobaric mass tagging, we applied the same standardized analysis pipeline previously published.
+To ensure consistency across all publicly available mass spectrometry datasets that used TMT isobaric mass tagging, we applied the same standardized analysis pipeline previously published in Farley et al.
+(2024, A), Farley et al.
+(2024, B), and Thomas et al.
+(2025)[@farleyTrifunctionalSphinganineNew2024a; @farleyTrifunctionalFattyAcid2024; @thomasTrifunctionalLipidDerivatives2025].
 This approach allows for better comparability between datasets.
@@
 Frank Stein developed and implemented the data analysis pipeline.
-In summary, we processed the mass spectrometry (MS) data using FragPipe[@yuAnalysisDIAProteomics2023], following established methodologies outlined in Farley et al.
-(2024, A), Farley et al.
-(2024, B), and Thomas et al.
-(2025)[@farleyTrifunctionalSphinganineNew2024a; @farleyTrifunctionalFattyAcid2024; @thomasTrifunctionalLipidDerivatives2025].
-To ensure accurate protein identification, we used a UniProt FASTA database that included common contaminants and reversed sequences for validation.
-Proteins were included in the final dataset only if they contained at least two unique peptides, each at least seven amino acids long.
 
-To account for potential technical variations across experiments, we applied a normalization step using the 'removeBatchEffect' function from the limma package, stabilizing variance in log2-transformed TMT reporter ion intensities[@huberVarianceStabilizationApplied2002; @ritchieLimmaPowersDifferential2015].
+In summary, we processed the mass spectrometry (MS) data using FragPipe[@yuAnalysisDIAProteomics2023].
+The protein search was performed using a UniProt FASTA database with one entry per gene, excluding isoforms and minimizing TrEMBL entries.
+Common contaminants and reversed sequences were also included for validation.
+Proteins were included in the final dataset if they contained at least two razor peptides, as FragPipe applies the Occam’s Razor principle, assigning shared peptides to the protein with the highest supporting evidence.
+
+For the database search, we included post-translational modifications (PTMs) such as oxidation (M), acetylation (N-term), and carbamidomethylation (C).
+The raw files were analyzed using FragPipe's protein.tsv output, which was used as the basis for downstream quantification.
+
+To account for potential technical variations across experiments, we applied a normalization step using the 'removeBatchEffect' function from the limma package to correct for batch effects in log2-transformed TMT reporter ion intensities[@huberVarianceStabilizationApplied2002; @ritchieLimmaPowersDifferential2015].
 Further normalization was carried out using the 'normalizeVSN' function of the same package.
@@
 * Enriched pathways are given statistical significance by assessing the likelihood that a pathway would be overrepresented through random chance.
-
-#### Gene Ontology Dot Plots
-
-#### Gene Ontology CNET maps

### 2025-03-07 IndividualStudies/SF_2024.qmd
adding credit to Berit for the structures
editing from Frank's suggestions, removing CNET

@@
 data <- readr::read_csv(paste0(here(), "/IndividualStudies/DataTables/SF_ACS-Chem-Bio_2024_download.csv"))
-
-# # # Opening the datatable for this page WHILE EDITING
-# data <- readr::read_csv("IndividualStudies/DataTables/SF_ACS-Chem-Bio_2024_download.csv")
 
@@
 
-![](/IndividualStudies/GO_plots/Sph-Spa_SF_2024_CC-CNETplot.png)
-
 #### Molecular Function
@@
 <iframe src="/IndividualStudies/GO_plots/Sph-Spa_SF_2024_MF-DOTplot.html" width="100%" height="500px"></iframe>
-
-(MF CNET plot failed in production)
 
@@
 
-(BP CNET plot failed in production)
-
-(BP CNET plot failed in production)
 :::

### 2025-03-07 LipidProbe/PhosphatidylinositolTrisphosphate.qmd
adding credit to Berit for the structures
editing from Frank's suggestions, removing CNET

--- 2025-01-15 LipidProbe/PhosphatidylinositolTrisphosphate.qmd
@@
 ---
-title: "Trifunctional Phosphatidylinositol 3,4,5-*bis*phosphate"
+title: "Trifunctional Phosphatidylinositol 3,4,5-*tris*phosphate"
 subtitle: "PI(3,4,5)P~3~"
+prefer-html: true
 ---
@@
 
+:::{.border}
+![Trifunctional Phosphatidylinositol 3,4,5-*tris*phosphate. Chemical structure drawn by Berit Blume.](/LipidProbe/Structures/TF_PI(3,4,5)P3.png)
+:::
+
 ## Protein interactome

### 2025-03-11 Resources/Re-run_GO_plots.R
adjusting axis labels for volcano and dot plots

@@ -15,128 +15,128 @@ library(crosstalk)
 ## Opening the source file for the ggplot custom theme
 source(paste0(here(), "/Resources/ggplot_styles.R"))
 
-## Sphingosine
-# Sph_data <- readr::read_csv(paste0(here(), "/LipidProbe/DataSets/Sph_Huh7_SF_2024.csv")) |>
-# 	filter(LipidProbe == "Sph")
+# Sphingosine
+Sph_data <- readr::read_csv(paste0(here(), "/LipidProbe/DataSets/Sph_Huh7_SF_2024.csv")) |>
+	filter(LipidProbe == "Sph")
 
-# CC_enrichment_plots(Sph_data, "dot", "/LipidProbe/GO_plots/Sph_SF_2024_CC-DOTplot")
-# CC_enrichment_plots(Sph_data, "cnet", "/LipidProbe/GO_plots/Sph_SF_2024_CC-CNETplot")
+CC_enrichment_plots(Sph_data, "dot", "/LipidProbe/GO_plots/Sph_SF_2024_CC-DOTplot")
+CC_enrichment_plots(Sph_data, "cnet", "/LipidProbe/GO_plots/Sph_SF_2024_CC-CNETplot")
 
-# MF_enrichment_plots(Sph_data, "dot", "/LipidProbe/GO_plots/Sph_SF_2024_MF-DOTplot")
-# MF_enrichment_plots(Sph_data, "cnet", "/LipidProbe/GO_plots/Sph_SF_2024_MF-CNETplot")
+MF_enrichment_plots(Sph_data, "dot", "/LipidProbe/GO_plots/Sph_SF_2024_MF-DOTplot")
+MF_enrichment_plots(Sph_data, "cnet", "/LipidProbe/GO_plots/Sph_SF_2024_MF-CNETplot")
 
-# BP_enrichment_plots(Sph_data, "dot", "/LipidProbe/GO_plots/Sph_SF_2024_BP-DOTplot")
-# BP_enrichment_plots(Sph_data, "cnet", "/LipidProbe/GO_plots/Sph_SF_2024_BP-CNETplot")
+BP_enrichment_plots(Sph_data, "dot", "/LipidProbe/GO_plots/Sph_SF_2024_BP-DOTplot")
[…]

### 2025-03-11 Resources/ggplot_styles.R

@@ -283,8 +283,8 @@ VolcanoPlotStandardized <- function(data) {
                                     "no hit" = 0.75), 
                         name = "Trend") +
         facet_wrap(~LipidProbe, ncol = 2) +
-        xlab("Log2 fold-change") +
-        ylab("-log10(p-value)") +
+        xlab("Log2 Fold-Change") +
+        ylab("-Log10(p-value)") +
         theme_minimal() +
         theme(text = element_text(family = "serif")) +
         theme(panel.border = element_rect(color = NA, fill = NA))+
@@ -396,7 +396,7 @@ CC_enrichment_plots <- function(data, plotReturnType, filename){
 				scale_colour_gradientn(colours = c("#377eb8", "#984ea3", "#e41a1c", "#ff7f00", "#ffff33"), ) +
 				# ggtitle("Cellular compartment") +
 				ylab("") +
-				xlab("LipidProbe")
+				xlab("lipid probe")
 				theme(axis.text.x = element_text(angle = 0, vjust = 0.5, hjust = 1, size = 12, face = "bold"),
               axis.text.y = element_text(size = 12))
 
@@ -504,7 +504,7 @@ MF_enrichment_plots <- function(data, plotReturnType, filename){
 				scale_colour_gradientn(colours = c("#377eb8", "#984ea3", "#e41a1c", "#ff7f00", "#ffff33"), ) +
 				# ggtitle("Cellular compartment") +
 				ylab("") +
-				xlab("LipidProbe")
+				xlab("lipid probe")
 				theme(axis.text.x = element_text(angle = 0, vjust = 0.5, hjust = 1))
 
 			dot <- ggplotly(dot)
@@ -601,7 +601,7 @@ BP_enrichment_plots <- function(data, plotReturnType, filename){
           scale_colour_gradientn(colours = c("#377eb8", "#984ea3", "#e41a1c", "#ff7f00", "#ffff33"), ) +
           # ggtitle("Cellular compartment") +
           ylab("") +
-          xlab("LipidProbe")
+          xlab("lipid probe")
           theme(axis.text.x = element_text(angle = 0, vjust = 0.5, hjust = 1))
 
         dot <- ggplotly(dot)

### 2025-03-11 index.qmd
cleaning up homepage for preview

@@
 
-**This repository is still under construction, please forgive us for incomplete sections as we build features!**
+<!-- **This repository is still under construction, please forgive us for incomplete sections as we build features!** -->
 
-The goal of this site is to increase the accessibility of proteomics data utilizing multi-functionalized lipid analogs/probes to identify the lipid::protein interactions of biologically active lipids.
+The goal of this site is to increase the accessibility of proteomics data utilizing multi-functionalized lipid analogs/probes to identify the lipid:protein interactions of biologically active lipids.
 

### 2025-03-12 LipidProbe/1-10_FattyAcid.qmd
adding credit to Berit for the structures
editing from Frank's suggestions, removing CNET
updating structures

@@
 :::{.border}
-![Trifunctional 1-10 Fatty Acid](/LipidProbe/Structures/TF_1-10_fatty_acid.png)
+::: {layout="[[-25,75], [100]]"}
+![Native Fatty Acid.](/LipidProbe/Structures/fatty_acid.png)
+
+![Trifunctional 1-10 Fatty Acid.](/LipidProbe/Structures/TF_1-10_fatty_acid.png)
+
+Chemical structures drawn by Berit Blume.
+:::
 :::
@@
 
-(CC CNET plot failed in production)
-
 #### Molecular Function
@@
 (No MF pathways identified among enriched hits and candidates.)
-
-(MF CNET plot failed in production)
 
@@
 
-(BP CNET plot failed in production)
 :::

### 2025-03-12 LipidProbe/8-3_FattyAcid.qmd
adding credit to Berit for the structures
editing from Frank's suggestions, removing CNET
updating structures

@@
 :::{.border}
-![Trifunctional 8-3 Fatty Acid](/LipidProbe/Structures/TF_8-3_fatty_acid.png)
+::: {layout="[[-25,75], [100]]"}
+![Native Fatty Acid.](/LipidProbe/Structures/fatty_acid.png)
+
+![Trifunctional 8-3 Fatty Acid.](/LipidProbe/Structures/TF_8-3_fatty_acid.png)
+
+Chemical structures drawn by Berit Blume.
+:::
 :::
@@
 <iframe src="/LipidProbe/GO_plots/8-3FA_SF_2024_CC-DOTplot.html" width="100%" height="500px"></iframe>
-
-(CC CNET plot failed in production)
 
@@
 
-(MF CNET plot failed in production)
 :::

### 2025-03-12 LipidProbe/PhosphatidicAcid.qmd
adding credit to Berit for the structures
editing from Frank's suggestions, removing CNET
updating structures

@@
 :::{.border}
-![Trifunctional Phosphatidic Acid](/LipidProbe/Structures/TF_PA.png)
+::: {layout="[[-15,85], [100]]"}
+![Native Phosphatidic Acid.](/LipidProbe/Structures/PA.png)
+
+![Trifunctional Phosphatidic Acid.](/LipidProbe/Structures/TF_PA.png)
+
+Chemical structures drawn by Berit Blume.
+:::
 :::
@@
 <iframe src="/LipidProbe/GO_plots/PA_AT_2025_MF-DOTplot.html" width="100%" height="500px"></iframe>
-
-(MF CNET plot failed in production)
 

### 2025-03-12 LipidProbe/Phosphatidylethanolamine.qmd
adding credit to Berit for the structures
editing from Frank's suggestions, removing CNET
updating structures

@@
 :::{.border}
-![Trifunctional Phosphatidylethanolamine](/LipidProbe/Structures/TF_PE.png)
+::: {layout="[[-0.01,99.99], [100]]"}
+![Native Phosphatidylethanolamine.](/LipidProbe/Structures/PE.png)
+
+![Trifunctional Phosphatidylethanolamine.](/LipidProbe/Structures/TF_PE.png)
+
+Chemical structures drawn by Berit Blume.
+:::
+:::
+
+:::{.border}
+![Trifunctional Phosphatidylethanolamine. Chemical structure drawn by Berit Blume.](/LipidProbe/Structures/TF_PE.png)
 :::
@@
 <iframe src="/LipidProbe/GO_plots/PE_AT_2025_MF-DOTplot.html" width="100%" height="500px"></iframe>
-
-(MF CNET plot failed in production)
 

### 2025-03-12 LipidProbe/PhosphatidylinositolTrisphosphate.qmd
updating structures

@@
 :::{.border}
-![Trifunctional Phosphatidylinositol 3,4,5-*tris*phosphate. Chemical structure drawn by Berit Blume.](/LipidProbe/Structures/TF_PI(3,4,5)P3.png)
+::: {layout="[[-1.5,98.5], [100]]"}
+![Native PI(3,4,5)P~3~.](/LipidProbe/Structures/PI(3,4)P2.png)
+
+![Trifunctional PI(3,4,5)P~3~.](/LipidProbe/Structures/TF_PI(3,4,5)P3.png)
+
+Chemical structures drawn by Berit Blume.
+:::
 :::

### 2025-03-12 LipidProbe/Sphinganine.qmd
editing from Frank's suggestions, removing CNET
updating structures

@@
 :::{.border}
-![Trifunctional Sphinganine. Chemical structure drawn by Berit Blume.](/LipidProbe/Structures/TF_Sphinganine.png)
+::: {layout="[[100], [100]]"}
+![Native Sphinganine.](/LipidProbe/Structures/Sphinganine.png)
+
+![Trifunctional Sphinganine.](/LipidProbe/Structures/TF_Sphinganine.png)
+
+Chemical structures drawn by Berit Blume.
+:::
 :::
@@
 <iframe src="/LipidProbe/GO_plots/Spa_SF_2024_MF-DOTplot.html" width="100%" height="500px"></iframe>
-
-(MF CNET plot failed in production)
 

### 2025-03-12 LipidProbe/Sphingosine.qmd
editing from Frank's suggestions, removing CNET
updating structures

@@
 :::{.border}
-![Trifunctional Sphingosine. Chemical structure drawn by Berit Blume.](/LipidProbe/Structures/TF_Sphingosine.png)
+::: {layout="[[100], [100]]"}
+![Native Sphingosine.](/LipidProbe/Structures/Sphingosine.png)
+
+![Trifunctional Sphingosine.](/LipidProbe/Structures/TF_Sphingosine.png)
+
+Chemical structures drawn by Berit Blume.
+:::
 :::

### 2025-03-13 LipidProbe/1-10_FattyAcid.qmd
Judah found some errors in the data tables - fixed them

@@
 data <- data |>
-  dplyr::select(gene_name, LipidProbe, hit_annotation, logFC, pvalue, fdr) |>
+  dplyr::select(gene_name, hit_annotation, logFC, pvalue, fdr) |>
   mutate(logFC = signif(logFC, digits=3),
@@
           fdr = signif(fdr, digits = 3)) |>
-  arrange(hit_annotation) |>
-  arrange(LipidProbe)
+  arrange(hit_annotation, -logFC)
 
@@
                   group = ~hit_annotation,
-									inline=TRUE)
+                  inline="true")
 )
@@
           options = list(pageLength = 10),
-                         colnames = c("Gene Name", "Lipid Probe", "Hit Annotation", "LogFC", "p value", "FDR"))
-
+                         colnames = c("Rank", "Gene Name", "Hit Annotation", "LogFC", "p value", "FDR"))
 ```

### 2025-03-13 LipidProbe/8-3_FattyAcid.qmd
Judah found some errors in the data tables - fixed them

@@
 ```{r, echo=FALSE, warning=FALSE}
+
 # Here is the code to make the filterable lists shown in the crosstalk table below
@@
           options = list(pageLength = 10),
-                         colnames = c("Gene Name", "Lipid Probe", "Hit Annotation", "LogFC", "p value", "FDR"))
+                         colnames = c("Rank", "Gene Name", "Hit Annotation", "LogFC", "p value", "FDR"))
 

### 2025-03-13 LipidProbe/PhosphatidicAcid.qmd
Judah found some errors in the data tables - fixed them

@@
           pvalue = signif(pvalue, digits=3)) |>
-  arrange(hit_annotation)
+  arrange(hit_annotation, -logFC)
 
@@
           caption = "'No hit' proteins are unenriched or depleted in the presence of probe, 'enriched candidates' are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and 'enriched hits' are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV",
-          options = list(pageLength = 10))
+          options = list(pageLength = 10),
+                         colnames = c("Rank", "Gene Name", "Hit Annotation", "LogFC", "p value"))
 

### 2025-03-13 LipidProbe/Phosphatidylethanolamine.qmd
Judah found some errors in the data tables - fixed them

@@
           caption = "'No hit' proteins are unenriched or depleted in the presence of probe, 'enriched candidates' are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and 'enriched hits' are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV",
-          options = list(pageLength = 10))
+          options = list(pageLength = 10),
+                         colnames = c("Rank", "Gene Name", "Hit Annotation", "LogFC", "p value"))
 ```

### 2025-03-13 LipidProbe/Sphinganine.qmd
Judah found some errors in the data tables - fixed them

@@
           fdr = signif(fdr, digits = 3)) |>
-  arrange(hit_annotation)
+  arrange(hit_annotation, -logFC)
 
@@
 
-{{< downloadthis DataSets/Sph_Huh7_SF_2024.csv dname="Sph_Huh7_SF_ACS-Chem-Bio_download">}}
+{{< downloadthis DataSets/Spa_Huh7_SF_2024.csv dname="Spa_Huh7_SF_ACS-Chem-Bio_download">}}
 

### 2025-03-13 LipidProbe/1-10_FattyAcid.qmd
added PI page with structure, no data

@@
 ::: {layout="[[-25,75], [100]]"}
-![Native Fatty Acid.](/LipidProbe/Structures/fatty_acid.png)
+![(A) Native Fatty Acid.](/LipidProbe/Structures/fatty_acid.png)
 
-![Trifunctional 1-10 Fatty Acid.](/LipidProbe/Structures/TF_1-10_fatty_acid.png)
+![(B) Trifunctional 1-10 Fatty Acid.](/LipidProbe/Structures/TF_1-10_fatty_acid.png)
 

### 2025-03-13 LipidProbe/8-3_FattyAcid.qmd
added PI page with structure, no data

@@
 ::: {layout="[[-25,75], [100]]"}
-![Native Fatty Acid.](/LipidProbe/Structures/fatty_acid.png)
+![(A) Native Fatty Acid.](/LipidProbe/Structures/fatty_acid.png)
 
-![Trifunctional 8-3 Fatty Acid.](/LipidProbe/Structures/TF_8-3_fatty_acid.png)
+![(B) Trifunctional 8-3 Fatty Acid.](/LipidProbe/Structures/TF_8-3_fatty_acid.png)
 

### 2025-03-13 LipidProbe/PhosphatidicAcid.qmd
added PI page with structure, no data

@@
 ::: {layout="[[-15,85], [100]]"}
-![Native Phosphatidic Acid.](/LipidProbe/Structures/PA.png)
+![(A) Native Phosphatidic Acid.](/LipidProbe/Structures/PA.png)
 
-![Trifunctional Phosphatidic Acid.](/LipidProbe/Structures/TF_PA.png)
+![(B) Trifunctional Phosphatidic Acid.](/LipidProbe/Structures/TF_PA.png)
 

### 2025-03-13 LipidProbe/Phosphatidylethanolamine.qmd
added PI page with structure, no data

@@
 ::: {layout="[[-0.01,99.99], [100]]"}
-![Native Phosphatidylethanolamine.](/LipidProbe/Structures/PE.png)
+![(A) Native Phosphatidylethanolamine.](/LipidProbe/Structures/PE.png)
 
-![Trifunctional Phosphatidylethanolamine.](/LipidProbe/Structures/TF_PE.png)
+![(B) Trifunctional Phosphatidylethanolamine.](/LipidProbe/Structures/TF_PE.png)
 

### 2025-03-13 LipidProbe/PhosphatidylinositolTrisphosphate.qmd
added PI page with structure, no data

@@
 ::: {layout="[[-1.5,98.5], [100]]"}
-![Native PI(3,4,5)P~3~.](/LipidProbe/Structures/PI(3,4)P2.png)
+![(A) Native PI(3,4,5)P~3~.](/LipidProbe/Structures/PI(3,4)P2.png)
 
-![Trifunctional PI(3,4,5)P~3~.](/LipidProbe/Structures/TF_PI(3,4,5)P3.png)
+![(B) Trifunctional PI(3,4,5)P~3~.](/LipidProbe/Structures/TF_PI(3,4,5)P3.png)
 

### 2025-03-13 LipidProbe/Sphinganine.qmd
added PI page with structure, no data

@@
 ::: {layout="[[100], [100]]"}
-![Native Sphinganine.](/LipidProbe/Structures/Sphinganine.png)
+![(A) Native Sphinganine.](/LipidProbe/Structures/Sphinganine.png)
 
-![Trifunctional Sphinganine.](/LipidProbe/Structures/TF_Sphinganine.png)
+![(B) Trifunctional Sphinganine.](/LipidProbe/Structures/TF_Sphinganine.png)
 

### 2025-03-13 LipidProbe/Sphingosine.qmd
added PI page with structure, no data

@@
 ::: {layout="[[100], [100]]"}
-![Native Sphingosine.](/LipidProbe/Structures/Sphingosine.png)
+![(A) Native Sphingosine.](/LipidProbe/Structures/Sphingosine.png)
 
-![Trifunctional Sphingosine.](/LipidProbe/Structures/TF_Sphingosine.png)
+![(B) Trifunctional Sphingosine.](/LipidProbe/Structures/TF_Sphingosine.png)
 

### 2025-03-13 index.qmd
added PI page with structure, no data

@@
   <a href="LipidProbe/PhosphatidicAcid.qmd" style="text-decoration: none;">
-        <button style="background-color: #3498db; color: white; font-size: 20px; padding: 15px 30px; border: none; border-radius: 8px; margin: 10px; cursor: pointer;">
+      <button style="background-color: #97bdef; color: white; font-size: 20px; padding: 15px 30px; border: none; border-radius: 8px; margin: 10px; cursor: pointer;">
           Phosphatidic Acid
@@
   <a href="LipidProbe/Phosphatidylethanolamine.qmd" style="text-decoration: none;">
-        <button style="background-color: #e74c3c; color: white; font-size: 20px; padding: 15px 30px; border: none; border-radius: 8px; margin: 10px; cursor: pointer;">
+      <button style="background-color: #2986cc; color: white; font-size: 20px; padding: 15px 30px; border: none; border-radius: 8px; margin: 10px; cursor: pointer;">
           Phosphatidylethanolamine
@@
 
+    <a href="LipidProbe/Phosphatidylinositol.qmd" style="text-decoration: none;">
+        <button style="background-color: rgb(231, 109, 104); color: white; font-size: 20px; padding: 15px 30px; border: none; border-radius: 8px; margin: 10px; cursor: pointer;">
+            Phosphatidylinositol (PI)
+        </button>
+    </a>
+
+    <br>
+
     <a href="LipidProbe/PhosphatidylinositolBisphosphate.qmd" style="text-decoration: none;">
-        <button style="background-color: #a86532; color: white; font-size: 20px; padding: 15px 30px; border: none; border-radius: 8px; margin: 10px; cursor: pointer;">
+        <button style="background-color: #f14334; color: white; font-size: 20px; padding: 15px 30px; border: none; border-radius: 8px; margin: 10px; cursor: pointer;">
             PI(4,5)P<sub>2</sub>
@@
     <a href="LipidProbe/PhosphatidylinositolTrisphosphate.qmd" style="text-decoration: none;">
-        <button style="background-color: #8732a8; color: white; font-size: 20px; padding: 15px 30px; border: none; border-radius: 8px; margin: 10px; cursor: pointer;">
+        <button style="background-color:rgb(223, 21, 21); color: white; font-size: 20px; padding: 15px 30px; border: none; border-radius: 8px; margin: 10px; cursor: pointer;">
             PI(3,4,5)P<sub>3</sub>
@@
     <a href="LipidProbe/Diacylglycerol.qmd" style="text-decoration: none;">
-        <button style="background-color: #3277a8; color: white; font-size: 20px; padding: 15px 30px; border: none; border-radius: 8px; margin: 10px; cursor: pointer;">
+        <button style="background-color: #2ecc71; color: white; font-size: 20px; padding: 15px 30px; border: none; border-radius: 8px; margin: 10px; cursor: pointer;">
             Diacylglycerol
@@
     <a href="LipidProbe/Sphinganine.qmd" style="text-decoration: none;">
-        <button style="background-color: #2ecc71; color: white; font-size: 20px; padding: 15px 30px; border: none; border-radius: 8px; margin: 10px; cursor: pointer;">
+        <button style="background-color:rgb(101, 46, 204); color: white; font-size: 20px; padding: 15px 30px; border: none; border-radius: 8px; margin: 10px; cursor: pointer;">
             Sphinganine
@@
     <a href="LipidProbe/Sphingosine.qmd" style="text-decoration: none;">
-        <button style="background-color: #eba434; color: white; font-size: 20px; padding: 15px 30px; border: none; border-radius: 8px; margin: 10px; cursor: pointer;">
+        <button style="background-color:rgb(202, 52, 235); color: white; font-size: 20px; padding: 15px 30px; border: none; border-radius: 8px; margin: 10px; cursor: pointer;">
             Sphingosine
@@
 	<a href="LipidProbe/8-3_FattyAcid.qmd" style="text-decoration: none;">
-        <button style="background-color: #ba34eb; color: white; font-size: 20px; padding: 15px 30px; border: none; border-radius: 8px; margin: 10px; cursor: pointer;">
+        <button style="background-color:rgb(235, 177, 52); color: white; font-size: 20px; padding: 15px 30px; border: none; border-radius: 8px; margin: 10px; cursor: pointer;">
             8-3 Fatty Acid
@@
     <a href="LipidProbe/1-10_FattyAcid.qmd" style="text-decoration: none;">
-        <button style="background-color: #a83260; color: white; font-size: 20px; padding: 15px 30px; border: none; border-radius: 8px; margin: 10px; cursor: pointer;">
+        <button style="background-color:rgb(237, 111, 38); color: white; font-size: 20px; padding: 15px 30px; border: none; border-radius: 8px; margin: 10px; cursor: pointer;">
             1-10 Fatty Acid

### 2025-03-15 IndividualStudies/template_study.qmd
Added template files for the individual studies

--- 2025-03-07 IndividualStudies/SF_2024.qmd
@@
 ---
-title: "Farley et al. 2024"
-subtitle: "Trifunctional Sphinganine: A New Tool to Dissect Sphingolipid Function"
+title: "Template based on Farley et al. 2024"
+subtitle: "Study title"
 format: 
@@
 ---
+
+<!-- CHANGE THIS TO POINT TO THE NEW DATASET -->
 
@@
 
-# Opening the datatable for this page IN FINAL RENDER
+# Opening the datatable for this page - CHANGE!
 data <- readr::read_csv(paste0(here(), "/IndividualStudies/DataTables/SF_ACS-Chem-Bio_2024_download.csv"))
@@
 
-{{< include /StudyInformation_includes/SF_2024_A_include.qmd >}}
+{{< include /StudyInformation_includes/template_include.qmd >}}
 
@@
 
+<!-- CHANGE THESE  TO NEW VERSION MADE VIA FUNCTIONS IN Resources/Run_GO_DOTplots.R -->
 #### Cell Compartment
@@
 
+<!-- CHANGE THIS TO POINT TO THE RIGHT DATA FILE -->
+
 {{< downloadthis DataTables/SF_ACS-Chem-Bio_2024_download.csv dname="SF_ACS-Chem-Bio_2024">}}

### 2025-03-15 LipidProbe/template_lipidprobe.qmd
Added template files for the individual studies

--- 2025-03-13 LipidProbe/Sphingosine.qmd
@@
 ---
-title: "Trifunctional Sphingosine"
+title: "Lipid Probe Template"
 format: html
@@
 ::: {layout="[[100], [100]]"}
-![Native Sphingosine.](/LipidProbe/Structures/Sphingosine.png)
+![(A) Native structure.]()
 
-![Trifunctional Sphingosine.](/LipidProbe/Structures/TF_Sphingosine.png)
+![(B) Trifunctional structure.]()
 
@@
 
-### Cell background: Huh7
+### Cell background:
 
@@
 
-{{< include /StudyInformation_includes/SF_2024_A_include.qmd >}}
+{{< include StudyInformation_includes/template_include.qmd >}}
 
@@
 
-<!-- Data wrangling to make the plots -->
+<!-- CHANGE THIS TO POINT TO THE NEW DATASET -->
 
@@
 
-#  SF_2024_data <- readr::read_csv("LipidProbe/DataSets/SF_ACS-Chem-Bio_2024_download.csv") |>
-#  	filter(LipidProbe == "Sph")
-
-# 	write.csv(SF_2024_data, "LipidProbe/DataSets/Sph_Huh7_SF_2024.csv")
-
 # Opening the datatable for this page
-data <- readr::read_csv(paste0(here(), "/LipidProbe/DataSets/Sph_Huh7_SF_2024.csv")) |>
-	filter(LipidProbe == "Sph")
+data <- readr::read_csv(paste0(here(), "/LipidProbe/DataSets/Sph_Huh7_SF_2024.csv"))
 
@@
 
+<!-- CHANGE THIS TO THE CORRECT DOT PLOT, RENDERED VIA FUNCTIONS CALLED IN Resources/Run_GO_DOTplots.R -->
 <iframe src="/LipidProbe/GO_plots/Sph_SF_2024_CC-DOTplot.html" width="100%" height="500px"></iframe>
@@
 
+<!-- CHANGE THESE IF THE MF AND BP DOT PLOTS WORK PROPERLY -->
 (No MF pathways identified among enriched hits and candidates.)
@@
 
+<!-- CHANGE THIS TO THE CORRECT NEW DATASET -->
 {{< downloadthis DataSets/Sph_Huh7_SF_2024.csv dname="Sph_Huh7_SF_ACS-Chem-Bio_download">}}

### 2025-03-24 IndividualStudies/DH_2017.qmd
adding a draft of the NAPE page

@@
 
-Depicted below are the average PSM count for two replicates each of UV-irradiated samples treated with trifunctionalized Sph, DAG, and FA.
-
 :::{.border}
@@
 ```{r Making Heat Map, echo=FALSE, fig.height=10, warning=FALSE}
+#| fig-cap: "Heat map depicts the average PSM count for two replicates each of UV-irradiated samples treated with trifunctionalized Sph, DAG, and FA. Color denotes the "
 
@@
 ```{r Making Venn Diagram, echo=FALSE, warning=FALSE, width = 8}
+#| fig-cap: "A Venn diagram depicts the overlapping identification of proteins between the three lipid probes.
+There are 41 proteins uniquely identified after enrichment with tf-Sph, 130 proteins uniquely identified after enrichment with tf-DAG, and no proteins uniquely identified to tf-8:3-FA."
 
@@
 <iframe src="/IndividualStudies/GO_plots/DH_2017_BP_DOTPLOT.html" width="100%" height="500px"></iframe>
+
 :::

### 2025-03-24 LipidProbe/N-Acylphosphatidylethanolamine.qmd
adding a draft of the NAPE page

---
title: "Bifunctional N-Acylphosphatidylethanolamine"
prefer-html: true
format:
  html: default
callout-icon: false
---

## Structure

:::{.border}
::: {layout="[[-0.01,99.99], [100]]"}
<!-- ![(A) Native N-Acylphosphatidylethanolamine.](/LipidProbe/Structures/PE.png) -->

![(B) Bifunctional N-Acylphosphatidylethanolamine.](/LipidProbe/Structures/BF_NAPE.png)

:::
:::

## Protein Interactome

```{r setup_and_data_wrangling, echo=FALSE, warning=FALSE, include=FALSE}
library(here)

## Opening the source file for the ggplot custom theme
source(paste0(here::here(), "/Resources/ggplot_styles.R"))

data <- readr::read_csv(paste0(here::here(), "/IndividualStudies/DataTables/DCC_2025_ChemrXiv_FilteredDataset.csv")) |> 
  group_by(gene_name) |>
  summarise(logFC = mean(logFC),
            pvalue = mean(pvalue),
            numReplicates = n()) |>
  arrange(-(numReplicates)) |>
  mutate(LipidProbe = "BF-NAPE",
         hit_annotation = case_when(numReplicates == 1 ~ "no hit",
                                    numReplicates == 2 ~ "enriched candidate",
                                    numReplicates == 3 ~ "enriched hit")) |>
  glimpse()

# Organize the hit annotations as factors
data$hit_annotation <- factor(pull(data, hit_annotation), levels = c("enriched hit", "hit", "enriched candidate", "candidate", "no hit", "NA"), ordered = TRUE)

```

::::{.callout-tip}
### Cell background: HeLa

::: {.callout-note collapse="true"}

{{< include /StudyInformation_includes/DCC_2025_include.qmd >}}

:::

#### Data visualization

::: {.panel-tabset}

##### Volcano Plot

```{r NAPE_volcano, echo=FALSE, warning=FALSE}
#| fig-cap: "Volcano plots depict the relative enrichment of each protein versus non-crosslinked control (x-axis) and the statistical significance of each protein following a Student's t-test (y-axis, -log10 transformed). Black proteins are identified in only one replicate, Purple enriched candidates are defined as proteins identified in two replicates, and Orange enriched hits are defined as proteins identified in all three replicates)."

VolcanoPlotStandardized(data)

```

##### Ranked Order Plot

```{r NAPE_RO, echo=FALSE, warning=FALSE}
#| fig-cap: "Ranked-order plots depict the relative enrichment of each protein versus non-crosslinked control (y-axis) from lowest to highest. Black proteins are identified in only one replicate, Purple enriched candidates are defined as proteins identified in two replicates, and Orange enriched hits are defined as proteins identified in all three replicates)."

RankedOrderPlotStandard(data)
```

##### Venn Diagram
```{r Venn_wrangling, include=FALSE, warning=FALSE}

###### Wrangling for the Venn Diagram ######
# Read the dataset
VennData <- readr::read_csv(paste0(here::here(), "/IndividualStudies/DataTables/DCC_2025_ChemrXiv_FilteredDataset.csv"))

# Separates out each of the genesets, then forces them back together in a vectorized list.
A_proteins <- VennData |>
  filter(Replicate == "A") |>
  dplyr::select(gene_name)

B_proteins <- VennData |>
  filter(Replicate == "B") |>
  dplyr::select(gene_name)

C_proteins <- VennData |>
  filter(Replicate == "C") |>
  dplyr::select(gene_name)

VennList <- list("Replicate A" = as.list(A_proteins$gene_name), "Replicate B" = as.list(B_proteins$gene_name), "Replicate C" = as.list(C_proteins$gene_name))
```

```{r NAPE_Venn, echo=FALSE, warning=FALSE}
#| fig-cap: "A Venn diagram depicts the overlapping identification of proteins between the three replicates. There are 88 proteins enriched uniquely in Replicate A, 75 proteins enriched uniquely in Replicate B, and 64 proteins enriched uniquely in Replicate C."

ggvenn <- ggvenn(VennList,
                      show_percentage = FALSE,
                      show_elements = FALSE,
                      fill_color = c("orange", "purple", "blue")) +
        labs(x = "", y = "") +
        theme_minimal()

ggvenn

```

:::

<!-- 
## Gene Ontology Analysis

**In beta: GO analysis still under development**

:::::{.border}
::::{#fig-PE_GOplots}
::: {.panel-tabset}

#### Cell Compartment

(No CC pathways identified among enriched hits and candidates.)

#### Molecular Function

(No MF pathways identified among enriched hits and candidates.)

#### Biological Process

(No BP pathways identified among enriched hits and candidates.)

:::

GO Dot plots display the enrichment of GO terms among the proteins enriched to the probe. For these analyses, only proteins categorized as "enriched candidates" and "enriched hits" were subject to GO analysis. The Cell Compartment analysis assesses whether the list of enriched proteins contains a statistically significant number of proteins in the same cellular region; appropriately, the Molecular Function and Biological Process analyses does the same for molecular function and biological process, respectively. [Click here for more information about Gene Ontology analysis.](/Background/DataAnalysisAndStatistics.qmd#gene-ontology-overview)

::::
::::: -->

#### Data exploration and download

Check the boxes below to filter the dataset by which lipid probe was used in the pulldown and by significance thresholds.

:::{.border}
```{r NAPE_DataTable, echo=FALSE, warning=FALSE}

# Here is the code to make the filterable lists shown in the crosstalk table below

data <- data |>
  dplyr::select(gene_name, LipidProbe, hit_annotation, logFC, pvalue, numReplicates) |>
  mutate(logFC = signif(logFC, digits=3),
          pvalue = signif(pvalue, digits=3)) |>
  arrange(-logFC) |>
  arrange(hit_annotation)

## Creates a reactive dataframe
data_reactive <- crosstalk::SharedData$new(data)

htmltools::tags$div(
  class = "filter-container",
  filter_checkbox(id = "LipidProbe",
                  label = "Lipid probe in pulldown:", 
                  sharedData = data_reactive,
                  group = ~LipidProbe),
  filter_checkbox(id = "hit_annotation",
                  label = "Enrichment criteria:", 
                  sharedData = data_reactive,
                  group = ~hit_annotation)
)

## Displays the reactive dataframe
datatable(data_reactive, 
          options = list(pageLength = 15),
                         colnames = c("Gene Name", "Lipid Probe", "Hit Annotation", "LogFC", "p value", "FDR"),
                         rownames=FALSE)

```
:::

<br>

{{< downloadthis DataSets/DCC_2025_ChemrXiv_FilteredDataset.csv dname="DCC_2025_ChemrXiv_FilteredDataset">}}

::::

### 2025-03-24 StudyInformation_includes/AT_2025_include.qmd
adding a draft of the NAPE page

@@
 
-<a href="/LipidProbe/PhosphatidicAcid.qmd" class="hover-preview">Phosphatidic Acid</a>
+<a href="/LipidProbe/PhosphatidicAcid.qmd" class="hover-preview">Trifunctional Phosphatidic Acid</a>
 <span class="hover-image">
@@
 
-<a href="/LipidProbe/Phosphatidylethanolamine.qmd" class="hover-preview">Phosphatidylethanolamine</a>
+<a href="/LipidProbe/Phosphatidylethanolamine.qmd" class="hover-preview">Trifunctional Phosphatidylethanolamine</a>
 <span class="hover-image">

### 2025-03-24 StudyInformation_includes/DCC_2025_include.qmd
adding a draft of the NAPE page

## Study details

#### Authors

#### Journal
ChemR&Chi;iv

<https://doi.org/10.26434/chemrxiv-2025-j8nqz>{target="_blank"}

#### Abstract
Most eukaryotic membranes comprise phospholipids bearing two hydrophobic tails, but N-
acylphosphatidylethanolamine (NAPE) stands out as a long-known but poorly understood
phospholipid with three hydrophobic groups. What little attention that NAPE has received has been
devoted to understanding its metabolic functions as a precursor to N-acylethanolamines, bioactive
lipids that act as endocannabinoids. Yet, levels of NAPE increase during myocardial infarction and
ischemia, suggesting potential signaling roles for this lipid. Here, we exploit photoaffinity labeling
(PAL) to identify NAPE-interacting proteins and elucidate signaling functions of NAPE. By
positioning diazirine and alkyne groups in metabolically distinct regions of the NAPE molecule,
we ensured that our PAL probe reported on interactions of NAPE and not NAE. Our studies
identified several NAPE interactors, including two single-pass transmembrane proteins,
CD147/Basigin and CD44, both of which serve as chaperones for monocarboxylate transporters
(MCTs) from the SLC16A family that mediate lactate flux across the plasma membrane.
Functional studies revealed that NAPE stimulates lactate efflux by MCTs dependent upon CD147
and CD44, establishing NAPE as a bona fide signaling lipid and pointing to potential physiological
roles in metabolic and energy homeostasis that may be pathologically relevant in ischemia.

#### Lipid probes utilized

<a href="/LipidProbe/N-Acylphosphatidylethanolamine.qmd" class="hover-preview">Bifunctional NAPE</a>
<span class="hover-image">
  <img src="/LipidProbe/Structures/BF_NAPE.png" alt="Bifunctional NAPE" />
</span>

#### Cell line analyzed

[HeLa](https://www.atcc.org/products/ccl-2){target="_blank"}

#### Uncaging & Crosslinking timeline

| Lipid Probe | Uptake time | Interaction time | Crosslinking time |
|:-------|:------:|:------:|:------:|:------:|
| LEI-401    | 30 min  | 60 min | 30 min  |

#### Mass spectrometry quantification method

SILAC

::: {.callout-note collapse="true"}
<!-- ##### ProteomeXchange details

**ProteomeXchange title:** Trifunctional lipid derivatives: PE’s mi-tochondrial interactome

**ProteomeXchange accession:** PXD059960

**PubMed ID:** Not applicable

**Publication DOI:** 10.1039/D4CC03599B

**Project Webpage:** http://www.ebi.ac.uk/pride/archive/projects/PXD059960

**FTP Download:** https://ftp.pride.ebi.ac.uk/pride/data/archive/2025/01/PXD059960 -->
:::

#### Additional sample preparation <span class="help-symbol" title="e.g. sub-cellular fractionation, depletion, etc.">?</span>

### 2025-03-24 StudyInformation_includes/DH_2017_include.qmd
Trying to fix the dotplot framing on mobile, not much luck yet
adding a draft of the NAPE page

@@
 
-[Sphingosine](/LipidProbe/Sphingosine.qmd)
+[Trifunctional Sphingosine](/LipidProbe/Sphingosine.qmd)
 
-[Diacylglycerol](/LipidProbe/Diacylglycerol.qmd)
+[Trifunctional Diacylglycerol](/LipidProbe/Diacylglycerol.qmd)
 
-[8-3 Fatty acid](/LipidProbe/8-3_FattyAcid.qmd)
+[Trifunctional 8-3 Fatty acid](/LipidProbe/8-3_FattyAcid.qmd)
 
@@
 
+#### Uncaging & Crosslinking timeline
+
+| Lipid Probe | Uptake time | Uncaging time | Interaction time | Crosslinking time |
+|:-------|:------:|:------:|:------:|:------:|
+| Sph |  5 min | 2.5 min  | 0 min | 2.5 min  |
+| DAG |  15 min | 2.5 min  | 0 min | 2.5 min  |
+| 8-3 FA |  15 min | 2.5 min  | 0 min | 2.5 min  |
+
 #### Mass spectrometry quantification method

### 2025-03-24 Resources/Run_GO_DOTplots.R

@@ -140,3 +140,28 @@ MF_enrichment_plots(AT_2025, "dot", "PE-PA_AT_2025_MF-DOTplot")
 
 BP_enrichment_plots(AT_2025, "dot", "PE-PA_AT_2025_BP-DOTplot")
 # BP_enrichment_plots(AT_2025, "cnet", "PE-PA_AT_2025_BP-CNETplot")
+
+
+# DCC_2025
+
+/Users/gaelenguzman/LipidInteractomics_Website_local/LipidInteractomics_Website/IndividualStudies/DataTables/DCC_2025_ChemrXiv_FilteredDataset.csv
+
+DCC_2025 <- readr::read_csv(paste0(here(), "/IndividualStudies/DataTables/DCC_2025_ChemrXiv_FilteredDataset.csv")) |>
+  group_by(gene_name) |>
+  summarise(logFC = mean(logFC),
+            pvalue = mean(pvalue),
+            numReplicates = n()) |>
+  arrange(-(numReplicates)) |>
+  mutate(LipidProbe = "BF-NAPE",
+         hit_annotation = case_when(numReplicates == 1 ~ "no hit",
+                                    numReplicates == 2 ~ "enriched candidate",
+                                    numReplicates == 3 ~ "enriched hit"))
+
+CC_enrichment_plots(DCC_2025, "dot", "NAPE_DCC_2025_CC-DOTplot")
+# CC_enrichment_plots(AT_2025, "cnet", "PE-PA_AT_2025_CC-CNETplot")
+
+MF_enrichment_plots(DCC_2025, "dot", "NAPE_DCC_2025_MF-DOTplot")
+# MF_enrichment_plots(AT_2025, "cnet", "PE-PA_AT_2025_MF-CNETplot")
+
+BP_enrichment_plots(DCC_2025, "dot", "NAPE_DCC_2025_BP-DOTplot")
+# BP_enrichment_plots(AT_2025, "cnet", "PE-PA_AT_2025_BP-CNETplot")

### 2025-03-25 IndividualStudies/DCC_2025.qmd
putting NAPE on the index

---
title: "Chiu et al. 2025"
subtitle: "Photoaffinity Labeling Reveals a Role for the Unusual Triply Acylated Phospholipid N-Acylphosphatidylethanolamine in Lactate Homeostasis"
format: 
  html:
    embed-resources: false
standalone: false
---

::: {.callout-note collapse="true"}

{{< include /StudyInformation_includes/DCC_2025_include.qmd >}}

:::

## Data visualization

```{r setup_and_data_wrangling, echo=FALSE, warning=FALSE, include=FALSE}
library(here)

## Opening the source file for the ggplot custom theme
source(paste0(here::here(), "/Resources/ggplot_styles.R"))

data <- readr::read_csv(paste0(here::here(), "/IndividualStudies/DataTables/DCC_2025_ChemrXiv_FullDataset.csv")) |> 
  group_by(gene_name) |>
  filter(gene_name != "", ratio_MvsL != "") |>
  summarise(logFC = mean(log2(ratio_MvsL)),
            pvalue = mean(pvalue),
            numReplicates = n(),
            AveExpr = log10(mean(mean(L_abundance), mean(M_abundance)))) |>
  arrange(-logFC) |>
  mutate(LipidProbe = "BF-NAPE",
         hit_annotation = case_when(.default = "no hit",
                                    logFC >= 0.5849625 & pvalue <= 0.01 & numReplicates == 2 ~ "enriched candidate",
                                    logFC >= 0.5849625 & pvalue <= 0.01 & numReplicates == 3 ~ "enriched hit")) |>
  glimpse()

median_logFC <- median(data$logFC)

data$logFC <- data$logFC - median_logFC

# Organize the hit annotations as factors
data$hit_annotation <- factor(pull(data, hit_annotation), levels = c("enriched hit", "hit", "enriched candidate", "candidate", "no hit", "NA"), ordered = TRUE)

```

::::{.border}
::: {.panel-tabset}

#### Volcano plots

```{r, echo=FALSE, warning=FALSE}
#| fig-cap: "Volcano plots depict the relative enrichment of each protein versus non-crosslinked control (x-axis) and the statistical significance of each protein following a Student's t-test (y-axis, -log10 transformed). Black proteins are identified in only one replicate, Purple enriched candidates are defined as proteins identified in two replicates & fold-change > 1.5 (logFC 0.585) & pvalue < 0.01, and Orange enriched hits are defined as proteins identified in all three replicates & fold-change > 1.5 (logFC 0.585) & pvalue < 0.01)."

VolcanoPlotStandardized(data)

```

#### Ranked-order plots

```{r, echo=FALSE, warning=FALSE}
#| fig-cap: "Ranked-order plots depict the relative enrichment of each protein versus non-crosslinked control (y-axis) from lowest to highest. Black proteins are identified in only one replicate, Purple enriched candidates are defined as proteins identified in two replicates & fold-change > 1.5 (logFC 0.585) & pvalue < 0.01, and Orange enriched hits are defined as proteins identified in all three replicates & fold-change > 1.5 (logFC 0.585) & pvalue < 0.01)."

RankedOrderPlotStandard(data)
```

#### MA Plots

```{r, echo=FALSE, warning=FALSE}
#| fig-cap: "MA plots depict the average abundance of each protein in the crosslinked and uncrosslinked conditions (x-axis) versus the log2-transformed fold-change between the crosslinked and uncrosslinked conditions (y-axis). Black proteins are identified in only one replicate, Purple enriched candidates are defined as proteins identified in two replicates & fold-change > 1.5 (logFC 0.585) & pvalue < 0.01, and Orange enriched hits are defined as proteins identified in all three replicates & fold-change > 1.5 (logFC 0.585) & pvalue < 0.01)."

MAStandard(data)

```

#### Venn Diagram

```{r Venn_wrangling, include=FALSE, warning=FALSE}

###### Wrangling for the Venn Diagram ######
# Read the dataset
VennData <- readr::read_csv(paste0(here::here(), "/LipidProbe/DataSets/DCC_2025_ChemrXiv_FilteredDataset.csv"))

# Separates out each of the genesets, then forces them back together in a vectorized list.
A_proteins <- VennData |>
  filter(Replicate == "A") |>
  dplyr::select(gene_name)

B_proteins <- VennData |>
  filter(Replicate == "B") |>
  dplyr::select(gene_name)

C_proteins <- VennData |>
  filter(Replicate == "C") |>
  dplyr::select(gene_name)

VennList <- list("Replicate A" = as.list(A_proteins$gene_name), "Replicate B" = as.list(B_proteins$gene_name), "Replicate C" = as.list(C_proteins$gene_name))
```

```{r NAPE_Venn, echo=FALSE, warning=FALSE}
#| fig-cap: "A Venn diagram depicts the overlapping identification of proteins between the three replicates. The full dataset was filtered to only include proteins with fold-change > 1.5 (logFC > 0.585) and p-value < 0.01 There are 88 proteins enriched uniquely in Replicate A, 75 proteins enriched uniquely in Replicate B, and 64 proteins enriched uniquely in Replicate C."

ggvenn <- ggvenn(VennList,
                      show_percentage = FALSE,
                      show_elements = FALSE,
                      fill_color = c("orange", "purple", "blue")) +
        labs(x = "", y = "") +
        theme_minimal()

ggvenn

```

:::
::::

## Data exploration

:::{.border}
```{r NAPE_DataTable, echo=FALSE, warning=FALSE}

# Here is the code to make the filterable lists shown in the crosstalk table below

data <- data |>
  dplyr::select(gene_name, LipidProbe, hit_annotation, logFC, pvalue, numReplicates) |>
  mutate(logFC = signif(logFC, digits=3),
          pvalue = signif(pvalue, digits=3)) |>
  arrange(-logFC) |>
  arrange(hit_annotation)

## Creates a reactive dataframe
data_reactive <- crosstalk::SharedData$new(data)

htmltools::tags$div(
  class = "filter-container",
  filter_checkbox(id = "LipidProbe",
                  label = "Lipid probe in pulldown:", 
                  sharedData = data_reactive,
                  group = ~LipidProbe),
  filter_checkbox(id = "hit_annotation",
                  label = "Enrichment criteria:", 
                  sharedData = data_reactive,
                  group = ~hit_annotation)
)

## Displays the reactive dataframe
datatable(data_reactive, 
          caption = "This datatable contains all the data plotted above. Check the boxes below to filter the dataset by which lipid probe was used in the pulldown and by significance thresholds. logFC ratios are median normalized. \"Num Replicate IDs\" denotes the number of replicates in which the protein was identified. As above, \"enriched hit\" denotes proteins identified in all three replicates & fold-change > 1.5 (logFC 0.585) & pvalue < 0.01. \"enriched candidates\" are proteins identified in two replicates & fold-change > 1.5 (logFC 0.585) & pvalue < 0.01.",
          options = list(pageLength = 15),
                         colnames = c("Gene Name", "Lipid Probe", "Hit Annotation", "LogFC", "p value", "Num Replicate IDs"),
                         rownames=FALSE)

```

:::

<br>

```{r save_csv, include=FALSE, echo=FALSE, warning=FALSE}

# write_csv(data, paste0(here(), "/LipidProbe/DataSets/DCC_2025_ChemrXiv_Download.csv"))

```

## Data download

{{< downloadthis DataTables/DCC_2025_ChemrXiv_Download.csv dname="DCC_2025_ChemrXiv_Download">}}

### 2025-03-25 IndividualStudies/SF_2024.qmd
putting NAPE on the index

@@
 
-## Data exploration and download
+## Data exploration
 
@@
 datatable(data_reactive, 
+          caption = "'No hit' proteins are unenriched or depleted in the presence of probe, 'enriched candidates' are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and 'enriched hits' are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV",
           options = list(pageLength = 15),

### 2025-03-25 LipidProbe/N-Acylphosphatidylethanolamine.qmd
putting NAPE on the index

@@
 title: "Bifunctional N-Acylphosphatidylethanolamine"
+subtitle: "NAPE"
 prefer-html: true
@@
 
-data <- readr::read_csv(paste0(here::here(), "/IndividualStudies/DataTables/DCC_2025_ChemrXiv_FilteredDataset.csv")) |> 
+data <- readr::read_csv(paste0(here::here(), "/LipidProbe/DataSets/DCC_2025_ChemrXiv_FullDataset.csv")) |> 
   group_by(gene_name) |>
-  summarise(logFC = mean(logFC),
+  filter(gene_name != "" & ratio_MvsL != "" & L_abundance != "" & M_abundance != "") |>
+  summarise(logFC = mean(log2(ratio_MvsL)),
             pvalue = mean(pvalue),
-            numReplicates = n()) |>
-  arrange(-(numReplicates)) |>
+            numReplicates = n(),
+            AveExpr = log10(mean(mean(L_abundance), mean(M_abundance)))) |>
+  arrange(logFC) |>
   mutate(LipidProbe = "BF-NAPE",
-         hit_annotation = case_when(numReplicates == 1 ~ "no hit",
-                                    numReplicates == 2 ~ "enriched candidate",
-                                    numReplicates == 3 ~ "enriched hit")) |>
+         hit_annotation = case_when(.default = "no hit",
+                                    logFC >= 0.5849625 & pvalue <= 0.01 & numReplicates == 2 ~ "enriched candidate",
+                                    logFC >= 0.5849625 & pvalue <= 0.01 & numReplicates == 3 ~ "enriched hit")) |>
   glimpse()
+
+median_logFC <- median(data$logFC)
+
+data$logFC <- data$logFC - median_logFC
 
@@
 
+::::{.border}
 ::: {.panel-tabset}
@@
 ```{r NAPE_volcano, echo=FALSE, warning=FALSE}
-#| fig-cap: "Volcano plots depict the relative enrichment of each protein versus non-crosslinked control (x-axis) and the statistical significance of each protein following a Student's t-test (y-axis, -log10 transformed).
-Black proteins are identified in only one replicate, Purple enriched candidates are defined as proteins identified in two replicates, and Orange enriched hits are defined as proteins identified in all three replicates)."
+#| fig-cap: "Volcano plots depict the relative enrichment of each protein versus non-crosslinked control (x-axis, log2 transformed and median normalized) and the statistical significance of each protein following a Student's t-test (y-axis, -log10 transformed).
+Black proteins are identified in only one replicate, Purple enriched candidates are defined as proteins identified in two replicates & fold-change > 1.5 (logFC 0.585) & pvalue < 0.01, and Orange enriched hits are defined as proteins identified in all three replicates & fold-change > 1.5 (logFC 0.585) & pvalue < 0.01)."
 
@@
 #| fig-cap: "Ranked-order plots depict the relative enrichment of each protein versus non-crosslinked control (y-axis) from lowest to highest.
-Black proteins are identified in only one replicate, Purple enriched candidates are defined as proteins identified in two replicates, and Orange enriched hits are defined as proteins identified in all three replicates)."
+Black proteins are identified in only one replicate, Purple enriched candidates are defined as proteins identified in two replicates & fold-change > 1.5 (logFC 0.585) & pvalue < 0.01, and Orange enriched hits are defined as proteins identified in all three replicates & fold-change > 1.5 (logFC 0.585) & pvalue < 0.01)."
 
 RankedOrderPlotStandard(data)
+```
+
+##### MA Plot
+
+```{r, NAPE_MA, echo=FALSE, warning=FALSE}
+#| fig-cap: "MA plots depict the average abundance of each protein in the crosslinked and uncrosslinked conditions (x-axis) versus the log2-transformed fold-change between the crosslinked and uncrosslinked conditions (y-axis).
+Black proteins are identified in only one replicate, Purple enriched candidates are defined as proteins identified in two replicates & fold-change > 1.5 (logFC 0.585) & pvalue < 0.01, and Orange enriched hits are defined as proteins identified in all three replicates & fold-change > 1.5 (logFC 0.585) & pvalue < 0.01)."
+
+MAStandard(data)
 ```
@@
 # Read the dataset
-VennData <- readr::read_csv(paste0(here::here(), "/IndividualStudies/DataTables/DCC_2025_ChemrXiv_FilteredDataset.csv"))
+VennData <- readr::read_csv(paste0(here::here(), "/LipidProbe/DataSets/DCC_2025_ChemrXiv_FilteredDataset.csv"))
 
@@
 :::
-
-<!-- 
-## Gene Ontology Analysis
-
-**In beta: GO analysis still under development**
-
-:::::{.border}
-::::{#fig-PE_GOplots}
-::: {.panel-tabset}
-
-#### Cell Compartment
-
-(No CC pathways identified among enriched hits and candidates.)
-
-#### Molecular Function
-
-(No MF pathways identified among enriched hits and candidates.)
-
-#### Biological Process
-
-(No BP pathways identified among enriched hits and candidates.)
-
-:::
-
-GO Dot plots display the enrichment of GO terms among the proteins enriched to the probe.
-For these analyses, only proteins categorized as "enriched candidates" and "enriched hits" were subject to GO analysis.
-The Cell Compartment analysis assesses whether the list of enriched proteins contains a statistically significant number of proteins in the same cellular region; appropriately, the Molecular Function and Biological Process analyses does the same for molecular function and biological process, respectively.
-[Click here for more information about Gene Ontology analysis.](/Background/DataAnalysisAndStatistics.qmd#gene-ontology-overview)
-
 ::::
-::::: -->
 
 #### Data exploration and download
-
-Check the boxes below to filter the dataset by which lipid probe was used in the pulldown and by significance thresholds.
 
@@
 datatable(data_reactive, 
+          caption = "This datatable contains all the data plotted above.
+Check the boxes below to filter the dataset by which lipid probe was used in the pulldown and by significance thresholds.
+logFC ratios are median normalized.
+\"Num Replicate IDs\" denotes the number of replicates in which the protein was identified.
+As above, \"enriched hit\" denotes proteins identified in all three replicates & fold-change > 1.5 (logFC 0.585) & pvalue < 0.01.
+\"enriched candidates\" are proteins identified in two replicates & fold-change > 1.5 (logFC 0.585) & pvalue < 0.01.",
           options = list(pageLength = 15),
-                         colnames = c("Gene Name", "Lipid Probe", "Hit Annotation", "LogFC", "p value", "FDR"),
+                         colnames = c("Gene Name", "Lipid Probe", "Hit Annotation", "LogFC", "p value", "Num Replicate IDs"),
                          rownames=FALSE)
@@
 ```
+
 :::
@@
 
-{{< downloadthis DataSets/DCC_2025_ChemrXiv_FilteredDataset.csv dname="DCC_2025_ChemrXiv_FilteredDataset">}}
+```{r save_csv, include=FALSE, echo=FALSE, warning=FALSE}
+
+# write_csv(data, paste0(here(), "/LipidProbe/DataSets/DCC_2025_ChemrXiv_Download.csv"))
+
+```
+
+{{< downloadthis DataSets/DCC_2025_ChemrXiv_Download.csv dname="DCC_2025_ChemrXiv_Download">}}
 

### 2025-03-25 StudyInformation_includes/DCC_2025_include.qmd
putting NAPE on the index

@@
 #### Authors
+
+Din-Chi Chiu, Hening Lin, Jeremy M. Baskin
 
@@
 
-::: {.callout-note collapse="true"}
-<!-- ##### ProteomeXchange details
-
-**ProteomeXchange title:** Trifunctional lipid derivatives: PE’s mi-tochondrial interactome
-
-**ProteomeXchange accession:** PXD059960
-
-**PubMed ID:** Not applicable
-
-**Publication DOI:** 10.1039/D4CC03599B
-
-**Project Webpage:** http://www.ebi.ac.uk/pride/archive/projects/PXD059960
-
-**FTP Download:** https://ftp.pride.ebi.ac.uk/pride/data/archive/2025/01/PXD059960 -->
-:::
-
 #### Additional sample preparation <span class="help-symbol" title="e.g. sub-cellular fractionation, depletion, etc.">?</span>

### 2025-03-25 index.qmd
putting NAPE on the index

@@
           Phosphatidylethanolamine
+      </button>
+  </a>
+
+   <a href="LipidProbe/N-Acylphosphatidylethanolamine.qmd" style="text-decoration: none;">
+      <button style="background-color:rgb(41, 188, 204); color: white; font-size: 20px; padding: 15px 30px; border: none; border-radius: 8px; margin: 10px; cursor: pointer;">
+          N-Acylphosphatidylethanolamine
       </button>

### 2025-03-25 Resources/ggplot_styles.R

@@ -88,7 +88,7 @@ MAStandard <- function(data) {
         geom_point(aes(text = paste0("Gene name: ", gene_name, "\n",
                                     "LogFC: ", logFC, "\n",
                                     "p-value: ", pvalue, "\n",
-                                    "AveExper: ", AveExpr, "\n"))) +
+                                    "AveExpr: ", AveExpr, "\n"))) +
         geom_hline(yintercept = 0, linetype = 2) +
         geom_vline(xintercept = 0, linetype = 2) +
         scale_x_continuous(limits = c(0.9 * min(abs(data$AveExpr)), 1.1 * max(abs(data$AveExpr))))+

### 2025-03-25 ShinyApps/LipidInteractomics_ShinyApp/app.R

@@ -303,3 +303,4 @@ ProbeVSProbePlotter <- function(data, probe1Name, probe2Name) {
 
 
 shinyApp(ui, server)
+

### 2025-03-25 index.qmd
adding index listing to study overview

--- 2025-03-13 index.qmd
@@
           Phosphatidylethanolamine
+      </button>
+  </a>
+
+   <a href="LipidProbe/N-Acylphosphatidylethanolamine.qmd" style="text-decoration: none;">
+      <button style="background-color:rgb(41, 188, 204); color: white; font-size: 20px; padding: 15px 30px; border: none; border-radius: 8px; margin: 10px; cursor: pointer;">
+          N-Acylphosphatidylethanolamine (NAPE)
       </button>

### 2025-03-25 ShinyApps/LipidInteractomics_ShinyApp/app.R

@@ -7,10 +7,10 @@ library(shiny)
 library(here)
 
 # File path for testing
-df <- read_csv(paste0(here(), "/ShinyApps/LipidInteractomics_ShinyApp/combinedProbeDatasets_TMT.csv"))
+#df <- read_csv(paste0(here(), "/ShinyApps/LipidInteractomics_ShinyApp/combinedProbeDatasets_TMT.csv"))
 
 # File path for deploying to Shinyapps.io
-#df <- read_csv("combinedProbeDatasets_TMT.csv")
+df <- read_csv("combinedProbeDatasets_TMT.csv")
 
 probeOptions <- unique(df$LipidProbe)
 

### 2025-03-25 IndividualStudies/AT_2025.qmd
editing from Frank's suggestions, removing CNET
putting NAPE on the index
polishing dag page a little

@@
 subtitle: "Trifunctional lipid derivatives: PE’s mitochondrial interactome"
+date: 2024-12-26
 format: 
@@
 
-![](/IndividualStudies/GO_plots/PE-PA_AT_2025_CC-CNETplot.png)
-
 #### Molecular Function
@@
 <iframe src="/IndividualStudies/GO_plots/PE-PA_AT_2025_MF-DOTplot.html" width="100%" height="500px"></iframe>
-
-![](/IndividualStudies/GO_plots/PE-PA_AT_2025_MF-CNETplot.png)
 
@@
 
-![](/IndividualStudies/GO_plots/PE-PA_AT_2025_BP-CNETplot.png)
 :::

### 2025-03-25 IndividualStudies/DCC_2025.qmd
polishing dag page a little

@@
 subtitle: "Photoaffinity Labeling Reveals a Role for the Unusual Triply Acylated Phospholipid N-Acylphosphatidylethanolamine in Lactate Homeostasis"
+date: 2025-03-06
 format: 

### 2025-03-25 IndividualStudies/DH_2017.qmd
putting NAPE on the index
polishing dag page a little

@@
 subtitle: "Trifunctional lipid probes for comprehensive studies of single lipid species in living cells"
+date: 2017-02-14
 format:
@@
 
+## Data exploration
+
 :::{.border}

### 2025-03-25 IndividualStudies/RM_2021.qmd
putting NAPE on the index
polishing dag page a little

@@
 subtitle: "Synthesis and Cellular Labeling of Multifunctional Phosphatidylinositol *Bis*- and *Tris*phosphate Derivatives"
+date: 2021-06-01
 format: 

### 2025-03-25 IndividualStudies/SF_2024.qmd
polishing dag page a little

@@
 subtitle: "Trifunctional Sphinganine: A New Tool to Dissect Sphingolipid Function"
+date: 2024-02-16
 format: 

### 2025-03-25 IndividualStudies/SF_2024_B.qmd
editing from Frank's suggestions, removing CNET
polishing dag page a little

@@
 subtitle: "Trifunctional fatty acid derivatives: the impact of diazirine placement"
+date: 2024-05-25
 format: 
@@
 
-![](/IndividualStudies/GO_plots/8-3FA-1-10FA_SF_2024_CC-CNETplot.png)
-
 #### Molecular Function
@@
 <iframe src="/IndividualStudies/GO_plots/8-3FA-1-10FA_SF_2024_MF-DOTplot.html" width="100%" height="500px"></iframe>
-
-(MF CNET plot failed in production)
 

### 2025-03-25 StudyInformation_includes/AT_2025_include.qmd
polishing dag page a little

@@
 <span class="hover-image">
-  <img src="/LipidProbe/Structures/TF_PE.png" alt="PPhosphatidylethanolamine" />
+  <img src="/LipidProbe/Structures/TF_PE.png" alt="Phosphatidylethanolamine" />
 </span>

### 2025-03-25 StudyInformation_includes/DH_2017_include.qmd
polishing dag page a little

@@
 
-[Trifunctional Sphingosine](/LipidProbe/Sphingosine.qmd)
+<a href="/LipidProbe/Sphingosine.qmd" class="hover-preview">Trifunctional Sphingosine</a>
+<span class="hover-image">
+  <img src="Structures/TF_Sphingosine.png" alt="Trifunctional Sphingosine" />
+</span>
 
-[Trifunctional Diacylglycerol](/LipidProbe/Diacylglycerol.qmd)
+<a href="/LipidProbe/Diacylglycerol.qmd" class="hover-preview">Trifunctional Diacylglycerol</a>
+<span class="hover-image">
+  <img src="Structures/TF_DAG.png" alt="Trifunctional Diacylglycerol" />
+</span>
 
-[Trifunctional 8-3 Fatty acid](/LipidProbe/8-3_FattyAcid.qmd)
+<a href="/LipidProbe/8-3_FattyAcid.qmd" class="hover-preview">Trifunctional 8-3 Fatty Acid</a>
+<span class="hover-image">
+  <img src="Structures/TF_8-3_fatty_acid.png" alt="Trifunctional 8-3 Fatty Acid" />
+</span>
 

### 2025-03-25 LipidProbe/FormattingTemplate.qmd
adding credit to Berit for the structures
example

@@
 subtitle: "HTML page of individual lipid probe data"
+format: 
+  html:
+    embed-resources: false
 ---
@@
 # data$hit_annotation <- factor(pull(data, hit_annotation), levels = c("enriched hit", "hit", "enriched candidate", "candidate", "no hit", "NA"), ordered = TRUE)
-
-# # Building an ID column to maintain the order on the x-axis
-# ID <- c()
-# for(i in 0:(nrow(data))){
-# 	ID[i] = i
-# }
-
-# # Applies the ID column to the Spa results
-# data_ranked <- data |>
-#     arrange(logFC) |>
-# 	filter(LipidProbe == "1-10 FA") |>
-# 	mutate(ID = ID)
 

### 2025-03-25 LipidProbe/PhosphatidicAcid.qmd
adding a draft of the NAPE page
putting NAPE on the index
example

@@
 format: 
-  html: default
+  html:
+    embed-resources: false
 callout-icon: false
@@
 
-data <- readr::read_csv(paste0(here(), "/LipidProbe/DataSets/PA_HeLa_AT_2025.csv"))
+data <- readr::read_csv(paste0(here::here(), "/LipidProbe/DataSets/PA_HeLa_AT_2025.csv"))
 
@@
 
-## Gene Ontology Analysis
+#### Gene Ontology Analysis
 
@@
 
-#### Cell Compartment
+##### Cell Compartment
 
@@
 
-#### Molecular Function
+##### Molecular Function
 
@@
 
-#### Biological Process
+##### Biological Process
 
@@
 
-## Data exploration and download
+#### Data exploration and download
 

### 2025-03-25 LipidProbe/Phosphatidylethanolamine.qmd
putting NAPE on the index
example

@@
 format: 
-  html: default
+  html:
+    embed-resources: false
 callout-icon: false
-
 ---
@@
 :::
-:::
-
-:::{.border}
-![Trifunctional Phosphatidylethanolamine. Chemical structure drawn by Berit Blume.](/LipidProbe/Structures/TF_PE.png)
 :::

### 2025-03-28 IndividualStudies/DCC_2025.qmd
adding WY_2021 study, checking if authors like it

@@
 data <- readr::read_csv(paste0(here::here(), "/IndividualStudies/DataTables/DCC_2025_ChemrXiv_FullDataset.csv")) |> 
-  group_by(gene_name) |>
+  group_by(gene_ID) |>
   filter(gene_name != "", ratio_MvsL != "") |>
-  summarise(logFC = mean(log2(ratio_MvsL)),
+  summarise(gene_name = gene_name,
+            logFC = mean(log2(ratio_MvsL)),
             pvalue = mean(pvalue),
             numReplicates = n(),
-            AveExpr = log10(mean(mean(L_abundance), mean(M_abundance)))) |>
+            AveExpr = log10(mean(L_abundance) + mean(M_abundance))/2) |>
   arrange(-logFC) |>

### 2025-03-28 IndividualStudies/WY_2021.qmd
adding WY_2021 study, checking if authors like it

---
title: "Yu et al. 2021"
subtitle: "A Chemoproteomics Approach to Profile Phospholipase D-Derived Phosphatidyl Alcohol Interactions"
date: 2021-12-15
format: 
  html:
    embed-resources: false
standalone: false
---

::: {.callout-note collapse="true"}

{{< include /StudyInformation_includes/WY_2021_include.qmd >}}

:::

```{r NewPlottingFunctions, include=FALSE, echo=FALSE}
RankedOrderPlotSpecial <- function(data) {
    ################
    #' A standardized Ranked Order plot theme
    #' Requires an input dataframe with the columns "gene_name", "LipidProbe", "logFC", "pvalue", and "hit_annotation"
    ################

    # Applies ID column to each probe
    data <- data |>
      group_by(LipidProbe) |>
      arrange(logFC, .by_group = TRUE) |>
      mutate(ID = row_number()) |>
      ungroup()

    # First makes a ggplot template to later apply ggplotly
    RankedOrderPlots <- data |>
        ggplot(aes(x = ID,
                   y = logFC,
                   color = factor(hit_annotation),
                   fill = factor(hit_annotation),
                   shape = factor(hit_annotation),
                   alpha = factor(hit_annotation),
                   size = factor(hit_annotation))) +
        geom_point(aes(text = paste0("Gene name: ", gene_name, "\n",
                                    "LogFC: ", logFC, "\n"))) +
        geom_hline(yintercept = 0, linetype = 2) +
        geom_vline(xintercept = 0, linetype = 2) +
        scale_shape_manual(values = c("enriched hit" = 21,
                                    "hit" = 21,
                                    "enriched candidate" = 24,
                                    "candidate" = 24,
                                    "no hit" = 22), 
                        name = "Trend") +
        scale_color_manual(values = c("enriched hit" = "black",
                                    "hit" = "black",
                                    "enriched candidate" = "black",
                                    "candidate" = "black",
                                    "no hit" = "black"), 
                        name = "Trend") +
        scale_fill_manual(values = c("enriched hit" = "orange",
                                    "hit" = "orange",
                                    "enriched candidate" = "purple",
                                    "candidate" = "purple",
                                    "no hit" = "black"), 
                        name = "Trend") +
        scale_alpha_manual(values = c("enriched hit" = 0.8,
                                    "hit" = 0.8,
                                    "enriched candidate" = 0.5,
                                    "candidate" = 0.5,
                                    "no hit" = 0.25), 
                        name = "Trend") +
        scale_size_manual(values = c("enriched hit" = 4,
                                    "hit" = 4,
                                    "enriched candidate" = 2,
                                    "candidate" = 2, 
                                    "no hit" = 0.75), 
                        name = "Trend") +
        facet_wrap(~LipidProbe) +
        ylab("Log2 fold-change") +
        xlab("Ranked-order gene") +
        theme_minimal() +
        theme(text = element_text(family = "serif")) +
        theme(panel.border = element_rect(color = NA, fill = NA)) +
        theme(legend.title = element_text(size = 12, face = "bold")) +
        theme(axis.title = element_text(size = 12, face = "bold")) +
        theme(legend.text = element_text(size = 12))  +
        theme(strip.text = element_text(
    size = 20))
    m <- list(l=50, r = 50, b= 100, pad = 4)

    RankedOrderPlotly <- ggplotly(RankedOrderPlots,
                            tooltip = c("text", dynamicTicks = TRUE),
                            hovermode = "closest",
                            autosize = T,
                            margin = m) |>
                    layout(showlegend = FALSE)

    return(RankedOrderPlotly)
}

MASpecial <- function(data) {

    ################
    #' A standardized MA plot function
    #' Receives a dataframe. Needs to have the following columns for the aes() to work: AveExpr, logFC, hit_annotation, gene_name.
    #' Dynamically determines the limits of the plot under the scale_x/y_scontinuous calls
    #' Produces first a facet-wrapped ggplot, then converts it to a plotly plot.
    ################

    MAPlots <- data |>
        ggplot(aes(x = AveExpr,
                   y = logFC,
                   color = factor(hit_annotation),
                   fill = factor(hit_annotation),
                   shape = factor(hit_annotation),
                   alpha = factor(hit_annotation),
                   size = factor(hit_annotation))) +
        geom_point(aes(text = paste0("Gene name: ", gene_name, "\n",
                                    "LogFC: ", logFC, "\n",
                                    "AveExpr: ", AveExpr, "\n"))) +
        geom_hline(yintercept = 0, linetype = 2) +
        geom_vline(xintercept = 0, linetype = 2) +
        scale_x_continuous(limits = c(0.9 * min(abs(data$AveExpr)), 1.1 * max(abs(data$AveExpr))))+
        scale_y_continuous(limits = c(-1.1 * max(abs(data$logFC)), 1.1 * max(abs(data$logFC))))+
        scale_shape_manual(values = c("enriched hit" = 21,
                                    "hit" = 21,
                                    "enriched candidate" = 24,
                                    "candidate" = 24,
                                    "no hit" = 22), 
                        name = "Trend") +
        scale_color_manual(values = c("enriched hit" = "black",
                                    "hit" = "black",
                                    "enriched candidate" = "black",
                                    "candidate" = "black",
                                    "no hit" = "black"), 
                        name = "Trend") +
        scale_fill_manual(values = c("enriched hit" = "orange",
                                    "hit" = "orange",
                                    "enriched candidate" = "purple",
                                    "candidate" = "purple",
                                    "no hit" = "black"), 
                        name = "Trend") +
        scale_alpha_manual(values = c("enriched hit" = 0.8,
                                    "hit" = 0.8,
                                    "enriched candidate" = 0.5,
                                    "candidate" = 0.5,
                                    "no hit" = 0.25), 
                        name = "Trend") +
        scale_size_manual(values = c("enriched hit" = 4,
                                    "hit" = 4,
                                    "enriched candidate" = 2,
                                    "candidate" = 2, 
                                    "no hit" = 0.75), 
                        name = "Trend") +
        facet_wrap(~LipidProbe) +
        ylab("Log2 fold-change") +
        xlab("Average Ion Intensity") +
        theme_minimal() +
        theme(text = element_text(family = "serif")) +
        theme(panel.border = element_rect(color = NA, fill = NA)) +
        theme(legend.title = element_text(size = 12, face = "bold")) +
        theme(axis.title = element_text(size = 12, face = "bold")) +
        theme(legend.text = element_text(size = 12)) +
        theme(strip.text = element_text(
    size = 20))

    m <- list(l=50, r = 50, b= 100, pad = 4)

    MAPlotly <- ggplotly(MAPlots,
                            tooltip = c("text", dynamicTicks = TRUE),
                            hovermode = "closest",
                            autosize = T,
                            margin = m) |>
                    layout(showlegend = FALSE)

    return(MAPlotly)
}

```

```{r Setup_Data_Wrangling, include=FALSE, echo=FALSE}
## intitialize libraries
library(here)
library(biomaRt)
library(rentrez)

## Opening the source file for the ggplot custom theme
source(paste0(here(), "/Resources/ggplot_styles.R"))

# Opening raw data file for wrangling and cleaning up
RawData <- read_csv(paste0(here::here(), "/IndividualStudies/DataTables/WY_2021_ACSChemBio_RawData.csv"))

#RawData <- read_csv("IndividualStudies/DataTables/WY_2021_ACSChemBio_RawData.csv")

RawData <- RawData |>
  filter(Coverage != 0 & Fold_change != 0) |>
  group_by(Accession) |>
  summarise(gene_name = Description,
            logFC = mean(log2(Fold_change)),
            # pvalue = mean(pvalue),
            numReplicates = n(),
            AveExpr = log10(mean(Control_abundance) + mean(Sample_abundance)/2)) |>
  arrange(-logFC)

median_logFC <- median(RawData$logFC)

RawData$logFC <- RawData$logFC - median_logFC

RawData <- RawData |> 
  mutate(LipidProbe = "PDAA",
        AveExpr = case_when(.default = AveExpr,
                              AveExpr == -Inf ~ 0),
                              hit_annotation = case_when(.default = "no hit",
                                                          logFC >= 0.5849625 & numReplicates == 2 ~ "enriched candidate",
                                                          logFC >= 0.5849625 & numReplicates == 3 ~ "enriched hit")) |>         
  glimpse()

nrow(RawData |> filter(hit_annotation == "enriched hit"))

# Organize the hit annotations as factors
RawData$hit_annotation <- factor(pull(RawData, hit_annotation), levels = c("enriched hit", "hit", "enriched candidate", "candidate", "no hit", "NA"), ordered = TRUE)

# write_csv(RawData, paste0(here(), "/IndividualStudies/DataTables/WY_2021_ACSChemBio_Download.csv"))

```

## Data visualization

::::{.border}
::: {.panel-tabset}

##### Ranked order plot

```{r, echo=FALSE, warning=FALSE}
#| fig-cap: "Data as reported in [Yu et al., 2021, 2024](/IndividualStudies/WY_2021.qmd). Black proteins are identified in only one replicate, Purple enriched candidates are defined as proteins identified in two replicates & fold-change > 1.5 (logFC 0.585) & pvalue < 0.01, and Orange enriched hits are defined as proteins identified in all three replicates & fold-change > 1.5 (logFC 0.585) & pvalue < 0.01)."

RankedOrderPlotSpecial(RawData)
```

##### MA plot

```{r, echo=FALSE, warning=FALSE}
#| fig-cap: "Data as reported in [Yu et al., 2021](/IndividualStudies/WY_2021.qmd). Black proteins are identified in only one replicate, Purple enriched candidates are defined as proteins identified in two replicates & fold-change > 1.5 (logFC 0.585) & pvalue < 0.01, and Orange enriched hits are defined as proteins identified in all three replicates & fold-change > 1.5 (logFC 0.585) & pvalue < 0.01)."

MASpecial(RawData)
```

##### Venn Diagram

```{r Venn_wrangling, include=FALSE, warning=FALSE}

###### Wrangling for the Venn Diagram ######
# Read the dataset

VennData <- read_csv("DataTables/WY_2021_ACSChemBio_RawData.csv")  |>
  mutate(gene_name = Description)

# Separates out each of the genesets, then forces them back together in a vectorized list.
A_proteins <- VennData |>
  filter(Trial == 1) |>
  dplyr::select(gene_name)

B_proteins <- VennData |>
  filter(Trial == 2) |>
  dplyr::select(gene_name)

C_proteins <- VennData |>
  filter(Trial == 3) |>
  dplyr::select(gene_name)

VennList <- list("Trial 1" = as.list(A_proteins$gene_name), "Trial 2" = as.list(B_proteins$gene_name), "Trial 3" = as.list(C_proteins$gene_name))
```

```{r NAPE_Venn, echo=FALSE, warning=FALSE}
#| fig-cap: "Data as reported in [Yu et al., 2021](/IndividualStudies/WY_2021.qmd). A Venn diagram depicts the overlapping identification of proteins between the three trials (replicates)."

ggvenn <- ggvenn(VennList,
                      show_percentage = FALSE,
                      show_elements = FALSE,
                      fill_color = c("orange", "purple", "blue")) +
        labs(x = "", y = "") +
        theme_minimal()

ggvenn

```

:::
::::

## Data exploration

:::{.border}
```{r NAPE_DataTable, echo=FALSE, warning=FALSE}

# Here is the code to make the filterable lists shown in the crosstalk table below

data <- RawData |>
  dplyr::select(Accession, gene_name, LipidProbe, hit_annotation, logFC, numReplicates) |>
  mutate(logFC = signif(logFC, digits=3)) |>
  arrange(-logFC) |>
  arrange(hit_annotation)

## Creates a reactive dataframe
data_reactive <- crosstalk::SharedData$new(data)

htmltools::tags$div(
  class = "filter-container",
  filter_checkbox(id = "LipidProbe",
                  label = "Lipid probe in pulldown:", 
                  sharedData = data_reactive,
                  group = ~LipidProbe),
  filter_checkbox(id = "hit_annotation",
                  label = "Enrichment criteria:", 
                  sharedData = data_reactive,
                  group = ~hit_annotation)
)

## Displays the reactive dataframe
datatable(data_reactive, 
          caption = "This datatable contains all the data plotted above. Check the boxes below to filter the dataset by which lipid probe was used in the pulldown and by significance thresholds. logFC ratios are median normalized. \"Num Replicate IDs\" denotes the number of replicates in which the protein was identified. As above, \"enriched hit\" denotes proteins identified in all three replicates & fold-change > 1.5 (logFC 0.585) & pvalue < 0.01. \"enriched candidates\" are proteins identified in two replicates & fold-change > 1.5 (logFC 0.585) & pvalue < 0.01.",
          options = list(pageLength = 15),
                         colnames = c("Accession", "Gene Name", "Lipid Probe", "Hit Annotation", "LogFC", "Num Replicate IDs"),
                         rownames=FALSE)

```

:::

<br>

## Data download

{{< downloadthis DataTables/WY_2021_ACSChemBio_Download.csv dname="WY_2021_ACS-ChemBio_Download">}}

### 2025-03-28 StudyInformation_includes/DCC_2025_include.qmd
adding WY_2021 study, checking if authors like it

@@
 #### Abstract
-Most eukaryotic membranes comprise phospholipids bearing two hydrophobic tails, but N-
-acylphosphatidylethanolamine (NAPE) stands out as a long-known but poorly understood
-phospholipid with three hydrophobic groups. What little attention that NAPE has received has been
-devoted to understanding its metabolic functions as a precursor to N-acylethanolamines, bioactive
-lipids that act as endocannabinoids. Yet, levels of NAPE increase during myocardial infarction and
-ischemia, suggesting potential signaling roles for this lipid. Here, we exploit photoaffinity labeling
-(PAL) to identify NAPE-interacting proteins and elucidate signaling functions of NAPE. By
-positioning diazirine and alkyne groups in metabolically distinct regions of the NAPE molecule,
-we ensured that our PAL probe reported on interactions of NAPE and not NAE. Our studies
-identified several NAPE interactors, including two single-pass transmembrane proteins,
-CD147/Basigin and CD44, both of which serve as chaperones for monocarboxylate transporters
-(MCTs) from the SLC16A family that mediate lactate flux across the plasma membrane.
-Functional studies revealed that NAPE stimulates lactate efflux by MCTs dependent upon CD147
-and CD44, establishing NAPE as a bona fide signaling lipid and pointing to potential physiological
-roles in metabolic and energy homeostasis that may be pathologically relevant in ischemia.
+Most eukaryotic membranes comprise phospholipids bearing two hydrophobic tails, but N-acylphosphatidylethanolamine (NAPE) stands out as a long-known but poorly understood phospholipid with three hydrophobic groups.
+What little attention that NAPE has received has been devoted to understanding its metabolic functions as a precursor to N-acylethanolamines, bioactive lipids that act as endocannabinoids.
+Yet, levels of NAPE increase during myocardial infarction and ischemia, suggesting potential signaling roles for this lipid.
+Here, we exploit photoaffinity labeling (PAL) to identify NAPE-interacting proteins and elucidate signaling functions of NAPE.
+By positioning diazirine and alkyne groups in metabolically distinct regions of the NAPE molecule, we ensured that our PAL probe reported on interactions of NAPE and not NAE.
+Our studies identified several NAPE interactors, including two single-pass transmembrane proteins, CD147/Basigin and CD44, both of which serve as chaperones for monocarboxylate transporters (MCTs) from the SLC16A family that mediate lactate flux across the plasma membrane.
+Functional studies revealed that NAPE stimulates lactate efflux by MCTs dependent upon CD147 and CD44, establishing NAPE as a bona fide signaling lipid and pointing to potential physiological roles in metabolic and energy homeostasis that may be pathologically relevant in ischemia.
 

### 2025-03-28 StudyInformation_includes/WY_2021_include.qmd
adding WY_2021 study, checking if authors like it

## Study details

##### Authors

Weizhi Yu, Zhi Lin, Christina M. Woo, Jeremy M. Baskin

##### Journal

ACS Chemical Biology

<https://doi.org/10.1021/acschembio.1c00584>{target="_blank"}

##### Abstract

Alcohol consumption leads to formation of phosphatidylethanol (PEth) via the transphosphatidylation activity of phospholipase D (PLD) enzymes. Though this non-natural phospholipid routinely serves as a biomarker of chronic alcoholism, its pathophysiological roles remain unknown. We use a minimalist diazirine alkyne alcohol as an ethanol surrogate to generate clickable, photoaffinity lipid reporters of PEth localization and lipid–protein interactions via PLD-mediated transphosphatidylation. We use these tools to visualize phosphatidyl alcohols in a manner compatible with standard permeabilization and immunofluorescence methods. We also use click chemistry tagging, enrichment, and proteomics analysis to define the phosphatidyl alcohol interactome. Our analysis reveals an enrichment of putative interactors at various membrane locations, and we validate one such interaction with the single-pass transmembrane protein basigin/CD147. This study provides a comprehensive view of the molecular interactions of phosphatidyl alcohols with the cellular proteome and points to future work to connect such interactions to potential pathophysiological roles of PEth.

##### Lipid probes utilized

PDAA

<!-- 
<a href="/LipidProbe/N-Acylphosphatidylethanolamine.qmd" class="hover-preview">Bifunctional NAPE</a>
<span class="hover-image">
  <img src="/LipidProbe/Structures/BF_NAPE.png" alt="Bifunctional NAPE" />
</span> -->

##### Cell line analyzed

[HeLa](https://www.atcc.org/products/ccl-2){target="_blank"}

#### Uncaging & Crosslinking timeline

##### Mass spectrometry quantification method

PSM

### 2025-03-28 IndividualStudies/DCC_2025.qmd
minor update for jeremy

--- 2025-03-25 IndividualStudies/DCC_2025.qmd
@@
 data <- readr::read_csv(paste0(here::here(), "/IndividualStudies/DataTables/DCC_2025_ChemrXiv_FullDataset.csv")) |> 
-  group_by(gene_name) |>
-  filter(gene_name != "", ratio_MvsL != "") |>
-  summarise(logFC = mean(log2(ratio_MvsL)),
+  group_by(gene_ID) |>
+  filter(ratio_MvsL != "") |>
+  summarise(gene_name = gene_name,
+            logFC = mean(log2(ratio_MvsL)),
             pvalue = mean(pvalue),
             numReplicates = n(),
-            AveExpr = log10(mean(mean(L_abundance), mean(M_abundance)))) |>
+            AveExpr = log10(mean(L_abundance) + mean(M_abundance))/2) |>
   arrange(-logFC) |>
@@
 \"enriched candidates\" are proteins identified in two replicates & fold-change > 1.5 (logFC 0.585) & pvalue < 0.01.",
-          options = list(pageLength = 15),
+          options = list(pageLength = 10),
                          colnames = c("Gene Name", "Lipid Probe", "Hit Annotation", "LogFC", "p value", "Num Replicate IDs"),

### 2025-03-28 IndividualStudies/WY_2021.qmd
minor update for jeremy

@@
 \"enriched candidates\" are proteins identified in two replicates & fold-change > 1.5 (logFC 0.585) & pvalue < 0.01.",
-          options = list(pageLength = 15),
+          options = list(pageLength = 10),
                          colnames = c("Accession", "Gene Name", "Lipid Probe", "Hit Annotation", "LogFC", "Num Replicate IDs"),

### 2025-03-29 IndividualStudies/DCC_2025.qmd
fixing the table at the bottom of DCC_2025

@@
 data <- readr::read_csv(paste0(here::here(), "/IndividualStudies/DataTables/DCC_2025_ChemrXiv_FullDataset.csv")) |> 
-  group_by(gene_ID) |>
+  group_by(gene_name) |>
   filter(ratio_MvsL != "") |>
-  summarise(gene_name = gene_name,
-            logFC = mean(log2(ratio_MvsL)),
+  summarise(logFC = mean(log2(ratio_MvsL)),
             pvalue = mean(pvalue),
@@
 
-data <- data |>
+data2 <- data |>
   dplyr::select(gene_name, LipidProbe, hit_annotation, logFC, pvalue, numReplicates) |>
@@
           pvalue = signif(pvalue, digits=3)) |>
-  arrange(-logFC) |>
-  arrange(hit_annotation)
+  arrange(hit_annotation, numReplicates, -logFC, )
+
+unique(data2$gene_name)
 

### 2025-03-29 IndividualStudies/DCC_2025.qmd
ok last push for the week

@@
 
-data2 <- data |>
+data <- data |>
   dplyr::select(gene_name, LipidProbe, hit_annotation, logFC, pvalue, numReplicates) |>
@@
           pvalue = signif(pvalue, digits=3)) |>
-  arrange(hit_annotation, numReplicates, -logFC, )
-
-unique(data2$gene_name)
+  arrange(hit_annotation, numReplicates, -logFC)
 

### 2025-03-30 IndividualStudies/DCC_2025.qmd
added gene names to all of Jeremys datasets

@@
          hit_annotation = case_when(.default = "no hit",
-                                    logFC >= 0.5849625 & pvalue <= 0.01 & numReplicates == 2 ~ "enriched candidate",
-                                    logFC >= 0.5849625 & pvalue <= 0.01 & numReplicates == 3 ~ "enriched hit")) |>
+                                    logFC >= 0.5849625 & pvalue <= 0.05 & numReplicates == 2 ~ "enriched candidate",
+                                    logFC >= 0.5849625 & pvalue <= 0.05 & numReplicates == 3 ~ "enriched hit")) |>
   glimpse()
@@
 #| fig-cap: "Ranked-order plots depict the relative enrichment of each protein versus non-crosslinked control (y-axis) from lowest to highest.
-Black proteins are identified in only one replicate, Purple enriched candidates are defined as proteins identified in two replicates & fold-change > 1.5 (logFC 0.585) & pvalue < 0.01, and Orange enriched hits are defined as proteins identified in all three replicates & fold-change > 1.5 (logFC 0.585) & pvalue < 0.01)."
+Black proteins are identified in only one replicate, Purple enriched candidates are defined as proteins identified in two replicates & fold-change > 1.5 (logFC 0.585) & pvalue < 0.05, and Orange enriched hits are defined as proteins identified in all three replicates & fold-change > 1.5 (logFC 0.585) & pvalue < 0.05)."
 
@@
 #| fig-cap: "MA plots depict the average abundance of each protein in the crosslinked and uncrosslinked conditions (x-axis) versus the log2-transformed fold-change between the crosslinked and uncrosslinked conditions (y-axis).
-Black proteins are identified in only one replicate, Purple enriched candidates are defined as proteins identified in two replicates & fold-change > 1.5 (logFC 0.585) & pvalue < 0.01, and Orange enriched hits are defined as proteins identified in all three replicates & fold-change > 1.5 (logFC 0.585) & pvalue < 0.01)."
+Black proteins are identified in only one replicate, Purple enriched candidates are defined as proteins identified in two replicates & fold-change > 1.5 (logFC 0.585) & pvalue < 0.05, and Orange enriched hits are defined as proteins identified in all three replicates & fold-change > 1.5 (logFC 0.585) & pvalue < 0.05)."
 
@@
 # Read the dataset
-VennData <- readr::read_csv(paste0(here::here(), "/LipidProbe/DataSets/DCC_2025_ChemrXiv_FilteredDataset.csv"))
+VennData <- readr::read_csv(paste0(here::here(), "/IndividualStudies/DataTables/DCC_2025_ChemrXiv_FullDataset.csv")) |>
+
+  filter(ratio_MvsL > log2(1.5), pvalue < 0.05) |>
+  glimpse()
 
@@
 #| fig-cap: "A Venn diagram depicts the overlapping identification of proteins between the three replicates.
-The full dataset was filtered to only include proteins with fold-change > 1.5 (logFC > 0.585) and p-value < 0.01 There are 88 proteins enriched uniquely in Replicate A, 75 proteins enriched uniquely in Replicate B, and 64 proteins enriched uniquely in Replicate C."
+The full dataset was filtered to only include proteins with fold-change > 1.5 (logFC > 0.585) and p-value < 0.05 There are 88 proteins enriched uniquely in Replicate A, 75 proteins enriched uniquely in Replicate B, and 64 proteins enriched uniquely in Replicate C."
 
@@
 \"Num Replicate IDs\" denotes the number of replicates in which the protein was identified.
-As above, \"enriched hit\" denotes proteins identified in all three replicates & fold-change > 1.5 (logFC 0.585) & pvalue < 0.01.
-\"enriched candidates\" are proteins identified in two replicates & fold-change > 1.5 (logFC 0.585) & pvalue < 0.01.",
+As above, \"enriched hit\" denotes proteins identified in all three replicates & fold-change > 1.5 (logFC 0.585) & pvalue < 0.05.
+\"enriched candidates\" are proteins identified in two replicates & fold-change > 1.5 (logFC 0.585) & pvalue < 0.05.",
           options = list(pageLength = 10),

### 2025-03-30 IndividualStudies/WY_2021.qmd
added gene names to all of Jeremys datasets

@@
 
-# Opening raw data file for wrangling and cleaning up
-RawData <- read_csv(paste0(here::here(), "/IndividualStudies/DataTables/WY_2021_ACSChemBio_RawData.csv"))
-
-#RawData <- read_csv("IndividualStudies/DataTables/WY_2021_ACSChemBio_RawData.csv")
-
-RawData <- RawData |>
+RawData <- read_csv(paste0(here::here(), "/IndividualStudies/DataTables/WY_2021_ACSChemBio_RawData.csv")) |>
   filter(Coverage != 0 & Fold_change != 0) |>
-  group_by(Accession) |>
-  summarise(gene_name = Description,
-            logFC = mean(log2(Fold_change)),
+  mutate(gene_name = gene_name...3) |>
+  group_by(gene_name) |>
+  summarise(logFC = mean(log2(Fold_change)),
             # pvalue = mean(pvalue),
@@
 :::{.border}
-```{r NAPE_DataTable, echo=FALSE, warning=FALSE}
+```{r PDAA_DataTable, echo=FALSE, warning=FALSE}
 
@@
 data <- RawData |>
-  dplyr::select(Accession, gene_name, LipidProbe, hit_annotation, logFC, numReplicates) |>
+  dplyr::select(gene_name, LipidProbe, hit_annotation, logFC, numReplicates) |>
   mutate(logFC = signif(logFC, digits=3)) |>
@@
           options = list(pageLength = 10),
-                         colnames = c("Accession", "Gene Name", "Lipid Probe", "Hit Annotation", "LogFC", "Num Replicate IDs"),
+                         colnames = c("Gene Name", "Lipid Probe", "Hit Annotation", "LogFC", "Num Replicate IDs"),
                          rownames=FALSE)

### 2025-03-30 Resources/get_gene_names.r

@@ -1,0 +1,92 @@
+# ###############
+# # This script retrieves gene symbols from RefSeq protein accession numbers using the NCBI Entrez API.
+# # It handles outdated accessions by checking for linked updated protein IDs.
+# # It also filters out entries without gene symbols and saves the results to a CSV file.
+# ###############
+# # Load necessary libraries
+# library(rentrez)
+# library(dplyr)
+# library(readr)
+# library(here)
+# library(tidyr)
+# library(tibble)
+
+
+# # Function to get gene symbol from a RefSeq protein accession number
+# get_gene_symbol <- function(accession) {
+#     # Search NCBI protein database for the given accession
+#     search_result <- entrez_search(db = "protein", term = accession)
+    
+#     if (length(search_result$ids) > 0) {
+#         protein_id <- search_result$ids[1]  # Get first valid protein ID
+
+#         # Check for newer version of the protein accession
+#         protein_links <- entrez_link(dbfrom = "protein", id = protein_id, db = "protein")
+
+#         if (!is.null(protein_links$links$protein_protein)) {
+#             latest_protein_id <- protein_links$links$protein_protein[1]  # Take the first linked updated protein
+#             message(paste("Accession", accession, "is outdated. Updating to", latest_protein_id))
+#             return(get_gene_symbol(latest_protein_id))  # Retry with the latest accession
+#         }
+
+#         # Use entrez_link to find the linked Gene ID
+#         links <- entrez_link(dbfrom = "protein", id = protein_id, db = "gene")
+
+#         if (length(links$links$protein_gene) > 0) {
+#             gene_id <- links$links$protein_gene[1]  # Get the linked Gene ID
+
+#             # Retrieve summary information for the gene
+#             gene_summary <- entrez_summary(db = "gene", id = gene_id)
+            
+#             print(gene_summary$name)
+#             return(gene_summary$name)  # Extract official gene symbol
+#         }
+#     } 
+
+#     message(paste("Accession not found or no gene linked:", accession))
+#     return(NA)  # Return NA if not found
+# }
+
+# get_gene_symbol <- Vectorize(get_gene_symbol)
+
+
+
[…]

### 2025-03-31 IndividualStudies/DCC_2025.qmd
adding structures for NAPE and bf-NAPE

@@
 
+```{r HiddenOriginalDataWrangling, include=FALSE, echo=FALSE}
+
+# data <- readr::read_csv(paste0(here::here(), "/IndividualStudies/DataTables/DCC_2025_ChemrXiv_FullDataset.csv")) |> 
+#   group_by(gene_name) |>
+#   filter(ratio_MvsL != "") |>
+#   summarise(logFC = mean(log2(ratio_MvsL)),
+#             pvalue = mean(pvalue),
+#             numReplicates = n(),
+#             AveExpr = log10(mean(L_abundance) + mean(M_abundance))/2) |>
+#   arrange(-logFC) |>
+#   mutate(LipidProbe = "BF-NAPE",
+#          hit_annotation = case_when(.default = "no hit",
+#                                     logFC >= 0.5849625 & pvalue <= 0.05 & numReplicates == 2 ~ "enriched candidate",
+#                                     logFC >= 0.5849625 & pvalue <= 0.05 & numReplicates == 3 ~ "enriched hit")) |>
+#   glimpse()
+
+# median_logFC <- median(data$logFC)
+
+# data$logFC <- data$logFC - median_logFC
+
+```
+
 ## Data visualization
@@
 ## Opening the source file for the ggplot custom theme
-source(paste0(here::here(), "/Resources/ggplot_styles.R"))
+source(here::here("Resources/ggplot_styles.R"))
 
-data <- readr::read_csv(paste0(here::here(), "/IndividualStudies/DataTables/DCC_2025_ChemrXiv_FullDataset.csv")) |> 
-  group_by(gene_name) |>
-  filter(ratio_MvsL != "") |>
-  summarise(logFC = mean(log2(ratio_MvsL)),
-            pvalue = mean(pvalue),
-            numReplicates = n(),
-            AveExpr = log10(mean(L_abundance) + mean(M_abundance))/2) |>
-  arrange(-logFC) |>
-  mutate(LipidProbe = "BF-NAPE",
-         hit_annotation = case_when(.default = "no hit",
-                                    logFC >= 0.5849625 & pvalue <= 0.05 & numReplicates == 2 ~ "enriched candidate",
-                                    logFC >= 0.5849625 & pvalue <= 0.05 & numReplicates == 3 ~ "enriched hit")) |>
-  glimpse()
-
-median_logFC <- median(data$logFC)
-
-data$logFC <- data$logFC - median_logFC
+data <- readr::read_csv(here::here("IndividualStudies/DataTables/DCC_2025_ChemrXiv_Download.csv"))
 
@@
 
-# write_csv(data, paste0(here(), "/LipidProbe/DataSets/DCC_2025_ChemrXiv_Download.csv"))
+# write_csv(data, here("IndividualStudies/DataTables/DCC_2025_ChemrXiv_Download.csv"))
 

### 2025-03-31 IndividualStudies/WY_2021.qmd
adding structures for NAPE and bf-NAPE

@@
         scale_x_continuous(limits = c(0.9 * min(abs(data$AveExpr)), 1.1 * max(abs(data$AveExpr))))+
-        scale_y_continuous(limits = c(-1.1 * max(abs(data$logFC)), 1.1 * max(abs(data$logFC))))+
+        scale_y_continuous(limits = c(-1.1 * max(abs(data$logFC)), 5))+
         scale_shape_manual(values = c("enriched hit" = 21,
@@
 
+```{r HiddenDataWrangling, include=FALSE, echo=FALSE}
+
+# RawData <- read_csv(here::here("IndividualStudies/DataTables/WY_2021_ACSChemBio_RawData.csv")) |>
+#   filter(Coverage != 0 & Fold_change != 0) |>
+#   mutate(gene_name = gene_name...3) |>
+#   group_by(gene_name) |>
+#   summarise(logFC = mean(log2(Fold_change)),
+#             # pvalue = mean(pvalue),
+#             numReplicates = n(),
+#             AveExpr = log10(mean(Control_abundance) + mean(Sample_abundance)/2)) |>
+#   arrange(-logFC)
+
+# median_logFC <- median(RawData$logFC)
+
+# RawData$logFC <- RawData$logFC - median_logFC
+
+# RawData <- RawData |> 
+#   mutate(LipidProbe = "PDAA",
+#         AveExpr = case_when(.default = AveExpr,
+#                               AveExpr == -Inf ~ 0),
+#                               hit_annotation = case_when(.default = "no hit",
+#                                                           logFC >= 0.5849625 & numReplicates == 2 ~ "enriched candidate",
+#                                                           logFC >= 0.5849625 & numReplicates == 3 ~ "enriched hit")) |>         
+#   glimpse()
+
+# write_csv(RawData, here("IndividualStudies/DataTables/WY_2021_ACSChemBio_Download.csv"))
+
+```
+
 ```{r Setup_Data_Wrangling, include=FALSE, echo=FALSE}
@@
 ## Opening the source file for the ggplot custom theme
-source(paste0(here(), "/Resources/ggplot_styles.R"))
+source(here("Resources/ggplot_styles.R"))
 
-RawData <- read_csv(paste0(here::here(), "/IndividualStudies/DataTables/WY_2021_ACSChemBio_RawData.csv")) |>
-  filter(Coverage != 0 & Fold_change != 0) |>
-  mutate(gene_name = gene_name...3) |>
-  group_by(gene_name) |>
-  summarise(logFC = mean(log2(Fold_change)),
-            # pvalue = mean(pvalue),
-            numReplicates = n(),
-            AveExpr = log10(mean(Control_abundance) + mean(Sample_abundance)/2)) |>
-  arrange(-logFC)
-
-median_logFC <- median(RawData$logFC)
-
-RawData$logFC <- RawData$logFC - median_logFC
-
-RawData <- RawData |> 
-  mutate(LipidProbe = "PDAA",
-        AveExpr = case_when(.default = AveExpr,
-                              AveExpr == -Inf ~ 0),
-                              hit_annotation = case_when(.default = "no hit",
-                                                          logFC >= 0.5849625 & numReplicates == 2 ~ "enriched candidate",
-                                                          logFC >= 0.5849625 & numReplicates == 3 ~ "enriched hit")) |>         
-  glimpse()
-
-nrow(RawData |> filter(hit_annotation == "enriched hit"))
+data <- read_csv(here("IndividualStudies/DataTables/WY_2021_ACSChemBio_Download.csv"))
 
 # Organize the hit annotations as factors
-RawData$hit_annotation <- factor(pull(RawData, hit_annotation), levels = c("enriched hit", "hit", "enriched candidate", "candidate", "no hit", "NA"), ordered = TRUE)
-
-# write_csv(RawData, paste0(here(), "/IndividualStudies/DataTables/WY_2021_ACSChemBio_Download.csv"))
+data$hit_annotation <- factor(pull(data, hit_annotation), levels = c("enriched hit", "hit", "enriched candidate", "candidate", "no hit", "NA"), ordered = TRUE)
 
@@
 
-RankedOrderPlotSpecial(RawData)
+RankedOrderPlotSpecial(data)
 ```
@@
 
-MASpecial(RawData)
+MASpecial(data)
 ```
@@
 
-VennData <- read_csv("DataTables/WY_2021_ACSChemBio_RawData.csv")  |>
-  mutate(gene_name = Description)
+VennData <- read_csv(here("IndividualStudies/DataTables/WY_2021_ACSChemBio_RawData.csv")) |>
+  mutate(gene_name = gene_name...3)
 
@@
 
-data <- RawData |>
+data <- data |>
   dplyr::select(gene_name, LipidProbe, hit_annotation, logFC, numReplicates) |>

### 2025-03-31 LipidProbe/N-Acylphosphatidylethanolamine.qmd
example
adding structures for NAPE and bf-NAPE

@@
 subtitle: "NAPE"
-prefer-html: true
 format: 
-  html: default
+  html:
+    embed-resources: false
 callout-icon: false
@@
 ::: {layout="[[-0.01,99.99], [100]]"}
-<!-- ![(A) Native N-Acylphosphatidylethanolamine.](/LipidProbe/Structures/PE.png) -->
+![(A) Native N-Acylphosphatidylethanolamine.](/LipidProbe/Structures/NAPE.png)
 
-![(B) Bifunctional N-Acylphosphatidylethanolamine.](/LipidProbe/Structures/BF_NAPE.png)
+![(B) Bifunctional N-Acylphosphatidylethanolamine.](/LipidProbe/Structures/BF-NAPE.png)
 
@@
 ## Opening the source file for the ggplot custom theme
-source(paste0(here::here(), "/Resources/ggplot_styles.R"))
+source(here::here("Resources/ggplot_styles.R"))
 
-data <- readr::read_csv(paste0(here::here(), "/LipidProbe/DataSets/DCC_2025_ChemrXiv_FullDataset.csv")) |> 
-  group_by(gene_name) |>
-  filter(gene_name != "" & ratio_MvsL != "" & L_abundance != "" & M_abundance != "") |>
-  summarise(logFC = mean(log2(ratio_MvsL)),
-            pvalue = mean(pvalue),
-            numReplicates = n(),
-            AveExpr = log10(mean(mean(L_abundance), mean(M_abundance)))) |>
-  arrange(logFC) |>
-  mutate(LipidProbe = "BF-NAPE",
-         hit_annotation = case_when(.default = "no hit",
-                                    logFC >= 0.5849625 & pvalue <= 0.01 & numReplicates == 2 ~ "enriched candidate",
-                                    logFC >= 0.5849625 & pvalue <= 0.01 & numReplicates == 3 ~ "enriched hit")) |>
-  glimpse()
-
-median_logFC <- median(data$logFC)
-
-data$logFC <- data$logFC - median_logFC
+data <- readr::read_csv(here::here("LipidProbe/DataSets/DCC_2025_ChemrXiv_Download.csv"))
 
@@
 
-```{r save_csv, include=FALSE, echo=FALSE, warning=FALSE}
-
-# write_csv(data, paste0(here(), "/LipidProbe/DataSets/DCC_2025_ChemrXiv_Download.csv"))
-
-```
-
 {{< downloadthis DataSets/DCC_2025_ChemrXiv_Download.csv dname="DCC_2025_ChemrXiv_Download">}}

### 2025-03-31 StudyInformation_includes/DH_2017_include.qmd
adding structures for NAPE and bf-NAPE

--- 2025-03-24 StudyInformation_includes/DH_2017_include.qmd
@@
 
-[Trifunctional Sphingosine](/LipidProbe/Sphingosine.qmd)
+<a href="/LipidProbe/Sphingosine.qmd" class="hover-preview">Trifunctional Sphingosine</a>
+<span class="hover-image">
+  <img src="/LipidProbe/Structures/TF_Sphingosine.png" alt="Trifunctional Sphingosine" />
+</span>
 
-[Trifunctional Diacylglycerol](/LipidProbe/Diacylglycerol.qmd)
+<a href="/LipidProbe/Diacylglycerol.qmd" class="hover-preview">Trifunctional Diacylglycerol</a>
+<span class="hover-image">
+  <img src="/LipidProbe/Structures/TF_DAG.png" alt="Trifunctional Diacylglycerol" />
+</span>
 
-[Trifunctional 8-3 Fatty acid](/LipidProbe/8-3_FattyAcid.qmd)
+<a href="/LipidProbe/8-3_FattyAcid.qmd" class="hover-preview">Trifunctional 8-3 Fatty Acid</a>
+<span class="hover-image">
+  <img src="/LipidProbe/Structures/TF_8-3_fatty_acid.png" alt="Trifunctional 8-3 Fatty Acid" />
+</span>
 

### 2025-03-31 BioinformaticsApplicationNote/GG_2025_applicationNote.qmd
Adding Yu et al 2021 to yaml, adding JMB edits to manuscript

--- 2025-02-18 BioinformaticsApplicationNote/GG_2025_applicationNote.qmd
@@
     email: gaelen.guzman@lipidinteractome.org
+  - name: "Frank Stein"
+    affiliations:
+      - name: "Proteomics Core Facility, European Molecular Biology Laboratory"
+        city: Heidelberg
+        country: Germany
+        postal-code: 69117
+    orcid: 0000-0001-9695-1692
+  - name: Jeremy M. Baskin
+    affiliations:
+      - name: "Department of Chemistry and Chemical Biology and Weill Institute for Cell and Molecular Biology, Cornell University"
+        city: Ithaca
+        state: NY
+        postal-code: 14853
   - name: "Carsten Schultz"
@@
 
-Gaelen Guzman^1,^*, Carsten Schulz^1^, Fikadu G. Tafesse^1^
+Gaelen Guzman^1,^*, Frank Stein^2^, Jeremy M. Baskin^3^, Carsten Schulz^1^, Fikadu G. Tafesse^1^
 
-^1^ = Oregon Health & Science University; * = Corresponding author: <gaelen.guzman@lipidinteractome.org>
+^1^ = Departments of Molecular Immunology and Immunology and  Chemical Physiology and Biochemistry, Oregon Health & Science University, Portland, OR, USA; ^2^ = Proteomics Core Facility, European Molecular Biology Laboratory, Heidelberg, Germany; ^3^ = Department of Chemistry and Chemical Biology and Weill Institute for Cell and Molecular Biology, Cornell University, Ithaca, NY, USA; * = Corresponding author: <gaelen.guzman@lipidinteractome.org>
 :::
@@
 
-The Lipid Interactome addresses this gap by providing a structured, interactive site that adheres to FAIR data principles -- ensuring that lipid interactome studies are Findable, Accessible, Interoperable, and Reusable.
+The Lipid Interactome addresses this gap by providing a structured, interactive web portal that adheres to FAIR data principles -- ensuring that lipid interactome studies are Findable, Accessible, Interoperable, and Reusable.
 Through standardized data formatting, interactive visualizations, and direct cross-study comparisons, this resource enables researchers to systematically explore the protein-binding partners of diverse bioactive lipids.
@@
 
-Lipid-protein interactions, proteomics, interactomics, database, multifunctionalized lipids
+Lipid-protein interactions, proteomics, interactomics, database, multifunctionalized lipids, photoaffinity labeling
 
@@
 These probes incorporate strategically designed functional groups that enable covalent crosslinking, affinity enrichment, and controlled activation.
-Most commonly, these include: (1) a diazirine ring for photoactivatable crosslinking upon exposure to 355 nm ultraviolet (UV) light, stabilizing lipid–protein interactions; (2) a terminal alkyne, permitting click chemistry-based enrichment; and, in some cases, (3) a coumarin photocage, which shields the lipid probe from premature enzymatic modification until selectively released by 405 nm light.
+Most commonly, these include: (1) a diazirine group for photoactivatable crosslinking upon exposure to 355 nm ultraviolet (UV) light, stabilizing non-covalent and often modest-affinity lipid–protein interactions; (2) a terminal alkyne, permitting click chemistry-based enrichment; and, in some cases, (3) a coumarin photocage, which shields the lipid probe from premature enzymatic modification until it is selectively cleaved by 405 nm light (a wavelength that does not induce diazirine photolysis).
 Together, these modifications enable direct proteomic identification of lipid interactors, distinguishing true binding partners from transient or non-specific associations[@haberkantFatFabulousBifunctional2014; @schultzChemicalToolsLipid2023; @farleyTrifunctionalSphinganineNew2024a].
 
-Several studies have already employed these lipid probes to elucidate the interactomes of key bioactive lipids, including diacylglycerol, sphingosine, sphinganine, phosphatidic acid, and phosphatidylethanolamine[@hoglingerTrifunctionalLipidProbes2017; @farleyTrifunctionalSphinganineNew2024a; @farleyTrifunctionalFattyAcid2024; @thomasTrifunctionalLipidDerivatives2025].
+Several studies have already employed these lipid probes to elucidate the interactomes of key bioactive lipids, including diacylglycerol, sphingosine, sphinganine, phosphatidic acid, and phosphatidylethanolamine, N-acylphosphatidylethanolamine, and  phosphatidyl alcohol[@hoglingerTrifunctionalLipidProbes2017; @farleyTrifunctionalSphinganineNew2024a; @farleyTrifunctionalFattyAcid2024; @thomasTrifunctionalLipidDerivatives2025; @chiuPhotoaffinityLabelingReveals2025; @yuChemoproteomicsApproachProfile2022].
 These studies have followed a comparative proteomics workflow, wherein crosslinked (“+UV”) and non-crosslinked (“-UV”) samples are analyzed side by side to minimize artifacts and confirm specificity[@haberkantFatFabulousBifunctional2014; @schultzChemicalToolsLipid2023].
@@
 
-By providing a centralized platform for lipid interactome data, the Lipid Interactome significantly lowers the barriers to entry for researchers investigating lipid signaling pathways.
-This repository represents a necessary step toward systematizing lipid–protein interaction studies, ensuring that bioactive lipids are afforded the same level of proteomic scrutiny as their protein counterparts.
+By providing a centralized platform for lipid interactome data, the Lipid Interactome significantly lowers the barriers to entry for researchers investigating lipid signaling pathways, enabling hypothesis generation through comparative analysis of multiple studies.
+Overall, this repository represents an important step toward systematizing lipid–protein interaction studies, ensuring that bioactive lipids are afforded the same level of proteomic scrutiny as their protein counterparts.
 
@@
 By leveraging standardized data formatting and interactive visualization—including study-specific analysis pages, lipid probe aggregation, and cross-study comparisons via a Shiny application—the platform facilitates intuitive exploration of protein–lipid interactions.
-As a living repository, we actively encourage researchers to contribute their findings through our [Data Submission](#) page, ensuring that this resource continues to evolve alongside advancements in lipidomics research.
+As a living repository, we actively encourage researchers to contribute their findings through our [Data Submission](https://www.lipidinteractome.org/contactus/datasubmission) page, ensuring that this resource continues to evolve alongside advancements in lipidomics research.
 
@@
 These pages include interactive Volcano, Ranked-Order, and MA plots, which enable visualization of differential protein enrichment across experimental conditions.
-The plots are rendered using the Plotly and htmlwidgetsR packages, ensuring a responsive, client-side experience that supports zooming, hovering, and data filtering \[REF: Plotly, htmlwidgets\].
+The plots are rendered using the Plotly and htmlwidgetsR packages, ensuring a responsive, client-side experience that supports zooming, hovering, and data filtering[@plotly; @ramnathvaidyanathanHtmlwidgetsHTMLWidgets2015].
 For transparency and reproducibility, all datasets associated with a given study are available for direct download.
@@
 
-While there are numerous ways to quantify the mass spectrometry (MS) data, the studies included in our repository have utilized the same (or highly similar) quantitative MS pipeline using Tandem Mass Tagging\[REF\].
+While there are numerous ways to quantify the mass spectrometry (MS) data, the majority of studies included in our repository have utilized the same (or highly similar) quantitative MS pipeline using Tandem Mass Tagging[@thompsonTandemMassTags2003].
 These datasets include those reported by Farley et al.
@@
 (2025)[@farleyTrifunctionalSphinganineNew2024a; @farleyTrifunctionalFattyAcid2024; @thomasTrifunctionalLipidDerivatives2025].
+Some studies have also featured quantitative MS analysis using stable isotope labeling of amino acids in cell culture (SILAC), which also enables extraction of key data described below[@chiuPhotoaffinityLabelingReveals2025; @yuChemoproteomicsApproachProfile2022].
 Correspondingly, the ideal data structure for incorporation into our repository will include the following:
@@
 The advent of functionalized lipid probes has fundamentally transformed lipid biology by enabling the proteomic identification of lipid-binding proteins with unprecedented specificity.
-However, as the number of published lipid interactome studies grows, the lack of a centralized framework for comparing and integrating these datasets presents a significant challenge.
+However, as the number of published lipid interactome studies grows, the lack of a centralized framework for comparing and integrating these datasets presents a significant challenge for deciphering biological functions of individual lipids and lipid-binding proteins holistically and identifying trends across datasets.
 The Lipid Interactome was developed to address this need by providing researchers with a structured platform to explore, cross-reference, and build upon previous findings.
@@
 
-GG designed, implemented, and wrote the majority of the LipidInteractome site and manuscript.
-FS wrote the data analysis section of the site, provided significant intellectual contribution to the site design, and edited the manuscript.
-AN provided substantial editing of the site and manuscript.
-CS and FT provided significant intellectual contribution and text editing of the site and manuscript, and oversaw the site development.
+GG designed, implemented, and wrote the majority of the LipidInteractome repository and manuscript.
+FS wrote the data analysis section of the repository, provided significant intellectual contribution to the repository design, and edited the manuscript.
+AN provided substantial editing of the repository and manuscript.
+JMB edited the manuscript and contributed data to the repository.
+CS and FT provided significant intellectual contribution and text editing of the repository and manuscript, and oversaw the site development.
 

### 2025-03-31 IndividualStudies/WY_2021.qmd
Adding Yu et al 2021 to yaml, adding JMB edits to manuscript

@@
 
+#### Gene Ontology Analysis
+
+**In beta: GO analysis still under development**
+
+:::::{.border}
+::::{#fig-PE_GOplots}
+::: {.panel-tabset}
+
+##### Cell Compartment
+
+<iframe src="/LipidProbe/GO_plots/PDAA_WY_2021_CC-DOTplot.html" width="100%" height="500px"></iframe>
+
+##### Molecular Function
+
+No enriched molecular functions identified among enriched hits and candidates.
+
+##### Biological Process
+
+No enriched biological processes identified among enriched hits and candidates.
+
+:::
+
+GO Dot plots display the enrichment of GO terms among the proteins enriched to the probe.
+For these analyses, only proteins categorized as "enriched candidates" and "enriched hits" were subject to GO analysis.
+The Cell Compartment analysis assesses whether the list of enriched proteins contains a statistically significant number of proteins in the same cellular region; appropriately, the Molecular Function and Biological Process analyses does the same for molecular function and biological process, respectively.
+[Click here for more information about Gene Ontology Analysis.](/Background/DataAnalysisAndStatistics.qmd#gene-ontology-overview)
+::::
+:::::
+
 ## Data exploration

### 2025-03-31 LipidProbe/Phosphatidylalcohol.qmd
Adding Yu et al 2021 to yaml, adding JMB edits to manuscript

--- 2025-03-31 IndividualStudies/WY_2021.qmd
@@
 ---
-title: "Yu et al. 2021"
-subtitle: "A Chemoproteomics Approach to Profile Phospholipase D-Derived Phosphatidyl Alcohol Interactions"
-date: 2021-12-15
+title: "Phosphatidyl diazirine alkyne alcohol"
+subtitle: "PDAA"
 format: 
@@
     embed-resources: false
-standalone: false
+callout-icon: false
 ---
+
+## Structure
+
+:::{.border}
+::: {layout="[[100], [-25, 50, -25], [100]]"}
+![(A) Native Phosphatidylethanol.](/LipidProbe/Structures/POH.png)
+
+![(B) Diazirine alkyne alcohol.](/LipidProbe/Structures/DAA.png)
+
+![(C) Phosphatidyl diazirine alkyne alcohol (PDAA).](/LipidProbe/Structures/PDAA.png)
+
+Temporary chemical structures drawn by Gaelen Guzman.
+:::
+:::
+
+## Protein Interactome
 
@@
 
-```{r HiddenDataWrangling, include=FALSE, echo=FALSE}
-
-# RawData <- read_csv(here::here("IndividualStudies/DataTables/WY_2021_ACSChemBio_RawData.csv")) |>
-#   filter(Coverage != 0 & Fold_change != 0) |>
-#   mutate(gene_name = gene_name...3) |>
-#   group_by(gene_name) |>
-#   summarise(logFC = mean(log2(Fold_change)),
-#             # pvalue = mean(pvalue),
-#             numReplicates = n(),
-#             AveExpr = log10(mean(Control_abundance) + mean(Sample_abundance)/2)) |>
-#   arrange(-logFC)
-
-# median_logFC <- median(RawData$logFC)
-
-# RawData$logFC <- RawData$logFC - median_logFC
-
-# RawData <- RawData |> 
-#   mutate(LipidProbe = "PDAA",
-#         AveExpr = case_when(.default = AveExpr,
-#                               AveExpr == -Inf ~ 0),
-#                               hit_annotation = case_when(.default = "no hit",
-#                                                           logFC >= 0.5849625 & numReplicates == 2 ~ "enriched candidate",
-#                                                           logFC >= 0.5849625 & numReplicates == 3 ~ "enriched hit")) |>         
-#   glimpse()
-
-# write_csv(RawData, here("IndividualStudies/DataTables/WY_2021_ACSChemBio_Download.csv"))
-
-```
-
-```{r Setup_Data_Wrangling, include=FALSE, echo=FALSE}
+```{r PDAA_setup, include=FALSE, echo=FALSE}
 ## intitialize libraries
@@
 
-## Data visualization
+#### Data visualization
 
@@
 ```{r, echo=FALSE, warning=FALSE}
-#| fig-cap: "Data as reported in [Yu et al., 2021, 2024](/IndividualStudies/WY_2021.qmd).
-Black proteins are identified in only one replicate, Purple enriched candidates are defined as proteins identified in two replicates & fold-change > 1.5 (logFC 0.585) & pvalue < 0.01, and Orange enriched hits are defined as proteins identified in all three replicates & fold-change > 1.5 (logFC 0.585) & pvalue < 0.01)."
+#| fig-cap: "Data as reported in [Farley et al., 2024](/IndividualStudies/SF_2024.qmd).
+Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV)."
 
@@
 
-##### MA plot
+##### MA Plot
 
 ```{r, echo=FALSE, warning=FALSE}
-#| fig-cap: "Data as reported in [Yu et al., 2021](/IndividualStudies/WY_2021.qmd).
-Black proteins are identified in only one replicate, Purple enriched candidates are defined as proteins identified in two replicates & fold-change > 1.5 (logFC 0.585) & pvalue < 0.01, and Orange enriched hits are defined as proteins identified in all three replicates & fold-change > 1.5 (logFC 0.585) & pvalue < 0.01)."
+#| fig-cap: "Data as reported in [Farley et al., 2024](/IndividualStudies/SF_2024.qmd).
+Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV)."
 
 MASpecial(data)
+
 ```
@@
 
-## Data exploration
+#### Data exploration and download
+
+Check the boxes below to filter by significance thresholds.
 
@@
 ```
-
 :::
@@
 
-## Data download
-
-{{< downloadthis DataTables/WY_2021_ACSChemBio_Download.csv dname="WY_2021_ACS-ChemBio_Download">}}
+{{< downloadthis DataSets/PDAA_WY_2021_ACSChemBio_Download.csv dname="PDAA_WY_2021_ACSChemBio_download">}}

### 2025-03-31 LipidProbe/Sphinganine.qmd
putting NAPE on the index
example
adding WY_2021 study, checking if authors like it
Adding Yu et al 2021 to yaml, adding JMB edits to manuscript

@@
 title: "Trifunctional Sphinganine"
-prefer-html: true
-format: html
+format: 
+  html:
+    embed-resources: false
 callout-icon: false
@@
 
+#### Data visualization
+
+::::{.border}
 ::: {.panel-tabset}
@@
 
-:::{.border}
 ```{r, echo=FALSE, warning=FALSE}
@@
 ```
-:::
 
@@
 :::
-:::
+::::
 
-## Gene Ontology Analysis
+#### Gene Ontology Analysis
 

### 2025-03-31 StudyInformation_includes/DCC_2025_include.qmd
Adding Yu et al 2021 to yaml, adding JMB edits to manuscript

@@
 <span class="hover-image">
-  <img src="/LipidProbe/Structures/BF_NAPE.png" alt="Bifunctional NAPE" />
+  <img src="/Structures/BF-NAPE.png" alt="Bifunctional NAPE" />
 </span>

### 2025-03-31 StudyInformation_includes/WY_2021_include.qmd
Adding Yu et al 2021 to yaml, adding JMB edits to manuscript

@@
 
-PDAA
-
-<!-- 
-<a href="/LipidProbe/N-Acylphosphatidylethanolamine.qmd" class="hover-preview">Bifunctional NAPE</a>
+<a href="/LipidProbe/PhosphatidylAlcohol.qmd" class="hover-preview">Phosphatidyl Alcohol</a>
 <span class="hover-image">
-  <img src="/LipidProbe/Structures/BF_NAPE.png" alt="Bifunctional NAPE" />
-</span> -->
+  <img src="/LipidProbe/Structures/PDAA.png" alt="Phosphatidyl diazirine alkyne alcohol" />
+</span>
 

### 2025-03-31 index.qmd
example
Adding Yu et al 2021 to yaml, adding JMB edits to manuscript

@@
           N-Acylphosphatidylethanolamine (NAPE)
+      </button>
+  </a>
+
+  <a href="LipidProbe/PhosphatidylAlcohol.qmd" style="text-decoration: none;">
+      <button style="background-color:rgb(41, 204, 131); color: white; font-size: 20px; padding: 15px 30px; border: none; border-radius: 8px; margin: 10px; cursor: pointer;">
+          Phosphatidyl Alcohol
       </button>

### 2025-03-31 Resources/Run_GO_DOTplots.R

@@ -165,3 +165,16 @@ MF_enrichment_plots(DCC_2025, "dot", "NAPE_DCC_2025_MF-DOTplot")
 
 BP_enrichment_plots(DCC_2025, "dot", "NAPE_DCC_2025_BP-DOTplot")
 # BP_enrichment_plots(AT_2025, "cnet", "PE-PA_AT_2025_BP-CNETplot")
+
+## WY_2021
+
+WY_2021 <- read_csv(here("IndividualStudies/DataTables/WY_2021_ACSChemBio_Download.csv"))
+
+CC_enrichment_plots(WY_2021, "dot", "PDAA_WY_2021_CC-DOTplot")
+# CC_enrichment_plots(AT_2025, "cnet", "PE-PA_AT_2025_CC-CNETplot")
+
+MF_enrichment_plots(WY_2021, "dot", "PDAA_WY_2021_MF-DOTplot")
+# MF_enrichment_plots(AT_2025, "cnet", "PE-PA_AT_2025_MF-CNETplot")
+
+BP_enrichment_plots(WY_2021, "dot", "PDAA_WY_2021_BP-DOTplot")
+# BP_enrichment_plots(AT_2025, "cnet", "PE-PA_AT_2025_BP-CNETplot")

### 2025-03-31 index.qmd
typo on index page

--- 2025-03-25 index.qmd
@@
           N-Acylphosphatidylethanolamine (NAPE)
+      </button>
+  </a>
+
+  <a href="LipidProbe/Phosphatidylalcohol.qmd" style="text-decoration: none;">
+      <button style="background-color:rgb(41, 204, 131); color: white; font-size: 20px; padding: 15px 30px; border: none; border-radius: 8px; margin: 10px; cursor: pointer;">
+          Phosphatidyl Alcohol
       </button>

### 2025-04-01 BioinformaticsApplicationNote/GG_2025_applicationNote.qmd
Fixed the PDAA pages with the new dataset

@@
       - name:  "Oregon Health & Science University"
+        department: Molecular Microbiology and Immunology
         address: 3222 SW Research Dr
@@
     email: gaelen.guzman@lipidinteractome.org
+  - name: "André Nadler"
+    affiliations:
+      - name: "Max Plank Institute"
+        department: "Molecular Cell Biology and Genetics"
+        city: Dresden
+        country: Germany
+        postal-code: 01307
+    orcid: 0000-0001-6329-3910
   - name: "Frank Stein"
     affiliations:
-      - name: "Proteomics Core Facility, European Molecular Biology Laboratory"
+      - name: "European Molecular Biology Laboratory"
+        department: "Proteomics Core Facility"
         city: Heidelberg
@@
     affiliations:
-      - name: "Department of Chemistry and Chemical Biology and Weill Institute for Cell and Molecular Biology, Cornell University"
+      - name: "Cornell University"
+        department: "Department of Chemistry and Chemical Biology and Weill Institute for Cell and Molecular Biology"
         city: Ithaca
@@
         postal-code: 14853
+    orcid: 0000-0003-2939-3138
   - name: "Carsten Schultz"
@@
       - name:  "Oregon Health & Science University"
+        department: "Chemical Physiology and Biochemistry"
         address: 3222 SW Research Dr
@@
 
-Gaelen Guzman^1,^*, Frank Stein^2^, Jeremy M. Baskin^3^, Carsten Schulz^1^, Fikadu G. Tafesse^1^
+Gaelen Guzman^1,^*, André Nadler^2^, Frank Stein^3^, Jeremy M. Baskin^4^, Carsten Schulz^1^, Fikadu G. Tafesse^1^
 
-^1^ = Departments of Molecular Immunology and Immunology and  Chemical Physiology and Biochemistry, Oregon Health & Science University, Portland, OR, USA; ^2^ = Proteomics Core Facility, European Molecular Biology Laboratory, Heidelberg, Germany; ^3^ = Department of Chemistry and Chemical Biology and Weill Institute for Cell and Molecular Biology, Cornell University, Ithaca, NY, USA; * = Corresponding author: <gaelen.guzman@lipidinteractome.org>
+^1^ = Departments of Molecular Immunology and Immunology and  Chemical Physiology and Biochemistry, Oregon Health & Science University, Portland, OR, USA; ^2^ = Max Plank Institute of Molecular Cell Biology and Genetics, Dresden Germany; ^3^ = Proteomics Core Facility, European Molecular Biology Laboratory, Heidelberg, Germany; ^4^ = Department of Chemistry and Chemical Biology and Weill Institute for Cell and Molecular Biology, Cornell University, Ithaca, NY, USA; * = Corresponding author: <gaelen.guzman@lipidinteractome.org>
 :::
@@
 
+## Funding
+
+This work was supported by funding from the National Institutes of Health (NIAID R01 AI141549-02, to FGT, CS; NIGMS R01 GM 127631 to C.S., and R01 GM151682 to JMB).
+
 ## Conflicts of Interest

### 2025-04-01 IndividualStudies/WY_2021.qmd
Fixed the PDAA pages with the new dataset

@@
 
-```{r NewPlottingFunctions, include=FALSE, echo=FALSE}
-RankedOrderPlotSpecial <- function(data) {
-    ################
-    #' A standardized Ranked Order plot theme
-    #' Requires an input dataframe with the columns "gene_name", "LipidProbe", "logFC", "pvalue", and "hit_annotation"
-    ################
-
-    # Applies ID column to each probe
-    data <- data |>
-      group_by(LipidProbe) |>
-      arrange(logFC, .by_group = TRUE) |>
-      mutate(ID = row_number()) |>
-      ungroup()
-
-    # First makes a ggplot template to later apply ggplotly
-    RankedOrderPlots <- data |>
-        ggplot(aes(x = ID,
-                   y = logFC,
-                   color = factor(hit_annotation),
-                   fill = factor(hit_annotation),
-                   shape = factor(hit_annotation),
-                   alpha = factor(hit_annotation),
-                   size = factor(hit_annotation))) +
-        geom_point(aes(text = paste0("Gene name: ", gene_name, "\n",
-                                    "LogFC: ", logFC, "\n"))) +
-        geom_hline(yintercept = 0, linetype = 2) +
-        geom_vline(xintercept = 0, linetype = 2) +
-        scale_shape_manual(values = c("enriched hit" = 21,
-                                    "hit" = 21,
-                                    "enriched candidate" = 24,
-                                    "candidate" = 24,
-                                    "no hit" = 22), 
-                        name = "Trend") +
-        scale_color_manual(values = c("enriched hit" = "black",
-                                    "hit" = "black",
-                                    "enriched candidate" = "black",
-                                    "candidate" = "black",
-                                    "no hit" = "black"), 
-                        name = "Trend") +
-        scale_fill_manual(values = c("enriched hit" = "orange",
-                                    "hit" = "orange",
-                                    "enriched candidate" = "purple",
-                                    "candidate" = "purple",
-                                    "no hit" = "black"), 
-                        name = "Trend") +
-        scale_alpha_manual(values = c("enriched hit" = 0.8,
-                                    "hit" = 0.8,
-                                    "enriched candidate" = 0.5,
-                                    "candidate" = 0.5,
-                                    "no hit" = 0.25), 
-                        name = "Trend") +
-        scale_size_manual(values = c("enriched hit" = 4,
-                                    "hit" = 4,
-                                    "enriched candidate" = 2,
-                                    "candidate" = 2, 
-                                    "no hit" = 0.75), 
-                        name = "Trend") +
-        facet_wrap(~LipidProbe) +
-        ylab("Log2 fold-change") +
-        xlab("Ranked-order gene") +
-        theme_minimal() +
-        theme(text = element_text(family = "serif")) +
-        theme(panel.border = element_rect(color = NA, fill = NA)) +
-        theme(legend.title = element_text(size = 12, face = "bold")) +
-        theme(axis.title = element_text(size = 12, face = "bold")) +
-        theme(legend.text = element_text(size = 12))  +
-        theme(strip.text = element_text(
-    size = 20))
-    m <- list(l=50, r = 50, b= 100, pad = 4)
-
-    RankedOrderPlotly <- ggplotly(RankedOrderPlots,
-                            tooltip = c("text", dynamicTicks = TRUE),
-                            hovermode = "closest",
-                            autosize = T,
-                            margin = m) |>
-                    layout(showlegend = FALSE)
-
-    return(RankedOrderPlotly)
-}
-
-MASpecial <- function(data) {
-
-    ################
-    #' A standardized MA plot function
-    #' Receives a dataframe. Needs to have the following columns for the aes() to work: AveExpr, logFC, hit_annotation, gene_name.
-    #' Dynamically determines the limits of the plot under the scale_x/y_scontinuous calls
-    #' Produces first a facet-wrapped ggplot, then converts it to a plotly plot.
-    ################
-
-    MAPlots <- data |>
-        ggplot(aes(x = AveExpr,
-                   y = logFC,
-                   color = factor(hit_annotation),
-                   fill = factor(hit_annotation),
-                   shape = factor(hit_annotation),
-                   alpha = factor(hit_annotation),
-                   size = factor(hit_annotation))) +
-        geom_point(aes(text = paste0("Gene name: ", gene_name, "\n",
-                                    "LogFC: ", logFC, "\n",
-                                    "AveExpr: ", AveExpr, "\n"))) +
-        geom_hline(yintercept = 0, linetype = 2) +
-        geom_vline(xintercept = 0, linetype = 2) +
-        scale_x_continuous(limits = c(0.9 * min(abs(data$AveExpr)), 1.1 * max(abs(data$AveExpr))))+
-        scale_y_continuous(limits = c(-1.1 * max(abs(data$logFC)), 5))+
-        scale_shape_manual(values = c("enriched hit" = 21,
-                                    "hit" = 21,
-                                    "enriched candidate" = 24,
-                                    "candidate" = 24,
-                                    "no hit" = 22), 
-                        name = "Trend") +
-        scale_color_manual(values = c("enriched hit" = "black",
-                                    "hit" = "black",
-                                    "enriched candidate" = "black",
-                                    "candidate" = "black",
-                                    "no hit" = "black"), 
-                        name = "Trend") +
-        scale_fill_manual(values = c("enriched hit" = "orange",
-                                    "hit" = "orange",
-                                    "enriched candidate" = "purple",
-                                    "candidate" = "purple",
-                                    "no hit" = "black"), 
-                        name = "Trend") +
-        scale_alpha_manual(values = c("enriched hit" = 0.8,
-                                    "hit" = 0.8,
-                                    "enriched candidate" = 0.5,
-                                    "candidate" = 0.5,
-                                    "no hit" = 0.25), 
-                        name = "Trend") +
-        scale_size_manual(values = c("enriched hit" = 4,
-                                    "hit" = 4,
-                                    "enriched candidate" = 2,
-                                    "candidate" = 2, 
-                                    "no hit" = 0.75), 
-                        name = "Trend") +
-        facet_wrap(~LipidProbe) +
-        ylab("Log2 fold-change") +
-        xlab("Average Ion Intensity") +
-        theme_minimal() +
-        theme(text = element_text(family = "serif")) +
-        theme(panel.border = element_rect(color = NA, fill = NA)) +
-        theme(legend.title = element_text(size = 12, face = "bold")) +
-        theme(axis.title = element_text(size = 12, face = "bold")) +
-        theme(legend.text = element_text(size = 12)) +
-        theme(strip.text = element_text(
-    size = 20))
-
-    m <- list(l=50, r = 50, b= 100, pad = 4)
-
-    MAPlotly <- ggplotly(MAPlots,
-                            tooltip = c("text", dynamicTicks = TRUE),
-                            hovermode = "closest",
-                            autosize = T,
-                            margin = m) |>
-                    layout(showlegend = FALSE)
-
-    return(MAPlotly)
-}
-
-```
-
-```{r HiddenDataWrangling, include=FALSE, echo=FALSE}
-
-# RawData <- read_csv(here::here("IndividualStudies/DataTables/WY_2021_ACSChemBio_RawData.csv")) |>
-#   filter(Coverage != 0 & Fold_change != 0) |>
-#   mutate(gene_name = gene_name...3) |>
-#   group_by(gene_name) |>
-#   summarise(logFC = mean(log2(Fold_change)),
-#             # pvalue = mean(pvalue),
-#             numReplicates = n(),
-#             AveExpr = log10(mean(Control_abundance) + mean(Sample_abundance)/2)) |>
-#   arrange(-logFC)
-
-# median_logFC <- median(RawData$logFC)
-
-# RawData$logFC <- RawData$logFC - median_logFC
-
-# RawData <- RawData |> 
-#   mutate(LipidProbe = "PDAA",
-#         AveExpr = case_when(.default = AveExpr,
-#                               AveExpr == -Inf ~ 0),
-#                               hit_annotation = case_when(.default = "no hit",
-#                                                           logFC >= 0.5849625 & numReplicates == 2 ~ "enriched candidate",
-#                                                           logFC >= 0.5849625 & numReplicates == 3 ~ "enriched hit")) |>         
-#   glimpse()
-
-# write_csv(RawData, here("IndividualStudies/DataTables/WY_2021_ACSChemBio_Download.csv"))
-
-```
-
 ```{r Setup_Data_Wrangling, include=FALSE, echo=FALSE}
@@
 library(here)
-library(biomaRt)
-library(rentrez)
+library(limma)
 
@@
 
+```{r WY_2025_seriousDataWrangling, include=FALSE, echo=FALSE}
+
+# # RawData <- read_csv(here::here("IndividualStudies/DataTables/WY_2021_ACSChemBio_RawData2.csv"))
+
+# filtered_data <- RawData |> 
+#   filter(if_all(starts_with("Control_"), ~ !is.na(.) & . != 0) & 
+#          if_all(starts_with("Sample_"), ~ !is.na(.) & . != 0)) |>
+#   arrange(-Control_1)
+
+# # Convert wide format to long format
+# long_data <- filtered_data |> 
+#   pivot_longer(cols = -gene_name, 
+#                names_to = c("Condition", "Replicate"), 
+#                names_sep = "_", 
+#                values_to = "Abundance") |> 
+#   mutate(Condition = ifelse(Condition == "Control", "Control", "Sample"))
+
+# # Count the number of observations per gene per condition
+# complete_genes <- long_data |> 
+#   filter(if_all(starts_with("Abundance"), ~ !is.na(.))) |> # Keep only genes with full data in both groups
+#   group_by(gene_name, Condition) |> 
+#   summarise(count = n(), .groups = "drop") |> 
+#   pivot_wider(names_from = Condition, values_from = count, values_fill = 0) |> 
+#   filter(Control == 3 & Sample == 3) |>  
+#   pull(gene_name)
+
+# # Filter the original dataset to include only these complete genes
+# filtered_data <- long_data |> 
+#   filter(gene_name %in% complete_genes)
+
+# # Run t-test for each gene
+# t_test_results <- filtered_data |> 
+#   group_by(gene_name) |> 
+#   summarise(
+#     pvalue = t.test(Abundance[Condition == "Sample"], 
+#                      Abundance[Condition == "Control"], 
+#                      var.equal = TRUE)$p.value,
+#     logFC = log2(mean(Abundance[Condition == "Sample"]) / mean(Abundance[Condition == "Control"]))
+#   ) |> 
+#   mutate(adj_p_value = p.adjust(pvalue, method = "BH"),
+#           LipidProbe = "PDAA",
+#           hit_annotation = case_when(.default = "no hit",
+#                                       logFC > log2(1.5) &  pvalue < 0.05 ~ "enriched hit"))  # Adjust p-values for multiple testing
+
+# averaged_data <- filtered_data |> 
+#   group_by(gene_name) |>
+#   summarise(AveExpr = log10(mean(Abundance)))
+
+# data <- t_test_results |>
+#   left_join(averaged_data)
+
+# # write_csv(data, here("IndividualStudies/DataTables/WY_2021_ACSChemBio_Download.csv"))
+
+```
+
 ## Data visualization
@@
 
+##### Volcano plots
+
+```{r, echo=FALSE, warning=FALSE}
+#| fig-cap: "Volcano plots depict the relative enrichment of each protein versus non-crosslinked control (x-axis) and the statistical significance of each protein following a Student's t-test (y-axis, -log10 transformed).
+Black proteins are designated as not statistically significant.
+Orange \"enriched hit\" denotes proteins with fold-changes > 1.5 (logFC > 0.5) pvalue < 0.05.
+Only proteins identified in all three replicates are displayed."
+
+VolcanoPlotStandardized(data)
+
+```
+
 ##### Ranked order plot
@@
 #| fig-cap: "Data as reported in [Yu et al., 2021, 2024](/IndividualStudies/WY_2021.qmd).
-Black proteins are identified in only one replicate, Purple enriched candidates are defined as proteins identified in two replicates & fold-change > 1.5 (logFC 0.585) & pvalue < 0.01, and Orange enriched hits are defined as proteins identified in all three replicates & fold-change > 1.5 (logFC 0.585) & pvalue < 0.01)."
+Black proteins are designated as not statistically significant.
+Orange \"enriched hit\" denotes proteins with fold-changes > 1.5 (logFC > 0.5) pvalue < 0.05.
+Only proteins identified in all three replicates are displayed."
 
-RankedOrderPlotSpecial(data)
+RankedOrderPlotStandard(data)
 ```
@@
 #| fig-cap: "Data as reported in [Yu et al., 2021](/IndividualStudies/WY_2021.qmd).
-Black proteins are identified in only one replicate, Purple enriched candidates are defined as proteins identified in two replicates & fold-change > 1.5 (logFC 0.585) & pvalue < 0.01, and Orange enriched hits are defined as proteins identified in all three replicates & fold-change > 1.5 (logFC 0.585) & pvalue < 0.01)."
+Black proteins are designated as not statistically significant.
+Orange \"enriched hit\" denotes proteins with fold-changes > 1.5 (logFC > 0.5) pvalue < 0.05.
+Only proteins identified in all three replicates are displayed."
 
-MASpecial(data)
+MAStandard(data)
 ```
 
-##### Venn Diagram
+<!-- ##### Venn Diagram -->
 
@@
 
-###### Wrangling for the Venn Diagram ######
-# Read the dataset
+# ###### Wrangling for the Venn Diagram ######
+# # Read the dataset
 
-VennData <- read_csv(here("IndividualStudies/DataTables/WY_2021_ACSChemBio_RawData.csv")) |>
-  mutate(gene_name = gene_name...3)
+# VennData <- read_csv(here("IndividualStudies/DataTables/WY_2021_ACSChemBio_RawData2.csv"))
 
-# Separates out each of the genesets, then forces them back together in a vectorized list.
-A_proteins <- VennData |>
-  filter(Trial == 1) |>
-  dplyr::select(gene_name)
+# # Convert wide format to long format
+# VennData <- VennData |> 
+#   mutate(logFC_1 = log2(Sample_1 / Control_1),
+#          logFC_2 = log2(Sample_2 / Control_2),
+#          logFC_3 = log2(Sample_3 / Control_3)) |>
+#   pivot_longer(cols = c(8,9,10)) |>
+#   select(gene_name, name, value) |>
+#   filter(!is.na(value)) |> 
+#   mutate(Replicate = case_when(name == "logFC_1" ~ 1,
+#                                name == "logFC_2" ~ 2,
+#                                name == "logFC_3" ~ 3))
 
-B_proteins <- VennData |>
-  filter(Trial == 2) |>
-  dplyr::select(gene_name)
+# # Separates out each of the genesets, then forces them back together in a vectorized list.
+# A_proteins <- VennData |>
+#   filter(Replicate == 1) |>
+#   dplyr::select(gene_name)
 
-C_proteins <- VennData |>
-  filter(Trial == 3) |>
-  dplyr::select(gene_name)
+# B_proteins <- VennData |>
+#   filter(Replicate == 2) |>
+#   dplyr::select(gene_name)
 
-VennList <- list("Trial 1" = as.list(A_proteins$gene_name), "Trial 2" = as.list(B_proteins$gene_name), "Trial 3" = as.list(C_proteins$gene_name))
+# C_proteins <- VennData |>
+#   filter(Replicate == 3) |>
+#   dplyr::select(gene_name)
+
+# VennList <- list("Trial 1" = as.list(A_proteins$gene_name), "Trial 2" = as.list(B_proteins$gene_name), "Trial 3" = as.list(C_proteins$gene_name))
 ```
 
-```{r NAPE_Venn, echo=FALSE, warning=FALSE}
-#| fig-cap: "Data as reported in [Yu et al., 2021](/IndividualStudies/WY_2021.qmd). A Venn diagram depicts the overlapping identification of proteins between the three trials (replicates)."
+```{r NAPE_Venn, include=FALSE, echo=FALSE, warning=FALSE}
+# #| fig-cap: "Data as reported in [Yu et al., 2021](/IndividualStudies/WY_2021.qmd). A Venn diagram depicts the overlapping identification of proteins between the three trials (replicates)."
 
-ggvenn <- ggvenn(VennList,
-                      show_percentage = FALSE,
-                      show_elements = FALSE,
-                      fill_color = c("orange", "purple", "blue")) +
-        labs(x = "", y = "") +
-        theme_minimal()
+# ggvenn <- ggvenn(VennList,
+#                       show_percentage = FALSE,
+#                       show_elements = FALSE,
+#                       fill_color = c("orange", "purple", "blue")) +
+#         labs(x = "", y = "") +
+#         theme_minimal()
 
-ggvenn
+# ggvenn
 
@@
 data <- data |>
-  dplyr::select(gene_name, LipidProbe, hit_annotation, logFC, numReplicates) |>
+  dplyr::select(gene_name, LipidProbe, hit_annotation, logFC, pvalue) |>
   mutate(logFC = signif(logFC, digits=3)) |>
+  mutate(pvalue = signif(pvalue, digits=3)) |>
   arrange(-logFC) |>
@@
 Check the boxes below to filter the dataset by which lipid probe was used in the pulldown and by significance thresholds.
-logFC ratios are median normalized.
-\"Num Replicate IDs\" denotes the number of replicates in which the protein was identified.
-As above, \"enriched hit\" denotes proteins identified in all three replicates & fold-change > 1.5 (logFC 0.585) & pvalue < 0.01.
-\"enriched candidates\" are proteins identified in two replicates & fold-change > 1.5 (logFC 0.585) & pvalue < 0.01.",
+\"enriched hit\" denotes proteins with fold-changes > 1.5 (logFC > 0.5) pvalue < 0.05.
+Only proteins identified in all three replicates are displayed.",
           options = list(pageLength = 10),
-                         colnames = c("Gene Name", "Lipid Probe", "Hit Annotation", "LogFC", "Num Replicate IDs"),
+                         colnames = c("Gene Name", "Lipid Probe", "Hit Annotation", "LogFC", "p value"),
                          rownames=FALSE)

### 2025-04-01 _site/LipidProbe/PhosphatidylAlcohol.qmd
Fixed the PDAA pages with the new dataset

--- 2025-04-01 IndividualStudies/WY_2021.qmd
@@
 
-```{r Setup_Data_Wrangling, include=FALSE, echo=FALSE}
+```{r PDAA_setup, include=FALSE, echo=FALSE}
 ## intitialize libraries
 library(here)
-library(limma)
+library(biomaRt)
+library(rentrez)
 
@@
 
-```{r WY_2025_seriousDataWrangling, include=FALSE, echo=FALSE}
-
-# # RawData <- read_csv(here::here("IndividualStudies/DataTables/WY_2021_ACSChemBio_RawData2.csv"))
-
-# filtered_data <- RawData |> 
-#   filter(if_all(starts_with("Control_"), ~ !is.na(.) & . != 0) & 
-#          if_all(starts_with("Sample_"), ~ !is.na(.) & . != 0)) |>
-#   arrange(-Control_1)
-
-# # Convert wide format to long format
-# long_data <- filtered_data |> 
-#   pivot_longer(cols = -gene_name, 
-#                names_to = c("Condition", "Replicate"), 
-#                names_sep = "_", 
-#                values_to = "Abundance") |> 
-#   mutate(Condition = ifelse(Condition == "Control", "Control", "Sample"))
-
-# # Count the number of observations per gene per condition
-# complete_genes <- long_data |> 
-#   filter(if_all(starts_with("Abundance"), ~ !is.na(.))) |> # Keep only genes with full data in both groups
-#   group_by(gene_name, Condition) |> 
-#   summarise(count = n(), .groups = "drop") |> 
-#   pivot_wider(names_from = Condition, values_from = count, values_fill = 0) |> 
-#   filter(Control == 3 & Sample == 3) |>  
-#   pull(gene_name)
-
-# # Filter the original dataset to include only these complete genes
-# filtered_data <- long_data |> 
-#   filter(gene_name %in% complete_genes)
-
-# # Run t-test for each gene
-# t_test_results <- filtered_data |> 
-#   group_by(gene_name) |> 
-#   summarise(
-#     pvalue = t.test(Abundance[Condition == "Sample"], 
-#                      Abundance[Condition == "Control"], 
-#                      var.equal = TRUE)$p.value,
-#     logFC = log2(mean(Abundance[Condition == "Sample"]) / mean(Abundance[Condition == "Control"]))
-#   ) |> 
-#   mutate(adj_p_value = p.adjust(pvalue, method = "BH"),
-#           LipidProbe = "PDAA",
-#           hit_annotation = case_when(.default = "no hit",
-#                                       logFC > log2(1.5) &  pvalue < 0.05 ~ "enriched hit"))  # Adjust p-values for multiple testing
-
-# averaged_data <- filtered_data |> 
-#   group_by(gene_name) |>
-#   summarise(AveExpr = log10(mean(Abundance)))
-
-# data <- t_test_results |>
-#   left_join(averaged_data)
-
-# # write_csv(data, here("IndividualStudies/DataTables/WY_2021_ACSChemBio_Download.csv"))
-
-```
-
-## Data visualization
+#### Data visualization
 

### 2025-04-01 BioinformaticsApplicationNote/GG_2025_applicationNote.qmd
Updating Application Note manuscript

@@
 
-Lipids are more than passive structural components of cellular membranes—they are active participants in signaling pathways, cellular homeostasis, organellar communications, and membrane dynamics.
-Despite their critical biological roles, lipid–protein interactions have historically been challenging to study.
-The small size and biophysical properties of lipids make conventional proteomics approaches unsuitable for mapping their interactors.
-Unlike proteins, which can be readily tagged or immobilized for affinity-based interaction studies, lipids require specialized chemical modifications to enable selective and controlled interaction profiling.
+Historically, lipids have been considered merely the passive structural components of cellular membranes.
+However, recent decades have revealed that this diverse category of biomolecule plays essential and active roles in the cell, ranging from modulating membrane dynamics, determining organelle identity, serving as catabolites for energy storage and metabolism, and bioactive signaling mediators for organellar and intracellular signaling[@barischMembraneDamageRepair2023; @vanmeerMembraneLipidsWhere2008a; @holthuisLipidLandscapesPipelines2014a; @niphakisGlobalMapLipidBinding2015a; @chernomordikProteinLipidInterplayFusion2003; @simonsLipidRaftsSignal2000a].
+Interactions with proteins are essential to many of these crucial lipid functions -- and yet, lipid–protein interactions are extremely challenging to study: The small size and biophysical properties of lipids make conventional proteomics approaches unsuitable for mapping lipid interactors[@schultzChemicalToolsLipid2023].
+Unlike proteins, which can be readily tagged or immobilized for affinity-based interaction studies, lipids require specialized chemical modifications to enable selective and controlled interaction profiling[@schultzFlashClickMultifunctionalized2022a].
 
-Recent advances in developing multifunctionalized lipid analogs have revolutionized the field, enabling the systematic interrogation of lipid interactomes.
+Recent advances in developing multifunctionalized lipid analogs have revolutionized the field, enabling the systematic interrogation of lipid interactomes[@schultzFlashClickMultifunctionalized2022a].
 These probes incorporate strategically designed functional groups that enable covalent crosslinking, affinity enrichment, and controlled activation.
-Most commonly, these include: (1) a diazirine group for photoactivatable crosslinking upon exposure to 355 nm ultraviolet (UV) light, stabilizing non-covalent and often modest-affinity lipid–protein interactions; (2) a terminal alkyne, permitting click chemistry-based enrichment; and, in some cases, (3) a coumarin photocage, which shields the lipid probe from premature enzymatic modification until it is selectively cleaved by 405 nm light (a wavelength that does not induce diazirine photolysis).
+Most commonly, these include: (1) a diazirine group for photoactivatable crosslinking upon exposure to 355 nm ultraviolet (UV) light, stabilizing non-covalent and often modest-affinity lipid–protein interactions; (2) a terminal alkyne, permitting click chemistry-based enrichment; and, in some cases, (3) a coumarin photocage, which shields the lipid probe from premature enzymatic modification until it is selectively cleaved by 405 nm light (a wavelength that does not induce diazirine photolysis)[@schultzFlashClickMultifunctionalized2022a; @schultzChemicalToolsLipid2023; @hoglingerTrifunctionalLipidProbes2017; @haberkantFatFabulousBifunctional2014].
 Together, these modifications enable direct proteomic identification of lipid interactors, distinguishing true binding partners from transient or non-specific associations[@haberkantFatFabulousBifunctional2014; @schultzChemicalToolsLipid2023; @farleyTrifunctionalSphinganineNew2024a].
@@
 Several studies have already employed these lipid probes to elucidate the interactomes of key bioactive lipids, including diacylglycerol, sphingosine, sphinganine, phosphatidic acid, and phosphatidylethanolamine, N-acylphosphatidylethanolamine, and  phosphatidyl alcohol[@hoglingerTrifunctionalLipidProbes2017; @farleyTrifunctionalSphinganineNew2024a; @farleyTrifunctionalFattyAcid2024; @thomasTrifunctionalLipidDerivatives2025; @chiuPhotoaffinityLabelingReveals2025; @yuChemoproteomicsApproachProfile2022].
-These studies have followed a comparative proteomics workflow, wherein crosslinked (“+UV”) and non-crosslinked (“-UV”) samples are analyzed side by side to minimize artifacts and confirm specificity[@haberkantFatFabulousBifunctional2014; @schultzChemicalToolsLipid2023].
+These initial studies have followed a comparative proteomics workflow, wherein crosslinked (“+UV”) and non-crosslinked (“-UV”) samples are analyzed side by side to minimize artifacts and confirm specificity[@haberkantFatFabulousBifunctional2014; @schultzChemicalToolsLipid2023].
 However, despite the growing number of lipid interactome datasets, no centralized resource has existed to compile, compare, and standardize these findings.
 
-To address this gap, we present the Lipid Interactome database -- a curated repository designed to facilitate the comparative analysis of lipid–protein interactions from multiple studies.
+To address this gap, we present the [Lipid Interactome](https://www.lipidinteractome.org) -- a curated repository designed to facilitate the comparative analysis of lipid–protein interactions from multiple studies.
 This resource consolidates proteomics data from multifunctional lipid probes, enabling researchers to efficiently explore and contextualize lipid-binding proteins across different lipid species and cellular models.
-Currently, the repository hosts interactomes derived from trifunctionalized phosphatidic acid, phosphatidylethanolamine, sphingosine, and sphinganine in HeLa and Huh7 cells[@thomasTrifunctionalLipidDerivatives2025; @farleyTrifunctionalSphinganineNew2024a].
+Currently, the repository hosts interactomes derived from trifunctionalized phosphatidic acid, phosphatidylethanolamine, N-acylphosphatidylethanolamine, phosphatidyl alcohol, sphingosine, and sphinganine in HeLa and Huh7 cells[@thomasTrifunctionalLipidDerivatives2025; @chiuPhotoaffinityLabelingReveals2025; @yuChemoproteomicsApproachProfile2022; @farleyTrifunctionalSphinganineNew2024a].
 Additionally, it includes control datasets from two fatty acid probes to distinguish specific from non-specific lipid-binding proteins[@farleyTrifunctionalFattyAcid2024].
+We additionally intend to expand this resource to include more complex experimental designs as they are published (e.g.
+Disease versus Healthy Control or Infection versus Mock).
 
@@
 Each page seamlessly integrates R-generated figures, embedding scripts directly into the source material to ensure reproducibility and transparency.
-The repository currently hosts data from five published studies, with an expandable framework that supports the incorporation of future datasets as the field progresses.
+The repository currently hosts data from seven published studies, with an expandable framework that supports the incorporation of future datasets as the field progresses.
 
@@
 UV
-: *U*ltra *V*iolet
+: *U*ltra*V*iolet
 
@@
 JMB edited the manuscript and contributed data to the repository.
-CS and FT provided significant intellectual contribution and text editing of the repository and manuscript, and oversaw the site development.
+CS and FT provided significant intellectual contribution and text editing of the repository and manuscript and oversaw the site development.
 
@@
 
-This work was supported by funding from the National Institutes of Health (NIAID R01 AI141549-02, to FGT, CS; NIGMS R01 GM 127631 to C.S., and R01 GM151682 to JMB).
+This work was supported by funding from the National Institutes of Health (NIAID R01 AI141549-02, to FGT, CS; NIGMS R01 GM127631 to C.S., and NIGMS R01 GM151682 to JMB).
 

### 2025-04-01 Resources/Run_GO_DOTplots.R

@@ -144,7 +144,6 @@ BP_enrichment_plots(AT_2025, "dot", "PE-PA_AT_2025_BP-DOTplot")
 
 # DCC_2025
 
-/Users/gaelenguzman/LipidInteractomics_Website_local/LipidInteractomics_Website/IndividualStudies/DataTables/DCC_2025_ChemrXiv_FilteredDataset.csv
 
 DCC_2025 <- readr::read_csv(paste0(here(), "/IndividualStudies/DataTables/DCC_2025_ChemrXiv_FilteredDataset.csv")) |>
   group_by(gene_name) |>
@@ -170,11 +169,11 @@ BP_enrichment_plots(DCC_2025, "dot", "NAPE_DCC_2025_BP-DOTplot")
 
 WY_2021 <- read_csv(here("IndividualStudies/DataTables/WY_2021_ACSChemBio_Download.csv"))
 
-CC_enrichment_plots(WY_2021, "dot", "PDAA_WY_2021_CC-DOTplot")
+CC_enrichment_plots(WY_2021, "dot", "/LipidProbe/GO_plots/PDAA_WY_2021_CC-DOTplot")
 # CC_enrichment_plots(AT_2025, "cnet", "PE-PA_AT_2025_CC-CNETplot")
 
-MF_enrichment_plots(WY_2021, "dot", "PDAA_WY_2021_MF-DOTplot")
+MF_enrichment_plots(WY_2021, "dot", "/LipidProbe/GO_plots/PDAA_WY_2021_MF-DOTplot")
 # MF_enrichment_plots(AT_2025, "cnet", "PE-PA_AT_2025_MF-CNETplot")
 
-BP_enrichment_plots(WY_2021, "dot", "PDAA_WY_2021_BP-DOTplot")
+BP_enrichment_plots(WY_2021, "dot", "/LipidProbe/GO_plots/PDAA_WY_2021_BP-DOTplot")
 # BP_enrichment_plots(AT_2025, "cnet", "PE-PA_AT_2025_BP-CNETplot")

### 2025-04-01 Resources/ggplot_styles.R

@@ -308,6 +308,8 @@ VolcanoPlotStandardized <- function(data) {
     return(VolcanoPlotly)
 }
 
+data <- read_csv(here("IndividualStudies/DataTables/WY_2021_ACSChemBio_Download.csv"))
+
 CC_enrichment_plots <- function(data, plotReturnType, filename){
 
 	################

### 2025-04-08 Background/DataAnalysisAndStatistics.qmd
adding SILAC overview

@@
 
-## TMT quantitative mass spec pipeline {#sec-DataAnalysis_TMTPipeline}
+## TMT quantitative mass spectrometry pipeline {#sec-DataAnalysis_TMTPipeline}
 
@@
 A value greater than 1 suggests that a given GO term is more prevalent in our dataset than expected by chance.
+
+## SILAC quantitative and mass spectrometry pipeline {#sec-SILAC_DataAnalysis}
+
+In this repository, only one dataset utilized SILAC to quantify protein interactors, [Chiu et al.
+2025](/IndividualStudies/DCC_2025.qmd), and so an *ad hoc* method was applied to coerce the data into the framework of the standardized data visualizations of the site.
+The results are as reported in Chiu et al.
+2025[@chiuPhotoaffinityLabelingReveals2025].
 

### 2025-04-08 Background/ProteomicsUsingMultifunctionalProbes.qmd
adding SILAC overview

@@
 
+An early (and still used) form of isotopic labeling was known as Stable Isotope Labeling with Amino acids in Cell culture (SILAC).
+This method allows for quantification of the relative protein abundances between two or three conditions in cell culture.
+
 Modern isotopic label-based techniques such as iTRAQ (isotopic Tagging for Relative and Absolute  Quantification) and TMT (Tandem Mass Tagging) have become the norm.
@@
 
-##### How It Works
+##### How SILAC Works:
 
-1.  **Chemical Labeling:** Each sample is chemically tagged with a unique TMT label, which consists of a reactive group binding to peptides and a mass reporter for sample differentiation.
+1.
+**Isotopic Labeling:** Independent cell culturing conditions are pre-treated with media containing with differing amino acid composition, encoding the peptides of each condition with either "heavy" arginine and lysine residues (containing C~13~ isotopes) or "light" (containing a standard proportion of C~12~ isotopes).
+Media treatments are typically for several days or weeks to allow for substantial incorporation of heavy/light labeled isotopes into cells (this is typically dependent on the rate of cell division).
+
+2.
+**Experimental conditions:** After isotopic labeling, the experimental conditions can be applied.
+In the case of lipid probe interactions studies, one would treat the cells with probe, and either uncage via UV irradiation or leave caged for control.
+The cells are then collected, lysed and protein is collected.
+
+3. **Sample pooling:** After protein collection, samples can be pooled, digested, and desalted.
+
+4. **Mass Spectrometry Analysis:**
+
+  -   **MS1 (Peptide Isolation):** Heavy and Light peptides will differ in m/z depending on their composition of lysine and arginine (a heavy peptide with a single lysine residue will be 6 daltons heavier than its light counterpart).
+These Heavy/Light peptide pairs will be isolated independently for MS2 analysis.
+
+    -   **MS2 (Peptide Sequencing & Tag Fragmentation):** Peptides are fragmented for sequence identification.
+
+5.
+**Quantification:** The relative abundance of a given peptide can be calculated from the Heavy/Light MS1 ratio -- thus, the quantification data is collected at the MS1 level, and is limited by the MS1 duty cycle.
+For this reason, SILAC can have a high sensitivity to abundant peptides "swamping" the signal of less abundant peptides.
+A high degree of fractionation is frequently needed to maximize protein identifications.
+
+6.
+**Comparison and Statistics:** The fold-change in protein abundance is directly encoded in the Heavy/Light ratio of SILAC peptide pairs.
+Typically a Student's t-test can be used to calculate the statistical significance of each protein.
+
+##### Advantages of SILAC
+
+- **Simple and Robust:** Because the isotopic labeling is accomplished via media feeding, there are no challenging chemical reactions and a high degree of incorporation can be achieved reliably *in vitro*.
+Similarly, the sample pooling occurs at a very early stage in the sample preparation process, limiting any biasing losses of one sample or its control.
+
+##### Disadvantages/Limitations of SILAC
+
+- **Long Label Incorporation Time:** Because the rate of label incorporation is dependent on the cell division rate, slowly-dividing cells (e.g.
+neurons, organoids) can be prohibitively expensive to perform.
+
+- **Low Factor of Multiplexing:** As of this writing, only two or three conditions can be compared within a single multiplex cassette.
+
+- **MS1 Quantification Sacrifices Protein IDs:** Because SILAC quantification is at the MS1 level, one can only acquire data for half as many unique peptide IDs (or one third, in the case of Triple SILAC).
+
+- **Limited to Laboratory Samples:** Because the samples must be pre-treated with heavy or light media, only cell cultures or small lab animals are conducive to SILAC analysis.
+It is impossible (or prohibitively expensive) to investigate biopsied human samples or larger tissues using SILAC.
+
+##### SILAC Conclusion
+
+While SILAC is a powerful technique, its limitations have resulted in a general reduction in its use in interaction experiments.
+Among the datasets presented in this repository at the time of writing, only the dataset presented in [Chiu et al.
+2025](/IndividualStudies/DCC_2025.qmd) was prepared using SILAC[@chiuPhotoaffinityLabelingReveals2025].
+
+##### How TMT & iTRAQ Work:
+
+1.  **Chemical Labeling:** Each sample is chemically tagged with a unique TMT or iTRAQ label, which consists of a reactive group binding to peptides and a mass reporter for sample differentiation.
 
@@
 
-    -   **MS2 (Peptide Sequencing & Tag Fragmentation):** Peptides are fragmented for sequence identification, and TMT mass tags fragment to generate reporter ions.
+    -   **MS2 (Peptide Sequencing & Tag Fragmentation):** Peptides are fragmented for sequence identification, and TMT/iTRAQ mass tags fragment to generate reporter ions.
 
@@
 A pooled control channel enables comparison across cassettes, allowing many samples to be analyzed in a single experiment or large-scale study.
+iTRAQ has fallen out of favor somewhat because it is limited to 4 samples per cassette, though it is still commonly used.
 
-##### Advantages of TMT Labeling
+##### Advantages of TMT/iTRAQ Labeling
 
@@
 
-TMT-based mass spectrometry is a valuable tool for large-scale proteomics, offering high-throughput, precise, and deep proteome coverage.
+TMT- or iTRAQ based mass spectrometry is a valuable tool for large-scale proteomics, offering high-throughput, precise, and deep proteome coverage.
 While it requires advanced instrumentation and careful sample preparation, its ability to multiplex multiple samples in a single run makes it an attractive option for high-confidence protein quantification.

### 2025-05-14 Background/MultifunctionalLipidProbesOverview.qmd
updating some of Carsten's edits and some other small changes

@@
 
-Functionalized lipid probes are at the intersection of several niche biotechnologies.
+Functionalized lipid probes are a toolset intended to fuse several niche biotechnologies.
 This overview will serve as a summary of the capabilities, nuances, and limitations of their utility.
-Additional resources and published review articles will be referenced and linked below for greater detail.
+Please find additional resources and published primary and review articles below for greater detail.
 
@@
 While proteins have long been the primary focus of interaction studies, lipids play an equally crucial yet often under-appreciated role in cellular function.
-Therefore, there is a need for detailed knowledge of lipid-protein interactions (the lipid interactome), in healthy and diseased cells and tissue.
+Therefore, there is a need for detailed knowledge of lipid-protein interactions (the lipid interactome).
+To learn about diseases and to find new therapeutic targets, in the comparison of the lipid interactomes of healthy and diseased cells and tissue is currently developing into a new field of lipid biology.
 
@@
 By studying lipid-lipid interactions and lipid interactomes, researchers will gain deeper insight into how these molecular interactions influence local and global membrane architecture and dynamics.
-Understanding these interactions and interactomes is essential for unraveling fundamental processes like vesicle trafficking, cell signaling, and membrane compartmentalization.
+Understanding these interactions and interactomes is essential for unraveling fundamental processes such as vesicle trafficking, cell division, cell signaling, and membrane compartmentalization.
 
@@
 Rapidly turned-over phosphatidylinositol 3,4,5-*tris*phosphate triggers cell survival, growth, movement, and proliferation.
-These examples  highlights how lipid signaling can affect cellular behavior and physiological responses.
+These examples  highlight how lipid signaling can affect cellular behavior and physiological responses.
+
+### Lipids in Disease
+
+Many diseases are caused by or affiliated with a lack or an accumulation of lipids, e.g.
+in atherosclerosis of in lipid storage diseases.
+However, recent evidence shows that in many if not most disease states specific lipid species are up- or down-regulated.
+A good example are viral and bacterial infections.
+If we learn about the effects of these altered lipids, we might identify new biochemical mechanisms essential for disease development and hence new therapeutic targets.
 
@@
 In addition, synthetic lipid tools are designed to provide a defined composition of fatty acids and carbon backbones connected to a specific head group while genetic and pharmacological methods are more likely to produce a diverse group of lipid species.
+The lipid binding pocket of a protein might only in some cases be a great therapeutic target while the function of the lipid binding protein might well be.
 
@@
 
-To overcome these challenges, researchers have developed synthetic analogs of native lipids.
+To overcome the challenges outlined above, researchers have developed synthetic analogs of native lipids.
 These modified lipids allow for precise investigation of lipid function while preserving their essential biological properties.
-The key modifications used in this approach include a photo-crosslinking group (usually a diazirine), an alkyne group for click chemistry, and a photo-removable (cage) group for preventing premature probe metabolism.
+The key modifications used in this approach include one to three functional modifications, namely a photo-crosslinking group (usually a diazirine), an alkyne group for click chemistry, and a photo-removable (cage) group for preventing premature probe metabolism.
 
-#### Diazirine group {#sec-Diazirine}
+#### Diazirine Group {#sec-Diazirine}
 
@@
 
-##### Key properties of diazirine crosslinking:
+##### Key Properties of Diazirine Crosslinking:
 
@@
 Among the various crosslinking motifs, the diazirine ring is the smallest, making it the least likely to interfere with a lipid’s natural interactions.
-Upon exposure to 355 nm UV light, the diazirine ring forms a reactive carbene radical, which rapidly covalently bonds with nearby molecules.
-This reaction is highly versatile, as the carbene can insert into carbon-hydrogen, sulfur-hydrogen, nitrogen-hydrogen, oxygen-hydrogen, or double bonds, allowing for broad coverage of potential interaction partners[@haberkantFatFabulousBifunctional2014].Despite these numerous options, reaction with glutamate seems to be modestly preferred [@westDesignEvaluationCyclobutane2022].
-
+Still, the introduction of diazirine into a fatty acid side chain will slightly decrease hydrophobicity and lipid ordering.
+Upon exposure to 355 nm UV light, the diazirine ring forms a reactive intermediate, which rapidly form covalent bonds with nearby molecules.
+This reaction is highly versatile, as reactive intermediates such as carbenes can insert into nearby carbon-hydrogen, sulfur-hydrogen, nitrogen-hydrogen, oxygen-hydrogen, or double bonds, allowing for broad coverage of potential interaction partners1.
+Despite these numerous options, reaction with glutamate seems to be modestly preferred2.
 The small size and high reactivity of diazirine crosslinking make it an invaluable tool for capturing lipid-protein interactions while minimizing perturbations to native lipid function.
 
-##### The effect of diazirine placement on crosslinking targets {#sec-DiazirinePlacement}
+##### The Effect of Diazirine Placement on Crosslinking Targets {#sec-DiazirinePlacement}
 
@@
 An example of this shift is [1-10 Fatty Acid](/LipidProbe/1-10_FattyAcid.qmd), in which the diazirine ring was diazirine on carbon 3 of the fatty acid.
+
+Increasingly, lipid derivatives with the diazirine located on or near the lipid head group become available.
+Hence, many additions to the lipid interactome database now show interactions with proteins located at the membrane interface or cytosolic proteins.
+Future comparison of intramembrane versus membrane interface crosslinking will provide a more global view on lipid interactomes.
 
@@
 
-##### A versatile bioorthogonal handle
+##### A Versatile Bioorthogonal Handle
 
@@
 
-The terminal alkyne is particularly useful because it undergoes azide-alkyne cycloaddition, the prototypical click chemistry reaction.
-This reaction is highly specific, rapid, and bio-orthogonal, meaning it does not interfere with natural cellular processes.
+The terminal alkyne is particularly useful because it undergoes copper-catalyzed azide-alkyne cycloaddition, the prototypical click chemistry reaction.
+This reaction is highly specific, rapid, and bio-orthogonal, meaning it does not produce reaction products with natural cellular molecules.
+.
 By reacting the alkyne with an azide-containing probe, researchers can introduce fluorescent markers for imaging or affinity tags for isolating lipid-protein complexes.
@@
 Another important use is affinity-based enrichment.
-Lipids containing a terminal alkyne can be captured using azide-functionalized beads, enabling the isolation of lipid-protein complexes after photo-crosslinking for analysis by mass spectrometry.
+Lipids containing a terminal alkyne can be captured using azide-functionalized beads (or resins), enabling the isolation of lipid-protein complexes after photo-crosslinking for analysis by mass spectrometry.
 This method has been instrumental in identifying proteins that interact with specific lipid species, shedding light on lipid signaling pathways and metabolic networks.
+An alternative is to covalently attach biotin to the lipid-protein conjugates and the use of streptavidin beads to wash and isolate them.
 
-#### Coumarin Photocage {#sec-Coumarin}
-Lipids play an essential role in cellular signaling which often relies on transient abundance of lipid species.
+#### The Photo-activatable Group (Cage) {#sec-Coumarin}
+
+Essential roles of lipids in cellular signaling often rely on a transient abundance of lipid species, in some cases on the sub-minute scale.
 Hence, studying lipids in intact cells presents unique challenges due to their highly dynamic metabolism.
 Unlike proteins, which are relatively stable once synthesized, many bioactive lipids are continuously synthesized, modified, interconverted, and degraded as part of an extensive and tightly regulated lipid metabolic network.
-Even lipids so far not associated with cellular signaling show rapid turnover, which makes it difficult to study the effects of a specific lipid species in isolation, as the lipid of interest may be enzymatically altered before it can exert its intended biological function.
+Even lipids so far not associated with cellular signaling show rapid turnover, which makes it difficult to study the effects of a specific lipid species in isolation, as a lipid of interest artificially introduced to cells may be enzymatically altered before it can exert its intended biological function.
 
-One strategy to overcome this challenge is using photocaged lipid analogs, which remain biologically inert until exposed to a specific wavelength of light.
-Irradiation with this wavelength "uncages" the lipid derivative within seconds to reveal its native structure.
-This allows researchers to control the timing and location of lipid activation, enabling targeted investigation of lipid function with high spatiotemporal resolution.
+One strategy to overcome this challenge is using photo-activatable (caged) lipid derivatives.
+These  remain biologically inert until exposed to a specific wavelength of light.
+Irradiation releases the biologically active lipid derivative within seconds.
+Subcellular illumination allows researchers to control the timing and location of lipid levels, enabling targeted investigation of lipid function with high spatiotemporal resolution.
 
-##### A light-activated protection group
+##### A Light-Activated Protection Group
 
-One of the most effective tools for photocaging lipids is based on 7-diethylamino-4-methylene coumarin, a photolabile protection group that can be removed upon exposure to 400 nm light.
+There is a limited but significant number of photo-activatable protecting groups that have been used successfully in biological experiments, One of the most effective tools for photocaging lipids is based on 7-diethylamino-4-methylene coumarin, a photolabile protection group that can be removed upon exposure to 405 nm light.
 When attached to a lipid’s headgroup, the coumarin moiety temporarily blocks interactions with proteins, preventing the lipid from participating in its normal biological pathways.
-However, upon photoactivation, the coumarin group is cleaved, restoring the lipid to its native structure and allowing it to engage with its biological targets.
+Upon photoactivation, the coumarin group is removed via a fast radical-based mechanism, restoring the lipid to its native structure and allowing it to engage with its biological targets.
+Another advantage are the fluorescent properties of the caging group which permits monitoring of cell entry and cell location.
 
-This approach is useful for studying lipid-protein interactions, as uncaging the lipid in a controlled manner ensures that protein binders recognize the native lipid structure only when and where the researcher intends.
+Other photo-activatable groups include nitrobenzyl groups and Bodipy cages.
+The former often need shorter wavelengths for the (somewhat slower) photo-reaction.
+In addition, nitrobenzyl groups are not fluorescent and hence cannot not be used for following lipid derivative entry into cells.
+Bodipy cages have great photo-chemical properties and permit uncaging at longer wavelengths but add significantly more bulk to the lipid derivative.
 
-An alternative to coumarin-based caging groups are o-nitrobenzyl.
+This uncaging approach is very useful for studying lipid-protein interactions in intact cells and tissue where longer incubation times are needed, as uncaging the lipid in a controlled manner ensures that protein binders recognize the native lipid structure only when and where the researcher intends.
 
@@
 used a caged sphingosine analog to investigate the role of sphingosine in calcium signaling.
-They found that upon photoactivation of the caged sphingosine, lysosomal calcium release was triggered, revealing a crucial link between sphingosine metabolism and intracellular calcium dynamics [@hoglingerIntracellularSphingosineReleases2015a].
+They found that upon photoactivation of the caged sphingosine, lysosomal calcium release was triggered, revealing a crucial link between sphingosine metabolism and intracellular calcium dynamics[@hoglingerIntracellularSphingosineReleases2015a].
 This discovery significantly expanded the understanding of the sphingosine signaling cascade and its downstream effects.
@@
 
-##### An Additional Benefit: Coumarin’s Inherent Fluorescence
+## Limitations of multi-functionalized lipid probes
 
-A unique advantage of using coumarin as a photocaging group is its intrinsic fluorescence.
-This means that before the lipid is even uncaged, its cellular incorporation can be directly visualized using a fluorescence microscope.
-By tracking fluorescence intensity and distribution, researchers can quickly determine whether a functionalized lipid has successfully intercalated into the target cell’s membrane or accumulated in specific subcellular compartments.
+*	While significant effort has minimized the effect that each modification has on the biophysical properties of the lipid analogs, it remains the case that adding a diazirine and a terminal alkyne will necessarily affect their physical properties – perhaps affecting sub-cellular localization and binding.
 
-This dual functionality—serving as both a caging group and a fluorescent probe—makes coumarin a useful tool for studying lipid localization, uptake, and bioactivity.
-
-These modifications stabilize protein-lipid interactions and enable the selective enrichment of lipid-bound proteins, all while maintaining tight spatial and temporal control.
-Each of these tools is described in further detail below.
-
-## Limitations of multifunctionalized lipid probes
-
-* While significant effort has minimized the effect that each modification has on the biophysical properties of the lipid analogs, it remains the case that adding a diazirine and a terminal alkyne will necessarily affect their physical properties -- perhaps affecting sub-cellular localization and binding.
 *	The coumarin cage has been repeatedly shown to protect lipid analogs from premature metabolism, but it should be recognized that this comes with some distinct changes to the behavior of the native lipid.
-  - For example, when a cell is treated with a photocaged lipid probe, the probe intercalates into every membrane in the cell -- including membranes which the native lipid would not enter.
-This may lead to the identification of non-biologically-relevant hits.
+    -	For example, when a cell is exposed to a photocaged lipid probe, the probe intercalates predominantly to endomembranes even if the native lipid is known to reside in the plasma membrane, as was shown for PIP3.
+This may lead to the identification of non-biologically-relevant hits or require enough time for lipid translocation after uncaging.
 *	Similarly, the diazirine and alkyne groups may have minor effects on the biophysical properties of the lipid probe as it interacts with other lipids and proteins within the membrane bilayer.
 This may be more relevant for proteins which preferentially bind to the acyl chain.
-  - For example, Some work has been done to demonstrate that the placement of the diazirine ring along the length of the acyl chain can have impacts on the interactome of the lipid probe[@farleyTrifunctionalFattyAcid2024].
-Farley et al (2024) demonstrated this using trifunctional Fatty Acid probes by placing the diazirine either 3 carbons from the terminus (8-3 FA) or 10 carbons from the terminus (1-10 FA).
+    -	For example, some work has been done to demonstrate that the placement of the diazirine ring along the length of the acyl chain can have impacts on the interactome of the lipid probe[@farleyTrifunctionalFattyAcid2024].
+Farley et al (2024) demonstrated this using trifunctional fatty acid probes by placing the diazirine either 3 carbons from the terminus (8-3 FA) or 10 carbons from the terminus (1-10 FA).
 They identified several proteins with distinct enrichment profiles, including VDAC1 and VDAC2 (which are preferentially enriched to the 8-3 FA probe), and ACAD9 and UBB (which are preferentially enriched to the 1-10 FA probe).
 *	Quantification of +UV versus -UV
-  - The details of the quantitative mass spectrometry are describe in our [Overview of Proteomics Methods](ProteomicsUsingMultifunctionalProbes.qmd), however, we hope to succinctly describe that quantitative mass spectrometry techniques necessarily require normalization at sample input level -- thereby exaggerating the abundance of proteins in the -UV control samples.
-  - It should be noted, therefore, that there is little meaning to a protein which is "enriched" toward the -UV condition.
-For this reason, all proteins which are "depleted" following irradiation with UV have been designated as "no hit" in our analyses.
+    -	The details of the quantitative mass spectrometry are described in our Overview of Proteomics Methods.
+However, we hope to succinctly describe that quantitative mass spectrometry techniques necessarily require normalization at sample input level – thereby exaggerating the abundance of proteins in the -UV control samples.
+    -	It should be noted, therefore, that there is little meaning to a protein which is “enriched” toward the -UV condition.
+For this reason, all proteins which are “depleted” following irradiation with UV have been designated as “no hit” in most of the analyses.

### 2025-05-30 IndividualStudies/SK_2024.qmd
Finally getting the bf-GPI data page online

---
title: "Kundu et al. 2024"
subtitle: "Investigation of Glycosylphosphatidylinositol (GPI)‐Plasma Membrane Interaction in Live Cells and the Influence of GPI Glycan Structure on the Interaction"
date: 2024-02-07
format: 
  html:
    embed-resources: false
standalone: false
---

::: {.callout-note collapse="true"}

{{< include /StudyInformation_includes/SK_2024_include.qmd >}}

:::

```{r Setup, include=FALSE, echo=FALSE}
library(here)

## Opening the source file for the ggplot custom theme
source(here::here("Resources/ggplot_styles.R"))

```

```{r AddingToSearchByProteinPage, include=FALSE, echo=FALSE}

# data <- readr::read_csv(here::here("IndividualStudies/DataTables/SK_2024_ChemEuro.csv")) |>
#   dplyr::select(LipidProbe, gene_name, logFC, pvalue, hit_annotation) |>
#   glimpse()

# CombinedProbeData <- read_csv(here("ShinyApps/LipidInteractomics_ShinyApp/combinedProbeDatasets_TMT.csv")) |>
#   dplyr::select(-`...1`) |>
#   glimpse() |>
#   rbind(data)

# write_csv(CombinedProbeData, here("ShinyApps/LipidInteractomics_ShinyApp/combinedProbeDatasets_TMT.csv"))

```

```{r HiddenOriginalDataWrangling, include=FALSE, echo=FALSE}

# gene_names <- read_csv(here("IndividualStudies/DataTables/gene_symbol_results.csv")) |>
#   mutate(
#     gene_name = case_when(
#       gene_symbol == "unnamed protein product [Homo sapiens]" ~ accession,
#       gene_symbol == "unknown [Homo sapiens]" ~ accession,
#       TRUE ~ str_remove(gene_symbol, "\"$")
#     ) 
#   ) |>
#   mutate(Accession = accession) |>
#   dplyr::select(-gene_symbol, -accession) |>
#   glimpse()

# rawData <- readr::read_csv(here("IndividualStudies/DataTables/SK_2024_fullDataset_originalHandoff.csv")) |>
#   dplyr::select(Accession, Description, `Abundance Ratio (log2): (Penta) / (Control)`, `Abundance Ratio Adj. P-Value: (Penta) / (Control)`, `Abundances (Grouped): Control`, `Abundances (Grouped): Penta`) |>
#   rename(logFC = `Abundance Ratio (log2): (Penta) / (Control)`,
#           pvalue = `Abundance Ratio Adj. P-Value: (Penta) / (Control)`,
#          Control_abundance = `Abundances (Grouped): Control`,
#          Penta_abundance = `Abundances (Grouped): Penta`) |>
#   mutate(AveExpr = log2((Control_abundance + Penta_abundance)/2)) |>
#   left_join(gene_names, by = "Accession") |>
#   dplyr::select(gene_name, Accession, Description, logFC, pvalue, AveExpr, Control_abundance, Penta_abundance) |>
#   mutate(hit_annotation = case_when(.default = "no hit",
#                                     logFC >= 2 & pvalue <= 0.05 ~ "enriched hit",
#                                     logFC >= 1 & pvalue < 0.05 ~ "enriched candidate")) |>
#   mutate(LipidProbe = "bf-GPI") |>
#   glimpse()

# write_csv(rawData, here("IndividualStudies/DataTables/SK_2024_ChemEuro.csv"))

# library(biomaRt)

# # Try connecting to a mirror
# ensembl <- useEnsembl(biomart = "ensembl", 
#                       dataset = "hsapiens_gene_ensembl",
#                       mirror = "useast")  # or "uswest", "asia"

# # Function to get gene symbol or fallback gene title
# get_gene_symbol <- function(accession) {
#   tryCatch({
#     search <- entrez_search(db = "protein", term = accession)
#     if (length(search$ids) == 0) return(NA)

#     gb_record <- entrez_fetch(db = "protein", id = search$ids[[1]], rettype = "gb", retmode = "text")
#     match <- regmatches(gb_record, regexpr("/gene=\"[^\"]+\"", gb_record))

#     gene <- if (length(match) > 0) {
#       sub("/gene=\"|\"", "", match)
#     } else {
#       summary <- entrez_summary(db = "protein", id = search$ids[[1]])
#       summary$title
#     }

#     return(gene)
#   }, error = function(e) {
#     message("Error with accession ", accession, ": ", e$message)
#     return(NA)
#   })
# }

# # Your vector of accession numbers
# accessions <- pull(rawData, Accession)

# # Path to your CSV results file
# csv_file <- here("IndividualStudies/DataTables/gene_symbol_results.csv")

# # Load previously saved results if the file exists
# if (file.exists(csv_file)) {
#   results <- read.csv(csv_file, stringsAsFactors = FALSE)
#   processed <- results$accession
# } else {
#   results <- data.frame(accession = character(), gene_symbol = character(), stringsAsFactors = FALSE)
#   processed <- character()
# }

# # Iterate through accessions, skipping ones already done
# for (acc in accessions) {
#   if (acc %in% processed) next  # skip if already processed

#   gene <- get_gene_symbol(acc)
#   results <- rbind(results, data.frame(accession = acc, gene_symbol = gene, stringsAsFactors = FALSE))

#   # Save progress after every accession
#   write.csv(results, csv_file, row.names = FALSE)

#   message("Processed: ", acc)
# }

```

```{r ReadingData, echo=FALSE, warning=FALSE, include=FALSE}

data <- readr::read_csv(here::here("IndividualStudies/DataTables/SK_2024_ChemEuro.csv")) |>
  glimpse()

# Organize the hit annotations as factors
data$hit_annotation <- factor(pull(data, hit_annotation), levels = c("enriched hit", "hit", "enriched candidate", "candidate", "no hit", "NA"), ordered = TRUE)

```

## Data visualization

::: {.panel-tabset}

#### Volcano plots

:::{.border}
```{r, echo=FALSE, warning=FALSE}
#| fig-cap: "Volcano plots depict the relative enrichment of each protein versus control (x-axis) and the statistical significance of each protein following a Student's t-test (y-axis, -log10 transformed). The left panel depicts the results of a pulldown using trifunctionalized phosphatidic acid; the right panel depicts the results of the pulldown using trifunctionalized phosphatidylethanolamine. Black proteins are unenriched or depleted in the presence of probe, Purple proteins are enriched to the probe but fall below a FDR or p-value threshold of significance, and Orange proteins surpass the threshold of significance (need details of threshold)."

VolcanoPlotStandardized(data)

```
:::

#### Ranked-order plots

:::{.border}
```{r, echo=FALSE, warning=FALSE}
#| fig-cap: "Ranked-order plots depict the relative enrichment of each protein versus control (y-axis) from lowest to highest. The left panel depicts the results of a pulldown using trifunctionalized phosphatidic acid; the right panel depicts the results of the pulldown using trifunctionalized phosphatidylethanolamine. Black proteins are unenriched or depleted in the presence of probe, Purple proteins are enriched to the probe but fall below a FDR or p-value threshold of significance, and Orange proteins surpass the threshold of significance (need details of threshold)."

RankedOrderPlotStandard(data)
```
:::

#### MA Plots

:::{.border}
```{r, echo=FALSE, warning=FALSE}
#| fig-cap: "MA plots"

MAStandard(data)

```

:::
:::

## Data exploration

Check the boxes below to filter the dataset by which lipid probe was used in the pulldown and by significance thresholds.

:::{.border}
```{r, echo=FALSE, warning=FALSE}

# Here is the code to make the filterable lists shown in the crosstalk table below

data <- data |>
  dplyr::select(gene_name, LipidProbe, hit_annotation, logFC, pvalue) |>
  mutate(logFC = signif(logFC, digits=3),
          pvalue = signif(pvalue, digits=3)) |>
  arrange(hit_annotation) |>
  arrange(LipidProbe)

## Creates a reactive dataframe
data_reactive <- crosstalk::SharedData$new(data)

htmltools::tags$div(
  class = "filter-container",
  filter_checkbox(id = "LipidProbe",
                  label = "Lipid probe in pulldown:", 
                  sharedData = data_reactive,
                  group = ~LipidProbe),
  filter_checkbox(id = "hit_annotation",
                  label = "Enrichment criteria:", 
                  sharedData = data_reactive,
                  group = ~hit_annotation)
)

## Displays the reactive dataframe
datatable(data_reactive, 
          caption = "'No hit' proteins are unenriched or depleted in the presence of probe, 'enriched candidates' are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and 'enriched hits' are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV", 
          options = list(pageLength = 15),
                         colnames = c("Gene Name", "Lipid Probe", "Hit Annotation", "LogFC", "p value", "FDR"))

```
:::

## Data download

{{< downloadthis DataTables/SK_2024_ChemEuro.csv dname="SK_2024_ChemEuro_2024">}}

### 2025-05-30 LipidProbe/Glycosylphosphatidylinositol.qmd
Finally getting the bf-GPI data page online

--- 2025-03-25 LipidProbe/PhosphatidicAcid.qmd
@@
 ---
-title: "Trifunctional Phosphatidic Acid"
+title: "Bifunctional Glycosylphosphatidylinositol (GPI)"
 prefer-html: true
@@
 
-:::{.border}
-::: {layout="[[-15,85], [100]]"}
-![(A) Native Phosphatidic Acid.](/LipidProbe/Structures/PA.png)
-
-![(B) Trifunctional Phosphatidic Acid.](/LipidProbe/Structures/TF_PA.png)
-
-Chemical structures drawn by Berit Blume.
-:::
-:::
+(Still working on this section, please forgive us for the incomplete structure!)
 
@@
 
-{{< include /StudyInformation_includes/AT_2025_include.qmd >}}
+{{< include /StudyInformation_includes/SK_2024_include.qmd >}}
 
@@
 
-# Data wrangling to prepare Alix's data to the standardized inputs for my plotting functions.
-# Read the data to a df
-
-# AT_2025 <- readr::read_csv("LipidProbe/DataSets/AT_ChemicalCommunications_2025_download.csv") |>
-# 	filter(LipidProbe == "PA")
-
-# write.csv(AT_2025, "LipidProbe/DataSets/PA_HeLa_AT_2025.csv")
-
-data <- readr::read_csv(paste0(here::here(), "/LipidProbe/DataSets/PA_HeLa_AT_2025.csv"))
+data <- readr::read_csv(here::here("LipidProbe/DataSets/bf-GPI_SK_2024_ChemEuro.csv"))
 
@@
 ```{r, echo=FALSE, warning=FALSE}
-#| fig-cap: "Data as reported in [Thomas et al., 2025](/IndividualStudies/AT_2025.qmd).
+#| fig-cap: "Data as reported in [Kundu et al., 2024](/IndividualStudies/SK_2024.qmd).
 Volcano plots depict the relative enrichment of each protein versus non-crosslinked control (x-axis) and the statistical significance of each protein following a Student's t-test (y-axis, -log10 transformed).
@@
 ```{r, echo=FALSE, warning=FALSE}
-#| fig-cap: "Data as reported in [Thomas et al., 2025](/IndividualStudies/AT_2025.qmd).
+#| fig-cap: "Data as reported in [Kundu et al., 2024](/IndividualStudies/SK_2024.qmd).
 Ranked-order plots depict the relative enrichment of each protein versus non-crosslinked control (y-axis) from lowest to highest.
@@
 ```{r, echo=FALSE, warning=FALSE}
-#| fig-cap: "Data as reported in [Thomas et al., 2025](/IndividualStudies/AT_2025.qmd).
+#| fig-cap: "Data as reported in [Kundu et al., 2024](/IndividualStudies/SK_2024.qmd).
 MA plots depict the average abundance of each protein in the crosslinked and uncrosslinked conditions (x-axis) versus the log2-transformed fold-change between the crosslinked and uncrosslinked conditions (y-axis).
@@
 
-print("Data not yet provided.")
+MAStandard(data)
 
@@
 ##### Cell Compartment
-
-<iframe src="/LipidProbe/GO_plots/PA_AT_2025_CC-DOTplot.html" width="100%" height="500px"></iframe>
-
-##### Molecular Function
-
-<iframe src="/LipidProbe/GO_plots/PA_AT_2025_MF-DOTplot.html" width="100%" height="500px"></iframe>
-
-##### Biological Process
-
-<iframe src="/LipidProbe/GO_plots/PA_AT_2025_BP-DOTplot.html" width="100%" height="500px"></iframe>
-
-:::
-
-GO Dot plots display the enrichment of GO terms among the proteins enriched to the probe.
-For these analyses, only proteins categorized as "enriched candidates" and "enriched hits" were subject to GO analysis.
-The Cell Compartment analysis assesses whether the list of enriched proteins contains a statistically significant number of proteins in the same cellular region; appropriately, the Molecular Function and Biological Process analyses does the same for molecular function and biological process, respectively.
-[Click here for more information about Gene Ontology Analysis.](/Background/DataAnalysisAndStatistics.qmd#gene-ontology-overview)
-::::
-:::::
 
@@
 
-{{< downloadthis DataSets/PA_HeLa_AT_2025.csv dname="PA_HeLa_AT_ChemComm_download">}}
+{{< downloadthis LipidProbe/DataSets/bf-GPI_SK_2024_ChemEuro.csv dname="bf-GPI_SK_2024_ChemEuro">}}
 

### 2025-05-30 StudyInformation_includes/SK_2024_include.qmd
Finally getting the bf-GPI data page online

#### Study details

##### Authors
Sayan Kundu, Mohit Jaiswal, Venkanna Babu Mullapudi, Jiatong Guo, Manasi Kamat, Kari B. Basso, Zhongwu Guo

##### Journal
Chemistry - A European Journal
<https://doi.org/10.1002/chem.202303047>{target="_blank"}

##### Abstract

Glycosylphosphatidylinositols (GPIs) need to interact with other components in the cell membrane to transduce transmembrane signals. A bifunctional GPI probe was employed for photoaffinity‐based proximity labelling and identification of GPI‐interacting proteins in the cell membrane. This probe contained the entire core structure of GPIs and was functionalized with photoreactive diazirine and clickable alkyne to facilitate its crosslinking with proteins and attachment of an affinity tag. It was disclosed that this probe was more selective than our previously reported probe containing only a part structure of the GPI core for cell membrane incorporation and an improved probe for studying GPI‐cell membrane interaction. Eighty‐eight unique membrane proteins, many of which are related to GPIs/GPI‐anchored proteins, were identified utilizing this probe. The proteomics dataset is a valuable resource for further analyses and data mining to find new GPI‐related proteins and signalling pathways. A comparison of these results with those of our previous probe provided direct evidence for the profound impact of GPI glycan structure on its interaction with the cell membrane.

##### Lipid probes utilized

Bifunctional Glycosylphosphatidylinositol (bf-GPI)

Bifunctional phosphatidyl moiety with \alpha&-D-glucoside (Control)

##### Cell line analyzed

[HeLa](https://www.atcc.org/products/ccl-2){target="_blank"}

#### Uncaging & Crosslinking timeline

| Lipid Probe | Uptake time | Uncaging time | Interaction time | Crosslinking time |
|:-------|:------:|:------:|:------:|:------:|
| bf-GPI |  180 min | NA  | NA | 15 min  |
| Control |  180 min | NA  | NA | 15 min  |

##### Mass spectrometry quantification method

Precursor ion intensity Label Free Quantitation (LFQ), performed using Proteome Discoverer

##### Additional sample preparation <span class="help-symbol" title="e.g. sub-cellular fractionation, depletion, etc.">?</span>

### 2025-05-30 index.qmd
Finally getting the bf-GPI data page online

@@
 
+  <a href="LipidProbe/Phosphatidylalcohol.qmd" style="text-decoration: none;">
+      <button style="background-color:rgb(41, 204, 131); color: white; font-size: 20px; padding: 15px 30px; border: none; border-radius: 8px; margin: 10px; cursor: pointer;">
+          Phosphatidyl Alcohol
+      </button>
+  </a>
+
   <a href="LipidProbe/N-Acylphosphatidylethanolamine.qmd" style="text-decoration: none;">
@@
           N-Acylphosphatidylethanolamine (NAPE)
-      </button>
-  </a>
-
-  <a href="LipidProbe/Phosphatidylalcohol.qmd" style="text-decoration: none;">
-      <button style="background-color:rgb(41, 204, 131); color: white; font-size: 20px; padding: 15px 30px; border: none; border-radius: 8px; margin: 10px; cursor: pointer;">
-          Phosphatidyl Alcohol
       </button>
@@
 
+    <a href="LipidProbe/Glycosylphosphatidylinositol.qmd" style="text-decoration: none;">
+        <button style="background-color:rgb(143, 46, 204); color: white; font-size: 20px; padding: 15px 30px; border: none; border-radius: 8px; margin: 10px; cursor: pointer;">
+            Glycosylphosphatidylinositol (GPI)
+        </button>
+    </a>
+
     <br>

### 2025-05-30 Resources/Run_GO_DOTplots.R

@@ -177,3 +177,16 @@ MF_enrichment_plots(WY_2021, "dot", "/LipidProbe/GO_plots/PDAA_WY_2021_MF-DOTplo
 
 BP_enrichment_plots(WY_2021, "dot", "/LipidProbe/GO_plots/PDAA_WY_2021_BP-DOTplot")
 # BP_enrichment_plots(AT_2025, "cnet", "PE-PA_AT_2025_BP-CNETplot")
+
+## SK_2024
+
+SK_2024 <- read_csv(here("IndividualStudies/DataTables/SK_2024_ChemEuro.csv"))
+
+CC_enrichment_plots(SK_2024, "dot", "/LipidProbe/GO_plots/PDAA_WY_2021_CC-DOTplot")
+# CC_enrichment_plots(AT_2025, "cnet", "PE-PA_AT_2025_CC-CNETplot")
+
+MF_enrichment_plots(SK_2024, "dot", "/LipidProbe/GO_plots/PDAA_WY_2021_MF-DOTplot")
+# MF_enrichment_plots(AT_2025, "cnet", "PE-PA_AT_2025_MF-CNETplot")
+
+BP_enrichment_plots(SK_2024, "dot", "/LipidProbe/GO_plots/PDAA_WY_2021_BP-DOTplot")
+# BP_enrichment_plots(AT_2025, "cnet", "PE-PA_AT_2025_BP-CNETplot")

### 2025-05-30 Resources/get_gene_names.r

@@ -49,6 +49,7 @@
 
 # get_gene_symbol <- Vectorize(get_gene_symbol)
 
+# get_gene_symbol("BAG37094.1")
 
 
 # DCC_2025_RawData <- read_csv(here("IndividualStudies/DataTables/DCC_2025_ChemrXiv_FullDataset.csv"))

### 2025-05-30 IndividualStudies/SF_2024.qmd
found some text issues in the plot legends, now fixed

@@
 MAStandard(data)
+
+#| fig-cap: "MA plots depict the average abundance of each protein in the crosslinked and uncrosslinked conditions (x-axis) versus the log2-transformed fold-change between the crosslinked and uncrosslinked conditions (y-axis).
+Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV)."
 

### 2025-05-30 IndividualStudies/SK_2024.qmd
found some text issues in the plot legends, now fixed

@@
 The left panel depicts the results of a pulldown using trifunctionalized phosphatidic acid; the right panel depicts the results of the pulldown using trifunctionalized phosphatidylethanolamine.
-Black proteins are unenriched or depleted in the presence of probe, Purple proteins are enriched to the probe but fall below a FDR or p-value threshold of significance, and Orange proteins surpass the threshold of significance (need details of threshold)."
+Black proteins are unenriched or depleted in the presence of probe, Purple proteins are enriched to the probe but fall below a Fold-change or p-value threshold of significance (p < 0.05 & logFC > 1), and Orange proteins surpass the threshold of significance (p < 0.05 & logFC > 2)."
 
@@
 ```{r, echo=FALSE, warning=FALSE}
-#| fig-cap: "MA plots"
+#| fig-cap: "MA plots depict the average abundance of each protein in the crosslinked and uncrosslinked conditions (x-axis) versus the log2-transformed fold-change between the crosslinked and uncrosslinked conditions (y-axis).
+Black proteins are unenriched or depleted in the presence of probe, Purple proteins are enriched to the probe but fall below a Fold-change or p-value threshold of significance (p < 0.05 & logFC > 1), and Orange proteins surpass the threshold of significance (p < 0.05 & logFC > 2)."
 
@@
 datatable(data_reactive, 
-          caption = "'No hit' proteins are unenriched or depleted in the presence of probe, 'enriched candidates' are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and 'enriched hits' are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV",
+          caption = "'No hit' proteins are unenriched or depleted in the presence of probe, 'enriched candidates' are defined as proteins with a p-value < 0.05 and a fold-change > 2 (log2FC > 1) for the bf-GPI versus control probe, and 'enriched hits' are defined as proteins with a p-value < 0.05 and a fold change of at least 4-fold (log2FC >2) for the bf-GPI versus control probe",
           options = list(pageLength = 15),
-                         colnames = c("Gene Name", "Lipid Probe", "Hit Annotation", "LogFC", "p value", "FDR"))
+                         colnames = c("Gene Name", "Lipid Probe", "Hit Annotation", "LogFC", "p value"))
 

### 2025-05-30 LipidProbe/1-10_FattyAcid.qmd
example
found some text issues in the plot legends, now fixed

@@
 title: "Trifunctional 1-10 Fatty Acid"
-prefer-html: true
+format: 
+  html:
+    embed-resources: false
 callout-icon: false
@@
 #| fig-cap: "Data as reported in [Farley et al., 2024(B)](/IndividualStudies/SF_2024_B.qmd).
+MA plots depict the average abundance of each protein in the crosslinked and uncrosslinked conditions (x-axis) versus the log2-transformed fold-change between the crosslinked and uncrosslinked conditions (y-axis).
 Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV)."

### 2025-05-30 LipidProbe/8-3_FattyAcid.qmd
example
found some text issues in the plot legends, now fixed

@@
 title: "Trifunctional 8-3 Fatty Acid"
-prefer-html: true
-html: default
+format: 
+  html:
+    embed-resources: false
 callout-icon: false
@@
 #| fig-cap: "Data as reported in [Farley et al., 2024(B)](/IndividualStudies/SF_2024_B.qmd).
+MA plots depict the average abundance of each protein in the crosslinked and uncrosslinked conditions (x-axis) versus the log2-transformed fold-change between the crosslinked and uncrosslinked conditions (y-axis).
 Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV."

### 2025-05-30 LipidProbe/Glycosylphosphatidylinositol.qmd
found some text issues in the plot legends, now fixed

@@
 The left panel depicts the results of a pulldown using trifunctionalized phosphatidic acid; the right panel depicts the results of the pulldown using trifunctionalized phosphatidylethanolamine.
-Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV."
+Black proteins are unenriched or depleted in the presence of probe, Purple proteins are enriched to the probe but fall below a Fold-change or p-value threshold of significance (p < 0.05 & logFC > 1), and Orange proteins surpass the threshold of significance (p < 0.05 & logFC > 2)."
 
@@
 MA plots depict the average abundance of each protein in the crosslinked and uncrosslinked conditions (x-axis) versus the log2-transformed fold-change between the crosslinked and uncrosslinked conditions (y-axis).
-Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV."
+Black proteins are unenriched or depleted in the presence of probe, Purple proteins are enriched to the probe but fall below a Fold-change or p-value threshold of significance (p < 0.05 & logFC > 1), and Orange proteins surpass the threshold of significance (p < 0.05 & logFC > 2)."
 

### 2025-05-30 LipidProbe/Phosphatidylalcohol.qmd
found some text issues in the plot legends, now fixed

@@
 
-```{r NewPlottingFunctions, include=FALSE, echo=FALSE}
-RankedOrderPlotSpecial <- function(data) {
-    ################
-    #' A standardized Ranked Order plot theme
-    #' Requires an input dataframe with the columns "gene_name", "LipidProbe", "logFC", "pvalue", and "hit_annotation"
-    ################
-
-    # Applies ID column to each probe
-    data <- data |>
-      group_by(LipidProbe) |>
-      arrange(logFC, .by_group = TRUE) |>
-      mutate(ID = row_number()) |>
-      ungroup()
-
-    # First makes a ggplot template to later apply ggplotly
-    RankedOrderPlots <- data |>
-        ggplot(aes(x = ID,
-                   y = logFC,
-                   color = factor(hit_annotation),
-                   fill = factor(hit_annotation),
-                   shape = factor(hit_annotation),
-                   alpha = factor(hit_annotation),
-                   size = factor(hit_annotation))) +
-        geom_point(aes(text = paste0("Gene name: ", gene_name, "\n",
-                                    "LogFC: ", logFC, "\n"))) +
-        geom_hline(yintercept = 0, linetype = 2) +
-        geom_vline(xintercept = 0, linetype = 2) +
-        scale_shape_manual(values = c("enriched hit" = 21,
-                                    "hit" = 21,
-                                    "enriched candidate" = 24,
-                                    "candidate" = 24,
-                                    "no hit" = 22), 
-                        name = "Trend") +
-        scale_color_manual(values = c("enriched hit" = "black",
-                                    "hit" = "black",
-                                    "enriched candidate" = "black",
-                                    "candidate" = "black",
-                                    "no hit" = "black"), 
-                        name = "Trend") +
-        scale_fill_manual(values = c("enriched hit" = "orange",
-                                    "hit" = "orange",
-                                    "enriched candidate" = "purple",
-                                    "candidate" = "purple",
-                                    "no hit" = "black"), 
-                        name = "Trend") +
-        scale_alpha_manual(values = c("enriched hit" = 0.8,
-                                    "hit" = 0.8,
-                                    "enriched candidate" = 0.5,
-                                    "candidate" = 0.5,
-                                    "no hit" = 0.25), 
-                        name = "Trend") +
-        scale_size_manual(values = c("enriched hit" = 4,
-                                    "hit" = 4,
-                                    "enriched candidate" = 2,
-                                    "candidate" = 2, 
-                                    "no hit" = 0.75), 
-                        name = "Trend") +
-        facet_wrap(~LipidProbe) +
-        ylab("Log2 fold-change") +
-        xlab("Ranked-order gene") +
-        theme_minimal() +
-        theme(text = element_text(family = "serif")) +
-        theme(panel.border = element_rect(color = NA, fill = NA)) +
-        theme(legend.title = element_text(size = 12, face = "bold")) +
-        theme(axis.title = element_text(size = 12, face = "bold")) +
-        theme(legend.text = element_text(size = 12))  +
-        theme(strip.text = element_text(
-    size = 20))
-    m <- list(l=50, r = 50, b= 100, pad = 4)
-
-    RankedOrderPlotly <- ggplotly(RankedOrderPlots,
-                            tooltip = c("text", dynamicTicks = TRUE),
-                            hovermode = "closest",
-                            autosize = T,
-                            margin = m) |>
-                    layout(showlegend = FALSE)
-
-    return(RankedOrderPlotly)
-}
-
-MASpecial <- function(data) {
-
-    ################
-    #' A standardized MA plot function
-    #' Receives a dataframe. Needs to have the following columns for the aes() to work: AveExpr, logFC, hit_annotation, gene_name.
-    #' Dynamically determines the limits of the plot under the scale_x/y_scontinuous calls
-    #' Produces first a facet-wrapped ggplot, then converts it to a plotly plot.
-    ################
-
-    MAPlots <- data |>
-        ggplot(aes(x = AveExpr,
-                   y = logFC,
-                   color = factor(hit_annotation),
-                   fill = factor(hit_annotation),
-                   shape = factor(hit_annotation),
-                   alpha = factor(hit_annotation),
-                   size = factor(hit_annotation))) +
-        geom_point(aes(text = paste0("Gene name: ", gene_name, "\n",
-                                    "LogFC: ", logFC, "\n",
-                                    "AveExpr: ", AveExpr, "\n"))) +
-        geom_hline(yintercept = 0, linetype = 2) +
-        geom_vline(xintercept = 0, linetype = 2) +
-        scale_x_continuous(limits = c(0.9 * min(abs(data$AveExpr)), 1.1 * max(abs(data$AveExpr))))+
-        scale_y_continuous(limits = c(-1.1 * max(abs(data$logFC)), 5))+
-        scale_shape_manual(values = c("enriched hit" = 21,
-                                    "hit" = 21,
-                                    "enriched candidate" = 24,
-                                    "candidate" = 24,
-                                    "no hit" = 22), 
-                        name = "Trend") +
-        scale_color_manual(values = c("enriched hit" = "black",
-                                    "hit" = "black",
-                                    "enriched candidate" = "black",
-                                    "candidate" = "black",
-                                    "no hit" = "black"), 
-                        name = "Trend") +
-        scale_fill_manual(values = c("enriched hit" = "orange",
-                                    "hit" = "orange",
-                                    "enriched candidate" = "purple",
-                                    "candidate" = "purple",
-                                    "no hit" = "black"), 
-                        name = "Trend") +
-        scale_alpha_manual(values = c("enriched hit" = 0.8,
-                                    "hit" = 0.8,
-                                    "enriched candidate" = 0.5,
-                                    "candidate" = 0.5,
-                                    "no hit" = 0.25), 
-                        name = "Trend") +
-        scale_size_manual(values = c("enriched hit" = 4,
-                                    "hit" = 4,
-                                    "enriched candidate" = 2,
-                                    "candidate" = 2, 
-                                    "no hit" = 0.75), 
-                        name = "Trend") +
-        facet_wrap(~LipidProbe) +
-        ylab("Log2 fold-change") +
-        xlab("Average Ion Intensity") +
-        theme_minimal() +
-        theme(text = element_text(family = "serif")) +
-        theme(panel.border = element_rect(color = NA, fill = NA)) +
-        theme(legend.title = element_text(size = 12, face = "bold")) +
-        theme(axis.title = element_text(size = 12, face = "bold")) +
-        theme(legend.text = element_text(size = 12)) +
-        theme(strip.text = element_text(
-    size = 20))
-
-    m <- list(l=50, r = 50, b= 100, pad = 4)
-
-    MAPlotly <- ggplotly(MAPlots,
-                            tooltip = c("text", dynamicTicks = TRUE),
-                            hovermode = "closest",
-                            autosize = T,
-                            margin = m) |>
-                    layout(showlegend = FALSE)
-
-    return(MAPlotly)
-}
-
-```
-
 ```{r PDAA_setup, include=FALSE, echo=FALSE}
@@
 ```{r, echo=FALSE, warning=FALSE}
-#| fig-cap: "Data as reported in [Farley et al., 2024](/IndividualStudies/SF_2024.qmd).
-Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV)."
+#| fig-cap: "Data as reported in [Yu et al., 2021, 2024](/IndividualStudies/WY_2021.qmd).
+Black proteins are designated as not statistically significant.
+Orange \"enriched hit\" denotes proteins with fold-changes > 1.5 (logFC > 0.5) pvalue < 0.05.
+Only proteins identified in all three replicates are displayed."
 
-RankedOrderPlotSpecial(data)
+RankedOrderPlotStandard(data)
 ```
 
-##### MA Plot
+##### MA plot
 
 ```{r, echo=FALSE, warning=FALSE}
-#| fig-cap: "Data as reported in [Farley et al., 2024](/IndividualStudies/SF_2024.qmd).
-Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV)."
+#| fig-cap: "Data as reported in [Yu et al., 2021](/IndividualStudies/WY_2021.qmd).
+MA plots depict the average abundance of each protein in the crosslinked and uncrosslinked conditions (x-axis) versus the log2-transformed fold-change between the crosslinked and uncrosslinked conditions (y-axis).
+Black proteins are designated as not statistically significant.
+Orange \"enriched hit\" denotes proteins with fold-changes > 1.5 (logFC > 0.5) pvalue < 0.05.
+Only proteins identified in all three replicates are displayed."
 
-MASpecial(data)
-
+MAStandard(data)
 ```
 
-##### Venn Diagram
+<!-- ##### Venn Diagram -->
 

### 2025-05-30 LipidProbe/Sphingosine.qmd
putting NAPE on the index
example
found some text issues in the plot legends, now fixed

@@
 title: "Trifunctional Sphingosine"
-format: html
-prefer-html: true
+format: 
+  html:
+    embed-resources: false
 callout-icon: false
@@
 :::
+
+#### Data visualization
 
@@
 #| fig-cap: "Data as reported in [Farley et al., 2024](/IndividualStudies/SF_2024.qmd).
+MA plots depict the average abundance of each protein in the crosslinked and uncrosslinked conditions (x-axis) versus the log2-transformed fold-change between the crosslinked and uncrosslinked conditions (y-axis).
 Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV)."

### 2025-06-16 Background/MultifunctionalLipidProbesOverview.qmd
Finally getting the bf-GPI data page online
Updating with data wrangling scripts and some suggested reviewer changes

@@
 Functionalized lipid probes are a toolset intended to fuse several niche biotechnologies.
-This overview will serve as a summary of the capabilities, nuances, and limitations of their utility.
+This overview will serve as a summary of the capabilifties, nuances, and limitations of their utility.
 Please find additional resources and published primary and review articles below for greater detail.
@@
 Upon exposure to 355 nm UV light, the diazirine ring forms a reactive intermediate, which rapidly form covalent bonds with nearby molecules.
-This reaction is highly versatile, as reactive intermediates such as carbenes can insert into nearby carbon-hydrogen, sulfur-hydrogen, nitrogen-hydrogen, oxygen-hydrogen, or double bonds, allowing for broad coverage of potential interaction partners1.
-Despite these numerous options, reaction with glutamate seems to be modestly preferred2.
+This reaction is highly versatile, as reactive intermediates such as carbenes can insert into nearby carbon-hydrogen, sulfur-hydrogen, nitrogen-hydrogen, oxygen-hydrogen, or double bonds, allowing for broad coverage of potential interaction partners[@haberkantFatFabulousBifunctional2014].
+Despite these numerous options, reaction with glutamate seems to be modestly preferred[@westDesignEvaluationCyclobutane2022].
 The small size and high reactivity of diazirine crosslinking make it an invaluable tool for capturing lipid-protein interactions while minimizing perturbations to native lipid function.

### 2025-06-16 HourlyTracking/202505_GG-Hours.qmd
Updating with data wrangling scripts and some suggested reviewer changes

---
title: "April 2025 Hours Report"
author: "Gaelen Guzman"
date: "2025 05 02"
output: 
  pdf_document:
    keep_tex: true
fontsize: 12pt
geometry: margin=1in
header-includes:
  - "\\usepackage{fancyhdr}"
  - "\\pagestyle{fancy}"
  - "\\fancyhead[L]{Gaelen Guzman}"
  - "\\fancyhead[C]{Hours Report}"
  - "\\fancyhead[R]{2025 06 02}"
  - "\\fancyfoot{}"
  - "\\renewcommand{\\headrulewidth}{0.4pt}"
  - "\\renewcommand{\\footrulewidth}{0pt}"
---

Carsten Schultz,

Please find below the hours I logged for the month of May 2025, with descriptions of each day's activity. In total, I performed 8 hours of work at an hourly rate of $50 (USD), for a total bill of $400.

Please forward payments to the following account:

| | |
| :--- | :--- |
| Bank | Wells Fargo | 
| Account name |  Gaelen Guzman | 
| Address | 2925 SE Clinton St., Portland, OR 97202 |
| Account number | 8583230647 | 
| Routing number | 124103799 |

```{r, echo=FALSE, warning=FALSE, include = FALSE}
# filepath: [Hours.csv](http://_vscodecontentref_/0)
library(readr)
library(kableExtra)
library(knitr)
library(dplyr)
library(here)

# Read the Hours.csv file and handle unnamed columns
hours_data <- read_csv(here("HourlyTracking/hours.csv"), col_names = c("Date", "Hours", "Activity"), show_col_types = FALSE) |>
  mutate(Date = as.Date(as.character(Date), format = "%Y%m%d")) |>
  select(Date, Hours, Activity) |>
  filter(Date >= as.Date("2025-05-01") & Date < as.Date("2025-06-01")) %>%  # Filter for April 2025
  glimpse()

sum(hours_data$Hours)

```

```{r, echo=FALSE}

# Display the table with text wrapping for the "Activity" column
kable(
  hours_data,
  format = "latex",
  booktabs = TRUE,
  caption = "Hours Logged",
  label = "hours-logged"
) %>%
  column_spec(3, width = "10cm")  # Adjust the width of the "Activity" column
```

<br>

Thank you,

Gaelen Guzman

### 2025-06-16 IndividualStudies/DCC_2025.qmd
first update in a long time, minor changes
Updating with data wrangling scripts and some suggested reviewer changes

@@
 :::
-
-```{r HiddenOriginalDataWrangling, include=FALSE, echo=FALSE}
-
-# data <- readr::read_csv(paste0(here::here(), "/IndividualStudies/DataTables/DCC_2025_ChemrXiv_FullDataset.csv")) |> 
-#   group_by(gene_name) |>
-#   filter(ratio_MvsL != "") |>
-#   summarise(logFC = mean(log2(ratio_MvsL)),
-#             pvalue = mean(pvalue),
-#             numReplicates = n(),
-#             AveExpr = log10(mean(L_abundance) + mean(M_abundance))/2) |>
-#   arrange(-logFC) |>
-#   mutate(LipidProbe = "BF-NAPE",
-#          hit_annotation = case_when(.default = "no hit",
-#                                     logFC >= 0.5849625 & pvalue <= 0.05 & numReplicates == 2 ~ "enriched candidate",
-#                                     logFC >= 0.5849625 & pvalue <= 0.05 & numReplicates == 3 ~ "enriched hit")) |>
-#   glimpse()
-
-# median_logFC <- median(data$logFC)
-
-# data$logFC <- data$logFC - median_logFC
-
-```
 
@@
 
-```{r, echo=FALSE, warning=FALSE}
+```{r Volcanoplots, echo=FALSE, warning=FALSE}
 #| fig-cap: "Volcano plots depict the relative enrichment of each protein versus non-crosslinked control (x-axis) and the statistical significance of each protein following a Student's t-test (y-axis, -log10 transformed).
@@
 
-```{r, echo=FALSE, warning=FALSE}
+```{r ROplots, echo=FALSE, warning=FALSE}
 #| fig-cap: "Ranked-order plots depict the relative enrichment of each protein versus non-crosslinked control (y-axis) from lowest to highest.
@@
 
-```{r, echo=FALSE, warning=FALSE}
+```{r MAplots, echo=FALSE, warning=FALSE}
 #| fig-cap: "MA plots depict the average abundance of each protein in the crosslinked and uncrosslinked conditions (x-axis) versus the log2-transformed fold-change between the crosslinked and uncrosslinked conditions (y-axis).
@@
 # Read the dataset
-VennData <- readr::read_csv(paste0(here::here(), "/IndividualStudies/DataTables/DCC_2025_ChemrXiv_FullDataset.csv")) |>
-
+VennData <- readr::read_csv(here("IndividualStudies/DataTables/DataWrangling/DCC_2025_ChemrXiv_FullDataset.csv")) |>
   filter(ratio_MvsL > log2(1.5), pvalue < 0.05) |>
@@
 data <- data |>
-  dplyr::select(gene_name, LipidProbe, hit_annotation, logFC, pvalue, numReplicates) |>
+  dplyr::select(gene_name, gene_ID, LipidProbe, hit_annotation, logFC, pvalue, numReplicates) |>
   mutate(logFC = signif(logFC, digits=3),
@@
           options = list(pageLength = 10),
-                         colnames = c("Gene Name", "Lipid Probe", "Hit Annotation", "LogFC", "p value", "Num Replicate IDs"),
+                         colnames = c("Gene Name", "Gene ID/Accession", "Lipid Probe", "Hit Annotation", "LogFC", "p value", "Num Replicate IDs"),
                          rownames=FALSE)

### 2025-06-16 IndividualStudies/SK_2024.qmd
Updating with data wrangling scripts and some suggested reviewer changes

@@
 source(here::here("Resources/ggplot_styles.R"))
-
-```
-
-```{r AddingToSearchByProteinPage, include=FALSE, echo=FALSE}
-
-# data <- readr::read_csv(here::here("IndividualStudies/DataTables/SK_2024_ChemEuro.csv")) |>
-#   dplyr::select(LipidProbe, gene_name, logFC, pvalue, hit_annotation) |>
-#   glimpse()
-
-# CombinedProbeData <- read_csv(here("ShinyApps/LipidInteractomics_ShinyApp/combinedProbeDatasets_TMT.csv")) |>
-#   dplyr::select(-`...1`) |>
-#   glimpse() |>
-#   rbind(data)
-
-# write_csv(CombinedProbeData, here("ShinyApps/LipidInteractomics_ShinyApp/combinedProbeDatasets_TMT.csv"))
-
-```
-
-```{r HiddenOriginalDataWrangling, include=FALSE, echo=FALSE}
-
-# gene_names <- read_csv(here("IndividualStudies/DataTables/gene_symbol_results.csv")) |>
-#   mutate(
-#     gene_name = case_when(
-#       gene_symbol == "unnamed protein product [Homo sapiens]" ~ accession,
-#       gene_symbol == "unknown [Homo sapiens]" ~ accession,
-#       TRUE ~ str_remove(gene_symbol, "\"$")
-#     ) 
-#   ) |>
-#   mutate(Accession = accession) |>
-#   dplyr::select(-gene_symbol, -accession) |>
-#   glimpse()
-
-# rawData <- readr::read_csv(here("IndividualStudies/DataTables/SK_2024_fullDataset_originalHandoff.csv")) |>
-#   dplyr::select(Accession, Description, `Abundance Ratio (log2): (Penta) / (Control)`, `Abundance Ratio Adj.
-P-Value: (Penta) / (Control)`, `Abundances (Grouped): Control`, `Abundances (Grouped): Penta`) |>
-#   rename(logFC = `Abundance Ratio (log2): (Penta) / (Control)`,
-#           pvalue = `Abundance Ratio Adj. P-Value: (Penta) / (Control)`,
-#          Control_abundance = `Abundances (Grouped): Control`,
-#          Penta_abundance = `Abundances (Grouped): Penta`) |>
-#   mutate(AveExpr = log2((Control_abundance + Penta_abundance)/2)) |>
-#   left_join(gene_names, by = "Accession") |>
-#   dplyr::select(gene_name, Accession, Description, logFC, pvalue, AveExpr, Control_abundance, Penta_abundance) |>
-#   mutate(hit_annotation = case_when(.default = "no hit",
-#                                     logFC >= 2 & pvalue <= 0.05 ~ "enriched hit",
-#                                     logFC >= 1 & pvalue < 0.05 ~ "enriched candidate")) |>
-#   mutate(LipidProbe = "bf-GPI") |>
-#   glimpse()
-
-# write_csv(rawData, here("IndividualStudies/DataTables/SK_2024_ChemEuro.csv"))
-
-# library(biomaRt)
-
-# # Try connecting to a mirror
-# ensembl <- useEnsembl(biomart = "ensembl", 
-#                       dataset = "hsapiens_gene_ensembl",
-#                       mirror = "useast")  # or "uswest", "asia"
-
-# # Function to get gene symbol or fallback gene title
-# get_gene_symbol <- function(accession) {
-#   tryCatch({
-#     search <- entrez_search(db = "protein", term = accession)
-#     if (length(search$ids) == 0) return(NA)
-
-#     gb_record <- entrez_fetch(db = "protein", id = search$ids[[1]], rettype = "gb", retmode = "text")
-#     match <- regmatches(gb_record, regexpr("/gene=\"[^\"]+\"", gb_record))
-
-#     gene <- if (length(match) > 0) {
-#       sub("/gene=\"|\"", "", match)
-#     } else {
-#       summary <- entrez_summary(db = "protein", id = search$ids[[1]])
-#       summary$title
-#     }
-
-#     return(gene)
-#   }, error = function(e) {
-#     message("Error with accession ", accession, ": ", e$message)
-#     return(NA)
-#   })
-# }
-
-# # Your vector of accession numbers
-# accessions <- pull(rawData, Accession)
-
-# # Path to your CSV results file
-# csv_file <- here("IndividualStudies/DataTables/gene_symbol_results.csv")
-
-# # Load previously saved results if the file exists
-# if (file.exists(csv_file)) {
-#   results <- read.csv(csv_file, stringsAsFactors = FALSE)
-#   processed <- results$accession
-# } else {
-#   results <- data.frame(accession = character(), gene_symbol = character(), stringsAsFactors = FALSE)
-#   processed <- character()
-# }
-
-# # Iterate through accessions, skipping ones already done
-# for (acc in accessions) {
-#   if (acc %in% processed) next  # skip if already processed
-
-#   gene <- get_gene_symbol(acc)
-#   results <- rbind(results, data.frame(accession = acc, gene_symbol = gene, stringsAsFactors = FALSE))
-
-#   # Save progress after every accession
-#   write.csv(results, csv_file, row.names = FALSE)
-
-#   message("Processed: ", acc)
-# }
 
@@
 data <- data |>
-  dplyr::select(gene_name, LipidProbe, hit_annotation, logFC, pvalue) |>
+  dplyr::select(gene_name, Accession, LipidProbe, hit_annotation, logFC, pvalue) |>
   mutate(logFC = signif(logFC, digits=3),
@@
           options = list(pageLength = 15),
-                         colnames = c("Gene Name", "Lipid Probe", "Hit Annotation", "LogFC", "p value"))
+                         colnames = c("Gene Name", "Gene ID/Accession", "Lipid Probe", "Hit Annotation", "LogFC", "p value"))
 

### 2025-06-16 IndividualStudies/WY_2021.qmd
Updating with data wrangling scripts and some suggested reviewer changes

@@
 data$hit_annotation <- factor(pull(data, hit_annotation), levels = c("enriched hit", "hit", "enriched candidate", "candidate", "no hit", "NA"), ordered = TRUE)
-
-```
-
-```{r WY_2025_seriousDataWrangling, include=FALSE, echo=FALSE}
-
-# # RawData <- read_csv(here::here("IndividualStudies/DataTables/WY_2021_ACSChemBio_RawData2.csv"))
-
-# filtered_data <- RawData |> 
-#   filter(if_all(starts_with("Control_"), ~ !is.na(.) & . != 0) & 
-#          if_all(starts_with("Sample_"), ~ !is.na(.) & . != 0)) |>
-#   arrange(-Control_1)
-
-# # Convert wide format to long format
-# long_data <- filtered_data |> 
-#   pivot_longer(cols = -gene_name, 
-#                names_to = c("Condition", "Replicate"), 
-#                names_sep = "_", 
-#                values_to = "Abundance") |> 
-#   mutate(Condition = ifelse(Condition == "Control", "Control", "Sample"))
-
-# # Count the number of observations per gene per condition
-# complete_genes <- long_data |> 
-#   filter(if_all(starts_with("Abundance"), ~ !is.na(.))) |> # Keep only genes with full data in both groups
-#   group_by(gene_name, Condition) |> 
-#   summarise(count = n(), .groups = "drop") |> 
-#   pivot_wider(names_from = Condition, values_from = count, values_fill = 0) |> 
-#   filter(Control == 3 & Sample == 3) |>  
-#   pull(gene_name)
-
-# # Filter the original dataset to include only these complete genes
-# filtered_data <- long_data |> 
-#   filter(gene_name %in% complete_genes)
-
-# # Run t-test for each gene
-# t_test_results <- filtered_data |> 
-#   group_by(gene_name) |> 
-#   summarise(
-#     pvalue = t.test(Abundance[Condition == "Sample"], 
-#                      Abundance[Condition == "Control"], 
-#                      var.equal = TRUE)$p.value,
-#     logFC = log2(mean(Abundance[Condition == "Sample"]) / mean(Abundance[Condition == "Control"]))
-#   ) |> 
-#   mutate(adj_p_value = p.adjust(pvalue, method = "BH"),
-#           LipidProbe = "PDAA",
-#           hit_annotation = case_when(.default = "no hit",
-#                                       logFC > log2(1.5) &  pvalue < 0.05 ~ "enriched hit"))  # Adjust p-values for multiple testing
-
-# averaged_data <- filtered_data |> 
-#   group_by(gene_name) |>
-#   summarise(AveExpr = log10(mean(Abundance)))
-
-# data <- t_test_results |>
-#   left_join(averaged_data)
-
-# # write_csv(data, here("IndividualStudies/DataTables/WY_2021_ACSChemBio_Download.csv"))
 

### 2025-06-16 StudyInformation_includes/DCC_2025_include.qmd
Updating with data wrangling scripts and some suggested reviewer changes

@@
 <span class="hover-image">
-  <img src="/Structures/BF-NAPE.png" alt="Bifunctional NAPE" />
+  <img src="/LipidProbe/Structures/BF-NAPE.png" alt="Bifunctional NAPE" />
 </span>

### 2025-06-16 IndividualStudies/DataTables/DataWrangling/DCC_2025_wrangling.R

@@ -1,0 +1,41 @@
+####################
+# Data wrangling script for DCC_2025
+
+####################
+
+# loading packages from source styles script
+library(here)
+
+## Opening the source file for the ggplot custom theme
+source(here::here("Resources/ggplot_styles.R"))
+
+############################################################
+
+
+# Coercing original data handoff into standardized format for my plotting functions
+#   - averaging logFC and pvalues for the ids of each protein by replicate, counting the number of reps for each protein
+#   - adding statistical annotation based on the publication's cutoffs
+#   - maintained the original statistical output from the publication
+data <- readr::read_csv(here("IndividualStudies/DataTables/DataWrangling/DCC_2025_ChemrXiv_FullDataset.csv")) |>
+  glimpse() |>
+  group_by(gene_name) |>
+  filter(ratio_MvsL != "") |>
+  summarise(gene_ID = dplyr::first(gene_ID),
+            logFC = mean(log2(ratio_MvsL)),
+            pvalue = mean(pvalue),
+            numReplicates = n(),
+            AveExpr = log10(mean(L_abundance) + mean(M_abundance))/2) |>
+  arrange(-logFC) |>
+  mutate(LipidProbe = "BF-NAPE",
+         hit_annotation = case_when(.default = "no hit",
+                                    logFC >= 0.5849625 & pvalue <= 0.05 & numReplicates == 2 ~ "enriched candidate",
+                                    logFC >= 0.5849625 & pvalue <= 0.05 & numReplicates == 3 ~ "enriched hit")) |>
+  glimpse()
+
+
+# Median normalizing the logFC values for each protein id'd
+median_logFC <- median(data$logFC)
+
+data$logFC <- data$logFC - median_logFC
+
+write_csv(data, here("IndividualStudies/DataTables/DCC_2025_ChemrXiv_Download.csv"))

### 2025-06-16 IndividualStudies/DataTables/DataWrangling/SK_2024_wrangling.R

@@ -1,0 +1,127 @@
+####################
+# Data wrangling script for SK_2024
+
+####################
+
+# loading packages from source styles script
+library(here)
+
+## Opening the source file for the ggplot custom theme
+source(here::here("Resources/ggplot_styles.R"))
+
+
+############################################################
+
+# 1 - Need to extract gene names from accession numbers
+
+library(biomaRt)
+
+# Try connecting to a mirror
+ensembl <- useEnsembl(biomart = "ensembl", 
+                      dataset = "hsapiens_gene_ensembl",
+                      mirror = "useast")  # or "uswest", "asia"
+
+# Function to get gene symbol or fallback gene title
+get_gene_symbol <- function(accession) {
+  tryCatch({
+    search <- entrez_search(db = "protein", term = accession)
+    if (length(search$ids) == 0) return(NA)
+
+    gb_record <- entrez_fetch(db = "protein", id = search$ids[[1]], rettype = "gb", retmode = "text")
+    match <- regmatches(gb_record, regexpr("/gene=\"[^\"]+\"", gb_record))
+
+    gene <- if (length(match) > 0) {
+      sub("/gene=\"|\"", "", match)
+    } else {
+      summary <- entrez_summary(db = "protein", id = search$ids[[1]])
+      summary$title
+    }
+
+    return(gene)
+  }, error = function(e) {
+    message("Error with accession ", accession, ": ", e$message)
+    return(NA)
+  })
+}
+
+# Vector of accession numbers
+accessions <- pull(rawData, Accession)
+
+# Path to CSV results file
+csv_file <- here("IndividualStudies/DataTables/gene_symbol_results.csv")
+
+# Load previously saved results if the file exists
+if (file.exists(csv_file)) {
+  results <- read.csv(csv_file, stringsAsFactors = FALSE)
+  processed <- results$accession
+} else {
+  results <- data.frame(accession = character(), gene_symbol = character(), stringsAsFactors = FALSE)
+  processed <- character()
+}
+
+# Iterate through accessions, skipping ones already done
+for (acc in accessions) {
+  if (acc %in% processed) next  # skip if already processed
+
+  gene <- get_gene_symbol(acc)
[…]

### 2025-06-16 IndividualStudies/DataTables/DataWrangling/WY_2021_wrangling.R

@@ -1,0 +1,64 @@
+####################
+# Data wrangling script for WY_2021
+
+####################
+
+# loading packages from source styles script
+library(here)
+
+## Opening the source file for the ggplot custom theme
+source(here::here("Resources/ggplot_styles.R"))
+
+############################################################
+
+
+RawData <- read_csv(here::here("IndividualStudies/DataTables/WY_2021_ACSChemBio_RawData2.csv"))
+
+filtered_data <- RawData |> 
+  filter(if_all(starts_with("Control_"), ~ !is.na(.) & . != 0) & 
+         if_all(starts_with("Sample_"), ~ !is.na(.) & . != 0)) |>
+  arrange(-Control_1)
+         
+# Convert wide format to long format
+long_data <- filtered_data |> 
+  pivot_longer(cols = -gene_name, 
+               names_to = c("Condition", "Replicate"), 
+               names_sep = "_", 
+               values_to = "Abundance") |> 
+  mutate(Condition = ifelse(Condition == "Control", "Control", "Sample"))
+
+# Count the number of observations per gene per condition
+complete_genes <- long_data |> 
+  filter(if_all(starts_with("Abundance"), ~ !is.na(.))) |> # Keep only genes with full data in both groups
+  group_by(gene_name, Condition) |> 
+  summarise(count = n(), .groups = "drop") |> 
+  pivot_wider(names_from = Condition, values_from = count, values_fill = 0) |> 
+  filter(Control == 3 & Sample == 3) |>  
+  pull(gene_name)
+
+# Filter the original dataset to include only these complete genes
+filtered_data <- long_data |> 
+  filter(gene_name %in% complete_genes)
+
+# Run t-test for each gene
+t_test_results <- filtered_data |> 
+  group_by(gene_name) |> 
+  summarise(
+    pvalue = t.test(Abundance[Condition == "Sample"], 
+                     Abundance[Condition == "Control"], 
+                     var.equal = TRUE)$p.value,
+    logFC = log2(mean(Abundance[Condition == "Sample"]) / mean(Abundance[Condition == "Control"]))
+  ) |> 
+  mutate(adj_p_value = p.adjust(pvalue, method = "BH"),
+          LipidProbe = "PDAA",
+          hit_annotation = case_when(.default = "no hit",
[…]

### 2025-06-16 Resources/ggplot_styles.R

@@ -91,8 +91,8 @@ MAStandard <- function(data) {
                                     "AveExpr: ", AveExpr, "\n"))) +
         geom_hline(yintercept = 0, linetype = 2) +
         geom_vline(xintercept = 0, linetype = 2) +
-        scale_x_continuous(limits = c(0.9 * min(abs(data$AveExpr)), 1.1 * max(abs(data$AveExpr))))+
-        scale_y_continuous(limits = c(-1.1 * max(abs(data$logFC)), 1.1 * max(abs(data$logFC))))+
+        scale_x_continuous(limits = c(0.9 * min(safe_abs(data$AveExpr)), 1.1 * max(safe_abs(data$AveExpr))))+
+        scale_y_continuous(limits = c(-1.1 * max(safe_abs(data$logFC)), 1.1 * max(safe_abs(data$logFC))))+
         scale_shape_manual(values = c("enriched hit" = 21,
                                     "hit" = 21,
                                     "enriched candidate" = 24,

### 2025-06-16 IndividualStudies/SF_2024.qmd
Fixed the SF 2024 data pages to include wrangling scripts and accession numbers

@@
 # Opening the datatable for this page IN FINAL RENDER
-data <- readr::read_csv(paste0(here(), "/IndividualStudies/DataTables/SF_ACS-Chem-Bio_2024_download.csv"))
+data <- readr::read_csv(here("IndividualStudies/DataTables/SF_ACS-Chem-Bio_2024_download.csv"))
 
@@
 :::{.border}
-```{r, echo=FALSE, warning=FALSE}
+```{r Volcanoplots, echo=FALSE, warning=FALSE}
 #| fig-cap: "Volcano plots depict the relative enrichment of each protein versus control (x-axis) and the statistical significance of each protein following a Student's t-test (y-axis, -log10 transformed).
-The left panel depicts the results of a pulldown using trifunctionalized phosphatidic acid; the right panel depicts the results of the pulldown using trifunctionalized phosphatidylethanolamine.
+The left panel depicts the results of a pulldown using trifunctionalized sphingosine; the right panel depicts the results of the pulldown using trifunctionalized sphinganine.
 Black proteins are unenriched or depleted in the presence of probe, Purple proteins are enriched to the probe but fall below a FDR or p-value threshold of significance, and Orange proteins surpass the threshold of significance (need details of threshold)."
@@
 :::{.border}
-```{r, echo=FALSE, warning=FALSE}
+```{r ROplots, echo=FALSE, warning=FALSE}
 #| fig-cap: "Ranked-order plots depict the relative enrichment of each protein versus control (y-axis) from lowest to highest.
-The left panel depicts the results of a pulldown using trifunctionalized phosphatidic acid; the right panel depicts the results of the pulldown using trifunctionalized phosphatidylethanolamine.
+The left panel depicts the results of a pulldown using trifunctionalized sphingosine; the right panel depicts the results of the pulldown using trifunctionalized sphinganine.
 Black proteins are unenriched or depleted in the presence of probe, Purple proteins are enriched to the probe but fall below a FDR or p-value threshold of significance, and Orange proteins surpass the threshold of significance (need details of threshold)."
@@
 :::{.border}
-```{r, echo=FALSE, warning=FALSE}
-#| fig-cap: "MA plots"
+```{r MAplots, echo=FALSE, warning=FALSE}
+#| fig-cap: "MA plots depict the average abundance of each protein in the crosslinked and uncrosslinked conditions (x-axis) versus the log2-transformed fold-change between the crosslinked and uncrosslinked conditions (y-axis).
+The left panel depicts the results of a pulldown using trifunctionalized sphingosine; the right panel depicts the results of the pulldown using trifunctionalized sphinganine.
+Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV)."
 
 MAStandard(data)
-
-#| fig-cap: "MA plots depict the average abundance of each protein in the crosslinked and uncrosslinked conditions (x-axis) versus the log2-transformed fold-change between the crosslinked and uncrosslinked conditions (y-axis).
-Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV)."
 
@@
 data <- data |>
-  dplyr::select(gene_name, LipidProbe, hit_annotation, logFC, pvalue, fdr) |>
+  dplyr::select(gene_name, protein_id, LipidProbe, hit_annotation, logFC, pvalue, AveExpr, fdr) |>
   mutate(logFC = signif(logFC, digits=3),
           pvalue = signif(pvalue, digits=3),
+          AveExpr = signif(AveExpr, digits=3),
           fdr = signif(fdr, digits = 3)) |>
@@
           options = list(pageLength = 15),
-                         colnames = c("Gene Name", "Lipid Probe", "Hit Annotation", "LogFC", "p value", "FDR"))
+                         colnames = c("Gene Name","Protein ID/Accession", "Lipid Probe", "Hit Annotation", "LogFC", "p value", "Average Expression", "FDR"))
 

### 2025-06-16 IndividualStudies/SF_2024_B.qmd
Fixed the PDAA pages with the new dataset
Fixed the SF 2024 data pages to include wrangling scripts and accession numbers

@@
 # Opening the datatable for this page IN FINAL RENDER
-data <- readr::read_csv(paste0(here(), "/IndividualStudies/DataTables/SF_Chem_Comm_2024_download.csv"))
+data <- readr::read_csv(here("IndividualStudies/DataTables/SF_ChemComm_2024_download.csv"))
 
@@
 ## Displays the reactive dataframe
-datatable(data_reactive, options = list(pageLength = 15))
+datatable(data_reactive, options = list(pageLength = 10))
 
@@
 
-{{< downloadthis DataTables/SF_Chem_Comm_2024_download.csv dname="SF_Chem_Comm_2024">}}
+{{< downloadthis DataTables/SF_ChemComm_2024_download.csv dname="SF_Chem_Comm_2024">}}

### 2025-06-16 IndividualStudies/DataTables/DataWrangling/SF_2024_ACS-Chem-Bio_wrangling.R

@@ -1,0 +1,29 @@
+####################
+# Data wrangling script for SK_2024
+
+####################
+
+# loading packages from source styles script
+library(here)
+
+## Opening the source file for the ggplot custom theme
+source(here::here("Resources/ggplot_styles.R"))
+
+
+############################################################
+
+data <- read_csv(here("IndividualStudies/DataTables/DataWrangling/SF_ACS-ChemBio_2024_Limma_results_V3.csv")) |>
+  glimpse()
+
+
+data <- data |>
+  select(gene_name, protein_id, logFC, pvalue, AveExpr, hit_annotation, sample, comparison, fdr) |>
+  filter(sample == "Huh7") |>
+  filter(comparison == "Spa_UV - Spa_noUV" | comparison == "Sph_UV - Sph_noUV") |>
+  mutate(LipidProbe = case_when(comparison == "Spa_UV - Spa_noUV" ~ "Spa",
+                                comparison == "Sph_UV - Sph_noUV" ~ "Sph")) |>
+  select(-comparison, -sample) |>
+  select(gene_name, protein_id, LipidProbe, hit_annotation, logFC, pvalue, AveExpr, fdr) |>
+  glimpse() 
+
+write_csv(data, here("IndividualStudies/DataTables/SF_ACS-Chem-Bio_2024_download.csv"))

### 2025-06-16 IndividualStudies/DataTables/DataWrangling/SF_2024_ChemComm_wrangling.R

@@ -1,0 +1,31 @@
+####################
+# Data wrangling script for SK_2024
+
+####################
+
+# loading packages from source styles script
+library(here)
+
+## Opening the source file for the ggplot custom theme
+source(here::here("Resources/ggplot_styles.R"))
+
+
+############################################################
+
+data <- read_csv(here("IndividualStudies/DataTables/DataWrangling/SF_ACS-ChemComm_2024_Limma_results_V3.csv")) |>
+  glimpse()
+
+unique(data$comparison)
+
+
+data <- data |>
+  select(gene_name, protein_id, logFC, pvalue, AveExpr, hit_annotation, sample, comparison, fdr) |>
+  filter(sample == "Huh7") |>
+  filter(comparison == "FA_8_3_UV - FA_8_3_noUV" | comparison == "FA_1_10_UV - FA_1_10_noUV") |>
+  mutate(LipidProbe = case_when(comparison == "FA_8_3_UV - FA_8_3_noUV" ~ "8-3 FA",
+                                comparison == "FA_1_10_UV - FA_1_10_noUV" ~ "1-10 FA")) |>
+  select(-comparison, -sample) |>
+  select(gene_name, protein_id, LipidProbe, hit_annotation, logFC, pvalue, AveExpr, fdr) |>
+  glimpse() 
+
+write_csv(data, here("IndividualStudies/DataTables/SF_ChemComm_2024_download.csv"))

### 2025-06-17 LipidProbe/EnrichedHitsComparison.qmd
example
Updated text of ProbevsProbeComparison page

@@
 title: "Comparing the Enriched Hits of Different Probes"
+format: 
+  html:
+    embed-resources: false
 ---
@@
 
-For a select subset of the lipid probes depicted on this repository, one can directly compare their enrichment of proteins.
-In the case of the trifunctionalized PE, PA, Sph, Spa, 8-3 FA, and 1-10 FA probes, all were analyzed using quantitative mass spectrometry via [Tandem Mass Tagging](/Background/MultifunctionalLipidProbesOverview.qmd#sec-TMT).
-
-Use the dropdown menu below to select two lipid probes to plot against each other and visualize the enriched hits of each probe.
-Black proteins are unenriched in respect to both probes; Purple proteins are "enriched" with respect to only the probe on the x-axis; Green proteins are "enriched" with respect to only the probe on the y-axis; and Orange proteins are "enriched" in both probes.
-Depicted are only the proteins present in the datasets of both probes.
+While the results of proteomics data resulting from distinct mass spectrometry analyses should not be directly compared quantitatively (i.e.
+performing statistical comparison between datasets collected on different instruments using different methods), one may qualitatively compare the results of different analyses and assess whether hits are co-enriched between different lipid probe affinity handles.
+We have prepared the visualization tool below to enable this to be done visually.
 
@@
 :::{.border}
+:::{#fig-ProbeVsProbeComparison}
 ```{=html}
@@
       width: 100%;
-      height: 90vh;
+      height: 75vh;
       border: none;
@@
 ```
+
+This Shiny app plots the enrichment results of two user-selected datasets against each other for visual comparison of protein enrichment toward each lipid probe.
+Use the dropdown menus to select lipid probes to plot against each other and visualize the enriched hits of each probe.
+Proteins missing in one dataset are temporarily assigned a logFC of 0 for visualization -- thus, they will appear along one axis.
+Black proteins are unenriched in respect to both probes; Purple proteins are "enriched" with respect to only the probe on the x-axis; Green proteins are "enriched" with respect to only the probe on the y-axis; and Orange proteins are "enriched" in both probes.
+The significance thresholds for each dataset are as defined on the respective lipid probe or studies page -- this page is intended for a simple qualitative comparison of hits between datasets.
 :::
 
-## Shared hits
+<!-- 
+## Shared hits -->
 
@@
 
-PA_data <- read_csv(paste0(here(), "/LipidProbe/DataSets/PA_HeLa_AT_2025.csv")) |>
-  filter(hit_annotation == "enriched hit") |>
-	select(LipidProbe, gene_name)
+# PA_data <- read_csv(paste0(here(), "/LipidProbe/DataSets/PA_HeLa_AT_2025.csv")) |>
+#   filter(hit_annotation == "enriched hit") |>
+# 	select(LipidProbe, gene_name)
 
-PE_data <- read_csv(paste0(here(), "/LipidProbe/DataSets/PE_HeLa_AT_2025.csv")) |>
-	filter(hit_annotation == "enriched hit") |>
-	select(LipidProbe, gene_name)
+# PE_data <- read_csv(paste0(here(), "/LipidProbe/DataSets/PE_HeLa_AT_2025.csv")) |>
+# 	filter(hit_annotation == "enriched hit") |>
+# 	select(LipidProbe, gene_name)
 
-Spa_data <- read_csv(paste0(here(), "/LipidProbe/DataSets/Spa_Huh7_SF_2024.csv")) |>
-	filter(hit_annotation == "enriched hit") |>
-	select(LipidProbe, gene_name)
+# Spa_data <- read_csv(paste0(here(), "/LipidProbe/DataSets/Spa_Huh7_SF_2024.csv")) |>
+# 	filter(hit_annotation == "enriched hit") |>
+# 	select(LipidProbe, gene_name)
 
-Sph_data <- read_csv(paste0(here(), "/LipidProbe/DataSets/Sph_Huh7_SF_2024.csv")) |>
-	filter(hit_annotation == "enriched hit") |>
-	select(LipidProbe, gene_name)
+# Sph_data <- read_csv(paste0(here(), "/LipidProbe/DataSets/Sph_Huh7_SF_2024.csv")) |>
+# 	filter(hit_annotation == "enriched hit") |>
+# 	select(LipidProbe, gene_name)
 
-FA_8_3_data <- read_csv(paste0(here(), "/LipidProbe/DataSets/8-3_FA_Huh7_SF_2024.csv")) |>
-	filter(hit_annotation == "enriched hit") |>
-	select(LipidProbe, gene_name)
+# FA_8_3_data <- read_csv(paste0(here(), "/LipidProbe/DataSets/8-3_FA_Huh7_SF_2024.csv")) |>
+# 	filter(hit_annotation == "enriched hit") |>
+# 	select(LipidProbe, gene_name)
 
-FA_1_10_data <- read_csv(paste0(here(), "/LipidProbe/DataSets/1-10_FA_Huh7_SF_2024.csv")) |>
-	filter(hit_annotation == "enriched hit") |>
-	select(LipidProbe, gene_name)
+# FA_1_10_data <- read_csv(paste0(here(), "/LipidProbe/DataSets/1-10_FA_Huh7_SF_2024.csv")) |>
+# 	filter(hit_annotation == "enriched hit") |>
+# 	select(LipidProbe, gene_name)
 
-combinedDataset <- rbind(PA_data, PE_data, Spa_data, Sph_data, FA_8_3_data, FA_1_10_data)
+# combinedDataset <- rbind(PA_data, PE_data, Spa_data, Sph_data, FA_8_3_data, FA_1_10_data)
 

### 2025-06-17 LipidProbe/EnrichedHitsComparison.qmd
Updated the shiny app

@@
 Black proteins are unenriched in respect to both probes; Purple proteins are "enriched" with respect to only the probe on the x-axis; Green proteins are "enriched" with respect to only the probe on the y-axis; and Orange proteins are "enriched" in both probes.
-The significance thresholds for each dataset are as defined on the respective lipid probe or studies page -- this page is intended for a simple qualitative comparison of hits between datasets.
+The red dashed line denotes the line of best fit between the datasets, determined via linear regression (the red text denotes the line formula and adjusted R^2^ value).
+
+Note that the significance thresholds for each dataset are as defined on the respective lipid probe or studies page and are not the same between studies -- this page is intended for a simple qualitative comparison of hits between datasets.
 :::

### 2025-06-17 IndividualStudies/DataTables/DataWrangling/DCC_2025_wrangling.R

@@ -12,7 +12,8 @@ source(here::here("Resources/ggplot_styles.R"))
 ############################################################
 
 
-# Coercing original data handoff into standardized format for my plotting functions
+# 1 -  Coercing original data handoff into standardized format for my plotting functions
+
 #   - averaging logFC and pvalues for the ids of each protein by replicate, counting the number of reps for each protein
 #   - adding statistical annotation based on the publication's cutoffs
 #   - maintained the original statistical output from the publication
@@ -39,3 +40,19 @@ median_logFC <- median(data$logFC)
 data$logFC <- data$logFC - median_logFC
 
 write_csv(data, here("IndividualStudies/DataTables/DCC_2025_ChemrXiv_Download.csv"))
+
+
+# 2 - Adding to compare lipid probes page
+
+data <- readr::read_csv(here::here("IndividualStudies/DataTables/DCC_2025_ChemrXiv_Download.csv")) |>
+  dplyr::select(LipidProbe, gene_name, logFC, pvalue, hit_annotation) |>
+  mutate(CellLine = "HeLa") |>
+  glimpse()
+
+CombinedProbeData <- read_csv(here("ShinyApps/LipidInteractomics_ShinyApp/combinedProbeDatasets_TMT.csv")) |>
+  # dplyr::select(-`...1`) |>
+  glimpse() |>
+  rbind(data)
+
+write_csv(CombinedProbeData, here("ShinyApps/LipidInteractomics_ShinyApp/combinedProbeDatasets_TMT.csv"))  
+

### 2025-06-17 IndividualStudies/DataTables/DataWrangling/WY_2021_wrangling.R

@@ -11,6 +11,7 @@ source(here::here("Resources/ggplot_styles.R"))
 
 ############################################################
 
+# 1 - Coercing data handoff into standard format
 
 RawData <- read_csv(here::here("IndividualStudies/DataTables/WY_2021_ACSChemBio_RawData2.csv"))
 
@@ -62,3 +63,22 @@ data <- t_test_results |>
   left_join(averaged_data)
 
 write_csv(data, here("IndividualStudies/DataTables/WY_2021_ACSChemBio_Download.csv"))
+
+############################################################
+
+# 2 - Adding to compare lipid probes page
+
+data <- readr::read_csv(here::here("IndividualStudies/DataTables/WY_2021_ACSChemBio_Download.csv")) |>
+  dplyr::select(LipidProbe, gene_name, logFC, pvalue, hit_annotation) |>
+  mutate(CellLine = "HeLa") |>
+  glimpse()
+
+CombinedProbeData <- read_csv(here("ShinyApps/LipidInteractomics_ShinyApp/combinedProbeDatasets_TMT.csv")) |>
+  # dplyr::select(-`...1`) |>
+  glimpse() |>
+  rbind(data)
+
+CombinedProbeData |> filter(LipidProbe == "PDAA")
+
+write_csv(CombinedProbeData, here("ShinyApps/LipidInteractomics_ShinyApp/combinedProbeDatasets_TMT.csv"))  
+

### 2025-06-17 ShinyApps/LipidInteractomics_ShinyApp/AddingCellBackgroundColumn.R

@@ -1,0 +1,18 @@
+## Needed a script space to add in a column for the cell line used for the lipid probe selected
+
+# Library initialization
+library(here)
+library(dplyr)
+library(tidyr)
+library(readr)
+
+BigDataset <- read_csv(here("ShinyApps/LipidInteractomics_ShinyApp/combinedProbeDatasets_TMT.csv")) |> 
+  mutate(CellLine = case_when(LipidProbe == "PA" | LipidProbe == "PE" | LipidProbe == "BF-NAPE" | LipidProbe == "PDAA" | LipidProbe == "bf-GPI" ~ "HeLa",
+                              LipidProbe == "Spa" | LipidProbe == "Sph" | LipidProbe == "8-3 FA" | LipidProbe == "1-10 FA" ~ "Huh7")) |>
+  glimpse()
+ 
+
+unique(BigDataset$LipidProbe)
+
+
+write_csv(BigDataset, here("ShinyApps/LipidInteractomics_ShinyApp/combinedProbeDatasets_TMT.csv"))

### 2025-06-17 ShinyApps/LipidInteractomics_ShinyApp/app.R

@@ -5,14 +5,16 @@ library(plotly)
 library(readr)
 library(shiny)
 library(here)
-
 # File path for testing
-#df <- read_csv(paste0(here(), "/ShinyApps/LipidInteractomics_ShinyApp/combinedProbeDatasets_TMT.csv"))
+# df <- read_csv("~/LipidInteractomics_Website_local/LipidInteractomics_Website/ShinyApps/LipidInteractomics_ShinyApp/combinedProbeDatasets_TMT.csv") 
+
 
 # File path for deploying to Shinyapps.io
-df <- read_csv("combinedProbeDatasets_TMT.csv")
+df <- read_csv("combinedProbeDatasets_TMT.csv") |>
+   mutate(probeOptions = paste0(LipidProbe, " - ", CellLine))
 
-probeOptions <- unique(df$LipidProbe)
+
+probeOptions <- unique(df$probeOptions)
 
 # Shiny App
 ui <- fluidPage(
@@ -35,20 +37,14 @@ server <- function(input, output, session) {
 	# Creating filtered datasets for the probes selected
 	xData <- reactive({
 		xData <- df |>
-			filter(LipidProbe == input$probe1) 
+			filter(probeOptions == input$probe1) 
 		return(xData)
 	})
 
 	yData <- reactive({
 		yData <- df |>
-			filter(LipidProbe == input$probe2) 
+			filter(probeOptions == input$probe2) 
 		return(yData)
-	})
-
-	zData <- reactive({
-		zData <- df |>
-			filter(LipidProbe == input$probe3) 
-		return(zData)
 	})
 
 	# The output call for making the plot - includes some data wrangling to make sure the selected probes are handled properly. A

### 2025-06-26 IndividualStudies/AT_2025.qmd
Updating some of the lipid probe pages with accession numbers, cleaning up captions for datatables

@@
 ```
+
+This datatable contains all the data plotted above.
+Check the boxes below to filter the dataset by which lipid probe was used in the pulldown and by significance thresholds.
+'No hit' proteins are unenriched or depleted in the presence of probe, 'enriched candidates' are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and 'enriched hits' are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV.
 :::

### 2025-06-26 IndividualStudies/DCC_2025.qmd
Updating some of the lipid probe pages with accession numbers, cleaning up captions for datatables

@@
 datatable(data_reactive, 
-          caption = "This datatable contains all the data plotted above.
-Check the boxes below to filter the dataset by which lipid probe was used in the pulldown and by significance thresholds.
-logFC ratios are median normalized.
-\"Num Replicate IDs\" denotes the number of replicates in which the protein was identified.
-As above, \"enriched hit\" denotes proteins identified in all three replicates & fold-change > 1.5 (logFC 0.585) & pvalue < 0.05.
-\"enriched candidates\" are proteins identified in two replicates & fold-change > 1.5 (logFC 0.585) & pvalue < 0.05.",
           options = list(pageLength = 10),
-                         colnames = c("Gene Name", "Gene ID/Accession", "Lipid Probe", "Hit Annotation", "LogFC", "p value", "Num Replicate IDs"),
+                         colnames = c("Gene Name", "Accession #", "Lipid Probe", "Hit Annotation", "LogFC", "p value", "Num Replicate IDs"),
                          rownames=FALSE)
@@
 
+This datatable contains all the data plotted above.
+Check the boxes below to filter the dataset by which lipid probe was used in the pulldown and by significance thresholds.
+logFC ratios are median normalized.
+"Num Replicate IDs" denotes the number of replicates in which the protein was identified.
+As above, "enriched hit" denotes proteins identified in all three replicates & fold-change > 1.5 (logFC 0.585) & pvalue < 0.05.
+"enriched candidates" are proteins identified in two replicates & fold-change > 1.5 (logFC 0.585) & pvalue < 0.05.
 :::

### 2025-06-26 IndividualStudies/SF_2024.qmd
Updating some of the lipid probe pages with accession numbers, cleaning up captions for datatables

@@
 datatable(data_reactive, 
-          caption = "'No hit' proteins are unenriched or depleted in the presence of probe, 'enriched candidates' are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and 'enriched hits' are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV",
           options = list(pageLength = 15),

### 2025-06-26 IndividualStudies/SF_2024_B.qmd
Updating some of the lipid probe pages with accession numbers, cleaning up captions for datatables

@@
 ## Displays the reactive dataframe
-datatable(data_reactive, options = list(pageLength = 10))
+datatable(data_reactive,
+         options = list(pageLength = 10))
 
 ```
+
+This datatable contains all the data plotted above.
+Check the boxes below to filter the dataset by which lipid probe was used in the pulldown and by significance thresholds.
+'No hit' proteins are unenriched or depleted in the presence of probe, 'enriched candidates' are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and 'enriched hits' are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV.
 :::

### 2025-06-26 LipidProbe/1-10_FattyAcid.qmd
Updating some of the lipid probe pages with accession numbers, cleaning up captions for datatables

@@
 data <- data |>
-  dplyr::select(gene_name, hit_annotation, logFC, pvalue, fdr) |>
+  dplyr::select(gene_name, protein_id, hit_annotation, logFC, pvalue, AveExpr, fdr) |>
   mutate(logFC = signif(logFC, digits=3),
           pvalue = signif(pvalue, digits=3),
+          AveExpr = signif(AveExpr, digits=3),
           fdr = signif(fdr, digits = 3)) |>
@@
 datatable(data_reactive, 
-          caption = "'No hit' proteins are unenriched or depleted in the presence of probe, 'enriched candidates' are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and 'enriched hits' are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV",
           options = list(pageLength = 10),
-                         colnames = c("Rank", "Gene Name", "Hit Annotation", "LogFC", "p value", "FDR"))
+                         colnames = c("Gene Name", "Accession #", "Hit Annotation", "LogFC", "p value", "AveExpr (log10)", "FDR"))
 ```
+
+This datatable contains all the data plotted above.
+Check the boxes below to filter the dataset by which lipid probe was used in the pulldown and by significance thresholds.
+'No hit' proteins are unenriched or depleted in the presence of probe, 'enriched candidates' are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and 'enriched hits' are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV.
 :::

### 2025-06-26 LipidProbe/8-3_FattyAcid.qmd
Updating some of the lipid probe pages with accession numbers, cleaning up captions for datatables

@@
 datatable(data_reactive, 
-          caption = "'No hit' proteins are unenriched or depleted in the presence of probe, 'enriched candidates' are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and 'enriched hits' are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV",
           options = list(pageLength = 10),
-                         colnames = c("Rank", "Gene Name", "Hit Annotation", "LogFC", "p value", "FDR"))
+                         colnames = c("Gene Name", "Accession #", "Hit Annotation", "LogFC", "p value", "AveExpr (log10)", "FDR"))
+```
 
-```
+This datatable contains all the data plotted above.
+Check the boxes below to filter the dataset by which lipid probe was used in the pulldown and by significance thresholds.
+'No hit' proteins are unenriched or depleted in the presence of probe, 'enriched candidates' are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and 'enriched hits' are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV.
 :::

### 2025-06-26 LipidProbe/Glycosylphosphatidylinositol.qmd
Updating some of the lipid probe pages with accession numbers, cleaning up captions for datatables

@@
 datatable(data_reactive, 
-          caption = "'No hit' proteins are unenriched or depleted in the presence of probe, 'enriched candidates' are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and 'enriched hits' are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV",
           options = list(pageLength = 10),
@@
 ```
+
+This datatable contains all the data plotted above. Check the boxes below to filter the dataset by which lipid probe was used in the pulldown and by significance thresholds.
+
+<!-- 'No hit' proteins are unenriched or depleted in the presence of probe, 'enriched candidates' are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and 'enriched hits' are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV.
+-->
 :::

### 2025-06-26 LipidProbe/DataSets/WranglingFromStudies.R

@@ -1,0 +1,20 @@
+## intitialize libraries
+library(here)
+
+## Opening the source file for the ggplot custom theme
+source(paste0(here(), "/Resources/ggplot_styles.R"))
+
+
+### 1-10 FA & 8-3 FA
+
+FullStudyData <- read_csv(here("IndividualStudies/DataTables/SF_ChemComm_2024_download.csv"))
+
+FA1_10 <- FullStudyData |>
+  filter(LipidProbe == "1-10 FA")
+
+write_csv(FA1_10, here("LipidProbe/DataSets/1-10_FA_Huh7_SF_2024.csv"))
+
+FA8_3 <- FullStudyData |>
+  filter(LipidProbe == "8-3 FA")
+
+write_csv(FA8_3, here("LipidProbe/DataSets/8-3_FA_Huh7_SF_2024.csv"))

### 2025-07-07 HourlyTracking/202506_GG-Hours.qmd
pushing small changes and hours log

--- 2025-06-16 HourlyTracking/202505_GG-Hours.qmd
@@
 ---
-title: "April 2025 Hours Report"
+title: "June 2025 Lipid Interactome Monthly Invoice"
 author: "Gaelen Guzman"
-date: "2025 05 02"
+date: "2025 07 01"
 output: 
@@
   - "\\fancyhead[L]{Gaelen Guzman}"
-  - "\\fancyhead[C]{Hours Report}"
-  - "\\fancyhead[R]{2025 06 02}"
+  - "\\fancyhead[C]{Lipid Interactome Monthly Invoice}"
+  - "\\fancyhead[R]{2025 07 01}"
   - "\\fancyfoot{}"
@@
 
-Please find below the hours I logged for the month of May 2025, with descriptions of each day's activity.
-In total, I performed 8 hours of work at an hourly rate of $50 (USD), for a total bill of $400.
+Please find below the hours I logged for the month of June 2025, with descriptions of each day's activity.
+In total, I performed 9 hours of work at an hourly rate of $50 (USD), for a total bill of $450.
 
@@
   select(Date, Hours, Activity) |>
-  filter(Date >= as.Date("2025-05-01") & Date < as.Date("2025-06-01")) %>%  # Filter for April 2025
+  filter(Date >= as.Date("2025-06-01") & Date < as.Date("2025-07-01")) %>%  # Filter for April 2025
   glimpse()

### 2025-07-18 BioinformaticsApplicationNote/GG_2025_applicationNote.qmd
Cleaned up the compare probes shiny app to make it easier to maintain.

@@
 
-If you would like to submit a relevant dataset, see our [Data Submission Page](https://www.lipidinteractome.org/DataSubmission.html) for details, contact info, and instructions.
+If you would like to submit a relevant dataset, see our [Data Submission Page](https://lipidinteractome.org/contactus/datasubmission) for details, contact info, and instructions.
 For site feedback and additional questions, please email the site administrators at <Contact.Us@lipidinteractome.org>
@@
 By leveraging standardized data formatting and interactive visualization—including study-specific analysis pages, lipid probe aggregation, and cross-study comparisons via a Shiny application—the platform facilitates intuitive exploration of protein–lipid interactions.
-As a living repository, we actively encourage researchers to contribute their findings through our [Data Submission](https://www.lipidinteractome.org/contactus/datasubmission) page, ensuring that this resource continues to evolve alongside advancements in lipidomics research.
+As a living repository, we actively encourage researchers to contribute their findings through our [Data Submission](https://lipidinteractome.org/contactus/datasubmission) page, ensuring that this resource continues to evolve alongside advancements in lipidomics research.
 
@@
 The repository is structured to facilitate intuitive navigation between experimental datasets, offering clear entry points for study-specific and lipid-specific analyses.
-Because this resource is intended as a living repository, we actively invite researchers to contribute their findings following the submission guidelines detailed on our [Data Submission](https://www.lipidinteractome.org/contactus/datasubmission) page.
+Because this resource is intended as a living repository, we actively invite researchers to contribute their findings following the submission guidelines detailed on our [Data Submission](https://lipidinteractome.org/contactus/datasubmission) page.
 

### 2025-07-18 LipidProbe/EnrichedHitsComparison.qmd
Cleaned up the compare probes shiny app to make it easier to maintain.

@@
 <body>
-  <iframe src="https://gaelen-guzman.shinyapps.io/lipidinteractomics_shinyapp/"></iframe>
+  <iframe src="https://gaelen-guzman.shinyapps.io/CompareLipidProbes/"></iframe>
 </body>
@@
 The red dashed line denotes the line of best fit between the datasets, determined via linear regression (the red text denotes the line formula and adjusted R^2^ value).
+Note that the significance thresholds for each dataset are as defined on the respective lipid probe or studies page and are not the same between studies -- this page is intended for a simple qualitative comparison of hits between datasets.
 
-Note that the significance thresholds for each dataset are as defined on the respective lipid probe or studies page and are not the same between studies -- this page is intended for a simple qualitative comparison of hits between datasets.
 :::

### 2025-07-18 ShinyApps/CompareLipidProbes/PlottingFunction.R

@@ -1,0 +1,122 @@
+library(dplyr)
+library(tidyr)
+library(ggplot2)
+library(plotly)
+library(readr)
+library(shiny)
+library(here)
+library(duckplyr)
+
+## The plotting function
+
+ProbeVSProbePlotter <- function(data, probe1Name, probe2Name) {
+
+	## Prepares the linear regression overlaid on the plot
+
+	lmData <- data |>
+        filter(hit_annotation.x != "no id" & hit_annotation.y != "no id")
+      
+	lm_xvsy <- lm(formula = lmData$logFC.y ~ lmData$logFC.x)
+	#print(summary(lm_xvsy))
+	
+	pStars <- if(summary(lm_xvsy)$coef[2, 4] < 0.0001){
+		"****"
+	}else{
+		if(summary(lm_xvsy)$coef[2, 4] < 0.001){ 
+			"***"
+		}else{
+			if(summary(lm_xvsy)$coef[2, 4] < 0.01){
+				"**"
+			}else{
+				if(summary(lm_xvsy)$coef[2, 4] < 0.05){
+					"*"
+				}else(
+					"ns"
+				)
+			}
+		}
+	}
+      
+      
+	lmLabel <- ifelse(lm_xvsy$coef[[1]] > 0, paste0("\ny =", signif(lm_xvsy$coef[[2]], 3), "x + ", signif(lm_xvsy$coef[[1]], 3), "\n",
+																									"Adj R^2 = ", signif(summary(lm_xvsy)$adj.r.squared, 5), "; ",
+																									"p: ", pStars),
+										paste0("\ny =", signif(lm_xvsy$coef[[2]], 3), "x - ", abs(signif(lm_xvsy$coef[[1]], 3)), "\n",
+														"Adj R^2 = ", signif(summary(lm_xvsy)$adj.r.squared, 5)))
+	
+
+	limits <- max(abs(max(data$logFC.x, na.rm = TRUE)),
+							abs(max(data$logFC.y, na.rm = TRUE)))
+
+	ggplotter <- data |>
+			ggplot(aes(x = logFC.x,
+								 y = logFC.y,
+								 color = factor(combined_hit_annotation),
+								 fill = factor(combined_hit_annotation),
+								 shape = factor(combined_hit_annotation),
+								 size = factor(combined_hit_annotation),
+								 alpha = factor(combined_hit_annotation))) +
[…]

### 2025-07-18 ShinyApps/CompareLipidProbes/app.R

@@ -4,19 +4,30 @@ library(ggplot2)
 library(plotly)
 library(readr)
 library(shiny)
-library(here)
-# File path for testing
-# df <- read_csv("~/LipidInteractomics_Website_local/LipidInteractomics_Website/ShinyApps/LipidInteractomics_ShinyApp/combinedProbeDatasets_TMT.csv") 
+library(duckplyr)
+
+# Load plotting function source
+
+# source("/Users/gaelenguzman/LipidInteractomics_Website_local/LipidInteractomics_Website/ShinyApps/CompareLipidProbes/PlottingFunction.R")
+
+# # File path for testing
+# df <- read_csv("/Users/gaelenguzman/LipidInteractomics_Website_local/LipidInteractomics_Website/ShinyApps/CompareLipidProbes/combinedProbeDatasets_TMT.csv") |>
+#     mutate(probeOptions = paste0(LipidProbe, " - ", CellLine))
+
 
 
 # File path for deploying to Shinyapps.io
+source("PlottingFunction.R")
 df <- read_csv("combinedProbeDatasets_TMT.csv") |>
    mutate(probeOptions = paste0(LipidProbe, " - ", CellLine))
 
 
 probeOptions <- unique(df$probeOptions)
 
-# Shiny App
+
+
+########################################################
+# UI
 ui <- fluidPage(
   titlePanel("Interactive LogFC Comparison"),
   
@@ -32,6 +43,8 @@ ui <- fluidPage(
   )
 )
 
+########################################################
+# Server
 server <- function(input, output, session) {
 	
 	# Creating filtered datasets for the probes selected
@@ -181,122 +194,6 @@ server <- function(input, output, session) {
 			)
   })
 }
-
-
-## The plotting function
-
-ProbeVSProbePlotter <- function(data, probe1Name, probe2Name) {
-
-	## Prepares the linear regression overlaid on the plot
-
-	lmData <- data |>
-        filter(hit_annotation.x != "no id" & hit_annotation.y != "no id")
-      
-	lm_xvsy <- lm(formula = lmData$logFC.y ~ lmData$logFC.x)
-	#print(summary(lm_xvsy))
-	
-	pStars <- if(summary(lm_xvsy)$coef[2, 4] < 0.0001){
-		"****"
-	}else{
-		if(summary(lm_xvsy)$coef[2, 4] < 0.001){ 
-			"***"
-		}else{
[…]

### 2025-07-18 ShinyApps/LipidInteractomics_ShinyApp/AddingCellBackgroundColumn.R

@@ -1,18 +1,0 @@
-## Needed a script space to add in a column for the cell line used for the lipid probe selected
-
-# Library initialization
-library(here)
-library(dplyr)
-library(tidyr)
-library(readr)
-
-BigDataset <- read_csv(here("ShinyApps/LipidInteractomics_ShinyApp/combinedProbeDatasets_TMT.csv")) |> 
-  mutate(CellLine = case_when(LipidProbe == "PA" | LipidProbe == "PE" | LipidProbe == "BF-NAPE" | LipidProbe == "PDAA" | LipidProbe == "bf-GPI" ~ "HeLa",
-                              LipidProbe == "Spa" | LipidProbe == "Sph" | LipidProbe == "8-3 FA" | LipidProbe == "1-10 FA" ~ "Huh7")) |>
-  glimpse()
- 
-
-unique(BigDataset$LipidProbe)
-
-
-write_csv(BigDataset, here("ShinyApps/LipidInteractomics_ShinyApp/combinedProbeDatasets_TMT.csv"))

### 2025-07-23 IndividualStudies/AT_2025.qmd
working on uploading Franks new analysis of Alixs data. Working in new branch.

@@
  -->
+
+## NB: This is a test page with the re-analyzed data from Frank
+
+I see from this new analysis that the publication only included the results from the membrane prep -- and excluded the cytosol fraction.
+Just because Frank provided both sets in his re-worked analysis, I wanted to incorporate both here to see if we want to display both online; if we decide we don't want the cytosol prep, I can easily remove that section!
 

### 2025-07-23 IndividualStudies/AT_2025_2.qmd
working on uploading Franks new analysis of Alixs data. Working in new branch.

--- 2025-07-23 IndividualStudies/AT_2025.qmd
@@
 
-## Data visualization
+::: {.callout-tip}
+
+## Membrane Fraction
+
+### Data visualization
 
@@
 library(here)
+library(dplyr)
+library(duckplyr)
+library(ggplot2)
+library(ggrepel)
+library(emojifont)
+library(dplyr)
+library(tidyr)
+library(docstring)
+library(clusterProfiler)
+library(org.Hs.eg.db)
+library(enrichplot)
+library(igraph)
+library(ggtangle)
+library(stringr)
+library(crosstalk)
+library(plotly)
+library(grid)
+library(readr)
+library(rmarkdown)
+library(gt)
+library(DT)
+library(heatmaply)
+library(ggvenn)
+library(scales)
+library(htmltools)
 
@@
 
-# Data wrangling to prepare Alix's data to the standardized inputs for my plotting functions.
-# Read the data to a df
-
-data <- readr::read_csv(paste0(here(), "/IndividualStudies/DataTables/AT_ChemicalCommunications_2025_download.csv"))
+# Read the membrane data to a df
+data <- readr::read_csv(here("IndividualStudies/DataTables/AT_ChemicalCommunications_2025_membrane_download.csv"))
 
 # Organize the hit annotations as factors
-data$hit_annotation <- factor(pull(data, hit_annotation), levels = c("enriched hit", "enriched candidate", "no hit", "NA"), ordered=TRUE)
+data$hit_annotation <- factor(pull(data, hit_annotation), levels = c("enriched hit", "hit", "enriched candidate", "candidate", "no hit",  "NA"), ordered=TRUE)
+
+data |>
+  arrange(hit_annotation) |>
+  glimpse()
 
@@
 :::
-
-## Gene Ontology Analysis
+<!-- 
+### Gene Ontology Analysis
 
@@
 ::::
-:::::
+::::: -->
 
-## Data exploration
+### Data exploration
 
@@
 ## Displays the reactive dataframe
-datatable(data_reactive, options = list(pageLength = 20))
+datatable(data_reactive, options = list(pageLength = 10))
 
@@
 
-## Data download
+### Data download
 
-{{< downloadthis DataTables/AT_ChemicalCommunications_2025_download.csv dname="AT_ChemicalCommunications_2025">}}
+{{< downloadthis DataTables/AT_ChemicalCommunications_2025_membrane_download.csv dname="AT_ChemicalCommunications_2025">}}
+
+:::
+
+:::{.callout-tip}
+
+## Cytosolic Fraction
+
+### Data visualization
+
+```{r setup2, echo=FALSE, include=FALSE}
+
+## intitialize libraries
+library(here)
+library(dplyr)
+library(duckplyr)
+library(ggplot2)
+library(ggrepel)
+library(emojifont)
+library(dplyr)
+library(tidyr)
+library(docstring)
+library(clusterProfiler)
+library(org.Hs.eg.db)
+library(enrichplot)
+library(igraph)
+library(ggtangle)
+library(stringr)
+library(crosstalk)
+library(plotly)
+library(grid)
+library(readr)
+library(rmarkdown)
+library(gt)
+library(DT)
+library(heatmaply)
+library(ggvenn)
+library(scales)
+library(htmltools)
+
+## Opening the source file for the ggplot custom theme
+source(paste0(here(), "/Resources/ggplot_styles.R"))
+
+# Read the membrane data to a df
+data <- readr::read_csv(here("IndividualStudies/DataTables/AT_ChemicalCommunications_2025_Cytosol_download.csv"))
+
+# Organize the hit annotations as factors
+data$hit_annotation <- factor(pull(data, hit_annotation), levels = c("enriched hit", "hit", "enriched candidate", "candidate", "no hit",  "NA"), ordered=TRUE)
+
+data |>
+  arrange(hit_annotation) |>
+  glimpse()
+
+```
+
+::: {.panel-tabset}
+
+#### Volcano plots
+
+:::{.border}
+```{r, echo=FALSE, warning=FALSE}
+#| fig-cap: "Volcano plots depict the relative enrichment of each protein versus non-crosslinked control (x-axis) and the statistical significance of each protein following a Student's t-test (y-axis, -log10 transformed).
+The left panel depicts the results of a pulldown using trifunctionalized phosphatidic acid; the right panel depicts the results of the pulldown using trifunctionalized phosphatidylethanolamine.
+Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV)."
+
+VolcanoPlotStandardized(data)
+
+```
+:::
+
+#### Ranked-order plots
+
+:::{.border}
+```{r, echo=FALSE, warning=FALSE}
+#| fig-cap: "Ranked-order plots depict the relative enrichment of each protein versus non-crosslinked control (y-axis) from lowest to highest.
+The left panel depicts the results of a pulldown using trifunctionalized phosphatidic acid; the right panel depicts the results of the pulldown using trifunctionalized phosphatidylethanolamine.
+Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV)."
+
+RankedOrderPlotStandard(data)
+```
+:::
+
+#### MA Plots
+
+:::{.border}
+```{r, echo=FALSE, warning=FALSE}
+#| fig-cap: "MA plots depict the average abundance of each protein in the crosslinked and uncrosslinked conditions (x-axis) versus the log2-transformed fold-change between the crosslinked and uncrosslinked conditions (y-axis).
+Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV)."
+
+MAStandard(data)
+
+```
+
+:::
+:::
+<!-- 
+### Gene Ontology Analysis
+
+**In beta: GO analysis still under development**
+
+:::::{.border}
+::::{#fig-PE_GOplots}
+::: {.panel-tabset}
+
+#### Cell Compartment
+
+<iframe src="/IndividualStudies/GO_plots/PE-PA_AT_2025_CC-DOTplot.html" width="100%" height="500px"></iframe>
+
+#### Molecular Function
+
+<iframe src="/IndividualStudies/GO_plots/PE-PA_AT_2025_MF-DOTplot.html" width="100%" height="500px"></iframe>
+
+#### Biological Process
+
+<iframe src="/IndividualStudies/GO_plots/PE-PA_AT_2025_BP-DOTplot.html" width="100%" height="500px"></iframe>
+
+:::
+
+GO Dot plots display the enrichment of GO terms among the proteins enriched to the probe.
+For these analyses, only proteins categorized as "enriched candidates" and "enriched hits" were subject to GO analysis.
+The Cell Compartment analysis assesses whether the list of enriched proteins contains a statistically significant number of proteins in the same cellular region; appropriately, the Molecular Function and Biological Process analyses does the same for molecular function and biological process, respectively.
+[Click here for more information about Gene Ontology analysis.](/Background/DataAnalysisAndStatistics.qmd#gene-ontology-overview)
+::::
+::::: -->
+
+### Data exploration
+
+Check the boxes below to filter the dataset by which lipid probe was used in the pulldown and by significance thresholds.
+
+:::{.border}
+```{r, echo=FALSE}
+
+# Here is the code to make the filterable lists shown in the crosstalk table below
+
+## Creates a reactive dataframe
+data_reactive <- crosstalk::SharedData$new(data)
+
+htmltools::tags$div(
+  class = "filter-container",
+  filter_checkbox(id = "LipidProbe",
+                  label = "Lipid probe in pulldown:", 
+                  sharedData = data_reactive,
+                  group = ~LipidProbe),
+  filter_checkbox(id = "hit_annotation",
+                  label = "Enrichment criteria:", 
+                  sharedData = data_reactive,
+                  group = ~hit_annotation)
+)
+
+?crosstalk::filter_checkbox()
+
+## Displays the reactive dataframe
+datatable(data_reactive, options = list(pageLength = 10))
+
+```
+
+This datatable contains all the data plotted above.
+Check the boxes below to filter the dataset by which lipid probe was used in the pulldown and by significance thresholds.
+'No hit' proteins are unenriched or depleted in the presence of probe, 'enriched candidates' are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and 'enriched hits' are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV.
+:::
+
+### Data download
+
+{{< downloadthis DataTables/AT_ChemicalCommunications_2025_cytosol_download.csv dname="AT_ChemicalCommunications_2025">}}
+
+:::

### 2025-07-23 IndividualStudies/DataTables/DataWrangling/AT_ChemComm2025_wrangling.R

@@ -1,0 +1,54 @@
+####################
+# Data wrangling script for AT_2025
+
+####################
+
+
+# loading packages from source styles script
+library(here)
+
+## Opening the source file for the ggplot custom theme
+source(here::here("Resources/ggplot_styles.R"))
+
+############################################################
+
+# Membrane dataset first 
+
+dataRaw <- readr::read_csv(paste0(here(), "/IndividualStudies/DataTables/DataWrangling/AT_ChemComm2025_membrane.csv")) 
+
+data <- dataRaw |>
+  mutate(
+    gene_name = Gene,
+    protein_id = Protein.ID,
+    hit_annotation = case_when(hit_annotation == "hit" & logFC < 0 ~ "no hit",
+                               hit_annotation == "candidate" & logFC < 0 ~ "no hit",
+                               .default = hit_annotation),
+    LipidProbe = case_when(comparison.label == "PE_UV vs PE_NoUV" ~ "PE",
+                           comparison.label == "PA_UV vs PA_NoUV" ~ "PA")
+  ) |>
+  dplyr::select(gene_name, protein_id, Protein.Description, LipidProbe, sample, logFC, AveExpr, pvalue, hit_annotation, -Gene, -Protein.ID, -comparison.label) |>
+  arrange(hit_annotation) |>
+  glimpse()
+
+# write_csv(data, here("IndividualStudies/DataTables/AT_ChemicalCommunications_2025_membrane_download.csv"))  
+
+
+# Cytosol dataset second
+dataRaw <- readr::read_csv(paste0(here(), "/IndividualStudies/DataTables/DataWrangling/AT_ChemComm2025_cytosol.csv")) 
+
+data <- dataRaw |>
+  mutate(
+    gene_name = Gene,
+    protein_id = Protein.ID,
+    hit_annotation = case_when(hit_annotation == "hit" & logFC < 0 ~ "no hit",
+                               hit_annotation == "candidate" & logFC < 0 ~ "no hit",
+                               .default = hit_annotation),
+    LipidProbe = case_when(comparison.label == "PE_UV vs PE_NoUV" ~ "PE",
+                           comparison.label == "PA_UV vs PA_NoUV" ~ "PA"),
+    sample = case_when(sample == "cytosole" ~ "cytosol",
+                      .default = sample)
+  ) |>
[…]

### 2025-07-23 ShinyApps/CompareLipidProbes/app.R

@@ -5,6 +5,8 @@ library(plotly)
 library(readr)
 library(shiny)
 library(duckplyr)
+library(shinycssloaders)
+
 
 # Load plotting function source
 
@@ -37,7 +39,7 @@ ui <- fluidPage(
       selectInput("probe2", "Select Second LipidProbe:", choices = probeOptions, selected = probeOptions[2])
     ),
     mainPanel(
-      plotlyOutput("logFCPlot"),
+      withSpinner(plotlyOutput("logFCPlot")),
 
     )
   )

### 2025-07-29 index.qmd
I tried cleaning things up and it made a lot of changes... Hoping this will push properly.

@@
   html:
+    template-engine: jinja
     embed-resources: false
+
 standalone: false
@@
 ## Site Overview
-
-<!-- **This repository is still under construction, please forgive us for incomplete sections as we build features!** -->
 
@@
   <a href="LipidProbe/Phosphatidylalcohol.qmd" style="text-decoration: none;">
-      <button style="background-color:rgb(41, 204, 131); color: white; font-size: 20px; padding: 15px 30px; border: none; border-radius: 8px; margin: 10px; cursor: pointer;">
+      <button style="background-color:rgba(41, 204, 131, 1); color: white; font-size: 20px; padding: 15px 30px; border: none; border-radius: 8px; margin: 10px; cursor: pointer;">
           Phosphatidyl Alcohol

### 2025-07-29 IndividualStudies/RM_2021.qmd
adding frank's new pip3 data

@@
 
-# Opening the datatable for this page WHILE TESTING
-# RM_2021_data <- readr::read_csv("IndividualStudies/DataTables/RM_Angewandte_2021_download.csv")
+# Opening the datatable for this page
+RM_2021_data <- readr::read_csv(here("IndividualStudies/DataTables/RM_Angewandte_2021_download.csv")) |>
+  mutate(
+    hit_annotation = case_when(
+      hit_annotation == "enriched hit" & logFC < 0 ~ "hit",
+      hit_annotation == "enriched candidate" & logFC < 0 ~ "candidate",
+      .default = hit_annotation
+    )
+  )
 
-# Opening the datatable for this page WHILE RENDERING
-RM_2021_data <- readr::read_csv("DataTables/RM_Angewandte_2021_download.csv")
+# Organize the hit annotations as factors
+RM_2021_data$hit_annotation <- factor(pull(RM_2021_data, hit_annotation), levels = c("enriched hit", "hit", "enriched candidate", "candidate", "no hit",  "NA"), ordered=TRUE)
 
+RM_2021_data <- RM_2021_data |>
+  arrange(hit_annotation) |>
+  glimpse()
 ```
@@
 
-## Data visualization
+::: {.callout-tip}
 
-#### Heat map
+## Membrane Fraction
 
-#### Venn Diagram
+```{r FilteringForMembraneProteins, include=FALSE, echo=FALSE}
+data <- RM_2021_data |>
+  filter(Fraction == "Membrane (+UV vs -UV)")
+
+```
+
+### Data visualization
+
+::: {.panel-tabset}
+
+#### Volcano plots
+
+:::{.border}
+```{r, echo=FALSE, warning=FALSE}
+#| fig-cap: "Volcano plots depict the relative enrichment of each protein versus non-crosslinked control (x-axis) and the statistical significance of each protein following a Student's t-test (y-axis, -log10 transformed).
+The left panel depicts the results of a pulldown using trifunctionalized phosphatidic acid; the right panel depicts the results of the pulldown using trifunctionalized phosphatidylethanolamine.
+Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV)."
+
+VolcanoPlotStandardized(data)
+
+```
+:::
+
+#### Ranked-order plots
+
+:::{.border}
+```{r, echo=FALSE, warning=FALSE}
+#| fig-cap: "Ranked-order plots depict the relative enrichment of each protein versus non-crosslinked control (y-axis) from lowest to highest.
+The left panel depicts the results of a pulldown using trifunctionalized phosphatidic acid; the right panel depicts the results of the pulldown using trifunctionalized phosphatidylethanolamine.
+Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV)."
+
+RankedOrderPlotStandard(data)
+```
+:::
+
+#### MA Plots
+
+:::{.border}
+```{r, echo=FALSE, warning=FALSE}
+#| fig-cap: "MA plots depict the average abundance of each protein in the crosslinked and uncrosslinked conditions (x-axis) versus the log2-transformed fold-change between the crosslinked and uncrosslinked conditions (y-axis).
+Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV)."
+
+MAStandard(data)
+
+```
+
+:::
+:::
+:::
+
+::: {.callout-tip}
+
+## Cytosolic Fraction
+
+```{r FilteringForCytosolProteins, include=FALSE, echo=FALSE}
+data <- RM_2021_data |>
+  filter(Fraction == "Cytosol (+UV vs -UV)")
+
+```
+
+### Data visualization
+
+::: {.panel-tabset}
+
+#### Volcano plots
+
+:::{.border}
+```{r, echo=FALSE, warning=FALSE}
+#| fig-cap: "Volcano plots depict the relative enrichment of each protein versus non-crosslinked control (x-axis) and the statistical significance of each protein following a Student's t-test (y-axis, -log10 transformed).
+The left panel depicts the results of a pulldown using trifunctionalized phosphatidic acid; the right panel depicts the results of the pulldown using trifunctionalized phosphatidylethanolamine.
+Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV)."
+
+VolcanoPlotStandardized(data)
+
+```
+:::
+
+#### Ranked-order plots
+
+:::{.border}
+```{r, echo=FALSE, warning=FALSE}
+#| fig-cap: "Ranked-order plots depict the relative enrichment of each protein versus non-crosslinked control (y-axis) from lowest to highest.
+The left panel depicts the results of a pulldown using trifunctionalized phosphatidic acid; the right panel depicts the results of the pulldown using trifunctionalized phosphatidylethanolamine.
+Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV)."
+
+RankedOrderPlotStandard(data)
+```
+:::
+
+#### MA Plots
+
+:::{.border}
+```{r, echo=FALSE, warning=FALSE}
+#| fig-cap: "MA plots depict the average abundance of each protein in the crosslinked and uncrosslinked conditions (x-axis) versus the log2-transformed fold-change between the crosslinked and uncrosslinked conditions (y-axis).
+Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV)."
+
+MAStandard(data)
+
+```
+
+:::
+:::
+:::
+
+## Data exploration
+
+Check the boxes below to filter the dataset by which lipid probe was used in the pulldown and by significance thresholds.
+
+:::{.border}
+```{r, echo=FALSE}
+
+RM_2021_data <- RM_2021_data |>
+  select(-hit_annotation_method) |>
+  mutate(
+    logFC = signif(logFC, digits = 4),
+    pvalue = signif(pvalue, digits = 4),
+    AveExpr = signif(AveExpr, digits = 4),
+    fdr = signif(fdr, digits = 4)
+  )
+
+# Here is the code to make the filterable lists shown in the crosstalk table below
+
+## Creates a reactive dataframe
+data_reactive <- crosstalk::SharedData$new(RM_2021_data)
+
+htmltools::tags$div(
+  class = "filter-container",
+  filter_checkbox(id = "LipidProbe",
+                  label = "Lipid probe in pulldown:", 
+                  sharedData = data_reactive,
+                  group = ~LipidProbe),
+  filter_checkbox(id = "hit_annotation",
+                  label = "Enrichment criteria:", 
+                  sharedData = data_reactive,
+                  group = ~hit_annotation),
+  filter_checkbox(id = "Fraction",
+                  label = "Cellular fraction",
+                  sharedData = data_reactive,
+                  group = ~Fraction)
+)
+
+## Displays the reactive dataframe
+datatable(data_reactive, options = list(pageLength = 10))
+
+```
+
+NB: Data analysis overview pending.
+:::
 

### 2025-07-29 SearchByProtein/SearchByProtein.qmd
Added documentation to MaintenanceInstructions, improved standardization
example
adding frank's new pip3 data

--- 2025-02-07 SearchByProtein/SearchByProtein.qmd
@@
 title: "Search enrichment by protein"
+format: 
+  html:
+    embed-resources: false
 ---
@@
 
+here()
 ## Opening the source file for the ggplot custom theme
-source(paste0(here(), "/Resources/ggplot_styles.R"))
+source(here("Resources/ggplot_styles.R"))
 
-# Read call for testing, comment out for rendering
-data <- read_csv(paste0(here(), "/SearchByProtein/combinedProbeDatasets_TMT.csv"))
+data <- read_csv(paste0(here(), "/_data/combinedProbeDatasets_TMT.csv"))
 
 datawhole <- data |>
-	select(gene_name, LipidProbe, hit_annotation, logFC, pvalue, fdr) |>
+	dplyr::select(gene_name, LipidProbe, hit_annotation, logFC, pvalue) |>
 	mutate(logFC = signif(logFC, digits=3),
@@
           options = list(pageLength = 6,
+                          color = "#ffffff",
 												 dom = "l<t>ipr"),
-												 colnames = c("Gene Name", "Lipid Probe", "Hit Annotation", "logFC", "pvalue", "FDR", "Study Details"))
+												 colnames = c("Gene Name", "Lipid Probe", "Hit Annotation", "logFC", "pvalue", "Study Details"))
 

### 2025-07-29 IndividualStudies/DataTables/DataWrangling/RM_2021_Wrangling.R

@@ -1,0 +1,36 @@
+####################
+# Data wrangling script for RM_2021
+
+####################
+
+# loading packages from source styles script
+library(here)
+
+## Opening the source file for the ggplot custom theme
+source(here::here("Resources/ggplot_styles.R"))
+
+dataRaw <- read_csv(here("IndividualStudies/DataTables/DataWrangling/RM_2021_limmaResults.csv")) |>
+  glimpse()
+
+data <- dataRaw |>
+  filter(sample %in% c("UV")) |>
+  filter(comparison.label %in% c("cytosole vs cytosole_minusUV", "membrane vs membrane_minusUV")) |>
+  mutate(
+    Fraction = case_when(
+      comparison.label == "cytosole vs cytosole_minusUV" ~ "Cytosol (+UV vs -UV)",
+      comparison.label == "membrane vs membrane_minusUV" ~ "Membrane (+UV vs -UV)"
+    ),
+    gene_name = Gene,
+    protein_id = Protein.ID,
+    LipidProbe = "PI(3,4,5)P3"
+  ) |>
+  dplyr::select(gene_name, protein_id, Protein.Description, LipidProbe, Fraction, hit_annotation_method, logFC, pvalue, AveExpr, fdr, hit_annotation) |>
+  glimpse()
+
+unique(data$hit_annotation)
+
+data |>
+  filter(hit_annotation %in% c("enriched hit", "enriched candidate")) |>
+  glimpse()
+
+write_csv(data, "IndividualStudies/DataTables/RM_Angewandte_2021_download.csv")

### 2025-07-29 Resources/ggplot_styles.R

@@ -94,9 +94,9 @@ MAStandard <- function(data) {
         scale_x_continuous(limits = c(0.9 * min(safe_abs(data$AveExpr)), 1.1 * max(safe_abs(data$AveExpr))))+
         scale_y_continuous(limits = c(-1.1 * max(safe_abs(data$logFC)), 1.1 * max(safe_abs(data$logFC))))+
         scale_shape_manual(values = c("enriched hit" = 21,
-                                    "hit" = 21,
+                                    "hit" = 22,
                                     "enriched candidate" = 24,
-                                    "candidate" = 24,
+                                    "candidate" = 22,
                                     "no hit" = 22), 
                         name = "Trend") +
         scale_color_manual(values = c("enriched hit" = "black",
@@ -106,21 +106,21 @@ MAStandard <- function(data) {
                                     "no hit" = "black"), 
                         name = "Trend") +
         scale_fill_manual(values = c("enriched hit" = "orange",
-                                    "hit" = "orange",
+                                    "hit" = "black",
                                     "enriched candidate" = "purple",
-                                    "candidate" = "purple",
+                                    "candidate" = "black",
                                     "no hit" = "black"), 
                         name = "Trend") +
         scale_alpha_manual(values = c("enriched hit" = 0.8,
-                                    "hit" = 0.8,
+                                    "hit" = 0.25,
                                     "enriched candidate" = 0.5,
-                                    "candidate" = 0.5,
+                                    "candidate" = 0.25,
                                     "no hit" = 0.25), 
                         name = "Trend") +
         scale_size_manual(values = c("enriched hit" = 4,
-                                    "hit" = 4,
+                                    "hit" = 0.75,
                                     "enriched candidate" = 2,
-                                    "candidate" = 2, 
+                                    "candidate" = 0.75, 
                                     "no hit" = 0.75), 
                         name = "Trend") +
         facet_wrap(~LipidProbe) +
@@ -175,9 +175,9 @@ RankedOrderPlotStandard <- function(data) {
         geom_hline(yintercept = 0, linetype = 2) +
         geom_vline(xintercept = 0, linetype = 2) +
         scale_shape_manual(values = c("enriched hit" = 21,
-                                    "hit" = 21,
+                                    "hit" = 22,
                                     "enriched candidate" = 24,
-                                    "candidate" = 24,
+                                    "candidate" = 22,
                                     "no hit" = 22), 
                         name = "Trend") +
         scale_color_manual(values = c("enriched hit" = "black",
[…]

### 2025-07-29 IndividualStudies/AT_2025.qmd
Removed text about how the AT_2025 data is a test page

--- 2025-06-26 IndividualStudies/AT_2025.qmd
@@
 
-# Data wrangling to prepare Alix's data to the standardized inputs for my plotting functions.
-# Read the data to a df
-
-data <- readr::read_csv(paste0(here(), "/IndividualStudies/DataTables/AT_ChemicalCommunications_2025_download.csv"))
+# Read the membrane data to a df
+data <- readr::read_csv(here("IndividualStudies/DataTables/AT_ChemicalCommunications_2025_membrane_download.csv"))
 
 # Organize the hit annotations as factors
-data$hit_annotation <- factor(pull(data, hit_annotation), levels = c("enriched hit", "enriched candidate", "no hit", "NA"), ordered=TRUE)
+data$hit_annotation <- factor(pull(data, hit_annotation), levels = c("enriched hit", "hit", "enriched candidate", "candidate", "no hit",  "NA"), ordered=TRUE)
 
@@
 ::::
-:::::
+::::: -->
 
-## Data exploration
+### Data exploration
+
+Check the boxes below to filter the dataset by which lipid probe was used in the pulldown and by significance thresholds.
+
+:::{.border}
+```{r, echo=FALSE}
+
+# Here is the code to make the filterable lists shown in the crosstalk table below
+
+## Creates a reactive dataframe
+data_reactive <- crosstalk::SharedData$new(data)
+
+htmltools::tags$div(
+  class = "filter-container",
+  filter_checkbox(id = "LipidProbe",
+                  label = "Lipid probe in pulldown:", 
+                  sharedData = data_reactive,
+                  group = ~LipidProbe),
+  filter_checkbox(id = "hit_annotation",
+                  label = "Enrichment criteria:", 
+                  sharedData = data_reactive,
+                  group = ~hit_annotation)
+)
+
+## Displays the reactive dataframe
+datatable(data_reactive, options = list(pageLength = 10))
+
+```
+
+This datatable contains all the data plotted above.
+Check the boxes below to filter the dataset by which lipid probe was used in the pulldown and by significance thresholds.
+'No hit' proteins are unenriched or depleted in the presence of probe, 'enriched candidates' are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and 'enriched hits' are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV.
+:::
+
+### Data download
+
+{{< downloadthis DataTables/AT_ChemicalCommunications_2025_membrane_download.csv dname="AT_ChemicalCommunications_2025">}}
+
+:::
+
+:::{.callout-tip}
+
+## Cytosolic Fraction
+
+### Data visualization
+
+```{r setup2, echo=FALSE, include=FALSE}
+
+## intitialize libraries
+library(here)
+library(dplyr)
+library(duckplyr)
+library(ggplot2)
+library(ggrepel)
+library(emojifont)
+library(dplyr)
+library(tidyr)
+library(docstring)
+library(clusterProfiler)
+library(org.Hs.eg.db)
+library(enrichplot)
+library(igraph)
+library(ggtangle)
+library(stringr)
+library(crosstalk)
+library(plotly)
+library(grid)
+library(readr)
+library(rmarkdown)
+library(gt)
+library(DT)
+library(heatmaply)
+library(ggvenn)
+library(scales)
+library(htmltools)
+
+## Opening the source file for the ggplot custom theme
+source(paste0(here(), "/Resources/ggplot_styles.R"))
+
+# Read the membrane data to a df
+data <- readr::read_csv(here("IndividualStudies/DataTables/AT_ChemicalCommunications_2025_Cytosol_download.csv"))
+
+# Organize the hit annotations as factors
+data$hit_annotation <- factor(pull(data, hit_annotation), levels = c("enriched hit", "hit", "enriched candidate", "candidate", "no hit",  "NA"), ordered=TRUE)
+
+data |>
+  arrange(hit_annotation) |>
+  glimpse()
+
+```
+
+::: {.panel-tabset}
+
+#### Volcano plots
+
+:::{.border}
+```{r, echo=FALSE, warning=FALSE}
+#| fig-cap: "Volcano plots depict the relative enrichment of each protein versus non-crosslinked control (x-axis) and the statistical significance of each protein following a Student's t-test (y-axis, -log10 transformed).
+The left panel depicts the results of a pulldown using trifunctionalized phosphatidic acid; the right panel depicts the results of the pulldown using trifunctionalized phosphatidylethanolamine.
+Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV)."
+
+VolcanoPlotStandardized(data)
+
+```
+:::
+
+#### Ranked-order plots
+
+:::{.border}
+```{r, echo=FALSE, warning=FALSE}
+#| fig-cap: "Ranked-order plots depict the relative enrichment of each protein versus non-crosslinked control (y-axis) from lowest to highest.
+The left panel depicts the results of a pulldown using trifunctionalized phosphatidic acid; the right panel depicts the results of the pulldown using trifunctionalized phosphatidylethanolamine.
+Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV)."
+
+RankedOrderPlotStandard(data)
+```
+:::
+
+#### MA Plots
+
+:::{.border}
+```{r, echo=FALSE, warning=FALSE}
+#| fig-cap: "MA plots depict the average abundance of each protein in the crosslinked and uncrosslinked conditions (x-axis) versus the log2-transformed fold-change between the crosslinked and uncrosslinked conditions (y-axis).
+Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV)."
+
+MAStandard(data)
+
+```
+
+:::
+:::
+<!-- 
+### Gene Ontology Analysis
+
+**In beta: GO analysis still under development**
+
+:::::{.border}
+::::{#fig-PE_GOplots}
+::: {.panel-tabset}
+
+#### Cell Compartment
+
+<iframe src="/IndividualStudies/GO_plots/PE-PA_AT_2025_CC-DOTplot.html" width="100%" height="500px"></iframe>
+
+#### Molecular Function
+
+<iframe src="/IndividualStudies/GO_plots/PE-PA_AT_2025_MF-DOTplot.html" width="100%" height="500px"></iframe>
+
+#### Biological Process
+
+<iframe src="/IndividualStudies/GO_plots/PE-PA_AT_2025_BP-DOTplot.html" width="100%" height="500px"></iframe>
+
+:::
+
+GO Dot plots display the enrichment of GO terms among the proteins enriched to the probe.
+For these analyses, only proteins categorized as "enriched candidates" and "enriched hits" were subject to GO analysis.
+The Cell Compartment analysis assesses whether the list of enriched proteins contains a statistically significant number of proteins in the same cellular region; appropriately, the Molecular Function and Biological Process analyses does the same for molecular function and biological process, respectively.
+[Click here for more information about Gene Ontology analysis.](/Background/DataAnalysisAndStatistics.qmd#gene-ontology-overview)
+::::
+::::: -->
+
+### Data exploration
 
@@
 
-## Data download
+### Data download
 
-{{< downloadthis DataTables/AT_ChemicalCommunications_2025_download.csv dname="AT_ChemicalCommunications_2025">}}
+{{< downloadthis DataTables/AT_ChemicalCommunications_2025_cytosol_download.csv dname="AT_ChemicalCommunications_2025">}}
+
+:::

### 2025-07-29 IndividualStudies/AT_2025.qmd
Spent a long time learning about custom divs, applied a new one for cell types

@@
   html:
-    embed-resources: true
-standalone: true
+    embed-resources: false
+
+standalone: false
 ---
@@
 
-::: {.callout-tip}
-
-## Membrane Fraction
+:::{.cells collapse="true"}
+::::{.cells-header}
+Membrane Fraction
+::::
+::::{.cells-container}
 
@@
 :::
+::::
 :::
+
 <!-- 
@@
 
-:::{.callout-tip}
-
-## Cytosolic Fraction
+:::{.cells collapse="true"}
+::::{.cells-header}
+Cytosolic Fraction
+::::
+::::{.cells-container}
 
@@
 
+::::
 :::

### 2025-07-29 LipidProbe/Glycosylphosphatidylinositol.qmd
Fixed GPI download link
Spent a long time learning about custom divs, applied a new one for cell types

@@
     embed-resources: false
-callout-icon: false
 ---
@@
 
-{{< downloadthis LipidProbe/DataSets/bf-GPI_SK_2024_ChemEuro.csv dname="bf-GPI_SK_2024_ChemEuro">}}
+{{< downloadthis DataSets/bf-GPI_SK_2024_ChemEuro.csv dname="bf-GPI_SK_2024_ChemEuro">}}
 

### 2025-07-29 LipidProbe/Sphingosine.qmd
Spent a long time learning about custom divs, applied a new one for cell types

@@
 
-:::: {.callout-tip}
-
-### Cell background: Huh7
+:::{.cells collapse="true"}
+::::{.cells-header}
+Cell background: Huh7
+::::
+::::{.cells-container}
 
@@
 ::::
+:::
 
-:::: {.callout-tip}
-
-### Cell background: HeLa
+:::{.cells collapse="true"}
+::::{.cells-header}
+Cell background: HeLa
+::::
+::::{.cells-container}
 
@@
 
+**\*Data presentation still in development.**
+
 ::::
+:::

### 2025-07-29 Resources/testing.qmd
Spent a long time learning about custom divs, applied a new one for cell types

::: todo
Remember to complete this section.
:::

::: test
This information is crucial for understanding the concept.
:::

::: {.thumbs-up title="That was a hard task!"}
You did a great job completing this task.
:::

::: {.cells}
Does this do it??
:::

:::{.cells}
::::{.cells-header}
Membrane fraction
::::
::::{.cells-container}
* Know how to make your own callouts.
* Be able to mess with some SCSS/CSS styling.
::::
:::

::: {.callout-tip}

## Membrane Fraction

* content
* content
* content
:::

### 2025-07-29 _site/LipidProbe/PhosphatidylAlcohol.qmd
Spent a long time learning about custom divs, applied a new one for cell types

@@
 #| fig-cap: "Data as reported in [Yu et al., 2021](/IndividualStudies/WY_2021.qmd).
+MA plots depict the average abundance of each protein in the crosslinked and uncrosslinked conditions (x-axis) versus the log2-transformed fold-change between the crosslinked and uncrosslinked conditions (y-axis).
 Black proteins are designated as not statistically significant.

### 2025-07-30 BioinformaticsApplicationNote/GG_2025_applicationNote.qmd
Working on the application note

@@
 page-navigation: false
+
+format:
+  docx:
+    fig-height: 5
+    reference-doc: custom-reference-doc.docx
+  # pdf: 
+  #   latex-engine: pdflatex
 ---
@@
 
-This site can be viewed at [LipidInteractome.org](lipidinteractome.org) all data is available for download. No user information is collected or necessary for data navigation and interaction.
+This site can be viewed at [LipidInteractome.org](lipidinteractome.org) all data is available for download. No user information is collected or necessary for data navigation, interaction, or download.
 
@@
 
-Recent advances in developing multifunctionalized lipid analogs have revolutionized the field, enabling the systematic interrogation of lipid interactomes[@schultzFlashClickMultifunctionalized2022a].
+Recent advances in synthetic, multifunctionalized lipid analogs have revolutionized the field, enabling the systematic interrogation of lipid interactomes[@schultzFlashClickMultifunctionalized2022a].
 These probes incorporate strategically designed functional groups that enable covalent crosslinking, affinity enrichment, and controlled activation.
@@
 
-Several studies have already employed these lipid probes to elucidate the interactomes of key bioactive lipids, including diacylglycerol, sphingosine, sphinganine, phosphatidic acid, and phosphatidylethanolamine, N-acylphosphatidylethanolamine, and  phosphatidyl alcohol[@hoglingerTrifunctionalLipidProbes2017; @farleyTrifunctionalSphinganineNew2024a; @farleyTrifunctionalFattyAcid2024; @thomasTrifunctionalLipidDerivatives2025; @chiuPhotoaffinityLabelingReveals2025; @yuChemoproteomicsApproachProfile2022].
+Numerous studies have already employed these lipid probes to elucidate the interactomes of key bioactive lipids, including diacylglycerol, sphingosine, sphinganine, phosphatidic acid, and phosphatidylethanolamine, N-acylphosphatidylethanolamine, and  phosphatidyl alcohol[@hoglingerTrifunctionalLipidProbes2017; @farleyTrifunctionalSphinganineNew2024a; @farleyTrifunctionalFattyAcid2024; @thomasTrifunctionalLipidDerivatives2025; @chiuPhotoaffinityLabelingReveals2025; @yuChemoproteomicsApproachProfile2022; @mullerSynthesisCellularLabeling2021].
 These initial studies have followed a comparative proteomics workflow, wherein crosslinked (“+UV”) and non-crosslinked (“-UV”) samples are analyzed side by side to minimize artifacts and confirm specificity[@haberkantFatFabulousBifunctional2014; @schultzChemicalToolsLipid2023].
@@
 This resource consolidates proteomics data from multifunctional lipid probes, enabling researchers to efficiently explore and contextualize lipid-binding proteins across different lipid species and cellular models.
-Currently, the repository hosts interactomes derived from trifunctionalized phosphatidic acid, phosphatidylethanolamine, N-acylphosphatidylethanolamine, phosphatidyl alcohol, sphingosine, and sphinganine in HeLa and Huh7 cells[@thomasTrifunctionalLipidDerivatives2025; @chiuPhotoaffinityLabelingReveals2025; @yuChemoproteomicsApproachProfile2022; @farleyTrifunctionalSphinganineNew2024a].
+Currently, the repository hosts interactomes derived from trifunctionalized phosphatidic acid, phosphatidylethanolamine, phosphatidylinositol *tris*phosphate, N-acylphosphatidylethanolamine, phosphatidyl alcohol, sphingosine, and sphinganine in HeLa and Huh7 cells[@thomasTrifunctionalLipidDerivatives2025; @mullerSynthesisCellularLabeling2021; @chiuPhotoaffinityLabelingReveals2025; @yuChemoproteomicsApproachProfile2022; @farleyTrifunctionalSphinganineNew2024a].
 Additionally, it includes control datasets from two fatty acid probes to distinguish specific from non-specific lipid-binding proteins[@farleyTrifunctionalFattyAcid2024].
@@
 The Lipid Interactome is an interactive discovery platform built using Quarto, designed to centralize and enhance the study of lipid–protein interactions through curated datasets and dynamic visualization tools.
-Each page seamlessly integrates R-generated figures, embedding scripts directly into the source material to ensure reproducibility and transparency.
+Each page integrates R-generated figures, embedding scripts directly into the source material to ensure reproducibility and transparency.
 The repository currently hosts data from seven published studies, with an expandable framework that supports the incorporation of future datasets as the field progresses.
 
-At its core, the Lipid Interactome enables the direct comparison of lipid interactomes across studies, providing researchers with invaluable insights into the diverse roles that bioactive lipids play in cellular processes.
-By leveraging standardized data formatting and interactive visualization—including study-specific analysis pages, lipid probe aggregation, and cross-study comparisons via a Shiny application—the platform facilitates intuitive exploration of protein–lipid interactions.
+At its core, the Lipid Interactome enables the direct, qualitative comparison of lipid interactomes between studies, providing researchers with invaluable insights into the diverse roles that bioactive lipids play in cellular processes.
+By leveraging standardized data formatting and interactive visualization -- including study-specific analysis pages, lipid probe aggregation, and cross-study comparisons via a Shiny application -- the platform facilitates intuitive exploration of protein–lipid interactions.
 As a living repository, we actively encourage researchers to contribute their findings through our [Data Submission](https://lipidinteractome.org/contactus/datasubmission) page, ensuring that this resource continues to evolve alongside advancements in lipidomics research.
@@
 This standardization effort facilitates direct cross-study comparisons without requiring extensive reformatting by the end user.
+Each dataset is accompanied by metadata which describe the sample handling and data analysis techniques -- with clarifying text describing how "significance" is determined for each analysis.
 
@@
 To facilitate efficient exploration and analysis of lipid–protein interaction data, the Lipid Interactome repository incorporates a suite of interactive visualization and data access tools.
-These modules are designed to enhance user engagement, provide clear interpretability of experimental findings, and streamline data retrieval for further computational analysis.
+These modules are designed to enhance user engagement, provide clear interpretability of experimental findings, and streamline data retrieval for further computational analysis -- overall, the site is designed to ensure that the Lipid Interactome is not merely a static repository, but rather a dynamic and evolving resource for lipid biologists and bioinformaticians alike.
 
@@
 
-Each study contributing to the repository is provided with a dedicated results page, allowing users to examine its findings in detail.
+Each publication contributing to the repository is provided with a dedicated results page, allowing users to examine study findings in detail.
 These pages include interactive Volcano, Ranked-Order, and MA plots, which enable visualization of differential protein enrichment across experimental conditions.
-The plots are rendered using the Plotly and htmlwidgetsR packages, ensuring a responsive, client-side experience that supports zooming, hovering, and data filtering[@plotly; @ramnathvaidyanathanHtmlwidgetsHTMLWidgets2015].
+The plots are rendered using the Plotly and htmlwidgetsR packages, ensuring a responsive, client-side experience that supports zooming, hovering, image export, and data filtering[@plotly; @ramnathvaidyanathanHtmlwidgetsHTMLWidgets2015].
 For transparency and reproducibility, all datasets associated with a given study are available for direct download.
@@
 
-Beyond individual study pages, datasets are further organized by lipid probe, providing a consolidated view of protein interactors detected across multiple experiments.
-Each lipid-specific page includes study metadata, cell type, and facilitates cross-study comparisons.
+In addition to the pages for each independent publication, datasets are further organized by lipid probe, providing a consolidated view of protein interactors detected across multiple experiments and independent studies.
+Each lipid-specific page includes study metadata and cell type -- facilitating cross-study comparisons.
 Future iterations of the repository will extend this functionality by enabling direct comparisons of interactomes obtained from different cell lines treated with the same lipid probe, further refining the contextual understanding of lipid–protein interactions.
@@
 
-Where study design permits, data has been integrated into an interactive Shiny application, allowing users to perform direct probe-to-probe comparisons ([Probe vs Probe Comparisons](https://www.lipidinteractome.org/lipidprobe/enrichedhitscomparison)).
+Where study design permits, data has been integrated into an interactive Shiny application, allowing users to perform direct (though qualitative) probe-to-probe comparisons ([Probe vs Probe Comparisons](https://www.lipidinteractome.org/lipidprobe/enrichedhitscomparison)).
 This tool enables researchers to explore the similarity of lipid interactomes across experimental conditions via linear regression analysis, highlighting proteins that are significantly enriched in one dataset, both datasets, or neither.
@@
 
-These data access and visualization tools are designed to ensure that the Lipid Interactome is not merely a static repository, but rather a dynamic and evolving resource for lipid biologists and bioinformaticians alike.
+Because each publication utilizes distinct sample handling and data analysis techniques, we emphasize that these comparisons are qualitative -- we hope to discourage quantitative statements regarding relative enrichment between lipid probes (e.g.
+"Protein X is enriched 3x more to Lipid A than to Lipid B").
+However, great utility lies in assessing co-enrichment (or orthogonal enrichment) of proteins to disparate lipid probes without quantitative comparison.
 
@@
 
-While there are numerous ways to quantify the mass spectrometry (MS) data, the majority of studies included in our repository have utilized the same (or highly similar) quantitative MS pipeline using Tandem Mass Tagging[@thompsonTandemMassTags2003].
+While there are numerous ways to quantify the mass spectrometry (MS) data, the majority of studies included in our repository have utilized the same (or highly similar) quantitative MS pipeline using data-dependent acquisition techniques, such as Tandem Mass Tagging[@thompsonTandemMassTags2003].
 These datasets include those reported by Farley et al.
@@
 
-| Gene name | logFC | p value |  AveExpr   |  FDR   |
-|:----------|:------------------------:|:-------:|:----------:|:------:|
-| GeneA     |           1.2            |  0.001  | 1.0x10^18^ | 0.0001 |
-| GeneB     |           0.1            |   0.6   | 1.0x10^5^  | 0.005  |
-| ...       |           ...            |   ...   |    ...     |  ...   |
+| Gene name | [Uniprot accession](https://www.uniprot.org/help/accession_numbers) | logFC | p value |  AveExpr   |  FDR   |
+|:---------- | :------: |:------------------------:|:-------:|:----------:|:------:|
+| GeneA     | P80723 |           1.2            |  0.001  | 1.0x10^18^ | 0.0001 |
+| GeneB     | P32004 |          0.1            |   0.6   | 1.0x10^5^  | 0.005  |
+| ...       | ... |          ...            |   ...   |    ...     |  ...   |
 : **Example data table for smooth incorporation into Lipid Interactome.** ***Column descriptions:*** *Gene name*: The identifier for genes identified in the dataset (or Accession Number).
+*Uniprot accession*: Stable identifiers of UniProtKB entries; integrates species and isoform data on the identified protein.
 *Enrichment value*: Fold change of Experimental versus Control fold-change, typically log2-transformed -- ideally the product of TMT or other quantitative mass spectrometry methods.
@@
 
-We are working on providing visualization functionality for studies which utilized Peptide Spectral Matching to report enrichment toward lipid probes.
+**We wish to emphasize that we will collaborate with data providers to prepare visualizations which best suit their datasets -- the example dataset above merely depicts an ideal case which allows for easy incorporation and cross-study comparison.**
+
+Additionally, we are working on providing visualization functionality for studies which utilized Peptide Spectral Matching (PSM) to report enrichment toward lipid probes.
+Similarly, data-independent acquisitio (DIA) is a quickly emerging alternative to data-dependent acquisition (DDA; e.g.
+TMT) [@birhanuMassSpectrometrybasedProteomics2023; @boysClinicalApplicationsMass2023]; as with PSM datasets, we are working to incorporate DIA data formats.
 
@@
 This functionality will not only reduce redundancy in experimental design but also strengthen the reproducibility and biological interpretation of lipid interactome research.
-To support this vision, we invite researchers to contribute their datasets via our [Data Submission page](https://www.lipidinteractome.org/DataSubmission.html), fostering a collaborative and transparent approach to lipid biology.
+To support this vision, we invite researchers to contribute their datasets via our [Data Submission page](https://lipidinteractome.org/contactus/datasubmission), fostering a collaborative and transparent approach to lipid biology.
 
@@
 : *An*alysis *o*f *Va*riance
+
+PSM
+: *P*eptide *S*pectral *M*atching
+
+DIA
+: *D*ata-*I*ndedpendent *A*cquisition
+
+DDA
+: *D*ata-*D*edpendent *A*cquisition
 
@@
 The authors have no conflicts of interest to declare.
+
+<br>
+
+## Citations
+
+:::{#refs}
+:::

### 2025-07-30 _site/BioinformaticsApplicationNote/GG_2025_applicationNote.tex
Working on the application note

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  letterpaper,
  DIV=11,
  numbers=noendperiod]{scrartcl}

\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\makeatletter
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}{
    \@ifstar
      \xxxParagraphStar
      \xxxParagraphNoStar
  }
  \newcommand{\xxxParagraphStar}[1]{\oldparagraph*{#1}\mbox{}}
  \newcommand{\xxxParagraphNoStar}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}{
    \@ifstar
      \xxxSubParagraphStar
      \xxxSubParagraphNoStar
  }
  \newcommand{\xxxSubParagraphStar}[1]{\oldsubparagraph*{#1}\mbox{}}
  \newcommand{\xxxSubParagraphNoStar}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\makeatother

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\newsavebox\pandoc@box
\newcommand*\pandocbounded[1]{% scales image to fit in text height/width
  \sbox\pandoc@box{#1}%
  \Gscale@div\@tempa{\textheight}{\dimexpr\ht\pandoc@box+\dp\pandoc@box\relax}%
  \Gscale@div\@tempb{\linewidth}{\wd\pandoc@box}%
  \ifdim\@tempb\p@<\@tempa\p@\let\@tempa\@tempb\fi% select the smaller of both
  \ifdim\@tempa\p@<\p@\scalebox{\@tempa}{\usebox\pandoc@box}%
  \else\usebox{\pandoc@box}%
  \fi%
}
% Set default figure placement to htbp
\def\fps@figure{htbp}
\makeatother
% definitions for citeproc citations
\NewDocumentCommand\citeproctext{}{}
\NewDocumentCommand\citeproc{mm}{%
  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
\makeatletter
 % allow citations to break across lines
 \let\@cite@ofmt\@firstofone
 % avoid brackets around text for \cite:
 \def\@biblabel#1{}
 \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
 {\begin{list}{}{%
  \setlength{\itemindent}{0pt}
  \setlength{\leftmargin}{0pt}
  \setlength{\parsep}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
   \setlength{\leftmargin}{\cslhangindent}
   \setlength{\itemindent}{-1\cslhangindent}
  \fi
  % set entry spacing
  \setlength{\itemsep}{#2\baselineskip}}}
 {\end{list}}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\KOMAoption{captions}{tableheading}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother

\usepackage{bookmark}

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={The Lipid Interactome},
  pdfkeywords={Lipid-protein
interactions, Proteomics, Interactomics, Database, Multifunctionalized
lipids},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{The Lipid Interactome}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{An interactive and open access platform for exploring cellular
lipid-protein interactomes}
\author{Gaelen Guzman \and André Nadler \and Frank Stein \and Jeremy M.
Baskin \and Carsten Schultz \and Fikadu Tafesse}
\date{2025-02-04}

\begin{document}
\maketitle

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsection{Authors}\label{authors}

Gaelen Guzman\textsuperscript{1,}*, André Nadler\textsuperscript{2},
Frank Stein\textsuperscript{3}, Jeremy M. Baskin\textsuperscript{4},
Carsten Schulz\textsuperscript{1}, Fikadu G. Tafesse\textsuperscript{1}

\textsuperscript{1} = Departments of Molecular Immunology and Immunology
and Chemical Physiology and Biochemistry, Oregon Health \& Science
University, Portland, OR, USA; \textsuperscript{2} = Max Plank Institute
of Molecular Cell Biology and Genetics, Dresden Germany;
\textsuperscript{3} = Proteomics Core Facility, European Molecular
Biology Laboratory, Heidelberg, Germany; \textsuperscript{4} =
Department of Chemistry and Chemical Biology and Weill Institute for
Cell and Molecular Biology, Cornell University, Ithaca, NY, USA; * =
Corresponding author:
\href{mailto:gaelen.guzman@lipidinteractome.org}{\nolinkurl{gaelen.guzman@lipidinteractome.org}}

\subsection{Summary}\label{summary}

\subsubsection{Abstract}\label{abstract}

Lipid--protein interactions play essential roles in cellular signaling
and membrane dynamics, yet their systematic characterization has long
been hindered by the inherent biochemical properties of lipids. Recent
advances in functionalized lipid probes -- equipped with
photoactivatable crosslinkers, affinity handles, and photocleavable
protecting groups -- have enabled proteomics-based identification of
lipid interacting proteins with unprecedented specificity and
resolution. Despite the growing number of published lipid interactomes,
there remains no centralized effort to harmonize, compare, or integrate
these datasets.

The Lipid Interactome addresses this gap by providing a structured,
interactive web portal that adheres to FAIR data principles -- ensuring
that lipid interactome studies are Findable, Accessible, Interoperable,
and Reusable. Through standardized data formatting, interactive
visualizations, and direct cross-study comparisons, this resource
enables researchers to systematically explore the protein-binding
partners of diverse bioactive lipids. By consolidating and curating
lipid interactome proteomics data from multiple studies, the Lipid
Interactome database serves as a critical tool for deciphering the
biological functions of lipids in cellular systems.

\subsubsection{Availability}\label{availability}

This site can be viewed at
\href{lipidinteractome.org}{LipidInteractome.org} all data is available
for download. No user information is collected or necessary for data
navigation, interaction, or download.

\subsubsection{Data Submission \&
Contact}\label{data-submission-contact}

If you would like to submit a relevant dataset, see our
\href{https://lipidinteractome.org/contactus/datasubmission}{Data
Submission Page} for details, contact info, and instructions. For site
feedback and additional questions, please email the site administrators
at
\href{mailto:Contact.Us@lipidinteractome.org}{\nolinkurl{Contact.Us@lipidinteractome.org}}

\subsubsection{Keywords}\label{keywords}

Lipid-protein interactions, proteomics, interactomics, database,
multifunctionalized lipids, photoaffinity labeling

\subsection{Introduction}\label{introduction}

Historically, lipids have been considered merely the passive structural
components of cellular membranes. However, recent decades have revealed
that this diverse category of biomolecule plays essential and active
roles in the cell, ranging from modulating membrane dynamics,
determining organelle identity, serving as catabolites for energy
storage and metabolism, and bioactive signaling mediators for organellar
and intracellular signaling\textsuperscript{1--6}. Interactions with
proteins are essential to many of these crucial lipid functions -- and
yet, lipid--protein interactions are extremely challenging to study: The
small size and biophysical properties of lipids make conventional
proteomics approaches unsuitable for mapping lipid
interactors\textsuperscript{7}. Unlike proteins, which can be readily
tagged or immobilized for affinity-based interaction studies, lipids
require specialized chemical modifications to enable selective and
controlled interaction profiling\textsuperscript{8}.

Recent advances in synthetic, multifunctionalized lipid analogs have
revolutionized the field, enabling the systematic interrogation of lipid
interactomes\textsuperscript{8}. These probes incorporate strategically
designed functional groups that enable covalent crosslinking, affinity
enrichment, and controlled activation. Most commonly, these include: (1)
a diazirine group for photoactivatable crosslinking upon exposure to 355
nm ultraviolet (UV) light, stabilizing non-covalent and often
modest-affinity lipid--protein interactions; (2) a terminal alkyne,
permitting click chemistry-based enrichment; and, in some cases, (3) a
coumarin photocage, which shields the lipid probe from premature
enzymatic modification until it is selectively cleaved by 405 nm light
(a wavelength that does not induce diazirine
photolysis)\textsuperscript{7--10}. Together, these modifications enable
direct proteomic identification of lipid interactors, distinguishing
true binding partners from transient or non-specific
associations\textsuperscript{7,10,11}.

Numerous studies have already employed these lipid probes to elucidate
the interactomes of key bioactive lipids, including diacylglycerol,
sphingosine, sphinganine, phosphatidic acid, and
phosphatidylethanolamine, N-acylphosphatidylethanolamine, and
phosphatidyl alcohol\textsuperscript{9,11--16}. These initial studies
have followed a comparative proteomics workflow, wherein crosslinked
(``+UV'') and non-crosslinked (``-UV'') samples are analyzed side by
side to minimize artifacts and confirm
specificity\textsuperscript{7,10}. However, despite the growing number
of lipid interactome datasets, no centralized resource has existed to
compile, compare, and standardize these findings.

To address this gap, we present the
\href{https://www.lipidinteractome.org}{Lipid Interactome} -- a curated
repository designed to facilitate the comparative analysis of
lipid--protein interactions from multiple studies. This resource
consolidates proteomics data from multifunctional lipid probes, enabling
researchers to efficiently explore and contextualize lipid-binding
proteins across different lipid species and cellular models. Currently,
the repository hosts interactomes derived from trifunctionalized
phosphatidic acid, phosphatidylethanolamine, phosphatidylinositol
\emph{tris}phosphate, N-acylphosphatidylethanolamine, phosphatidyl
alcohol, sphingosine, and sphinganine in HeLa and Huh7
cells\textsuperscript{11,13--16}. Additionally, it includes control
datasets from two fatty acid probes to distinguish specific from
non-specific lipid-binding proteins\textsuperscript{12}. We additionally
intend to expand this resource to include more complex experimental
designs as they are published (e.g.~Disease versus Healthy Control or
Infection versus Mock).

By providing a centralized platform for lipid interactome data, the
Lipid Interactome significantly lowers the barriers to entry for
researchers investigating lipid signaling pathways, enabling hypothesis
generation through comparative analysis of multiple studies. Overall,
this repository represents an important step toward systematizing
lipid--protein interaction studies, ensuring that bioactive lipids are
afforded the same level of proteomic scrutiny as their protein
counterparts.

\subsection{Description}\label{description}

\subsubsection{Overview}\label{overview}

The~Lipid Interactome~is an interactive discovery platform built
using~Quarto, designed to centralize and enhance the study of
lipid--protein interactions through curated datasets and dynamic
visualization tools. Each page integrates~R-generated figures, embedding
scripts directly into the source material to ensure reproducibility and
transparency. The repository currently hosts data from~seven published
studies, with an expandable framework that supports the incorporation of
future datasets as the field progresses.

At its core, the~Lipid Interactome~enables the~direct, qualitative
comparison~of lipid interactomes between studies, providing researchers
with invaluable insights into the diverse roles that bioactive lipids
play in cellular processes. By leveraging standardized data formatting
and interactive visualization -- including study-specific analysis
pages, lipid probe aggregation, and cross-study comparisons via
a~Shiny~application -- the platform facilitates intuitive exploration of
protein--lipid interactions. As a~living repository, we actively
encourage researchers to contribute their findings through
our~\href{https://lipidinteractome.org/contactus/datasubmission}{Data~Submission}~page,
ensuring that this resource continues to evolve alongside advancements
in lipidomics research.

\subsubsection{FAIR data principles}\label{fair-data-principles}

The~Lipid Interactome~database was developed with the FAIR (Findable,
Accessible, Interoperable, and Reusable) data principles in mind,
ensuring that lipid--protein interaction data can be systematically
explored, compared, and reused by the research community. Given the
historical inconsistency in proteomics data curation, we have taken
deliberate steps to standardize, annotate, and document our datasets for
maximum utility.

\paragraph{Findable}\label{findable}

To address the fragmented nature of lipid interactome studies, we have
established a centralized platform where researchers can interact with
the results of individual studies or explore aggregated findings across
multiple studies on a given lipid. The repository is structured to
facilitate intuitive navigation between experimental datasets, offering
clear entry points for study-specific and lipid-specific analyses.
Because this resource is intended as a living repository, we actively
invite researchers to contribute their findings following the submission
guidelines detailed on
our~\href{https://lipidinteractome.org/contactus/datasubmission}{Data
Submission}~page.

\paragraph{Accessible}\label{accessible}

All datasets within~the Lipid Interactome~are available for download in
standardized~\texttt{.csv}~format, ensuring broad accessibility across
different computational environments. To further enhance usability, we
provide
a~\href{https://www.lipidinteractome.org/background/multifunctionallipidprobesoverview}{detailed~overview~of
data~generation~and~analysis}, including explicit descriptions of
dataset structure, column definitions, and the inherent limitations of
multifunctional lipid probes. Only peer-reviewed proteomics datasets are
included in this repository to maintain high data quality and
reliability.

\paragraph{Interoperable}\label{interoperable}

Given the diversity of methodologies employed across lipid interactome
studies, we have taken care to harmonize data formats and metadata
annotations. While many studies share common analytical pipelines,
others employ distinct mass spectrometry workflows. To ensure
consistency, we have structured the data to allow parallel comparisons
and
provided~\href{https://www.lipidinteractome.org/background/proteomicsusingmultifunctionalprobes}{documentation~on~methodological~differences}.
This standardization effort facilitates direct cross-study comparisons
without requiring extensive reformatting by the end user. Each dataset
is accompanied by metadata which describe the sample handling and data
analysis techniques -- with clarifying text describing how
``significance'' is determined for each analysis.

\paragraph{Reusable}\label{reusable}

To maximize the utility of these datasets, we provide extensive
documentation detailing data acquisition, analysis workflows, and
potential limitations. Wherever possible, technical jargon has been
minimized to ensure accessibility to a broad audience, from lipid
biologists to computational scientists. Additionally, we reference key
publications that delve deeper into the synthesis of lipid probes and
the specifics of each proteomics workflow, allowing researchers to
further contextualize and validate their findings.

By adhering to these FAIR principles,~the Lipid Interactome~database
aims to serve as a robust and enduring resource for the lipid biology
community, reducing redundancy, improving data transparency, and
accelerating the study of lipid-mediated signaling.

\subsubsection{Data Visualization and Download
Modules}\label{data-visualization-and-download-modules}

To facilitate efficient exploration and analysis of lipid--protein
interaction data, the~Lipid Interactome~repository incorporates a suite
of interactive visualization and data access tools. These modules are
designed to enhance user engagement, provide clear interpretability of
experimental findings, and streamline data retrieval for further
computational analysis -- overall, the site is designed to ensure that
the~Lipid Interactome~is not merely a static repository, but rather a
dynamic and evolving resource for lipid biologists and bioinformaticians
alike.

\paragraph{Study-Specific Data
Exploration}\label{study-specific-data-exploration}

Each publication contributing to the repository is provided with a
dedicated results page, allowing users to examine study findings in
detail. These pages include interactive~Volcano,~Ranked-Order, and~MA
plots, which enable visualization of differential protein enrichment
across experimental conditions. The plots are rendered using
the~Plotly~and~htmlwidgetsR packages, ensuring a responsive, client-side
experience that supports zooming, hovering, image export, and data
filtering\textsuperscript{17,18}. For transparency and reproducibility,
all datasets associated with a given study are available for direct
download.

\paragraph{Lipid Probe-Specific Pages}\label{lipid-probe-specific-pages}

In addition to the pages for each independent publication, datasets are
further organized by lipid probe, providing a consolidated view of
protein interactors detected across multiple experiments and independent
studies. Each lipid-specific page includes study metadata and cell type
-- facilitating cross-study comparisons. Future iterations of the
repository will extend this functionality by enabling direct comparisons
of interactomes obtained from different cell lines treated with the same
lipid probe, further refining the contextual understanding of
lipid--protein interactions.

\paragraph{Comparative Analysis via Shiny
Application}\label{comparative-analysis-via-shiny-application}

Where study design permits, data has been integrated into an
interactive~Shiny~application, allowing users to perform direct (though
qualitative)~probe-to-probe
comparisons~(\href{https://www.lipidinteractome.org/lipidprobe/enrichedhitscomparison}{Probe~vs~Probe~Comparisons}).
This tool enables researchers to explore the similarity of lipid
interactomes across experimental conditions via~linear regression
analysis, highlighting proteins that are significantly enriched in one
dataset, both datasets, or neither. By providing an intuitive framework
for interactome comparison, this feature aids in the identification of
promising targets for further investigation.

Because each publication utilizes distinct sample handling and data
analysis techniques, we emphasize that these comparisons are qualitative
-- we hope to discourage quantitative statements regarding relative
enrichment between lipid probes (e.g.~``Protein X is enriched 3x more to
Lipid A than to Lipid B''). However, great utility lies in assessing
co-enrichment (or orthogonal enrichment) of proteins to disparate lipid
probes without quantitative comparison.

\subsubsection{Data format}\label{data-format}

While there are numerous ways to quantify the mass spectrometry (MS)
data, the majority of studies included in our repository have utilized
the same (or highly similar) quantitative MS pipeline using
data-dependent acquisition techniques, such as Tandem Mass
Tagging\textsuperscript{19}. These datasets include those reported by
Farley et al.~(2024), Farley et al.~(2024), and Thomas et
al.~(2025)\textsuperscript{11--13}. Some studies have also featured
quantitative MS analysis using stable isotope labeling of amino acids in
cell culture (SILAC), which also enables extraction of key data
described below\textsuperscript{14,15}. Correspondingly, the ideal data
structure for incorporation into our repository will include the
following:

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\linewidth - 10\tabcolsep) * \real{0.1486}}
  >{\centering\arraybackslash}p{(\linewidth - 10\tabcolsep) * \real{0.1081}}
  >{\centering\arraybackslash}p{(\linewidth - 10\tabcolsep) * \real{0.3514}}
  >{\centering\arraybackslash}p{(\linewidth - 10\tabcolsep) * \real{0.1216}}
  >{\centering\arraybackslash}p{(\linewidth - 10\tabcolsep) * \real{0.1622}}
  >{\centering\arraybackslash}p{(\linewidth - 10\tabcolsep) * \real{0.1081}}@{}}
\caption{\textbf{Example data table for smooth incorporation into Lipid
Interactome.} \textbf{\emph{Column descriptions:}} \emph{Gene name}: The
identifier for genes identified in the dataset (or Accession Number).
\emph{Uniprot accession}: Stable identifiers of UniProtKB entries;
integrates species and isoform data on the identified protein.
\emph{Enrichment value}: Fold change of Experimental versus Control
fold-change, typically log2-transformed -- ideally the product of TMT or
other quantitative mass spectrometry methods. \emph{p value}: the
results of an ANOVA or LIMMA analysis, corrected for multiple hypothesis
testing. \emph{AveExpr}: An averaged value of the m/z ion intensity of
the Experimental condition and Control condition used for the enrichment
value (used to prepare MA plots for quality control). \emph{FDR}:
False-discovery rate of protein
identification.}\label{tbl-1}\tabularnewline
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Gene name
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
\href{https://www.uniprot.org/help/accession_numbers}{Uniprot accession}
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
logFC
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
p value
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
AveExpr
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
FDR
\end{minipage} \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Gene name
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
\href{https://www.uniprot.org/help/accession_numbers}{Uniprot accession}
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
logFC
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
p value
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
AveExpr
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
FDR
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
GeneA & P80723 & 1.2 & 0.001 & 1.0x10\textsuperscript{18} & 0.0001 \\
GeneB & P32004 & 0.1 & 0.6 & 1.0x10\textsuperscript{5} & 0.005 \\
\ldots{} & \ldots{} & \ldots{} & \ldots{} & \ldots{} & \ldots{} \\
\end{longtable}

\textbf{We wish to emphasize that we will collaborate with data
providers to prepare visualizations which best suit their datasets --
the example dataset above merely depicts an ideal case which allows for
easy incorporation and cross-study comparison.}

Additionally, we are working on providing visualization functionality
for studies which utilized Peptide Spectral Matching (PSM) to report
enrichment toward lipid probes. Similarly, data-independent acquisitio
(DIA) is a quickly emerging alternative to data-dependent acquisition
(DDA; e.g.~TMT)\textsuperscript{20,21}; as with PSM datasets, we are
working to incorporate DIA data formats.

\subsection{Discussion}\label{discussion}

The advent of functionalized lipid probes has fundamentally transformed
lipid biology by enabling the proteomic identification of lipid-binding
proteins with unprecedented specificity. However, as the number of
published lipid interactome studies grows, the lack of a centralized
framework for comparing and integrating these datasets presents a
significant challenge for deciphering biological functions of individual
lipids and lipid-binding proteins holistically and identifying trends
across datasets. The Lipid Interactome was developed to address this
need by providing researchers with a structured platform to explore,
cross-reference, and build upon previous findings. By aggregating and
standardizing lipid--protein interaction data, this resource facilitates
the rapid identification of candidate lipid-binding proteins and
supports orthogonal validation efforts.

Designed as a continuously expanding repository, the Lipid Interactome
will evolve alongside advances in lipid probe technologies and
interactomics. Future iterations will incorporate validation studies for
each lipid probe, offering researchers a dedicated space to compare
findings across experimental contexts. This functionality will not only
reduce redundancy in experimental design but also strengthen the
reproducibility and biological interpretation of lipid interactome
research. To support this vision, we invite researchers to contribute
their datasets via our
\href{https://lipidinteractome.org/contactus/datasubmission}{Data
Submission page}, fostering a collaborative and transparent approach to
lipid biology.

\subsection{Abbreviations}\label{abbreviations}

\begin{description}
\tightlist
\item[UV]
\emph{U}ltra\emph{V}iolet
\item[MS]
\emph{M}ass \emph{S}pectrometry
\item[LIMMA]
\emph{Li}near \emph{M}odels for \emph{M}icro\emph{a}rray and RNA-Seq
Data
\item[ANOVA]
\emph{An}alysis \emph{o}f \emph{Va}riance
\item[PSM]
\emph{P}eptide \emph{S}pectral \emph{M}atching
\item[DIA]
\emph{D}ata-\emph{I}ndedpendent \emph{A}cquisition
\item[DDA]
\emph{D}ata-\emph{D}edpendent \emph{A}cquisition
\end{description}

\subsection{Contributions}\label{contributions}

GG designed, implemented, and wrote the majority of the LipidInteractome
repository and manuscript. FS wrote the data analysis section of the
repository, provided significant intellectual contribution to the
repository design, and edited the manuscript. AN provided substantial
editing of the repository and manuscript. JMB edited the manuscript and
contributed data to the repository. CS and FT provided significant
intellectual contribution and text editing of the repository and
manuscript and oversaw the site development.

\subsection{Funding}\label{funding}

This work was supported by funding from the National Institutes of
Health (NIAID R01 AI141549-02, to FGT, CS; NIGMS R01 GM127631 to C.S.,
and NIGMS R01 GM151682 to JMB).

\subsection{Conflicts of Interest}\label{conflicts-of-interest}

The authors have no conflicts of interest to declare.

\subsection{Citations}\label{citations}

\phantomsection\label{refs}
\begin{CSLReferences}{0}{0}
\bibitem[\citeproctext]{ref-barischMembraneDamageRepair2023}
\CSLLeftMargin{1. }%
\CSLRightInline{Barisch, C., Holthuis, J. C. M. \& Cosentino, K.
\href{https://doi.org/10.1515/hsz-2022-0321}{Membrane damage and repair:
A thin line between life and death}. \emph{Biological Chemistry}
\textbf{404}, 467--490 (2023).}

\bibitem[\citeproctext]{ref-vanmeerMembraneLipidsWhere2008a}
\CSLLeftMargin{2. }%
\CSLRightInline{van Meer, G., Voelker, D. R. \& Feigenson, G. W.
\href{https://doi.org/10.1038/nrm2330}{Membrane lipids: Where they are
and how they behave}. \emph{Nature Reviews Molecular Cell Biology}
\textbf{9}, 112--124 (2008).}

\bibitem[\citeproctext]{ref-holthuisLipidLandscapesPipelines2014a}
\CSLLeftMargin{3. }%
\CSLRightInline{Holthuis, J. C. M. \& Menon, A. K.
\href{https://doi.org/10.1038/nature13474}{Lipid landscapes and
pipelines in membrane homeostasis}. \emph{Nature} \textbf{510}, 48--57
(2014).}

\bibitem[\citeproctext]{ref-niphakisGlobalMapLipidBinding2015a}
\CSLLeftMargin{4. }%
\CSLRightInline{Niphakis, M. J. \emph{et al.}
\href{https://doi.org/10.1016/j.cell.2015.05.045}{A {Global Map} of
{Lipid-Binding Proteins} and {Their Ligandability} in {Cells}}.
\emph{Cell} \textbf{161}, 1668--1680 (2015).}

\bibitem[\citeproctext]{ref-chernomordikProteinLipidInterplayFusion2003}
\CSLLeftMargin{5. }%
\CSLRightInline{Chernomordik, L. V. \& Kozlov, M. M.
\href{https://doi.org/10.1146/annurev.biochem.72.121801.161504}{Protein-{Lipid
Interplay} in {Fusion} and {Fission} of {Biological Membranes}}.
\emph{Annual Review of Biochemistry} \textbf{72}, 175--207 (2003).}

\bibitem[\citeproctext]{ref-simonsLipidRaftsSignal2000a}
\CSLLeftMargin{6. }%
\CSLRightInline{Simons, K. \& Toomre, D.
\href{https://doi.org/10.1038/35036052}{Lipid rafts and signal
transduction}. \emph{Nature Reviews Molecular Cell Biology} \textbf{1},
31--39 (2000).}

\bibitem[\citeproctext]{ref-schultzChemicalToolsLipid2023}
\CSLLeftMargin{7. }%
\CSLRightInline{Schultz, C.
\href{https://doi.org/10.1021/acs.accounts.2c00851}{Chemical {Tools} for
{Lipid Cell Biology}}. \emph{Accounts of Chemical Research} \textbf{56},
1168--1177 (2023).}

\bibitem[\citeproctext]{ref-schultzFlashClickMultifunctionalized2022a}
\CSLLeftMargin{8. }%
\CSLRightInline{Schultz, C., Farley, S. E. \& Tafesse, F. G.
\href{https://doi.org/10.1021/jacs.2c02705}{{`{Flash} \& {Click}'}:
{Multifunctionalized Lipid Derivatives} as {Tools To Study Viral
Infections}}. \emph{Journal of the American Chemical Society}
\textbf{144}, 13987--13995 (2022).}

\bibitem[\citeproctext]{ref-hoglingerTrifunctionalLipidProbes2017}
\CSLLeftMargin{9. }%
\CSLRightInline{Höglinger, D. \emph{et al.}
\href{https://doi.org/10.1073/pnas.1611096114}{Trifunctional lipid
probes for comprehensive studies of single lipid species in living
cells}. \emph{Proceedings of the National Academy of Sciences}
\textbf{114}, 1566--1571 (2017).}

\bibitem[\citeproctext]{ref-haberkantFatFabulousBifunctional2014}
\CSLLeftMargin{10. }%
\CSLRightInline{Haberkant, P. \& Holthuis, J. C. M.
\href{https://doi.org/10.1016/j.bbalip.2014.01.003}{Fat \& fabulous:
{Bifunctional} lipids in the spotlight}. \emph{Biochimica et Biophysica
Acta - Molecular and Cell Biology of Lipids} \textbf{1841}, 1022--1030
(2014).}

\bibitem[\citeproctext]{ref-farleyTrifunctionalSphinganineNew2024a}
\CSLLeftMargin{11. }%
\CSLRightInline{Farley, S., Stein, F., Haberkant, P., Tafesse, F. G. \&
Schultz, C.
\href{https://doi.org/10.1021/acschembio.3c00554}{Trifunctional
{Sphinganine}: {A New Tool} to {Dissect Sphingolipid Function}}.
\emph{ACS Chemical Biology} \textbf{19}, 336--347 (2024).}

\bibitem[\citeproctext]{ref-farleyTrifunctionalFattyAcid2024}
\CSLLeftMargin{12. }%
\CSLRightInline{Farley, S. E. \emph{et al.}
\href{https://doi.org/10.1039/D4CC00974F}{Trifunctional fatty acid
derivatives: The impact of diazirine placement}. \emph{Chemical
Communications} \textbf{60}, 6651--6654 (2024).}

\bibitem[\citeproctext]{ref-thomasTrifunctionalLipidDerivatives2025}
\CSLLeftMargin{13. }%
\CSLRightInline{Thomas, A. \emph{et al.} Trifunctional lipid
derivatives: {PE}'s mitochondrial interactome. \emph{Chemical
Communications} 10.1039.D4CC03599B (2025)
doi:\href{https://doi.org/10.1039/D4CC03599B}{10.1039/D4CC03599B}.}

\bibitem[\citeproctext]{ref-chiuPhotoaffinityLabelingReveals2025}
\CSLLeftMargin{14. }%
\CSLRightInline{Chiu, D.-C., Lin, H. \& Baskin, J. M. Photoaffinity
{Labeling Reveals} a {Role} for the {Unusual Triply Acylated
Phospholipid N-Acylphosphatidylethanolamine} in {Lactate Homeostasis}.
(2025)
doi:\href{https://doi.org/10.26434/chemrxiv-2025-j8nqz}{10.26434/chemrxiv-2025-j8nqz}.}

\bibitem[\citeproctext]{ref-yuChemoproteomicsApproachProfile2022}
\CSLLeftMargin{15. }%
\CSLRightInline{Yu, W., Lin, Z., Woo, C. M. \& Baskin, J. M.
\href{https://doi.org/10.1021/acschembio.1c00584}{A {Chemoproteomics
Approach} to {Profile Phospholipase D-Derived Phosphatidyl Alcohol
Interactions}}. \emph{ACS Chemical Biology} \textbf{17}, 3276--3283
(2022).}

\bibitem[\citeproctext]{ref-mullerSynthesisCellularLabeling2021}
\CSLLeftMargin{16. }%
\CSLRightInline{Muller, R., Kojic, A., Citir, M. \& Schultz, C.
\href{https://doi.org/10.1002/anie.202103599}{Synthesis and {Cellular
Labeling} of {Multifunctional Phosphatidylinositol Bis}- and
{Trisphosphate Derivatives}}. \emph{Angewandte Chemie International
Edition} \textbf{60}, 19759--19765 (2021).}

\bibitem[\citeproctext]{ref-plotly}
\CSLLeftMargin{17. }%
\CSLRightInline{Inc., P. T. Collaborative data science. (2015).}

\bibitem[\citeproctext]{ref-ramnathvaidyanathanHtmlwidgetsHTMLWidgets2015}
\CSLLeftMargin{18. }%
\CSLRightInline{Ramnath Vaidyanathan \emph{et al.} Htmlwidgets: {HTML
Widgets} for {R}. (2015).}

\bibitem[\citeproctext]{ref-thompsonTandemMassTags2003}
\CSLLeftMargin{19. }%
\CSLRightInline{Thompson, A. \emph{et al.}
\href{https://doi.org/10.1021/ac0262560}{Tandem {Mass Tags}: {A Novel
Quantification Strategy} for {Comparative Analysis} of {Complex Protein
Mixtures} by {MS}/{MS}}. \emph{Analytical Chemistry} \textbf{75},
1895--1904 (2003).}

\bibitem[\citeproctext]{ref-birhanuMassSpectrometrybasedProteomics2023}
\CSLLeftMargin{20. }%
\CSLRightInline{Birhanu, A. G.
\href{https://doi.org/10.1186/s12014-023-09424-x}{Mass
spectrometry-based proteomics as an emerging tool in clinical
laboratories}. \emph{Clinical Proteomics} \textbf{20}, (2023).}

\bibitem[\citeproctext]{ref-boysClinicalApplicationsMass2023}
\CSLLeftMargin{21. }%
\CSLRightInline{Boys, E. L., Liu, J., Robinson, P. J. \& Reddel, R. R.
\href{https://doi.org/10.1002/pmic.202200238}{Clinical applications of
mass spectrometry-based proteomics in cancer: {Where} are we?}
\emph{PROTEOMICS} \textbf{23}, 2200238 (2023).}

\end{CSLReferences}

\end{document}

### 2025-07-31 BioinformaticsApplicationNote/GG_2025_applicationNote.qmd
Adding Frank's new data to PIP3 individual lipid probe page

@@
 
-Lipid–protein interactions play essential roles in cellular signaling and membrane dynamics, yet their systematic characterization has long been hindered by the inherent biochemical properties of lipids.
+Lipid-protein interactions play essential roles in cellular signaling and membrane dynamics, yet their systematic characterization has long been hindered by the inherent biochemical properties of lipids.
 Recent advances in functionalized lipid probes -- equipped with photoactivatable crosslinkers, affinity handles, and photocleavable protecting groups -- have enabled proteomics-based identification of lipid interacting proteins with unprecedented specificity and resolution.

### 2025-07-31 LipidProbe/PhosphatidylinositolTrisphosphate.qmd
example
Spent a long time learning about custom divs, applied a new one for cell types
Adding Frank's new data to PIP3 individual lipid probe page

@@
 subtitle: "PI(3,4,5)P~3~"
-prefer-html: true
+format: 
+  html:
+    embed-resources: false
 ---
@@
 
-## Protein interactome
+## Protein Interactome
+
+```{r setup, echo=FALSE, include=FALSE}
+## intitialize libraries
+library(here)
+
+## Opening the source file for the ggplot custom theme
+source(paste0(here(), "/Resources/ggplot_styles.R"))
+
+# Opening the datatable for this page
+RM_2021_data <- readr::read_csv(here("LipidProbe/DataSets/PIP3_HeLa_RM_2021_download.csv")) |>
+  mutate(
+    hit_annotation = case_when(
+      hit_annotation == "enriched hit" & logFC < 0 ~ "hit",
+      hit_annotation == "enriched candidate" & logFC < 0 ~ "candidate",
+      .default = hit_annotation
+    )
+  )
+
+# Organize the hit annotations as factors
+RM_2021_data$hit_annotation <- factor(pull(RM_2021_data, hit_annotation), levels = c("enriched hit", "hit", "enriched candidate", "candidate", "no hit",  "NA"), ordered=TRUE)
+
+RM_2021_data <- RM_2021_data |>
+  arrange(hit_annotation) |>
+  glimpse()
+```
+
+::: {.callout-note collapse="true"}
+
+{{< include /StudyInformation_includes/RM_2021_include.qmd >}}
+
+:::
+
+::: {.callout-tip}
+
+### Membrane Fraction
+
+```{r FilteringForMembraneProteins, include=FALSE, echo=FALSE}
+data <- RM_2021_data |>
+  filter(Fraction == "Membrane (+UV vs -UV)")
+
+```
+
+#### Data visualization
+
+::: {.panel-tabset}
+
+##### Volcano plots
+
+:::{.border}
+```{r, echo=FALSE, warning=FALSE}
+#| fig-cap: "Volcano plots depict the relative enrichment of each protein versus non-crosslinked control (x-axis) and the statistical significance of each protein following a Student's t-test (y-axis, -log10 transformed).
+The left panel depicts the results of a pulldown using trifunctionalized phosphatidic acid; the right panel depicts the results of the pulldown using trifunctionalized phosphatidylethanolamine.
+Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV)."
+
+VolcanoPlotStandardized(data)
+
+```
+:::
+
+##### Ranked-order plots
+
+:::{.border}
+```{r, echo=FALSE, warning=FALSE}
+#| fig-cap: "Ranked-order plots depict the relative enrichment of each protein versus non-crosslinked control (y-axis) from lowest to highest.
+The left panel depicts the results of a pulldown using trifunctionalized phosphatidic acid; the right panel depicts the results of the pulldown using trifunctionalized phosphatidylethanolamine.
+Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV)."
+
+RankedOrderPlotStandard(data)
+```
+:::
+
+##### MA Plots
+
+:::{.border}
+```{r, echo=FALSE, warning=FALSE}
+#| fig-cap: "MA plots depict the average abundance of each protein in the crosslinked and uncrosslinked conditions (x-axis) versus the log2-transformed fold-change between the crosslinked and uncrosslinked conditions (y-axis).
+Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV)."
+
+MAStandard(data)
+
+```
+
+:::
+:::
+:::
+
+::: {.callout-tip}
+
+### Cytosolic Fraction
+
+```{r FilteringForCytosolProteins, include=FALSE, echo=FALSE}
+data <- RM_2021_data |>
+  filter(Fraction == "Cytosol (+UV vs -UV)")
+
+```
+
+#### Data visualization
+
+::: {.panel-tabset}
+
+##### Volcano plots
+
+:::{.border}
+```{r, echo=FALSE, warning=FALSE}
+#| fig-cap: "Volcano plots depict the relative enrichment of each protein versus non-crosslinked control (x-axis) and the statistical significance of each protein following a Student's t-test (y-axis, -log10 transformed).
+The left panel depicts the results of a pulldown using trifunctionalized phosphatidic acid; the right panel depicts the results of the pulldown using trifunctionalized phosphatidylethanolamine.
+Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV)."
+
+VolcanoPlotStandardized(data)
+
+```
+:::
+
+##### Ranked-order plots
+
+:::{.border}
+```{r, echo=FALSE, warning=FALSE}
+#| fig-cap: "Ranked-order plots depict the relative enrichment of each protein versus non-crosslinked control (y-axis) from lowest to highest.
+The left panel depicts the results of a pulldown using trifunctionalized phosphatidic acid; the right panel depicts the results of the pulldown using trifunctionalized phosphatidylethanolamine.
+Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV)."
+
+RankedOrderPlotStandard(data)
+```
+:::
+
+##### MA Plots
+
+:::{.border}
+```{r, echo=FALSE, warning=FALSE}
+#| fig-cap: "MA plots depict the average abundance of each protein in the crosslinked and uncrosslinked conditions (x-axis) versus the log2-transformed fold-change between the crosslinked and uncrosslinked conditions (y-axis).
+Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV)."
+
+MAStandard(data)
+
+```
+
+:::
+:::
+:::
+
+## Data exploration
+
+Check the boxes below to filter the dataset by which lipid probe was used in the pulldown and by significance thresholds.
+
+:::{.border}
+```{r, echo=FALSE}
+
+RM_2021_data <- RM_2021_data |>
+  select(-hit_annotation_method) |>
+  mutate(
+    logFC = signif(logFC, digits = 4),
+    pvalue = signif(pvalue, digits = 4),
+    AveExpr = signif(AveExpr, digits = 4),
+    fdr = signif(fdr, digits = 4)
+  )
+
+# Here is the code to make the filterable lists shown in the crosstalk table below
+
+## Creates a reactive dataframe
+data_reactive <- crosstalk::SharedData$new(RM_2021_data)
+
+htmltools::tags$div(
+  class = "filter-container",
+  filter_checkbox(id = "LipidProbe",
+                  label = "Lipid probe in pulldown:", 
+                  sharedData = data_reactive,
+                  group = ~LipidProbe),
+  filter_checkbox(id = "hit_annotation",
+                  label = "Enrichment criteria:", 
+                  sharedData = data_reactive,
+                  group = ~hit_annotation),
+  filter_checkbox(id = "Fraction",
+                  label = "Cellular fraction",
+                  sharedData = data_reactive,
+                  group = ~Fraction)
+)
+
+## Displays the reactive dataframe
+datatable(data_reactive, options = list(pageLength = 10))
+
+```
+
+NB: Data analysis overview pending.
+:::
+
+## Data download
+
+{{< downloadthis DataSets/PIP3_HeLa_RM_2021_download.csv dname="PIP3_HeLa_RM_2021">}}

### 2025-08-04 HourlyTracking/202507_GG-Hours.qmd
Updated July invoice

--- 2025-06-16 HourlyTracking/202505_GG-Hours.qmd
@@
 ---
-title: "April 2025 Hours Report"
+title: "July 2025 Lipid Interactome Monthly Invoice"
 author: "Gaelen Guzman"
-date: "2025 05 02"
+date: "2025 08 04"
 output: 
@@
   - "\\fancyhead[L]{Gaelen Guzman}"
-  - "\\fancyhead[C]{Hours Report}"
-  - "\\fancyhead[R]{2025 06 02}"
+  - "\\fancyhead[C]{Lipid Interactome Monthly Invoice}"
+  - "\\fancyhead[R]{2025 08 04}"
   - "\\fancyfoot{}"
@@
 
-Please find below the hours I logged for the month of May 2025, with descriptions of each day's activity.
-In total, I performed 8 hours of work at an hourly rate of $50 (USD), for a total bill of $400.
+Please find below the hours I logged for the month of July 2025, with descriptions of each day's activity.
+In total, I performed 6 hours of work at an hourly rate of $50 (USD), for a total bill of $300.
 
@@
   select(Date, Hours, Activity) |>
-  filter(Date >= as.Date("2025-05-01") & Date < as.Date("2025-06-01")) %>%  # Filter for April 2025
+  filter(Date >= as.Date("2025-07-01") & Date < as.Date("2025-08-01")) %>%  # Filter for April 2025
   glimpse()

### 2025-08-06 ContactUs/about.tex
Updated legends on the RM_2021 page

--- 2025-07-30 _site/BioinformaticsApplicationNote/GG_2025_applicationNote.tex
@@
 \makeatother
-% definitions for citeproc citations
-\NewDocumentCommand\citeproctext{}{}
-\NewDocumentCommand\citeproc{mm}{%
-  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
-\makeatletter
- % allow citations to break across lines
- \let\@cite@ofmt\@firstofone
- % avoid brackets around text for \cite:
- \def\@biblabel#1{}
- \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
-\makeatother
-\newlength{\cslhangindent}
-\setlength{\cslhangindent}{1.5em}
-\newlength{\csllabelwidth}
-\setlength{\csllabelwidth}{3em}
-\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
- {\begin{list}{}{%
-  \setlength{\itemindent}{0pt}
-  \setlength{\leftmargin}{0pt}
-  \setlength{\parsep}{0pt}
-  % turn on hanging indent if param 1 is 1
-  \ifodd #1
-   \setlength{\leftmargin}{\cslhangindent}
-   \setlength{\itemindent}{-1\cslhangindent}
-  \fi
-  % set entry spacing
-  \setlength{\itemsep}{#2\baselineskip}}}
- {\end{list}}
-\usepackage{calc}
-\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
-\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
 
 \KOMAoption{captions}{tableheading}
+\makeatletter
+\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
+\@ifpackageloaded{fontawesome5}{}{\usepackage{fontawesome5}}
+\definecolor{quarto-callout-color}{HTML}{909090}
+\definecolor{quarto-callout-note-color}{HTML}{0758E5}
+\definecolor{quarto-callout-important-color}{HTML}{CC1914}
+\definecolor{quarto-callout-warning-color}{HTML}{EB9113}
+\definecolor{quarto-callout-tip-color}{HTML}{00A047}
+\definecolor{quarto-callout-caution-color}{HTML}{FC5300}
+\definecolor{quarto-callout-color-frame}{HTML}{acacac}
+\definecolor{quarto-callout-note-color-frame}{HTML}{4582ec}
+\definecolor{quarto-callout-important-color-frame}{HTML}{d9534f}
+\definecolor{quarto-callout-warning-color-frame}{HTML}{f0ad4e}
+\definecolor{quarto-callout-tip-color-frame}{HTML}{02b875}
+\definecolor{quarto-callout-caution-color-frame}{HTML}{fd7e14}
+\makeatother
 \makeatletter
@@
 \hypersetup{
-  pdftitle={The Lipid Interactome},
-  pdfkeywords={Lipid-protein
-interactions, Proteomics, Interactomics, Database, Multifunctionalized
-lipids},
+  pdftitle={About},
   colorlinks=true,
@@
 
-\title{The Lipid Interactome}
-\usepackage{etoolbox}
-\makeatletter
-\providecommand{\subtitle}[1]{% add subtitle to \maketitle
-  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
-}
-\makeatother
-\subtitle{An interactive and open access platform for exploring cellular
-lipid-protein interactomes}
-\author{Gaelen Guzman \and André Nadler \and Frank Stein \and Jeremy M.
-Baskin \and Carsten Schultz \and Fikadu Tafesse}
-\date{2025-02-04}
+\title{About}
+\author{}
+\date{}
 
@@
 
-\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}
+This repository is still under construction (as you can probably tell).
+Someday soon this page will have details about the founders of this
+resource, as well as a data submission form. Until then, please contact
+the site administrators for additional information about protocols,
+experimental design, and website feedback:
 
-\subsection{Authors}\label{authors}
+\href{mailto:contact.us@LipidInteractome.org}{\nolinkurl{contact.us@LipidInteractome.org}}
 
-Gaelen Guzman\textsuperscript{1,}*, André Nadler\textsuperscript{2},
-Frank Stein\textsuperscript{3}, Jeremy M. Baskin\textsuperscript{4},
-Carsten Schulz\textsuperscript{1}, Fikadu G. Tafesse\textsuperscript{1}
+\subsubsection{Github repository}\label{github-repository}
 
-\textsuperscript{1} = Departments of Molecular Immunology and Immunology
-and Chemical Physiology and Biochemistry, Oregon Health \& Science
-University, Portland, OR, USA; \textsuperscript{2} = Max Plank Institute
-of Molecular Cell Biology and Genetics, Dresden Germany;
-\textsuperscript{3} = Proteomics Core Facility, European Molecular
-Biology Laboratory, Heidelberg, Germany; \textsuperscript{4} =
-Department of Chemistry and Chemical Biology and Weill Institute for
-Cell and Molecular Biology, Cornell University, Ithaca, NY, USA; * =
-Corresponding author:
-\href{mailto:gaelen.guzman@lipidinteractome.org}{\nolinkurl{gaelen.guzman@lipidinteractome.org}}
+This site was written by Gaelen Guzman and was built using Quarto. Find
+out more about Quarto \href{https://quarto.org}{here}.
 
-\subsection{Summary}\label{summary}
+This site can be pulled from GitHub at:
+\url{https://github.com/gaelenDG/LipidInteractomics_Website}
 
-\subsubsection{Abstract}\label{abstract}
+\subsubsection{Site structure}\label{site-structure}
 
-Lipid--protein interactions play essential roles in cellular signaling
-and membrane dynamics, yet their systematic characterization has long
-been hindered by the inherent biochemical properties of lipids. Recent
-advances in functionalized lipid probes -- equipped with
-photoactivatable crosslinkers, affinity handles, and photocleavable
-protecting groups -- have enabled proteomics-based identification of
-lipid interacting proteins with unprecedented specificity and
-resolution. Despite the growing number of published lipid interactomes,
-there remains no centralized effort to harmonize, compare, or integrate
-these datasets.
+\begin{tcolorbox}[enhanced jigsaw, bottomtitle=1mm, coltitle=black, arc=.35mm, rightrule=.15mm, colback=white, breakable, colbacktitle=quarto-callout-note-color!10!white, colframe=quarto-callout-note-color-frame, bottomrule=.15mm, title=\textcolor{quarto-callout-note-color}{\faInfo}\hspace{0.5em}{Note}, toprule=.15mm, opacitybacktitle=0.6, toptitle=1mm, titlerule=0mm, left=2mm, leftrule=.75mm, opacityback=0]
 
-The Lipid Interactome addresses this gap by providing a structured,
-interactive web portal that adheres to FAIR data principles -- ensuring
-that lipid interactome studies are Findable, Accessible, Interoperable,
-and Reusable. Through standardized data formatting, interactive
-visualizations, and direct cross-study comparisons, this resource
-enables researchers to systematically explore the protein-binding
-partners of diverse bioactive lipids. By consolidating and curating
-lipid interactome proteomics data from multiple studies, the Lipid
-Interactome database serves as a critical tool for deciphering the
-biological functions of lipids in cellular systems.
+\_site\\
+├── 404.html\\
+├── Background\\
+│ ├── BackgroundFigures\\
+│ │ └── BaselineProteomics\_ExperimentalDesign.png │ ├──
+BaselineProteomics\_ExperimentalDesign.png\\
+│ ├── DataAnalysisAndStatistics.html\\
+│ ├── MultifunctionalLipidProbesOverview.html\\
+│ └── ProteomicsUsingMultifunctionalProbes.html\\
+├── ContactUs\\
+│ ├── DataSubmission.html\\
+│ └── about.html\\
+├── IndividualStudies\\
+│ ├── AT\_2025.html\\
+│ ├── DH\_2017.html\\
+│ ├── RM\_2021.html\\
+│ ├── SF\_2024.html\\
+│ ├── SF\_2024\_B.html\\
+│ └── StudyOverview.html\\
+├── LipidProbe\\
+│ ├── 1-10\_FattyAcid.html\\
+│ ├── 8-3\_FattyAcid.html\\
+│ ├── Diacylglycerol.html\\
+│ ├── EnrichedHitsComparison.html\\
+│ ├── FormattingTemplate.html\\
+│ ├── PhosphatidicAcid.html\\
+│ ├── Phosphatidylethanolamine.html\\
+│ ├── PhosphatidylinositolBisphosphate.html\\
+│ ├── PhosphatidylinositolTrisphosphate.html\\
+│ ├── Sphinganine.html\\
+│ ├── Sphingosine.html\\
+│ └── Structures\\
+│ ├── 1-10\_FattyAcid\_Structure.png\\
+│ ├── 8-3\_FattyAcid\_Structure.png\\
+│ ├── PIP3\_Structure.png\\
+│ ├── PhosphatidicAcid\_Structure.png\\
+│ ├── PhosphatidylethanolamineStructure.png\\
+│ ├── SphinganineStructure.png\\
+│ └── SphingosineStructure.png\\
+├── MaintenanceInstructions.html\\
+├── Resources\\
+│ └── styles.css\\
+├── index.html
 
-\subsubsection{Availability}\label{availability}
-
-This site can be viewed at
-\href{lipidinteractome.org}{LipidInteractome.org} all data is available
-for download. No user information is collected or necessary for data
-navigation, interaction, or download.
-
-\subsubsection{Data Submission \&
-Contact}\label{data-submission-contact}
-
-If you would like to submit a relevant dataset, see our
-\href{https://lipidinteractome.org/contactus/datasubmission}{Data
-Submission Page} for details, contact info, and instructions. For site
-feedback and additional questions, please email the site administrators
-at
-\href{mailto:Contact.Us@lipidinteractome.org}{\nolinkurl{Contact.Us@lipidinteractome.org}}
-
-\subsubsection{Keywords}\label{keywords}
-
-Lipid-protein interactions, proteomics, interactomics, database,
-multifunctionalized lipids, photoaffinity labeling
-
-\subsection{Introduction}\label{introduction}
-
-Historically, lipids have been considered merely the passive structural
-components of cellular membranes. However, recent decades have revealed
-that this diverse category of biomolecule plays essential and active
-roles in the cell, ranging from modulating membrane dynamics,
-determining organelle identity, serving as catabolites for energy
-storage and metabolism, and bioactive signaling mediators for organellar
-and intracellular signaling\textsuperscript{1--6}. Interactions with
-proteins are essential to many of these crucial lipid functions -- and
-yet, lipid--protein interactions are extremely challenging to study: The
-small size and biophysical properties of lipids make conventional
-proteomics approaches unsuitable for mapping lipid
-interactors\textsuperscript{7}. Unlike proteins, which can be readily
-tagged or immobilized for affinity-based interaction studies, lipids
-require specialized chemical modifications to enable selective and
-controlled interaction profiling\textsuperscript{8}.
-
-Recent advances in synthetic, multifunctionalized lipid analogs have
-revolutionized the field, enabling the systematic interrogation of lipid
-interactomes\textsuperscript{8}. These probes incorporate strategically
-designed functional groups that enable covalent crosslinking, affinity
-enrichment, and controlled activation. Most commonly, these include: (1)
-a diazirine group for photoactivatable crosslinking upon exposure to 355
-nm ultraviolet (UV) light, stabilizing non-covalent and often
-modest-affinity lipid--protein interactions; (2) a terminal alkyne,
-permitting click chemistry-based enrichment; and, in some cases, (3) a
-coumarin photocage, which shields the lipid probe from premature
-enzymatic modification until it is selectively cleaved by 405 nm light
-(a wavelength that does not induce diazirine
-photolysis)\textsuperscript{7--10}. Together, these modifications enable
-direct proteomic identification of lipid interactors, distinguishing
-true binding partners from transient or non-specific
-associations\textsuperscript{7,10,11}.
-
-Numerous studies have already employed these lipid probes to elucidate
-the interactomes of key bioactive lipids, including diacylglycerol,
-sphingosine, sphinganine, phosphatidic acid, and
-phosphatidylethanolamine, N-acylphosphatidylethanolamine, and
-phosphatidyl alcohol\textsuperscript{9,11--16}. These initial studies
-have followed a comparative proteomics workflow, wherein crosslinked
-(``+UV'') and non-crosslinked (``-UV'') samples are analyzed side by
-side to minimize artifacts and confirm
-specificity\textsuperscript{7,10}. However, despite the growing number
-of lipid interactome datasets, no centralized resource has existed to
-compile, compare, and standardize these findings.
-
-To address this gap, we present the
-\href{https://www.lipidinteractome.org}{Lipid Interactome} -- a curated
-repository designed to facilitate the comparative analysis of
-lipid--protein interactions from multiple studies. This resource
-consolidates proteomics data from multifunctional lipid probes, enabling
-researchers to efficiently explore and contextualize lipid-binding
-proteins across different lipid species and cellular models. Currently,
-the repository hosts interactomes derived from trifunctionalized
-phosphatidic acid, phosphatidylethanolamine, phosphatidylinositol
-\emph{tris}phosphate, N-acylphosphatidylethanolamine, phosphatidyl
-alcohol, sphingosine, and sphinganine in HeLa and Huh7
-cells\textsuperscript{11,13--16}. Additionally, it includes control
-datasets from two fatty acid probes to distinguish specific from
-non-specific lipid-binding proteins\textsuperscript{12}. We additionally
-intend to expand this resource to include more complex experimental
-designs as they are published (e.g.~Disease versus Healthy Control or
-Infection versus Mock).
-
-By providing a centralized platform for lipid interactome data, the
-Lipid Interactome significantly lowers the barriers to entry for
-researchers investigating lipid signaling pathways, enabling hypothesis
-generation through comparative analysis of multiple studies. Overall,
-this repository represents an important step toward systematizing
-lipid--protein interaction studies, ensuring that bioactive lipids are
-afforded the same level of proteomic scrutiny as their protein
-counterparts.
-
-\subsection{Description}\label{description}
-
-\subsubsection{Overview}\label{overview}
-
-The~Lipid Interactome~is an interactive discovery platform built
-using~Quarto, designed to centralize and enhance the study of
-lipid--protein interactions through curated datasets and dynamic
-visualization tools. Each page integrates~R-generated figures, embedding
-scripts directly into the source material to ensure reproducibility and
-transparency. The repository currently hosts data from~seven published
-studies, with an expandable framework that supports the incorporation of
-future datasets as the field progresses.
-
-At its core, the~Lipid Interactome~enables the~direct, qualitative
-comparison~of lipid interactomes between studies, providing researchers
-with invaluable insights into the diverse roles that bioactive lipids
-play in cellular processes. By leveraging standardized data formatting
-and interactive visualization -- including study-specific analysis
-pages, lipid probe aggregation, and cross-study comparisons via
-a~Shiny~application -- the platform facilitates intuitive exploration of
-protein--lipid interactions. As a~living repository, we actively
-encourage researchers to contribute their findings through
-our~\href{https://lipidinteractome.org/contactus/datasubmission}{Data~Submission}~page,
-ensuring that this resource continues to evolve alongside advancements
-in lipidomics research.
-
-\subsubsection{FAIR data principles}\label{fair-data-principles}
-
-The~Lipid Interactome~database was developed with the FAIR (Findable,
-Accessible, Interoperable, and Reusable) data principles in mind,
-ensuring that lipid--protein interaction data can be systematically
-explored, compared, and reused by the research community. Given the
-historical inconsistency in proteomics data curation, we have taken
-deliberate steps to standardize, annotate, and document our datasets for
-maximum utility.
-
-\paragraph{Findable}\label{findable}
-
-To address the fragmented nature of lipid interactome studies, we have
-established a centralized platform where researchers can interact with
-the results of individual studies or explore aggregated findings across
-multiple studies on a given lipid. The repository is structured to
-facilitate intuitive navigation between experimental datasets, offering
-clear entry points for study-specific and lipid-specific analyses.
-Because this resource is intended as a living repository, we actively
-invite researchers to contribute their findings following the submission
-guidelines detailed on
-our~\href{https://lipidinteractome.org/contactus/datasubmission}{Data
-Submission}~page.
-
-\paragraph{Accessible}\label{accessible}
-
-All datasets within~the Lipid Interactome~are available for download in
-standardized~\texttt{.csv}~format, ensuring broad accessibility across
-different computational environments. To further enhance usability, we
-provide
-a~\href{https://www.lipidinteractome.org/background/multifunctionallipidprobesoverview}{detailed~overview~of
-data~generation~and~analysis}, including explicit descriptions of
-dataset structure, column definitions, and the inherent limitations of
-multifunctional lipid probes. Only peer-reviewed proteomics datasets are
-included in this repository to maintain high data quality and
-reliability.
-
-\paragraph{Interoperable}\label{interoperable}
-
-Given the diversity of methodologies employed across lipid interactome
-studies, we have taken care to harmonize data formats and metadata
-annotations. While many studies share common analytical pipelines,
-others employ distinct mass spectrometry workflows. To ensure
-consistency, we have structured the data to allow parallel comparisons
-and
-provided~\href{https://www.lipidinteractome.org/background/proteomicsusingmultifunctionalprobes}{documentation~on~methodological~differences}.
-This standardization effort facilitates direct cross-study comparisons
-without requiring extensive reformatting by the end user. Each dataset
-is accompanied by metadata which describe the sample handling and data
-analysis techniques -- with clarifying text describing how
-``significance'' is determined for each analysis.
-
-\paragraph{Reusable}\label{reusable}
-
-To maximize the utility of these datasets, we provide extensive
-documentation detailing data acquisition, analysis workflows, and
-potential limitations. Wherever possible, technical jargon has been
-minimized to ensure accessibility to a broad audience, from lipid
-biologists to computational scientists. Additionally, we reference key
-publications that delve deeper into the synthesis of lipid probes and
-the specifics of each proteomics workflow, allowing researchers to
-further contextualize and validate their findings.
-
-By adhering to these FAIR principles,~the Lipid Interactome~database
-aims to serve as a robust and enduring resource for the lipid biology
-community, reducing redundancy, improving data transparency, and
-accelerating the study of lipid-mediated signaling.
-
-\subsubsection{Data Visualization and Download
-Modules}\label{data-visualization-and-download-modules}
-
-To facilitate efficient exploration and analysis of lipid--protein
-interaction data, the~Lipid Interactome~repository incorporates a suite
-of interactive visualization and data access tools. These modules are
-designed to enhance user engagement, provide clear interpretability of
-experimental findings, and streamline data retrieval for further
-computational analysis -- overall, the site is designed to ensure that
-the~Lipid Interactome~is not merely a static repository, but rather a
-dynamic and evolving resource for lipid biologists and bioinformaticians
-alike.
-
-\paragraph{Study-Specific Data
-Exploration}\label{study-specific-data-exploration}
-
-Each publication contributing to the repository is provided with a
-dedicated results page, allowing users to examine study findings in
-detail. These pages include interactive~Volcano,~Ranked-Order, and~MA
-plots, which enable visualization of differential protein enrichment
-across experimental conditions. The plots are rendered using
-the~Plotly~and~htmlwidgetsR packages, ensuring a responsive, client-side
-experience that supports zooming, hovering, image export, and data
-filtering\textsuperscript{17,18}. For transparency and reproducibility,
-all datasets associated with a given study are available for direct
-download.
-
-\paragraph{Lipid Probe-Specific Pages}\label{lipid-probe-specific-pages}
-
-In addition to the pages for each independent publication, datasets are
-further organized by lipid probe, providing a consolidated view of
-protein interactors detected across multiple experiments and independent
-studies. Each lipid-specific page includes study metadata and cell type
--- facilitating cross-study comparisons. Future iterations of the
-repository will extend this functionality by enabling direct comparisons
-of interactomes obtained from different cell lines treated with the same
-lipid probe, further refining the contextual understanding of
-lipid--protein interactions.
-
-\paragraph{Comparative Analysis via Shiny
-Application}\label{comparative-analysis-via-shiny-application}
-
-Where study design permits, data has been integrated into an
-interactive~Shiny~application, allowing users to perform direct (though
-qualitative)~probe-to-probe
-comparisons~(\href{https://www.lipidinteractome.org/lipidprobe/enrichedhitscomparison}{Probe~vs~Probe~Comparisons}).
-This tool enables researchers to explore the similarity of lipid
-interactomes across experimental conditions via~linear regression
-analysis, highlighting proteins that are significantly enriched in one
-dataset, both datasets, or neither. By providing an intuitive framework
-for interactome comparison, this feature aids in the identification of
-promising targets for further investigation.
-
-Because each publication utilizes distinct sample handling and data
-analysis techniques, we emphasize that these comparisons are qualitative
--- we hope to discourage quantitative statements regarding relative
-enrichment between lipid probes (e.g.~``Protein X is enriched 3x more to
-Lipid A than to Lipid B''). However, great utility lies in assessing
-co-enrichment (or orthogonal enrichment) of proteins to disparate lipid
-probes without quantitative comparison.
-
-\subsubsection{Data format}\label{data-format}
-
-While there are numerous ways to quantify the mass spectrometry (MS)
-data, the majority of studies included in our repository have utilized
-the same (or highly similar) quantitative MS pipeline using
-data-dependent acquisition techniques, such as Tandem Mass
-Tagging\textsuperscript{19}. These datasets include those reported by
-Farley et al.~(2024), Farley et al.~(2024), and Thomas et
-al.~(2025)\textsuperscript{11--13}. Some studies have also featured
-quantitative MS analysis using stable isotope labeling of amino acids in
-cell culture (SILAC), which also enables extraction of key data
-described below\textsuperscript{14,15}. Correspondingly, the ideal data
-structure for incorporation into our repository will include the
-following:
-
-\begin{longtable}[]{@{}
-  >{\raggedright\arraybackslash}p{(\linewidth - 10\tabcolsep) * \real{0.1486}}
-  >{\centering\arraybackslash}p{(\linewidth - 10\tabcolsep) * \real{0.1081}}
-  >{\centering\arraybackslash}p{(\linewidth - 10\tabcolsep) * \real{0.3514}}
-  >{\centering\arraybackslash}p{(\linewidth - 10\tabcolsep) * \real{0.1216}}
-  >{\centering\arraybackslash}p{(\linewidth - 10\tabcolsep) * \real{0.1622}}
-  >{\centering\arraybackslash}p{(\linewidth - 10\tabcolsep) * \real{0.1081}}@{}}
-\caption{\textbf{Example data table for smooth incorporation into Lipid
-Interactome.} \textbf{\emph{Column descriptions:}} \emph{Gene name}: The
-identifier for genes identified in the dataset (or Accession Number).
-\emph{Uniprot accession}: Stable identifiers of UniProtKB entries;
-integrates species and isoform data on the identified protein.
-\emph{Enrichment value}: Fold change of Experimental versus Control
-fold-change, typically log2-transformed -- ideally the product of TMT or
-other quantitative mass spectrometry methods. \emph{p value}: the
-results of an ANOVA or LIMMA analysis, corrected for multiple hypothesis
-testing. \emph{AveExpr}: An averaged value of the m/z ion intensity of
-the Experimental condition and Control condition used for the enrichment
-value (used to prepare MA plots for quality control). \emph{FDR}:
-False-discovery rate of protein
-identification.}\label{tbl-1}\tabularnewline
-\toprule\noalign{}
-\begin{minipage}[b]{\linewidth}\raggedright
-Gene name
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-\href{https://www.uniprot.org/help/accession_numbers}{Uniprot accession}
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-logFC
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-p value
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-AveExpr
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-FDR
-\end{minipage} \\
-\midrule\noalign{}
-\endfirsthead
-\toprule\noalign{}
-\begin{minipage}[b]{\linewidth}\raggedright
-Gene name
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-\href{https://www.uniprot.org/help/accession_numbers}{Uniprot accession}
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-logFC
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-p value
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-AveExpr
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-FDR
-\end{minipage} \\
-\midrule\noalign{}
-\endhead
-\bottomrule\noalign{}
-\endlastfoot
-GeneA & P80723 & 1.2 & 0.001 & 1.0x10\textsuperscript{18} & 0.0001 \\
-GeneB & P32004 & 0.1 & 0.6 & 1.0x10\textsuperscript{5} & 0.005 \\
-\ldots{} & \ldots{} & \ldots{} & \ldots{} & \ldots{} & \ldots{} \\
-\end{longtable}
-
-\textbf{We wish to emphasize that we will collaborate with data
-providers to prepare visualizations which best suit their datasets --
-the example dataset above merely depicts an ideal case which allows for
-easy incorporation and cross-study comparison.}
-
-Additionally, we are working on providing visualization functionality
-for studies which utilized Peptide Spectral Matching (PSM) to report
-enrichment toward lipid probes. Similarly, data-independent acquisitio
-(DIA) is a quickly emerging alternative to data-dependent acquisition
-(DDA; e.g.~TMT)\textsuperscript{20,21}; as with PSM datasets, we are
-working to incorporate DIA data formats.
-
-\subsection{Discussion}\label{discussion}
-
-The advent of functionalized lipid probes has fundamentally transformed
-lipid biology by enabling the proteomic identification of lipid-binding
-proteins with unprecedented specificity. However, as the number of
-published lipid interactome studies grows, the lack of a centralized
-framework for comparing and integrating these datasets presents a
-significant challenge for deciphering biological functions of individual
-lipids and lipid-binding proteins holistically and identifying trends
-across datasets. The Lipid Interactome was developed to address this
-need by providing researchers with a structured platform to explore,
-cross-reference, and build upon previous findings. By aggregating and
-standardizing lipid--protein interaction data, this resource facilitates
-the rapid identification of candidate lipid-binding proteins and
-supports orthogonal validation efforts.
-
-Designed as a continuously expanding repository, the Lipid Interactome
-will evolve alongside advances in lipid probe technologies and
-interactomics. Future iterations will incorporate validation studies for
-each lipid probe, offering researchers a dedicated space to compare
-findings across experimental contexts. This functionality will not only
-reduce redundancy in experimental design but also strengthen the
-reproducibility and biological interpretation of lipid interactome
-research. To support this vision, we invite researchers to contribute
-their datasets via our
-\href{https://lipidinteractome.org/contactus/datasubmission}{Data
-Submission page}, fostering a collaborative and transparent approach to
-lipid biology.
-
-\subsection{Abbreviations}\label{abbreviations}
-
-\begin{description}
-\tightlist
-\item[UV]
-\emph{U}ltra\emph{V}iolet
-\item[MS]
-\emph{M}ass \emph{S}pectrometry
-\item[LIMMA]
-\emph{Li}near \emph{M}odels for \emph{M}icro\emph{a}rray and RNA-Seq
-Data
-\item[ANOVA]
-\emph{An}alysis \emph{o}f \emph{Va}riance
-\item[PSM]
-\emph{P}eptide \emph{S}pectral \emph{M}atching
-\item[DIA]
-\emph{D}ata-\emph{I}ndedpendent \emph{A}cquisition
-\item[DDA]
-\emph{D}ata-\emph{D}edpendent \emph{A}cquisition
-\end{description}
-
-\subsection{Contributions}\label{contributions}
-
-GG designed, implemented, and wrote the majority of the LipidInteractome
-repository and manuscript. FS wrote the data analysis section of the
-repository, provided significant intellectual contribution to the
-repository design, and edited the manuscript. AN provided substantial
-editing of the repository and manuscript. JMB edited the manuscript and
-contributed data to the repository. CS and FT provided significant
-intellectual contribution and text editing of the repository and
-manuscript and oversaw the site development.
-
-\subsection{Funding}\label{funding}
-
-This work was supported by funding from the National Institutes of
-Health (NIAID R01 AI141549-02, to FGT, CS; NIGMS R01 GM127631 to C.S.,
-and NIGMS R01 GM151682 to JMB).
-
-\subsection{Conflicts of Interest}\label{conflicts-of-interest}
-
-The authors have no conflicts of interest to declare.
-
-\subsection{Citations}\label{citations}
-
-\phantomsection\label{refs}
-\begin{CSLReferences}{0}{0}
-\bibitem[\citeproctext]{ref-barischMembraneDamageRepair2023}
-\CSLLeftMargin{1. }%
-\CSLRightInline{Barisch, C., Holthuis, J. C. M. \& Cosentino, K.
-\href{https://doi.org/10.1515/hsz-2022-0321}{Membrane damage and repair:
-A thin line between life and death}. \emph{Biological Chemistry}
-\textbf{404}, 467--490 (2023).}
-
-\bibitem[\citeproctext]{ref-vanmeerMembraneLipidsWhere2008a}
-\CSLLeftMargin{2. }%
-\CSLRightInline{van Meer, G., Voelker, D. R. \& Feigenson, G. W.
-\href{https://doi.org/10.1038/nrm2330}{Membrane lipids: Where they are
-and how they behave}. \emph{Nature Reviews Molecular Cell Biology}
-\textbf{9}, 112--124 (2008).}
-
-\bibitem[\citeproctext]{ref-holthuisLipidLandscapesPipelines2014a}
-\CSLLeftMargin{3. }%
-\CSLRightInline{Holthuis, J. C. M. \& Menon, A. K.
-\href{https://doi.org/10.1038/nature13474}{Lipid landscapes and
-pipelines in membrane homeostasis}. \emph{Nature} \textbf{510}, 48--57
-(2014).}
-
-\bibitem[\citeproctext]{ref-niphakisGlobalMapLipidBinding2015a}
-\CSLLeftMargin{4. }%
-\CSLRightInline{Niphakis, M. J. \emph{et al.}
-\href{https://doi.org/10.1016/j.cell.2015.05.045}{A {Global Map} of
-{Lipid-Binding Proteins} and {Their Ligandability} in {Cells}}.
-\emph{Cell} \textbf{161}, 1668--1680 (2015).}
-
-\bibitem[\citeproctext]{ref-chernomordikProteinLipidInterplayFusion2003}
-\CSLLeftMargin{5. }%
-\CSLRightInline{Chernomordik, L. V. \& Kozlov, M. M.
-\href{https://doi.org/10.1146/annurev.biochem.72.121801.161504}{Protein-{Lipid
-Interplay} in {Fusion} and {Fission} of {Biological Membranes}}.
-\emph{Annual Review of Biochemistry} \textbf{72}, 175--207 (2003).}
-
-\bibitem[\citeproctext]{ref-simonsLipidRaftsSignal2000a}
-\CSLLeftMargin{6. }%
-\CSLRightInline{Simons, K. \& Toomre, D.
-\href{https://doi.org/10.1038/35036052}{Lipid rafts and signal
-transduction}. \emph{Nature Reviews Molecular Cell Biology} \textbf{1},
-31--39 (2000).}
-
-\bibitem[\citeproctext]{ref-schultzChemicalToolsLipid2023}
-\CSLLeftMargin{7. }%
-\CSLRightInline{Schultz, C.
-\href{https://doi.org/10.1021/acs.accounts.2c00851}{Chemical {Tools} for
-{Lipid Cell Biology}}. \emph{Accounts of Chemical Research} \textbf{56},
-1168--1177 (2023).}
-
-\bibitem[\citeproctext]{ref-schultzFlashClickMultifunctionalized2022a}
-\CSLLeftMargin{8. }%
-\CSLRightInline{Schultz, C., Farley, S. E. \& Tafesse, F. G.
-\href{https://doi.org/10.1021/jacs.2c02705}{{`{Flash} \& {Click}'}:
-{Multifunctionalized Lipid Derivatives} as {Tools To Study Viral
-Infections}}. \emph{Journal of the American Chemical Society}
-\textbf{144}, 13987--13995 (2022).}
-
-\bibitem[\citeproctext]{ref-hoglingerTrifunctionalLipidProbes2017}
-\CSLLeftMargin{9. }%
-\CSLRightInline{Höglinger, D. \emph{et al.}
-\href{https://doi.org/10.1073/pnas.1611096114}{Trifunctional lipid
-probes for comprehensive studies of single lipid species in living
-cells}. \emph{Proceedings of the National Academy of Sciences}
-\textbf{114}, 1566--1571 (2017).}
-
-\bibitem[\citeproctext]{ref-haberkantFatFabulousBifunctional2014}
-\CSLLeftMargin{10. }%
-\CSLRightInline{Haberkant, P. \& Holthuis, J. C. M.
-\href{https://doi.org/10.1016/j.bbalip.2014.01.003}{Fat \& fabulous:
-{Bifunctional} lipids in the spotlight}. \emph{Biochimica et Biophysica
-Acta - Molecular and Cell Biology of Lipids} \textbf{1841}, 1022--1030
-(2014).}
-
-\bibitem[\citeproctext]{ref-farleyTrifunctionalSphinganineNew2024a}
-\CSLLeftMargin{11. }%
-\CSLRightInline{Farley, S., Stein, F., Haberkant, P., Tafesse, F. G. \&
-Schultz, C.
-\href{https://doi.org/10.1021/acschembio.3c00554}{Trifunctional
-{Sphinganine}: {A New Tool} to {Dissect Sphingolipid Function}}.
-\emph{ACS Chemical Biology} \textbf{19}, 336--347 (2024).}
-
-\bibitem[\citeproctext]{ref-farleyTrifunctionalFattyAcid2024}
-\CSLLeftMargin{12. }%
-\CSLRightInline{Farley, S. E. \emph{et al.}
-\href{https://doi.org/10.1039/D4CC00974F}{Trifunctional fatty acid
-derivatives: The impact of diazirine placement}. \emph{Chemical
-Communications} \textbf{60}, 6651--6654 (2024).}
-
-\bibitem[\citeproctext]{ref-thomasTrifunctionalLipidDerivatives2025}
-\CSLLeftMargin{13. }%
-\CSLRightInline{Thomas, A. \emph{et al.} Trifunctional lipid
-derivatives: {PE}'s mitochondrial interactome. \emph{Chemical
-Communications} 10.1039.D4CC03599B (2025)
-doi:\href{https://doi.org/10.1039/D4CC03599B}{10.1039/D4CC03599B}.}
-
-\bibitem[\citeproctext]{ref-chiuPhotoaffinityLabelingReveals2025}
-\CSLLeftMargin{14. }%
-\CSLRightInline{Chiu, D.-C., Lin, H. \& Baskin, J. M. Photoaffinity
-{Labeling Reveals} a {Role} for the {Unusual Triply Acylated
-Phospholipid N-Acylphosphatidylethanolamine} in {Lactate Homeostasis}.
-(2025)
-doi:\href{https://doi.org/10.26434/chemrxiv-2025-j8nqz}{10.26434/chemrxiv-2025-j8nqz}.}
-
-\bibitem[\citeproctext]{ref-yuChemoproteomicsApproachProfile2022}
-\CSLLeftMargin{15. }%
-\CSLRightInline{Yu, W., Lin, Z., Woo, C. M. \& Baskin, J. M.
-\href{https://doi.org/10.1021/acschembio.1c00584}{A {Chemoproteomics
-Approach} to {Profile Phospholipase D-Derived Phosphatidyl Alcohol
-Interactions}}. \emph{ACS Chemical Biology} \textbf{17}, 3276--3283
-(2022).}
-
-\bibitem[\citeproctext]{ref-mullerSynthesisCellularLabeling2021}
-\CSLLeftMargin{16. }%
-\CSLRightInline{Muller, R., Kojic, A., Citir, M. \& Schultz, C.
-\href{https://doi.org/10.1002/anie.202103599}{Synthesis and {Cellular
-Labeling} of {Multifunctional Phosphatidylinositol Bis}- and
-{Trisphosphate Derivatives}}. \emph{Angewandte Chemie International
-Edition} \textbf{60}, 19759--19765 (2021).}
-
-\bibitem[\citeproctext]{ref-plotly}
-\CSLLeftMargin{17. }%
-\CSLRightInline{Inc., P. T. Collaborative data science. (2015).}
-
-\bibitem[\citeproctext]{ref-ramnathvaidyanathanHtmlwidgetsHTMLWidgets2015}
-\CSLLeftMargin{18. }%
-\CSLRightInline{Ramnath Vaidyanathan \emph{et al.} Htmlwidgets: {HTML
-Widgets} for {R}. (2015).}
-
-\bibitem[\citeproctext]{ref-thompsonTandemMassTags2003}
-\CSLLeftMargin{19. }%
-\CSLRightInline{Thompson, A. \emph{et al.}
-\href{https://doi.org/10.1021/ac0262560}{Tandem {Mass Tags}: {A Novel
-Quantification Strategy} for {Comparative Analysis} of {Complex Protein
-Mixtures} by {MS}/{MS}}. \emph{Analytical Chemistry} \textbf{75},
-1895--1904 (2003).}
-
-\bibitem[\citeproctext]{ref-birhanuMassSpectrometrybasedProteomics2023}
-\CSLLeftMargin{20. }%
-\CSLRightInline{Birhanu, A. G.
-\href{https://doi.org/10.1186/s12014-023-09424-x}{Mass
-spectrometry-based proteomics as an emerging tool in clinical
-laboratories}. \emph{Clinical Proteomics} \textbf{20}, (2023).}
-
-\bibitem[\citeproctext]{ref-boysClinicalApplicationsMass2023}
-\CSLLeftMargin{21. }%
-\CSLRightInline{Boys, E. L., Liu, J., Robinson, P. J. \& Reddel, R. R.
-\href{https://doi.org/10.1002/pmic.202200238}{Clinical applications of
-mass spectrometry-based proteomics in cancer: {Where} are we?}
-\emph{PROTEOMICS} \textbf{23}, 2200238 (2023).}
-
-\end{CSLReferences}
+\end{tcolorbox}
 

### 2025-08-06 HourlyTracking/202507_GG-Hours.qmd
Updated legends on the RM_2021 page

@@
 ---
-title: "July 2025 Lipid Interactome Monthly Invoice"
+titlJuly 2025 Lipid Interactome Monthly Invoice"
 author: "Gaelen Guzman"

### 2025-08-06 LipidProbe/PhosphatidylinositolTrisphosphate.qmd
Updated legends on the RM_2021 page

@@
 #| fig-cap: "Volcano plots depict the relative enrichment of each protein versus non-crosslinked control (x-axis) and the statistical significance of each protein following a Student's t-test (y-axis, -log10 transformed).
-The left panel depicts the results of a pulldown using trifunctionalized phosphatidic acid; the right panel depicts the results of the pulldown using trifunctionalized phosphatidylethanolamine.
+Original publication reported results in terms of peptide spectral matches; here, data have been reanalyzed to compare normalized intensities of experimental (+UV)and control (-UV) samples without isobaric mass tags.
 Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV)."
@@
 #| fig-cap: "Ranked-order plots depict the relative enrichment of each protein versus non-crosslinked control (y-axis) from lowest to highest.
-The left panel depicts the results of a pulldown using trifunctionalized phosphatidic acid; the right panel depicts the results of the pulldown using trifunctionalized phosphatidylethanolamine.
+Original publication reported results in terms of peptide spectral matches; here, data have been reanalyzed to compare normalized intensities of experimental (+UV)and control (-UV) samples without isobaric mass tags.
 Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV)."
@@
 #| fig-cap: "MA plots depict the average abundance of each protein in the crosslinked and uncrosslinked conditions (x-axis) versus the log2-transformed fold-change between the crosslinked and uncrosslinked conditions (y-axis).
+Original publication reported results in terms of peptide spectral matches; here, data have been reanalyzed to compare normalized intensities of experimental (+UV)and control (-UV) samples without isobaric mass tags.
 Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV)."

### 2025-08-06 StudyInformation_includes/RM_2021_include.qmd
adding a draft of the NAPE page
Updated legends on the RM_2021 page

@@
 
-[PI(3,4,5)P~3~](/LipidProbe/PhosphatidylinositolTrisphosphate.qmd)
+[Trifunctional PI(3,4,5)P~3~](/LipidProbe/PhosphatidylinositolTrisphosphate.qmd)
 
@@
 
-Peptide spectral counting
+Peptide spectral counting *(in original publication)*
+
+Label free quantification *(as reported here, enabled via fresh analysis by Frank Stein, EMBL)*
 
 #### Additional sample preparation <span class="help-symbol" title="e.g. sub-cellular fractionation, depletion, etc.">?</span>
+
+Samples were split into membrane and cytosolic fractions and analyzed as independent mass spec samples.
+Additional *No Probe* controls were included for raw input, though not used in displaying the data on this site.

### 2025-08-29 BioinformaticsApplicationNote/Bioinformatics_ReviewerResponseLetter.qmd
Addressing more of the reviewer comments, accession numbers mostly

---

format: 
  docx:
    reference-doc: custom-reference-doc.docx
  # pdf: 
  #   latex-engine: pdflatex
---

Dear Dr. Hutchins,

We thank you again for the opportunity to address the reviewers' comments on our first draft of our manuscript -- we have included with this letter an updated mansucript draft and have incorporated as many of their suggestions as we could feasibly achieve in the Lipid Interactome site.

We are grateful for thought that the reviewers put into their comments. We interpreted several throughlines in their comments: 1. Requests for additional metadata about study methodology and the incorporation of additional data (e.g. accession numbers in addition to gene names), 2. Requests for additional information about data submission, processing, and harmonization methods, 3. Requests for an automated/scalable data submission pipeline, and 4. The identification of typographical errors, malformed links, and bugs in the site.

Many of these points have been addressed directly either in the text or on the Lipid Interactome repository. For example, the broken links and typographical errors in figure captions have been addressed, additional cell line information has been added to our *Comparing the Enriched Hits of Different Probes* Shiny app, we have included of accession number to convey crucial information about isoform identifications in addition to using gene name to identify hits (where possible in the original datasets; the authors of Hoglinger 2017 have been unresponsive and we do not have the accession number data for their results) and clarification about the qualitative nature of the comparisons displayed in the Shiny app. We have additionally provided links to download the R scripts were used to "wrangle" the submitted data to the formats that our data visualization functions accept.

We highly concur with the reviewers' request for an automated data submission system. At present, this site has been built, managed, and maintained through the efforts of a single individual and we do not currently have the resources to overhaul the site to sufficiently incorporate these needs; we are seeking additional funding from the Open Oregon Educational Resources and the Code for Science and Society programs to support this individual in building these functionalities into our site. It is a long-term vision of our group to build a more scalable version of this repository which requires minimal manual management and enables automated data submission. However, we further feel that the underlying architecture of this repository is independent of its utility to the external lipid research community.

### 2025-08-29 404.qmd
removed naughty docx formatting
Minor updates
Added template files for the individual studies
Addressing more of the reviewer comments, accession numbers mostly

@@
 ---
+title: "404 -- Page Not Found   "
 ---
@@
 
-<h2 style> Ooops! </h2>
+<h1 style> Ooops! </h1>
 
@@
 
-<b> The page you're looking for doesn't (perhaps it was moved or renamed, or perhaps the site is still under construction and you can check back soon).</b>
+<b> The page you're looking for doesn't exist (perhaps it was moved or renamed, or perhaps the site is still under construction and you can check back soon).</b>
 

### 2025-08-29 BioinformaticsApplicationNote/GG_2025_applicationNote.qmd
Addressing more of the reviewer comments, accession numbers mostly

@@
 Some studies have also featured quantitative MS analysis using stable isotope labeling of amino acids in cell culture (SILAC), which also enables extraction of key data described below[@chiuPhotoaffinityLabelingReveals2025; @yuChemoproteomicsApproachProfile2022].
-Correspondingly, the ideal data structure for incorporation into our repository will include the following:
+Correspondingly, the ideal data structure for incorporation into our repository will contain the information shown in @tbl-dataStructure.
 
 :::{.border}
-
 | Gene name | [Uniprot accession](https://www.uniprot.org/help/accession_numbers) | logFC | p value |  AveExpr   |  FDR   |
@@
 *FDR*: False-discovery rate of protein identification.
-{#tbl-1 .striped}
-
+{#tbl-dataStructure .striped}
 :::
@@
 
-**We wish to emphasize that we will collaborate with data providers to prepare visualizations which best suit their datasets -- the example dataset above merely depicts an ideal case which allows for easy incorporation and cross-study comparison.**
+**We wish to emphasize that we will collaborate with data providers to prepare visualizations which best suit their datasets -- the example dataset above merely depicts an ideal case which allows for easy incorporation and cross-study comparison.
+As proteomics techniques have improved rapidly in recent years, we have done our best to incorporate all data structures into this repository**
 
@@
 TMT) [@birhanuMassSpectrometrybasedProteomics2023; @boysClinicalApplicationsMass2023]; as with PSM datasets, we are working to incorporate DIA data formats.
+
+At present, we are accepting datasets as analyzed by the original researchers, including protein identifications, enrichment quantification, and the results of statistical testing.
+We are working to incorporate comprehensive details of the analysis workflow in each study.
 
@@
 Designed as a continuously expanding repository, the Lipid Interactome will evolve alongside advances in lipid probe technologies and interactomics.
+Ongoing efforts seek to incorporate enhanced scalability of this site, more robust data storage methods, and automated data submission.
+These functionalities will improve the utility of this repository, enabling applications such as machine learning for pattern recognition as the site grows.
 Future iterations will incorporate validation studies for each lipid probe, offering researchers a dedicated space to compare findings across experimental contexts.
 This functionality will not only reduce redundancy in experimental design but also strengthen the reproducibility and biological interpretation of lipid interactome research.
-To support this vision, we invite researchers to contribute their datasets via our [Data Submission page](https://lipidinteractome.org/contactus/datasubmission), fostering a collaborative and transparent approach to lipid biology.
+
+To support this vision, we invite researchers to contribute their datasets via our [Data Submission page](https://lipidinteractome.org/contactus/datasubmission).
+Using the FAIR data principles, we hope to foster a collaborative and transparent approach to lipid biology.
 
@@
 
-GG designed, implemented, and wrote the majority of the LipidInteractome repository and manuscript.
+GG designed, implemented, and wrote the majority of the Lipid Interactome repository and manuscript.
 FS wrote the data analysis section of the repository, provided significant intellectual contribution to the repository design, and edited the manuscript.

### 2025-08-29 ContactUs/about.tex
Addressing more of the reviewer comments, accession numbers mostly

@@
 
-\begin{tcolorbox}[enhanced jigsaw, bottomtitle=1mm, coltitle=black, arc=.35mm, rightrule=.15mm, colback=white, breakable, colbacktitle=quarto-callout-note-color!10!white, colframe=quarto-callout-note-color-frame, bottomrule=.15mm, title=\textcolor{quarto-callout-note-color}{\faInfo}\hspace{0.5em}{Note}, toprule=.15mm, opacitybacktitle=0.6, toptitle=1mm, titlerule=0mm, left=2mm, leftrule=.75mm, opacityback=0]
+\begin{tcolorbox}[enhanced jigsaw, bottomrule=.15mm, opacitybacktitle=0.6, opacityback=0, coltitle=black, colframe=quarto-callout-note-color-frame, breakable, title=\textcolor{quarto-callout-note-color}{\faInfo}\hspace{0.5em}{Note}, colbacktitle=quarto-callout-note-color!10!white, colback=white, leftrule=.75mm, titlerule=0mm, bottomtitle=1mm, toptitle=1mm, arc=.35mm, rightrule=.15mm, left=2mm, toprule=.15mm]
 

### 2025-08-29 IndividualStudies/AT_2025.qmd
Addressing more of the reviewer comments, accession numbers mostly

@@
 ```{r setup, echo=FALSE, include=FALSE}
-
 ## intitialize libraries
 library(here)
-library(dplyr)
-library(duckplyr)
-library(ggplot2)
-library(ggrepel)
-library(emojifont)
-library(dplyr)
-library(tidyr)
-library(docstring)
-library(clusterProfiler)
-library(org.Hs.eg.db)
-library(enrichplot)
-library(igraph)
-library(ggtangle)
-library(stringr)
-library(crosstalk)
-library(plotly)
-library(grid)
-library(readr)
-library(rmarkdown)
-library(gt)
-library(DT)
-library(heatmaply)
-library(ggvenn)
-library(scales)
-library(htmltools)
+
+here()
 
 ## Opening the source file for the ggplot custom theme
-source(paste0(here(), "/Resources/ggplot_styles.R"))
+source(here("Resources/ggplot_styles.R"))
 
@@
 ```{r, echo=FALSE}
+# Slight cleanup for presenting in the datatable
+data <- data |>
+  mutate(logFC = signif(logFC, digits=3)) |>
+  mutate(pvalue = signif(pvalue, digits=3)) |>
+  arrange(-logFC) |>
+  arrange(hit_annotation) |>
+  select(-Protein.Description)
 
@@
 ## Displays the reactive dataframe
-datatable(data_reactive, options = list(pageLength = 10))
-
+datatable(data_reactive, 
+          options = list(pageLength = 10),
+          colnames = c("Rank", "Gene Name", "Accession #", "Lipid Probe", "Fraction", "LogFC", "AveExpr", "p value", "Hit Annotation"))
 ```
@@
 ```{r setup2, echo=FALSE, include=FALSE}
-
-## intitialize libraries
-library(here)
-library(dplyr)
-library(duckplyr)
-library(ggplot2)
-library(ggrepel)
-library(emojifont)
-library(dplyr)
-library(tidyr)
-library(docstring)
-library(clusterProfiler)
-library(org.Hs.eg.db)
-library(enrichplot)
-library(igraph)
-library(ggtangle)
-library(stringr)
-library(crosstalk)
-library(plotly)
-library(grid)
-library(readr)
-library(rmarkdown)
-library(gt)
-library(DT)
-library(heatmaply)
-library(ggvenn)
-library(scales)
-library(htmltools)
-
-## Opening the source file for the ggplot custom theme
-source(paste0(here(), "/Resources/ggplot_styles.R"))
 
@@
 ## Displays the reactive dataframe
-datatable(data_reactive, options = list(pageLength = 10))
+datatable(data_reactive, 
+          options = list(pageLength = 10),
+          colnames = c("Rank", "Gene Name", "Accession #", "Lipid Probe", "Fraction", "LogFC", "AveExpr", "p value", "Hit Annotation"))
 

### 2025-08-29 IndividualStudies/SF_2024.qmd
Addressing more of the reviewer comments, accession numbers mostly

@@
           options = list(pageLength = 15),
-                         colnames = c("Gene Name","Protein ID/Accession", "Lipid Probe", "Hit Annotation", "LogFC", "p value", "Average Expression", "FDR"))
+                         colnames = c("Gene Name","Accession #", "Lipid Probe", "Hit Annotation", "LogFC", "p value", "Average Expression", "FDR"))
 

### 2025-08-29 IndividualStudies/SF_2024_B.qmd
Addressing more of the reviewer comments, accession numbers mostly

@@
 datatable(data_reactive, 
-         options = list(pageLength = 10))
+          options = list(pageLength = 15),
+                         colnames = c("Gene Name","Accession #", "Lipid Probe", "Hit Annotation", "LogFC", "p value", "Average Expression", "FDR"))
 

### 2025-08-29 IndividualStudies/SK_2024.qmd
Addressing more of the reviewer comments, accession numbers mostly

@@
 datatable(data_reactive, 
-          caption = "'No hit' proteins are unenriched or depleted in the presence of probe, 'enriched candidates' are defined as proteins with a p-value < 0.05 and a fold-change > 2 (log2FC > 1) for the bf-GPI versus control probe, and 'enriched hits' are defined as proteins with a p-value < 0.05 and a fold change of at least 4-fold (log2FC >2) for the bf-GPI versus control probe",
           options = list(pageLength = 15),
-                         colnames = c("Gene Name", "Gene ID/Accession", "Lipid Probe", "Hit Annotation", "LogFC", "p value"))
+                         colnames = c("Gene Name", "Accession #", "Lipid Probe", "Hit Annotation", "LogFC", "p value"))
 
 ```
+'No hit' proteins are unenriched or depleted in the presence of probe, 'enriched candidates' are defined as proteins with a p-value < 0.05 and a fold-change > 2 (log2FC > 1) for the bf-GPI versus control probe, and 'enriched hits' are defined as proteins with a p-value < 0.05 and a fold change of at least 4-fold (log2FC >2) for the bf-GPI versus control probe
 :::

### 2025-08-29 IndividualStudies/WY_2021.qmd
Addressing more of the reviewer comments, accession numbers mostly

@@
 data <- data |>
-  dplyr::select(gene_name, LipidProbe, hit_annotation, logFC, pvalue) |>
+  dplyr::select(gene_name, Accession, LipidProbe, hit_annotation, logFC, pvalue) |>
   mutate(logFC = signif(logFC, digits=3)) |>
@@
           options = list(pageLength = 10),
-                         colnames = c("Gene Name", "Lipid Probe", "Hit Annotation", "LogFC", "p value"),
+                         colnames = c("Gene Name", "Accession #", "Lipid Probe", "Hit Annotation", "LogFC", "p value"),
                          rownames=FALSE)

### 2025-08-29 LipidProbe/Glycosylphosphatidylinositol.qmd
Addressing more of the reviewer comments, accession numbers mostly

@@
 source(paste0(here(), "/Resources/ggplot_styles.R"))
-
 ```
@@
 data <- data |>
-  dplyr::select(gene_name, hit_annotation, logFC, pvalue) |>
+  dplyr::select(gene_name, Accession, hit_annotation, logFC, pvalue) |>
   mutate(logFC = signif(logFC, digits=3),
@@
           options = list(pageLength = 10),
-                         colnames = c("Rank", "Gene Name", "Hit Annotation", "LogFC", "p value"))
+          colnames = c("Rank", "Gene Name", "Accession #", "Hit Annotation", "LogFC", "p value"))
 

### 2025-08-29 LipidProbe/N-Acylphosphatidylethanolamine.qmd
Spent a long time learning about custom divs, applied a new one for cell types
Addressing more of the reviewer comments, accession numbers mostly

@@
 data <- data |>
-  dplyr::select(gene_name, LipidProbe, hit_annotation, logFC, pvalue, numReplicates) |>
+  dplyr::select(gene_name, gene_ID, hit_annotation, logFC, pvalue, numReplicates) |>
   mutate(logFC = signif(logFC, digits=3),
@@
   class = "filter-container",
-  filter_checkbox(id = "LipidProbe",
-                  label = "Lipid probe in pulldown:", 
-                  sharedData = data_reactive,
-                  group = ~LipidProbe),
   filter_checkbox(id = "hit_annotation",
@@
 datatable(data_reactive, 
-          caption = "This datatable contains all the data plotted above.
+          options = list(pageLength = 15),
+                         colnames = c("Gene Name", "Accession #", "Hit Annotation", "LogFC", "p value", "Num Replicate IDs"),
+                         rownames=FALSE)
+
+```
+
+This datatable contains all the data plotted above.
 Check the boxes below to filter the dataset by which lipid probe was used in the pulldown and by significance thresholds.
@@
 As above, \"enriched hit\" denotes proteins identified in all three replicates & fold-change > 1.5 (logFC 0.585) & pvalue < 0.01.
-\"enriched candidates\" are proteins identified in two replicates & fold-change > 1.5 (logFC 0.585) & pvalue < 0.01.",
-          options = list(pageLength = 15),
-                         colnames = c("Gene Name", "Lipid Probe", "Hit Annotation", "LogFC", "p value", "Num Replicate IDs"),
-                         rownames=FALSE)
-
-```
+\"enriched candidates\" are proteins identified in two replicates & fold-change > 1.5 (logFC 0.585) & pvalue < 0.01.
 

### 2025-08-29 LipidProbe/PhosphatidicAcid.qmd
Spent a long time learning about custom divs, applied a new one for cell types
Addressing more of the reviewer comments, accession numbers mostly

@@
 
+:::{.cells collapse="true"}
+::::{.cells-header}
+Membrane Fraction
+::::
+::::{.cells-container}
+
 #### Data visualization
@@
 ```{r setup, echo=FALSE, include=FALSE}
-
 ## intitialize libraries
@@
 
+here()
+
 ## Opening the source file for the ggplot custom theme
-source(paste0(here(), "/Resources/ggplot_styles.R"))
+source(here("Resources/ggplot_styles.R"))
 
-```
-
-```{r, echo=FALSE, include=FALSE}
-
-# Data wrangling to prepare Alix's data to the standardized inputs for my plotting functions.
-# Read the data to a df
-
-# AT_2025 <- readr::read_csv("LipidProbe/DataSets/AT_ChemicalCommunications_2025_download.csv") |>
-# 	filter(LipidProbe == "PA")
-
-# write.csv(AT_2025, "LipidProbe/DataSets/PA_HeLa_AT_2025.csv")
-
-data <- readr::read_csv(paste0(here::here(), "/LipidProbe/DataSets/PA_HeLa_AT_2025.csv"))
+# Read the membrane data to a df
+data <- readr::read_csv(here("LipidProbe/DataSets/PA_membrane_HeLa_AT_2025.csv"))
 
 # Organize the hit annotations as factors
-data$hit_annotation <- factor(pull(data, hit_annotation), levels = c("enriched hit", "enriched candidate", "no hit", "NA"), ordered=TRUE)
+data$hit_annotation <- factor(pull(data, hit_annotation), levels = c("enriched hit", "hit", "enriched candidate", "candidate", "no hit",  "NA"), ordered=TRUE)
 
@@
 Volcano plots depict the relative enrichment of each protein versus non-crosslinked control (x-axis) and the statistical significance of each protein following a Student's t-test (y-axis, -log10 transformed).
-The left panel depicts the results of a pulldown using trifunctionalized phosphatidic acid; the right panel depicts the results of the pulldown using trifunctionalized phosphatidylethanolamine.
 Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV."
@@
 Ranked-order plots depict the relative enrichment of each protein versus non-crosslinked control (y-axis) from lowest to highest.
-The left panel depicts the results of a pulldown using trifunctionalized phosphatidic acid; the right panel depicts the results of the pulldown using trifunctionalized phosphatidylethanolamine.
 Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV."
@@
 :::
+::::
 :::
 
+<!-- 
 #### Gene Ontology Analysis
@@
 ::::
-:::::
+::::: -->
 
@@
 # Here is the code to make the filterable lists shown in the crosstalk table below
+# Slight cleanup for presenting in the datatable
+data <- data |>
+  mutate(logFC = signif(logFC, digits=3)) |>
+  mutate(pvalue = signif(pvalue, digits=3)) |>
+  arrange(-logFC) |>
+  arrange(hit_annotation) |>
+  select(-Protein.Description)
 
-data <- data |>
-  dplyr::select(gene_name, hit_annotation, logFC, pvalue) |>
-  mutate(logFC = signif(logFC, digits=3),
-          pvalue = signif(pvalue, digits=3)) |>
-  arrange(hit_annotation, -logFC)
+# Here is the code to make the filterable lists shown in the crosstalk table below
 
@@
   class = "filter-container",
+  filter_checkbox(id = "LipidProbe",
+                  label = "Lipid probe in pulldown:", 
+                  sharedData = data_reactive,
+                  group = ~LipidProbe),
   filter_checkbox(id = "hit_annotation",
@@
                   sharedData = data_reactive,
-                  group = ~hit_annotation,
-                  inline="true")
+                  group = ~hit_annotation)
 )
@@
           options = list(pageLength = 10),
-                         colnames = c("Rank", "Gene Name", "Hit Annotation", "LogFC", "p value"))
+          colnames = c("Rank", "Gene Name", "Accession #", "Lipid Probe", "Fraction", "LogFC", "AveExpr", "p value", "Hit Annotation"))
 
@@
 
-{{< downloadthis DataSets/PA_HeLa_AT_2025.csv dname="PA_HeLa_AT_ChemComm_download">}}
+{{< downloadthis DataSets/PA_membrane_HeLa_AT_2025.csv dname="PA_membrane_HeLa_AT_ChemComm_download">}}
 
 ::::
+
+:::{.cells collapse="true"}
+::::{.cells-header}
+Cytosolic Fraction
+::::
+::::{.cells-container}
+
+#### Data visualization
+
+```{r setup2, echo=FALSE, include=FALSE}
+
+# Read the membrane data to a df
+data <- readr::read_csv(here("LipidProbe/DataSets/PA_cytosol_HeLa_AT_2025.csv"))
+
+# Organize the hit annotations as factors
+data$hit_annotation <- factor(pull(data, hit_annotation), levels = c("enriched hit", "hit", "enriched candidate", "candidate", "no hit",  "NA"), ordered=TRUE)
+
+```
+
+::: {.panel-tabset}
+
+##### Volcano plots
+
+:::{.border}
+```{r, echo=FALSE, warning=FALSE}
+#| fig-cap: "Data as reported in [Thomas et al., 2025](/IndividualStudies/AT_2025.qmd).
+Volcano plots depict the relative enrichment of each protein versus non-crosslinked control (x-axis) and the statistical significance of each protein following a Student's t-test (y-axis, -log10 transformed).
+Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV."
+
+VolcanoPlotStandardized(data)
+
+```
+:::
+
+##### Ranked-order plots
+
+:::{.border}
+```{r, echo=FALSE, warning=FALSE}
+#| fig-cap: "Data as reported in [Thomas et al., 2025](/IndividualStudies/AT_2025.qmd).
+Ranked-order plots depict the relative enrichment of each protein versus non-crosslinked control (y-axis) from lowest to highest.
+Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV."
+
+RankedOrderPlotStandard(data)
+```
+:::
+
+##### MA Plot
+
+:::{.border}
+```{r, echo=FALSE, warning=FALSE}
+#| fig-cap: "Data as reported in [Thomas et al., 2025](/IndividualStudies/AT_2025.qmd).
+MA plots depict the average abundance of each protein in the crosslinked and uncrosslinked conditions (x-axis) versus the log2-transformed fold-change between the crosslinked and uncrosslinked conditions (y-axis).
+Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV."
+
+MAStandard(data)
+
+```
+
+:::
+::::
+:::
+
+#### Data exploration and download
+
+Check the boxes below to filter the dataset by which lipid probe was used in the pulldown and by significance thresholds.
+
+:::{.border}
+```{r, echo=FALSE}
+
+# Here is the code to make the filterable lists shown in the crosstalk table below
+# Slight cleanup for presenting in the datatable
+data <- data |>
+  mutate(logFC = signif(logFC, digits=3)) |>
+  mutate(pvalue = signif(pvalue, digits=3)) |>
+  arrange(-logFC) |>
+  arrange(hit_annotation) |>
+  select(-Protein.Description)
+
+# Here is the code to make the filterable lists shown in the crosstalk table below
+
+## Creates a reactive dataframe
+data_reactive <- crosstalk::SharedData$new(data)
+
+htmltools::tags$div(
+  class = "filter-container",
+  filter_checkbox(id = "LipidProbe",
+                  label = "Lipid probe in pulldown:", 
+                  sharedData = data_reactive,
+                  group = ~LipidProbe),
+  filter_checkbox(id = "hit_annotation",
+                  label = "Enrichment criteria:", 
+                  sharedData = data_reactive,
+                  group = ~hit_annotation)
+)
+
+## Displays the reactive dataframe
+datatable(data_reactive, 
+          caption = "'No hit' proteins are unenriched or depleted in the presence of probe, 'enriched candidates' are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and 'enriched hits' are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV",
+          options = list(pageLength = 10),
+          colnames = c("Rank", "Gene Name", "Accession #", "Lipid Probe", "Fraction", "LogFC", "AveExpr", "p value", "Hit Annotation"))
+
+```
+:::
+
+<br>
+
+{{< downloadthis DataSets/PA_cytosol_HeLa_AT_2025.csv dname="PA_cytosol_HeLa_AT_ChemComm_download">}}
+
+::::
+:::

### 2025-08-29 LipidProbe/Phosphatidylethanolamine.qmd
Spent a long time learning about custom divs, applied a new one for cell types
Addressing more of the reviewer comments, accession numbers mostly

@@
 
+here()
+
 ## Opening the source file for the ggplot custom theme
-source(paste0(here(), "/Resources/ggplot_styles.R"))
+source(here("Resources/ggplot_styles.R"))
 
-```
-
-```{r, echo=FALSE, include=FALSE}
-
-# Data wrangling to prepare Alix's data to the standardized inputs for my plotting functions.
-
-# Read the data to a df
-data <- readr::read_csv(paste0(here(), "/LipidProbe/DataSets/PE_HeLa_AT_2025.csv"))
+# Read the membrane data to a df
+data <- readr::read_csv(here("LipidProbe/DataSets/PE_membrane_HeLa_AT_2025.csv"))
 
 # Organize the hit annotations as factors
-data$hit_annotation <- factor(pull(data, hit_annotation), levels = c("enriched hit", "enriched candidate", "no hit", "NA"), ordered=TRUE)
-
-# Building an ID column to maintain the order on the x-axis
-ID <- c()
-for(i in 0:(nrow(data))){
-	ID[i] = i
-}
-
-# Applies the ID column to the PE results
-AT_2025_ranked <- data |>
-    arrange(logFC) |>
-	filter(LipidProbe == "PE") |>
-	mutate(ID = ID)
+data$hit_annotation <- factor(pull(data, hit_annotation), levels = c("enriched hit", "hit", "enriched candidate", "candidate", "no hit",  "NA"), ordered=TRUE)
 
@@
 Volcano plots depict the relative enrichment of each protein versus non-crosslinked control (x-axis) and the statistical significance of each protein following a Student's t-test (y-axis, -log10 transformed).
-The left panel depicts the results of a pulldown using trifunctionalized phosphatidic acid; the right panel depicts the results of the pulldown using trifunctionalized phosphatidylethanolamine.
-Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV)."
+Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV."
 
@@
 Ranked-order plots depict the relative enrichment of each protein versus non-crosslinked control (y-axis) from lowest to highest.
-The left panel depicts the results of a pulldown using trifunctionalized phosphatidic acid; the right panel depicts the results of the pulldown using trifunctionalized phosphatidylethanolamine.
-Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV)."
+Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV."
 
-RankedOrderPlotStandard(AT_2025_ranked)
+RankedOrderPlotStandard(data)
 ```
@@
 MA plots depict the average abundance of each protein in the crosslinked and uncrosslinked conditions (x-axis) versus the log2-transformed fold-change between the crosslinked and uncrosslinked conditions (y-axis).
-Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV)."
+Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV."
 
-print("Data not yet provided.")
+MAStandard(data)
 
 ```
+
 :::
+::::
 :::
 
+<!-- 
 #### Gene Ontology Analysis
@@
 The Cell Compartment analysis assesses whether the list of enriched proteins contains a statistically significant number of proteins in the same cellular region; appropriately, the Molecular Function and Biological Process analyses does the same for molecular function and biological process, respectively.
-[Click here for more information about Gene Ontology analysis.](/Background/DataAnalysisAndStatistics.qmd#gene-ontology-overview)
+[Click here for more information about Gene Ontology Analysis.](/Background/DataAnalysisAndStatistics.qmd#gene-ontology-overview)
 ::::
-:::::
+::::: -->
 
@@
           options = list(pageLength = 10),
-                         colnames = c("Rank", "Gene Name", "Hit Annotation", "LogFC", "p value"))
+          colnames = c("Rank", "Gene Name", "Accession #", "Lipid Probe", "Fraction", "LogFC", "AveExpr", "p value", "Hit Annotation"))
+
 ```
@@
 
-{{< downloadthis DataSets/PE_HeLa_AT_2025.csv dname="PE_HeLa_AT_ChemComm_download">}}
+<br>
+
+{{< downloadthis DataSets/PE_membrane_HeLa_AT_2025.csv dname="PE_membrane_HeLa_AT_ChemComm_download">}}
 
 ::::
+
+:::{.cells collapse="true"}
+::::{.cells-header}
+Cytosolic Fraction
+::::
+::::{.cells-container}
+
+#### Data visualization
+
+```{r setup2, echo=FALSE, include=FALSE}
+
+# Read the membrane data to a df
+data <- readr::read_csv(here("LipidProbe/DataSets/PE_cytosol_HeLa_AT_2025.csv"))
+
+# Organize the hit annotations as factors
+data$hit_annotation <- factor(pull(data, hit_annotation), levels = c("enriched hit", "hit", "enriched candidate", "candidate", "no hit",  "NA"), ordered=TRUE)
+
+```
+
+::: {.panel-tabset}
+
+##### Volcano plots
+
+:::{.border}
+```{r, echo=FALSE, warning=FALSE}
+#| fig-cap: "Data as reported in [Thomas et al., 2025](/IndividualStudies/AT_2025.qmd).
+Volcano plots depict the relative enrichment of each protein versus non-crosslinked control (x-axis) and the statistical significance of each protein following a Student's t-test (y-axis, -log10 transformed).
+Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV."
+
+VolcanoPlotStandardized(data)
+
+```
+:::
+
+##### Ranked-order plots
+
+:::{.border}
+```{r, echo=FALSE, warning=FALSE}
+#| fig-cap: "Data as reported in [Thomas et al., 2025](/IndividualStudies/AT_2025.qmd).
+Ranked-order plots depict the relative enrichment of each protein versus non-crosslinked control (y-axis) from lowest to highest.
+Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV."
+
+RankedOrderPlotStandard(data)
+```
+:::
+
+##### MA Plot
+
+:::{.border}
+```{r, echo=FALSE, warning=FALSE}
+#| fig-cap: "Data as reported in [Thomas et al., 2025](/IndividualStudies/AT_2025.qmd).
+MA plots depict the average abundance of each protein in the crosslinked and uncrosslinked conditions (x-axis) versus the log2-transformed fold-change between the crosslinked and uncrosslinked conditions (y-axis).
+Black proteins are unenriched or depleted in the presence of probe, Purple enriched candidates are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and Orange enriched hits are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV."
+
+MAStandard(data)
+
+```
+
+:::
+::::
+:::
+
+#### Data exploration and download
+
+Check the boxes below to filter the dataset by which lipid probe was used in the pulldown and by significance thresholds.
+
+:::{.border}
+```{r, echo=FALSE}
+
+# Here is the code to make the filterable lists shown in the crosstalk table below
+# Slight cleanup for presenting in the datatable
+data <- data |>
+  mutate(logFC = signif(logFC, digits=3)) |>
+  mutate(pvalue = signif(pvalue, digits=3)) |>
+  arrange(-logFC) |>
+  arrange(hit_annotation) |>
+  select(-Protein.Description)
+
+# Here is the code to make the filterable lists shown in the crosstalk table below
+
+## Creates a reactive dataframe
+data_reactive <- crosstalk::SharedData$new(data)
+
+htmltools::tags$div(
+  class = "filter-container",
+  filter_checkbox(id = "LipidProbe",
+                  label = "Lipid probe in pulldown:", 
+                  sharedData = data_reactive,
+                  group = ~LipidProbe),
+  filter_checkbox(id = "hit_annotation",
+                  label = "Enrichment criteria:", 
+                  sharedData = data_reactive,
+                  group = ~hit_annotation)
+)
+
+## Displays the reactive dataframe
+datatable(data_reactive, 
+          caption = "'No hit' proteins are unenriched or depleted in the presence of probe, 'enriched candidates' are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and 'enriched hits' are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV",
+          options = list(pageLength = 10),
+          colnames = c("Rank", "Gene Name", "Accession #", "Lipid Probe", "Fraction", "LogFC", "AveExpr", "p value", "Hit Annotation"))
+
+```
+:::
+
+<br>
+
+{{< downloadthis DataSets/PE_cytosol_HeLa_AT_2025.csv dname="PE_cytosol_HeLa_AT_ChemComm_download">}}
+
+::::
+:::

### 2025-08-29 LipidProbe/PhosphatidylinositolTrisphosphate.qmd
Addressing more of the reviewer comments, accession numbers mostly

@@
 library(here)
-
+here()
 ## Opening the source file for the ggplot custom theme
-source(paste0(here(), "/Resources/ggplot_styles.R"))
+source((here("Resources/ggplot_styles.R")))
 
@@
 RM_2021_data <- RM_2021_data |>
-  select(-hit_annotation_method) |>
+  select(-hit_annotation_method, -Protein.Description) |>
   mutate(
@@
 ## Displays the reactive dataframe
-datatable(data_reactive, options = list(pageLength = 10))
+datatable(data_reactive, 
+          options = list(pageLength = 10),
+          colnames = c("Rank", "Gene Name", "Accession #","Lipid Probe", "Fraction", "LogFC", "p value", "FDR", "Hit Annotation"))
 

### 2025-08-29 LipidProbe/Sphinganine.qmd
Addressing more of the reviewer comments, accession numbers mostly

@@
 ## Opening the source file for the ggplot custom theme
-source(paste0(here(), "/Resources/ggplot_styles.R"))
+source(here("Resources/ggplot_styles.R"))
 
@@
 # Opening the datatable for this page
-data <- readr::read_csv(paste0(here(), "/LipidProbe/DataSets/Spa_Huh7_SF_2024.csv")) |>
+data <- readr::read_csv(here("LipidProbe/DataSets/Spa_Huh7_SF_2024.csv"), ) |>
 	filter(LipidProbe == "Spa")
@@
 data <- data |>
-  dplyr::select(gene_name, hit_annotation, logFC, pvalue, fdr) |>
+  dplyr::select(gene_name, protein_id, hit_annotation, logFC, pvalue, fdr) |>
   mutate(logFC = signif(logFC, digits=3),
@@
 datatable(data_reactive, 
-          caption = "'No hit' proteins are unenriched or depleted in the presence of probe, 'enriched candidates' are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and 'enriched hits' are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV",
           options = list(pageLength = 10),
-                         colnames = c("Rank", "Gene Name", "Hit Annotation", "LogFC", "p value", "FDR"))
+                         colnames = c("Rank", "Gene Name","Accession #", "Hit Annotation", "LogFC", "p value", "FDR"))
 
 ```
+
+'No hit' proteins are unenriched or depleted in the presence of probe, 'enriched candidates' are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and 'enriched hits' are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV.
 :::

### 2025-08-29 LipidProbe/Sphingosine.qmd
Addressing more of the reviewer comments, accession numbers mostly

@@
 datatable(data_reactive, 
-          caption = "'No hit' proteins are unenriched or depleted in the presence of probe, 'enriched candidates' are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and 'enriched hits' are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV",
           options = list(pageLength = 10),
-                         colnames = c("Rank", "Gene Name", "Hit Annotation", "LogFC", "p value", "FDR"))
+                         colnames = c("Rank", "Gene Name", "Accession #", "Hit Annotation", "LogFC", "p value", "FDR"))
 
 ```
-
+'No hit' proteins are unenriched or depleted in the presence of probe, 'enriched candidates' are defined as proteins with a false discovery rate less than 0.2 and a fold change of at least 1.5-fold, and 'enriched hits' are defined as proteins with a false discovery rate less than 0.05 and a fold change of at least 2-fold in the +UV over the -UV.
 :::

### 2025-08-29 StudyInformation_includes/AT_2025_include.qmd
working on uploading Franks new analysis of Alixs data. Working in new branch.
Addressing more of the reviewer comments, accession numbers mostly

@@
 #### Additional sample preparation <span class="help-symbol" title="e.g. sub-cellular fractionation, depletion, etc.">?</span>
+
+Cell lysates were separated into membrane and cytosolic fractions. This publication reports the results of just the membrane fraction.
+
+#### Data wrangling
+Use the download button below to download the R script used to wrangle the authors' original submission into the data visualization tools on the Lipid Interactome:
+
+{{< downloadthis /Users/gaelenguzman/LipidInteractomics_Website_local/LipidInteractomics_Website/IndividualStudies/DataTables/DataWrangling/AT_ChemComm2025_wrangling.R dname="AT_ChemComm2025_wrangling">}}

### 2025-08-29 StudyInformation_includes/DCC_2025_include.qmd
Addressing more of the reviewer comments, accession numbers mostly

@@
 #### Additional sample preparation <span class="help-symbol" title="e.g. sub-cellular fractionation, depletion, etc.">?</span>
+
+#### Data wrangling
+Use the download button below to download the R script used to wrangle the authors' original submission into the data visualization tools on the Lipid Interactome:
+
+{{< downloadthis /Users/gaelenguzman/LipidInteractomics_Website_local/LipidInteractomics_Website/IndividualStudies/DataTables/DataWrangling/DCC_2025_wrangling.R dname="DCC_2025_wrangling">}}

### 2025-08-29 StudyInformation_includes/RM_2021_include.qmd
Addressing more of the reviewer comments, accession numbers mostly

@@
 Additional *No Probe* controls were included for raw input, though not used in displaying the data on this site.
+
+#### Data wrangling
+Use the download button below to download the R script used to wrangle the authors' original submission into the data visualization tools on the Lipid Interactome:
+
+{{< downloadthis /Users/gaelenguzman/LipidInteractomics_Website_local/LipidInteractomics_Website/IndividualStudies/DataTables/DataWrangling/RM_2021_Wrangling.R dname="RM_2021_wrangling">}}

### 2025-08-29 StudyInformation_includes/SF_2024_A_include.qmd
Addressing more of the reviewer comments, accession numbers mostly

@@
 #### Additional sample preparation <span class="help-symbol" title="e.g. sub-cellular fractionation, depletion, etc.">?</span>
+
+#### Data wrangling
+Use the download button below to download the R script used to wrangle the authors' original submission into the data visualization tools on the Lipid Interactome:
+
+{{< downloadthis /Users/gaelenguzman/LipidInteractomics_Website_local/LipidInteractomics_Website/IndividualStudies/DataTables/DataWrangling/SF_2024_ACS-Chem-Bio_wrangling.R dname="F_2024_ACS-Chem-Bio_wrangling">}}

### 2025-08-29 StudyInformation_includes/SF_2024_B_include.qmd
Fixed the SF 2024 data pages to include wrangling scripts and accession numbers
Addressing more of the reviewer comments, accession numbers mostly

@@
 ##### Journal
-ACS Chemical Biology
+Chemical Communications, Issue 52, 2024
 
@@
 ##### Additional sample preparation <span class="help-symbol" title="e.g. sub-cellular fractionation, depletion, etc.">?</span>
+
+#### Data wrangling
+Use the download button below to download the R script used to wrangle the authors' original submission into the data visualization tools on the Lipid Interactome:
+
+{{< downloadthis /Users/gaelenguzman/LipidInteractomics_Website_local/LipidInteractomics_Website/IndividualStudies/DataTables/DataWrangling/SF_2024_ChemComm_wrangling.R dname="SF_2024_ChemComm_wrangling">}}

### 2025-08-29 StudyInformation_includes/SK_2024_include.qmd
Addressing more of the reviewer comments, accession numbers mostly

@@
 ##### Additional sample preparation <span class="help-symbol" title="e.g. sub-cellular fractionation, depletion, etc.">?</span>
+
+#### Data wrangling
+Use the download button below to download the R script used to wrangle the authors' original submission into the data visualization tools on the Lipid Interactome:
+
+{{< downloadthis /Users/gaelenguzman/LipidInteractomics_Website_local/LipidInteractomics_Website/IndividualStudies/DataTables/DataWrangling/SK_2024_wrangling.R dname="SK_2024_wrangling">}}

### 2025-08-29 StudyInformation_includes/WY_2021_include.qmd
Addressing more of the reviewer comments, accession numbers mostly

@@
 PSM
+
+#### Data wrangling
+Use the download button below to download the R script used to wrangle the authors' original submission into the data visualization tools on the Lipid Interactome:
+
+{{< downloadthis /Users/gaelenguzman/LipidInteractomics_Website_local/LipidInteractomics_Website/IndividualStudies/DataTables/DataWrangling/WY_2021_wrangling.R dname="WY_2021_wrangling">}}

### 2025-08-29 IndividualStudies/DataTables/DataWrangling/AT_ChemComm2025_wrangling.R

@@ -3,52 +3,104 @@
 
 ####################
 
-
 # loading packages from source styles script
 library(here)
-
+here()
 ## Opening the source file for the ggplot custom theme
-source(here::here("Resources/ggplot_styles.R"))
+source(here::here("LipidInteractomics_Website/Resources/ggplot_styles.R"))
 
 ############################################################
 
-# Membrane dataset first 
+# Membrane dataset first
 
-dataRaw <- readr::read_csv(paste0(here(), "/IndividualStudies/DataTables/DataWrangling/AT_ChemComm2025_membrane.csv")) 
+dataRaw <- readr::read_csv(here(
+  "LipidInteractomics_Website/IndividualStudies/DataTables/DataWrangling/AT_ChemComm2025_membrane.csv"
+))
 
 data <- dataRaw |>
   mutate(
     gene_name = Gene,
     protein_id = Protein.ID,
-    hit_annotation = case_when(hit_annotation == "hit" & logFC < 0 ~ "no hit",
-                               hit_annotation == "candidate" & logFC < 0 ~ "no hit",
-                               .default = hit_annotation),
-    LipidProbe = case_when(comparison.label == "PE_UV vs PE_NoUV" ~ "PE",
-                           comparison.label == "PA_UV vs PA_NoUV" ~ "PA")
+    hit_annotation = case_when(
+      hit_annotation == "hit" & logFC < 0 ~ "no hit",
+      hit_annotation == "candidate" & logFC < 0 ~ "no hit",
+      .default = hit_annotation
+    ),
+    LipidProbe = case_when(
+      comparison.label == "PE_UV vs PE_NoUV" ~ "PE",
+      comparison.label == "PA_UV vs PA_NoUV" ~ "PA"
+    )
   ) |>
-  dplyr::select(gene_name, protein_id, Protein.Description, LipidProbe, sample, logFC, AveExpr, pvalue, hit_annotation, -Gene, -Protein.ID, -comparison.label) |>
+  dplyr::select(
+    gene_name,
+    protein_id,
+    Protein.Description,
+    LipidProbe,
+    sample,
+    logFC,
+    AveExpr,
+    pvalue,
+    hit_annotation,
+    -Gene,
+    -Protein.ID,
+    -comparison.label
+  ) |>
   arrange(hit_annotation) |>
   glimpse()
 
[…]

### 2025-08-29 IndividualStudies/DataTables/DataWrangling/DCC_2025_wrangling.R

@@ -7,7 +7,7 @@
 library(here)
 
 ## Opening the source file for the ggplot custom theme
-source(here::here("Resources/ggplot_styles.R"))
+source(here::here("LipidInteractomics_Website/Resources/ggplot_styles.R"))
 
 ############################################################
 
@@ -17,7 +17,7 @@ source(here::here("Resources/ggplot_styles.R"))
 #   - averaging logFC and pvalues for the ids of each protein by replicate, counting the number of reps for each protein
 #   - adding statistical annotation based on the publication's cutoffs
 #   - maintained the original statistical output from the publication
-data <- readr::read_csv(here("IndividualStudies/DataTables/DataWrangling/DCC_2025_ChemrXiv_FullDataset.csv")) |>
+data <- readr::read_csv(here("LipidInteractomics_Website/IndividualStudies/DataTables/DataWrangling/DCC_2025_ChemrXiv_FullDataset.csv")) |>
   glimpse() |>
   group_by(gene_name) |>
   filter(ratio_MvsL != "") |>

### 2025-08-29 IndividualStudies/DataTables/DataWrangling/SF_2024_ACS-Chem-Bio_wrangling.R

@@ -12,7 +12,7 @@ source(here::here("Resources/ggplot_styles.R"))
 
 ############################################################
 
-data <- read_csv(here("IndividualStudies/DataTables/DataWrangling/SF_ACS-ChemBio_2024_Limma_results_V3.csv")) |>
+data <- read_csv(here("LipidInteractomics_Website/IndividualStudies/DataTables/DataWrangling/SF_ACS-ChemBio_2024_Limma_results_V3.csv")) |>
   glimpse()
 
 
@@ -26,4 +26,14 @@ data <- data |>
   select(gene_name, protein_id, LipidProbe, hit_annotation, logFC, pvalue, AveExpr, fdr) |>
   glimpse() 
 
-write_csv(data, here("IndividualStudies/DataTables/SF_ACS-Chem-Bio_2024_download.csv"))
+# write_csv(data, here("LipidInteractomics_Website/IndividualStudies/DataTables/SF_ACS-Chem-Bio_2024_download.csv"))
+
+Sph_data <- data |>
+  filter(LipidProbe == "Sph")
+
+write_csv(Sph_data, here("LipidInteractomics_Website/LipidProbe/DataSets/Sph_Huh7_SF_2024.csv"))
+
+Spa_data <- data |>
+  filter(LipidProbe == "Spa")
+
+write_csv(Spa_data, here("LipidInteractomics_Website/LipidProbe/DataSets/Spa_Huh7_SF_2024.csv"))

### 2025-08-29 IndividualStudies/DataTables/DataWrangling/WY_2021_wrangling.R

@@ -13,72 +13,96 @@ source(here::here("Resources/ggplot_styles.R"))
 
 # 1 - Coercing data handoff into standard format
 
-RawData <- read_csv(here::here("IndividualStudies/DataTables/WY_2021_ACSChemBio_RawData2.csv"))
+RawData <- read_csv(here::here(
+  "LipidInteractomics_Website/IndividualStudies/DataTables/DataWrangling/WY_2021_ACSChemBio_RawData2.csv"
+))
 
-filtered_data <- RawData |> 
-  filter(if_all(starts_with("Control_"), ~ !is.na(.) & . != 0) & 
-         if_all(starts_with("Sample_"), ~ !is.na(.) & . != 0)) |>
+filtered_data <- RawData |>
+  filter(
+    if_all(starts_with("Control_"), ~ !is.na(.) & . != 0) &
+      if_all(starts_with("Sample_"), ~ !is.na(.) & . != 0)
+  ) |>
   arrange(-Control_1)
-         
+
 # Convert wide format to long format
-long_data <- filtered_data |> 
-  pivot_longer(cols = -gene_name, 
-               names_to = c("Condition", "Replicate"), 
-               names_sep = "_", 
-               values_to = "Abundance") |> 
+long_data <- filtered_data |>
+  pivot_longer(
+    cols = c(-gene_name, -Accession),
+    names_to = c("Condition", "Replicate"),
+    names_sep = "_",
+    values_to = "Abundance"
+  ) |>
   mutate(Condition = ifelse(Condition == "Control", "Control", "Sample"))
 
 # Count the number of observations per gene per condition
-complete_genes <- long_data |> 
+complete_genes <- long_data |>
   filter(if_all(starts_with("Abundance"), ~ !is.na(.))) |> # Keep only genes with full data in both groups
-  group_by(gene_name, Condition) |> 
-  summarise(count = n(), .groups = "drop") |> 
-  pivot_wider(names_from = Condition, values_from = count, values_fill = 0) |> 
-  filter(Control == 3 & Sample == 3) |>  
+  group_by(gene_name, Condition) |>
+  summarise(count = n(), .groups = "drop") |>
+  pivot_wider(names_from = Condition, values_from = count, values_fill = 0) |>
+  filter(Control == 3 & Sample == 3) |>
   pull(gene_name)
 
 # Filter the original dataset to include only these complete genes
[…]

### 2025-08-29 Resources/ggplot_styles.R

@@ -308,8 +308,6 @@ VolcanoPlotStandardized <- function(data) {
     return(VolcanoPlotly)
 }
 
-data <- read_csv(here("IndividualStudies/DataTables/WY_2021_ACSChemBio_Download.csv"))
-
 CC_enrichment_plots <- function(data, plotReturnType, filename){
 
 	################

### 2025-08-29 BioinformaticsApplicationNote/Bioinformatics_ReviewerResponseLetter.qmd
updated hours sheet

@@
 For example, the broken links and typographical errors in figure captions have been addressed, additional cell line information has been added to our *Comparing the Enriched Hits of Different Probes* Shiny app, we have included of accession number to convey crucial information about isoform identifications in addition to using gene name to identify hits (where possible in the original datasets; the authors of Hoglinger 2017 have been unresponsive and we do not have the accession number data for their results) and clarification about the qualitative nature of the comparisons displayed in the Shiny app.
-We have additionally provided links to download the R scripts were used to "wrangle" the submitted data to the formats that our data visualization functions accept.
+We have additionally provided links to download the R scripts which were used to "wrangle" the submitted data to the formats that our data visualization functions accept.
 

### 2025-08-29 HourlyTracking/202508_GG-Hours.qmd
updated hours sheet

--- 2025-08-06 HourlyTracking/202507_GG-Hours.qmd
@@
 ---
-titlJuly 2025 Lipid Interactome Monthly Invoice"
+title: August 2025 Lipid Interactome Monthly Invoice
 author: "Gaelen Guzman"
-date: "2025 08 04"
+date: "2025 09 04"
 output: 
@@
   - "\\fancyhead[C]{Lipid Interactome Monthly Invoice}"
-  - "\\fancyhead[R]{2025 08 04}"
+  - "\\fancyhead[R]{2025 09 04}"
   - "\\fancyfoot{}"
@@
 
-Carsten Schultz,
+Dear Dr. Schultz,
 
-Please find below the hours I logged for the month of July 2025, with descriptions of each day's activity.
-In total, I performed 6 hours of work at an hourly rate of $50 (USD), for a total bill of $300.
+Please find below the hours I logged for the month of August 2025, with descriptions of each day's activity.
+In total, I performed 4 hours of work at an hourly rate of $50 (USD), for a total bill of $200.
 
@@
   select(Date, Hours, Activity) |>
-  filter(Date >= as.Date("2025-07-01") & Date < as.Date("2025-08-01")) %>%  # Filter for April 2025
+  filter(Date >= as.Date("2025-08-01") & Date < as.Date("2025-09-01")) %>%  # Filter for April 2025
   glimpse()

### 2025-09-04 LipidProbe/PhosphatidicAcid.qmd
Working to address reviewer concerns

@@
 
-:::{.border}
+::: {.border}
 ::: {layout="[[-15,85], [100]]"}
@@
 
-::::{.callout-tip}
+:::: {.callout-tip}
+
 ### Cell background: HeLa
@@
 :::::{.border}
-::::{#fig-PE_GOplots}
+::::{#fig-PA_GOplots}
 ::: {.panel-tabset}

### 2025-09-04 LipidProbe/Sphingosine.qmd
Working to address reviewer concerns

@@
 
-:::{.cells collapse="true"}
-::::{.cells-header}
-Cell background: Huh7
-::::
-::::{.cells-container}
+:::{.callout-warning collapse="false"}
+### Cell Background: Huh7
 
@@
 
-::::
+<!-- End of .callout-warning block -->
 :::
 
-:::{.cells collapse="true"}
-::::{.cells-header}
-Cell background: HeLa
-::::
-::::{.cells-container}
+:::{.callout-warning collapse="false"}
+
+### Cell Background: HeLa
 
@@
 
-**\*Data presentation still in development.**
+**\*PSM data presentation still in development.**
 
-::::
+See [Höglinger et al. 2017](https://lipidinteractome.org/individualstudies/dh_2017) for results in context with Diacylglycerol and 8-3 Fatty Acid data.
+
+<!-- End of .callout-warning block -->
 :::

### 2025-09-04 StudyInformation_includes/RM_2021_include.qmd
Working to address reviewer concerns

@@
 
-Label free quantification *(as reported here, enabled via fresh analysis by Frank Stein, EMBL)*
+Label free quantification *(as reported here, enabled via fresh analysis by Frank Stein, EMBL -- details below)*
 
@@
 
+#### Data analysis
+
+**The authors of this paper were unable to provide the original results of their dataset, and we applied a label-free quantification data pipeline to their mass spectrometry files, publicly-available on ProteomExchange**
+
+For this analysis, raw protein intensities were processed by first selecting unique proteins supported by at least two razor peptides.
+Batch effects were then removed, and missing values were imputed using a hybrid strategy: KNN imputation was applied to high-confidence proteins with replicate-level missingness, while low-confidence proteins were assigned minimum detected values (MinDet).
+The data were subsequently variance-stabilized and normalized, after which differential abundance testing was performed using the limma framework.
+Parallel analyses were also carried out with the fdrtool package, with significance thresholds defined consistently across methods.
+Proteins were classified according to standard criteria: hits (FDR < 0.05 and |fold-change| > 1.5), candidates (FDR < 0.2 and |fold-change| > 1.5), enriched candidates (FDR < 0.2 and fold-change > 1.5), enriched hits (FDR < 0.05 and fold-change > 1.5), and all others as non-significant.
+
 #### Data wrangling

### 2025-09-04 IndividualStudies/DataTables/DataWrangling/AT_ChemComm2025_wrangling.R

@@ -17,7 +17,7 @@ dataRaw <- readr::read_csv(here(
   "LipidInteractomics_Website/IndividualStudies/DataTables/DataWrangling/AT_ChemComm2025_membrane.csv"
 ))
 
-data <- dataRaw |>
+MembraneData <- dataRaw |>
   mutate(
     gene_name = Gene,
     protein_id = Protein.ID,
@@ -50,13 +50,23 @@ data <- dataRaw |>
 
 # write_csv(data, here("IndividualStudies/DataTables/AT_ChemicalCommunications_2025_membrane_download.csv"))
 
-PA_data <- data |>
+PA_data <- MembraneData |>
   filter(LipidProbe == "PA")
-write_csv(PA_data, here("LipidInteractomics_Website/LipidProbe/DataSets/PA_membrane_HeLa_AT_2025.csv"))
+write_csv(
+  PA_data,
+  here(
+    "LipidInteractomics_Website/LipidProbe/DataSets/PA_membrane_HeLa_AT_2025.csv"
+  )
+)
 
-PE_data <- data |>
+PE_data <- MembraneData |>
   filter(LipidProbe == "PE")
-write_csv(PE_data, here("LipidInteractomics_Website/LipidProbe/DataSets/PE_membrane_HeLa_AT_2025.csv"))
+write_csv(
+  PE_data,
+  here(
+    "LipidInteractomics_Website/LipidProbe/DataSets/PE_membrane_HeLa_AT_2025.csv"
+  )
+)
 
 
 # Cytosol dataset second
@@ -64,7 +74,7 @@ dataRaw <- readr::read_csv(here(
   "LipidInteractomics_Website/IndividualStudies/DataTables/DataWrangling/AT_ChemComm2025_cytosol.csv"
 ))
 
-data <- dataRaw |>
+CytosolData <- dataRaw |>
   mutate(
     gene_name = Gene,
     protein_id = Protein.ID,
@@ -97,10 +107,39 @@ data <- dataRaw |>
 
 # write_csv(data, here("IndividualStudies/DataTables/AT_ChemicalCommunications_2025_cytosol_download.csv"))
 
-PA_data <- data |>
+PA_data <- CytosolData |>
   filter(LipidProbe == "PA")
-write_csv(PA_data, here("LipidInteractomics_Website/LipidProbe/DataSets/PA_cytosol_HeLa_AT_2025.csv"))
 
-PE_data <- data |>
[…]

### 2025-09-04 Resources/scripts.js

@@ -1,0 +1,68 @@
+document.addEventListener("DOMContentLoaded", function () {
+  // Find both patterns
+  const roots = document.querySelectorAll(
+    '.callout-cell.collapsible, .cells[collapse="true"], .cells[data-collapse="true"], .cells.collapsible'
+  );
+
+  roots.forEach(root => {
+    if (root.dataset.collapsibleInit === "1") return; // avoid double init
+    root.dataset.collapsibleInit = "1";
+
+    // 1) Find or create a header (prefer a direct child heading)
+    let header =
+      root.querySelector(':scope > .callout-header, :scope > .cells-header, :scope > h1, :scope > h2, :scope > h3, :scope > h4, :scope > h5, :scope > h6');
+
+    if (!header) {
+      // fallback: use first element as header if available
+      header = root.firstElementChild;
+      if (!header) return; // nothing to do
+    }
+
+    // Normalize header class based on container type
+    const isCells = root.classList.contains('cells');
+    header.classList.add(isCells ? 'cells-header' : 'callout-header');
+
+    // 2) Find or build the content wrapper
+    let content = root.querySelector(':scope > .callout-content, :scope > .cells-container');
+    if (!content) {
+      content = document.createElement('div');
+      content.className = isCells ? 'cells-container' : 'callout-content';
+      // Move all siblings after header into content
+      let sib = header.nextSibling;
+      while (sib) {
+        const next = sib.nextSibling;
+        content.appendChild(sib);
+        sib = next;
+      }
+      root.appendChild(content);
+    }
+
+    // 3) A11y + initial state
+    header.setAttribute('role', 'button');
+    header.setAttribute('tabindex', '0');
+
+    const startsOpen =
+      root.classList.contains('open') ||
+      root.getAttribute('open') === 'true' ||
+      root.getAttribute('data-open') === 'true';
+
+    const setOpen = (open) => {
+      content.style.display = open ? '' : 'none';
+      root.classList.toggle('open', open);
+      header.setAttribute('aria-expanded', String(open));
+    };
+
+    setOpen(!!startsOpen);
+
+    // 4) Toggle handlers (click + keyboard)
+    const toggle = () => setOpen(content.style.display === 'none');
+
+    header.addEventListener('click', toggle);
+    header.addEventListener('keydown', (e) => {
+      if (e.key === 'Enter' || e.key === ' ') {
+        e.preventDefault();
+        toggle();
+      }
+    });
+  });
+});

### 2025-09-04 ShinyApps/CompareLipidProbes/AddNewStudies.R

@@ -1,0 +1,55 @@
+
+
+
+smallDataset <- bigDataSet |>
+  mutate(studyPointer = paste(LipidProbe, CellLine, sep = " - "))
+
+studyPointers <- unique(smallDataset$studyPointer)
+
+studyPointers <- as.data.frame(studyPointers) |>
+  mutate(
+    Publication = case_when(
+      studyPointers %in% c("Sph - Huh7", "Spa - Huh7") ~
+        "Farley et al. 2024, Chemical Communications",
+      studyPointers %in% c("8-3 FA - Huh7", "1-10 FA - Huh7") ~
+        "Farley et al. 2024, ACS Chemical Biology",
+      studyPointers %in% c("BF-NAPE - HeLa") ~ "Chiu et al. 2025, ChemrXiv",
+      studyPointers %in% c("bf-GPI - HeLa") ~ "Kundu et al. 2024, Chem Euro",
+      studyPointers %in% c("PDAA - HeLa") ~ "Yu et al. 2021, ACS Chem Bio",
+      studyPointers %in%
+        c(
+          "PA - HeLa - Membrane",
+          "PE - HeLa - Membrane",
+          "PA - HeLa - Cytosol",
+          "PE - HeLa - Cytosol"
+        ) ~
+        "Thomas et al. 2025, Chemical Communications",
+    ),
+    URL = case_when(
+      studyPointers %in% c("Sph - Huh7", "Spa - Huh7") ~
+        "https://lipidinteractome.org/individualstudies/sf_2024_b",
+      studyPointers %in% c("8-3 FA - Huh7", "1-10 FA - Huh7") ~
+        "https://lipidinteractome.org/individualstudies/sf_2024",
+      studyPointers %in% c("BF-NAPE - HeLa") ~
+        "https://lipidinteractome.org/individualstudies/dcc_2025",
+      studyPointers %in% c("bf-GPI - HeLa") ~
+        "https://lipidinteractome.org/individualstudies/sk_2024",
+      studyPointers %in% c("PDAA - HeLa") ~
+        "https://lipidinteractome.org/individualstudies/wy_2021",
+      studyPointers %in%
+        c(
+          "PA - HeLa - Membrane",
+          "PE - HeLa - Membrane",
+          "PA - HeLa - Cytosol",
+          "PE - HeLa - Cytosol"
+        ) ~
+        "https://lipidinteractome.org/individualstudies/at_2025",
+    )
+  )
+
[…]

### 2025-09-04 ShinyApps/CompareLipidProbes/app.R

@@ -13,34 +13,51 @@ library(shinycssloaders)
 # source("/Users/gaelenguzman/LipidInteractomics_Website_local/LipidInteractomics_Website/ShinyApps/CompareLipidProbes/PlottingFunction.R")
 
 # # File path for testing
-# df <- read_csv("/Users/gaelenguzman/LipidInteractomics_Website_local/LipidInteractomics_Website/ShinyApps/CompareLipidProbes/combinedProbeDatasets_TMT.csv") |>
-#     mutate(probeOptions = paste0(LipidProbe, " - ", CellLine))
-
-
+# df <- read_csv(
+#   "/Users/gaelenguzman/LipidInteractomics_Website_local/LipidInteractomics_Website/ShinyApps/CompareLipidProbes/combinedProbeDatasets_TMT.csv"
+# ) |>
+#   mutate(probeOptions = paste0(LipidProbe, " - ", CellLine))
+#
+# studies <- read_csv(here(
+#   "/Users/gaelenguzman/LipidInteractomics_Website_local/LipidInteractomics_Website/ShinyApps/CompareLipidProbes/Studies.csv"
+# ))
 
 # File path for deploying to Shinyapps.io
-source("PlottingFunction.R")
-df <- read_csv("combinedProbeDatasets_TMT.csv") |>
-   mutate(probeOptions = paste0(LipidProbe, " - ", CellLine))
+source("combinedProbeDatasets_TMT.csv")
 
+df <- read_csv("combinedProbeDatasets_TMT.csv") |>
+  mutate(probeOptions = paste0(LipidProbe, " - ", CellLine))
+
+studies <- read_csv("Studies.csv")
 
 probeOptions <- unique(df$probeOptions)
-
 
 
 ########################################################
 # UI
 ui <- fluidPage(
   titlePanel("Interactive LogFC Comparison"),
-  
+
   sidebarLayout(
     sidebarPanel(
-      selectInput("probe1", "Select First LipidProbe:", choices = probeOptions, selected = probeOptions[1]),
-      selectInput("probe2", "Select Second LipidProbe:", choices = probeOptions, selected = probeOptions[2])
+      selectInput(
+        "probe1",
+        "Select First LipidProbe:",
+        choices = probeOptions,
+        selected = probeOptions[1]
+      ),
+      selectInput(
+        "probe2",
+        "Select Second LipidProbe:",
+        choices = probeOptions,
[…]

### 2025-09-04 StudyInformation_includes/AT_2025_include.qmd
Added download links to all the original data

@@
 {{< downloadthis /Users/gaelenguzman/LipidInteractomics_Website_local/LipidInteractomics_Website/IndividualStudies/DataTables/DataWrangling/AT_ChemComm2025_wrangling.R dname="AT_ChemComm2025_wrangling">}}
+
+Use the download buttons below to download the original data file prior to wrangling:
+
+{{< downloadthis /Users/gaelenguzman/LipidInteractomics_Website_local/LipidInteractomics_Website/IndividualStudies/DataTables/DataWrangling/AT_ChemComm2025_cytosol.csv dname="AT_2025_Cytosol_OriginalData">}}
+
+{{< downloadthis /Users/gaelenguzman/LipidInteractomics_Website_local/LipidInteractomics_Website/IndividualStudies/DataTables/DataWrangling/AT_ChemComm2025_membrane.csv dname="AT_2025_Membrane_OriginalData">}}

### 2025-09-04 StudyInformation_includes/DCC_2025_include.qmd
Added download links to all the original data

@@
 
+None
+
+#### Lipid interactomics data analysis
+
+Data as submitted by the original authors was not normalized.
+To make these results more similar to the other datasets presented here, we performed median normalization to center the distribution around a logFC value of 0 (see the R file below for wrangling).
+We also needed to do an Ensemble query to find the gene names for the accession numbers of proteins identified in this dataset.
+
 #### Data wrangling
@@
 {{< downloadthis /Users/gaelenguzman/LipidInteractomics_Website_local/LipidInteractomics_Website/IndividualStudies/DataTables/DataWrangling/DCC_2025_wrangling.R dname="DCC_2025_wrangling">}}
+
+Use the download button below to download the original data file prior to wrangling:
+
+{{< downloadthis /Users/gaelenguzman/LipidInteractomics_Website_local/LipidInteractomics_Website/IndividualStudies/DataTables/DataWrangling/DCC_2025_ChemrXiv_FullDataset.csv dname="DCC_2025_OriginalData">}}

### 2025-09-04 StudyInformation_includes/RM_2021_include.qmd
Added download links to all the original data

@@
 #### Data wrangling
+
 Use the download button below to download the R script used to wrangle the authors' original submission into the data visualization tools on the Lipid Interactome:
@@
 {{< downloadthis /Users/gaelenguzman/LipidInteractomics_Website_local/LipidInteractomics_Website/IndividualStudies/DataTables/DataWrangling/RM_2021_Wrangling.R dname="RM_2021_wrangling">}}
+
+Use the download button below to download the original data file prior to wrangling:
+
+{{< downloadthis /Users/gaelenguzman/LipidInteractomics_Website_local/LipidInteractomics_Website/IndividualStudies/DataTables/DataWrangling/RM_2021_limmaResults.csv dname="RM_2021_OriginalData">}}

### 2025-09-04 StudyInformation_includes/SF_2024_A_include.qmd
Added download links to all the original data

@@
 {{< downloadthis /Users/gaelenguzman/LipidInteractomics_Website_local/LipidInteractomics_Website/IndividualStudies/DataTables/DataWrangling/SF_2024_ACS-Chem-Bio_wrangling.R dname="F_2024_ACS-Chem-Bio_wrangling">}}
+
+Use the download button below to download the original data file prior to wrangling:
+
+{{< downloadthis /Users/gaelenguzman/LipidInteractomics_Website_local/LipidInteractomics_Website/IndividualStudies/DataTables/DataWrangling/SF_ACS-ChemComm_2024_Limma_results_V3.csv dname="SF_2024_ACS-ChemBio_OriginalData">}}

### 2025-09-04 StudyInformation_includes/SF_2024_B_include.qmd
Added download links to all the original data

@@
 {{< downloadthis /Users/gaelenguzman/LipidInteractomics_Website_local/LipidInteractomics_Website/IndividualStudies/DataTables/DataWrangling/SF_2024_ChemComm_wrangling.R dname="SF_2024_ChemComm_wrangling">}}
+
+Use the download button below to download the original data file prior to wrangling:
+
+{{< downloadthis /Users/gaelenguzman/LipidInteractomics_Website_local/LipidInteractomics_Website/IndividualStudies/DataTables/DataWrangling/SF_ChemComm_2024_Limma_results_V3.csv dname="SF_2024_ChemComm_OriginalData">}}

### 2025-09-04 StudyInformation_includes/SK_2024_include.qmd
Added download links to all the original data

@@
 {{< downloadthis /Users/gaelenguzman/LipidInteractomics_Website_local/LipidInteractomics_Website/IndividualStudies/DataTables/DataWrangling/SK_2024_wrangling.R dname="SK_2024_wrangling">}}
+
+Use the download button below to download the original data file prior to wrangling:
+
+{{< downloadthis /Users/gaelenguzman/LipidInteractomics_Website_local/LipidInteractomics_Website/IndividualStudies/DataTables/DataWrangling/SK_2024_fullDataset_originalHandoff.csv dname="SK_2024_ChemEuro_OriginalData">}}

### 2025-09-04 ShinyApps/CompareLipidProbes/app.R

@@ -23,7 +23,8 @@ library(shinycssloaders)
 # ))
 
 # File path for deploying to Shinyapps.io
-source("combinedProbeDatasets_TMT.csv")
+
+source("PlottingFunction.R")
 
 df <- read_csv("combinedProbeDatasets_TMT.csv") |>
   mutate(probeOptions = paste0(LipidProbe, " - ", CellLine))

### 2025-09-04 StudyInformation_includes/SF_2024_A_include.qmd
Fixed the rendering of the study metadata, it was caught in the freezed pages.

--- 2025-08-29 StudyInformation_includes/SF_2024_A_include.qmd
@@
 {{< downloadthis /Users/gaelenguzman/LipidInteractomics_Website_local/LipidInteractomics_Website/IndividualStudies/DataTables/DataWrangling/SF_2024_ACS-Chem-Bio_wrangling.R dname="F_2024_ACS-Chem-Bio_wrangling">}}
+
+Use the download button below to download the original data file prior to wrangling:
+
+{{< downloadthis /Users/gaelenguzman/LipidInteractomics_Website_local/LipidInteractomics_Website/IndividualStudies/DataTables/DataWrangling/SF_ChemComm_2024_Limma_results_V3.csv dname="SF_2024_ACS-ChemBio_OriginalData">}}

### 2025-09-04 StudyInformation_includes/SK_2024_include.tex
Fixed the rendering of the study metadata, it was caught in the freezed pages.

--- 2025-07-30 _site/BioinformaticsApplicationNote/GG_2025_applicationNote.tex
@@
 \makeatother
-% definitions for citeproc citations
-\NewDocumentCommand\citeproctext{}{}
-\NewDocumentCommand\citeproc{mm}{%
-  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
-\makeatletter
- % allow citations to break across lines
- \let\@cite@ofmt\@firstofone
- % avoid brackets around text for \cite:
- \def\@biblabel#1{}
- \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
-\makeatother
-\newlength{\cslhangindent}
-\setlength{\cslhangindent}{1.5em}
-\newlength{\csllabelwidth}
-\setlength{\csllabelwidth}{3em}
-\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
- {\begin{list}{}{%
-  \setlength{\itemindent}{0pt}
-  \setlength{\leftmargin}{0pt}
-  \setlength{\parsep}{0pt}
-  % turn on hanging indent if param 1 is 1
-  \ifodd #1
-   \setlength{\leftmargin}{\cslhangindent}
-   \setlength{\itemindent}{-1\cslhangindent}
-  \fi
-  % set entry spacing
-  \setlength{\itemsep}{#2\baselineskip}}}
- {\end{list}}
-\usepackage{calc}
-\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
-\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
 
@@
 \hypersetup{
-  pdftitle={The Lipid Interactome},
-  pdfkeywords={Lipid-protein
-interactions, Proteomics, Interactomics, Database, Multifunctionalized
-lipids},
   colorlinks=true,
@@
 
-\title{The Lipid Interactome}
-\usepackage{etoolbox}
-\makeatletter
-\providecommand{\subtitle}[1]{% add subtitle to \maketitle
-  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
-}
-\makeatother
-\subtitle{An interactive and open access platform for exploring cellular
-lipid-protein interactomes}
-\author{Gaelen Guzman \and André Nadler \and Frank Stein \and Jeremy M.
-Baskin \and Carsten Schultz \and Fikadu Tafesse}
-\date{2025-02-04}
+\author{}
+\date{}
 
 \begin{document}
-\maketitle
 
-\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}
+\paragraph{Study details}\label{study-details}
 
-\subsection{Authors}\label{authors}
+\subparagraph{Authors}\label{authors}
 
-Gaelen Guzman\textsuperscript{1,}*, André Nadler\textsuperscript{2},
-Frank Stein\textsuperscript{3}, Jeremy M. Baskin\textsuperscript{4},
-Carsten Schulz\textsuperscript{1}, Fikadu G. Tafesse\textsuperscript{1}
+Sayan Kundu, Mohit Jaiswal, Venkanna Babu Mullapudi, Jiatong Guo, Manasi
+Kamat, Kari B. Basso, Zhongwu Guo
 
-\textsuperscript{1} = Departments of Molecular Immunology and Immunology
-and Chemical Physiology and Biochemistry, Oregon Health \& Science
-University, Portland, OR, USA; \textsuperscript{2} = Max Plank Institute
-of Molecular Cell Biology and Genetics, Dresden Germany;
-\textsuperscript{3} = Proteomics Core Facility, European Molecular
-Biology Laboratory, Heidelberg, Germany; \textsuperscript{4} =
-Department of Chemistry and Chemical Biology and Weill Institute for
-Cell and Molecular Biology, Cornell University, Ithaca, NY, USA; * =
-Corresponding author:
-\href{mailto:gaelen.guzman@lipidinteractome.org}{\nolinkurl{gaelen.guzman@lipidinteractome.org}}
+\subparagraph{Journal}\label{journal}
 
-\subsection{Summary}\label{summary}
+Chemistry - A European Journal
+\url{https://doi.org/10.1002/chem.202303047}
 
-\subsubsection{Abstract}\label{abstract}
+\subparagraph{Abstract}\label{abstract}
 
-Lipid--protein interactions play essential roles in cellular signaling
-and membrane dynamics, yet their systematic characterization has long
-been hindered by the inherent biochemical properties of lipids. Recent
-advances in functionalized lipid probes -- equipped with
-photoactivatable crosslinkers, affinity handles, and photocleavable
-protecting groups -- have enabled proteomics-based identification of
-lipid interacting proteins with unprecedented specificity and
-resolution. Despite the growing number of published lipid interactomes,
-there remains no centralized effort to harmonize, compare, or integrate
-these datasets.
+Glycosylphosphatidylinositols (GPIs) need to interact with other
+components in the cell membrane to transduce transmembrane signals. A
+bifunctional GPI probe was employed for photoaffinity‐based proximity
+labelling and identification of GPI‐interacting proteins in the cell
+membrane. This probe contained the entire core structure of GPIs and was
+functionalized with photoreactive diazirine and clickable alkyne to
+facilitate its crosslinking with proteins and attachment of an affinity
+tag. It was disclosed that this probe was more selective than our
+previously reported probe containing only a part structure of the GPI
+core for cell membrane incorporation and an improved probe for studying
+GPI‐cell membrane interaction. Eighty‐eight unique membrane proteins,
+many of which are related to GPIs/GPI‐anchored proteins, were identified
+utilizing this probe. The proteomics dataset is a valuable resource for
+further analyses and data mining to find new GPI‐related proteins and
+signalling pathways. A comparison of these results with those of our
+previous probe provided direct evidence for the profound impact of GPI
+glycan structure on its interaction with the cell membrane.
 
-The Lipid Interactome addresses this gap by providing a structured,
-interactive web portal that adheres to FAIR data principles -- ensuring
-that lipid interactome studies are Findable, Accessible, Interoperable,
-and Reusable. Through standardized data formatting, interactive
-visualizations, and direct cross-study comparisons, this resource
-enables researchers to systematically explore the protein-binding
-partners of diverse bioactive lipids. By consolidating and curating
-lipid interactome proteomics data from multiple studies, the Lipid
-Interactome database serves as a critical tool for deciphering the
-biological functions of lipids in cellular systems.
+\subparagraph{Lipid probes utilized}\label{lipid-probes-utilized}
 
-\subsubsection{Availability}\label{availability}
+Bifunctional Glycosylphosphatidylinositol (bf-GPI)
 
-This site can be viewed at
-\href{lipidinteractome.org}{LipidInteractome.org} all data is available
-for download. No user information is collected or necessary for data
-navigation, interaction, or download.
+Bifunctional phosphatidyl moiety with \alpha\&-D-glucoside (Control)
 
-\subsubsection{Data Submission \&
-Contact}\label{data-submission-contact}
+\subparagraph{Cell line analyzed}\label{cell-line-analyzed}
 
-If you would like to submit a relevant dataset, see our
-\href{https://lipidinteractome.org/contactus/datasubmission}{Data
-Submission Page} for details, contact info, and instructions. For site
-feedback and additional questions, please email the site administrators
-at
-\href{mailto:Contact.Us@lipidinteractome.org}{\nolinkurl{Contact.Us@lipidinteractome.org}}
+\href{https://www.atcc.org/products/ccl-2}{HeLa}
 
-\subsubsection{Keywords}\label{keywords}
-
-Lipid-protein interactions, proteomics, interactomics, database,
-multifunctionalized lipids, photoaffinity labeling
-
-\subsection{Introduction}\label{introduction}
-
-Historically, lipids have been considered merely the passive structural
-components of cellular membranes. However, recent decades have revealed
-that this diverse category of biomolecule plays essential and active
-roles in the cell, ranging from modulating membrane dynamics,
-determining organelle identity, serving as catabolites for energy
-storage and metabolism, and bioactive signaling mediators for organellar
-and intracellular signaling\textsuperscript{1--6}. Interactions with
-proteins are essential to many of these crucial lipid functions -- and
-yet, lipid--protein interactions are extremely challenging to study: The
-small size and biophysical properties of lipids make conventional
-proteomics approaches unsuitable for mapping lipid
-interactors\textsuperscript{7}. Unlike proteins, which can be readily
-tagged or immobilized for affinity-based interaction studies, lipids
-require specialized chemical modifications to enable selective and
-controlled interaction profiling\textsuperscript{8}.
-
-Recent advances in synthetic, multifunctionalized lipid analogs have
-revolutionized the field, enabling the systematic interrogation of lipid
-interactomes\textsuperscript{8}. These probes incorporate strategically
-designed functional groups that enable covalent crosslinking, affinity
-enrichment, and controlled activation. Most commonly, these include: (1)
-a diazirine group for photoactivatable crosslinking upon exposure to 355
-nm ultraviolet (UV) light, stabilizing non-covalent and often
-modest-affinity lipid--protein interactions; (2) a terminal alkyne,
-permitting click chemistry-based enrichment; and, in some cases, (3) a
-coumarin photocage, which shields the lipid probe from premature
-enzymatic modification until it is selectively cleaved by 405 nm light
-(a wavelength that does not induce diazirine
-photolysis)\textsuperscript{7--10}. Together, these modifications enable
-direct proteomic identification of lipid interactors, distinguishing
-true binding partners from transient or non-specific
-associations\textsuperscript{7,10,11}.
-
-Numerous studies have already employed these lipid probes to elucidate
-the interactomes of key bioactive lipids, including diacylglycerol,
-sphingosine, sphinganine, phosphatidic acid, and
-phosphatidylethanolamine, N-acylphosphatidylethanolamine, and
-phosphatidyl alcohol\textsuperscript{9,11--16}. These initial studies
-have followed a comparative proteomics workflow, wherein crosslinked
-(``+UV'') and non-crosslinked (``-UV'') samples are analyzed side by
-side to minimize artifacts and confirm
-specificity\textsuperscript{7,10}. However, despite the growing number
-of lipid interactome datasets, no centralized resource has existed to
-compile, compare, and standardize these findings.
-
-To address this gap, we present the
-\href{https://www.lipidinteractome.org}{Lipid Interactome} -- a curated
-repository designed to facilitate the comparative analysis of
-lipid--protein interactions from multiple studies. This resource
-consolidates proteomics data from multifunctional lipid probes, enabling
-researchers to efficiently explore and contextualize lipid-binding
-proteins across different lipid species and cellular models. Currently,
-the repository hosts interactomes derived from trifunctionalized
-phosphatidic acid, phosphatidylethanolamine, phosphatidylinositol
-\emph{tris}phosphate, N-acylphosphatidylethanolamine, phosphatidyl
-alcohol, sphingosine, and sphinganine in HeLa and Huh7
-cells\textsuperscript{11,13--16}. Additionally, it includes control
-datasets from two fatty acid probes to distinguish specific from
-non-specific lipid-binding proteins\textsuperscript{12}. We additionally
-intend to expand this resource to include more complex experimental
-designs as they are published (e.g.~Disease versus Healthy Control or
-Infection versus Mock).
-
-By providing a centralized platform for lipid interactome data, the
-Lipid Interactome significantly lowers the barriers to entry for
-researchers investigating lipid signaling pathways, enabling hypothesis
-generation through comparative analysis of multiple studies. Overall,
-this repository represents an important step toward systematizing
-lipid--protein interaction studies, ensuring that bioactive lipids are
-afforded the same level of proteomic scrutiny as their protein
-counterparts.
-
-\subsection{Description}\label{description}
-
-\subsubsection{Overview}\label{overview}
-
-The~Lipid Interactome~is an interactive discovery platform built
-using~Quarto, designed to centralize and enhance the study of
-lipid--protein interactions through curated datasets and dynamic
-visualization tools. Each page integrates~R-generated figures, embedding
-scripts directly into the source material to ensure reproducibility and
-transparency. The repository currently hosts data from~seven published
-studies, with an expandable framework that supports the incorporation of
-future datasets as the field progresses.
-
-At its core, the~Lipid Interactome~enables the~direct, qualitative
-comparison~of lipid interactomes between studies, providing researchers
-with invaluable insights into the diverse roles that bioactive lipids
-play in cellular processes. By leveraging standardized data formatting
-and interactive visualization -- including study-specific analysis
-pages, lipid probe aggregation, and cross-study comparisons via
-a~Shiny~application -- the platform facilitates intuitive exploration of
-protein--lipid interactions. As a~living repository, we actively
-encourage researchers to contribute their findings through
-our~\href{https://lipidinteractome.org/contactus/datasubmission}{Data~Submission}~page,
-ensuring that this resource continues to evolve alongside advancements
-in lipidomics research.
-
-\subsubsection{FAIR data principles}\label{fair-data-principles}
-
-The~Lipid Interactome~database was developed with the FAIR (Findable,
-Accessible, Interoperable, and Reusable) data principles in mind,
-ensuring that lipid--protein interaction data can be systematically
-explored, compared, and reused by the research community. Given the
-historical inconsistency in proteomics data curation, we have taken
-deliberate steps to standardize, annotate, and document our datasets for
-maximum utility.
-
-\paragraph{Findable}\label{findable}
-
-To address the fragmented nature of lipid interactome studies, we have
-established a centralized platform where researchers can interact with
-the results of individual studies or explore aggregated findings across
-multiple studies on a given lipid. The repository is structured to
-facilitate intuitive navigation between experimental datasets, offering
-clear entry points for study-specific and lipid-specific analyses.
-Because this resource is intended as a living repository, we actively
-invite researchers to contribute their findings following the submission
-guidelines detailed on
-our~\href{https://lipidinteractome.org/contactus/datasubmission}{Data
-Submission}~page.
-
-\paragraph{Accessible}\label{accessible}
-
-All datasets within~the Lipid Interactome~are available for download in
-standardized~\texttt{.csv}~format, ensuring broad accessibility across
-different computational environments. To further enhance usability, we
-provide
-a~\href{https://www.lipidinteractome.org/background/multifunctionallipidprobesoverview}{detailed~overview~of
-data~generation~and~analysis}, including explicit descriptions of
-dataset structure, column definitions, and the inherent limitations of
-multifunctional lipid probes. Only peer-reviewed proteomics datasets are
-included in this repository to maintain high data quality and
-reliability.
-
-\paragraph{Interoperable}\label{interoperable}
-
-Given the diversity of methodologies employed across lipid interactome
-studies, we have taken care to harmonize data formats and metadata
-annotations. While many studies share common analytical pipelines,
-others employ distinct mass spectrometry workflows. To ensure
-consistency, we have structured the data to allow parallel comparisons
-and
-provided~\href{https://www.lipidinteractome.org/background/proteomicsusingmultifunctionalprobes}{documentation~on~methodological~differences}.
-This standardization effort facilitates direct cross-study comparisons
-without requiring extensive reformatting by the end user. Each dataset
-is accompanied by metadata which describe the sample handling and data
-analysis techniques -- with clarifying text describing how
-``significance'' is determined for each analysis.
-
-\paragraph{Reusable}\label{reusable}
-
-To maximize the utility of these datasets, we provide extensive
-documentation detailing data acquisition, analysis workflows, and
-potential limitations. Wherever possible, technical jargon has been
-minimized to ensure accessibility to a broad audience, from lipid
-biologists to computational scientists. Additionally, we reference key
-publications that delve deeper into the synthesis of lipid probes and
-the specifics of each proteomics workflow, allowing researchers to
-further contextualize and validate their findings.
-
-By adhering to these FAIR principles,~the Lipid Interactome~database
-aims to serve as a robust and enduring resource for the lipid biology
-community, reducing redundancy, improving data transparency, and
-accelerating the study of lipid-mediated signaling.
-
-\subsubsection{Data Visualization and Download
-Modules}\label{data-visualization-and-download-modules}
-
-To facilitate efficient exploration and analysis of lipid--protein
-interaction data, the~Lipid Interactome~repository incorporates a suite
-of interactive visualization and data access tools. These modules are
-designed to enhance user engagement, provide clear interpretability of
-experimental findings, and streamline data retrieval for further
-computational analysis -- overall, the site is designed to ensure that
-the~Lipid Interactome~is not merely a static repository, but rather a
-dynamic and evolving resource for lipid biologists and bioinformaticians
-alike.
-
-\paragraph{Study-Specific Data
-Exploration}\label{study-specific-data-exploration}
-
-Each publication contributing to the repository is provided with a
-dedicated results page, allowing users to examine study findings in
-detail. These pages include interactive~Volcano,~Ranked-Order, and~MA
-plots, which enable visualization of differential protein enrichment
-across experimental conditions. The plots are rendered using
-the~Plotly~and~htmlwidgetsR packages, ensuring a responsive, client-side
-experience that supports zooming, hovering, image export, and data
-filtering\textsuperscript{17,18}. For transparency and reproducibility,
-all datasets associated with a given study are available for direct
-download.
-
-\paragraph{Lipid Probe-Specific Pages}\label{lipid-probe-specific-pages}
-
-In addition to the pages for each independent publication, datasets are
-further organized by lipid probe, providing a consolidated view of
-protein interactors detected across multiple experiments and independent
-studies. Each lipid-specific page includes study metadata and cell type
--- facilitating cross-study comparisons. Future iterations of the
-repository will extend this functionality by enabling direct comparisons
-of interactomes obtained from different cell lines treated with the same
-lipid probe, further refining the contextual understanding of
-lipid--protein interactions.
-
-\paragraph{Comparative Analysis via Shiny
-Application}\label{comparative-analysis-via-shiny-application}
-
-Where study design permits, data has been integrated into an
-interactive~Shiny~application, allowing users to perform direct (though
-qualitative)~probe-to-probe
-comparisons~(\href{https://www.lipidinteractome.org/lipidprobe/enrichedhitscomparison}{Probe~vs~Probe~Comparisons}).
-This tool enables researchers to explore the similarity of lipid
-interactomes across experimental conditions via~linear regression
-analysis, highlighting proteins that are significantly enriched in one
-dataset, both datasets, or neither. By providing an intuitive framework
-for interactome comparison, this feature aids in the identification of
-promising targets for further investigation.
-
-Because each publication utilizes distinct sample handling and data
-analysis techniques, we emphasize that these comparisons are qualitative
--- we hope to discourage quantitative statements regarding relative
-enrichment between lipid probes (e.g.~``Protein X is enriched 3x more to
-Lipid A than to Lipid B''). However, great utility lies in assessing
-co-enrichment (or orthogonal enrichment) of proteins to disparate lipid
-probes without quantitative comparison.
-
-\subsubsection{Data format}\label{data-format}
-
-While there are numerous ways to quantify the mass spectrometry (MS)
-data, the majority of studies included in our repository have utilized
-the same (or highly similar) quantitative MS pipeline using
-data-dependent acquisition techniques, such as Tandem Mass
-Tagging\textsuperscript{19}. These datasets include those reported by
-Farley et al.~(2024), Farley et al.~(2024), and Thomas et
-al.~(2025)\textsuperscript{11--13}. Some studies have also featured
-quantitative MS analysis using stable isotope labeling of amino acids in
-cell culture (SILAC), which also enables extraction of key data
-described below\textsuperscript{14,15}. Correspondingly, the ideal data
-structure for incorporation into our repository will include the
-following:
+\paragraph{Uncaging \& Crosslinking
+timeline}\label{uncaging-crosslinking-timeline}
 
 \begin{longtable}[]{@{}
-  >{\raggedright\arraybackslash}p{(\linewidth - 10\tabcolsep) * \real{0.1486}}
-  >{\centering\arraybackslash}p{(\linewidth - 10\tabcolsep) * \real{0.1081}}
-  >{\centering\arraybackslash}p{(\linewidth - 10\tabcolsep) * \real{0.3514}}
-  >{\centering\arraybackslash}p{(\linewidth - 10\tabcolsep) * \real{0.1216}}
-  >{\centering\arraybackslash}p{(\linewidth - 10\tabcolsep) * \real{0.1622}}
-  >{\centering\arraybackslash}p{(\linewidth - 10\tabcolsep) * \real{0.1081}}@{}}
-\caption{\textbf{Example data table for smooth incorporation into Lipid
-Interactome.} \textbf{\emph{Column descriptions:}} \emph{Gene name}: The
-identifier for genes identified in the dataset (or Accession Number).
-\emph{Uniprot accession}: Stable identifiers of UniProtKB entries;
-integrates species and isoform data on the identified protein.
-\emph{Enrichment value}: Fold change of Experimental versus Control
-fold-change, typically log2-transformed -- ideally the product of TMT or
-other quantitative mass spectrometry methods. \emph{p value}: the
-results of an ANOVA or LIMMA analysis, corrected for multiple hypothesis
-testing. \emph{AveExpr}: An averaged value of the m/z ion intensity of
-the Experimental condition and Control condition used for the enrichment
-value (used to prepare MA plots for quality control). \emph{FDR}:
-False-discovery rate of protein
-identification.}\label{tbl-1}\tabularnewline
+  >{\raggedright\arraybackslash}p{(\linewidth - 8\tabcolsep) * \real{0.2000}}
+  >{\centering\arraybackslash}p{(\linewidth - 8\tabcolsep) * \real{0.2000}}
+  >{\centering\arraybackslash}p{(\linewidth - 8\tabcolsep) * \real{0.2000}}
+  >{\centering\arraybackslash}p{(\linewidth - 8\tabcolsep) * \real{0.2000}}
+  >{\centering\arraybackslash}p{(\linewidth - 8\tabcolsep) * \real{0.2000}}@{}}
 \toprule\noalign{}
 \begin{minipage}[b]{\linewidth}\raggedright
-Gene name
+Lipid Probe
 \end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-\href{https://www.uniprot.org/help/accession_numbers}{Uniprot accession}
+Uptake time
 \end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-logFC
+Uncaging time
 \end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-p value
+Interaction time
 \end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-AveExpr
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-FDR
-\end{minipage} \\
-\midrule\noalign{}
-\endfirsthead
-\toprule\noalign{}
-\begin{minipage}[b]{\linewidth}\raggedright
-Gene name
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-\href{https://www.uniprot.org/help/accession_numbers}{Uniprot accession}
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-logFC
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-p value
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-AveExpr
-\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
-FDR
+Crosslinking time
 \end{minipage} \\
@@
 \endlastfoot
-GeneA & P80723 & 1.2 & 0.001 & 1.0x10\textsuperscript{18} & 0.0001 \\
-GeneB & P32004 & 0.1 & 0.6 & 1.0x10\textsuperscript{5} & 0.005 \\
-\ldots{} & \ldots{} & \ldots{} & \ldots{} & \ldots{} & \ldots{} \\
+bf-GPI & 180 min & NA & NA & 15 min \\
+Control & 180 min & NA & NA & 15 min \\
 \end{longtable}
 
-\textbf{We wish to emphasize that we will collaborate with data
-providers to prepare visualizations which best suit their datasets --
-the example dataset above merely depicts an ideal case which allows for
-easy incorporation and cross-study comparison.}
+\subparagraph{Mass spectrometry quantification
+method}\label{mass-spectrometry-quantification-method}
 
-Additionally, we are working on providing visualization functionality
-for studies which utilized Peptide Spectral Matching (PSM) to report
-enrichment toward lipid probes. Similarly, data-independent acquisitio
-(DIA) is a quickly emerging alternative to data-dependent acquisition
-(DDA; e.g.~TMT)\textsuperscript{20,21}; as with PSM datasets, we are
-working to incorporate DIA data formats.
+Precursor ion intensity Label Free Quantitation (LFQ), performed using
+Proteome Discoverer
 
-\subsection{Discussion}\label{discussion}
+\subparagraph{\texorpdfstring{Additional sample preparation
+{?}}{Additional sample preparation ?}}\label{additional-sample-preparation}
 
-The advent of functionalized lipid probes has fundamentally transformed
-lipid biology by enabling the proteomic identification of lipid-binding
-proteins with unprecedented specificity. However, as the number of
-published lipid interactome studies grows, the lack of a centralized
-framework for comparing and integrating these datasets presents a
-significant challenge for deciphering biological functions of individual
-lipids and lipid-binding proteins holistically and identifying trends
-across datasets. The Lipid Interactome was developed to address this
-need by providing researchers with a structured platform to explore,
-cross-reference, and build upon previous findings. By aggregating and
-standardizing lipid--protein interaction data, this resource facilitates
-the rapid identification of candidate lipid-binding proteins and
-supports orthogonal validation efforts.
+\paragraph{Data wrangling}\label{data-wrangling}
 
-Designed as a continuously expanding repository, the Lipid Interactome
-will evolve alongside advances in lipid probe technologies and
-interactomics. Future iterations will incorporate validation studies for
-each lipid probe, offering researchers a dedicated space to compare
-findings across experimental contexts. This functionality will not only
-reduce redundancy in experimental design but also strengthen the
-reproducibility and biological interpretation of lipid interactome
-research. To support this vision, we invite researchers to contribute
-their datasets via our
-\href{https://lipidinteractome.org/contactus/datasubmission}{Data
-Submission page}, fostering a collaborative and transparent approach to
-lipid biology.
+Use the download button below to download the R script used to wrangle
+the authors' original submission into the data visualization tools on
+the Lipid Interactome:
 
-\subsection{Abbreviations}\label{abbreviations}
-
-\begin{description}
-\tightlist
-\item[UV]
-\emph{U}ltra\emph{V}iolet
-\item[MS]
-\emph{M}ass \emph{S}pectrometry
-\item[LIMMA]
-\emph{Li}near \emph{M}odels for \emph{M}icro\emph{a}rray and RNA-Seq
-Data
-\item[ANOVA]
-\emph{An}alysis \emph{o}f \emph{Va}riance
-\item[PSM]
-\emph{P}eptide \emph{S}pectral \emph{M}atching
-\item[DIA]
-\emph{D}ata-\emph{I}ndedpendent \emph{A}cquisition
-\item[DDA]
-\emph{D}ata-\emph{D}edpendent \emph{A}cquisition
-\end{description}
-
-\subsection{Contributions}\label{contributions}
-
-GG designed, implemented, and wrote the majority of the LipidInteractome
-repository and manuscript. FS wrote the data analysis section of the
-repository, provided significant intellectual contribution to the
-repository design, and edited the manuscript. AN provided substantial
-editing of the repository and manuscript. JMB edited the manuscript and
-contributed data to the repository. CS and FT provided significant
-intellectual contribution and text editing of the repository and
-manuscript and oversaw the site development.
-
-\subsection{Funding}\label{funding}
-
-This work was supported by funding from the National Institutes of
-Health (NIAID R01 AI141549-02, to FGT, CS; NIGMS R01 GM127631 to C.S.,
-and NIGMS R01 GM151682 to JMB).
-
-\subsection{Conflicts of Interest}\label{conflicts-of-interest}
-
-The authors have no conflicts of interest to declare.
-
-\subsection{Citations}\label{citations}
-
-\phantomsection\label{refs}
-\begin{CSLReferences}{0}{0}
-\bibitem[\citeproctext]{ref-barischMembraneDamageRepair2023}
-\CSLLeftMargin{1. }%
-\CSLRightInline{Barisch, C., Holthuis, J. C. M. \& Cosentino, K.
-\href{https://doi.org/10.1515/hsz-2022-0321}{Membrane damage and repair:
-A thin line between life and death}. \emph{Biological Chemistry}
-\textbf{404}, 467--490 (2023).}
-
-\bibitem[\citeproctext]{ref-vanmeerMembraneLipidsWhere2008a}
-\CSLLeftMargin{2. }%
-\CSLRightInline{van Meer, G., Voelker, D. R. \& Feigenson, G. W.
-\href{https://doi.org/10.1038/nrm2330}{Membrane lipids: Where they are
-and how they behave}. \emph{Nature Reviews Molecular Cell Biology}
-\textbf{9}, 112--124 (2008).}
-
-\bibitem[\citeproctext]{ref-holthuisLipidLandscapesPipelines2014a}
-\CSLLeftMargin{3. }%
-\CSLRightInline{Holthuis, J. C. M. \& Menon, A. K.
-\href{https://doi.org/10.1038/nature13474}{Lipid landscapes and
-pipelines in membrane homeostasis}. \emph{Nature} \textbf{510}, 48--57
-(2014).}
-
-\bibitem[\citeproctext]{ref-niphakisGlobalMapLipidBinding2015a}
-\CSLLeftMargin{4. }%
-\CSLRightInline{Niphakis, M. J. \emph{et al.}
-\href{https://doi.org/10.1016/j.cell.2015.05.045}{A {Global Map} of
-{Lipid-Binding Proteins} and {Their Ligandability} in {Cells}}.
-\emph{Cell} \textbf{161}, 1668--1680 (2015).}
-
-\bibitem[\citeproctext]{ref-chernomordikProteinLipidInterplayFusion2003}
-\CSLLeftMargin{5. }%
-\CSLRightInline{Chernomordik, L. V. \& Kozlov, M. M.
-\href{https://doi.org/10.1146/annurev.biochem.72.121801.161504}{Protein-{Lipid
-Interplay} in {Fusion} and {Fission} of {Biological Membranes}}.
-\emph{Annual Review of Biochemistry} \textbf{72}, 175--207 (2003).}
-
-\bibitem[\citeproctext]{ref-simonsLipidRaftsSignal2000a}
-\CSLLeftMargin{6. }%
-\CSLRightInline{Simons, K. \& Toomre, D.
-\href{https://doi.org/10.1038/35036052}{Lipid rafts and signal
-transduction}. \emph{Nature Reviews Molecular Cell Biology} \textbf{1},
-31--39 (2000).}
-
-\bibitem[\citeproctext]{ref-schultzChemicalToolsLipid2023}
-\CSLLeftMargin{7. }%
-\CSLRightInline{Schultz, C.
-\href{https://doi.org/10.1021/acs.accounts.2c00851}{Chemical {Tools} for
-{Lipid Cell Biology}}. \emph{Accounts of Chemical Research} \textbf{56},
-1168--1177 (2023).}
-
-\bibitem[\citeproctext]{ref-schultzFlashClickMultifunctionalized2022a}
-\CSLLeftMargin{8. }%
-\CSLRightInline{Schultz, C., Farley, S. E. \& Tafesse, F. G.
-\href{https://doi.org/10.1021/jacs.2c02705}{{`{Flash} \& {Click}'}:
-{Multifunctionalized Lipid Derivatives} as {Tools To Study Viral
-Infections}}. \emph{Journal of the American Chemical Society}
-\textbf{144}, 13987--13995 (2022).}
-
-\bibitem[\citeproctext]{ref-hoglingerTrifunctionalLipidProbes2017}
-\CSLLeftMargin{9. }%
-\CSLRightInline{Höglinger, D. \emph{et al.}
-\href{https://doi.org/10.1073/pnas.1611096114}{Trifunctional lipid
-probes for comprehensive studies of single lipid species in living
-cells}. \emph{Proceedings of the National Academy of Sciences}
-\textbf{114}, 1566--1571 (2017).}
-
-\bibitem[\citeproctext]{ref-haberkantFatFabulousBifunctional2014}
-\CSLLeftMargin{10. }%
-\CSLRightInline{Haberkant, P. \& Holthuis, J. C. M.
-\href{https://doi.org/10.1016/j.bbalip.2014.01.003}{Fat \& fabulous:
-{Bifunctional} lipids in the spotlight}. \emph{Biochimica et Biophysica
-Acta - Molecular and Cell Biology of Lipids} \textbf{1841}, 1022--1030
-(2014).}
-
-\bibitem[\citeproctext]{ref-farleyTrifunctionalSphinganineNew2024a}
-\CSLLeftMargin{11. }%
-\CSLRightInline{Farley, S., Stein, F., Haberkant, P., Tafesse, F. G. \&
-Schultz, C.
-\href{https://doi.org/10.1021/acschembio.3c00554}{Trifunctional
-{Sphinganine}: {A New Tool} to {Dissect Sphingolipid Function}}.
-\emph{ACS Chemical Biology} \textbf{19}, 336--347 (2024).}
-
-\bibitem[\citeproctext]{ref-farleyTrifunctionalFattyAcid2024}
-\CSLLeftMargin{12. }%
-\CSLRightInline{Farley, S. E. \emph{et al.}
-\href{https://doi.org/10.1039/D4CC00974F}{Trifunctional fatty acid
-derivatives: The impact of diazirine placement}. \emph{Chemical
-Communications} \textbf{60}, 6651--6654 (2024).}
-
-\bibitem[\citeproctext]{ref-thomasTrifunctionalLipidDerivatives2025}
-\CSLLeftMargin{13. }%
-\CSLRightInline{Thomas, A. \emph{et al.} Trifunctional lipid
-derivatives: {PE}'s mitochondrial interactome. \emph{Chemical
-Communications} 10.1039.D4CC03599B (2025)
-doi:\href{https://doi.org/10.1039/D4CC03599B}{10.1039/D4CC03599B}.}
-
-\bibitem[\citeproctext]{ref-chiuPhotoaffinityLabelingReveals2025}
-\CSLLeftMargin{14. }%
-\CSLRightInline{Chiu, D.-C., Lin, H. \& Baskin, J. M. Photoaffinity
-{Labeling Reveals} a {Role} for the {Unusual Triply Acylated
-Phospholipid N-Acylphosphatidylethanolamine} in {Lactate Homeostasis}.
-(2025)
-doi:\href{https://doi.org/10.26434/chemrxiv-2025-j8nqz}{10.26434/chemrxiv-2025-j8nqz}.}
-
-\bibitem[\citeproctext]{ref-yuChemoproteomicsApproachProfile2022}
-\CSLLeftMargin{15. }%
-\CSLRightInline{Yu, W., Lin, Z., Woo, C. M. \& Baskin, J. M.
-\href{https://doi.org/10.1021/acschembio.1c00584}{A {Chemoproteomics
-Approach} to {Profile Phospholipase D-Derived Phosphatidyl Alcohol
-Interactions}}. \emph{ACS Chemical Biology} \textbf{17}, 3276--3283
-(2022).}
-
-\bibitem[\citeproctext]{ref-mullerSynthesisCellularLabeling2021}
-\CSLLeftMargin{16. }%
-\CSLRightInline{Muller, R., Kojic, A., Citir, M. \& Schultz, C.
-\href{https://doi.org/10.1002/anie.202103599}{Synthesis and {Cellular
-Labeling} of {Multifunctional Phosphatidylinositol Bis}- and
-{Trisphosphate Derivatives}}. \emph{Angewandte Chemie International
-Edition} \textbf{60}, 19759--19765 (2021).}
-
-\bibitem[\citeproctext]{ref-plotly}
-\CSLLeftMargin{17. }%
-\CSLRightInline{Inc., P. T. Collaborative data science. (2015).}
-
-\bibitem[\citeproctext]{ref-ramnathvaidyanathanHtmlwidgetsHTMLWidgets2015}
-\CSLLeftMargin{18. }%
-\CSLRightInline{Ramnath Vaidyanathan \emph{et al.} Htmlwidgets: {HTML
-Widgets} for {R}. (2015).}
-
-\bibitem[\citeproctext]{ref-thompsonTandemMassTags2003}
-\CSLLeftMargin{19. }%
-\CSLRightInline{Thompson, A. \emph{et al.}
-\href{https://doi.org/10.1021/ac0262560}{Tandem {Mass Tags}: {A Novel
-Quantification Strategy} for {Comparative Analysis} of {Complex Protein
-Mixtures} by {MS}/{MS}}. \emph{Analytical Chemistry} \textbf{75},
-1895--1904 (2003).}
-
-\bibitem[\citeproctext]{ref-birhanuMassSpectrometrybasedProteomics2023}
-\CSLLeftMargin{20. }%
-\CSLRightInline{Birhanu, A. G.
-\href{https://doi.org/10.1186/s12014-023-09424-x}{Mass
-spectrometry-based proteomics as an emerging tool in clinical
-laboratories}. \emph{Clinical Proteomics} \textbf{20}, (2023).}
-
-\bibitem[\citeproctext]{ref-boysClinicalApplicationsMass2023}
-\CSLLeftMargin{21. }%
-\CSLRightInline{Boys, E. L., Liu, J., Robinson, P. J. \& Reddel, R. R.
-\href{https://doi.org/10.1002/pmic.202200238}{Clinical applications of
-mass spectrometry-based proteomics in cancer: {Where} are we?}
-\emph{PROTEOMICS} \textbf{23}, 2200238 (2023).}
-
-\end{CSLReferences}
+Use the download button below to download the original data file prior
+to wrangling:
 

### 2025-09-04 Resources/scripts.js

@@ -1,68 +1,0 @@
-document.addEventListener("DOMContentLoaded", function () {
-  // Find both patterns
-  const roots = document.querySelectorAll(
-    '.callout-cell.collapsible, .cells[collapse="true"], .cells[data-collapse="true"], .cells.collapsible'
-  );
-
-  roots.forEach(root => {
-    if (root.dataset.collapsibleInit === "1") return; // avoid double init
-    root.dataset.collapsibleInit = "1";
-
-    // 1) Find or create a header (prefer a direct child heading)
-    let header =
-      root.querySelector(':scope > .callout-header, :scope > .cells-header, :scope > h1, :scope > h2, :scope > h3, :scope > h4, :scope > h5, :scope > h6');
-
-    if (!header) {
-      // fallback: use first element as header if available
-      header = root.firstElementChild;
-      if (!header) return; // nothing to do
-    }
-
-    // Normalize header class based on container type
-    const isCells = root.classList.contains('cells');
-    header.classList.add(isCells ? 'cells-header' : 'callout-header');
-
-    // 2) Find or build the content wrapper
-    let content = root.querySelector(':scope > .callout-content, :scope > .cells-container');
-    if (!content) {
-      content = document.createElement('div');
-      content.className = isCells ? 'cells-container' : 'callout-content';
-      // Move all siblings after header into content
-      let sib = header.nextSibling;
-      while (sib) {
-        const next = sib.nextSibling;
-        content.appendChild(sib);
-        sib = next;
-      }
-      root.appendChild(content);
-    }
-
-    // 3) A11y + initial state
-    header.setAttribute('role', 'button');
-    header.setAttribute('tabindex', '0');
-
-    const startsOpen =
-      root.classList.contains('open') ||
-      root.getAttribute('open') === 'true' ||
-      root.getAttribute('data-open') === 'true';
-
-    const setOpen = (open) => {
-      content.style.display = open ? '' : 'none';
-      root.classList.toggle('open', open);
-      header.setAttribute('aria-expanded', String(open));
-    };
-
-    setOpen(!!startsOpen);
-
-    // 4) Toggle handlers (click + keyboard)
-    const toggle = () => setOpen(content.style.display === 'none');
-
-    header.addEventListener('click', toggle);
-    header.addEventListener('keydown', (e) => {
-      if (e.key === 'Enter' || e.key === ' ') {
-        e.preventDefault();
-        toggle();
-      }
-    });
-  });
-});

### 2025-09-04 LipidProbe/8-3_FattyAcid.qmd
Spent a long time learning about custom divs, applied a new one for cell types
ok one last change, made the sph, 8-3 FA  and dag pages show a line about developing the PSM data visualization, and added collapsible panels

@@
 
-::::{.callout-tip}
+::::{.callout-warning collapse="false"}
 ### Cell background: Huh7
@@
 
-::::{.callout-tip}
+::::{.callout-warning collapse="false"}
 ### Cell background: HeLa
@@
 
+**\*PSM data presentation still in development.**
+
+See [Höglinger et al. 2017](https://lipidinteractome.org/individualstudies/dh_2017) for results in context with Diacylglycerol and 8-3 Fatty Acid data.
+
 ::::

### 2025-09-04 LipidProbe/Diacylglycerol.qmd
updating with includes structure
Spent all day learning how to make my heatmap look less bad
trying to distinguish cell types more effectively on individual probe pages
adding credit to Berit for the structures
polishing dag page a little
example
Spent a long time learning about custom divs, applied a new one for cell types
ok one last change, made the sph, 8-3 FA  and dag pages show a line about developing the PSM data visualization, and added collapsible panels

--- 2025-01-14 LipidProbe/Diacylglycerol.qmd
@@
 title: "Trifunctional Diacylglycerol"
+format: 
+  html:
+    embed-resources: false
 ---
@@
 
-## Subcellular localization
+:::{.border}
+![(A) Trifunctional Diacylglycerol. Preliminary structure collected from Höglinger et al. 2017](/LipidProbe/Structures/TF_DAG.png)
+:::
 
 ## Protein interactome
+
+::::{.callout-tip}
+
+### Cell background: HeLa
+
+::: {.callout-note collapse="true"}
+
+{{< include /StudyInformation_includes/DH_2017_include.qmd >}}
+
+:::
+
+**\*PSM data presentation still in development.**
+
+See [Höglinger et al. 2017](https://lipidinteractome.org/individualstudies/dh_2017) for results in context with Diacylglycerol and 8-3 Fatty Acid data.
+
+::::

### 2025-09-04 HourlyTracking/202508_GG-Hours.qmd
updated hours page, saved copy of letter to editor

@@
 ---
-title: August 2025 Lipid Interactome Monthly Invoice
+title: Lipid Interactome Monthly Invoice
+subtitle: August 2025
 author: "Gaelen Guzman"
@@
 Please find below the hours I logged for the month of August 2025, with descriptions of each day's activity.
-In total, I performed 4 hours of work at an hourly rate of $50 (USD), for a total bill of $200.
+In total, I performed 5 hours of work at an hourly rate of $50 (USD), for a total bill of $250.
 

### 2025-09-04 ShinyApps/CompareLipidProbes/app.R

@@ -43,13 +43,13 @@ ui <- fluidPage(
     sidebarPanel(
       selectInput(
         "probe1",
-        "Select First LipidProbe:",
+        "Select First Lipid Probe:",
         choices = probeOptions,
         selected = probeOptions[1]
       ),
       selectInput(
         "probe2",
-        "Select Second LipidProbe:",
+        "Select Second Lipid Probe:",
         choices = probeOptions,
         selected = probeOptions[2]
       )

### 2025-09-10 BioinformaticsApplicationNote/GG_2025_applicationNote.qmd
Updated DCC_2025 include with official publication link

@@
 ---
-title: "The Lipid Interactome"
-subtitle: "An interactive and open access platform for exploring cellular lipid-protein interactomes"
+title: "The Lipid Interactome:"
+subtitle: "An interactive and open access platform for exploring cellular lipid-protein interactions"
 date: 2025-02-04
@@
 
-Gaelen Guzman^1,^*, André Nadler^2^, Frank Stein^3^, Jeremy M. Baskin^4^, Carsten Schulz^1^, Fikadu G. Tafesse^1^
+Gaelen Guzman^1,^*, André Nadler^3^, Frank Stein^4^, Jeremy M. Baskin^5^, Carsten Schulz^2^, Fikadu G. Tafesse^1,2^
 
-^1^ = Departments of Molecular Immunology and Immunology and  Chemical Physiology and Biochemistry, Oregon Health & Science University, Portland, OR, USA; ^2^ = Max Plank Institute of Molecular Cell Biology and Genetics, Dresden Germany; ^3^ = Proteomics Core Facility, European Molecular Biology Laboratory, Heidelberg, Germany; ^4^ = Department of Chemistry and Chemical Biology and Weill Institute for Cell and Molecular Biology, Cornell University, Ithaca, NY, USA; * = Corresponding author: <gaelen.guzman@lipidinteractome.org>
+^1^Department of Molecular Immunology & Immunology, Oregon Health & Science University, Portland, OR, USA; ^2^Chemical Physiology and Biochemistry, Oregon Health & Science University, Portland, OR, USA; ^3^Max Plank Institute of Molecular Cell Biology and Genetics, Dresden Germany; ^4^Proteomics Core Facility, European Molecular Biology Laboratory, Heidelberg, Germany; ^5^Department of Chemistry and Chemical Biology and Weill Institute for Cell and Molecular Biology, Cornell University, Ithaca, NY, USA; *Corresponding author: <gaelen.guzman@lipidinteractome.org>
 :::

### 2025-09-10 IndividualStudies/DCC_2025.qmd
Updated DCC_2025 include with official publication link

@@
 subtitle: "Photoaffinity Labeling Reveals a Role for the Unusual Triply Acylated Phospholipid N-Acylphosphatidylethanolamine in Lactate Homeostasis"
-date: 2025-03-06
+date: 2025-09-05
 format: 

### 2025-09-10 StudyInformation_includes/DCC_2025_include.qmd
Updated DCC_2025 include with official publication link

@@
 #### Journal
-ChemR&Chi;iv
+Journal of the American Chemical Society
 
-<https://doi.org/10.26434/chemrxiv-2025-j8nqz>{target="_blank"}
+<https://doi.org/10.1021/jacs.5c03851>{target="_blank"}
 
@@
 Most eukaryotic membranes comprise phospholipids bearing two hydrophobic tails, but N-acylphosphatidylethanolamine (NAPE) stands out as a long-known but poorly understood phospholipid with three hydrophobic groups.
-What little attention that NAPE has received has been devoted to understanding its metabolic functions as a precursor to N-acylethanolamines, bioactive lipids that act as endocannabinoids.
+What little attention NAPE has received has been devoted to understanding its metabolic functions as a precursor to N-acylethanolamine (NAE), a bioactive lipid that acts as an endocannabinoid.
 Yet, levels of NAPE increase during myocardial infarction and ischemia, suggesting potential signaling roles for this lipid.

### 2025-10-31 BioinformaticsApplicationNote/ResubmissionReviewerResponse.qmd
Updating with reviewer changes and some reorganization

---
format: 
  docx:
    reference-doc: custom-reference-doc.docx
---

Hello Dr. Ceci and Dr. Robinson,

We are quite excited that our manuscript is acceptable for publication and are happy to incorporate further clarifications about our data handling and the steps taken to align each dataset within the framework of the site. We are again grateful to the reviewers for taking the time to thoughtfully consider our manuscripts and the changes we incorporated in this newest version of our manuscript and our site.

We see two fundamental suggestions between the reviewers: (1) clarification of the data handling and alignment and (2) establishment of a more robust/scalable data management model.

To the first point, we have added further clarifying text to the manuscript seeking to emphasize that the data incorporated on the site is acquired through direct communication with authors -- where possible -- and from publicly available datasets published with the original studies. Further, we have added a short note on the raw data download section of the *Study Information* dropdown tab on each page to describe the source of the associated dataset (either provided by the authors or pulled from the published dataset).

We have also sought to clarify the data handling by adding a similar summary note to the s*Study Information* dropdown tab of each page describing the data wrangling performed. For most datasets, this is merely the re-naming of data columns and the inclusion of a statistical significance column which allows for color-coding in the automated plotting functions -- where "significance" is as defined in each original publication. As such, we further emphasize that direct comparison between studies is still not intended to be a quantitative method, but to give lipid researchers a sense of the similarities and differences in the sets of enriched hits between different lipid probes. A section has been added to our [Data Analysis and Statistics](https://lipidinteractome.org/background/dataanalysisandstatistics) background page describing the limitations of the comparison tool -- and this section is linked on the comparison page.

To the reviewers' second point regarding a scalable and AI-compatible data model, we wholeheartedly agree that our site's impact would be greatly increased with a more robust underlying data model. Notably, however, this first implementation of our site incorporates most, if not all, currently published lipid interactome datasets -- this is a developing field, and while interest is expanding (in part due to this effort), the scalability of the site is currently manageable via manual addition of new datasets.

We seek to emphasize that the suggested features would require root-level changes that are currently beyond our reach in both funding and skillset. We firmly aim to reconstruct the site with greater data management and a more scalable structure in its next iteration. At present, we believe that the key features of the site are of great benefit to lipid researchers: there is no comparable resource that so improves the findability and accessibility of these datasets, nor any other effort to make these datasets interoperable (as incomplete as ours is), and the downloadability of these datasets dramatically increases the reusability of these datasets.

We hope that the clarifying changes to our manuscript and the above-noted sections of our site are sufficient to address the reviewers' concerns. We thank them again for their time and consideration, and we thank the editors at Bioinformatics for this opportunity to publish our Application Note.

Best,

Dr. Fikadu Tafesse

---

**Summary of revisions**

* Clarifying text has been added to the manuscript to describe the source of datasets and the handling of data.

* Descriptive text has been added to each *Study Information* section of the site in order to clarify the source of the dataset (i.e. provided by the authors or as published/publicly available) and the steps taken to wrangle the dataset into alignment with the visualization functions on the site.

* A new section of the [Data Analysis and Statistics](https://lipidinteractome.org/background/dataanalysisandstatistics) background page clarifying the broad steps taken to align each dataset for inclusion in the site (e.g. column name alignment, the creation of a statistical annotation column, etc). This section is linked to from the dataset comparison tool to direct users who seek more information.

### 2025-10-31 Background/DataAnalysisAndStatistics.qmd
Updating with reviewer changes and some reorganization

@@
 
-<!-- 
-## PSM quantitative mass spec analysis
+## Aligning datasets for presentation on this site {#sec-DataAlignment}
 
-* Studies included in this repository which used a PSM-based analysis pipeline
-	- Hoglinger et al., 2017[@hoglingerTrifunctionalLipidProbes2017]
-	- Muller et al., 2021[@mullerSynthesisCellularLabeling2021]
+As described above, many methods are used to produce interactome proteomics data, and aligning these methods for interoperability ad comparison is a significant hurdle.
 
-* Need these details. -->
+For numerous reasons, it is fundamentally unreasonable to quantitatively compare the results of disparate proteomics datasets -- for example, even subtle changes in instrument settings can preclude comparison of datasets collected on the same mass spectrometer and sample handling differences between individuals performing the same techniques can produce differences between very-similar datasets.
+
+With this in mind, the Lipid Interactome seeks to align disparate datasets as much as possible and enable qualitative, visual comparisons between datasets.
+Each dataset is curated from its original source (either directly from the authors, or gathered from publicly available supplemental data) and wrangled to fit a standardized format, with common column headers and annotations of statistical significance.
+
+The datasets incorporated into the [Probe vs Probe Comparison](https://lipidinteractome.org/lipidprobe/enrichedhitscomparison) tool each consist of normalized ratiometric data of fundamentally similar form, with qualitatively comparable statistical annotations.
 
@@
 
+* In cases where ratiometric data is not available, heat maps have been employed to display relative enrichment between conditions. 
+  * For example, [Höglinger et al.
+2017](https://lipidinteractome.org/individualstudies/dh_2017) reports only peptide spectral mapping counts.
+In this case, we have excluded the data from the [Probe vs Probe Comparison](https://lipidinteractome.org/lipidprobe/enrichedhitscomparison) tool, as it is incompatible with this visualization technique.
+
 ### Gene Ontology Overview {#sec-DataAnalysis_GeneOntology}
 
+* **This tool is in development and is only available for some datasets.**
 * Gene Ontology (GO) analyses take a list of proteins and determines whether there is a greater than random enrichment of a biological feature.
@@
 * Enriched pathways are given statistical significance by assessing the likelihood that a pathway would be overrepresented through random chance.
+
+### Probe vs Probe Comparison tool {#sec-ProbevsProbeComparisonBackground}
+
+* This embedded Shiny app allows the user to select two datasets to visually compare along the axes of a scatter plot.
+* **Crucially, this tool is not intended for quantitative comparisons, as described in greater detail above in [@sec-DataAlignment].**
+* The statistical annotations of each dataset are compared and distinguished along the axes and denoted by color: 
+  * Black proteins are unenriched in respect to both probes.
+  * Purple proteins are “enriched” with respect to only the probe on the x-axis.
+  * Green proteins are “enriched” with respect to only the probe on the y-axis.
+  * Orange proteins are “enriched” in both probes.

### 2025-10-31 BioinformaticsApplicationNote/GG_2025_applicationNote.qmd
Updating with reviewer changes and some reorganization

@@
 
-Where study design permits, data has been integrated into an interactive Shiny application, allowing users to perform direct (though qualitative) probe-to-probe comparisons ([Probe vs Probe Comparisons](https://www.lipidinteractome.org/lipidprobe/enrichedhitscomparison)).
+Where study design permits, data has been integrated into an interactive Shiny application, allowing users to perform direct (though qualitative) probe-to-probe comparisons ([Probe vs Probe Comparisons](https://www.lipidinteractome.org/probevsprobecomparison/enrichedhitscomparison)).
 This tool enables researchers to explore the similarity of lipid interactomes across experimental conditions via linear regression analysis, highlighting proteins that are significantly enriched in one dataset, both datasets, or neither.
@@
 **We wish to emphasize that we will collaborate with data providers to prepare visualizations which best suit their datasets -- the example dataset above merely depicts an ideal case which allows for easy incorporation and cross-study comparison.
-As proteomics techniques have improved rapidly in recent years, we have done our best to incorporate all data structures into this repository**
+As proteomics techniques have improved rapidly in recent years, we have done our best to incorporate all data structures into this repository.**
 
@@
 At present, we are accepting datasets as analyzed by the original researchers, including protein identifications, enrichment quantification, and the results of statistical testing.
-We are working to incorporate comprehensive details of the analysis workflow in each study.
+Summaries of both source and data wrangling can be found in the *Study Information* dropdown section of each data page.
+Further, the raw data (as provided directly by authors or pulled from publicly-available datasts) and data wrangling scripts are available for download in the same dropdown tabs.
 

### 2025-10-31 ContactUs/about.qmd
Updating with reviewer changes and some reorganization

@@
 This site can be pulled from GitHub at: <https://github.com/gaelenDG/LipidInteractomics_Website>
-
-### Site structure
-
-::::{.callout-note collapse="true"}
-
-<!-- Run this to get a tree of the file structure, need to do some research on how this is depicted or if this is necessary -->
-```{r setup, include=FALSE, echo=FALSE}
-library(fs)
-
-tree <- fs::dir_tree(path = ".", recurse = TRUE, depth = 3) |>
-  stringr::str_subset("(^\\.|_site/|\\.git|\\.Rproj|\\.quarto|\\.cache)", negate = TRUE)
-
-```
-
-_site                                                
-	├── 404.html                                         
-	├── Background                                       
-	│   ├── BackgroundFigures                            
-	│   │   └── BaselineProteomics_ExperimentalDesign.png
-	│   ├── BaselineProteomics_ExperimentalDesign.png    
-	│   ├── DataAnalysisAndStatistics.html               
-	│   ├── MultifunctionalLipidProbesOverview.html      
-	│   └── ProteomicsUsingMultifunctionalProbes.html                
-	├── ContactUs                                        
-	│   ├── DataSubmission.html                          
-	│   └── about.html                                   
-	├── IndividualStudies                                
-	│   ├── AT_2025.html                                 
-	│   ├── DH_2017.html                                 
-	│   ├── RM_2021.html                                 
-	│   ├── SF_2024.html                                 
-	│   ├── SF_2024_B.html                               
-	│   └── StudyOverview.html                           
-	├── LipidProbe                                       
-	│   ├── 1-10_FattyAcid.html                          
-	│   ├── 8-3_FattyAcid.html                           
-	│   ├── Diacylglycerol.html                          
-	│   ├── EnrichedHitsComparison.html                  
-	│   ├── FormattingTemplate.html                      
-	│   ├── PhosphatidicAcid.html                        
-	│   ├── Phosphatidylethanolamine.html                
-	│   ├── PhosphatidylinositolBisphosphate.html        
-	│   ├── PhosphatidylinositolTrisphosphate.html       
-	│   ├── Sphinganine.html                             
-	│   ├── Sphingosine.html                             
-	│   └── Structures                                   
-	│       ├── 1-10_FattyAcid_Structure.png             
-	│       ├── 8-3_FattyAcid_Structure.png              
-	│       ├── PIP3_Structure.png                       
-	│       ├── PhosphatidicAcid_Structure.png           
-	│       ├── PhosphatidylethanolamineStructure.png    
-	│       ├── SphinganineStructure.png                 
-	│       └── SphingosineStructure.png                 
-	├── MaintenanceInstructions.html                     
-	├── Resources                                        
-	│   └── styles.css                                   
-	├── index.html
-
-::::

### 2025-10-31 ContactUs/about.tex
Updating with reviewer changes and some reorganization

@@
 
-\begin{tcolorbox}[enhanced jigsaw, bottomrule=.15mm, opacitybacktitle=0.6, opacityback=0, coltitle=black, colframe=quarto-callout-note-color-frame, breakable, title=\textcolor{quarto-callout-note-color}{\faInfo}\hspace{0.5em}{Note}, colbacktitle=quarto-callout-note-color!10!white, colback=white, leftrule=.75mm, titlerule=0mm, bottomtitle=1mm, toptitle=1mm, arc=.35mm, rightrule=.15mm, left=2mm, toprule=.15mm]
+\begin{tcolorbox}[enhanced jigsaw, coltitle=black, colbacktitle=quarto-callout-note-color!10!white, leftrule=.75mm, colback=white, opacitybacktitle=0.6, breakable, colframe=quarto-callout-note-color-frame, rightrule=.15mm, arc=.35mm, title=\textcolor{quarto-callout-note-color}{\faInfo}\hspace{0.5em}{Note}, toptitle=1mm, opacityback=0, bottomtitle=1mm, titlerule=0mm, bottomrule=.15mm, toprule=.15mm, left=2mm]
 

### 2025-10-31 HourlyTracking/202508_GG-Hours.qmd
Updating with reviewer changes and some reorganization

@@
 title: Lipid Interactome Monthly Invoice
-subtitle: August 2025
+subtitle: Invoice Number 20250801
 author: "Gaelen Guzman"
@@
   - "\\fancyhead[R]{2025 09 04}"
+  - "\\fancyhead[R]{Invoice Number 20250801}"
   - "\\fancyfoot{}"

### 2025-10-31 IndividualStudies/DataTables/DataWrangling/DCC_2025_wrangling.R

@@ -21,16 +21,22 @@ data <- readr::read_csv(here("LipidInteractomics_Website/IndividualStudies/DataT
   glimpse() |>
   group_by(gene_name) |>
   filter(ratio_MvsL != "") |>
-  summarise(gene_ID = dplyr::first(gene_ID),
-            logFC = mean(log2(ratio_MvsL)),
-            pvalue = mean(pvalue),
-            numReplicates = n(),
-            AveExpr = log10(mean(L_abundance) + mean(M_abundance))/2) |>
+  summarise(
+    gene_ID = dplyr::first(gene_ID),
+    logFC = mean(log2(ratio_MvsL)),
+    pvalue = mean(pvalue),
+    numReplicates = n(),
+    AveExpr = log10(mean(L_abundance) + mean(M_abundance)) / 2
+  ) |>
   arrange(-logFC) |>
-  mutate(LipidProbe = "BF-NAPE",
-         hit_annotation = case_when(.default = "no hit",
-                                    logFC >= 0.5849625 & pvalue <= 0.05 & numReplicates == 2 ~ "enriched candidate",
-                                    logFC >= 0.5849625 & pvalue <= 0.05 & numReplicates == 3 ~ "enriched hit")) |>
+  mutate(
+    LipidProbe = "BF-NAPE",
+    hit_annotation = case_when(
+      .default = "no hit",
+      logFC >= 0.5849625 & pvalue <= 0.05 & numReplicates == 2 ~ "enriched candidate",
+      logFC >= 0.5849625 & pvalue <= 0.05 & numReplicates == 3 ~ "enriched hit"
+    )
+  ) |>
   glimpse()
 
 
@@ -54,5 +60,4 @@ CombinedProbeData <- read_csv(here("ShinyApps/LipidInteractomics_ShinyApp/combin
   glimpse() |>
   rbind(data)
 
-write_csv(CombinedProbeData, here("ShinyApps/LipidInteractomics_ShinyApp/combinedProbeDatasets_TMT.csv"))  
-
+write_csv(CombinedProbeData, here("ShinyApps/LipidInteractomics_ShinyApp/combinedProbeDatasets_TMT.csv"))

### 2025-10-31 Resources/ggplot_styles.R

@@ -29,30 +29,35 @@ safe_abs <- function(x, default = NA) {
   #' Performs some error handling in the event of NA in joined datasets -- intended to be used while finding the limits of ggplots, as in VolcanoPlotStandardized.
   #' Takes an input, tries to coerce it into a numeric, performs the abs() operation on it
   #' Returns an input default value so the user can use trial and error.
- 
-  tryCatch({
-    # Ensures that x is numeric before taking abs()
-    abs(as.numeric(x))
-  }, error = function(e) {
-    default
-  })
+
+  tryCatch(
+    {
+      # Ensures that x is numeric before taking abs()
+      abs(as.numeric(x))
+    },
+    error = function(e) {
+      default
+    }
+  )
 }
 
 safe_log10 <- function(x, default = NA) {
   #' Takes an input, tries to coerce it into a numeric, performs the  log10() operation on it
   #' Performs some error handling in the event of NA in joined datasets -- intended to be used while finding the limits of ggplots, as in VolcanoPlotStandardized.
   #' Returns an input default value so the user can use trial and error.
-  
-     tryCatch({
-        # Ensures that x is numeric before taking log10()
-        log10(as.numeric(x))
-    }, error = function(e) {
-        default
-    })
+
+  tryCatch(
+    {
+      # Ensures that x is numeric before taking log10()
+      log10(as.numeric(x))
+    },
+    error = function(e) {
+      default
+    }
+  )
 }
 
-calculateFE <- function(GeneRatio, BgRatio)
-{
+calculateFE <- function(GeneRatio, BgRatio) {
   GeneRatio <- as.numeric(unlist(str_split(GeneRatio, pattern = "/")))
   BgRatio <- as.numeric(unlist(str_split(BgRatio, pattern = "/")))
   odds_ratio <- (GeneRatio[1] / GeneRatio[2]) / (BgRatio[1] / BgRatio[2])
@@ -60,8 +65,8 @@ calculateFE <- function(GeneRatio, BgRatio)
 }
 
 customPlot <- list(
-  theme_bw(base_size = 12), 
-  scale_fill_brewer(palette = "Set1"), 
+  theme_bw(base_size = 12),
+  scale_fill_brewer(palette = "Set1"),
   scale_colour_brewer(palette = "Set1")
 )
 
@@ -69,545 +74,615 @@ customPlot <- list(
 ################ Plotting Functions ################
 
 MAStandard <- function(data) {
+  ################
[…]

### 2025-10-31 ShinyApps/CompareLipidProbes/AddNewStudies.R

@@ -1,6 +1,3 @@
-
-
-
 smallDataset <- bigDataSet |>
   mutate(studyPointer = paste(LipidProbe, CellLine, sep = " - "))
 

### 2025-10-31 ShinyApps/CompareLipidProbes/app.R

@@ -38,7 +38,6 @@ probeOptions <- unique(df$probeOptions)
 # UI
 ui <- fluidPage(
   titlePanel("Interactive LogFC Comparison"),
-
   sidebarLayout(
     sidebarPanel(
       selectInput(
@@ -210,7 +209,6 @@ server <- function(input, output, session) {
           hit_annotation.x == "enriched hit" &
             hit_annotation.y == "enriched hit" ~
             "enriched on x- and y- axes",
-
           hit_annotation.x == "enriched hit" &
             hit_annotation.y == "enriched hit" &
             hit_annotation.z != "enriched hit" ~

### 2025-10-31 Background/DataAnalysisAndStatistics.qmd
Fixed broken links and section references caused by reorg

@@
 
-The datasets incorporated into the [Probe vs Probe Comparison](https://lipidinteractome.org/lipidprobe/enrichedhitscomparison) tool each consist of normalized ratiometric data of fundamentally similar form, with qualitatively comparable statistical annotations.
+The datasets incorporated into the [Probe vs Probe Comparison](https://lipidinteractome.org/probevsprobe/enrichedhitscomparison) tool each consist of normalized ratiometric data of fundamentally similar form, with qualitatively comparable statistical annotations.
 
@@
 2017](https://lipidinteractome.org/individualstudies/dh_2017) reports only peptide spectral mapping counts.
-In this case, we have excluded the data from the [Probe vs Probe Comparison](https://lipidinteractome.org/lipidprobe/enrichedhitscomparison) tool, as it is incompatible with this visualization technique.
+In this case, we have excluded the data from the [Probe vs Probe Comparison](https://lipidinteractome.org/probevsprobe/enrichedhitscomparison) tool, as it is incompatible with this visualization technique.
 

### 2025-10-31 Background/DataAnalysisAndStatistics.qmd
Fixed reference links

@@
 * This embedded Shiny app allows the user to select two datasets to visually compare along the axes of a scatter plot.
-* **Crucially, this tool is not intended for quantitative comparisons, as described in greater detail above in [@sec-DataAlignment].**
+* **Crucially, this tool is not intended for quantitative comparisons, as described in greater detail above in [Data Alignment @sec-DataAlignment].**
 * The statistical annotations of each dataset are compared and distinguished along the axes and denoted by color: 

### 2025-10-31 ProbeVsProbeComparison/EnrichedHitsComparison.qmd
Updating with reviewer changes and some reorganization
Fixed broken links and section references caused by reorg
Fixed reference links

--- 2025-07-18 LipidProbe/EnrichedHitsComparison.qmd
@@
 We have prepared the visualization tool below to enable this to be done visually.
+
+See our [Data Analysis & Statistics](https://lipidinteractome.org/background/dataanalysisandstatistics#sec-DataAlignment) background page for greater detail on the data alignment performed to enable this qualitative comparison.
 
@@
 The red dashed line denotes the line of best fit between the datasets, determined via linear regression (the red text denotes the line formula and adjusted R^2^ value).
-Note that the significance thresholds for each dataset are as defined on the respective lipid probe or studies page and are not the same between studies -- this page is intended for a simple qualitative comparison of hits between datasets.
+**Note that the significance thresholds for each dataset are as defined on the respective lipid probe or studies page and are not the same between studies -- this page is intended for a simple qualitative comparison of hits between datasets.
+See [here](https://lipidinteractome.org/background/dataanalysisandstatistics#sec-ProbevsProbeComparisonBackground) for more detail.**
 

### 2025-10-31 StudyInformation_includes/WY_2021_include.qmd
Added download links to all the original data
Added cell line info to includes

@@
 
+**Species:** *Homo sapiens*
+
+**Cell type:** Epithelial (immortalized cervical cancer line)
+
 #### Uncaging & Crosslinking timeline
@@
 {{< downloadthis /Users/gaelenguzman/LipidInteractomics_Website_local/LipidInteractomics_Website/IndividualStudies/DataTables/DataWrangling/WY_2021_wrangling.R dname="WY_2021_wrangling">}}
+
+Use the download button below to download the original data file prior to wrangling:
+
+{{< downloadthis /Users/gaelenguzman/LipidInteractomics_Website_local/LipidInteractomics_Website/IndividualStudies/DataTables/DataWrangling/WY_2021_ACSChemBio_RawData2.csv dname="WY_2021_ACS-ChemBio_OriginalData">}}

### 2025-11-28 BioinformaticsApplicationNote/GG_2025_applicationNote.tex
Pushing latest formatting edit of manuscript

--- 2025-07-30 _site/BioinformaticsApplicationNote/GG_2025_applicationNote.tex
@@
 \hypersetup{
-  pdftitle={The Lipid Interactome},
+  pdftitle={The Lipid Interactome:},
   pdfkeywords={Lipid-protein
@@
 
-\title{The Lipid Interactome}
+\title{The Lipid Interactome:}
 \usepackage{etoolbox}
@@
 \subtitle{An interactive and open access platform for exploring cellular
-lipid-protein interactomes}
+lipid-protein interactions}
 \author{Gaelen Guzman \and André Nadler \and Frank Stein \and Jeremy M.
@@
 
-Gaelen Guzman\textsuperscript{1,}*, André Nadler\textsuperscript{2},
-Frank Stein\textsuperscript{3}, Jeremy M. Baskin\textsuperscript{4},
-Carsten Schulz\textsuperscript{1}, Fikadu G. Tafesse\textsuperscript{1}
+Gaelen Guzman\textsuperscript{1,}*, André Nadler\textsuperscript{3},
+Frank Stein\textsuperscript{4}, Jeremy M. Baskin\textsuperscript{5},
+Carsten Schulz\textsuperscript{2}, Fikadu G.
+Tafesse\textsuperscript{1,2}
 
-\textsuperscript{1} = Departments of Molecular Immunology and Immunology
-and Chemical Physiology and Biochemistry, Oregon Health \& Science
-University, Portland, OR, USA; \textsuperscript{2} = Max Plank Institute
-of Molecular Cell Biology and Genetics, Dresden Germany;
-\textsuperscript{3} = Proteomics Core Facility, European Molecular
-Biology Laboratory, Heidelberg, Germany; \textsuperscript{4} =
-Department of Chemistry and Chemical Biology and Weill Institute for
-Cell and Molecular Biology, Cornell University, Ithaca, NY, USA; * =
-Corresponding author:
+\textsuperscript{1}Department of Molecular Immunology \& Immunology,
+Oregon Health \& Science University, Portland, OR, USA;
+\textsuperscript{2}Chemical Physiology and Biochemistry, Oregon Health
+\& Science University, Portland, OR, USA; \textsuperscript{3}Max Plank
+Institute of Molecular Cell Biology and Genetics, Dresden Germany;
+\textsuperscript{4}Proteomics Core Facility, European Molecular Biology
+Laboratory, Heidelberg, Germany; \textsuperscript{5}Department of
+Chemistry and Chemical Biology and Weill Institute for Cell and
+Molecular Biology, Cornell University, Ithaca, NY, USA; *Corresponding
+author:
 \href{mailto:gaelen.guzman@lipidinteractome.org}{\nolinkurl{gaelen.guzman@lipidinteractome.org}}
@@
 
-Lipid--protein interactions play essential roles in cellular signaling
+Lipid-protein interactions play essential roles in cellular signaling
 and membrane dynamics, yet their systematic characterization has long
@@
 storage and metabolism, and bioactive signaling mediators for organellar
-and intracellular signaling\textsuperscript{1--6}. Interactions with
-proteins are essential to many of these crucial lipid functions -- and
-yet, lipid--protein interactions are extremely challenging to study: The
+and intracellular signaling{[}@barischMembraneDamageRepair2023;
+@vanmeerMembraneLipidsWhere2008a;
+@holthuisLipidLandscapesPipelines2014a;
+@niphakisGlobalMapLipidBinding2015a;
+@chernomordikProteinLipidInterplayFusion2003;
+@simonsLipidRaftsSignal2000a{]}. Interactions with proteins are
+essential to many of these crucial lipid functions -- and yet,
+lipid--protein interactions are extremely challenging to study: The
 small size and biophysical properties of lipids make conventional
 proteomics approaches unsuitable for mapping lipid
-interactors\textsuperscript{7}. Unlike proteins, which can be readily
-tagged or immobilized for affinity-based interaction studies, lipids
-require specialized chemical modifications to enable selective and
-controlled interaction profiling\textsuperscript{8}.
+interactors{[}@schultzChemicalToolsLipid2023{]}. Unlike proteins, which
+can be readily tagged or immobilized for affinity-based interaction
+studies, lipids require specialized chemical modifications to enable
+selective and controlled interaction
+profiling{[}@schultzFlashClickMultifunctionalized2022a{]}.
 
@@
 revolutionized the field, enabling the systematic interrogation of lipid
-interactomes\textsuperscript{8}. These probes incorporate strategically
-designed functional groups that enable covalent crosslinking, affinity
-enrichment, and controlled activation. Most commonly, these include: (1)
-a diazirine group for photoactivatable crosslinking upon exposure to 355
-nm ultraviolet (UV) light, stabilizing non-covalent and often
-modest-affinity lipid--protein interactions; (2) a terminal alkyne,
-permitting click chemistry-based enrichment; and, in some cases, (3) a
-coumarin photocage, which shields the lipid probe from premature
-enzymatic modification until it is selectively cleaved by 405 nm light
-(a wavelength that does not induce diazirine
-photolysis)\textsuperscript{7--10}. Together, these modifications enable
-direct proteomic identification of lipid interactors, distinguishing
-true binding partners from transient or non-specific
-associations\textsuperscript{7,10,11}.
+interactomes{[}@schultzFlashClickMultifunctionalized2022a{]}. These
+probes incorporate strategically designed functional groups that enable
+covalent crosslinking, affinity enrichment, and controlled activation.
+Most commonly, these include: (1) a diazirine group for photoactivatable
+crosslinking upon exposure to 355 nm ultraviolet (UV) light, stabilizing
+non-covalent and often modest-affinity lipid--protein interactions; (2)
+a terminal alkyne, permitting click chemistry-based enrichment; and, in
+some cases, (3) a coumarin photocage, which shields the lipid probe from
+premature enzymatic modification until it is selectively cleaved by 405
+nm light (a wavelength that does not induce diazirine
+photolysis){[}@schultzFlashClickMultifunctionalized2022a;
+@schultzChemicalToolsLipid2023; @hoglingerTrifunctionalLipidProbes2017;
+@haberkantFatFabulousBifunctional2014{]}. Together, these modifications
+enable direct proteomic identification of lipid interactors,
+distinguishing true binding partners from transient or non-specific
+associations{[}@haberkantFatFabulousBifunctional2014;
+@schultzChemicalToolsLipid2023;
+@farleyTrifunctionalSphinganineNew2024a{]}.
 
@@
 phosphatidylethanolamine, N-acylphosphatidylethanolamine, and
-phosphatidyl alcohol\textsuperscript{9,11--16}. These initial studies
-have followed a comparative proteomics workflow, wherein crosslinked
+phosphatidyl alcohol{[}@hoglingerTrifunctionalLipidProbes2017;
+@farleyTrifunctionalSphinganineNew2024a;
+@farleyTrifunctionalFattyAcid2024;
+@thomasTrifunctionalLipidDerivatives2025;
+@chiuPhotoaffinityLabelingReveals2025;
+@yuChemoproteomicsApproachProfile2022;
+@mullerSynthesisCellularLabeling2021{]}. These initial studies have
+followed a comparative proteomics workflow, wherein crosslinked
 (``+UV'') and non-crosslinked (``-UV'') samples are analyzed side by
 side to minimize artifacts and confirm
-specificity\textsuperscript{7,10}. However, despite the growing number
+specificity{[}@haberkantFatFabulousBifunctional2014;
+@schultzChemicalToolsLipid2023{]}. However, despite the growing number
 of lipid interactome datasets, no centralized resource has existed to
@@
 alcohol, sphingosine, and sphinganine in HeLa and Huh7
-cells\textsuperscript{11,13--16}. Additionally, it includes control
-datasets from two fatty acid probes to distinguish specific from
-non-specific lipid-binding proteins\textsuperscript{12}. We additionally
-intend to expand this resource to include more complex experimental
-designs as they are published (e.g.~Disease versus Healthy Control or
-Infection versus Mock).
+cells{[}@thomasTrifunctionalLipidDerivatives2025;
+@mullerSynthesisCellularLabeling2021;
+@chiuPhotoaffinityLabelingReveals2025;
+@yuChemoproteomicsApproachProfile2022;
+@farleyTrifunctionalSphinganineNew2024a{]}. Additionally, it includes
+control datasets from two fatty acid probes to distinguish specific from
+non-specific lipid-binding
+proteins{[}@farleyTrifunctionalFattyAcid2024{]}. We additionally intend
+to expand this resource to include more complex experimental designs as
+they are published (e.g.~Disease versus Healthy Control or Infection
+versus Mock).
 
@@
 experience that supports zooming, hovering, image export, and data
-filtering\textsuperscript{17,18}. For transparency and reproducibility,
-all datasets associated with a given study are available for direct
-download.
+filtering{[}@plotly; @ramnathvaidyanathanHtmlwidgetsHTMLWidgets2015{]}.
+For transparency and reproducibility, all datasets associated with a
+given study are available for direct download.
 
@@
 qualitative)~probe-to-probe
-comparisons~(\href{https://www.lipidinteractome.org/lipidprobe/enrichedhitscomparison}{Probe~vs~Probe~Comparisons}).
+comparisons~(\href{https://www.lipidinteractome.org/probevsprobecomparison/enrichedhitscomparison}{Probe~vs~Probe~Comparisons}).
 This tool enables researchers to explore the similarity of lipid
@@
 data-dependent acquisition techniques, such as Tandem Mass
-Tagging\textsuperscript{19}. These datasets include those reported by
-Farley et al.~(2024), Farley et al.~(2024), and Thomas et
-al.~(2025)\textsuperscript{11--13}. Some studies have also featured
-quantitative MS analysis using stable isotope labeling of amino acids in
-cell culture (SILAC), which also enables extraction of key data
-described below\textsuperscript{14,15}. Correspondingly, the ideal data
-structure for incorporation into our repository will include the
-following:
+Tagging{[}@thompsonTandemMassTags2003{]}. These datasets include those
+reported by Farley et al.~(2024), Farley et al.~(2024), and Thomas et
+al.~(2025){[}@farleyTrifunctionalSphinganineNew2024a;
+@farleyTrifunctionalFattyAcid2024;
+@thomasTrifunctionalLipidDerivatives2025{]}. Some studies have also
+featured quantitative MS analysis using stable isotope labeling of amino
+acids in cell culture (SILAC), which also enables extraction of key data
+described below{[}@chiuPhotoaffinityLabelingReveals2025;
+@yuChemoproteomicsApproachProfile2022{]}. Correspondingly, the ideal
+data structure for incorporation into our repository will contain the
+information shown in Table~\ref{tbl-dataStructure}.
 
@@
 False-discovery rate of protein
-identification.}\label{tbl-1}\tabularnewline
+identification.}\label{tbl-dataStructure}\tabularnewline
 \toprule\noalign{}
@@
 the example dataset above merely depicts an ideal case which allows for
-easy incorporation and cross-study comparison.}
+easy incorporation and cross-study comparison. As proteomics techniques
+have improved rapidly in recent years, we have done our best to
+incorporate all data structures into this repository.}
 
@@
 (DIA) is a quickly emerging alternative to data-dependent acquisition
-(DDA; e.g.~TMT)\textsuperscript{20,21}; as with PSM datasets, we are
+(DDA; e.g.~TMT) {[}@birhanuMassSpectrometrybasedProteomics2023;
+@boysClinicalApplicationsMass2023{]}; as with PSM datasets, we are
 working to incorporate DIA data formats.
+
+At present, we are accepting datasets as analyzed by the original
+researchers, including protein identifications, enrichment
+quantification, and the results of statistical testing. Summaries of
+both source and data wrangling can be found in the \emph{Study
+Information} dropdown section of each data page. Further, the raw data
+(as provided directly by authors or pulled from publicly-available
+datasts) and data wrangling scripts are available for download in the
+same dropdown tabs.
 
@@
 will evolve alongside advances in lipid probe technologies and
-interactomics. Future iterations will incorporate validation studies for
-each lipid probe, offering researchers a dedicated space to compare
-findings across experimental contexts. This functionality will not only
-reduce redundancy in experimental design but also strengthen the
-reproducibility and biological interpretation of lipid interactome
-research. To support this vision, we invite researchers to contribute
-their datasets via our
+interactomics. Ongoing efforts seek to incorporate enhanced scalability
+of this site, more robust data storage methods, and automated data
+submission. These functionalities will improve the utility of this
+repository, enabling applications such as machine learning for pattern
+recognition as the site grows. Future iterations will incorporate
+validation studies for each lipid probe, offering researchers a
+dedicated space to compare findings across experimental contexts. This
+functionality will not only reduce redundancy in experimental design but
+also strengthen the reproducibility and biological interpretation of
+lipid interactome research.
+
+To support this vision, we invite researchers to contribute their
+datasets via our
 \href{https://lipidinteractome.org/contactus/datasubmission}{Data
-Submission page}, fostering a collaborative and transparent approach to
-lipid biology.
+Submission page}. Using the FAIR data principles, we hope to foster a
+collaborative and transparent approach to lipid biology.
 
@@
 
-GG designed, implemented, and wrote the majority of the LipidInteractome
-repository and manuscript. FS wrote the data analysis section of the
-repository, provided significant intellectual contribution to the
-repository design, and edited the manuscript. AN provided substantial
-editing of the repository and manuscript. JMB edited the manuscript and
-contributed data to the repository. CS and FT provided significant
-intellectual contribution and text editing of the repository and
-manuscript and oversaw the site development.
+GG designed, implemented, and wrote the majority of the Lipid
+Interactome repository and manuscript. FS wrote the data analysis
+section of the repository, provided significant intellectual
+contribution to the repository design, and edited the manuscript. AN
+provided substantial editing of the repository and manuscript. JMB
+edited the manuscript and contributed data to the repository. CS and FT
+provided significant intellectual contribution and text editing of the
+repository and manuscript and oversaw the site development.
 
@@
 \phantomsection\label{refs}
-\begin{CSLReferences}{0}{0}
-\bibitem[\citeproctext]{ref-barischMembraneDamageRepair2023}
-\CSLLeftMargin{1. }%
-\CSLRightInline{Barisch, C., Holthuis, J. C. M. \& Cosentino, K.
-\href{https://doi.org/10.1515/hsz-2022-0321}{Membrane damage and repair:
-A thin line between life and death}. \emph{Biological Chemistry}
-\textbf{404}, 467--490 (2023).}
-
-\bibitem[\citeproctext]{ref-vanmeerMembraneLipidsWhere2008a}
-\CSLLeftMargin{2. }%
-\CSLRightInline{van Meer, G., Voelker, D. R. \& Feigenson, G. W.
-\href{https://doi.org/10.1038/nrm2330}{Membrane lipids: Where they are
-and how they behave}. \emph{Nature Reviews Molecular Cell Biology}
-\textbf{9}, 112--124 (2008).}
-
-\bibitem[\citeproctext]{ref-holthuisLipidLandscapesPipelines2014a}
-\CSLLeftMargin{3. }%
-\CSLRightInline{Holthuis, J. C. M. \& Menon, A. K.
-\href{https://doi.org/10.1038/nature13474}{Lipid landscapes and
-pipelines in membrane homeostasis}. \emph{Nature} \textbf{510}, 48--57
-(2014).}
-
-\bibitem[\citeproctext]{ref-niphakisGlobalMapLipidBinding2015a}
-\CSLLeftMargin{4. }%
-\CSLRightInline{Niphakis, M. J. \emph{et al.}
-\href{https://doi.org/10.1016/j.cell.2015.05.045}{A {Global Map} of
-{Lipid-Binding Proteins} and {Their Ligandability} in {Cells}}.
-\emph{Cell} \textbf{161}, 1668--1680 (2015).}
-
-\bibitem[\citeproctext]{ref-chernomordikProteinLipidInterplayFusion2003}
-\CSLLeftMargin{5. }%
-\CSLRightInline{Chernomordik, L. V. \& Kozlov, M. M.
-\href{https://doi.org/10.1146/annurev.biochem.72.121801.161504}{Protein-{Lipid
-Interplay} in {Fusion} and {Fission} of {Biological Membranes}}.
-\emph{Annual Review of Biochemistry} \textbf{72}, 175--207 (2003).}
-
-\bibitem[\citeproctext]{ref-simonsLipidRaftsSignal2000a}
-\CSLLeftMargin{6. }%
-\CSLRightInline{Simons, K. \& Toomre, D.
-\href{https://doi.org/10.1038/35036052}{Lipid rafts and signal
-transduction}. \emph{Nature Reviews Molecular Cell Biology} \textbf{1},
-31--39 (2000).}
-
-\bibitem[\citeproctext]{ref-schultzChemicalToolsLipid2023}
-\CSLLeftMargin{7. }%
-\CSLRightInline{Schultz, C.
-\href{https://doi.org/10.1021/acs.accounts.2c00851}{Chemical {Tools} for
-{Lipid Cell Biology}}. \emph{Accounts of Chemical Research} \textbf{56},
-1168--1177 (2023).}
-
-\bibitem[\citeproctext]{ref-schultzFlashClickMultifunctionalized2022a}
-\CSLLeftMargin{8. }%
-\CSLRightInline{Schultz, C., Farley, S. E. \& Tafesse, F. G.
-\href{https://doi.org/10.1021/jacs.2c02705}{{`{Flash} \& {Click}'}:
-{Multifunctionalized Lipid Derivatives} as {Tools To Study Viral
-Infections}}. \emph{Journal of the American Chemical Society}
-\textbf{144}, 13987--13995 (2022).}
-
-\bibitem[\citeproctext]{ref-hoglingerTrifunctionalLipidProbes2017}
-\CSLLeftMargin{9. }%
-\CSLRightInline{Höglinger, D. \emph{et al.}
-\href{https://doi.org/10.1073/pnas.1611096114}{Trifunctional lipid
-probes for comprehensive studies of single lipid species in living
-cells}. \emph{Proceedings of the National Academy of Sciences}
-\textbf{114}, 1566--1571 (2017).}
-
-\bibitem[\citeproctext]{ref-haberkantFatFabulousBifunctional2014}
-\CSLLeftMargin{10. }%
-\CSLRightInline{Haberkant, P. \& Holthuis, J. C. M.
-\href{https://doi.org/10.1016/j.bbalip.2014.01.003}{Fat \& fabulous:
-{Bifunctional} lipids in the spotlight}. \emph{Biochimica et Biophysica
-Acta - Molecular and Cell Biology of Lipids} \textbf{1841}, 1022--1030
-(2014).}
-
-\bibitem[\citeproctext]{ref-farleyTrifunctionalSphinganineNew2024a}
-\CSLLeftMargin{11. }%
-\CSLRightInline{Farley, S., Stein, F., Haberkant, P., Tafesse, F. G. \&
-Schultz, C.
-\href{https://doi.org/10.1021/acschembio.3c00554}{Trifunctional
-{Sphinganine}: {A New Tool} to {Dissect Sphingolipid Function}}.
-\emph{ACS Chemical Biology} \textbf{19}, 336--347 (2024).}
-
-\bibitem[\citeproctext]{ref-farleyTrifunctionalFattyAcid2024}
-\CSLLeftMargin{12. }%
-\CSLRightInline{Farley, S. E. \emph{et al.}
-\href{https://doi.org/10.1039/D4CC00974F}{Trifunctional fatty acid
-derivatives: The impact of diazirine placement}. \emph{Chemical
-Communications} \textbf{60}, 6651--6654 (2024).}
-
-\bibitem[\citeproctext]{ref-thomasTrifunctionalLipidDerivatives2025}
-\CSLLeftMargin{13. }%
-\CSLRightInline{Thomas, A. \emph{et al.} Trifunctional lipid
-derivatives: {PE}'s mitochondrial interactome. \emph{Chemical
-Communications} 10.1039.D4CC03599B (2025)
-doi:\href{https://doi.org/10.1039/D4CC03599B}{10.1039/D4CC03599B}.}
-
-\bibitem[\citeproctext]{ref-chiuPhotoaffinityLabelingReveals2025}
-\CSLLeftMargin{14. }%
-\CSLRightInline{Chiu, D.-C., Lin, H. \& Baskin, J. M. Photoaffinity
-{Labeling Reveals} a {Role} for the {Unusual Triply Acylated
-Phospholipid N-Acylphosphatidylethanolamine} in {Lactate Homeostasis}.
-(2025)
-doi:\href{https://doi.org/10.26434/chemrxiv-2025-j8nqz}{10.26434/chemrxiv-2025-j8nqz}.}
-
-\bibitem[\citeproctext]{ref-yuChemoproteomicsApproachProfile2022}
-\CSLLeftMargin{15. }%
-\CSLRightInline{Yu, W., Lin, Z., Woo, C. M. \& Baskin, J. M.
-\href{https://doi.org/10.1021/acschembio.1c00584}{A {Chemoproteomics
-Approach} to {Profile Phospholipase D-Derived Phosphatidyl Alcohol
-Interactions}}. \emph{ACS Chemical Biology} \textbf{17}, 3276--3283
-(2022).}
-
-\bibitem[\citeproctext]{ref-mullerSynthesisCellularLabeling2021}
-\CSLLeftMargin{16. }%
-\CSLRightInline{Muller, R., Kojic, A., Citir, M. \& Schultz, C.
-\href{https://doi.org/10.1002/anie.202103599}{Synthesis and {Cellular
-Labeling} of {Multifunctional Phosphatidylinositol Bis}- and
-{Trisphosphate Derivatives}}. \emph{Angewandte Chemie International
-Edition} \textbf{60}, 19759--19765 (2021).}
-
-\bibitem[\citeproctext]{ref-plotly}
-\CSLLeftMargin{17. }%
-\CSLRightInline{Inc., P. T. Collaborative data science. (2015).}
-
-\bibitem[\citeproctext]{ref-ramnathvaidyanathanHtmlwidgetsHTMLWidgets2015}
-\CSLLeftMargin{18. }%
-\CSLRightInline{Ramnath Vaidyanathan \emph{et al.} Htmlwidgets: {HTML
-Widgets} for {R}. (2015).}
-
-\bibitem[\citeproctext]{ref-thompsonTandemMassTags2003}
-\CSLLeftMargin{19. }%
-\CSLRightInline{Thompson, A. \emph{et al.}
-\href{https://doi.org/10.1021/ac0262560}{Tandem {Mass Tags}: {A Novel
-Quantification Strategy} for {Comparative Analysis} of {Complex Protein
-Mixtures} by {MS}/{MS}}. \emph{Analytical Chemistry} \textbf{75},
-1895--1904 (2003).}
-
-\bibitem[\citeproctext]{ref-birhanuMassSpectrometrybasedProteomics2023}
-\CSLLeftMargin{20. }%
-\CSLRightInline{Birhanu, A. G.
-\href{https://doi.org/10.1186/s12014-023-09424-x}{Mass
-spectrometry-based proteomics as an emerging tool in clinical
-laboratories}. \emph{Clinical Proteomics} \textbf{20}, (2023).}
-
-\bibitem[\citeproctext]{ref-boysClinicalApplicationsMass2023}
-\CSLLeftMargin{21. }%
-\CSLRightInline{Boys, E. L., Liu, J., Robinson, P. J. \& Reddel, R. R.
-\href{https://doi.org/10.1002/pmic.202200238}{Clinical applications of
-mass spectrometry-based proteomics in cancer: {Where} are we?}
-\emph{PROTEOMICS} \textbf{23}, 2200238 (2023).}
-
+\begin{CSLReferences}{0}{1}
 \end{CSLReferences}

### 2025-11-28 HourlyTracking/202509_GG-Hours.qmd
Pushing latest formatting edit of manuscript

--- 2025-09-04 HourlyTracking/202508_GG-Hours.qmd
@@
 title: Lipid Interactome Monthly Invoice
-subtitle: August 2025
+subtitle: Invoice Number 20250901
 author: "Gaelen Guzman"
-date: "2025 09 04"
+date: "2025 10 31"
 output: 
@@
   - "\\fancyhead[R]{2025 09 04}"
+  - "\\fancyhead[R]{Invoice Number 20250901}"
   - "\\fancyfoot{}"
@@
 
-Please find below the hours I logged for the month of August 2025, with descriptions of each day's activity.
+Please find below the hours I logged for the month of September 2025, with descriptions of each day's activity.
 In total, I performed 5 hours of work at an hourly rate of $50 (USD), for a total bill of $250.
@@
   select(Date, Hours, Activity) |>
-  filter(Date >= as.Date("2025-08-01") & Date < as.Date("2025-09-01")) %>%  # Filter for April 2025
+  filter(Date >= as.Date("2025-09-01") & Date < as.Date("2025-10-01")) %>%  # Filter for April 2025
   glimpse()

### 2025-11-28 HourlyTracking/202510_GG-Hours.qmd
Pushing latest formatting edit of manuscript

--- 2025-09-04 HourlyTracking/202508_GG-Hours.qmd
@@
 title: Lipid Interactome Monthly Invoice
-subtitle: August 2025
+subtitle: Invoice Number 20251001
 author: "Gaelen Guzman"
-date: "2025 09 04"
+date: "2025 10 31"
 output: 
@@
   - "\\fancyhead[C]{Lipid Interactome Monthly Invoice}"
-  - "\\fancyhead[R]{2025 09 04}"
+  - "\\fancyhead[R]{2025 10 31}"
+  - "\\fancyhead[R]{Invoice Number 20251001}"
   - "\\fancyfoot{}"
@@
 
-Please find below the hours I logged for the month of August 2025, with descriptions of each day's activity.
-In total, I performed 5 hours of work at an hourly rate of $50 (USD), for a total bill of $250.
+Please find below the hours I logged for the month of October 2025, with descriptions of each day's activity.
+In total, I performed 2 hours of work at an hourly rate of $50 (USD), for a total bill of $100.
 
@@
   select(Date, Hours, Activity) |>
-  filter(Date >= as.Date("2025-08-01") & Date < as.Date("2025-09-01")) %>%  # Filter for April 2025
+  filter(Date >= as.Date("2025-10-01") & Date < as.Date("2025-11-01")) %>%  # Filter for April 2025
   glimpse()
